### 2018-05-23 atomic-swaps/atomic-swaps-paper/intro.tex
initial commit for atomic swap paper

\section{Introduction}\label{sec:intro}
\subsection{The Evolution of Atomic Swaps\cite{altcoin}:}
Atomic swaps enables trade across blockchains safely and quickly. This idea is being discussed since 2013. Atomic means that if the swap is not successful neither part loses anything. In other words, the swaps is either executed or not. Atomic swaps can be on-chain or off-chain. Off-chain swaps are instant, private and they require almost zero-fee. Both type of swaps utilize hashed-time-locked-contracts (HTLCs). This guarantees that a party can't take any funds before it offers its own.

Decred is the \textbf{first on-chain atomic swap}~\cite{decred}. One challenge to be overcome in Decred is that new blocks should be mined to show the change of ownership (it makes the system slower).

\textbf{The first on-chain Ethereum—Bitcoin atomic swap} is realized by Altcoin.io. Swaps take 2-3 mins.

\textbf{The first off-chain atomic swap} over the lightning network is realized by Lightning Labs. Lightning network enables the exchange of coins, off-chain. It creates payment channels. After the transaction is completed, the chains are updated and the channels are closed. It is scalable.

Their next goal: atomically swap any token for any other token, regardless of the blockchain it resides on.

\subsection{Atomic Swap of ERC20 Tokens on the Raiden Network~\cite{Raiden}:}
Raiden Network is similar to Bitcoin’s Lightning Network, but for Ethereum’s blockchain. It will enable instant, low-fee and scalable micro payments of ERC20 compliant tokens.

Problem in decentralised exchanges: sacrificing transaction speed for settlement on-chain.

\subsection{Republic Protocol ~\cite{zhang2017republic}:}
Republic: a decentralized open-source dark pool protocol facilitating atomic swaps between cryptocurrency pairs across the Bitcoin and Ethereum blockchains. Trades are on a hidden orderbook and the matching is done using secure multiparty computation. It is a secure, decentralized, scalable dark pool protocol capable of handling billions in trading volume daily. It facilitates the exchange of Ethereum, ERC20 and Bitcoin cryptocurrencies through a decentralized dark pool.

execution without exposing price and volume 
no trusted intermediary to operate a dark pool (dark pool = private exchanges where financial assets and instruments are traded and matched by an engine running on a hidden order book)

\section{Our Implementation}

\begin{itemize}
  \item ETH to ERC20 token atomic swap is implemented.
  \item ERC20 to ERC20 token atomic swap is implemented. 
  \item One contract can perform several swaps. Each swap is assigned a swapID.   
  \item Each swap has three states: OPEN, CLOSED or EXPIRED.
\end{itemize}

### 2018-05-28 frontrunning/Latex/main.tex
Template for the fruntrunning paper

\documentclass[envcountsect]{llncs}
\sloppy
\pagestyle{headings} 
\bibliographystyle{abbrv}

% = = = = = Packages = = = = = %

\input{setup/packages}
\input{setup/macros}
\input{setup/table}

% = = = = = Title = = = = = %

\begin{document}
\frontmatter
\mainmatter

\title{\Large \bf Frontrunning}
%\author{}

%\author{}
\institute{Concordia University}

\maketitle

% = = = = = Abstract = = = = = %

\input{sections/abstract}

% = = = = = Main Body = = = = = %

\input{sections/paper}

% = = = = = Bibliography = = = = = %

\bibliography{bib/Frontrunning_Ref}
%\nocite{*}

% = = = = = End Notes = = = = = %

\clearpage
\appendix

\end{document}

### 2018-05-28 frontrunning/Latex/sections/paper.tex
Template for the fruntrunning paper

% !TEX root = ../main.tex
\section{Introductory Remarks}

\subsection{What is frontrunning?} %Definition of frontrunning
%Traditional
%WRT blockchain and decentralization
\subsection{Miners and their power} 
%Transaction order, can be used for frontrunning

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =

\section{Related Work}

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =

\section{Comparison Framework}

Solutions: \par\noindent
Criteria:

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =

\section{Frontrunning Attacks}

\subsection{Financial Markets}
%oders, exchanges

\subsection{Non-financial Applications}
Applications, Ghazal, register domains before the user, (domain squatting?) \par\noindent
Other applications (look at Dapps or other blockchain use cases)\par\noindent
Arbitrage (buy before the order, sell to the original order) (other scenarios)\par\noindent
Maker griefing (attack on the system?s reputation itself)\par\noindent
Etherdelta case: Fill the order when cancelling transaction is sent. What would be the profitable scenario here?

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =

\section{Implications}

Historical evidence of such attacks:\par\noindent
Status ICO [link]\par\noindent
Bancor frontrunning [link, link]\par\noindent
?
New attacks:\par\noindent
Ghazal\par\noindent
Find more applications to frontrun, not necessarily monetary gain/financial

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
\section{Mitigations}

Commit / reveal methods
\begin{itemize}
\item{Send the hash first, send the actual data after (sealed-bid auctions)}
\item{Proof of burn methods (generate random addresses with no private keys)}
\end{itemize}
Submarines
\begin{itemize}
\item{The method described in HD can be optimized and more functional with the new changes to ethereum and solidity}
\item{Submarines 2.0: There can be a new way of doing this (new WRT hackingditributed article), can predict smart contract addresses using the nonce and data of the contract (forwarder/refunder), so funds can be sent to these addresses and then contracts can be deployed} 
\begin {itemize}
\item{Pros: new addresses, no indication of the order (Anonymity-set)}
\item{Cons: DDoS? Requires 3 transactions for each order?} >> 1 send the funds 2 Deploy the contract 3 call the function
\end{itemize}
\item{Other methods? Consensus protocol based solutions?}

\end{itemize}
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =

\section{Concluding Remarks}

%\subsubsection*{Acknowledgements.}

### 2018-06-12 frontrunning/Latex/sections/paper.tex
[frontrunning] notes and stuff on status ico

@@
 
-Historical evidence of such attacks:\par\noindent
-Status ICO [link]\par\noindent
-Bancor frontrunning [link, link]\par\noindent
-?
+\subsection{Historical evidence of such attacks:}\par\noindent
+There has been many incidents of frontrunning in real world blockchains specially where it facilitates monetary gain. Here we will analyze the evidence of these incidents:
+
+% NOTE: This seperation can also happen by another category, like: frontrunning by miners: status ico F2pool, and frontrunning by others
+
+\subsubsection{Status ICO}
+In July 2017, Status.im did their ICO and they reached their cap, hence closing the ICO, within 3 hours, by collecting over 200 million dollars (300K Ether) worth of Ethereum ~\cite{statusicoanalysis}.
+%NOTE: ICO Initial Coin Offering should be explained probably in introduction section.
+the process of ICO smart contract and how the capped system works --> limited time/funds can be included in the ico and why people would try to get in as soon as possible, explain how their investment strategy works and such.
+Maybe the second half could be explained here to say why frontrunning an ICO makes sense?
+% add more on capped ICOs, status used Distribution & Dynamic Ceilings : https://blog.status.im/distribution-dynamic-ceilings-e2f427f5cca  ~\cite{statuswhitepaper}
+
+% The dynamic ceiling and prevention of bigger investments getting their full investment in could be the reason behind the design of F2pool move, by having multiple addresses each contributing around 100ETH to the ICO smart contract, instead of having one big transaction in.
+%Also the ICO smart contract only accepted transactions with gas price lower than 50gwei, unless they were whitelisted before.
+this was for preventing high gas payers to get in front of the line.
+although as this was not clearly communicated to users (UX issues?), there were tons of transactions that failed due to high gas price but also clogged the ethereum network as the miners chose transactions with higher gas price to be included in their blocks.
+
+% weird findings: apparently all the tokens bought by f2pool was transfered to Yunbi, the chinese exchange: 0xB6c3647F55085B9a327404Fe8B718076Ee19245a
+
+% I would like to spend some time to make charts from the transactions happening on the date of the Status ICO
+% this will include: The blocks mined by F2Pool, containing transactions (~100 ETH) to Status ICO, other blocks mined in that time period, the movement of status tokens from those addresses allegedly linked to F2Pool (or/and Yunbi in this case).
+% https://github.com/corpetty/ICO_analysis/blob/master/status/Status.ipynb
+% https://github.com/corpetty/py-etherscan-api
+
+\subsubsection{Bancor}
+
 New attacks:\par\noindent

### 2018-06-13 frontrunning/Latex/sections/paper.tex
[frontrunning] More on status ICO

@@
 \subsubsection{Status ICO}
-In July 2017, Status.im did their ICO and they reached their cap, hence closing the ICO, within 3 hours, by collecting over 200 million dollars (300K Ether) worth of Ethereum ~\cite{statusicoanalysis}.
+ICO, Initial Coin Offering, is one of the blockchain applications, specially blockchains such as Ethereum with smart contract capability.
+The common practice is to deploy a smart contract on the blockchain indicating the details of the ICO such as the trade ratio, when it starts and ends, and more details on how it will be capped.
+In June 2017, Status.im started their ICO and within 3 hours they reached the dynamic ceiling in place that triggered the end of the ICO, summing in 300,000 ether in funds, estimated at more than 200 million dollars at the time of their ICO.
+~\cite{statusicoanalysis}.
+The idea behind Dynamic Ceilings is to make it more costly for larger contributors,  in the form of transaction fees, which have to split their contributions to different addresses, with minimal impact to smaller contributors~\cite{statuswhitepaper}.
+On the time of the ICO there were reports of Ethereum network being unusable and transactions were not confirming.
+Further study showed that some mining pools (\todo: define mining pool) could have been manipulating the network for their own profit.
+
 %NOTE: ICO Initial Coin Offering should be explained probably in introduction section.
@@
 % weird findings: apparently all the tokens bought by f2pool was transfered to Yunbi, the chinese exchange: 0xB6c3647F55085B9a327404Fe8B718076Ee19245a
+
+% Proof of f2pool involvement: https://etherscan.io/address/0x5fb8373bf5086fb38ef0fb686b3092145de0d1c1
+% funds come from f2pool and refunds goes back to f2pool again
 

### 2018-06-14 frontrunning/Latex/sections/paper.tex
[frontrunning] notes on the meeting
[frontrunning] Bancor description + Bacor Frontrunning Attacks

@@
 
-\section{Implications}
+\section{Implications} %change this to something else
 
@@
 Further study showed that some mining pools (\todo: define mining pool) could have been manipulating the network for their own profit.
+
+%@shayan: make charts and figure out the orange seller
 
@@
 
-\subsubsection{Bancor}
+%What is Bancor and how it can be frontrun:%
+\subsubsection{Bancor} is an Ethereum-based application that allows users to exchange their tokens without any counterparty risk.
+This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users.
+Smart Tokens can be bought and sold through the users smart contract at an automatically calculated price which displays supply and demand.
+Doing so, Bancor protocol provides continuous liquidity for digital assets without relying on an orderbook as there is no requirement to match sellers and buyers.
 
+\par\noindent\textbf{Front-running Bancor} Unlike other existing decentralized exchanges, Bancor handles all the trades and exchanges on the Ethereum blockchain, so all the transactions are visible to the public for ~16s (the average Ethereum blocktime) before being included within a block.
+This leaves Bancor vulnerable to frontrunning~\cite{BancorIs7:online} as attackers are given enough time to modify the transactions ordering and gain favourable profits.
+Bancor frontrunning attack can occur in two ways:
+\begin{itemize}
+\item {\textbf{Miner Frontrunning.}} As mention, Bancor protocol uses an algorithm that automatically calculates the price of digital assets to provide market liquidity.
+Essentially, buy orders increase the price of the tokens while sell order decrease them.
+So  dishonest miners can easily reorder the pending transactions and  profit from a guaranteed price-rise.
+For example, they can place their own buy order ahead of any other large buy order transaction and receive a better rate than other Bancor users.
+\item {\textbf{Non-miner Frontrunning.}} In order for the Ethereum transactions to be executed on the Ethereum Virtual Machine (EVM), users have to pay for the computations in small amount of Ether called \textit{gas}~\cite{AccountT67:online}.
+The price users pay for transactions can increase or decrease how quickly the transactions are executed by the miners.
+Therefore, any regular non-miner users who run a full-node Ethereum client can modify the order of pending transactions by paying a more amount of gas \ie by monitoring the network, upon seeing a  pending buy transaction which will further increase the price of the asset, a fontrunner user can pay a higher gas price and send his transaction a head of that.
+By doing so, he achieves a better rate from any other Bancor users.
+\end{itemize}
+
+ %Mahsa ToDos:%
 New attacks:\par\noindent
 Ghazal\par\noindent
-Find more applications to frontrun, not necessarily monetary gain/financial
+%@mahsa: write on ghazal and namecoin but with the focus on ghazal front running applications
+%@ possibility of PoC attack (@shayan @mahsa)
+%===========================%
 
@@
 
-Commit / reveal methods
+Commit / reveal methods %namecoin story @mahsa
 \begin{itemize}

### 2018-07-03 frontrunning/Latex/sections/paper.tex
pickle transaction list, minor edits on the paper
[frontrunning] Bancor frontrunning attacks explained in details

--- 2018-06-13 frontrunning/Latex/sections/paper.tex
@@
 \subsection{Financial Markets}
-%oders, exchanges
+%orders, exchanges
+% @shayan: front runnign attacks on 0x and etherdelta . if one past one found add it to Implications!
 
@@
 
+% maybe inlcude 0xbitcoin ERC721 mineable tokens frontrunning!
+
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
 
-\section{Implications}
+\section{Implications} %change this to something else
 
@@
 
-\subsubsection{Bancor}
+%What is Bancor and how it can be frontrun:%
 
+\subsubsection{Bancor} is an Ethereum-based application that allows users to exchange their tokens without any counterparty risk.
+This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users.
+Smart Tokens can be bought and sold through the users smart contract at an automatically calculated price which displays supply and demand.
+Doing so, Bancor protocol provides continuous liquidity for digital assets without relying on an orderbook as there is no requirement to match sellers and buyers.
+
+\par\noindent\textbf{Front-running Bancor} Recently, researchers have shown that Bancor is vulnerable to frontrunning attacks.
+Implemented on the Ethereum blockchain, when Bancor transactions are broadcast to the network, they sit in a pending transaction pool known as \textit{mempool} waiting for the miners to mine them.
+Since Bancor handles all the trades and exchanges on the Ethereum blockchain (unlike other existing decentralized exchanges), these transactions are all visible to the public for 16s (the average Ethereum blocktime) before being included within a block.
+This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favourable profits~\cite{BancorIs7:online}.
+Bancor frontrunning attacks can occur in two different ways:
+
+\begin{itemize}
+\item {\textbf{Miner Frontrunning.}} As mentioned, Bancor protocol uses an algorithm that automatically calculates the price of digital assets to provide better market liquidity.
+In the Bancor model, essentially buy orders increase the price of the tokens while sell order decrease it.
+Since the Blockchain miners are the only parties who can decide on the order of transactions within a block, they can easily intercept and reorder the pending transactions sitting in the mempool and profit from a guaranteed price-rise.
+For example, a miner learns about the pending \textit{buy} transaction of 1000 Ether, based on the Bancor design, if this transaction goes through, it causes the price of Ether to increase.
+So the dishonest miner can step in front of this transaction and  place his own buy order ahead of it.
+So he would simply create his \textit{buy} of 1000 Ether and include it within a block and now he mines the previous \textit{buy} transaction of 1000 Ether.
+Doing so, he would receive a better rate than other Bancor user, can sell the tokens he has received and gain a price advantage at the expense of others.
+Similarly, a dishonest miner can sell hi tokens in front, if he sees a pending \textit{sell} transaction.
+
+\item {\textbf{Non-miner Frontrunning.}} Researchers have also shown that a regular non-miner user can also front-run Bancor.
+In order for the Bancor transactions to be executed on the Ethereum Virtual Machine (EVM),  users have to pay for the computations in small amount of Ether called \textit{gas}~\cite{AccountT67:online}.
+The price that users pay for transactions (a.k.a.
+transaction fees) can increase or decrease how quickly they are executed and included within the blocks by the miners.
+This is because the Ethereum miners consume resources to process the transactions and so receive the transaction fees after creating the blocks.
+Once seeing two identical transactions with different transaction fees, profit maximizers miners are free to mine select the transaction which offers the highest fee.
+Therefore, any regular non-miner users who run a full-node Ethereum client can modify the order of pending transactions by paying a more amount of gas \ie by monitoring the network, upon seeing a  pending \textit{buy} transaction which will further increase the price of the asset, a font-runner user can pay a higher gas price and send his transaction a head of that.
+By doing so, he achieves a better rate from any other Bancor users.
+
+\end{itemize}
+
+ %Mahsa ToDos:%
 New attacks:\par\noindent
 Ghazal\par\noindent
-Find more applications to frontrun, not necessarily monetary gain/financial
+%@mahsa: write on ghazal and namecoin but with the focus on ghazal front running applications
+%@ possibility of PoC attack (@shayan @mahsa)
+%===========================%
 

### 2018-07-03 frontrunning/Latex/sections/paper.tex
[frontrunning] frontrunning attacks on namespaces

@@
 
- %Mahsa ToDos:%
-New attacks:\par\noindent
-Ghazal\par\noindent
-%@mahsa: write on ghazal and namecoin but with the focus on ghazal front running applications
+%Following section talks about frontrunning in namespaces but limited to Ghazal. Will talk about NameCoin in the section of mitigations (commit & reveal method) 
+\subsubsection{Namespaces} Although frontrunning attacks have been more showcased in the context of decentralized exchanges and trading systems, they are are not yet limited to the financial markets.
+Frontrunning can occur within other blockchain based applications such as naming systems.
+Blockchain-based namespaces have been introduced to eliminate the role of central parties \ie domain name system (DNS) which introduces single point of failures in the entire web.
+One such system is Ghazal, an Ethereum-based naming and PKI system~\cite{moosavighazal}.
+Ghazal users rely on the Ethereum blockchain to register their \texttt{.ghazal} domain names and bind certificates to those names.
+In Ghazal model, a user would register domain name by executing the \textit{registerdomain} function from the Ghazal smart contract with the domain name in plain text as the function argument.
+As mentioned before, These transactions will sit in the mempool so that it would be mined by Ethereum miners and included in the block.
+During this period in which the transaction is not yet confirmed, frontrunning attack can occur by (i) dishonest miners and/or (ii) regular non-miner user.
+In the first case, a miner would intercept the \textit{registerdomain} transaction and register that name ahead of the user.
+A regular non-miner node in the Ethereum network can frontrun other user's \textit{registerdomain} at a good profit by paying higher transaction fees.
+In both cases the adversarial party could sell the domain name to the users for higher price.
+
 %@ possibility of PoC attack (@shayan @mahsa)

### 2018-07-04 frontrunning/Latex/sections/paper.tex
[frontrunning] some on traditional frontrunning and introductory remarks

@@
 %Traditional
+Frontrunning was first appeared on the Chicago Board Options Exchange (SBOE) ~\cite{markham1988front}, and was later defined by \textit{Secrities Exchange Comission} in 1977 as following:
+\begin{quote}
+The practice of effecting an options transaction based upon non-public information regarding an impending block transaction in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.
+~\cite{sec1978cboe}
+\end{quote} 
+On the years after there were ongoing discussions between self-regulatory exchanges and SEC to regulate, detect and define laws to deal with frontrunning~\cite{markham1988front}, with SEC stating: 
+\begin{quote}
+it seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge.
+\footnote{Securities Exchange Act Release No.
+14156, November 19, 1977, (Letter from George A.
+Fitzsimmons, Secretary, Securities and Exchange Commission to Joseph W.
+Sullivan, President  CBOE).}
+\end{quote} 
+% http://3197d6d14b5f19f2f440-5e13d29c4c016cf96cbbfd197c579b45.r81.cf1.rackcdn.com/collection/papers/1970/1978_OptMkt_06_Chapter_III_3.pdf
+Initially the frontrunning policies only applied to certain options, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{sec2012frontrunning}.
+
+%In actuality, front-running is more complex than this definition suggests.
+It encompasses at least three forms of conduct, each of which raises different regulatory and policy issues.9 They are: (1) trading by third parties who are tipped on an impending block trade ("tippee" trading); (2) transactions in which the owner or purchaser of the block trade itself engages in the offset- ting futures or options transaction as a means of "hedging" against price fluctuations caused by the block transaction ("self-front-running"); 1 ° and (3) transactions where a broker with knowledge of an impending customer block order trades ahead of that order for the broker's own profit ("trading ahead").
+% from JerryWMarkhamFrontRunning.pdf
+
+% More to read and add from : SECURITIES AND EXCHANGE COMMISSION Release No. 34-67079. pdf included in Related_Documents
+% https://www.sec.gov/about/annual_report/1988.pdf
+
+\textbf{Frontrunning in Blockchains}: The main discussion regarding regulations for exchanges on the topic of frontrunning, comes from the fact that information access is layered and some could be accessed only by insider actors, such as the broker, the IT administrator, \etc.
+In the blockchain world, everyone running a node of such blockchain could potentially have access to such information, hence it makes it much easier for any actor to engage in frontrunning within applications running on the blockchain.
+Some other key differences are the fact that such actor can stay anonymous and also enforcing regulation is infeasible in traditional sense, however the decentral application could be designed in such a way to prevent frontrunning attacks.
+
 %WRT blockchain and decentralization
@@
 % maybe inlcude 0xbitcoin ERC721 mineable tokens frontrunning!
+% mint: https://etherscan.io/tx/0x9883bc3ad018fd2b649982f88fbad7dc5abcb8f11c4f1d87ef814ba30c2b3428
 
@@
 Doing so, he would receive a better rate than other Bancor user, can sell the tokens he has received and gain a price advantage at the expense of others.
-Similarly, a dishonest miner can sell hi tokens in front, if he sees a pending \textit{sell} transaction.
+Similarly, a dishonest miner can sell his tokens in front, if he sees a pending \textit{sell} transaction.
 

### 2018-07-04 frontrunning/Latex/sections/paper.tex
[frontrunning] minor changes and added some notes

@@
 
-\textbf{Frontrunning in Blockchains}: The main discussion regarding regulations for exchanges on the topic of frontrunning, comes from the fact that information access is layered and some could be accessed only by insider actors, such as the broker, the IT administrator, \etc.
-In the blockchain world, everyone running a node of such blockchain could potentially have access to such information, hence it makes it much easier for any actor to engage in frontrunning within applications running on the blockchain.
+% more on the definition in the wiki page: https://en.wikipedia.org/wiki/Front_running
+
+% [optional but interesting] Here we can talk about Principal–agent problem: https://en.wikipedia.org/wiki/Principal%E2%80%93agent_problem
+
+\textbf{Frontrunning in Blockchains}: One of the main discussion regarding regulations for exchanges on the topic of frontrunning, comes from the fact that information access is layered and some could be accessed only by insider actors, such as the broker, the IT administrator, \etc.
+In the blockchain world, everyone running a node of one blockchain could potentially have access to such information, hence it makes it is more susceptible for any actor to engage in frontrunning within applications running on the blockchain.
 Some other key differences are the fact that such actor can stay anonymous and also enforcing regulation is infeasible in traditional sense, however the decentral application could be designed in such a way to prevent frontrunning attacks.
@@
 \section{Related Work}
+
+~\cite{malinova2017market}
+~\cite{aune2017footprints}
 
@@
 % @shayan: front runnign attacks on 0x and etherdelta . if one past one found add it to Implications!
+% http://hackingdistributed.com/2017/08/13/cost-of-decent/
 
@@
 % mint: https://etherscan.io/tx/0x9883bc3ad018fd2b649982f88fbad7dc5abcb8f11c4f1d87ef814ba30c2b3428
+
+% @Mahsa: some interesting read (check out the references) for domain name front running : https://en.wikipedia.org/wiki/Domain_name_front_running
 

### 2018-07-06 frontrunning/Latex/sections/paper.tex
[frontrunning] Restructure and notes from meeting

@@
 % !TEX root = ../main.tex
-\section{Introductory Remarks}
+
+\section{Introduction}
+
+% PAPER BEING SOLD HERE
+
+\section{Priliminary}
 
 \subsection{What is frontrunning?} %Definition of frontrunning
+
 %Traditional
+
+%talking about front running
+
+%Miners in Bitcoin can do selfish mining and such but in theory
+% here we talk about miners actually being malicious(?) to profit themselves.
+
+%In actuality, front-running is more complex than this definition suggests.
+It encompasses at least three forms of conduct, each of which raises different regulatory and policy issues.9 They are: (1) trading by third parties who are tipped on an impending block trade ("tippee" trading); (2) transactions in which the owner or purchaser of the block trade itself engages in the offset- ting futures or options transaction as a means of "hedging" against price fluctuations caused by the block transaction ("self-front-running"); 1 ° and (3) transactions where a broker with knowledge of an impending customer block order trades ahead of that order for the broker's own profit ("trading ahead").
+% from JerryWMarkhamFrontRunning.pdf
+
+% More to read and add from : SECURITIES AND EXCHANGE COMMISSION Release No. 34-67079. pdf included in Related_Documents
+% https://www.sec.gov/about/annual_report/1988.pdf
+
+% more on the definition in the wiki page: https://en.wikipedia.org/wiki/Front_running
+
+% [optional but interesting] Here we can talk about Principal–agent problem: https://en.wikipedia.org/wiki/Principal%E2%80%93agent_problem
+
+% ticket scalping : https://en.wikipedia.org/wiki/Ticket_resale
+
+\subsection{Historical Context}
 Frontrunning was first appeared on the Chicago Board Options Exchange (SBOE) ~\cite{markham1988front}, and was later defined by \textit{Secrities Exchange Comission} in 1977 as following:
@@
 
-%In actuality, front-running is more complex than this definition suggests.
-It encompasses at least three forms of conduct, each of which raises different regulatory and policy issues.9 They are: (1) trading by third parties who are tipped on an impending block trade ("tippee" trading); (2) transactions in which the owner or purchaser of the block trade itself engages in the offset- ting futures or options transaction as a means of "hedging" against price fluctuations caused by the block transaction ("self-front-running"); 1 ° and (3) transactions where a broker with knowledge of an impending customer block order trades ahead of that order for the broker's own profit ("trading ahead").
-% from JerryWMarkhamFrontRunning.pdf
-
-% More to read and add from : SECURITIES AND EXCHANGE COMMISSION Release No. 34-67079. pdf included in Related_Documents
-% https://www.sec.gov/about/annual_report/1988.pdf
-
-% more on the definition in the wiki page: https://en.wikipedia.org/wiki/Front_running
-
-% [optional but interesting] Here we can talk about Principal–agent problem: https://en.wikipedia.org/wiki/Principal%E2%80%93agent_problem
-
-\textbf{Frontrunning in Blockchains}: One of the main discussion regarding regulations for exchanges on the topic of frontrunning, comes from the fact that information access is layered and some could be accessed only by insider actors, such as the broker, the IT administrator, \etc.
+\subsection{Frontrunning in Blockchains}: One of the main discussion regarding regulations for exchanges on the topic of frontrunning, comes from the fact that information access is layered and some could be accessed only by insider actors, such as the broker, the IT administrator, \etc.
 In the blockchain world, everyone running a node of one blockchain could potentially have access to such information, hence it makes it is more susceptible for any actor to engage in frontrunning within applications running on the blockchain.
@@
 
-%WRT blockchain and decentralization
-\subsection{Miners and their power}
-%Transaction order, can be used for frontrunning
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-
-\section{Related Work}
+\subsection{Related Work}
 
@@
 
+% Shayan: talk about frontrunning in other blockchains, such as privacy preserving blockchains --> no transparency less chance of frontrunning?  
+% this is a big problem with Dapps, what other blockchains support smart contracts that have this problem.
+
+% Mahsa: talk about namecoin frontrunning from the paper
+
+% NOTE: use double-spend paper (first)
+% talk about double-spend one kind of frontrunning (relationship between frontrunning vs double spend) rushing actors. 
+% Double-spending fast payments in bitcoin.pdf
+
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
 
-\section{Comparison Framework}
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
 
-Solutions: \par\noindent
-Criteria:
+%\section{Comparison Framework}
 
@@
 
+%NOTE: top 10 dapps, talk about frontrunning attacks on them.
+
 % @Mahsa: some interesting read (check out the references) for domain name front running : https://en.wikipedia.org/wiki/Domain_name_front_running
@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+
+\section{Potential Front runners} % Who and How.
+
+%WRT blockchain and decentralization
+
+% TALK ABOUT IT {Miners and their power}
+
+%Transaction order, can be used for frontrunning
+
+\subsection{Miners}
+
+% Mining blocks hence order of the transactions within a block --> reorder
+%
+
+% Use example of the paper, talk about status ICO or some other miner reorder frontrunning
+
+\subsection{non-miner}
+% Use high gasprice to get infront
+% Sybil attacks?
+%
+
+% Use example of  namecoin/domain . use an example of Alice wants to register a domain and bob uses GasPrice to get in front of Alice.
 
@@
 % NOTE: This seperation can also happen by another category, like: frontrunning by miners: status ico F2pool, and frontrunning by others
+
+% ICOs and ceiling
+% hard cap --> frontrun and buy the tokens in big chunk
+% dynamic ceiling, fair token distribution --> status ICO
 
@@
 Commit / reveal methods %namecoin story @mahsa 
+% 1) Go dark
 \begin{itemize}
@@
 \end{itemize}
+
+% How are we solving this in orderbooks?
+%shayan: Give the fees in a decental orderbook to the miners so change the incentive model and they are incentivized to act honestly
+%2) kill the incentive (change the incentive) ^ .
+
+% also call options on a random ending block, so timing of the incoming transactiion does not matter
+
+%3) change the mechanics. similar to double spend mitigation, fee structure. with gas limits gasprice limit (status ico did. and bancor after the attack)
+
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
@@
 
+% @shayan:
+% Could talk about a tool / a framework to detect frontrunning
+% Circle in the py-etherscan guy about having the tools to detect such things
+
 %\subsubsection*{Acknowledgements.}

### 2018-08-04 frontrunning/Latex/sections/paper.tex
[frontrunning] added some notes and literature
[frontrunning] notes from July 25, 2018
[frontrunning] some more notes

@@
 % PAPER BEING SOLD HERE
+% @mahsa summary of `What is frontrunning?` in 2 sentenses, frontrunning in blockchain and why is this important to consider in blockchain/dapp design
+% require more indepth academic look into the issue
 
-\section{Priliminary}
+\section{Preliminary}
 
 \subsection{What is frontrunning?} %Definition of frontrunning
+
+%Some notes (to be paraphrased):
+%if other market participants can obtain prior or contemporaneous knowledge of transactions, they may attempt to trade before the institutional investors can complete their trades, a practice known as front running.
+In financial markets, any sort of front running or information leakage is a serious concern.
+%We would like to ask what causes such front-running behaviour. There are two factors: (1) imperfect competition and (2) liquidity uncertainty
+~\cite{liang2005distressed} : talks about front running in illiquid markets (contains lots of useful definitions of frontrunning to talk about in this section)
+
+% @mahsa
 
@@
 % here we talk about miners actually being malicious(?) to profit themselves.
-
-%In actuality, front-running is more complex than this definition suggests.
-It encompasses at least three forms of conduct, each of which raises different regulatory and policy issues.9 They are: (1) trading by third parties who are tipped on an impending block trade ("tippee" trading); (2) transactions in which the owner or purchaser of the block trade itself engages in the offset- ting futures or options transaction as a means of "hedging" against price fluctuations caused by the block transaction ("self-front-running"); 1 ° and (3) transactions where a broker with knowledge of an impending customer block order trades ahead of that order for the broker's own profit ("trading ahead").
-% from JerryWMarkhamFrontRunning.pdf
-
-% More to read and add from : SECURITIES AND EXCHANGE COMMISSION Release No. 34-67079. pdf included in Related_Documents
-% https://www.sec.gov/about/annual_report/1988.pdf
 
@@
 \begin{quote}
-The practice of effecting an options transaction based upon non-public information regarding an impending block transaction in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.
+The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.
 ~\cite{sec1978cboe}
 \end{quote}
+
+%In actuality, front-running is more complex than this definition suggests.
+It encompasses at least three forms of conduct, each of which raises different regulatory and policy issues.9 They are: (1) trading by third parties who are tipped on an impending block trade ("tippee" trading); (2) transactions in which the owner or purchaser of the block trade itself engages in the offset- ting futures or options transaction as a means of "hedging" against price fluctuations caused by the block transaction ("self-front-running"); 1 ° and (3) transactions where a broker with knowledge of an impending customer block order trades ahead of that order for the broker's own profit ("trading ahead").
+% from JerryWMarkhamFrontRunning.pdf
+
+% More to read and add from : SECURITIES AND EXCHANGE COMMISSION Release No. 34-67079. pdf included in Related_Documents
+% https://www.sec.gov/about/annual_report/1988.pdf
+
 On the years after there were ongoing discussions between self-regulatory exchanges and SEC to regulate, detect and define laws to deal with frontrunning~\cite{markham1988front}, with SEC stating: 
@@
 Initially the frontrunning policies only applied to certain options, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{sec2012frontrunning}.
+
+%@shayan complete the historical context
 
@@
 
-%\section{Comparison Framework}
-
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
 
-\section{Frontrunning Attacks}
+\section{Frontrunning Attacks in Blockchain}
 

### 2018-08-05 atomic-swaps/atomic-swaps-paper/intro.tex
[atomic swaps] new table and figures

@@
 \section{Introduction}\label{sec:intro}
-\subsection{The Evolution of Atomic Swaps\cite{altcoin}:}
-Atomic swaps enables trade across blockchains safely and quickly.
-This idea is being discussed since 2013.
-Atomic means that if the swap is not successful neither part loses anything.
-In other words, the swaps is either executed or not.
+An atomic swap enables involving parties to exchange cryptocurrencies, tokens on or off-chain without the involvement of a third party.
+Atomicity guarantees that either both sides of the swap happen, or neither.
+The risk of one party losing their assets is minimized.
+The concept of atomic swaps, which provides safe and quick trades, is being discussed since 2013\cite{altcoin}.
 Atomic swaps can be on-chain or off-chain.
-Off-chain swaps are instant, private and they require almost zero-fee.
-Both type of swaps utilize hashed-time-locked-contracts (HTLCs).
-This guarantees that a party can't take any funds before it offers its own.
+Off-chain swaps are instant, private and they almost doesn't incur any fees.
+Both type of swaps utilize hashed-time-locked-contracts (HTLCs) to guarantee that a party can't take any funds before providing his fund.
 
-Decred is the \textbf{first on-chain atomic swap}~\cite{decred}. One challenge to be overcome in Decred is that new blocks should be mined to show the change of ownership (it makes the system slower).
+\section{Related Work}
+Decred realized \textbf{the first on-chain atomic swap} between Decred and Litecoin~\cite{decred}.
+The need to mine new blocks to show the change of ownership can make the Decred's system slower.
+\textbf{The first on-chain Ethereum-Bitcoin atomic swap} is realized by Altcoin.io(REF!!).
+Lightning Labs performed \textbf{the first off-chain atomic swap} over the lightning network.
+Lightning network enables the off-chain exchange of coins  by creating payment channels between the trading parties.
+After the transaction is completed, the chains are updated and the channels are closed.
+Lightning network enables fast and scalable transactions and the involving parties don't have to pay transaction fees for every transaction.
 
-\textbf{The first on-chain Ethereum—Bitcoin atomic swap} is realized by Altcoin.io. Swaps take 2-3 mins.
-
-\textbf{The first off-chain atomic swap} over the lightning network is realized by Lightning Labs.
-Lightning network enables the exchange of coins, off-chain.
-It creates payment channels.
-After the transaction is completed, the chains are updated and the channels are closed.
-It is scalable.
-
-Their next goal: atomically swap any token for any other token, regardless of the blockchain it resides on.
-
-\subsection{Atomic Swap of ERC20 Tokens on the Raiden Network~\cite{Raiden}:}
-Raiden Network is similar to Bitcoin’s Lightning Network, but for Ethereum’s blockchain. It will enable instant, low-fee and scalable micro payments of ERC20 compliant tokens.
-
-Problem in decentralised exchanges: sacrificing transaction speed for settlement on-chain.
-
-\subsection{Republic Protocol ~\cite{zhang2017republic}:}
-Republic: a decentralized open-source dark pool protocol facilitating atomic swaps between cryptocurrency pairs across the Bitcoin and Ethereum blockchains.
+%Their next goal: atomically swap any token for any other token, regardless of the blockchain it resides on.
+Ethereum’s Raiden Network is analogous to Bitcoin’s Lightning Network and it provides instant, low-fee and scalable exchanges~\cite{Raiden}.
+The atomic swap of ERC20 tokens are performed on Raiden network.%Problem in decentralised exchanges: sacrificing transaction speed for settlement on-chain.
+Zhang et al.
+propose Republic Protocol, which is a decentralized open-source dark pool protocol that provides atomic swaps of cryptocurrencies across Bitcoin and Ethereum blockchains~\cite{zhang2017republic}.%Republic: a  facilitating atomic swaps between cryptocurrency pairs across the .
 Trades are on a hidden orderbook and the matching is done using secure multiparty computation.
 It is a secure, decentralized, scalable dark pool protocol capable of handling billions in trading volume daily.
-It facilitates the exchange of Ethereum, ERC20 and Bitcoin cryptocurrencies through a decentralized dark pool.
+Their proposed system enables the exchange of Ether, ERC20 and Bitcoin over a decentralized dark pool.
+%execution without exposing price and volume, no trusted intermediary to operate a dark pool (dark pool = private exchanges where financial assets and instruments are traded and matched by an engine running on a hidden order book)Republic Protocol removes the risk of asset theft, confiscation or possibility of interference from a malicious exchange operator.
+Components: Decentralized hidden order book, Decentralized order matching, Atomic swap infrastructure, REN token nodes have no incentive to ignore an order, especially since they do not know the identity of the trader, nor the details of the order
+In an atomic cross-chain swap setting, involving parties perform exchange across different blockchains like exchanging Bitcoin for Ether.
+In ~\cite{herlihy2018atomic}, a cross-chain swap is modeled as a directed graph where vertices correspond to the parties in the protocol and the arcs represent the transfers between them.
+%An atomic swap protocol can be thought of as a trust-free, Byzantine-hardened form of distributed commitment.
+An atomic cross-chain swap is a special case of a distributed atomic transaction, although not all atomic transactions can be expressed as cross-chain swaps.
+If swaps are recurrent, then it would be useful to conduct swaps off-chain as much as possible, similar to the way that Lightning and Raiden networks support off-chain transactions for bitcoin and ERC20 tokens.
 
-execution without exposing price and volume 
-no trusted intermediary to operate a dark pool (dark pool = private exchanges where financial assets and instruments are traded and matched by an engine running on a hidden order book)
+%FAIR EXCHANGE?
+%The fair exchange problem ~\cite{franklin1998secure}, ~\cite{micali2003simple} is a precursor to the atomic cross-chain swap problem.
+Alice has a digital asset Bob wants, and vice-versa, and at the end of the protocol, either Alice and Bob have exchanged assets, or they both keep their assets.
+In the absence of blockchains, trusted, or semi-trusted third parties are required, but roles of those trusted parties can be minimized in clever ways.
 
@@
 \end{itemize}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=1\textwidth]{approve}
+\caption{approve}
+\label{fig:withapprove}
+\vspace{-10pt}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=1\textwidth]{withoutapprove}
+\caption{without approve}
+\label{fig:withapprove}
+\vspace{-10pt}
+\end{figure}
+
+\section{Comparison of Token Standards}
+\subsection{ERC721}
+non-fungible, ERC20 compatible
+\subsection{ERC223}
+ERC20 has the problem of "non-recovarable" coins
+ERC20 needs to execute two functions to transfer coins: approve and transferFrom. ERC223 consumes half the amount of gas than the amount needed to transfer an ERC20 token.
+ERC223 offers 3 improvements:
+\begin{itemize}
+  \item no lost tokens
+  \item reject non-supported tokens
+  \item energy saving
+\end{itemize}
+
+tokenFallback: the receiving contract has a chance to do some work.
+\subsection{ERC777}
+
+\textbf{TO-DO:}
+\begin{itemize}
+  \item explain how we count transactions and the difference between margin and fixed transactions
+  \item introduce more settings in the table
+\end{itemize}
+
+\begin{table}[h!]
+\footnotesize
+\centering
+%\Huge
+%\resizebox{\columnwidth}{!}{%
+\begin{tabular}{ |c|c|c|c|c|c| }
+  \hline
+   maker & taker & class & order transactions (margin) & account (onetime) transactions (fixed) \\ \hline
+   ERC20 & ETH & approve & 3 & \\ \hline
+   ERC20 & ERC20 & approve & 4 & \\ \hline
+   ERC20-like & ETH & w/o approve & 5 & \\ \hline
+   ERC20-like & ERC20-like & w/o approve & 6 & \\ \hline
+   ERC223 & ETH & & &\\ \hline
+   ERC20 & ETH & collateralized & &\\ \hline
+   ERC20 & ETH & partially collateralized & &\\ \hline
+\end{tabular}
+\caption {swaps}
+%}
+\end{table}\label{Table:Comparison of different swaps}

### 2018-08-06 frontrunning/Latex/sections/paper.tex
[frontrunning] Historical Context draft + adding related documents

@@
 \subsection{Historical Context}
-Frontrunning was first appeared on the Chicago Board Options Exchange (SBOE) ~\cite{markham1988front}, and was later defined by \textit{Secrities Exchange Comission} in 1977 as following:
+Frontrunning was first appeared on the Chicago Board Options Exchange (CBoE) ~\cite{markham1988front}, and was identified by \textit{Securities Exchange Commission} in 1977 as the following:
 \begin{quote}
 The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.
-~\cite{sec1978cboe}
+~\cite{sec1978optionsmarket}
 \end{quote}
@@
 
-On the years after there were ongoing discussions between self-regulatory exchanges and SEC to regulate, detect and define laws to deal with frontrunning~\cite{markham1988front}, with SEC stating: 
+On the years after there were ongoing discussions between self-regulatory exchanges (\eg CBoE) and SEC to regulate, detect and define laws and regulations to deal with frontrunning~\cite{markham1988front}, with \textit{SEC} stating:
 \begin{quote}
-it seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge.
+It seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge.
 \footnote{Securities Exchange Act Release No.
@@
 \end{quote}
-% http://3197d6d14b5f19f2f440-5e13d29c4c016cf96cbbfd197c579b45.r81.cf1.rackcdn.com/collection/papers/1970/1978_OptMkt_06_Chapter_III_3.pdf
-Initially the frontrunning policies only applied to certain options, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{sec2012frontrunning}.
 
-%@shayan complete the historical context
+As defining what exactly is considered illegal front-running required more knowledge of how these new markets behave, CBoE and other exchanges (and brokers) issued educational circulars for their members asserting that frontrunning violates existing rules, with some examples of what is considered frontrunning.
+However difference of opinion regarding the unfairness o front running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~cite{sec1978optionsmarket}.
+
+Further reading on the early details on the history and challenges of detecting and regulating frontrunning can be found in~\cite{markham1988front} .
+% TODO: add a more recent publication here as well!
+
+Initially the frontrunning policies only applied to certain option markets, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{finra_2002}, which then in 2012 with the new amendment, FINRA Rule 5270, the frontrunnning rule was extended to cover trading in an option, derivative, or other financial instruments overlying a security with some exceptions~\cite{finra_2012, sec2012frontrunning}.
 
 \subsection{Frontrunning in Blockchains}: One of the main discussion regarding regulations for exchanges on the topic of frontrunning, comes from the fact that information access is layered and some could be accessed only by insider actors, such as the broker, the IT administrator, \etc.
-In the blockchain world, everyone running a node of one blockchain could potentially have access to such information, hence it makes it is more susceptible for any actor to engage in frontrunning within applications running on the blockchain.
-Some other key differences are the fact that such actor can stay anonymous and also enforcing regulation is infeasible in traditional sense, however the decentral application could be designed in such a way to prevent frontrunning attacks.
+In the blockchain world, anyone running a node of one blockchain could potentially have access to such information, hence it makes it is more susceptible for any actor to engage in frontrunning within applications running on the blockchain.
+Some other key differences are the fact that such actor can stay anonymous and also enforcing regulation is infeasible in traditional sense, however a decentral application could be designed in such a way to mitigate frontrunning attacks.
 

### 2018-08-06 frontrunning/Latex/sections/paper.tex
[frontrunning] minor changes

@@
 \subsection{Historical Context}
-Frontrunning was first appeared on the Chicago Board Options Exchange (CBoE) ~\cite{markham1988front}, and was identified by \textit{Securities Exchange Commission} in 1977 as the following:
+Frontrunning was first appeared on the Chicago Board Options Exchange ( \textit{CBoE}) ~\cite{markham1988front}, and was identified by \textit{Securities Exchange Commission} in 1977 as the following:
 \begin{quote}
@@
 
-On the years after there were ongoing discussions between self-regulatory exchanges (\eg CBoE) and SEC to regulate, detect and define laws and regulations to deal with frontrunning~\cite{markham1988front}, with \textit{SEC} stating:
+On the years after there were ongoing discussions between self-regulatory exchanges (\eg \textit{CBoE}) and  \textit{SEC} to regulate, detect and define laws and regulations to deal with frontrunning~\cite{markham1988front}, with \textit{SEC} stating:
 \begin{quote}
@@
 Fitzsimmons, Secretary, Securities and Exchange Commission to Joseph W.
-Sullivan, President  CBOE).}
+Sullivan, President  CBoE).}
 \end{quote}
 
-As defining what exactly is considered illegal front-running required more knowledge of how these new markets behave, CBoE and other exchanges (and brokers) issued educational circulars for their members asserting that frontrunning violates existing rules, with some examples of what is considered frontrunning.
+As defining what exactly is considered illegal front-running required more knowledge of how these new markets behave, \textit{CBoE} and other exchanges (and brokers) issued educational circulars for their members asserting that frontrunning violates existing rules, with some examples of what is considered frontrunning.
 However difference of opinion regarding the unfairness o front running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~cite{sec1978optionsmarket}.
@@
 
-Initially the frontrunning policies only applied to certain option markets, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{finra_2002}, which then in 2012 with the new amendment, FINRA Rule 5270, the frontrunnning rule was extended to cover trading in an option, derivative, or other financial instruments overlying a security with some exceptions~\cite{finra_2012, sec2012frontrunning}.
+Initially the frontrunning policies only applied to certain option markets, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{finra_2002}, which then in 2012 with the new amendment, FINRA Rule 5270, the frontrunning rule was extended to cover trading in an option, derivative, or other financial instruments overlying a security with some exceptions~\cite{finra_2012, sec2012frontrunning}.
 
@@
 Some other key differences are the fact that such actor can stay anonymous and also enforcing regulation is infeasible in traditional sense, however a decentral application could be designed in such a way to mitigate frontrunning attacks.
+
+% TODO: example with figure! similar to a traditional exchange. e.g an order on a decentral exchange, just the description then refer to \subsection{Financial Markets}
 

### 2018-08-07 frontrunning/Latex/sections/paper.tex
[frontrunning] Preliminary- What is frontrunning + related docs

--- 2018-08-04 frontrunning/Latex/sections/paper.tex
@@
 
-%Some notes (to be paraphrased):
-%if other market participants can obtain prior or contemporaneous knowledge of transactions, they may attempt to trade before the institutional investors can complete their trades, a practice known as front running.
-In financial markets, any sort of front running or information leakage is a serious concern.
-%We would like to ask what causes such front-running behaviour. There are two factors: (1) imperfect competition and (2) liquidity uncertainty
-~\cite{liang2005distressed} : talks about front running in illiquid markets (contains lots of useful definitions of frontrunning to talk about in this section)
+\emph{Front-running} is analogous to any course of action during which a person benefits from prior access to inside or confidential market information to upcoming transactions and trades.
+This problem can occur in both financial and non-financial systems, however, it is more noticeable within the trading and exchange systems as it was originated back in stock markets.
+In the old times, all the trades were executed on papers, so in case of receiving a large order from a client, the broker might say this loud and other people around the table could be informed.
+Therefore, a malicious trader would now run in front of that order and put his own transaction in between (before the trade was executed) and profit from the price increase of the stock.
+In other words, a group of market participants obtain non-public market information which allows them to front-run other users trades by putting their orders a head of those trades and benefit from advance knowledge of pending client orders.
+The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty.
+\textbf{should I explain more?!} Any sort of front-running activity within the financial markets is considered as an illegal practice.
 
-% @mahsa
-
-%Traditional
-
-%talking about front running
-
-%Miners in Bitcoin can do selfish mining and such but in theory
-% here we talk about miners actually being malicious(?) to profit themselves.
-
-% more on the definition in the wiki page: https://en.wikipedia.org/wiki/Front_running
+%%%%%%SHOULD WE KEEP THE FOLLOWINGS?%%%%%%
+%~\cite{liang2005distressed} : talks about front running in illiquid markets (contains lots of useful definitions of frontrunning to talk about in this section)
+%~\cite{sannikov2016dynamic}
 
 % [optional but interesting] Here we can talk about Principal–agent problem: https://en.wikipedia.org/wiki/Principal%E2%80%93agent_problem
+% ticket scalping : https://en.wikipedia.org/wiki/Ticket_resale
 
-% ticket scalping : https://en.wikipedia.org/wiki/Ticket_resale
+%______________________________________________________________%
 
@@
 \subsection{Miners}
-
+%Miners in Bitcoin can do selfish mining and such but in theory
+% here we talk about miners actually being malicious(?) to profit themselves. 
+%You can do the same thing on the blockchain.
+If a miner or user sees an unconfirmed transaction in the mempool they could squeeze their own transaction to come in front and profit from that.
+Essentially, profitting from reordering the transactions.
+% Miners can only frontrun in blocks they themselves happen to mine.
 % Mining blocks hence order of the transactions within a block --> reorder

### 2018-08-07 frontrunning/Latex/sections/paper.tex
[frontrunning] minor changes

@@
 The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty.
-\textbf{should I explain more?!} Any sort of front-running activity within the financial markets is considered as an illegal practice.
+\textbf{should I explain more?!} Any sort of front-running activity within the financial markets is considered as an unethical and illegal practice as it is unfairly beneficial for a few market participants who have the privilege of acting on this information and taking advantages at the expense of the investor.
 

### 2018-08-08 atomic-swaps/atomic-swaps-paper/intro.tex
[atomic swaps] more explanation about the table

@@
 
+%https://medium.com/@bitcoinatom/why-are-atomic-swaps-better-than-trading-on-exchanges-798492e150fd
 %Their next goal: atomically swap any token for any other token, regardless of the blockchain it resides on.
@@
 An atomic cross-chain swap is a special case of a distributed atomic transaction, although not all atomic transactions can be expressed as cross-chain swaps.
-If swaps are recurrent, then it would be useful to conduct swaps off-chain as much as possible, similar to the way that Lightning and Raiden networks support off-chain transactions for bitcoin and ERC20 tokens.
-
-%FAIR EXCHANGE?
-%The fair exchange problem ~\cite{franklin1998secure}, ~\cite{micali2003simple} is a precursor to the atomic cross-chain swap problem.
+If swaps are recurrent, then it would be useful to conduct swaps off-chain as much as possible, similar to the way that Lightning and Raiden networks support off-chain transactions for bitcoin and ERC20 tokens.FAIR EXCHANGE?
+The fair exchange problem ~\cite{franklin1998secure}, ~\cite{micali2003simple} is a precursor to the atomic cross-chain swap problem.
 Alice has a digital asset Bob wants, and vice-versa, and at the end of the protocol, either Alice and Bob have exchanged assets, or they both keep their assets.
@@
 
+\section{Atomic swaps with different settings}
+
 \begin{table}[h!]
@@
    maker & taker & class & order transactions (margin) & account (onetime) transactions (fixed) \\ \hline
-   ERC20 & ETH & approve & 3 & \\ \hline
-   ERC20 & ERC20 & approve & 4 & \\ \hline
-   ERC20-like & ETH & w/o approve & 5 & \\ \hline
-   ERC20-like & ERC20-like & w/o approve & 6 & \\ \hline
+   ERC20 & ETH & approve & 2 & 3 \\ \hline
+   ERC20 & ERC20 & approve & 3 & 4 \\ \hline
+   ERC20-like & ETH & w/o approve &  & \\ \hline
+   ERC20-like & ERC20-like & w/o approve &  & \\ \hline
    ERC223 & ETH & & &\\ \hline
@@
    ERC20 & ETH & partially collateralized & &\\ \hline
+   ERC20 & ERC223 & & \\ \hline
 \end{tabular}
@@
 \end{table}\label{Table:Comparison of different swaps}
+\textbf{ERC20 to ETH:} Somebody sets up the swap.
+Token holder calls approve on the ERC20 contract with the swap contract as the target/allowance holder/spender.
+The holder of the ETH calls a settle function, sending their ETH along with it.
+This triggers the swap and the swap contract calls transferFrom on the ERC20 contract, transferring the tokens from the token holder to the ETH holder.
+The swap contract at this stage also sends the ETH to the token holder.
+The atomic swap is now complete.
+Hence, approving on the ERC20 contract and calling the settle function are counted as the order transactions.
+When the one-time transactions are also considered, deploying the swap contract should also be counted, which in total makes 4 transactions.
+We assume that the token contract already exists.
+
+\textbf{ERC20 to ERC20:} For the order transactions, we have 3 in total as the other token holder should also approve the amount of tokens to be spent.

### 2018-08-08 frontrunning/Latex/sections/paper.tex
[Frontrunning] minor changes
[frontrunning] add breidenbach2018enter
[frontrunning] restructure the paper. Notes from meeting Aug 8, 2018

@@
 \section{Introduction}
+% Why is this important.
+% PAPER BEING SOLD HERE
 
-% PAPER BEING SOLD HERE
-% @mahsa summary of `What is frontrunning?` in 2 sentenses, frontrunning in blockchain and why is this important to consider in blockchain/dapp design
-% require more indepth academic look into the issue
+%______________________________________________________________%
 
-\section{Preliminary}
+\section{Preliminaries}
 
@@
 
-%%%%%%SHOULD WE KEEP THE FOLLOWINGS?%%%%%%
+\subsection{Frontrunning in Blockchains}: One of the main discussion regarding regulations for exchanges on the topic of frontrunning, comes from the fact that information access is layered and some could be accessed only by insider actors, such as the broker, the IT administrator, \etc.
+In the blockchain world, anyone running a node of one blockchain could potentially have access to such information, hence it makes it is more susceptible for any actor to engage in frontrunning within applications running on the blockchain.
+Some other key differences are the fact that such actor can stay anonymous and also enforcing regulation is infeasible in traditional sense, however a decentral application could be designed in such a way to mitigate frontrunning attacks.
+
+% Financial / Non-financial applications (description)
+% Examples: Decentral Exchanges / Whois/domain registry
+% @Mahsa ^
+
+%%%%%%SHOULD WE KEEP THE FOLLOWINGS?%%%%%% Maybe literature? 
 %~\cite{liang2005distressed} : talks about front running in illiquid markets (contains lots of useful definitions of frontrunning to talk about in this section)
@@
 
-% [optional but interesting] Here we can talk about Principal–agent problem: https://en.wikipedia.org/wiki/Principal%E2%80%93agent_problem
-% ticket scalping : https://en.wikipedia.org/wiki/Ticket_resale
-
 %______________________________________________________________%
 
-\subsection{Historical Context}
+\section{Related Work}
+As the traditional frontrunning was originated to trading financial instruments most of the literature are focused on financial aspects of the markets. %TODO: expand this with something
+
+\subsection{Historical Context / Classic Frontrunning}
 Frontrunning was first appeared on the Chicago Board Options Exchange ( \textit{CBoE}) ~\cite{markham1988front}, and was identified by \textit{Securities Exchange Commission} in 1977 as the following:
@@
 
-\subsection{Frontrunning in Blockchains}: One of the main discussion regarding regulations for exchanges on the topic of frontrunning, comes from the fact that information access is layered and some could be accessed only by insider actors, such as the broker, the IT administrator, \etc.
-In the blockchain world, anyone running a node of one blockchain could potentially have access to such information, hence it makes it is more susceptible for any actor to engage in frontrunning within applications running on the blockchain.
-Some other key differences are the fact that such actor can stay anonymous and also enforcing regulation is infeasible in traditional sense, however a decentral application could be designed in such a way to mitigate frontrunning attacks.
-
-% TODO: example with figure! similar to a traditional exchange. e.g an order on a decentral exchange, just the description then refer to \subsection{Financial Markets}
-
-\subsection{Related Work}
+\subsection{Recent Literature on Blockchain frontrunning}
 
@@
 ~\cite{aune2017footprints}
-
-% Shayan: talk about frontrunning in other blockchains, such as privacy preserving blockchains --> no transparency less chance of frontrunning?  
-% this is a big problem with Dapps, what other blockchains support smart contracts that have this problem.
-
-% Mahsa: talk about namecoin frontrunning from the paper
+~\cite{breidenbach2018enter}
 
@@
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+%______________________________________________________________%
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+\section{(On) Blockchain Frontrunning}
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+\subsection{Who can frontrun?}
+%Actors:
 
-\section{Frontrunning Attacks in Blockchain}
+All nodes connected to the network have the ability to front run specific transactions, however miners have special control on the blocks they happen to mine and hence more possible ways to frontrun.
 
-\subsection{Financial Markets}
-%orders, exchanges
-% @shayan: front runnign attacks on 0x and etherdelta . if one past one found add it to Implications!
-% http://hackingdistributed.com/2017/08/13/cost-of-decent/
+\subsubsection{Blockchain users/nodes}
 
-\subsection{Non-financial Applications}
-Applications, Ghazal, register domains before the user, (domain squatting?) \par\noindent
-Other applications (look at Dapps or other blockchain use cases)\par\noindent
-Arbitrage (buy before the order, sell to the original order) (other scenarios)\par\noindent
-Maker griefing (attack on the system?s reputation itself)\par\noindent
-Etherdelta case: Fill the order when cancelling transaction is sent. What would be the profitable scenario here?
+\begin{itemize}
+\item{\textbf{Higher GasPrice}: Monitor transactions, rebroadcast with higher GasPrice}
+\item{\textbf{Fully/well connected nodes}: Similar to HFT situation of faster connections to other nodes, for a higher chance of transaction inclusion, also Sybil attacks?} 
+\item{\textbf{Noticable by the network}: More visible to the network as both transactions are broadcast to all the nodes}
+\end{itemize}
 
+\subsubsection{Miners}
+
+\begin{itemize}
+\item{\textbf{Their own mined blocks}: The can only frontrun transactions within the block they mine. This could be done by reordering the transactions within the blocks.}
+%^ If a miner or user sees an unconfirmed transaction in the mempool they could squeeze their own transaction to come in front and profit from that.
+Essentially, profitting from reordering the transactions.
+
+\item{\textbf{Less Noticable by the network}: Miners can include transactions within the blocks they happen to mine without broadcasting the transactions, hence less chance of being detected by the network participants.}
+%Should the following be included? 
+%\item{\textbf{Incentivized mitigation methods}: applications could pay the fees to the miners to incentives them to behave } 
+\end{itemize}
+
+\subsection{Historical evidence}
+As blockchain records are immutably recorded, there is enough historical data to analyze for possible front running detection.
+For examples here we research some of the events of such attacks happening in the Ethereum blockchain applications.
+
+% TODO: @shayan: talk about cancel order frontrunning on decentral exchanges (etherdelta), griefing 
 % maybe inlcude 0xbitcoin ERC721 mineable tokens frontrunning!
@@
 
-%NOTE: top 10 dapps, talk about frontrunning attacks on them.
+\subsubsection{Status ICO} %Frontrunning by a miner/mining pool
 
-% @Mahsa: some interesting read (check out the references) for domain name front running : https://en.wikipedia.org/wiki/Domain_name_front_running
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-
-\section{Potential Front runners} % Who and How.
-
-%WRT blockchain and decentralization
-
-% TALK ABOUT IT {Miners and their power}
-
-%Transaction order, can be used for frontrunning
-
-\subsection{Miners}
-%Miners in Bitcoin can do selfish mining and such but in theory
-% here we talk about miners actually being malicious(?) to profit themselves. 
-%You can do the same thing on the blockchain.
-If a miner or user sees an unconfirmed transaction in the mempool they could squeeze their own transaction to come in front and profit from that.
-Essentially, profitting from reordering the transactions.
-% Miners can only frontrun in blocks they themselves happen to mine.
-% Mining blocks hence order of the transactions within a block --> reorder
-%
-
-% Use example of the paper, talk about status ICO or some other miner reorder frontrunning
-
-\subsection{non-miner}
-% Use high gasprice to get infront
-% Sybil attacks?
-%
-
-% Use example of  namecoin/domain . use an example of Alice wants to register a domain and bob uses GasPrice to get in front of Alice.
-
-\section{Implications} %change this to something else
-
-\subsection{Historical evidence of such attacks:}\par\noindent
-There has been many incidents of frontrunning in real world blockchains specially where it facilitates monetary gain. Here we will analyze the evidence of these incidents:
-
-% NOTE: This seperation can also happen by another category, like: frontrunning by miners: status ico F2pool, and frontrunning by others
+%@Shayan: Clean up this part, finish it!
 
@@
 
-\subsubsection{Status ICO}
 ICO, Initial Coin Offering, is one of the blockchain applications, specially blockchains such as Ethereum with smart contract capability.
@@
 
-\subsubsection{Bancor} is an Ethereum-based application that allows users to exchange their tokens without any counterparty risk.
+\subsubsection{Bancor} %frontrunning by network participants.
+Bancor is an Ethereum-based application that allows users to exchange their tokens without any counterparty risk.
 This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users.
@@
 Bancor frontrunning attacks can occur in two different ways:
+
+%Mahsa: clean up this. remove miner/non-miner separation. miner section would be refrenced to the miner section re-ordering in blocks they HAPPEN to mine.
+% Probably we could reuse these texts in the miner/non-miner section in Who can Frontrun section.
 
@@
 
+\subsubsection{Domain Name Registration} 
 %Following section talks about frontrunning in namespaces but limited to Ghazal. Will talk about NameCoin in the section of mitigations (commit & reveal method)
-\subsubsection{Namespaces} Although frontrunning attacks have been more showcased in the context of decentralized exchanges and trading systems, they are are not yet limited to the financial markets.
+%
+% PoC of frontrunning ghazal
+Although frontrunning attacks have been more showcased in the context of decentralized exchanges and trading systems, they are are not yet limited to the financial markets.
 Frontrunning can occur within other blockchain based applications such as naming systems.
@@
 
-%@ possibility of PoC attack (@shayan @mahsa)
-%===========================%
+%______________________________________________________________%
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-\section{Mitigations}
+\section{How to stop frontrunning?}
 
-Commit / reveal methods %namecoin story @mahsa 
-% 1) Go dark
+\emph{Traditional Frontrunning Prevention Methods}. regulations/enforcement/broker education/sealed order
+%@shayan: ^
+
+\emph{Blockchain Frontrunning mitigation/prevention}.
+The traditional methods of preventing frontrunning are based on regulation and restrictions applied to the brokers and actors within the markets, such methods do not apply to blockchains, no enforcement methods, ...
+
+There are two main approaches to prevent front running, one to design a blockchain that is frontrun-resistent , and the other to design the application logics in a way that front running is not possible.
+
+\subsection{Frontrun-resistent Blockchain}
+What does this mean to have a frontrun-resistent blockchain?  There are technical difficulties to achieve such solutions as there are unknown factors within such network designs (corner/edge cases).
+
 \begin{itemize}
-\item{Send the hash first, send the actual data after (sealed-bid auctions)}
-\item{Proof of burn methods (generate random addresses with no private keys)}
-\end{itemize}
-Submarines
-\begin{itemize}
-\item{The method described in HD can be optimized and more functional with the new changes to ethereum and solidity}
-\item{Submarines 2.0: There can be a new way of doing this (new WRT hackingditributed article), can predict smart contract addresses using the nonce and data of the contract (forwarder/refunder), so funds can be sent to these addresses and then contracts can be deployed}
-\begin {itemize}
-\item{Pros: new addresses, no indication of the order (Anonymity-set)}
-\item{Cons: DDoS? Requires 3 transactions for each order?} >> 1 send the funds 2 Deploy the contract 3 call the function
-\end{itemize}
-\item{Other methods? Consensus protocol based solutions?}
+\item{\textbf{Privacy Preserving Blockchians}: Shielded transactions in ZCash do not reveal the sender, receiver, the amount and the data included in the transactions, hence they cannot be seen by network participants to be frontrunned.
+Although this limites the functionality of the blockchain/smartcontracts/dapps }
+\item{textbf{Loopring/Dual Athoring}: Talk about this possible solution}
 
@@
 
-% How are we solving this in orderbooks?
-%shayan: Give the fees in a decental orderbook to the miners so change the incentive model and they are incentivized to act honestly
-%2) kill the incentive (change the incentive) ^ .
+\subsection{Application design to prevent frontrunning}
+Applications, in this case Dapps, could be designed in a way to prevent frontrunning.
 
-% also call options on a random ending block, so timing of the incoming transactiion does not matter
+\begin{itemize}
+\item{\textbf{Commit/Reveal}: describe.
+General solution to prevent data leaks of the transactions.
+although it does not hide the participatory factor (it shows the actor participated in the application but hides the details, obvious participation(commit))}
+% discussion about Anonymity-set ?
+\item{\textbf{Submarine sends}: describe. General solution similar to commit and reveal. This is to solve the participatory factor of the commit and reveal solution.}
 
-%3) change the mechanics. similar to double spend mitigation, fee structure. with gas limits gasprice limit (status ico did. and bancor after the attack)
+\item{\textbf{Application logic specific solution}: Depending on the use case of  the Dapp or the application, it could be designed in a way to deincentives some actors to frontrun the transactions or prevent them from doing so.
+As an example on desiging a decentral orderbook, it could be said that a miner could front run orders for financial gain on price improvement, however if the fees of the orders are sent to the miner of the block, it deincentiveses the miner to front run the orders as they already gain enough financial benefit from including the correct order of transactions.
+Another example for decentral orderbook design could be using call market design instead of  time-sensitive orderbooks.
+In such design the arrival time of the order does not matter as they are executed in batches.
+}
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+%Proof of burn methods ?
+
+\end{itemize}
+
+%______________________________________________________________%
 
@@
 
-% @shayan:
 % Could talk about a tool / a framework to detect frontrunning
-% Circle in the py-etherscan guy about having the tools to detect such things
 

### 2018-08-09 atomic-swaps/atomic-swaps-paper/intro.tex
[atomic swaps] new figures and updates in the table

@@
 \includegraphics[width=1\textwidth]{approve}
-\caption{approve}
+\caption{ETH to ERC20 with approve}
 \label{fig:withapprove}
@@
 \includegraphics[width=1\textwidth]{withoutapprove}
-\caption{without approve}
-\label{fig:withapprove}
+\caption{ETH to ERC20-like without approve}
+\label{fig:withoutapprove}
+\vspace{-10pt}
+\end{figure}
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=1\textwidth]{ERC20toERC223}
+	\caption{ERC20 to ERC223}
+	\label{fig:ERC20toERC223}
+	\vspace{-10pt}
+\end{figure}
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=1\textwidth]{ERC223toERC223}
+	\caption{ERC223 to ERC223}
+	\label{fig:ERC223toERC223}
+	\vspace{-10pt}
+\end{figure}
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=1\textwidth]{ETHtoERC223}
+	\caption{ETH to ERC223}
+	\label{fig:ETHtoERC223}
 	\vspace{-10pt}
@@
 
-\textbf{TO-DO:}
-\begin{itemize}
-  \item explain how we count transactions and the difference between margin and fixed transactions
-  \item introduce more settings in the table
-\end{itemize}
-
 \section{Atomic swaps with different settings}
+Atomic swaps can be realized using different kinds of tokens and there can be different variations depending on the function calls used or collateralization.
+Table~\ref{Table:Comparison of different swaps} illustrates the possible settings and compares the amount of transactions required for each case.
 
@@
    maker & taker & class & order transactions (margin) & account (onetime) transactions (fixed) \\ \hline
-   ERC20 & ETH & approve & 2 & 3 \\ \hline
-   ERC20 & ERC20 & approve & 3 & 4 \\ \hline
-   ERC20-like & ETH & w/o approve &  & \\ \hline
-   ERC20-like & ERC20-like & w/o approve &  & \\ \hline
-   ERC223 & ETH & & &\\ \hline
+   ERC20 & ETH & approve & 2 & 4 \\ \hline
+   ERC20 & ERC20 & approve & 2 & 5 \\ \hline
+   ERC20-like & ETH & w/o approve & 2 & 4 \\ \hline
+   ERC20-like & ERC20-like & w/o approve & 2 & 5 \\ \hline
+   ERC223 & ETH & hybrid & 2 & 4\\ \hline
    ERC20 & ETH & collateralized & &\\ \hline
    ERC20 & ETH & partially collateralized & &\\ \hline
-   ERC20 & ERC223 & & \\ \hline
+   ERC20 & ERC223 & hybrid & 2 & 5 \\ \hline
+   ERC223 & ERC223 & collateralized & 2 & 5\\ \hline
 \end{tabular}
@@
 \end{table}\label{Table:Comparison of different swaps} 
-\textbf{ERC20 to ETH:} Somebody sets up the swap.
+\textbf{ERC20 to ETH:} This setting is described in Figure~\ref{fig:withapprove}.
+Somebody deploys the swap contract.
+For each atomic swap between two parties, somebody (who may or may not be one of the transacting parties) initiates a swap object within the swap contract.
 Token holder calls approve on the ERC20 contract with the swap contract as the target/allowance holder/spender.
-The holder of the ETH calls a settle function, sending their ETH along with it.
+The token holder may approve the swap contract for multiple transactions by setting an allowance greater than necessary for one swap.
+The holder of the ETH calls a settle function on the swap contract, sending their ETH along with it.
 This triggers the swap and the swap contract calls transferFrom on the ERC20 contract, transferring the tokens from the token holder to the ETH holder.
@@
 The atomic swap is now complete.
-Hence, approving on the ERC20 contract and calling the settle function are counted as the order transactions.
-When the one-time transactions are also considered, deploying the swap contract should also be counted, which in total makes 4 transactions.
-We assume that the token contract already exists.
+Deploying the swap contract and approving on the ERC20 contract are considered as the fixed transactions as they do not need to be performed for every swap.
+The swap initialization and calling of the settle function, both within the swap contract, must be carried out for every swap.
+When taken with the fixed cost transactions, an atomic swap takes up to four transactions total.
 
-\textbf{ERC20 to ERC20:} For the order transactions, we have 3 in total as the other token holder should also approve the amount of tokens to be spent.
+\textbf{ERC20 to ERC20:} For the fixed transactions, we have 5 in total as the other token holder should also approve the amount of tokens to be spent.
+
+\textbf{ERC20-like to ETH:} This setting is described in Figure~\ref{fig:withoutapprove}. For this setting, the approve function in the ERC20 interface is not used.
+
+\textbf{ERC20-like to ERC20-like:}

### 2018-08-10 frontrunning/Latex/sections/paper.tex
[front running] Section Preliminaries Completed.

@@
 
-\subsection{What is frontrunning?} %Definition of frontrunning
+\subsection{What is Front running?} %Definition of frontrunning
+\label{sec:What is frontrunning?}
 
-\emph{Front-running} is analogous to any course of action during which a person benefits from prior access to inside or confidential market information to upcoming transactions and trades.
+\emph{Front running} is analogous to any course of action during which a person benefits from prior access to inside or confidential market information to upcoming transactions and trades.
 This problem can occur in both financial and non-financial systems, however, it is more noticeable within the trading and exchange systems as it was originated back in stock markets.
@@
 
-\subsection{Frontrunning in Blockchains}: One of the main discussion regarding regulations for exchanges on the topic of frontrunning, comes from the fact that information access is layered and some could be accessed only by insider actors, such as the broker, the IT administrator, \etc.
-In the blockchain world, anyone running a node of one blockchain could potentially have access to such information, hence it makes it is more susceptible for any actor to engage in frontrunning within applications running on the blockchain.
-Some other key differences are the fact that such actor can stay anonymous and also enforcing regulation is infeasible in traditional sense, however a decentral application could be designed in such a way to mitigate frontrunning attacks.
+\subsection{Front Running on the Blockchains}
 
-% Financial / Non-financial applications (description)
-% Examples: Decentral Exchanges / Whois/domain registry
-% @Mahsa ^
-
-%%%%%%SHOULD WE KEEP THE FOLLOWINGS?%%%%%% Maybe literature? 
-%~\cite{liang2005distressed} : talks about front running in illiquid markets (contains lots of useful definitions of frontrunning to talk about in this section)
-%~\cite{sannikov2016dynamic}
-
-%______________________________________________________________%
+Blockchain technology has received an exceptional amount of attention since it was first introduced as the underlying technology of the cryptocurrency Bitcoin in Satoshi Nakamoto's (pseudonymous) 2008 white paper \cite{nakamoto2008bitcoin}.
+Many decentralized applications that are nowadays built on top of this technology represent the significance of the blockchain as it completely eliminates the single points of failures within any systems.
+However, blockchains have some inherent characteristic that leave them vulnerable to \emph{front running} behaviour.
+Although this data structure is known to be publicly visible to every network participants, information is layered  and some of them are accessed only by insiders.
+Any network participants that runs a full node on the blockchain is able to obtain those information and as mentioned in Section~\ref{sec:What is frontrunning?}, this leaves the application vulnerable to front running.
+Decentralized exchanges are a group of blockchain financial applications where front running can be executed.
+Bancor \cite{hertzog2017bancor} is an example of such systems in which front runners benefit from potential price increase of the market stocks (details are provided in Section ...).
+Decentralized namespaces, as blockchain non-financial applications, are another example.
+Ghazal \cite{moosavighazal} is such system in which upon seeing a transaction from Alice to register \texttt{alice.com}, front runner can go ahead of her and register this domain name.
+He can later sell \texttt{alice.com} to Alice for a higher price and benefit from the price increase.
+%___________________________________________________________%
 

### 2018-08-13 frontrunning/Latex/sections/paper.tex
[frontrunning] section "Who Can Front-run?" completed

@@
 
-\section{(On) Blockchain Frontrunning}
+\section{(On) Blockchain Front-running}
 
-\subsection{Who can frontrun?}
-%Actors:
+\subsection{Who Can Front-run?}
 
-All nodes connected to the network have the ability to front run specific transactions, however miners have special control on the blocks they happen to mine and hence more possible ways to frontrun.
+In general, all the network participants have the ability to front run specific transactions that are sent to the network.
+However, miners can include any transactions they like into the block they attempt to mine.
+Thus, they possess special power in terms of front running as opposed to other users of the network.
+In the following, we discuss and compare the two groups of blockchain potential front runners.
+
+\subsubsection{Miners}
+As mentioned above, since the Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the pending transactions sitting in the mempool and profit from a guaranteed price-rise.
+For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 Ether, presumably if this transaction goes through, it causes the price of Ether to increase.
+So the dishonest miner can step in front of this transaction and  place his own buy order ahead of it.
+He would simply create his \textit{buy} of 1000 Ether and include it within a block and now he mines the previous \textit{buy} transaction of 1000 Ether.
+Doing so, he would receive a better rate than other network users, can sell the assets he has received and gain a price advantage at the expense of others.
+Similarly, a dishonest miner can sell his tokens in front, if he sees a pending \textit{sell} transaction.
+In an open source blockchain application, there is no rules on how transactions must be ordered and miners are free to send transactions in the order they prefer.
+However, miners can only front run other transactions (by reordering them) within the block they happen to mine while they do not broadcast any transactions to the network.
+This makes the miners to be less noticeable to the network when front running.
 
 \subsubsection{Blockchain users/nodes}
+Any regular (non-miner or miner) user can also front-run other transactions in the network.
+For regular users to front run others on the blockchain, they need to be fully/well connected to other nodes on the network.
+Doing so, they are able to listen to the network and monitor all transactions that are broadcast.
+On the Ethereum blockchain users have to pay for the computations in small amount of Ether called \textit{gas}~\cite{AccountT67:online}.
+The price that users pay for transactions (a.k.a.
+transaction fees) can increase or decrease how quickly they are executed and included within the blocks by the miners.
+This is because the Ethereum miners consume resources to process the transactions and so receive the transaction fees after creating the blocks.
+Once seeing two identical transactions with different transaction fees, profit maximizers miners are free to mine select the transaction which offers the highest fee.
+Therefore, any regular users who run a full-node Ethereum client can modify the order of pending transactions by paying a more amount of gas \ie by monitoring the network, upon seeing a  pending \textit{buy} transaction which will further increase the price of the asset, a font-runner user can pay a higher gas price and send his transaction a head of that.
+By doing so, he achieves a better rate from any other network users.
+Note that in this case, blockchain front runners are more visible to the network as they broadcast their transactions to all the network participants.
 
-\begin{itemize}
-\item{\textbf{Higher GasPrice}: Monitor transactions, rebroadcast with higher GasPrice}
-\item{\textbf{Fully/well connected nodes}: Similar to HFT situation of faster connections to other nodes, for a higher chance of transaction inclusion, also Sybil attacks?} 
-\item{\textbf{Noticable by the network}: More visible to the network as both transactions are broadcast to all the nodes}
-\end{itemize}
-
-\subsubsection{Miners}
-
-\begin{itemize}
-\item{\textbf{Their own mined blocks}: The can only frontrun transactions within the block they mine. This could be done by reordering the transactions within the blocks.}
-%^ If a miner or user sees an unconfirmed transaction in the mempool they could squeeze their own transaction to come in front and profit from that.
+%\subsubsection{Blockchain users/nodes}:
+%\begin{itemize}
+%\item{\textbf{Higher GasPrice}: Monitor transactions, rebroadcast with higher GasPrice}
+%\item{\textbf{Fully/well connected nodes}: Similar to HFT situation of faster connections to other nodes, for a higher chance of transaction inclusion, also Sybil attacks?} 
+%\item{\textbf{Noticable by the network}: More visible to the network as both transactions are broadcast to all the nodes}
+%\end{itemize}
+%
+%
+%\subsubsection{Miners}
+%
+%
+%\begin{itemize}
+%\item{\textbf{Their own mined blocks}: The can only frontrun transactions within the block they mine. This could be done by reordering the transactions within the blocks.}
+%%^ If a miner or user sees an unconfirmed transaction in the mempool they could squeeze their own transaction to come in front and profit from that.
 Essentially, profitting from reordering the transactions.
-
-\item{\textbf{Less Noticable by the network}: Miners can include transactions within the blocks they happen to mine without broadcasting the transactions, hence less chance of being detected by the network participants.}
-%Should the following be included? 
-%\item{\textbf{Incentivized mitigation methods}: applications could pay the fees to the miners to incentives them to behave } 
-\end{itemize}
+%
+%\item{\textbf{Less Noticable by the network}: Miners can include transactions within the blocks they happen to mine without broadcasting the transactions, hence less chance of being detected by the network participants.}
+%%Should the following be included? 
+%%\item{\textbf{Incentivized mitigation methods}: applications could pay the fees to the miners to incentives them to behave } 
+%\end{itemize}
 
@@
 
-%Mahsa: clean up this. remove miner/non-miner separation. miner section would be refrenced to the miner section re-ordering in blocks they HAPPEN to mine.
-% Probably we could reuse these texts in the miner/non-miner section in Who can Frontrun section.
-
-\begin{itemize}
-\item {\textbf{Miner Frontrunning.}} As mentioned, Bancor protocol uses an algorithm that automatically calculates the price of digital assets to provide better market liquidity.
+%\begin{itemize}
+%\item {\textbf{Miner Frontrunning.}} As mentioned, Bancor protocol uses an algorithm that automatically calculates the price of digital assets to provide better market liquidity.
 In the Bancor model, essentially buy orders increase the price of the tokens while sell order decrease it.
@@
 Similarly, a dishonest miner can sell his tokens in front, if he sees a pending \textit{sell} transaction.
-
-\item {\textbf{Non-miner Frontrunning.}} Researchers have also shown that a regular non-miner user can also front-run Bancor.
+%
+%
+%\item {\textbf{Non-miner Frontrunning.}} Researchers have also shown that a regular non-miner user can also front-run Bancor.
 In order for the Bancor transactions to be executed on the Ethereum Virtual Machine (EVM),  users have to pay for the computations in small amount of Ether called \textit{gas}~\cite{AccountT67:online}.
@@
 By doing so, he achieves a better rate from any other Bancor users.
-
-\end{itemize}
+%
+%\end{itemize}
 
 \subsubsection{Domain Name Registration}
+
+%"domain name frontrunning." The practice resulted in Network Solutions registering a previously-unregistered domain to itself immediately after someone searched for it, then holding the domain for four days before it could be purchased by someone else or at another registrar.
+But the company claims that it's merely trying to protect customers from others doing exactly that.
+Until there is more regulation over frontrunning from ICANN, this is the best it can come up with
+
 %Following section talks about frontrunning in namespaces but limited to Ghazal. Will talk about NameCoin in the section of mitigations (commit & reveal method)

### 2018-08-13 frontrunning/Latex/sections/paper.tex
[frontrunning] Bancor section completed.

@@
 \subsection{Who Can Front-run?}
+\label{sec:who can frontrun?}
 
@@
 \subsubsection{Bancor} %frontrunning by network participants.
-Bancor is an Ethereum-based application that allows users to exchange their tokens without any counterparty risk.
+
+Bancor is an Ethereum-based application that allows users to exchange their tokens without any counter-party risk.
 This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users.
 Smart Tokens can be bought and sold through the users smart contract at an automatically calculated price which displays supply and demand.
-Doing so, Bancor protocol provides continuous liquidity for digital assets without relying on an orderbook as there is no requirement to match sellers and buyers.
+Doing so, Bancor protocol provides continuous liquidity for digital assets without relying on an order book as there is no requirement to match sellers and buyers.
 
-\par\noindent\textbf{Front-running Bancor} Recently, researchers have shown that Bancor is vulnerable to frontrunning attacks.
+\par\noindent\textbf{Front-running Bancor} Recently, researchers have shown that Bancor is vulnerable to front running attacks.
 Implemented on the Ethereum blockchain, when Bancor transactions are broadcast to the network, they sit in a pending transaction pool known as \textit{mempool} waiting for the miners to mine them.
@@
 This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favourable profits~\cite{BancorIs7:online}.
-Bancor frontrunning attacks can occur in two different ways:
+As mentioned in Section~\ref{sec:who can frontrun?} and same as every other Ethereum based application, Bancor transactions can be front run by miners and other regular (non-miner) users.
+There is an implementation of a Bancor front running attack in the Python programming language which represent how a non-miner user can front run other network participants \cite{NewTab13:online}.
 

### 2018-08-15 frontrunning/Latex/sections/paper.tex
[frontrunning] Some text here and there.

@@
 As mentioned above, since the Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the pending transactions sitting in the mempool and profit from a guaranteed price-rise.
-For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 Ether, presumably if this transaction goes through, it causes the price of Ether to increase.
+For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token, i.e.
+TKN, presumably if this transaction goes through, it causes the price the purchased token to increase.
 So the dishonest miner can step in front of this transaction and  place his own buy order ahead of it.
-He would simply create his \textit{buy} of 1000 Ether and include it within a block and now he mines the previous \textit{buy} transaction of 1000 Ether.
-Doing so, he would receive a better rate than other network users, can sell the assets he has received and gain a price advantage at the expense of others.
+He would simply create his \textit{buy} of 1000 TKN and include it within a block and now he mines the previous \textit{buy} transaction of 1000 TKN.
+Doing so, he would receive a better rate than other network users, and can sell the assets he has received and gain a price advantage at the expense of others.
 Similarly, a dishonest miner can sell his tokens in front, if he sees a pending \textit{sell} transaction.
 In an open source blockchain application, there is no rules on how transactions must be ordered and miners are free to send transactions in the order they prefer.
-However, miners can only front run other transactions (by reordering them) within the block they happen to mine while they do not broadcast any transactions to the network.
-This makes the miners to be less noticeable to the network when front running.
+However, miners can only front run other transactions (by reordering them) within the block they happen to mine.
+They could do this also by not broadcasting their own transactions to the network, this makes the miners to be less noticeable to the network when front running.
+Another example here is in the case of decentral exchanges and order cancellation.
+Every exchange should have the functionality to cancel the orders, especially for a volatile market.
+In this case, when user decides that her order is not profitable anymore, she would send a cancelation transaction.
+Here the miner sees the cancelation transaction and puts his own order before the cancellation transaction to fill the order, potentially profiting from the order.
+They can also include the canceled transaction in their block to collect the full gas limit used by that transaction~\cite{CostofDecentralization:online}.
 
@@
 The price that users pay for transactions (a.k.a.
-transaction fees) can increase or decrease how quickly they are executed and included within the blocks by the miners.
+transaction fees) can increase or decrease how quickly miners will execute them and include them within the block they mine.
 This is because the Ethereum miners consume resources to process the transactions and so receive the transaction fees after creating the blocks.
-Once seeing two identical transactions with different transaction fees, profit maximizers miners are free to mine select the transaction which offers the highest fee.
-Therefore, any regular users who run a full-node Ethereum client can modify the order of pending transactions by paying a more amount of gas \ie by monitoring the network, upon seeing a  pending \textit{buy} transaction which will further increase the price of the asset, a font-runner user can pay a higher gas price and send his transaction a head of that.
-By doing so, he achieves a better rate from any other network users.
+Once seeing two identical transactions with different transaction fees,
+%Given the limited space in the blocks, a rational miner will prioritize transactions that pay higher gas price per unit of gas, this maximizes their profit in the block they mine.
+miners act to maximize their profit and are free to mine the transaction which offers the highest fee.
+Therefore, any regular users who run a full-node Ethereum client can modify the order of pending transactions by paying with a higher gas price\ie by monitoring the network, upon seeing a  pending \textit{buy} transaction which will further increase the price of the asset, a font-runner user can pay a higher gas price and hope to have his transaction a head of the other one mined.
+By doing so, he achieves a better rate from the other network users.
 Note that in this case, blockchain front runners are more visible to the network as they broadcast their transactions to all the network participants.
@@
 \section{How to stop frontrunning?}
+In the traditional markets, frontrunning is considered unethical and also illegal.
+In the blockchain space, the designers of the decentral applications cannot rely on the justice system for unethical behaviour, and they must assume that each participant in the network acts rationally in their own self interest, the application will be operating in an adversarial environment~\cite{0xfrontrunning:online}.
 

### 2018-08-15 frontrunning/Latex/sections/paper.tex
[frontrunning] Commitment scheme

@@
 In both cases the adversarial party could sell the domain name to the users for higher price.
+%TODO: also talk about ENS
 
@@
 In the blockchain space, the designers of the decentral applications cannot rely on the justice system for unethical behaviour, and they must assume that each participant in the network acts rationally in their own self interest, the application will be operating in an adversarial environment~\cite{0xfrontrunning:online}.
+A few decentral exchange projects such as \textit{EtherDelta} and \textit{0xProject}, have proposed solutions for frontrunning, which is off-chain orderbooks.
+The methods discussed within these projects prevent blockchain network participants from front running the orders as the orders are private and not known to the network and will not be broadcasted.
+However they are introducing third parties, \eg relayers in 0xproject, to be managing the orders with the promise not to reorder or frontrun other orders.
 
@@
 \begin{itemize}
-\item{\textbf{Commit/Reveal}: describe.
-General solution to prevent data leaks of the transactions.
-although it does not hide the participatory factor (it shows the actor participated in the application but hides the details, obvious participation(commit))}
+\item{\textbf{Commitment scheme}: Also known as \textit{Commit and Reveal}, is a cryptographic primitive that enables one to commit to a value (\eg statement, document, \dots} while keeping it a secret and on a later time reveal the committed value~\cite{brassard1988minimum}.
+Commitment scheme is a good method to prevent information leakage from the sensitive transactions.
+This could be done by simply broadcasting the hash value of the committed data and later on revealing the values that would be hashed to the committed hash.
+In the case of decentral exchanges, user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, user sends reveal transaction revealing the order details which will be executed in a fair order.
+Another use of such commitment scheme, is in Decentral DNS, such as Ghazal or ENS.
+User will send a commit transaction similar to a sealed bid, once the transaction is confirmed and the grace period is over, user sends a reveal transaction revealing the bid and also the details of the requested domain.
+
+%although it does not hide the participatory factor (it shows the actor participated in the application but hides the details, obvious participation(commit))}
 % discussion about Anonymity-set ?
+
 \item{\textbf{Submarine sends}: describe. General solution similar to commit and reveal. This is to solve the participatory factor of the commit and reveal solution.}

### 2018-08-15 frontrunning/Latex/sections/paper.tex
[frontrunning] fix bib file

@@
 
-Initially the frontrunning policies only applied to certain option markets, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{finra_2002}, which then in 2012 with the new amendment, FINRA Rule 5270, the frontrunning rule was extended to cover trading in an option, derivative, or other financial instruments overlying a security with some exceptions~\cite{finra_2012, sec2012frontrunning}.
+Initially the frontrunning policies only applied to certain option markets, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{finra_2002}, which then in 2012 with the new amendment, FINRA Rule 5270, the frontrunning rule was extended to cover trading in an option, derivative, or other financial instruments overlying a security with some exceptions~\cite{sec2012frontrunning, finra_2012}.
 
@@
 
+%TODO: a figure for commit and reveal?
+
 %although it does not hide the participatory factor (it shows the actor participated in the application but hides the details, obvious participation(commit))}

### 2018-08-15 frontrunning/Latex/setup/packages.tex
[frontrunning] fix bib file

% !TEX root = ../main.tex

%------------------------LNCS----------------------%

%None

%------------------------Packages----------------------%

% = = = Graphics
\usepackage[pdftex]{graphicx}
\graphicspath{{figures/}}
\DeclareGraphicsExtensions{.jpg,.png}

% = = = Subfig (note not subfigure)
\usepackage[caption=false,font=footnotesize]{subfig}

% = = = Math Symbols
\usepackage{amsmath}
%\usepackage{amstext,amssymb,amsthm}
\usepackage{bbm}
\usepackage{stmaryrd}

% = = = Other
\usepackage{array}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage[pdftitle=Title,pdfauthor=Anonymous]{hyperref}
\usepackage{adjustbox}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{makecell}
\usepackage{hhline}
\usepackage{lscape}
\usepackage{tabu}
\usepackage{tikz}
\usepackage{textcomp} %Using tilde
\usetikzlibrary{shapes,backgrounds} %Venn diagram
\usepackage[justification=centering]{caption} % to add caption in tabular environment using the command \captionof{table}{Your caption here} 
\usepackage{cite}

%---------------------------------------------------%
\usepackage{listings, xcolor}
\renewcommand{\lstlistingname}{Code}
\definecolor{verylightgray}{rgb}{.97,.97,.97}
\lstdefinelanguage{Solidity}{
keywords=[1]{anonymous, assembly, assert, balance, break, call, callcode, case, catch, class, constant, continue, contract, debugger, default, delegatecall, delete, do, else, event, export, external, false, finally, for, function, gas, if, implements, import, in, indexed, instanceof, interface, internal, is, length, library, log0, log1, log2, log3, log4, memory, modifier, new, payable, pragma, private, protected, public, pure, push, require, return, returns, revert, selfdestruct, send, storage, struct, suicide, super, switch, then, this, throw, transfer, true, try, typeof, using, value, view, while, with, addmod, ecrecover, keccak256, mulmod, ripemd160, sha256, sha3}, % generic keywords including crypto operations
	keywordstyle=[1]\color{blue}\bfseries,
	keywords=[2]{Stages,States, address, bool, byte, bytes, bytes1, bytes2, bytes3, bytes4, bytes5, bytes6, bytes7, bytes8, bytes9, bytes10, bytes11, bytes12, bytes13, bytes14, bytes15, bytes16, bytes17, bytes18, bytes19, bytes20, bytes21, bytes22, bytes23, bytes24, bytes25, bytes26, bytes27, bytes28, bytes29, bytes30, bytes31, bytes32, enum, int, int8, int16, int24, int32, int40, int48, int56, int64, int72, int80, int88, int96, int104, int112, int120, int128, int136, int144, int152, int160, int168, int176, int184, int192, int200, int208, int216, int224, int232, int240, int248, int256, mapping, string, uint, uint8, uint16, uint24, uint32, uint40, uint48, uint56, uint64, uint72, uint80, uint88, uint96, uint104, uint112, uint120, uint128, uint136, uint144, uint152, uint160, uint168, uint176, uint184, uint192, uint200, uint208, uint216, uint224, uint232, uint240, uint248, uint256, var, void, ether, finney, szabo, wei, days, hours, minutes, seconds, weeks, years},	% types; money and time units
	keywordstyle=[2]\color{teal}\bfseries,
	keywords=[3]{block, blockhash, coinbase, difficulty, gaslimit, number, timestamp, msg, data, gas, sender, sig, value, now, tx, gasprice, origin},	% environment variables
	keywordstyle=[3]\color{violet}\bfseries,
	identifierstyle=\color{black},
	sensitive=false,
	comment=[l]{//},
	morecomment=[s]{/*}{*/},
	commentstyle=\color{gray}\ttfamily,
	stringstyle=\color{red}\ttfamily,
	morestring=[b]',
	morestring=[b]"
}

\lstset{
	language=Solidity,
	backgroundcolor=\color{verylightgray},
	extendedchars=true,
	basicstyle=\footnotesize\ttfamily,
	showstringspaces=false,
	showspaces=false,
	numbers=left,
	numberstyle=\footnotesize,
	numbersep=9pt,
	tabsize=2,
	breaklines=true,
	showtabs=false,
	captionpos=b,
      escapeinside={<@}{@>},
}

%------------------------END----------------------%

### 2018-08-15 frontrunning/Latex/sections/paper.tex
[frontrunning] some more data for F2pool vs statusICO
[frontrunning] add figure for statusICO

@@
 He can later sell \texttt{alice.com} to Alice for a higher price and benefit from the price increase.
+Another application that is vulnerable to front running is Initial Coin Offering, ICO, smart contracts.
+ICO is a method to distribute tokens based on the deposits of the native coin, Ether in the case of Ethereum.
+ICOs mostly have capped quantity of tokens \TODO{talk about why?}, there is a competition on who can get in to get the tokens at a discounted price, hence an opportunity to frontrun other transactions to get in.
+
 %___________________________________________________________%
@@
 
-% TODO: @shayan: talk about cancel order frontrunning on decentral exchanges (etherdelta), griefing 
 % maybe inlcude 0xbitcoin ERC721 mineable tokens frontrunning!
@@
 
-%NOTE: ICO Initial Coin Offering should be explained probably in introduction section.
-the process of ICO smart contract and how the capped system works --> limited time/funds can be included in the ico and why people would try to get in as soon as possible, explain how their investment strategy works and such.
-Maybe the second half could be explained here to say why frontrunning an ICO makes sense?
 % add more on capped ICOs, status used Distribution & Dynamic Ceilings : https://blog.status.im/distribution-dynamic-ceilings-e2f427f5cca  ~\cite{statuswhitepaper}
@@
 
-% weird findings: apparently all the tokens bought by f2pool was transfered to Yunbi, the chinese exchange: 0xB6c3647F55085B9a327404Fe8B718076Ee19245a
-
 % Proof of f2pool involvement: https://etherscan.io/address/0x5fb8373bf5086fb38ef0fb686b3092145de0d1c1
@@
 
-% I would like to spend some time to make charts from the transactions happening on the date of the Status ICO
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.5\linewidth]{figures/F2Pool_transactions_to_StatusICO_and_Refunds.png}
+\caption{F2Pool prior to Status.im ICO deposited 100 Ether in multiple new Ethereum addresses.
+On the time of the ICO they sent these deposits to Status ICO smart contract and prioritized mining of these transactions in their mining pool, this was to overcome the dynamic ceiling algorithm of the token sale smart contract.
+Later on they sent the refunded Ether back to their own address.\label{fig:f2poolfrontrun}}
+\end{figure}
+
 % this will include: The blocks mined by F2Pool, containing transactions (~100 ETH) to Status ICO, other blocks mined in that time period, the movement of status tokens from those addresses allegedly linked to F2Pool (or/and Yunbi in this case).

### 2018-08-15 frontrunning/Latex/sections/paper.tex
[frontrunning] minor modifications

--- 2018-08-15 frontrunning/Latex/sections/paper.tex
@@
 As mentioned above, since the Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the pending transactions sitting in the mempool and profit from a guaranteed price-rise.
-For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token, i.e.
-TKN, presumably if this transaction goes through, it causes the price the purchased token to increase.
+For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 Ether, presumably if this transaction goes through, it causes the price of Ether to increase.
 So the dishonest miner can step in front of this transaction and  place his own buy order ahead of it.
-He would simply create his \textit{buy} of 1000 TKN and include it within a block and now he mines the previous \textit{buy} transaction of 1000 TKN.
-Doing so, he would receive a better rate than other network users, and can sell the assets he has received and gain a price advantage at the expense of others.
+He would simply create his \textit{buy} of 1000 Ether and include it within a block and now he mines the previous \textit{buy} transaction of 1000 Ether.
+Doing so, he would receive a better rate than other network users, can sell the assets he has received and gain a price advantage at the expense of others.
 Similarly, a dishonest miner can sell his tokens in front, if he sees a pending \textit{sell} transaction.
 In an open source blockchain application, there is no rules on how transactions must be ordered and miners are free to send transactions in the order they prefer.
-However, miners can only front run other transactions (by reordering them) within the block they happen to mine.
-They could do this also by not broadcasting their own transactions to the network, this makes the miners to be less noticeable to the network when front running.
-Another example here is in the case of decentral exchanges and order cancellation.
-Every exchange should have the functionality to cancel the orders, especially for a volatile market.
-In this case, when user decides that her order is not profitable anymore, she would send a cancelation transaction.
-Here the miner sees the cancelation transaction and puts his own order before the cancellation transaction to fill the order, potentially profiting from the order.
-They can also include the canceled transaction in their block to collect the full gas limit used by that transaction~\cite{CostofDecentralization:online}.
+However, miners can only front run other transactions (by reordering them) within the block they happen to mine while they do not broadcast any transactions to the network.
+This makes the miners to be less noticeable to the network when front running.
 
@@
 The price that users pay for transactions (a.k.a.
-transaction fees) can increase or decrease how quickly miners will execute them and include them within the block they mine.
+transaction fees) can increase or decrease how quickly they are executed and included within the blocks by the miners.
 This is because the Ethereum miners consume resources to process the transactions and so receive the transaction fees after creating the blocks.
-Once seeing two identical transactions with different transaction fees,
-%Given the limited space in the blocks, a rational miner will prioritize transactions that pay higher gas price per unit of gas, this maximizes their profit in the block they mine.
-miners act to maximize their profit and are free to mine the transaction which offers the highest fee.
-Therefore, any regular users who run a full-node Ethereum client can modify the order of pending transactions by paying with a higher gas price\ie by monitoring the network, upon seeing a  pending \textit{buy} transaction which will further increase the price of the asset, a font-runner user can pay a higher gas price and hope to have his transaction a head of the other one mined.
-By doing so, he achieves a better rate from the other network users.
+Once seeing two identical transactions with different transaction fees, profit maximizers miners are free to mine select the transaction which offers the highest fee.
+Therefore, any regular users who run a full-node Ethereum client can modify the order of pending transactions by paying a more amount of gas \ie by monitoring the network, upon seeing a  pending \textit{buy} transaction which will further increase the price of the asset, a font-runner user can pay a higher gas price and send his transaction a head of that.
+By doing so, he achieves a better rate from any other network users.
 Note that in this case, blockchain front runners are more visible to the network as they broadcast their transactions to all the network participants.
@@
 
-\subsubsection{Status ICO} %Frontrunning by a miner/mining pool
-
+\subsubsection{Status ICO} \hfill\\ %Frontrunning by a miner/mining pool 
 %@Shayan: Clean up this part, finish it! 
-
 % ICOs and ceiling
@@
 % dynamic ceiling, fair token distribution --> status ICO
-
-ICO, Initial Coin Offering, is one of the blockchain applications, specially blockchains such as Ethereum with smart contract capability.
+\noindent ICO, Initial Coin Offering, is one of the blockchain applications, specially blockchains such as Ethereum with smart contract capability.
 The common practice is to deploy a smart contract on the blockchain indicating the details of the ICO such as the trade ratio, when it starts and ends, and more details on how it will be capped.
@@
 
-\subsubsection{Bancor} %frontrunning by network participants.
-
-Bancor is an Ethereum-based application that allows users to exchange their tokens without any counter-party risk.
+\subsubsection{Bancor} \hfill\\
+\noindent Bancor is an Ethereum-based application that allows users to exchange their tokens without any counter-party risk.
 This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users.
@@
 
-\subsubsection{Domain Name Registration}
-
+\subsubsection{Domain Name Front-running} \hfill\\
 %"domain name frontrunning." The practice resulted in Network Solutions registering a previously-unregistered domain to itself immediately after someone searched for it, then holding the domain for four days before it could be purchased by someone else or at another registrar.
@@
 Until there is more regulation over frontrunning from ICANN, this is the best it can come up with
-
 %Following section talks about frontrunning in namespaces but limited to Ghazal. Will talk about NameCoin in the section of mitigations (commit & reveal method)
@@
 % PoC of frontrunning ghazal
-Although frontrunning attacks have been more showcased in the context of decentralized exchanges and trading systems, they are are not yet limited to the financial markets.
+\noindent Although frontrunning attacks have been more showcased in the context of decentralized exchanges and trading systems, they are are not yet limited to the financial markets.
 Frontrunning can occur within other blockchain based applications such as naming systems.
@@
 In both cases the adversarial party could sell the domain name to the users for higher price.
-%TODO: also talk about ENS
 
@@
 \section{How to stop frontrunning?}
-In the traditional markets, frontrunning is considered unethical and also illegal.
-In the blockchain space, the designers of the decentral applications cannot rely on the justice system for unethical behaviour, and they must assume that each participant in the network acts rationally in their own self interest, the application will be operating in an adversarial environment~\cite{0xfrontrunning:online}.
-A few decentral exchange projects such as \textit{EtherDelta} and \textit{0xProject}, have proposed solutions for frontrunning, which is off-chain orderbooks.
-The methods discussed within these projects prevent blockchain network participants from front running the orders as the orders are private and not known to the network and will not be broadcasted.
-However they are introducing third parties, \eg relayers in 0xproject, to be managing the orders with the promise not to reorder or frontrun other orders.
 
@@
 \begin{itemize}
-\item{\textbf{Commitment scheme}: Also known as \textit{Commit and Reveal}, is a cryptographic primitive that enables one to commit to a value (\eg statement, document, \dots} while keeping it a secret and on a later time reveal the committed value~\cite{brassard1988minimum}.
-Commitment scheme is a good method to prevent information leakage from the sensitive transactions.
-This could be done by simply broadcasting the hash value of the committed data and later on revealing the values that would be hashed to the committed hash.
-In the case of decentral exchanges, user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, user sends reveal transaction revealing the order details which will be executed in a fair order.
-Another use of such commitment scheme, is in Decentral DNS, such as Ghazal or ENS.
-User will send a commit transaction similar to a sealed bid, once the transaction is confirmed and the grace period is over, user sends a reveal transaction revealing the bid and also the details of the requested domain.
-
-%although it does not hide the participatory factor (it shows the actor participated in the application but hides the details, obvious participation(commit))}
+\item{\textbf{Commit/Reveal}: describe.
+General solution to prevent data leaks of the transactions.
+although it does not hide the participatory factor (it shows the actor participated in the application but hides the details, obvious participation(commit))}
 % discussion about Anonymity-set ?
-
 \item{\textbf{Submarine sends}: describe. General solution similar to commit and reveal. This is to solve the participatory factor of the commit and reveal solution.}

### 2018-08-16 frontrunning/Latex/sections/paper.tex
[frontrunning] add charts and more detail for status ICO

--- 2018-08-15 frontrunning/Latex/sections/paper.tex
@@
 
-%@shayan: make charts and figure out the orange seller
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.5\linewidth]{figures/Mining_pool_ratio.png}
+\caption{The percentage of Ethereum blocks mined between block 3903900 and 3908029, this is the time frame in which Status.im ICO was running.
+This percentage roughly shows the hashing power ratio each miner had at that time.
+\label{fig:mining_pool_ratio}} % IS THIS STATEMENT CORRECT?
+\end{figure}
+
+F2Pool, an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure ~\ref{fig:mining_pool_ratio}), sent 100 Ether to 30 new Ethereum addresses before Status.im ICO started.
+On the time the ICO started F2Pool constructed 31 transactions from the addresses they controlled to the ICO token sale smart contract without broadcasting these transactions to the network and focused their mining power to mine only their own transactions with some exceptions.
+As shown in figure  ~\ref{fig:Transactions_miners_while_status_ico_cut}, most of the top miners in the mentioned time window, have mined almost the same number of failed and successful transactions which were directed toward Status.im token sale, however F2Pool's transaction indicate they successful transactions were equivalent to 10\% of the failed transactions, hence maximizing the mining rewards for them while censoring other transactions to the token sale smart contract.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.5\linewidth]{figures/Transactions_miners_while_status_ico_cut.png}
+\caption{This chart shows the miner behaviour on the time window that Status.im ICO was running. \label{fig:Transactions_miners_while_status_ico_cut}} 
+\end{figure}
+
+Involvement of F2Pool in this action becomes obvious when the transactions from these 30 addresses are traced.
+As shown in figure ~\ref{fig:f2poolfrontrun}, the funds deposited by F2Pool in these addresses where sent to Status.im ICO and mined by F2Pool.
+Once the dynamic ceiling algorithm refunded a portion of the sent funds back to these addresses, these funds were again sent back to F2Pool main address.
+%TODO: these need more details and proofs. ask Jeremy about how to go on about this!
 
@@
 although as this was not clearly communicated to users (UX issues?), there were tons of transactions that failed due to high gas price but also clogged the ethereum network as the miners chose transactions with higher gas price to be included in their blocks.
-
-% Proof of f2pool involvement: https://etherscan.io/address/0x5fb8373bf5086fb38ef0fb686b3092145de0d1c1
-% funds come from f2pool and refunds goes back to f2pool again
 
@@
 
-% this will include: The blocks mined by F2Pool, containing transactions (~100 ETH) to Status ICO, other blocks mined in that time period, the movement of status tokens from those addresses allegedly linked to F2Pool (or/and Yunbi in this case).
-% https://github.com/corpetty/ICO_analysis/blob/master/status/Status.ipynb
-% https://github.com/corpetty/py-etherscan-api
-
 %What is Bancor and how it can be frontrun:%
-
 \subsubsection{Bancor} %frontrunning by network participants.

### 2018-08-16 frontrunning/Latex/sections/paper.tex

@@
 % PAPER BEING SOLD HERE
-
 %______________________________________________________________%
@@
 \subsection{Front Running on the Blockchains}
+\label{sec:Front Running on the Blockchains}
 
@@
 %What is Bancor and how it can be frontrun:%
-\subsubsection{Bancor} %frontrunning by network participants.
-
-Bancor is an Ethereum-based application that allows users to exchange their tokens without any counter-party risk.
+\subsubsection{Bancor} \hfill\\
+\noindent Bancor is an Ethereum-based application that allows users to exchange their tokens without any counter-party risk.
 This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users.
@@
 
-\subsubsection{Domain Name Registration}
-
-%"domain name frontrunning." The practice resulted in Network Solutions registering a previously-unregistered domain to itself immediately after someone searched for it, then holding the domain for four days before it could be purchased by someone else or at another registrar.
-But the company claims that it's merely trying to protect customers from others doing exactly that.
-Until there is more regulation over frontrunning from ICANN, this is the best it can come up with
-
-%Following section talks about frontrunning in namespaces but limited to Ghazal. Will talk about NameCoin in the section of mitigations (commit & reveal method)
-%
-% PoC of frontrunning ghazal
-Although frontrunning attacks have been more showcased in the context of decentralized exchanges and trading systems, they are are not yet limited to the financial markets.
-Frontrunning can occur within other blockchain based applications such as naming systems.
-Blockchain-based namespaces have been introduced to eliminate the role of central parties \ie domain name system (DNS) which introduces single point of failures in the entire web.
+\subsubsection{Domain Name Front-running} \hfill\\    %Following section talks about frontrunning in namespaces but limited to Ghazal.
+Will talk about NameCoin in the section of mitigations (commit & reveal method)
+\noindent As mentioned in Section~\ref{sec:Front Running on the Blockchains}, although front-running attacks have been more showcased in the context of decentralized exchanges and trading systems, they are are not yet limited to the financial markets.
+Front-running can occur within other (non-financial) blockchain applications such as naming systems.
+Blockchain-based domain registrar have been introduced to eliminate the role of central parties \ie domain name system (DNS) which introduce single point of failures in the entire web.
 One such system is Ghazal, an Ethereum-based naming and PKI system~\cite{moosavighazal}.
@@
 As mentioned before, These transactions will sit in the mempool so that it would be mined by Ethereum miners and included in the block.
-During this period in which the transaction is not yet confirmed, frontrunning attack can occur by (i) dishonest miners and/or (ii) regular non-miner user.
+During this period in which the transaction is not yet confirmed, front-running attack can occur by (i) dishonest miners and/or (ii) regular non-miner user.
 In the first case, a miner would intercept the \textit{registerdomain} transaction and register that name ahead of the user.
-A regular non-miner node in the Ethereum network can frontrun other user's \textit{registerdomain} at a good profit by paying higher transaction fees.
-In both cases the adversarial party could sell the domain name to the users for higher price.
+A regular non-miner node in the Ethereum network can front-run other user's \textit{registerdomain} at a good profit by paying higher transaction fees.
+This practice allows the adversarial party  to register an unregistered domain immediately after someone searched for it, and sell the domain name to the users for a higher price.
+Note that, domain name front-running also occurs in the vanilla system.
+In this case, front-runners would monitor and identify domain names of interest, and sell it back to the other users with a higher price~\cite{sac022en33:online}.
+% PoC of frontrunning ghazal
 %TODO: also talk about ENS
@@
 
-\subsection{Application design to prevent frontrunning}
-Applications, in this case Dapps, could be designed in a way to prevent frontrunning.
+\subsection{Application Design to Prevent Front-running}
+
+Another way of preventing the front-running activities is to design the applications, whether they are decentralized (Dapps) or centralized, in such a way that no information would be available to the malicious parties which enables them to front-run the other users.
+Followings discuss the two techniques which can be used by the Apps/DApps developers while designing the systems to prevent front-running activities.
 
 \begin{itemize}
-\item{\textbf{Commitment scheme}: Also known as \textit{Commit and Reveal}, is a cryptographic primitive that enables one to commit to a value (\eg statement, document, \dots} while keeping it a secret and on a later time reveal the committed value~\cite{brassard1988minimum}.
+\item{\textbf{Commitment scheme}: Also known as \textit{Commit and Reveal}, is a cryptographic primitive that enables one to commit to a value (\eg statement, document, \etc}) while keeping it a secret and on a later time reveal the committed value~\cite{brassard1988minimum}.
 Commitment scheme is a good method to prevent information leakage from the sensitive transactions.
@@
 In the case of decentral exchanges, user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, user sends reveal transaction revealing the order details which will be executed in a fair order.
-Another use of such commitment scheme, is in Decentral DNS, such as Ghazal or ENS.
-User will send a commit transaction similar to a sealed bid, once the transaction is confirmed and the grace period is over, user sends a reveal transaction revealing the bid and also the details of the requested domain.
+Another use of such commitment scheme, is in decentralized naming systems, such as Ghazal or ENS.
+In this case, a user would send a commit transaction similar to a sealed bid, once the transaction is confirmed and the grace period is over, user would send a reveal transaction revealing the bid and also the details of the requested domain.
+Using this scheme, one is able to hide information from the adversarial parties in the system and prevent them from front-running.
 

### 2018-08-16 frontrunning/Latex/sections/paper.tex
[frontrunning] more on ICO frontrunning, preparing for status ICO dynamic ceiling

@@
 ICO is a method to distribute tokens based on the deposits of the native coin, Ether in the case of Ethereum.
-ICOs mostly have capped quantity of tokens \TODO{talk about why?}, there is a competition on who can get in to get the tokens at a discounted price, hence an opportunity to frontrun other transactions to get in.
+After a few hacking incidents on high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered.
+This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to late comers on the open markets~\cite{zetzsche2018ico, li2018initial}.
+ICOs started to experiment with different fair capping methods, such as reverse dutch auction, dynamic ceilings, \eg ~\cite{kaal2017initial}.
+This competition made ICOs a good opportunity for frontrunning attacks.
 

### 2018-08-16 frontrunning/Latex/sections/paper.tex
[frontrunning] status ICO draft done

@@
 % dynamic ceiling, fair token distribution --> status ICO
-\noindent ICO, Initial Coin Offering, is one of the blockchain applications, specially blockchains such as Ethereum with smart contract capability.
-The common practice is to deploy a smart contract on the blockchain indicating the details of the ICO such as the trade ratio, when it starts and ends, and more details on how it will be capped.
-In June 2017, Status.im started their ICO and within 3 hours they reached the dynamic ceiling in place that triggered the end of the ICO, summing in 300,000 ether in funds, estimated at more than 200 million dollars at the time of their ICO.
-~\cite{statusicoanalysis}.
-The idea behind Dynamic Ceilings is to make it more costly for larger contributors,  in the form of transaction fees, which have to split their contributions to different addresses, with minimal impact to smaller contributors~\cite{statuswhitepaper}.
+
+\noindent As discussed in ~\ref{sec:Front Running on the Blockchains}, capped ICOs are a good application for frontrunning attacks.
+In June 2017, Status.im~\cite{statuswhitepaper} started their ICO and within 3 hours they reached their cap, resulted in close to 300,000 Ether of funding.
+They used a \textit{fair} token distribution method called \textit{Dynamic ceiling}, which was in place to prevent large investments to take place early and limited the amount of Ether deposited, this was an attempt to increase the time window for smaller investors.
+They implemented multiple caps --ceiling-- which each would have a maximum amount that can be deposited.
+In this case every deposit would be checked by the smart contract and the exceeding amount would be refunded to the sender while the accepted amount would be sent to the Status.im wallet ~\cite{statusicoanalysis}.
 On the time of the ICO there were reports of Ethereum network being unusable and transactions were not confirming.
-Further study showed that some mining pools (\todo: define mining pool) could have been manipulating the network for their own profit.
+Further study showed that some mining pools might have been manipulating the network for their own profit.
 
@@
 F2Pool, an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure ~\ref{fig:mining_pool_ratio}), sent 100 Ether to 30 new Ethereum addresses before Status.im ICO started.
-On the time the ICO started F2Pool constructed 31 transactions from the addresses they controlled to the ICO token sale smart contract without broadcasting these transactions to the network and focused their mining power to mine only their own transactions with some exceptions.
-As shown in figure  ~\ref{fig:Transactions_miners_while_status_ico_cut}, most of the top miners in the mentioned time window, have mined almost the same number of failed and successful transactions which were directed toward Status.im token sale, however F2Pool's transaction indicate they successful transactions were equivalent to 10\% of the failed transactions, hence maximizing the mining rewards for them while censoring other transactions to the token sale smart contract.
+On the time the ICO started F2Pool constructed 31 transactions from the addresses they controlled to the ICO token sale smart contract --without broadcasting these transactions to the network-- and focused their mining power to mine their own transactions.
+As shown in figure  ~\ref{fig:Transactions_miners_while_status_ico_cut}, most of the top miners in the mentioned time frame, have mined almost the same number of failed and successful transactions which were directed toward Status.im token sale, however F2Pool's transactions indicate their successful transactions were equivalent to 10\% of the failed transactions, hence maximizing the mining rewards, on gas, while censoring other transactions to the token sale smart contract.
 
@@
 \centering
-\includegraphics[width=0.5\linewidth]{figures/Transactions_miners_while_status_ico_cut.png}
+\includegraphics[width=0.7\linewidth]{figures/Transactions_miners_while_status_ico_cut.png}
 \caption{This chart shows the miner behaviour on the time window that Status.im ICO was running. \label{fig:Transactions_miners_while_status_ico_cut}} 
@@
 Once the dynamic ceiling algorithm refunded a portion of the sent funds back to these addresses, these funds were again sent back to F2Pool main address.
-%TODO: these need more details and proofs. ask Jeremy about how to go on about this!
-
-% add more on capped ICOs, status used Distribution & Dynamic Ceilings : https://blog.status.im/distribution-dynamic-ceilings-e2f427f5cca  ~\cite{statuswhitepaper}
-
-% The dynamic ceiling and prevention of bigger investments getting their full investment in could be the reason behind the design of F2pool move, by having multiple addresses each contributing around 100ETH to the ICO smart contract, instead of having one big transaction in.
-%Also the ICO smart contract only accepted transactions with gas price lower than 50gwei, unless they were whitelisted before.
-this was for preventing high gas payers to get in front of the line.
-although as this was not clearly communicated to users (UX issues?), there were tons of transactions that failed due to high gas price but also clogged the ethereum network as the miners chose transactions with higher gas price to be included in their blocks.
 
@@
 \centering
-\includegraphics[width=0.5\linewidth]{figures/F2Pool_transactions_to_StatusICO_and_Refunds.png}
+\includegraphics[width=0.7\linewidth]{figures/F2Pool_transactions_to_StatusICO_and_Refunds.png}
 \caption{F2Pool prior to Status.im ICO deposited 100 Ether in multiple new Ethereum addresses.
@@
 \end{figure}
+
+Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their code to behave in centain way that could result in their monetary profit. 
+%TODO: these might need more details and proofs. ask Jeremy about how to go on about this!
+
+%Also the ICO smart contract only accepted transactions with gas price lower than 50gwei, unless they were whitelisted before.
+this was for preventing high gas payers to get in front of the line.
+although as this was not clearly communicated to users (UX issues?), there were tons of transactions that failed due to high gas price but also clogged the ethereum network as the miners chose transactions with higher gas price to be included in their blocks.
 
@@
 In the blockchain space, the designers of the decentral applications cannot rely on the justice system for unethical behaviour, and they must assume that each participant in the network acts rationally in their own self interest, the application will be operating in an adversarial environment~\cite{0xfrontrunning:online}.
-A few decentral exchange projects such as \textit{EtherDelta} and \textit{0xProject}, have proposed solutions for frontrunning, which is off-chain orderbooks.
+A few decentral exchange projects such as \textit{EtherDelta} and \textit{0xProject}~\cite{warren20170x}, have proposed solutions for frontrunning, which is off-chain orderbooks.
 The methods discussed within these projects prevent blockchain network participants from front running the orders as the orders are private and not known to the network and will not be broadcasted.

### 2018-08-16 frontrunning/Latex/sections/paper.tex
[frontrunning] minor changes and some notes

@@
 
-\subsection{Historical evidence}
+\subsection{Historical evidence in the Blockchain}
 As blockchain records are immutably recorded, there is enough historical data to analyze for possible front running detection.
@@
 
-\subsubsection{Status ICO} \hfill\\ %Frontrunning by a miner/mining pool 
-%@Shayan: Clean up this part, finish it! 
-% ICOs and ceiling
-% hard cap --> frontrun and buy the tokens in big chunk
-% dynamic ceiling, fair token distribution --> status ICO
-
+\subsubsection{Status ICO} \hfill\\ 
 \noindent As discussed in ~\ref{sec:Front Running on the Blockchains}, capped ICOs are a good application for frontrunning attacks.
@@
 
+%NOTE: @mahsa: is this considered a Historical evidence? should we talk about this somewhere else and maybe do a PoC on Ghazal for this section?
 \subsubsection{Domain Name Front-running} \hfill\\    %Following section talks about frontrunning in namespaces but limited to Ghazal.

### 2018-08-16 frontrunning/Latex/sections/paper.tex
[frontrunning] transaction reordering

@@
 \subsubsection{Miners}
-As mentioned above, since the Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the pending transactions sitting in the mempool and profit from a guaranteed price-rise.
+As mentioned above, since the Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the pending transactions sitting in the mempool, this is known as \textbf{transaction reordering} attack.
+Miners could use this power to attack any smart contract with transaction-ordering dependence vulnerability~\cite{luu2016making}.
 For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token, i.e.
@@
 On the time of the ICO they sent these deposits to Status ICO smart contract and prioritized mining of these transactions in their mining pool, this was to overcome the dynamic ceiling algorithm of the token sale smart contract.
-Later on they sent the refunded Ether back to their own address.\label{fig:f2poolfrontrun}}
+Later on they sent the refunded Ether back to their own address.
+[Graph made using Blockseer.com] \label{fig:f2poolfrontrun}}
 \end{figure}
 
-Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their code to behave in centain way that could result in their monetary profit. 
+Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their code to behave in certain way to frontrun other transactions and result in monetary profit.
 %TODO: these might need more details and proofs. ask Jeremy about how to go on about this!
@@
 
+\emph{Fixed transaction ordering}: One possible solution to fix current blockchains in regards to transaction reordering by miners has been proposed by da Silva et al~\cite{fixedordering2018silva}, which consist of an algorithm, Fixed Transaction Ordering and Admission (FTOA) algorithm, in the consensus protocol that enforces the order of the transactions.
+
 \begin{itemize}

### 2018-08-23 frontrunning/Latex/sections/paper.tex
[frontrunning] notes from Aug 22, 2018 meeting

@@
 In this case, when user decides that her order is not profitable anymore, she would send a cancelation transaction.
-Here the miner sees the cancelation transaction and puts his own order before the cancellation transaction to fill the order, potentially profiting from the order.
+Here the miner sees the cancelation transaction and puts his own order before the cancellation transaction --transaction reordering-- to fill the order, potentially profiting from the order.
 They can also include the canceled transaction in their block to collect the full gas limit used by that transaction~\cite{CostofDecentralization:online}.
@@
 \end{figure}
+
+%TODO: make pie charts for each mining pool, all non-status-ico transactions vs success-ico-transactions vs failed-ico=transactions
+
+%TODO: describe failed/ successful transactions, what they mean!
 
@@
 
+%TODO: commit and reveal : partcipation factor and no collatorization
+
 %TODO: a figure for commit and reveal?
@@
 
+%TODO: also fixes collatorize the commit, but what about no collatorization cases but hide the participation (not really a frontrunning case)
 \item{\textbf{Submarine sends}: describe. General solution similar to commit and reveal. This is to solve the participatory factor of the commit and reveal solution.}

### 2018-08-27 frontrunning/Latex/sections/paper.tex
[frontrunning] related work

@@
 
-\subsection{Front Running on the Blockchains}
+\subsection{How are Blockchain Applications Vulnarable to Frontrunning?}
 \label{sec:Front Running on the Blockchains}
@@
 
-~\cite{malinova2017market}
+There are a few papers discussing frontrunning in the context of blockchain and decentral ledgers.
+
+Malinova and Park discuss different design settings for financial markets and trading platforms on decentral ledgers ~\cite{malinova2017market}.
+They argue that blockchain brings a new options of transparency which effects traders identity behaviour, specially in the presence of intermediately front runners.
+They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make frontrunning costly and inefficient.
+
 ~\cite{aune2017footprints}
 ~\cite{breidenbach2018enter}
+
+% Double spend papers: ~\cite{bamert2013have} ~\cite{karame2012double}
 

### 2018-08-27 frontrunning/Latex/sections/paper.tex
[frontrunning] related work - fingerprint approach

--- 2018-08-23 frontrunning/Latex/sections/paper.tex
@@
 
-\subsection{Recent Literature on Blockchain frontrunning}
+\subsection{Recent Literature on Blockchain front-running}
+
+Aune~\etal\cite{aune2017footprints} discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage.
+As mentioned in Section~\ref{sec:What is frontrunning?}, the information leakage results the entire system to be vulnerable to the front-running.
+They also propose a cryptographic approach to prevent any decentralized system from front-running.
+In this approach, which is similar to commit and reveal, a transaction hash (fingerprint) is broadcast to the network to secure time priority while not revealing the information.
+Once the hash is processed and assigned an index and timestamp, the transaction details are broadcast.
+This makes the transaction and its has to be executed at their reserved time priority and not vulnerable to the front-running.
 

### 2018-08-27 frontrunning/Latex/sections/paper.tex
[frontrunning] frontrunning to front-running and more

--- 2018-08-27 frontrunning/Latex/sections/paper.tex
@@
 
-\subsection{What is Front running?} %Definition of frontrunning
-\label{sec:What is frontrunning?}
+\subsection{What is Front running?} %Definition of front-running
+\label{sec:What is front-running?}
 
@@
 
-\subsection{Front Running on the Blockchains}
+\subsection{How are Blockchain Applications Vulnarable to front-running?}
 \label{sec:Front Running on the Blockchains}
@@
 Although this data structure is known to be publicly visible to every network participants, information is layered  and some of them are accessed only by insiders.
-Any network participants that runs a full node on the blockchain is able to obtain those information and as mentioned in Section~\ref{sec:What is frontrunning?}, this leaves the application vulnerable to front running.
+Any network participants that runs a full node on the blockchain is able to obtain those information and as mentioned in Section~\ref{sec:What is front-running?}, this leaves the application vulnerable to front running.
 Decentralized exchanges are a group of blockchain financial applications where front running can be executed.
-Bancor \cite{hertzog2017bancor} is an example of such systems in which front runners benefit from potential price increase of the market stocks (details are provided in Section ...).
+Bancor \cite{hertzog2017bancor} is an example of such systems in which front-runners benefit from potential price increase of the market stocks (details are provided in Section ...).
 Decentralized namespaces, as blockchain non-financial applications, are another example.
@@
 ICOs started to experiment with different fair capping methods, such as reverse dutch auction, dynamic ceilings, \eg ~\cite{kaal2017initial}.
-This competition made ICOs a good opportunity for frontrunning attacks.
+This competition made ICOs a good opportunity for front-running attacks.
 
@@
 \section{Related Work}
-As the traditional frontrunning was originated to trading financial instruments most of the literature are focused on financial aspects of the markets. %TODO: expand this with something
+As the traditional front-running was originated to trading financial instruments most of the literature are focused on financial aspects of the markets. %TODO: expand this with something
 
-\subsection{Historical Context / Classic Frontrunning}
-Frontrunning was first appeared on the Chicago Board Options Exchange ( \textit{CBoE}) ~\cite{markham1988front}, and was identified by \textit{Securities Exchange Commission} in 1977 as the following:
+\subsection{Historical Context / Classic front-running}
+front-running was first appeared on the Chicago Board Options Exchange ( \textit{CBoE}) ~\cite{markham1988front}, and was identified by \textit{Securities Exchange Commission} in 1977 as the following:
 \begin{quote}
@@
 It encompasses at least three forms of conduct, each of which raises different regulatory and policy issues.9 They are: (1) trading by third parties who are tipped on an impending block trade ("tippee" trading); (2) transactions in which the owner or purchaser of the block trade itself engages in the offset- ting futures or options transaction as a means of "hedging" against price fluctuations caused by the block transaction ("self-front-running"); 1 ° and (3) transactions where a broker with knowledge of an impending customer block order trades ahead of that order for the broker's own profit ("trading ahead").
-% from JerryWMarkhamFrontRunning.pdf
+% from JerryWMarkhamfront-running.pdf
 
@@
 
-On the years after there were ongoing discussions between self-regulatory exchanges (\eg \textit{CBoE}) and  \textit{SEC} to regulate, detect and define laws and regulations to deal with frontrunning~\cite{markham1988front}, with \textit{SEC} stating:
+On the years after there were ongoing discussions between self-regulatory exchanges (\eg \textit{CBoE}) and  \textit{SEC} to regulate, detect and define laws and regulations to deal with front-running~\cite{markham1988front}, with \textit{SEC} stating:
 \begin{quote}
@@
 
-As defining what exactly is considered illegal front-running required more knowledge of how these new markets behave, \textit{CBoE} and other exchanges (and brokers) issued educational circulars for their members asserting that frontrunning violates existing rules, with some examples of what is considered frontrunning.
+As defining what exactly is considered illegal front-running required more knowledge of how these new markets behave, \textit{CBoE} and other exchanges (and brokers) issued educational circulars for their members asserting that front-running violates existing rules, with some examples of what is considered front-running.
 However difference of opinion regarding the unfairness o front running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~cite{sec1978optionsmarket}.
 
-Further reading on the early details on the history and challenges of detecting and regulating frontrunning can be found in~\cite{markham1988front} .
+Further reading on the early details on the history and challenges of detecting and regulating front-running can be found in~\cite{markham1988front} .
 % TODO: add a more recent publication here as well!
 
-Initially the frontrunning policies only applied to certain option markets, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{finra_2002}, which then in 2012 with the new amendment, FINRA Rule 5270, the frontrunning rule was extended to cover trading in an option, derivative, or other financial instruments overlying a security with some exceptions~\cite{sec2012frontrunning, finra_2012}.
+Initially the front-running policies only applied to certain option markets, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{finra_2002}, which then in 2012 with the new amendment, FINRA Rule 5270, the front-running rule was extended to cover trading in an option, derivative, or other financial instruments overlying a security with some exceptions~\cite{sec2012frontrunning, finra_2012}.
 
@@
 
+A few researchers discussed front-running in the context of blockchain and decentral ledgers.
+
 Aune~\etal\cite{aune2017footprints} discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage.
-As mentioned in Section~\ref{sec:What is frontrunning?}, the information leakage results the entire system to be vulnerable to the front-running.
+As mentioned in Section~\ref{sec:What is front-running?}, the information leakage results the entire system to be vulnerable to the front-running.
 They also propose a cryptographic approach to prevent any decentralized system from front-running.
@@
 Once the hash is processed and assigned an index and timestamp, the transaction details are broadcast.
-This makes the transaction and its has to be executed at their reserved time priority and not vulnerable to the front-running.
+This makes the transaction and its hash to be executed at their reserved time priority and not vulnerable to front-running.
 
-~\cite{malinova2017market}
-~\cite{aune2017footprints}
+Malinova and Park discuss different design settings for financial markets and trading platforms on decentral ledgers ~\cite{malinova2017market}.
+They argue that blockchain brings a new options of transparency which affects traders behaviour, specially in the presence of intermediary front-runners.
+They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make front-running costly and inefficient.
+
  ~\cite{breidenbach2018enter}
 
+% Double spend papers: ~\cite{bamert2013have} ~\cite{karame2012double}
+
 % NOTE: use double-spend paper (first)
-% talk about double-spend one kind of frontrunning (relationship between frontrunning vs double spend) rushing actors. 
+% talk about double-spend one kind of front-running (relationship between front-running vs double spend) rushing actors. 
 % Double-spending fast payments in bitcoin.pdf
@@
 \subsection{Who Can Front-run?}
-\label{sec:who can frontrun?}
+\label{sec:who can front-run?}
 
@@
 Thus, they possess special power in terms of front running as opposed to other users of the network.
-In the following, we discuss and compare the two groups of blockchain potential front runners.
+In the following, we discuss and compare the two groups of blockchain potential front-runners.
 
@@
 By doing so, he achieves a better rate from the other network users.
-Note that in this case, blockchain front runners are more visible to the network as they broadcast their transactions to all the network participants.
+Note that in this case, blockchain front-runners are more visible to the network as they broadcast their transactions to all the network participants.
 
@@
 %\begin{itemize}
-%\item{\textbf{Their own mined blocks}: The can only frontrun transactions within the block they mine. This could be done by reordering the transactions within the blocks.}
+%\item{\textbf{Their own mined blocks}: The can only front-run transactions within the block they mine. This could be done by reordering the transactions within the blocks.}
 %%^ If a miner or user sees an unconfirmed transaction in the mempool they could squeeze their own transaction to come in front and profit from that.
@@
 
-% maybe inlcude 0xbitcoin ERC721 mineable tokens frontrunning!
+% maybe inlcude 0xbitcoin ERC721 mineable tokens front-running!
 % mint: https://etherscan.io/tx/0x9883bc3ad018fd2b649982f88fbad7dc5abcb8f11c4f1d87ef814ba30c2b3428
@@
 \subsubsection{Status ICO} \hfill\\ 
-\noindent As discussed in ~\ref{sec:Front Running on the Blockchains}, capped ICOs are a good application for frontrunning attacks.
+\noindent As discussed in ~\ref{sec:Front Running on the Blockchains}, capped ICOs are a good application for front-running attacks.
 In June 2017, Status.im~\cite{statuswhitepaper} started their ICO and within 3 hours they reached their cap, resulted in close to 300,000 Ether of funding.
@@
 Involvement of F2Pool in this action becomes obvious when the transactions from these 30 addresses are traced.
-As shown in figure ~\ref{fig:f2poolfrontrun}, the funds deposited by F2Pool in these addresses where sent to Status.im ICO and mined by F2Pool.
+As shown in figure ~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses where sent to Status.im ICO and mined by F2Pool.
 Once the dynamic ceiling algorithm refunded a portion of the sent funds back to these addresses, these funds were again sent back to F2Pool main address.
@@
 Later on they sent the refunded Ether back to their own address.
-[Graph made using Blockseer.com] \label{fig:f2poolfrontrun}}
+[Graph made using Blockseer.com] \label{fig:f2poolfront-run}}
 \end{figure}
 
-Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their code to behave in certain way to frontrun other transactions and result in monetary profit.
+Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their code to behave in certain way to front-run other transactions and result in monetary profit.
 %TODO: these might need more details and proofs. ask Jeremy about how to go on about this!
@@
 
-%What is Bancor and how it can be frontrun:%
+%What is Bancor and how it can be front-run:%
 \subsubsection{Bancor} \hfill\\
@@
 This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favourable profits~\cite{BancorIs7:online}.
-As mentioned in Section~\ref{sec:who can frontrun?} and same as every other Ethereum based application, Bancor transactions can be front run by miners and other regular (non-miner) users.
+As mentioned in Section~\ref{sec:who can front-run?} and same as every other Ethereum based application, Bancor transactions can be front run by miners and other regular (non-miner) users.
 There is an implementation of a Bancor front running attack in the Python programming language which represent how a non-miner user can front run other network participants \cite{NewTab13:online}.
@@
 %\begin{itemize}
-%\item {\textbf{Miner Frontrunning.}} As mentioned, Bancor protocol uses an algorithm that automatically calculates the price of digital assets to provide better market liquidity.
+%\item {\textbf{Miner front-running.}} As mentioned, Bancor protocol uses an algorithm that automatically calculates the price of digital assets to provide better market liquidity.
 In the Bancor model, essentially buy orders increase the price of the tokens while sell order decrease it.
@@
 %
-%\item {\textbf{Non-miner Frontrunning.}} Researchers have also shown that a regular non-miner user can also front-run Bancor.
+%\item {\textbf{Non-miner front-running.}} Researchers have also shown that a regular non-miner user can also front-run Bancor.
 In order for the Bancor transactions to be executed on the Ethereum Virtual Machine (EVM),  users have to pay for the computations in small amount of Ether called \textit{gas}~\cite{AccountT67:online}.
@@
 %NOTE: @mahsa: is this considered a Historical evidence? should we talk about this somewhere else and maybe do a PoC on Ghazal for this section?
-\subsubsection{Domain Name Front-running} \hfill\\    %Following section talks about frontrunning in namespaces but limited to Ghazal.
+\subsubsection{Domain Name Front-running} \hfill\\    %Following section talks about front-running in namespaces but limited to Ghazal.
 Will talk about NameCoin in the section of mitigations (commit & reveal method)
@@
 In this case, front-runners would monitor and identify domain names of interest, and sell it back to the other users with a higher price~\cite{sac022en33:online}.
-% PoC of frontrunning ghazal
+% PoC of front-running ghazal
 %TODO: also talk about ENS
@@
 
-\section{How to stop frontrunning?}
-In the traditional markets, frontrunning is considered unethical and also illegal.
+\section{How to stop front-running?}
+In the traditional markets, front-running is considered unethical and also illegal.
 In the blockchain space, the designers of the decentral applications cannot rely on the justice system for unethical behaviour, and they must assume that each participant in the network acts rationally in their own self interest, the application will be operating in an adversarial environment~\cite{0xfrontrunning:online}.
-A few decentral exchange projects such as \textit{EtherDelta} and \textit{0xProject}~\cite{warren20170x}, have proposed solutions for frontrunning, which is off-chain orderbooks.
+A few decentral exchange projects such as \textit{EtherDelta} and \textit{0xProject}~\cite{warren20170x}, have proposed solutions for front-running, which is off-chain orderbooks.
 The methods discussed within these projects prevent blockchain network participants from front running the orders as the orders are private and not known to the network and will not be broadcasted.
-However they are introducing third parties, \eg relayers in 0xproject, to be managing the orders with the promise not to reorder or frontrun other orders.
+However they are introducing third parties, \eg relayers in 0xproject, to be managing the orders with the promise not to reorder or front-run other orders.
 
-\emph{Traditional Frontrunning Prevention Methods}. regulations/enforcement/broker education/sealed order
+\emph{Traditional front-running Prevention Methods}. regulations/enforcement/broker education/sealed order
 %@shayan: ^
 
-\emph{Blockchain Frontrunning mitigation/prevention}.
-The traditional methods of preventing frontrunning are based on regulation and restrictions applied to the brokers and actors within the markets, such methods do not apply to blockchains, no enforcement methods, ...
+\emph{Blockchain front-running mitigation/prevention}.
+The traditional methods of preventing front-running are based on regulation and restrictions applied to the brokers and actors within the markets, such methods do not apply to blockchains, no enforcement methods, ...
 
-There are two main approaches to prevent front running, one to design a blockchain that is frontrun-resistent , and the other to design the application logics in a way that front running is not possible.
+There are two main approaches to prevent front running, one to design a blockchain that is front-run-resistent , and the other to design the application logics in a way that front running is not possible.
 
-\subsection{Frontrun-resistent Blockchain}
-What does this mean to have a frontrun-resistent blockchain?  There are technical difficulties to achieve such solutions as there are unknown factors within such network designs (corner/edge cases).
+\subsection{front-run-resistent Blockchain}
+What does this mean to have a front-run-resistent blockchain?  There are technical difficulties to achieve such solutions as there are unknown factors within such network designs (corner/edge cases).
 
@@
 \begin{itemize}
-\item{\textbf{Privacy Preserving Blockchians}: Shielded transactions in ZCash do not reveal the sender, receiver, the amount and the data included in the transactions, hence they cannot be seen by network participants to be frontrunned.
+\item{\textbf{Privacy Preserving Blockchians}: Shielded transactions in ZCash do not reveal the sender, receiver, the amount and the data included in the transactions, hence they cannot be seen by network participants to be front-runned.
 Although this limites the functionality of the blockchain/smartcontracts/dapps }
@@
 
-%TODO: also fixes collatorize the commit, but what about no collatorization cases but hide the participation (not really a frontrunning case)
+%TODO: also fixes collatorize the commit, but what about no collatorization cases but hide the participation (not really a front-running case)
 \item{\textbf{Submarine sends}: describe. General solution similar to commit and reveal. This is to solve the participatory factor of the commit and reveal solution.}
 
-\item{\textbf{Application logic specific solution}: Depending on the use case of  the Dapp or the application, it could be designed in a way to deincentives some actors to frontrun the transactions or prevent them from doing so.
+\item{\textbf{Application logic specific solution}: Depending on the use case of  the Dapp or the application, it could be designed in a way to deincentives some actors to front-run the transactions or prevent them from doing so.
 As an example on desiging a decentral orderbook, it could be said that a miner could front run orders for financial gain on price improvement, however if the fees of the orders are sent to the miner of the block, it deincentiveses the miner to front run the orders as they already gain enough financial benefit from including the correct order of transactions.
@@
 
-% Could talk about a tool / a framework to detect frontrunning
+% Could talk about a tool / a framework to detect front-running
 

### 2018-08-27 frontrunning/Latex/sections/paper.tex
[frontrunning]double spend

@@
 \subsection{Recent Literature on Blockchain front-running}
-
-A few researchers discussed front-running in the context of blockchain and decentral ledgers.
-
-Aune~\etal\cite{aune2017footprints} discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage.
+%NOTE (ASK JEREMY): decentral or decentralized?
+There are only a few research carried out on the front-running subject in the context of blockchain and decentral ledgers. 
+Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage~\cite{aune2017footprints}.
 As mentioned in Section~\ref{sec:What is front-running?}, the information leakage results the entire system to be vulnerable to the front-running.
@@
  ~\cite{breidenbach2018enter}
+
+Some researchers have discussed the double spending attack on the Bitcoin blockchain.
+In this attack, as the name implies, the adversary spends a coin more than one time.
+To do so, he would use the coin as an input of a transaction and broadcast it to the network, before the transaction gets validated and executed, he broadcasts another transaction associated with a higher transaction fee which spends the same input ~\cite{bamert2013have, karame2012double}.
+This adversarial behaviour is similar to the front-running attack where the attacker would front-run other users by paying a higher gas price when broadcasting his transactions to the network.
+As mentioned above, this leads to the faster execution of the transaction on the Ethereum blcokchain.
 

### 2018-08-27 frontrunning/Latex/sections/paper.tex
[frontrunning] related work breidenbach2018enter

--- 2018-08-27 frontrunning/Latex/sections/paper.tex
@@
 
- ~\cite{breidenbach2018enter}
+Breidenbach~\etal ~\cite{breidenbach2018enter} face the front-running issue in the context of automating bug bounties for smart contracts.
+Upon submitting the bug bounty to the Hydra smart contract, one can front-run the bug report and claim the bounty instead of the original reporter.
+They propose \textit{Submarine Commitments} which is to conceal the bounty claim and the participatory factor.
+They claim submarine commitments ``are a stronger form of a commit-reveal scheme''.
 
@@
 
-\emph{Fixed transaction ordering}: One possible solution to fix current blockchains in regards to transaction reordering by miners has been proposed by da Silva et al~\cite{fixedordering2018silva}, which consist of an algorithm, Fixed Transaction Ordering and Admission (FTOA) algorithm, in the consensus protocol that enforces the order of the transactions.
+\emph{Fixed transaction ordering}: One possible solution to fix current blockchains in regards to transaction reordering by miners has been proposed by da Silva~\etal~\cite{fixedordering2018silva}, which consist of an algorithm, Fixed Transaction Ordering and Admission (FTOA) algorithm, in the consensus protocol that enforces the order of the transactions.
 
@@
 %TODO: also fixes collatorize the commit, but what about no collatorization cases but hide the participation (not really a front-running case)
-\item{\textbf{Submarine sends}: describe. General solution similar to commit and reveal. This is to solve the participatory factor of the commit and reveal solution.}
+\item{\textbf{Submarine Commitments}: describe. General solution similar to commit and reveal. This is to solve the participatory factor of the commit and reveal solution.}
 

### 2018-08-27 frontrunning/Latex/sections/paper.tex
[frontrunning] lots of change here and there

@@
 
-\subsection{What is Front running?} %Definition of front-running
+\subsection{What is Front-running?} %Definition of front-running
 \label{sec:What is front-running?}
 
-\emph{Front running} is analogous to any course of action during which a person benefits from prior access to inside or confidential market information to upcoming transactions and trades.
+\emph{Front-running} is analogous to any course of action during which a person benefits from prior access to inside or confidential market information about upcoming transactions and trades.
 This problem can occur in both financial and non-financial systems, however, it is more noticeable within the trading and exchange systems as it was originated back in stock markets.
 In the old times, all the trades were executed on papers, so in case of receiving a large order from a client, the broker might say this loud and other people around the table could be informed.
-Therefore, a malicious trader would now run in front of that order and put his own transaction in between (before the trade was executed) and profit from the price increase of the stock.
+Therefore, a malicious trader would now run in front of that order and put his own transaction in-between (before the trade was executed) and profit from the price increase of the stock.
 In other words, a group of market participants obtain non-public market information which allows them to front-run other users trades by putting their orders a head of those trades and benefit from advance knowledge of pending client orders.
-The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty.
-\textbf{should I explain more?!} Any sort of front-running activity within the financial markets is considered as an unethical and illegal practice as it is unfairly beneficial for a few market participants who have the privilege of acting on this information and taking advantages at the expense of the investor.
+The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty~\cite{liang2005distressed}.
+Any sort of front-running activity within the financial markets is considered as an unethical and illegal practice as it is unfairly beneficial for a few market participants who have the privilege of acting on this information and taking advantages at the expense of the investors.
 
@@
 
-\subsection{Historical Context / Classic front-running}
-front-running was first appeared on the Chicago Board Options Exchange ( \textit{CBoE}) ~\cite{markham1988front}, and was identified by \textit{Securities Exchange Commission} in 1977 as the following:
+\subsection{Literature on Tranditional Front-running}
+As traditional frontrunning has been the subject of discussion for decades, there are many literatures on this subject.
+Here we focus on the historical context and how the regulations evolved to be what they are today.\\
+Front-running was first appeared on the Chicago Board Options Exchange ( \textit{CBoE}) ~\cite{markham1988front}, and was identified by \textit{Securities Exchange Commission} in 1977 as the following:
 \begin{quote}
@@
 
-\subsection{Recent Literature on Blockchain front-running}
+\subsection{Literature on Blockchain Front-running}
 %NOTE (ASK JEREMY): decentral or decentralized?
-There are only a few research carried out on the front-running subject in the context of blockchain and decentral ledgers. 
+There are only a few research carried out on the front-running subject in the context of blockchain and decentral ledgers. \\
+
 Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage~\cite{aune2017footprints}.
@@
 
-Some researchers have discussed the double spending attack on the Bitcoin blockchain.
-In this attack, as the name implies, the adversary spends a coin more than one time.
+One of the properties of Blockchain technology was to overcome double-spend, however this does not apply for fast payments and zero-confirmation transactions.
+\textit{Double-spend attack}, as the name implies, the adversary spends a coin more than one time.
 To do so, he would use the coin as an input of a transaction and broadcast it to the network, before the transaction gets validated and executed, he broadcasts another transaction associated with a higher transaction fee which spends the same input ~\cite{bamert2013have, karame2012double}.
-This adversarial behaviour is similar to the front-running attack where the attacker would front-run other users by paying a higher gas price when broadcasting his transactions to the network.
-As mentioned above, this leads to the faster execution of the transaction on the Ethereum blcokchain.
-
-% Double spend papers: ~\cite{bamert2013have} ~\cite{karame2012double}
-
-% NOTE: use double-spend paper (first)
-% talk about double-spend one kind of front-running (relationship between front-running vs double spend) rushing actors. 
-% Double-spending fast payments in bitcoin.pdf
+This adversarial behaviour is similar to the front-running attack where the attacker would front-run other users by paying a higher transaction fee when broadcasting his transactions to the network, hence a higher priority transaction for miners to include in the block they mine.
 
@@
 
-\section{(On) Blockchain Front-running}
+\section{On Blockchain Front-running}
 
@@
 
-In general, all the network participants have the ability to front run specific transactions that are sent to the network.
+In general, all the network participants have the ability to front-run specific transactions that are sent to the network.
 However, miners can include any transactions they like into the block they attempt to mine.
-Thus, they possess special power in terms of front running as opposed to other users of the network.
+Thus, they possess special power in terms of front-running as opposed to other users of the network.
 In the following, we discuss and compare the two groups of blockchain potential front-runners.
 
+\subsubsection{Blockchain Participants}
+Any regular (miner or non-miner) user can front-run other transactions in the network.
+For regular users to front-run others on the blockchain, they need to be well connected to other nodes on the network.
+Doing so, they are able to listen to the network and monitor all transactions that are broadcast.
+On the Ethereum blockchain, users have to pay for the computations in small amount of Ether called \textit{gas}~\cite{AccountT67:online}.
+The price that users pay for transactions (a.k.a.
+transaction fees) can increase or decrease how quickly miners will execute them and include them within the blocks they mine.
+This is because the Ethereum miners consume resources to process the transactions and so receive the transaction fees after creating the blocks.
+Once seeing two identical transactions with different transaction fees,  a rational miner will prioritize the transaction that pays higher gas price per unit of gas --gasPrice--, this is due to limited space in the blocks while maximizes their profit in the block they mine.
+Therefore, any regular users who run a full-node Ethereum client can front-run pending transactions by sending similar transaction with higher gas price.
+For example, in a decentral exchange, he can monitor the network and once seeing a pending \textit{buy} transaction which will further increase the price of the asset, a front-runner can send a transaction with a higher gas price and hope to have his transaction mined ahead of the original pending transaction.
+By doing so, he achieves a better rate from the buyer.
+Note that in this case, blockchain front-runners are visible to the network as they broadcast their transactions to all the network participants.
+
 \subsubsection{Miners}
-As mentioned above, since the Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the pending transactions sitting in the mempool, this is known as \textbf{transaction reordering} attack.
-Miners could use this power to attack any smart contract with transaction-ordering dependence vulnerability~\cite{luu2016making}.
+Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this is known as \textbf{transaction reordering} attack.
 For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token, i.e.
-TKN, presumably if this transaction goes through, it causes the price the purchased token to increase.
-So the dishonest miner can step in front of this transaction and  place his own buy order ahead of it.
-He would simply create his \textit{buy} of 1000 TKN and include it within a block and now he mines the previous \textit{buy} transaction of 1000 TKN.
-Doing so, he would receive a better rate than other network users, and can sell the assets he has received and gain a price advantage at the expense of others.
+TKN, presumably if this transaction goes through, it causes the price of the purchased token to increase.
+So the dishonest miner can step in front of this transaction and place his own buy order ahead.
+He would simply create his \textit{buy} of 1000 TKN and include it in front of the previous \textit{buy} transaction of 1000 TKN in the block he mines.
+Doing so, he would receive a better rate than other network users, and afterwards can sell the assets he has bought and gain a price advantage at the expense of others.
 Similarly, a dishonest miner can sell his tokens in front, if he sees a pending \textit{sell} transaction.
-In an open source blockchain application, there is no rules on how transactions must be ordered and miners are free to send transactions in the order they prefer.
-However, miners can only front run other transactions (by reordering them) within the block they happen to mine.
-They could do this also by not broadcasting their own transactions to the network, this makes the miners to be less noticeable to the network when front running.
+In an open source blockchain application, there is no rules on how transactions must be ordered and miners are free to mine transactions in any order they prefer.
+However, miners can only front-run transactions within the blocks they happen to mine.
+They could do this also by not broadcasting their own transactions to the network, this makes the miners to be less noticeable to the network when front-running.
 Another example here is in the case of decentral exchanges and order cancellation.
@@
 In this case, when user decides that her order is not profitable anymore, she would send a cancelation transaction.
-Here the miner sees the cancelation transaction and puts his own order before the cancellation transaction --transaction reordering-- to fill the order, potentially profiting from the order.
+Here the miner sees the cancelation transaction and puts his own order in front of the cancellation transaction --transaction reordering-- to fill the order, potentially profiting from the order.
 They can also include the canceled transaction in their block to collect the full gas limit used by that transaction~\cite{CostofDecentralization:online}.
-
-\subsubsection{Blockchain users/nodes}
-Any regular (non-miner or miner) user can also front-run other transactions in the network.
-For regular users to front run others on the blockchain, they need to be fully/well connected to other nodes on the network.
-Doing so, they are able to listen to the network and monitor all transactions that are broadcast.
-On the Ethereum blockchain users have to pay for the computations in small amount of Ether called \textit{gas}~\cite{AccountT67:online}.
-The price that users pay for transactions (a.k.a.
-transaction fees) can increase or decrease how quickly miners will execute them and include them within the block they mine.
-This is because the Ethereum miners consume resources to process the transactions and so receive the transaction fees after creating the blocks.
-Once seeing two identical transactions with different transaction fees,
-%Given the limited space in the blocks, a rational miner will prioritize transactions that pay higher gas price per unit of gas, this maximizes their profit in the block they mine.
-miners act to maximize their profit and are free to mine the transaction which offers the highest fee.
-Therefore, any regular users who run a full-node Ethereum client can modify the order of pending transactions by paying with a higher gas price\ie by monitoring the network, upon seeing a  pending \textit{buy} transaction which will further increase the price of the asset, a font-runner user can pay a higher gas price and hope to have his transaction a head of the other one mined.
-By doing so, he achieves a better rate from the other network users.
-Note that in this case, blockchain front-runners are more visible to the network as they broadcast their transactions to all the network participants.
-
-%\subsubsection{Blockchain users/nodes}:
-%\begin{itemize}
-%\item{\textbf{Higher GasPrice}: Monitor transactions, rebroadcast with higher GasPrice}
-%\item{\textbf{Fully/well connected nodes}: Similar to HFT situation of faster connections to other nodes, for a higher chance of transaction inclusion, also Sybil attacks?} 
-%\item{\textbf{Noticable by the network}: More visible to the network as both transactions are broadcast to all the nodes}
-%\end{itemize}
-%
-%
-%\subsubsection{Miners}
-%
-%
-%\begin{itemize}
-%\item{\textbf{Their own mined blocks}: The can only front-run transactions within the block they mine. This could be done by reordering the transactions within the blocks.}
-%%^ If a miner or user sees an unconfirmed transaction in the mempool they could squeeze their own transaction to come in front and profit from that.
-Essentially, profitting from reordering the transactions.
-%
-%\item{\textbf{Less Noticable by the network}: Miners can include transactions within the blocks they happen to mine without broadcasting the transactions, hence less chance of being detected by the network participants.}
-%%Should the following be included? 
-%%\item{\textbf{Incentivized mitigation methods}: applications could pay the fees to the miners to incentives them to behave } 
-%\end{itemize}
+Front-running can also occur in non-financial smart contracts.
+As an example, smart contract which adds all the participants to a party invite list, could only be closed by the smart contract owner.
+In this case when the owner sends the transaction to close the list, a miner can include his own list of participants before the close transaction in the block he mines.
+This is an issue with the design of the smart contracts and is known as transaction-ordering dependence vulnerability~\cite{luu2016making}.
 
@@
 }
+% talk about Incentivized mitigation method designs to prevent front running.
 

### 2018-08-28 frontrunning/Latex/sections/paper.tex
[frontrunning] fix miner transactions figure

@@
 
-\subsection{How are Blockchain Applications Vulnarable to front-running?}
+\subsection{How are Blockchain Applications Vulnarable to Front-running?}
 \label{sec:Front Running on the Blockchains}
@@
 \centering
-\includegraphics[width=0.7\linewidth]{figures/Transactions_miners_while_status_ico_cut.png}
-\caption{This chart shows the miner behaviour on the time window that Status.im ICO was running. \label{fig:Transactions_miners_while_status_ico_cut}} 
+\includegraphics[width=0.7\linewidth]{figures/Transactions_miners_while_status_ico_cut_only_icotx.png}
+\caption{This chart shows the miners behaviour on the time window that Status.im ICO was running.
+\textit{Successful Transactions} are the transactions that led to deposit and generation of Status.im tokens and \textit{Failed Transactions} are the transactions to the token sale smart contract that failed to retrieve any tokens, for varias reasons.
+It is clear that the number of successful transactions mined by F2Pool do not follow the random homogeneous pattern of the rest of the network.
+\label{fig:Transactions_miners_while_status_ico_cut}}
 \end{figure}

### 2018-08-28 frontrunning/Latex/sections/paper.tex
[frontrunning] reconstruct the mitigation methods

@@
 
-\subsection{How are Blockchain Applications Vulnarable to Front-running?}
+\subsection{How are Blockchain Applications Vulnerable to Front-running?}
 \label{sec:Front Running on the Blockchains}
@@
 
-\section{How to stop front-running?}
+\section{How to stop Front-running?}
 In the traditional markets, front-running is considered unethical and also illegal.
@@
 
-\emph{Traditional front-running Prevention Methods}. regulations/enforcement/broker education/sealed order
+\emph{Traditional Front-running Prevention Methods}. regulations/enforcement/broker education/sealed order
 %@shayan: ^
@@
 
-There are two main approaches to prevent front running, one to design a blockchain that is front-run-resistent , and the other to design the application logics in a way that front running is not possible.
+There are two main approaches to prevent front running, one to design a blockchain that is front-run resistant , and the other to design the application logics in a way that front running is not possible.
 
-\subsection{front-run-resistent Blockchain}
-What does this mean to have a front-run-resistent blockchain?  There are technical difficulties to achieve such solutions as there are unknown factors within such network designs (corner/edge cases).
+\subsection{Front-run Resistant Blockchain}
+What does this mean to have a front-run resistant blockchain?  There are technical difficulties to achieve such solutions as there are unknown factors within such network designs (corner/edge cases).
 
-\emph{Fixed transaction ordering}: One possible solution to fix current blockchains in regards to transaction reordering by miners has been proposed by da Silva~\etal~\cite{fixedordering2018silva}, which consist of an algorithm, Fixed Transaction Ordering and Admission (FTOA) algorithm, in the consensus protocol that enforces the order of the transactions.
+\subsubsection{Design Decision \#1: Fixed Transaction Ordering\newline}
 
-\begin{itemize}
-\item{\textbf{Privacy Preserving Blockchians}: Shielded transactions in ZCash do not reveal the sender, receiver, the amount and the data included in the transactions, hence they cannot be seen by network participants to be front-runned.
-Although this limites the functionality of the blockchain/smartcontracts/dapps }
-\item{textbf{Loopring/Dual Athoring}: Talk about this possible solution}
+One possible solution to fix current blockchains in regards to transaction reordering by miners has been proposed by da Silva~\etal~\cite{fixedordering2018silva}, which consist of an algorithm, Fixed Transaction Ordering and Admission (FTOA) algorithm, in the consensus protocol that enforces the order of the transactions.
 
-\end{itemize}
+\subsubsection{Design Decision \#2:Privacy Preserving Blockchian\newline}
+Shielded transactions in ZCash do not reveal the sender, receiver, the amount and the data included in the transactions, hence they cannot be seen by network participants to be front-runned.
+Although this limits the functionality of the blockchain/smartcontracts/dapps
+
+\subsubsection{Design Decision \#3: Loopring/Dual Authoring\newline}
+Talk about this possible solution
+
+%TODO: research on more proposed solutions!
 
@@
 
-\begin{itemize}
-\item{\textbf{Commitment scheme}: Also known as \textit{Commit and Reveal}, is a cryptographic primitive that enables one to commit to a value (\eg statement, document, \etc}) while keeping it a secret and on a later time reveal the committed value~\cite{brassard1988minimum}.
+\subsubsection{Design Decision \#1: Commitment Scheme\newline}
+Also known as \textit{Commit and Reveal}, is a cryptographic primitive that enables one to commit to a value (\eg statement, document, \etc) while keeping it a secret and on a later time reveal the committed value~\cite{brassard1988minimum}.
 Commitment scheme is a good method to prevent information leakage from the sensitive transactions.
@@
 %TODO: also fixes collatorize the commit, but what about no collatorization cases but hide the participation (not really a front-running case)
-\item{\textbf{Submarine Commitments}: describe. General solution similar to commit and reveal. This is to solve the participatory factor of the commit and reveal solution.}
+\subsubsection{Design Decision \#2: Submarine Commitments\newline}
+describe. General solution similar to commit and reveal. This is to solve the participatory factor of the commit and reveal solution.
 
-\item{\textbf{Application logic specific solution}: Depending on the use case of  the Dapp or the application, it could be designed in a way to deincentives some actors to front-run the transactions or prevent them from doing so.
+\subsubsection{Design Decision \#3: Logic Specific Solution\newline}
+Depending on the use case of  the Dapp or the application, it could be designed in a way to deincentives some actors to front-run the transactions or prevent them from doing so.
 As an example on desiging a decentral orderbook, it could be said that a miner could front run orders for financial gain on price improvement, however if the fees of the orders are sent to the miner of the block, it deincentiveses the miner to front run the orders as they already gain enough financial benefit from including the correct order of transactions.
@@
 In such design the arrival time of the order does not matter as they are executed in batches.
-}
 % talk about Incentivized mitigation method designs to prevent front running.
@@
 
-\end{itemize}
+%TODO: research on more possible solutions!
 

### 2018-08-28 frontrunning/Latex/sections/paper.tex
[frontrunning] Commit and reveal done, some on submarine sends

@@
 \subsubsection{Design Decision \#1: Commitment Scheme\newline}
-Also known as \textit{Commit and Reveal}, is a cryptographic primitive that enables one to commit to a value (\eg statement, document, \etc) while keeping it a secret and on a later time reveal the committed value~\cite{brassard1988minimum}.
+Also known as \textit{Commit and Reveal}, is a cryptographic primitive that enables one to commit to a value --binding-- (\eg statement, document, data, \etc) while keeping it a secret and reveal the committed value on a later time~\cite{brassard1988minimum}.
 Commitment scheme is a good method to prevent information leakage from the sensitive transactions.
@@
 In the case of decentral exchanges, user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, user sends reveal transaction revealing the order details which will be executed in a fair order.
+Depending on the Dapp design, either the order is collateralized, which means the commitment transaction includes the funds required for fulfilling the order, which will leak some information about the order, or is not collateralized and opens up the possibility of user never revealing the commitment, which will be considered as a DoS attack.
 Another use of such commitment scheme, is in decentralized naming systems, such as Ghazal or ENS.
@@
 Using this scheme, one is able to hide information from the adversarial parties in the system and prevent them from front-running.
+Similar approach applies to on-chain voting as well ~\cite{adChainPLCRVoting}, using sealed votes, voters can make sure their votes are hidden until a later date, however their participation and weight of the vote are publicly known.
+Other than the collateralization issue for the commit and reveal scheme, another obvious issue is the participatory factor.
+As there will be a direct transaction from the user to the DApp, It will be obvious that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme.
+Both these issues, albeit hiding the details of the order and preventing direct front-running, leak information to other participants which could lead to more sophisticated front-running attacks depending on the application design.
 
-%TODO: commit and reveal : partcipation factor and no collatorization
+%TODO: a figure for commit and reveal?  @Mahsa
 
-%TODO: a figure for commit and reveal?
+\subsubsection{Design Decision \#2: Submarine Commitments\newline}
+Submarine Commitments~\cite{breidenbach2018enter, submarinesendHD} are similar to Commitment Schemes with some key differences, such as hiding participatory factor and being fully collateralized.
+However, they could be design in other ways to suit the need of the DApp.
+With submarine send, it is possible to hide sender, receiver, value and data, the commitment transaction is identical to a transaction to a newly generated address.
+Submarine sends could be a solution for sealed-bid auctions on the blockchain to hide the existence of the bids for other participants.
 
-%although it does not hide the participatory factor (it shows the actor participated in the application but hides the details, obvious participation(commit))}
-% discussion about Anonymity-set ?
-
-%TODO: also fixes collatorize the commit, but what about no collatorization cases but hide the participation (not really a front-running case)
-\subsubsection{Design Decision \#2: Submarine Commitments\newline}
 describe. General solution similar to commit and reveal. This is to solve the participatory factor of the commit and reveal solution.
@@
 In such design the arrival time of the order does not matter as they are executed in batches.
+
+Designs similar to Malinova~\cite{Malinova} uses economic models in their trading market design to make front-running expensive and more costly than profitable.
+
 % talk about Incentivized mitigation method designs to prevent front running.

### 2018-08-28 frontrunning/Latex/sections/paper.tex
[frontrunning] Logic Specific Solutions

--- 2018-08-28 frontrunning/Latex/sections/paper.tex
@@
 \subsection{Front-run Resistant Blockchain}
+%%start with this: !!PARAPHRIZE!! ::::: The inherent architecture of the blockchain makes the task of frontrunning a decentralized order book trivial as a miner.
 What does this mean to have a front-run resistant blockchain?  There are technical difficulties to achieve such solutions as there are unknown factors within such network designs (corner/edge cases).
@@
 \subsubsection{Design Decision \#2:Privacy Preserving Blockchian\newline}
+Market participants are concerned about revealing information on their past trades, pur- chases, income, or liquidity needs (forget about market participants >> this leads to frontrunning)
 Shielded transactions in ZCash do not reveal the sender, receiver, the amount and the data included in the transactions, hence they cannot be seen by network participants to be front-runned.
@@
 \subsubsection{Design Decision \#3: Logic Specific Solution\newline}
-Depending on the use case of  the Dapp or the application, it could be designed in a way to deincentives some actors to front-run the transactions or prevent them from doing so.
-As an example on desiging a decentral orderbook, it could be said that a miner could front run orders for financial gain on price improvement, however if the fees of the orders are sent to the miner of the block, it deincentiveses the miner to front run the orders as they already gain enough financial benefit from including the correct order of transactions.
-Another example for decentral orderbook design could be using call market design instead of  time-sensitive orderbooks.
-In such design the arrival time of the order does not matter as they are executed in batches.
+To prevent from front-running, one can design the application in a way that it is not possible to be front-run:
+
+\begin{itemize}
+
+\item{Disincentives Front-running Actors:} This solution, which is economic rather than technical, is to disincentives the miners by paying them.
+As mentioned, the main reasons for miners to front-run the other orders is the financial gain they receive on the price improvement.
+However, if the application is designed in a way that the fees of the orders are sent to the miner of the block, he would have no incentive to front-run the orders as he already gains enough financial benefit from acting fairly and executing the transactions on their correct order.
+
+\item{Eliminating the Time-Order Dependency:} The applications can be designed to not rely on the time for the orders to be executed.
+For example when designing a decentral exchange, one can use \emph{the call market design} instead of a time-sensitive order book.
+In a call market design, the arrival time of the orders do not matter as they are executed in batches.
+
+\item{Eliminating the Price Dynamics:} In the context of decentralized exchanges where orderly and fair execution of the orders (transactions) cannot be guaranteed,  another solution is to replace the order book with the \emph{limit order book}.
+In such design, orders are not executed automatically and an auction process helps the users to choose the orders they want to execute against.
+By doing so, even if the orders are front-run by other users or miners, there would be no price improvement and financial benefits as the orders are limited.
+
+\end{itemize}
+
 % talk about Incentivized mitigation method designs to prevent front running.

### 2018-08-28 frontrunning/Latex/sections/paper.tex
[frontrunning] submarine sends

--- 2018-08-28 frontrunning/Latex/sections/paper.tex
@@
 
-describe. General solution similar to commit and reveal. This is to solve the participatory factor of the commit and reveal solution.
+The details of how Submarine commitments work is outside the scope of this paper, however in summary, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality it is possible to generate one outgoing transaction from an address in which no private key exists.
+By constructing a transaction from that address to the DApp and funding that address we fulfil the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}.
 

### 2018-08-28 frontrunning/Latex/sections/paper.tex
[frontrunning] merge fixes

@@
 \subsubsection{Design Decision \#3: Logic Specific Solution\newline}
-Depending on the use case of  the Dapp or the application, it could be designed in a way to deincentives some actors to front-run the transactions or prevent them from doing so.
-As an example on desiging a decentral orderbook, it could be said that a miner could front run orders for financial gain on price improvement, however if the fees of the orders are sent to the miner of the block, it deincentiveses the miner to front run the orders as they already gain enough financial benefit from including the correct order of transactions.
-Another example for decentral orderbook design could be using call market design instead of  time-sensitive orderbooks.
-In such design the arrival time of the order does not matter as they are executed in batches.
+To prevent from front-running, one can design the application in a way that it is not possible to be front-run:
+
+\begin{itemize}
+
+\item{Disincentives Front-running Actors:} This solution, which is economic rather than technical, is to disincentives the miners by paying them.
+As mentioned, the main reasons for miners to front-run the other orders is the financial gain they receive on the price improvement.
+However, if the application is designed in a way that the fees of the orders are sent to the miner of the block, he would have no incentive to front-run the orders as he already gains enough financial benefit from acting fairly and executing the transactions on their correct order.
+
+\item{Eliminating the Time-Order Dependency:} The applications can be designed to not rely on the time for the orders to be executed.
+For example when designing a decentral exchange, one can use \emph{the call market design} instead of a time-sensitive order book.
+In a call market design, the arrival time of the orders do not matter as they are executed in batches.
+
+\item{Eliminating the Price Dynamics:} In the context of decentralized exchanges where orderly and fair execution of the orders (transactions) cannot be guaranteed,  another solution is to replace the order book with the \emph{limit order book}.
+In such design, orders are not executed automatically and an auction process helps the users to choose the orders they want to execute against.
+By doing so, even if the orders are front-run by other users or miners, there would be no price improvement and financial benefits as the orders are limited.
+
+\end{itemize}
 

### 2018-08-28 frontrunning/Latex/sections/paper.tex
[frontrunning] changes on logic specific solutions

@@
 
-\subsubsection{Design Decision \#3: Logic Specific Solution\newline}
-To prevent from front-running, one can design the application in a way that it is not possible to be front-run:
+\subsubsection{Design Decision \#3: Logic Specific Solutions\newline}
+To prevent front-running, one can design the application in a way that it is not possible to be front-run:
 
-\begin{itemize}
-
-\item{Disincentives Front-running Actors:} This solution, which is economic rather than technical, is to disincentives the miners by paying them.
+\textbf{Disincentives Front-running Actors:} This solution, which is economic rather than technical, is to disincentives the miners by paying them.
 As mentioned, the main reasons for miners to front-run the other orders is the financial gain they receive on the price improvement.
@@
 
-\item{Eliminating the Time-Order Dependency:} The applications can be designed to not rely on the time for the orders to be executed.
+\textbf{Eliminating the Time-Order Dependency:} The applications can be designed to not rely on the time for the orders to be executed.
 For example when designing a decentral exchange, one can use \emph{the call market design} instead of a time-sensitive order book.
@@
 
-\item{Eliminating the Price Dynamics:} In the context of decentralized exchanges where orderly and fair execution of the orders (transactions) cannot be guaranteed,  another solution is to replace the order book with the \emph{limit order book}.
+\textbf{Eliminating the Price Dynamics:} In the context of decentralized exchanges where orderly and fair execution of the orders (transactions) cannot be guaranteed,  another solution is to replace the order book with the \emph{limit order book}.
 In such design, orders are not executed automatically and an auction process helps the users to choose the orders they want to execute against.
@@
 
-\end{itemize}
-
-Designs similar to Malinova~\cite{Malinova} uses economic models in their trading market design to make front-running expensive and more costly than profitable.
-
-% talk about Incentivized mitigation method designs to prevent front running.
+Note that depending on the applications plans, there might exist design decisions which cause the system to be front-run resistant.
+For example, Malinova~\cite{Malinova} proposes a design for a decentral exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable.
 
 %Proof of burn methods ? 
-
 %TODO: research on more possible solutions!

### 2018-08-28 frontrunning/Latex/sections/paper.tex
[frontrunning] Submarines done(ish)

--- 2018-08-28 frontrunning/Latex/sections/paper.tex
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.7\linewidth]{figures/LibSubmarine.png}
+\caption{ Submarine implementation~\cite{libsubmarine}.
+User generates an Unlock transaction from which the commitment address is retrieved.
+By funding the commitment address, user is commited to the unlock transaction.
+After the commitment transaction, in the reveal phase, user sends the reveal transaction to the DApp and then after she can broadcast the Unlock transaction to unlock the funds in the commitment address.
+Finally after the ``Auction'' is over, anyone can call Finalize function to finilize the process.
+\label{fig:LibSubmarine}}
+\end{figure}
+
 \subsubsection{Design Decision \#3: Logic Specific Solution\newline}

### 2018-08-28 frontrunning/Latex/sections/paper.tex

--- 2018-08-28 frontrunning/Latex/sections/paper.tex
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.7\linewidth]{figures/LibSubmarine.png}
+\caption{ Submarine implementation~\cite{libsubmarine}.
+User generates an Unlock transaction from which the commitment address is retrieved.
+By funding the commitment address, user is commited to the unlock transaction.
+After the commitment transaction, in the reveal phase, user sends the reveal transaction to the DApp and then after she can broadcast the Unlock transaction to unlock the funds in the commitment address.
+Finally after the ``Auction'' is over, anyone can call Finalize function to finilize the process.
+\label{fig:LibSubmarine}}
+\end{figure}
+
 \subsubsection{Design Decision \#3: Logic Specific Solutions\newline}

### 2018-08-28 frontrunning/Latex/sections/paper.tex
[frontrunning] Edits on structure

@@
 
-\textbf{Disincentives Front-running Actors:} This solution, which is economic rather than technical, is to disincentives the miners by paying them.
+\noindent\emph{Disincentivizing Front-running Actors:} This solution, which is economic rather than technical, is to disincentives the miners by paying them.
 As mentioned, the main reasons for miners to front-run the other orders is the financial gain they receive on the price improvement.
@@
 
-\textbf{Eliminating the Time-Order Dependency:} The applications can be designed to not rely on the time for the orders to be executed.
+\noindent\emph{Eliminating Time-Order Dependency:} The applications can be designed to not rely on the time for the orders to be executed.
 For example when designing a decentral exchange, one can use \emph{the call market design} instead of a time-sensitive order book.
@@
 
-\textbf{Eliminating the Price Dynamics:} In the context of decentralized exchanges where orderly and fair execution of the orders (transactions) cannot be guaranteed,  another solution is to replace the order book with the \emph{limit order book}.
+\noindent\emph{Eliminating Price Dynamics:} In the context of decentralized exchanges where orderly and fair execution of the orders (transactions) cannot be guaranteed,  another solution is to replace the order book with the \emph{limit order book}.
 In such design, orders are not executed automatically and an auction process helps the users to choose the orders they want to execute against.

### 2018-08-28 frontrunning/Latex/sections/paper.tex
[frontrunning] Edits here and there

@@
 
-Another way of preventing the front-running activities is to design the applications, whether they are decentralized (Dapps) or centralized, in such a way that no information would be available to the malicious parties which enables them to front-run the other users.
+Another method to prevent front-running activities is to design the applications, whether they are decentralized (Dapps) or centralized, in such a way that no information would be available to the malicious parties to enable them to front-run the other users.
 Followings discuss the two techniques which can be used by the Apps/DApps developers while designing the systems to prevent front-running activities.
@@
 \subsubsection{Design Decision \#1: Commitment Scheme\newline}
-Also known as \textit{Commit and Reveal}, is a cryptographic primitive that enables one to commit to a value --binding-- (\eg statement, document, data, \etc) while keeping it a secret and reveal the committed value on a later time~\cite{brassard1988minimum}.
-Commitment scheme is a good method to prevent information leakage from the sensitive transactions.
+Commitment scheme, also known as \textit{commit and reveal}, is a cryptographic primitive that enables one to commit to a value --binding-- (\eg statement, document, data, \etc) while keeping it a secret and reveal the committed value on a later time~\cite{brassard1988minimum}.
+Commitment scheme is a robust method to prevent information leakage from the sensitive transactions.
 This could be done by simply broadcasting the hash value of the committed data and later on revealing the values that would be hashed to the committed hash.
@@
 \subsubsection{Design Decision \#2: Submarine Commitments\newline}
-Submarine Commitments~\cite{breidenbach2018enter, submarinesendHD} are similar to Commitment Schemes with some key differences, such as hiding participatory factor and being fully collateralized.
+Submarine Commitments~\cite{breidenbach2018enter, submarinesendHD} are similar to the commitment schemes with some key differences such as hiding participatory factor and being fully collateralized.
 However, they could be design in other ways to suit the need of the DApp.
@@
 
-The details of how Submarine commitments work is outside the scope of this paper, however in summary, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality it is possible to generate one outgoing transaction from an address in which no private key exists.
-By constructing a transaction from that address to the DApp and funding that address we fulfil the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}.
+The details of how Submarine commitments work are outside the scope of this paper, however in summary, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality it is possible to generate one outgoing transaction from an address in which no private key exists.
+By constructing a transaction from that address to the DApp and funding that address, we fulfil the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}.
 
@@
 User generates an Unlock transaction from which the commitment address is retrieved.
-By funding the commitment address, user is commited to the unlock transaction.
+By funding the commitment address, user is committed to the unlock transaction.
 After the commitment transaction, in the reveal phase, user sends the reveal transaction to the DApp and then after she can broadcast the Unlock transaction to unlock the funds in the commitment address.
-Finally after the ``Auction'' is over, anyone can call Finalize function to finilize the process.
+Finally after the ``Auction'' is over, anyone can call Finalize function to finalize the process.
 \label{fig:LibSubmarine}}

### 2018-08-28 frontrunning/Latex/sections/paper.tex
[frontrunning] add fig submarine

--- 2018-08-28 frontrunning/Latex/sections/paper.tex
@@
 The details of how Submarine commitments work is outside the scope of this paper, however in summary, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality it is possible to generate one outgoing transaction from an address in which no private key exists.
-By constructing a transaction from that address to the DApp and funding that address we fulfil the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}.
+By constructing a transaction from that address to the DApp and funding that address we fulfil the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}, see Figure~\ref{fig:LibSubmarine}.
 

### 2018-08-28 frontrunning/Latex/sections/paper.tex

--- 2018-08-28 frontrunning/Latex/sections/paper.tex
@@
 Other than the collateralization issue for the commit and reveal scheme, another obvious issue is the participatory factor.
-As there will be a direct transaction from the user to the DApp, It will be obvious that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme.
+For anyone watching the DApp address, there will be a direct transaction from the user to the DApp address, It will be obvious that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme.
 Both these issues, albeit hiding the details of the order and preventing direct front-running, leak information to other participants which could lead to more sophisticated front-running attacks depending on the application design.
@@
 
-The details of how Submarine commitments work are outside the scope of this paper, however in summary, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality it is possible to generate one outgoing transaction from an address in which no private key exists.
-By constructing a transaction from that address to the DApp and funding that address, we fulfil the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}.
+The details of how Submarine commitments work is outside the scope of this paper, however in summary, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality it is possible to generate one outgoing transaction from an address in which no private key exists.
+By constructing a transaction from that address to the DApp and funding that address we fulfil the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}, see Figure~\ref{fig:LibSubmarine}.
 
@@
 \end{figure}
+%https://www.lucidchart.com/invitations/accept/3a259b74-1162-4fb5-8023-eb0311018295
 

### 2018-08-29 frontrunning/Latex/sections/paper.tex
[frontrunning] commit-reveal figure

@@
 Commitment scheme is a robust method to prevent information leakage from the sensitive transactions.
-This could be done by simply broadcasting the hash value of the committed data and later on revealing the values that would be hashed to the committed hash.
+This could be done by simply broadcasting the hash value of the committed data and later on revealing the values that would be hashed to the committed hash, see Figure~\ref{fig:commitReveal}.
 In the case of decentral exchanges, user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, user sends reveal transaction revealing the order details which will be executed in a fair order.
@@
 
-%TODO: a figure for commit and reveal?  @Mahsa
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.5\linewidth]{figures/commit-reveal.png}
+\caption{ Commit and Reveal.
+User sends a commitment transaction with the hash of the data, After the commitment period is over, user sends her reveal transaction to the DApp revealing the information that matches the commitment.
+\label{fig:commitReveal}}
+\end{figure}
+%https://www.lucidchart.com/invitations/accept/3cd4c865-83d4-4c71-9a4a-f2e870f2db2c
 
@@
 \centering
-\includegraphics[width=0.7\linewidth]{figures/LibSubmarine.png}
+\includegraphics[width=0.5\linewidth]{figures/LibSubmarine.png}
 \caption{ Submarine implementation~\cite{libsubmarine}.

### 2018-08-30 frontrunning/Latex/sections/paper.tex
[frontrunning] add figure for regular front-running

@@
 Once seeing two identical transactions with different transaction fees,  a rational miner will prioritize the transaction that pays higher gas price per unit of gas --gasPrice--, this is due to limited space in the blocks while maximizes their profit in the block they mine.
-Therefore, any regular users who run a full-node Ethereum client can front-run pending transactions by sending similar transaction with higher gas price.
+Therefore, any regular users who run a full-node Ethereum client can front-run pending transactions by sending similar transaction with higher gas price, see Figure~\ref{fig:RegularFrontrunning}.
 For example, in a decentral exchange, he can monitor the network and once seeing a pending \textit{buy} transaction which will further increase the price of the asset, a front-runner can send a transaction with a higher gas price and hope to have his transaction mined ahead of the original pending transaction.
@@
 Note that in this case, blockchain front-runners are visible to the network as they broadcast their transactions to all the network participants.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.7\linewidth]{figures/Regular_frontrunning.png}
+\caption{The Adversary up on seeing the Buy order, sends his own buy order with higher gas to front-run the first order. \label{fig:RegularFrontrunning}} 
+\end{figure}
 
@@
 This is an issue with the design of the smart contracts and is known as transaction-ordering dependence vulnerability~\cite{luu2016making}.
+
+%TODO: figure for miners reordering attack. it should be just two blocks with transaction inside where the second "modified" one has the orders specifically to profit the miner.
 
@@
 \includegraphics[width=0.5\linewidth]{figures/LibSubmarine.png}
-\caption{ Submarine implementation~\cite{libsubmarine}.
-User generates an Unlock transaction from which the commitment address is retrieved.
-By funding the commitment address, user is committed to the unlock transaction.
-After the commitment transaction, in the reveal phase, user sends the reveal transaction to the DApp and then after she can broadcast the Unlock transaction to unlock the funds in the commitment address.
-Finally after the ``Auction'' is over, anyone can call Finalize function to finalize the process.
+\caption{ Submarine Send~\cite{libsubmarine}.
+User generates an \textit{Unlock} transaction from which the commitment address is retrieved.
+By funding the \textit{commitment address}, user is committed to the unlock transaction.
+After the commitment transaction, in the reveal phase, user sends the \textit{reveal transaction} to the DApp and then after she can broadcast the Unlock transaction to unlock the funds in the commitment address.
+Finally after the ``Auction'' is over, anyone can call \textit{Finalize} function to finalize the process.
 \label{fig:LibSubmarine}}

### 2018-08-30 frontrunning/Latex/sections/paper.tex
[frontrunning] minor changes
[forontrunning] minor edits

@@
 \end{figure}
+%https://www.lucidchart.com/invitations/accept/f8ca2662-5269-425d-9deb-deb14af2aac7
 
@@
 \subsection{Front-run Resistant Blockchain}
-%%start with this: !!PARAPHRIZE!! ::::: The inherent architecture of the blockchain makes the task of frontrunning a decentralized order book trivial as a miner.
-What does this mean to have a front-run resistant blockchain?  There are technical difficulties to achieve such solutions as there are unknown factors within such network designs (corner/edge cases).
+What does this mean to have a front-run resistant blockchain?
+There are technical difficulties to achieve such solutions as there are unknown factors within such network designs (corner/edge cases).
+In this section, we describe the potential solutions using which, one can design and implement a decentral application that is resistant to front-running.
 
@@
 
-One possible solution to fix current blockchains in regards to transaction reordering by miners has been proposed by da Silva~\etal~\cite{fixedordering2018silva}, which consist of an algorithm, Fixed Transaction Ordering and Admission (FTOA) algorithm, in the consensus protocol that enforces the order of the transactions.
+One possible solution to fix current blockchains in regards to transaction reordering by miners has been proposed by da Silva~\etal~\cite{fixedordering2018silva}.
+This solution consists of an algorithm, known as Fixed Transaction Ordering and Admission (FTOA) algorithm, in the consensus protocol that enforces the order of the transactions.
 
 \subsubsection{Design Decision \#2:Privacy Preserving Blockchian\newline}
-Market participants are concerned about revealing information on their past trades, pur- chases, income, or liquidity needs (forget about market participants >> this leads to frontrunning)
+
+%NEEDS TO BE DONE:
+Market participants are concerned about revealing information on their past trades, purchases, income, or liquidity needs (forget about market participants >> this leads to frontrunning)
 Shielded transactions in ZCash do not reveal the sender, receiver, the amount and the data included in the transactions, hence they cannot be seen by network participants to be front-runned.

### 2018-08-30 frontrunning/Latex/sections/paper.tex
[frontrunning] CASE STUDY
[frontrunning] notes from meeting Aug 30

@@
 \section{Introduction}
+
+\textbf{CASE STUDY} should be used in here, also in abstract, also at the end of intro section
+
 % Why is this important.
@@
 %______________________________________________________________%
+
+%TODO: Censorship vs frontrunning ! can withholding a transaction be considered as frontrunning? 
+%using frontrunning losely, we do not want to defining what exactly front running is, but talking about possibiities of attacks in this nature and also how to prevent these from happening .
 
@@
 \label{sec:Front Running on the Blockchains}
+
+%TODO:  do this on top 10 Dapps, based on gas usage or a website.
+we wanted to look through the popular dapps but there's no such a list .
+therefor we used different examples as we could came up with.
+%maybe look into cryptokitties breed() if it is possible to front run any section
+%possible : maybe top 25 active daily usage DApps from dappradar.com
 
@@
 
-\subsection{Literature on Tranditional Front-running}
+\subsection{Literature on Traditional Front-running}
 As traditional frontrunning has been the subject of discussion for decades, there are many literatures on this subject.
@@
 
-\subsection{Historical evidence in the Blockchain}
+\section{Historical evidence in the Blockchain}
 As blockchain records are immutably recorded, there is enough historical data to analyze for possible front running detection.
 For examples here we research some of the events of such attacks happening in the Ethereum blockchain applications.
+
+%TODO: talk about why these three.
+just for emprical /theorical examples, there are tons of examples of front-running, here's three that we chose that are way different.
+one is emprical that we had to build tools to
 
@@
 
-\subsubsection{Status ICO} \hfill\\ 
+\subsection{Status ICO} \hfill\\ 
 \noindent As discussed in ~\ref{sec:Front Running on the Blockchains}, capped ICOs are a good application for front-running attacks.
@@
 As shown in figure  ~\ref{fig:Transactions_miners_while_status_ico_cut}, most of the top miners in the mentioned time frame, have mined almost the same number of failed and successful transactions which were directed toward Status.im token sale, however F2Pool's transactions indicate their successful transactions were equivalent to 10\% of the failed transactions, hence maximizing the mining rewards, on gas, while censoring other transactions to the token sale smart contract.
+
+%TODO: talk about the tools made to figure this out , it's ok to use jargons and technical terms. maybe a paragraph or two on this, with interfaces and service. ethereum-etl, google bigquery, ...
 
@@
 
+%TODO: this might not considered as the definition of frontrunning, but it is common to use frontrunning for this so we do the same.
+
 %Also the ICO smart contract only accepted transactions with gas price lower than 50gwei, unless they were whitelisted before.
@@
 %What is Bancor and how it can be front-run:%
-\subsubsection{Bancor} \hfill\\
+\subsection{Bancor} \hfill\\
 \noindent Bancor is an Ethereum-based application that allows users to exchange their tokens without any counter-party risk.
@@
 %NOTE: @mahsa: is this considered a Historical evidence? should we talk about this somewhere else and maybe do a PoC on Ghazal for this section?
-\subsubsection{Domain Name Front-running} \hfill\\    %Following section talks about front-running in namespaces but limited to Ghazal.
+\subsection{Domain Name Front-running} \hfill\\    %Following section talks about front-running in namespaces but limited to Ghazal.
 Will talk about NameCoin in the section of mitigations (commit & reveal method)
@@
 %TODO: also talk about ENS
+
+%TODO: ian goberg: private information retrieval .
+talk about domain name frontrunning in the traditional sense and how goDaddy can steal the domain when queried for availablity.
+however in blockchain the queiry is private and does not reveal the intention that you want to buy the domain.
+View only / solidity code on how to enable this
 
@@
 
-\subsubsection{Design Decision \#2:Privacy Preserving Blockchian\newline}
+\subsubsection{Design Decision \#2:Privacy Preserving Blockchain\newline}
 
@@
 Followings discuss the two techniques which can be used by the Apps/DApps developers while designing the systems to prevent front-running activities.
+
+% TODO: also talk about drawbacks, more expensinve, more transactions, UX, forget to reveal.
 
@@
 
-\noindent\emph{Eliminating Price Dynamics:} In the context of decentralized exchanges where orderly and fair execution of the orders (transactions) cannot be guaranteed,  another solution is to replace the order book with the \emph{limit order book}.
+%TODO: maybe remove this 
+%\noindent\emph{Eliminating Price Dynamics:} In the context of decentralized exchanges where orderly and fair execution of the orders (transactions) cannot be guaranteed,  another solution is to replace the order book with the \emph{limit order book}.
 In such design, orders are not executed automatically and an auction process helps the users to choose the orders they want to execute against.

### 2018-08-30 frontrunning/Latex/sections/paper.tex
[frontrunning] notes from the meeting

--- 2018-08-30 frontrunning/Latex/sections/paper.tex
@@
 \section{Introduction}
+
+Have a small discussion about arbitrage and censorship just to show that they orbit around front-running.
+For the FC: \textbf{CASE STUDY} should be used in here, also in abstract, also at the end of intro section.
+
 % Why is this important.
@@
 
-\subsection{How are Blockchain Applications Vulnerable to Front-running?}
-\label{sec:Front Running on the Blockchains}
+\subsection{How are Blockchain Applications Vulnerable to Front-running?} %which blockchain applications?
+\label{sec:Front Running on the Blockchains}t
+
+%Jeremy's Comments: Find some examples; you have to justify why you talked about only a specific group of examples.
+Need to have a criteria for what is vulnerable to frontrunning: like top ten dapps from specific blogs.
+Have a criteria.
 
@@
 
-\subsection{Literature on Tranditional Front-running}
+\subsection{Literature on Traditional Front-running}
+
+% talk about the AMF frontrunning.
+
 As traditional frontrunning has been the subject of discussion for decades, there are many literatures on this subject.
@@
 
-\subsection{Historical evidence in the Blockchain}
+\subsection{Historical evidence in the Blockchain}  % JEREMY's COMMENT:  try to sell it in a way that that the audience know that there are 1000 of the applications prone to the frontrunning but we picked 3 because they are different.
+
 As blockchain records are immutably recorded, there is enough historical data to analyze for possible front running detection.
@@
 Will talk about NameCoin in the section of mitigations (commit & reveal method)
+
+%Jeremy's Comment: contrast ghazal vs ens, or try to have some historical evidence for namespace on the Ethereums. Try too make ghazal less central.
+%Jeremy's comments: also talk about the "private information retrieval" (Ian Goldberg's work at waterloo)
+
 \noindent As mentioned in Section~\ref{sec:Front Running on the Blockchains}, although front-running attacks have been more showcased in the context of decentralized exchanges and trading systems, they are are not yet limited to the financial markets.
@@
 
-\subsubsection{Design Decision \#1: Commitment Scheme\newline}
-Commitment scheme, also known as \textit{commit and reveal}, is a cryptographic primitive that enables one to commit to a value --binding-- (\eg statement, document, data, \etc) while keeping it a secret and reveal the committed value on a later time~\cite{brassard1988minimum}.
+\subsubsection{Design Decision \#1: Commitment Scheme\newline} %talk about the drawbacks of this scheme: eg: you may forget to reveal. 
+Commitment scheme is a cryptographic primitive that enables one to commit to a value --binding-- (\eg statement, document, data, \etc) while keeping it a secret and reveal the committed value on a later time~\cite{brassard1988minimum}.
 Commitment scheme is a robust method to prevent information leakage from the sensitive transactions.
@@
 
+\noindent\emph{Eliminating Time-Order Dependency:} The applications can be designed to not rely on the time for the orders to be executed.
+For example when designing a decentral exchange, one can use \emph{the call market design} instead of a time-sensitive order book.
+In a call market design, the arrival time of the orders do not matter as they are executed in batches [cite Jeremy's prediction markets paper].
+
 \noindent\emph{Disincentivizing Front-running Actors:} This solution, which is economic rather than technical, is to disincentives the miners by paying them.
@@
 However, if the application is designed in a way that the fees of the orders are sent to the miner of the block, he would have no incentive to front-run the orders as he already gains enough financial benefit from acting fairly and executing the transactions on their correct order.
-
-\noindent\emph{Eliminating Time-Order Dependency:} The applications can be designed to not rely on the time for the orders to be executed.
-For example when designing a decentral exchange, one can use \emph{the call market design} instead of a time-sensitive order book.
-In a call market design, the arrival time of the orders do not matter as they are executed in batches.
 

### 2018-09-03 frontrunning/Latex/sections/paper.tex
[frontrunning] minor changes

@@
 
+%TODO: Censorship vs frontrunning ! can withholding a transaction be considered as frontrunning? 
+%using frontrunning losely, we do not want to defining what exactly front running is, but talking about possibiities of attacks in this nature and also how to prevent these from happening .
+
 \section{Preliminaries}
@@
 \label{sec:What is front-running?}
+
+%TODO:  do this on top 10 Dapps, based on gas usage or a website.
+we wanted to look through the popular dapps but there's no such a list .
+therefor we used different examples as we could came up with.
+%maybe look into cryptokitties breed() if it is possible to front run any section
+%possible : maybe top 25 active daily usage DApps from dappradar.com
 
@@
 Have a criteria.
+
+%TODO:  do this on top 10 Dapps, based on gas usage or a website.
+we wanted to look through the popular dapps but there's no such a list .
+therefor we used different examples as we could came up with.
+%maybe look into cryptokitties breed() if it is possible to front run any section
+%possible : maybe top 25 active daily usage DApps from https://dappradar.com/dapps
 
@@
 
+%TODO: talk about why these three.
+just for emprical /theorical examples, there are tons of examples of front-running, here's three that we chose that are way different.
+one is emprical that we had to build tools to
+
 % maybe inlcude 0xbitcoin ERC721 mineable tokens front-running!
@@
 Further study showed that some mining pools might have been manipulating the network for their own profit.
+On the other note, There were many transactions sent with higher gasPrice to front-run other transactions, however these transactions failed due to the restriction in place in the ICO smart contract to reject any transactions with higher than 50GWei gasPrice in an attempt to prevent this kind of front-running.
 
@@
 Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their code to behave in certain way to front-run other transactions and result in monetary profit.
+The dataset used for this analysis can be found on our github repository\footnote{Frontrunning Status.im ICO dataset: \url{http://github.com/TODO:ANONYMOUS}}
 %TODO: these might need more details and proofs. ask Jeremy about how to go on about this!
 
-%Also the ICO smart contract only accepted transactions with gas price lower than 50gwei, unless they were whitelisted before.
-this was for preventing high gas payers to get in front of the line.
-although as this was not clearly communicated to users (UX issues?), there were tons of transactions that failed due to high gas price but also clogged the ethereum network as the miners chose transactions with higher gas price to be included in their blocks.
-
 %What is Bancor and how it can be front-run:%
-\subsubsection{Bancor} \hfill\\
+\subsection{Bancor} \hfill\\
 \noindent Bancor is an Ethereum-based application that allows users to exchange their tokens without any counter-party risk.
@@
 There is an implementation of a Bancor front running attack in the Python programming language which represent how a non-miner user can front run other network participants \cite{NewTab13:online}.
-
-%\begin{itemize}
-%\item {\textbf{Miner front-running.}} As mentioned, Bancor protocol uses an algorithm that automatically calculates the price of digital assets to provide better market liquidity.
-In the Bancor model, essentially buy orders increase the price of the tokens while sell order decrease it.
-Since the Blockchain miners are the only parties who can decide on the order of transactions within a block, they can easily intercept and reorder the pending transactions sitting in the mempool and profit from a guaranteed price-rise.
-For example, a miner learns about the pending \textit{buy} transaction of 1000 Ether, based on the Bancor design, if this transaction goes through, it causes the price of Ether to increase.
-So the dishonest miner can step in front of this transaction and  place his own buy order ahead of it.
-So he would simply create his \textit{buy} of 1000 Ether and include it within a block and now he mines the previous \textit{buy} transaction of 1000 Ether.
-Doing so, he would receive a better rate than other Bancor user, can sell the tokens he has received and gain a price advantage at the expense of others.
-Similarly, a dishonest miner can sell his tokens in front, if he sees a pending \textit{sell} transaction.
-%
-%
-%\item {\textbf{Non-miner front-running.}} Researchers have also shown that a regular non-miner user can also front-run Bancor.
-In order for the Bancor transactions to be executed on the Ethereum Virtual Machine (EVM),  users have to pay for the computations in small amount of Ether called \textit{gas}~\cite{AccountT67:online}.
-The price that users pay for transactions (a.k.a.
-transaction fees) can increase or decrease how quickly they are executed and included within the blocks by the miners.
-This is because the Ethereum miners consume resources to process the transactions and so receive the transaction fees after creating the blocks.
-Once seeing two identical transactions with different transaction fees, profit maximizers miners are free to mine select the transaction which offers the highest fee.
-Therefore, any regular non-miner users who run a full-node Ethereum client can modify the order of pending transactions by paying a more amount of gas \ie by monitoring the network, upon seeing a  pending \textit{buy} transaction which will further increase the price of the asset, a font-runner user can pay a higher gas price and send his transaction a head of that.
-By doing so, he achieves a better rate from any other Bancor users.
-%
-%\end{itemize}
 
@@
 %TODO: also talk about ENS
+
+%TODO: ian goberg: private information retrieval .
+talk about domain name frontrunning in the traditional sense and how goDaddy can steal the domain when queried for availablity.
+however in blockchain the queiry is private and does not reveal the intention that you want to buy the domain.
+View only / solidity code on how to enable this
+
+\subsection{Crypto-Collectibles auctions} \hfill\\ 
+Crypto-Collectibles, also known as ERC-721 Non-Fungible Token Standard~\cite{erc721} , are one of the applications of Ethereum blockchain.
+Cryptokitties is known to be the most popular applications of ERC721 tokens~\cite{cryptokitties}.
+The main usage of these Cryptokitties is that users can breed them with each other and make new unique Cryptokitties, also they can buy or sell them through their main interface\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}}.
+See Figure~\ref{cryptokittie}.
+To buy a cryptokitty, user sends a bid transaction \textit{bid(uint256 \_tokenId)} containing the cryptokittties ID which can be found either on their website or on the ERC721 token smart contract.
+This transaction is visible from any other Ethereum node and could be easily front-run by sending the same transaction with higher gasPrice.
+%TODO: this needs a rewrite. 
+% https://etherscan.io/tx/0x62a76b7e345e8abd463487d0348c118a9314b197024e090fee7b1fbce434da40
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.4\linewidth]{figures/cryptokittie842912.png}
+\caption{ Cryptokitty Number 842912 \label{fig:cryptokittie}}
+\end{figure}
 

### 2018-09-04 frontrunning/Latex/sections/paper.tex
[frontrunning] ENS and cryptokitties

@@
 In this case, front-runners would monitor and identify domain names of interest, and sell it back to the other users with a higher price~\cite{sac022en33:online}.
-% PoC of front-running ghazal
-%TODO: also talk about ENS
 
+%Some edits required here!
+
+Ethereum Naming Service (ENS)\footnote{\url{https://ens.domains/}}, the most popular decentral naming service uses a sealed auction to purchase new domains with \textit{.eth} extension which can be resolved using any Ethereum web3 compatible browser.
+Although the implementation uses a sealed auction, the deposit should be equal or bigger than the bid, this information leakage could be used to front-run the transaction with the same bid amount.
+By doing so the front-runner invalidates the original bid.
+%e.g: https://etherscan.io/enslookup?q=handshaker.eth
 %TODO: ian goberg: private information retrieval .
@@
 View only / solidity code on how to enable this
+
+% PoC of front-running ghazal
 
@@
 To buy a cryptokitty, user sends a bid transaction \textit{bid(uint256 \_tokenId)} containing the cryptokittties ID which can be found either on their website or on the ERC721 token smart contract.
-This transaction is visible from any other Ethereum node and could be easily front-run by sending the same transaction with higher gasPrice.
+This is similar to open auctions and everyone can see the bid value and what is the bid for, this transaction is visible from any other Ethereum node and could be easily front-run by sending the same transaction with higher gasPrice.
 %TODO: this needs a rewrite. 

### 2018-09-04 frontrunning/Latex/sections/paper.tex
[frontrunning] Evidence for frontrunning on blockchain, table of top Dapps, some on localethereum

@@
 
-\subsection{Historical evidence in the Blockchain}  % JEREMY's COMMENT:  try to sell it in a way that that the audience know that there are 1000 of the applications prone to the frontrunning but we picked 3 because they are different.
+\subsection{Evidence of Front-running on the Blockchain}
 
 As blockchain records are immutably recorded, there is enough historical data to analyze for possible front running detection.
-For examples here we research some of the events of such attacks happening in the Ethereum blockchain applications.
+There is no perfect criteria to list top DApps on Ethereum blockchain, for the purpose of this research we analyzed the top 25 DApps based on recent user activities\footnote{List of decentralized applications \url{https://dappradar.com/dapps}}.
 
-%TODO: talk about why these three.
-just for emprical /theorical examples, there are tons of examples of front-running, here's three that we chose that are way different.
-one is emprical that we had to build tools to
+%TODO: fix the table! 
+\input{setup/table}
+
+From these DApps we looked at one example per category, most of which had front-running issues, some more severe than the other.
+Although none of these DApps are ICO smart contracts, we believe with the number of ICOs done on Ethereum it is worth to mention one instance of front-running on these applications as well.
 
@@
 Ethereum Naming Service (ENS)\footnote{\url{https://ens.domains/}}, the most popular decentral naming service uses a sealed auction to purchase new domains with \textit{.eth} extension which can be resolved using any Ethereum web3 compatible browser.
-Although the implementation uses a sealed auction, the deposit should be equal or bigger than the bid, this information leakage could be used to front-run the transaction with the same bid amount.
+Although the implementation uses a sealed auction, \textit{startAuctionsAndBid}, the deposit should be equal or bigger than the bid, this information leakage could be used to front-run the transaction with the same bid amount.
 By doing so the front-runner invalidates the original bid.
@@
 
+Going back to table~\ref{tab:top25dapps}, some DApps facilitate different methods to mitigate frontrunning issues.
+As an example LocalEthereum, a escrow-based exchange, uses challenge random values from the website to be included in the signature of the transaction (See ~\ref{code:localethereum}), hence removing any possibility of replay attack or possibility of any other address sending the similar order.
+
+\begin{lstlisting}[basicstyle=\scriptsize\ttfamily,caption={Code snippet from LocalEthereum smart contract.
+Values V,R and S are set by LocalEtherem to have a valid signature, also the tradeHash uses buyer and seller addresses, mitigating the possibility of front-running by a third party.},label={code:localethereum},float]
+    function createEscrow(bytes16 _tradeID, address _seller, address _buyer, uint256 _value, uint16 _fee,
+					uint32 _paymentWindowInSeconds, uint32 _expiry, uint8 _v, bytes32 _r, bytes32 _s) 
+        payable external {
+        bytes32 _tradeHash = keccak256(abi.encodePacked(_tradeID, _seller, _buyer, _value, _fee));
+	...
+        // A signature (v, r and s) must come from localethereum to open an escrow
+        bytes32 _invitationHash = keccak256(abi.encodePacked(
+            _tradeHash,
+            _paymentWindowInSeconds,
+            _expiry
+        )); 
+\end{lstlisting}
+
 %Proof of burn methods ? 

### 2018-09-04 frontrunning/Latex/setup/table.tex
[frontrunning] Evidence for frontrunning on blockchain, table of top Dapps, some on localethereum

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}

%TODO: fix the table !

\begin{table}[]
\begin{tabular}{@{}cl@{}}
\toprule
\textbf{DApp Category}                                                                               & \multicolumn{1}{c}{\textbf{DApp Names (Rank)}}                                                                                                                                                                                                                          \\ \midrule
\multicolumn{1}{|c|}{Exchanges}                                                                      & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}- IDEX (1)\\ - \textbf{ForkDelta, EtherDelta (2)}\\ - \textbf{Bancor (7)}\\ - The Token Store(13)\\ - LocalEthereum(14)\\ - Kyber (22)\end{tabular}}                                                                                       \\ \midrule
\multicolumn{1}{|c|}{\begin{tabular}[c]{@{}c@{}}Games, CryptoCollectibles \\ (ERC 721)\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}- \textbf{CryptoKitties (3)}\\ - Ethermon(4)\\ - Cryptogirl (9) \\ - Gods Unchained TCG (12) \\ - Blockchain Cuties(15) \\ - ETH.TOWN! (16) \\ - 0xUniverse (18) \\ - MLBCrypto Baseball (19) \\ - HyperDragons(25)\end{tabular}} \\ \midrule
\multicolumn{1}{|c|}{Gambling}                                                                       & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}- Fomo3D (5)\\ - DailyDivs (6)\\ - FomoWar (10)\\ - FairDapp (11)\\ - Zethr(17)\\ - dice2.win (20)\end{tabular}}                                                                                                         \\ \midrule
\multicolumn{1}{|c|}{High-Risk (Ponzi Schemes and Lotteries)}                                        & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}- PoWH 3D (8)\\ - Ether Shrimp Farm(21)\end{tabular}}                                                                                                                                                                    \\ \midrule
Misc                                                                                                 & \begin{tabular}[c]{@{}l@{}}- 0x Protocol (23)\\ - \textbf{Ethereum Name Service} (24)\end{tabular}                                                                                                                                             \\ \bottomrule
\end{tabular} 
  \caption{Top 25 DApps based on recent user activity from Dappradar.com}         \label{tab:top25dapps}                        
\end{table}

### 2018-09-04 frontrunning/Latex/sections/paper.tex
[frontrunning] Intro

--- 2018-09-04 frontrunning/Latex/sections/paper.tex
@@
 \section{Introduction}
+The history of the \emph{front-running} goes back to the ancient world, where markets in financial instruments were first started.
+For a trade to take place in those times, all the parties were required to be physically available in the exchange office.
+Clearly in such scenarios front-running was possible yet not detectable as a damaging activity.
+However with the rapid advances of the technology in the last few years, trading is not happening in person anymore and a greater amount of applications, whether financial or non-financial, are now vulnerable to front-running.
+Furthermore, Blockchain technology has introduced a new form of front-running which is inherent in all of the decentral applications.
+The other two issues which orbit around the front-running, are arbitrage and censorship.
+However, the goal of this paper is to provide a complete history of the front-running issue and thus the aforemationed will remain out of the scope of this research study.
+As there has been little quantitative analysis and research of the front-running issue, whether traditional or the new ones on that happen in decentralized application, we aim to take a thorough look into the history of the front-running, systematize all the solutions that have been proposed to this issue so far, and eventually match these solutions to their suitable use cases.\footnote{A note}
 
-Have a small discussion about arbitrage and censorship just to show that they orbit around front-running.
-For the FC: \textbf{CASE STUDY} should be used in here, also in abstract, also at the end of intro section.
+%Have a small discussion about arbitrage and censorship just to show that they orbit around front-running.
+%For the FC: \textbf{CASE STUDY} should be used in here, also in abstract, also at the end of intro section.
 
@@
 \subsection{How are Blockchain Applications Vulnerable to Front-running?} %which blockchain applications?
-\label{sec:Front Running on the Blockchains}t
+\label{sec:Front Running on the Blockchains}
 

### 2018-09-04 frontrunning/Latex/setup/table.tex
[frontrunning] Top 25 Dapps Latex Table

@@
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
+% ------------------------------------------------------------------------------------------------------------------------------------------------%
+% Top 25 Dapps Table:%
 
-%TODO: fix the table !
+\begin{table}[t]
+\centering
+\begin{tabular}{|c|c|}
+\hline
+\textbf{DApp Category}    								& \textbf{DApp Names (Rank)} \\  \hline
+\multirow{6}{*}{Exchanges} 							& IDEX (1) \\ 
+												& ForkDelta, EtherDelta (2) \\
+												& \textbf{Bancor (7)} \\
+												& The Token Store(13) \\
+												& LocalEthereum(14) \\
+												& Kyber (22) \\  \hline
 
-\begin{table}[]
-\begin{tabular}{@{}cl@{}}
-\toprule
-\textbf{DApp Category}                                                                               & \multicolumn{1}{c}{\textbf{DApp Names (Rank)}}                                                                                                                                                                                                                          \\ \midrule
-\multicolumn{1}{|c|}{Exchanges}                                                                      & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}- IDEX (1)\\ - \textbf{ForkDelta, EtherDelta (2)}\\ - \textbf{Bancor (7)}\\ - The Token Store(13)\\ - LocalEthereum(14)\\ - Kyber (22)\end{tabular}}                                                                                       \\ \midrule
-\multicolumn{1}{|c|}{\begin{tabular}[c]{@{}c@{}}Games, CryptoCollectibles \\ (ERC 721)\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}- \textbf{CryptoKitties (3)}\\ - Ethermon(4)\\ - Cryptogirl (9) \\ - Gods Unchained TCG (12) \\ - Blockchain Cuties(15) \\ - ETH.TOWN!
-(16) \\ - 0xUniverse (18) \\ - MLBCrypto Baseball (19) \\ - HyperDragons(25)\end{tabular}} \\ \midrule
-\multicolumn{1}{|c|}{Gambling}                                                                       & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}- Fomo3D (5)\\ - DailyDivs (6)\\ - FomoWar (10)\\ - FairDapp (11)\\ - Zethr(17)\\ - dice2.win (20)\end{tabular}}                                                                                                         \\ \midrule
-\multicolumn{1}{|c|}{High-Risk (Ponzi Schemes and Lotteries)}                                        & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}- PoWH 3D (8)\\ - Ether Shrimp Farm(21)\end{tabular}}                                                                                                                                                                    \\ \midrule
-Misc                                                                                                 & \begin{tabular}[c]{@{}l@{}}- 0x Protocol (23)\\ - \textbf{Ethereum Name Service} (24)\end{tabular}                                                                                                                                             \\ \bottomrule
+\multirow{9}{*}{Games, CryptoCollectibles \\ (ERC 721)}		& \textbf{CryptoKitties (3)} \\  
+												& Ethermon(4)\\
+												& Cryptogirl (9)\\
+												& Gods Unchained TCG (12)\\
+												& Blockchain Cuties(15)\\
+												& ETH.TOWN! (16)\\
+												& 0xUniverse (18)\\
+												& MLBCrypto Baseball (19)\\
+												& HyperDragons(25)\\ \hline
+
+\multirow{6}{*}{Gambling}								& Fomo3D (5) \\  
+												& DailyDivs (6) \\ 
+												& FomoWar (10) \\
+												& FairDapp (11)\\
+												& Zethr(17) \\
+												& dice2.win (20) \\
+												& Kyber (22) \\  \hline
 \end{tabular}
-  \caption{Top 25 DApps based on recent user activity from Dappradar.com}         \label{tab:top25dapps}                        
+\caption{\footnotesize{Top 25 DApps based on recent user activity from \texttt{Dappradar.com}.}\label{tab:top25dapps}}
 \end{table}
+% ------------------------------------------------------------------------------------------------------------------------------------------------%

### 2018-09-04 frontrunning/Latex/sections/paper.tex
[frontrunning] Top 25 Dapps Latex Table
[frontrunning] run on intro, other changes here and there

--- 2018-09-04 frontrunning/Latex/sections/paper.tex
@@
 \section{Introduction}
+The concept of the \emph{front-running} goes back to the decades ago when financial instrument markets first started.
+Initially the trades required to be physically available in the exchange office to deliver the bids and offers, and traders, in the knowledge of future market change, would run in front of the others to get their orders in before the change in the market to profit from the change.
+Clearly in such scenarios front-running was possible yet not detectable as a damaging activity.
+However with the rapid advances of the technology in the last few decades, trading is not happening in person anymore and a greater number of applications are now vulnerable to front-running.
+Furthermore, Blockchain technology has introduced transparency and open markets which led to a new threat of front-running and it inherently affects all decentral applications, whether financial or non-financial.
+Arbitrage and Censorship, are also issues that had been linked to front-running attacks on blockchain.
+However, the goal of this paper is to provide a complete look at the front-running issues and thus the aforementioned will remain out of the scope of this research study.
+There has been little quantitative analysis and research of the front-running issue in decentralized applications, we aim to take a thorough look into the history of the front-running, discuss multiple existing issues in the eco-system and systematize the proposed solutions, and eventually match these solutions to their suitable use cases.\footnote{A note to the reviewer, this paper falls under `Case Studies (e.g., of adoption, attacks, forks, scams, …)
+` and also mentions methods for `Fraud Detection and Financial Crime Prevention` }
 
-Have a small discussion about arbitrage and censorship just to show that they orbit around front-running.
-For the FC: \textbf{CASE STUDY} should be used in here, also in abstract, also at the end of intro section.
+%For the FC: \textbf{CASE STUDY} should be used in here, also in abstract, also at the end of intro section.
 
@@
 
-%TODO:  do this on top 10 Dapps, based on gas usage or a website.
-we wanted to look through the popular dapps but there's no such a list .
-therefor we used different examples as we could came up with.
-%maybe look into cryptokitties breed() if it is possible to front run any section
-%possible : maybe top 25 active daily usage DApps from dappradar.com
-
 \emph{Front-running} is analogous to any course of action during which a person benefits from prior access to inside or confidential market information about upcoming transactions and trades.
@@
 Have a criteria.
-
-%TODO:  do this on top 10 Dapps, based on gas usage or a website.
-we wanted to look through the popular dapps but there's no such a list .
-therefor we used different examples as we could came up with.
-%maybe look into cryptokitties breed() if it is possible to front run any section
-%possible : maybe top 25 active daily usage DApps from https://dappradar.com/dapps
 
@@
 This competition made ICOs a good opportunity for front-running attacks.
+In this paper we use multiple empirical examples to show possibility of front-running on DApps, for the sake of completeness, we use one incident on ICOs, and examples from the Top 25 DApps by recent user counts.
+%TODO: this last sentece is a bit weird here!
 

### 2018-09-04 frontrunning/Latex/setup/table.tex
[frontrunning] fix table shortstack

@@
 
-\multirow{9}{*}{Games, CryptoCollectibles \\ (ERC 721)}		& \textbf{CryptoKitties (3)} \\  
+\multirow{9}{*}{\shortstack{Games \\ CryptoCollectibles \\ (ERC 721)}}		& \textbf{CryptoKitties (3)} \\  
 												& Ethermon(4)\\

### 2018-09-04 frontrunning/Latex/sections/paper.tex
[frontrunning] Edits here and there

@@
 However, the goal of this paper is to provide a complete look at the front-running issues and thus the aforementioned will remain out of the scope of this research study.
-There has been little quantitative analysis and research of the front-running issue in decentralized applications, we aim to take a thorough look into the history of the front-running, discuss multiple existing issues in the eco-system and systematize the proposed solutions, and eventually match these solutions to their suitable use cases.\footnote{A note to the reviewer, this paper falls under `Case Studies (e.g., of adoption, attacks, forks, scams, …)
-` and also mentions methods for `Fraud Detection and Financial Crime Prevention` }
+There has been little quantitative analysis and research of the front-running issue in decentralized applications, we aim to take a thorough look into the history of the front-running, discuss multiple existing issues in the eco-system and systematize the proposed solutions, and eventually match these solutions to their suitable use cases.\footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".
+}
 
 %For the FC: \textbf{CASE STUDY} should be used in here, also in abstract, also at the end of intro section.
-
 % Why is this important.
@@
 %______________________________________________________________%
-
 %TODO: Censorship vs frontrunning ! can withholding a transaction be considered as frontrunning? 
@@
 Here we focus on the historical context and how the regulations evolved to be what they are today.\\
-Front-running was first appeared on the Chicago Board Options Exchange ( \textit{CBoE}) ~\cite{markham1988front}, and was identified by \textit{Securities Exchange Commission} in 1977 as the following:
+Front-running was first appeared on the Chicago Board Options Exchange (\textit{CBoE})~\cite{markham1988front}, and was identified by \textit{Securities Exchange Commission} in 1977 as the following:
 \begin{quote}
@@
 
-Breidenbach~\etal ~\cite{breidenbach2018enter} face the front-running issue in the context of automating bug bounties for smart contracts.
+Breidenbach~\etal~\cite{breidenbach2018enter} face the front-running issue in the context of automating bug bounties for smart contracts.
 Upon submitting the bug bounty to the Hydra smart contract, one can front-run the bug report and claim the bounty instead of the original reporter.
@@
 On the time the ICO started F2Pool constructed 31 transactions from the addresses they controlled to the ICO token sale smart contract --without broadcasting these transactions to the network-- and focused their mining power to mine their own transactions.
-As shown in figure  ~\ref{fig:Transactions_miners_while_status_ico_cut}, most of the top miners in the mentioned time frame, have mined almost the same number of failed and successful transactions which were directed toward Status.im token sale, however F2Pool's transactions indicate their successful transactions were equivalent to 10\% of the failed transactions, hence maximizing the mining rewards, on gas, while censoring other transactions to the token sale smart contract.
+As shown in Figure~\ref{fig:Transactions_miners_while_status_ico_cut}, most of the top miners in the mentioned time frame, have mined almost the same number of failed and successful transactions which were directed toward Status.im token sale, however F2Pool's transactions indicate their successful transactions were equivalent to 10\% of the failed transactions, hence maximizing the mining rewards, on gas, while censoring other transactions to the token sale smart contract.
 
@@
 Involvement of F2Pool in this action becomes obvious when the transactions from these 30 addresses are traced.
-As shown in figure ~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses where sent to Status.im ICO and mined by F2Pool.
+As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses where sent to Status.im ICO and mined by F2Pool.
 Once the dynamic ceiling algorithm refunded a portion of the sent funds back to these addresses, these funds were again sent back to F2Pool main address.
@@
 \subsection{Crypto-Collectibles auctions} \hfill\\ 
-Crypto-Collectibles, also known as ERC-721 Non-Fungible Token Standard~\cite{erc721} , are one of the applications of Ethereum blockchain.
+Crypto-Collectibles, also known as ERC-721 Non-Fungible Token Standard~\cite{erc721}, are one of the applications of Ethereum blockchain.
 Cryptokitties is known to be the most popular applications of ERC721 tokens~\cite{cryptokitties}.
@@
 See Figure~\ref{cryptokittie}.
-To buy a cryptokitty, user sends a bid transaction \textit{bid(uint256 \_tokenId)} containing the cryptokittties ID which can be found either on their website or on the ERC721 token smart contract.
+To buy a cryptokittie, user sends a bid transaction \textit{bid(uint256 \_tokenId)} containing the cryptokittties ID which can be found either on their website or on the ERC721 token smart contract.
 This is similar to open auctions and everyone can see the bid value and what is the bid for, this transaction is visible from any other Ethereum node and could be easily front-run by sending the same transaction with higher gasPrice.
@@
 In the blockchain space, the designers of the decentral applications cannot rely on the justice system for unethical behaviour, and they must assume that each participant in the network acts rationally in their own self interest, the application will be operating in an adversarial environment~\cite{0xfrontrunning:online}.
-A few decentral exchange projects such as \textit{EtherDelta} and \textit{0xProject}~\cite{warren20170x}, have proposed solutions for front-running, which is off-chain orderbooks.
+A few decentral exchange projects such as \textit{EtherDelta} and \textit{0xProject}~\cite{warren20170x}, have proposed solutions for front-running, which is off-chain order books.
 The methods discussed within these projects prevent blockchain network participants from front running the orders as the orders are private and not known to the network and will not be broadcasted.
@@
 Market participants are concerned about revealing information on their past trades, purchases, income, or liquidity needs (forget about market participants >> this leads to frontrunning)
-Shielded transactions in ZCash do not reveal the sender, receiver, the amount and the data included in the transactions, hence they cannot be seen by network participants to be front-runned.
+Shielded transactions in ZCash do not reveal the sender, receiver, the amount and the data included in the transactions, hence they cannot be seen by network participants to be front-run.
 Although this limits the functionality of the blockchain/smartcontracts/dapps
@@
 After the commitment transaction, in the reveal phase, user sends the \textit{reveal transaction} to the DApp and then after she can broadcast the Unlock transaction to unlock the funds in the commitment address.
-Finally after the ``Auction'' is over, anyone can call \textit{Finalize} function to finalize the process.
+Finally after the "Auction'' is over, anyone can call \textit{Finalize} function to finalize the process.
 \label{fig:LibSubmarine}}
@@
 
-Going back to table~\ref{tab:top25dapps}, some DApps facilitate different methods to mitigate frontrunning issues.
+Going back to Table~\ref{tab:top25dapps}, some DApps facilitate different methods to mitigate front-running issues.
 As an example LocalEthereum, a escrow-based exchange, uses challenge random values from the website to be included in the signature of the transaction (See ~\ref{code:localethereum}), hence removing any possibility of replay attack or possibility of any other address sending the similar order.

### 2018-09-04 frontrunning/Latex/sections/paper.tex
[frontrunning] Miner frontrunning Fig added

@@
 Here the miner sees the cancelation transaction and puts his own order in front of the cancellation transaction --transaction reordering-- to fill the order, potentially profiting from the order.
-They can also include the canceled transaction in their block to collect the full gas limit used by that transaction~\cite{CostofDecentralization:online}.
+They can also include the canceled transaction in their block to collect the full gas limit used by that transaction~\cite{CostofDecentralization:online}, see Figure~\ref{MinerFrontrunning}.
 Front-running can also occur in non-financial smart contracts.
@@
 %TODO: figure for miners reordering attack. it should be just two blocks with transaction inside where the second "modified" one has the orders specifically to profit the miner.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.7\linewidth]{figures/Miner_reorder_frontrun.png}
+\caption{The adversarial miner can monitor the Ethereum mempool for decentral exchange cancel orders and upon seeing the cancellation transaction, he puts his buy order before ahead.
+Doing so, the miner can profit from the underlying trade and also get the Gas included in the cancel transaction.
+\label{fig:MinerFrontrunning}}
+\end{figure}
+%https://www.lucidchart.com/invitations/accept/c8768786-4a3f-4c78-b3c8-aa04a6b81d06
 

### 2018-09-04 frontrunning/Latex/sections/paper.tex
[frontrunning] more on ENS

--- 2018-09-04 frontrunning/Latex/sections/paper.tex
@@
 By doing so the front-runner invalidates the original bid.
+This is similar to traditional domain squatting where the service provider maliciously buys the domains upon domain availably check and before the user gets the chance to finish his order.
+Although the exact same attack is not feasible on blockchain naming services as querying already registered domains are instant and without leaking any information of the intention of the user to the network.
 %e.g: https://etherscan.io/enslookup?q=handshaker.eth

### 2018-09-05 frontrunning/Latex/sections/paper.tex
[frontrunning] Notes from the meeting Sep 5

@@
 }
+
+\textbf{Note to Change the structure of the paper: to pitch this paper as a case study, we can polish it as a Bancor case study: 1) here is the bancor project that we look at 2) we find that the issue is mostly the frontrunning 3) So we take a deep look into what is frontrunning 4) we find other case studies that are vulnerable and go through each case}
 

### 2018-09-06 frontrunning/Latex/sections/paper.tex
[frontrunning] minor changes
[frontrunning] new intro

--- 2018-09-04 frontrunning/Latex/sections/paper.tex
@@
 \section{Introduction}
-The concept of the \emph{front-running} goes back to the decades ago when financial instrument markets first started.
+%The concept of the \emph{front-running} goes back to the decades ago when financial instrument markets first started.
 Initially the trades required to be physically available in the exchange office to deliver the bids and offers, and traders, in the knowledge of future market change, would run in front of the others to get their orders in before the change in the market to profit from the change.
@@
 However, the goal of this paper is to provide a complete look at the front-running issues and thus the aforementioned will remain out of the scope of this research study.
-There has been little quantitative analysis and research of the front-running issue in decentralized applications, we aim to take a thorough look into the history of the front-running, discuss multiple existing issues in the eco-system and systematize the proposed solutions, and eventually match these solutions to their suitable use cases.\footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".
+There has been little quantitative analysis and research of the front-running issue in decentralized applications, we aim to take a thorough look into the history of the front-running, discuss multiple existing issues in the eco-system and systematize the proposed solutions, and eventually match these solutions to their suitable use cases.
+\footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".
 }
+%
+%\textbf{Note to Change the structure of the paper: to pitch this paper as a case study, we can polish it as a Bancor case study: 1) here is the bancor project that we look at 2) we find that the issue is mostly the frontrunning 3) So we take a deep look into what is frontrunning 4) we find other case studies that are vulnerable and go through each case}
+
+Decentral applications are on the rise with Turing complete blockchains maturing to handle high monetary value transactions.
+Tokenization mushroomed to a whole ecosystem of tokenized applications on the blockchain, these applications inherently become a market as tokens are in the core of them.
+We started looking at some of these applications, in specific \textit{Bancor}~\cite{hertzog2017bancor}, to look into possible issues rising from these new models.
+Transparency of blockchains, although being a good feature of them, opens up these markets to some attack vectors that might not be visible on the time of the application design, one main attack is known as \textbf{front-running}, whether financial or non-financial.
+Arbitrage and Censorship, are also issues arises from the designs on the blockchain technology and had been linked to front-running attacks, hence we use the term \textit{front-running] losely to talk about any transaction manupulation with the intention of getting other transactions in before the original transaction takes place.
+In this paper, our focus is to have a complete overview of front-running on the blockchain while analysing Bancor issues.
+While looking at the possibility of front-running on other applications, we found interesting case studies that affects most of the top 25 decentral applications on Ethereum blockchain.
 
@@
 % PAPER BEING SOLD HERE
+
 %______________________________________________________________%
@@
 
+Blockchain, as a secure ledger, gives the impression of ultimate secure platform for decentral applications and one might not consider implementing the application with security in mind.
 In general, all the network participants have the ability to front-run specific transactions that are sent to the network.
@@
 
-%TODO: fix the table! 
+%TODO: fix the table!  %mahsa: add MISC back to the table! 
 \input{setup/table}

### 2018-09-06 frontrunning/Latex/sections/paper.tex
[frontrunning] rewrite the preliminaries and restructure the sections

--- 2018-09-05 frontrunning/Latex/sections/paper.tex
@@
 However, the goal of this paper is to provide a complete look at the front-running issues and thus the aforementioned will remain out of the scope of this research study.
-There has been little quantitative analysis and research of the front-running issue in decentralized applications, we aim to take a thorough look into the history of the front-running, discuss multiple existing issues in the eco-system and systematize the proposed solutions, and eventually match these solutions to their suitable use cases.\footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".
-}
+There has been little quantitative analysis and research of the front-running issue in decentralized applications, we aim to take a thorough look into the history of the front-running, discuss multiple existing issues in the eco-system and systematize the proposed solutions, and eventually match these solutions to their suitable use cases.\footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".}
 
@@
 \emph{Front-running} is analogous to any course of action during which a person benefits from prior access to inside or confidential market information about upcoming transactions and trades.
-This problem can occur in both financial and non-financial systems, however, it is more noticeable within the trading and exchange systems as it was originated back in stock markets.
+The idea of front-running was originated back in stock markets.
 In the old times, all the trades were executed on papers, so in case of receiving a large order from a client, the broker might say this loud and other people around the table could be informed.
 Therefore, a malicious trader would now run in front of that order and put his own transaction in-between (before the trade was executed) and profit from the price increase of the stock.
-In other words, a group of market participants obtain non-public market information which allows them to front-run other users trades by putting their orders a head of those trades and benefit from advance knowledge of pending client orders.
-The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty~\cite{liang2005distressed}.
-Any sort of front-running activity within the financial markets is considered as an unethical and illegal practice as it is unfairly beneficial for a few market participants who have the privilege of acting on this information and taking advantages at the expense of the investors.
+This problem occurs when a group of market participants obtain non-public market information which allows them to front-run other users trades by putting their orders a head of those trades and benefit from advance knowledge of pending client orders
+Nowadays, there are a wide range of decentral applications implemented on the blockchain.
+Built on the blockchain infrastructure, there is no trusted third party within any of the decentralized applications and there is no central version of information that is vulnerable to security attacks.
+However, due to the inherent nature of the blockchain data structure, these applications are open to what is called \emph{front-running}.
+One such application is \textbf{Bancor} -- an Ethereum-based application that allows users to exchange their tokens without any counter-party risk.
+Researchers have shown that this financial blcokchain application is open to a simple front-running attack.
+However, front-running vulnerability is not limited to the financial application and it can happen in other types of blockchain applications as well.
+
+%The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty~\cite{liang2005distressed}.
+Any sort of front-running activity wis considered as an unethical and illegal practice as it is unfairly beneficial for a few system participants who have the privilege of acting on this information and taking advantages at the expense of the investors.
 
@@
 %______________________________________________________________%
+\section{Front-running on Bancor}
+
+Bancor is an Ethereum-based application that allows users to exchange their tokens without any counter-party risk.
+This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users.
+Smart Tokens can be bought and sold through the users smart contract at an automatically calculated price which displays supply and demand.
+Doing so, Bancor protocol provides continuous liquidity for digital assets without relying on an order book as there is no requirement to match sellers and buyers.
+Recently, researchers have shown that Bancor is vulnerable to front running attacks.
+Implemented on the Ethereum blockchain, when Bancor transactions are broadcast to the network, they sit in a pending transaction pool known as \textit{mempool} waiting for the miners to mine them.
+Since Bancor handles all the trades and exchanges on the Ethereum blockchain (unlike other existing decentralized exchanges), these transactions are all visible to the public for 16s (the average Ethereum blocktime) before being included within a block.
+This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favourable profits~\cite{BancorIs7:online}.
+As mentioned in Section~\ref{sec:who can front-run?} and same as every other Ethereum based application, Bancor transactions can be front run by miners and other regular (non-miner) users.
+There is an implementation of a Bancor front running attack in the Python programming language which represent how a non-miner user can front run other network participants \cite{NewTab13:online}.
 
@@
 
-\subsection{Evidence of Front-running on the Blockchain}
+\subsection{OCase Studies}
 
@@
 %TODO: these might need more details and proofs. ask Jeremy about how to go on about this!
-
-%What is Bancor and how it can be front-run:%
-\subsection{Bancor} \hfill\\
-\noindent Bancor is an Ethereum-based application that allows users to exchange their tokens without any counter-party risk.
-This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users.
-Smart Tokens can be bought and sold through the users smart contract at an automatically calculated price which displays supply and demand.
-Doing so, Bancor protocol provides continuous liquidity for digital assets without relying on an order book as there is no requirement to match sellers and buyers.
-
-\par\noindent\textbf{Front-running Bancor} Recently, researchers have shown that Bancor is vulnerable to front running attacks.
-Implemented on the Ethereum blockchain, when Bancor transactions are broadcast to the network, they sit in a pending transaction pool known as \textit{mempool} waiting for the miners to mine them.
-Since Bancor handles all the trades and exchanges on the Ethereum blockchain (unlike other existing decentralized exchanges), these transactions are all visible to the public for 16s (the average Ethereum blocktime) before being included within a block.
-This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favourable profits~\cite{BancorIs7:online}.
-As mentioned in Section~\ref{sec:who can front-run?} and same as every other Ethereum based application, Bancor transactions can be front run by miners and other regular (non-miner) users.
-There is an implementation of a Bancor front running attack in the Python programming language which represent how a non-miner user can front run other network participants \cite{NewTab13:online}.
 

### 2018-09-06 frontrunning/Latex/sections/paper.tex

--- 2018-09-06 frontrunning/Latex/sections/paper.tex
@@
 \section{Introduction}
+
 %The concept of the \emph{front-running} goes back to the decades ago when financial instrument markets first started.

### 2018-09-06 frontrunning/Latex/sections/paper.tex
[frontrunning] Notes from the meeting

--- 2018-09-06 frontrunning/Latex/sections/paper.tex
@@
 \section{Introduction}
+
 The concept of the \emph{front-running} goes back to the decades ago when financial instrument markets first started.
@@
 However, the goal of this paper is to provide a complete look at the front-running issues and thus the aforementioned will remain out of the scope of this research study.
-There has been little quantitative analysis and research of the front-running issue in decentralized applications, we aim to take a thorough look into the history of the front-running, discuss multiple existing issues in the eco-system and systematize the proposed solutions, and eventually match these solutions to their suitable use cases.\footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".}
-
-\textbf{Note to Change the structure of the paper: to pitch this paper as a case study, we can polish it as a Bancor case study: 1) here is the bancor project that we look at 2) we find that the issue is mostly the frontrunning 3) So we take a deep look into what is frontrunning 4) we find other case studies that are vulnerable and go through each case}
+There has been little quantitative analysis and research of the front-running issue in decentralized applications, we aim to take a thorough look into the history of the front-running, discuss multiple existing issues in the eco-system and systematize the proposed solutions, and eventually match these solutions to their suitable use cases.
+\footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".
+}
 
@@
 % PAPER BEING SOLD HERE
+%\textbf{Note to Change the structure of the paper: to pitch this paper as a case study, we can polish it as a Bancor case study: 1) here is the bancor project that we look at 2) we find that the issue is mostly the frontrunning 3) So we take a deep look into what is frontrunning 4) we find other case studies that are vulnerable and go through each case}
+
+%Decentral applications are on the rise with Turing complete blockchains maturing to handle high monetary value transactions.
+Tokenization mushroomed to a whole ecosystem of tokenized applications on the blockchain, these applications inherently become a market as tokens are in the core of them.
+We started looking at some of these applications, in specific \textit{Bancor}~\cite{hertzog2017bancor}, to look into possible issues rising from these new models.
+Transparency of blockchains, although being a good feature of them, opens up these markets to some attack vectors that might not be visible on the time of the application design, one main attack is known as \textbf{front-running}, whether financial or non-financial.
+Arbitrage and Censorship, are also issues arises from the designs on the blockchain technology and had been linked to front-running attacks, hence we use the term \textit{front-running] losely to talk about any transaction manupulation with the intention of getting other transactions in before the original transaction takes place.
+In this paper, our focus is to have a complete overview of front-running on the blockchain while analysing Bancor issues.
+While looking at the possibility of front-running on other applications, we found interesting case studies that affects most of the top 25 decentral applications on Ethereum blockchain.
+
 %______________________________________________________________%
@@
 
-%TODO: fix the table! 
+%TODO: fix the table!  %mahsa: add MISC back to the table! %%%% put a seperate cell for name services and put the ENS
+% Mention that the categories were taken from that website (Dapp.com) OR recategorize categorize the table
+
 \input{setup/table}
@@
 
-\section{How to stop Front-running?}
+\section{How to stop Front-running?} %We have have the applicability of the solutions inline.
+
 In the traditional markets, front-running is considered unethical and also illegal.

### 2018-09-06 frontrunning/Latex/setup/table.tex
[frontrunning] Edits on the top 25 Dapps table
[frontrunning] Notes from the meeting

--- 2018-09-04 frontrunning/Latex/setup/table.tex
@@
 
-\multirow{9}{*}{Games, CryptoCollectibles \\ (ERC 721)}		& \textbf{CryptoKitties (3)} \\  
+\multirow{9}{*}{\shortstack{Crypto-Collectible \\ Games \\ (ERC 721)}}		& \textbf{CryptoKitties (3)} \\  
 															& Ethermon(4)\\
@@
 															& Kyber (22) \\  \hline
+
+\multirow{2}{*}{\shortstack{High-Risk \\ (Ponzi Schemes and Lotteries)}}		& PoWH 3D (8)	 \\ 
+															& Ether Shrimp Farm(21) \\  \hline
+
+\multirow{2}{*}{Misc}												& 0x Protocol (23) \\
+															& \textbf{Ethereum Name Service (24)}  \\  \hline
+
 \end{tabular}

### 2018-09-06 frontrunning/Latex/sections/paper.tex
[frontrunning] some notes

--- 2018-09-06 frontrunning/Latex/sections/paper.tex
@@
 Transparency of blockchains, although being a good feature of them, opens up these markets to some attack vectors that might not be visible on the time of the application design, one main attack is known as \textbf{front-running}, whether financial or non-financial.
-Arbitrage and Censorship, are also issues arises from the designs on the blockchain technology and had been linked to front-running attacks, hence we use the term \textit{front-running] losely to talk about any transaction manupulation with the intention of getting other transactions in before the original transaction takes place.
+Arbitrage and Censorship, are also issues arises from the designs on the blockchain technology and had been linked to front-running attacks, hence we use the term \textit{front-running} losely to talk about any transaction manupulation with the intention of getting other transactions in before the original transaction takes place.
 In this paper, our focus is to have a complete overview of front-running on the blockchain while analysing Bancor issues.
@@
 This problem occurs when a group of market participants obtain non-public market information which allows them to front-run other users trades by putting their orders a head of those trades and benefit from advance knowledge of pending client orders
-Nowadays, there are a wide range of decentral applications implemented on the blockchain.
-Built on the blockchain infrastructure, there is no trusted third party within any of the decentralized applications and there is no central version of information that is vulnerable to security attacks.
-However, due to the inherent nature of the blockchain data structure, these applications are open to what is called \emph{front-running}.
+Nowadays, there are a wide range of decentral applications implemented using blockchain technology.
+Being decentralized, there is no central version of information to be attacked, however, due to the inherent nature of the blockchain infrastructure, the data flow is transparent hence these applications are open to \emph{front-running} attacks.
 One such application is \textbf{Bancor} -- an Ethereum-based application that allows users to exchange their tokens without any counter-party risk.
-Researchers have shown that this financial blcokchain application is open to a simple front-running attack.
+Researchers have shown that this financial blockchain application is open to a simple front-running attack.
 However, front-running vulnerability is not limited to the financial application and it can happen in other types of blockchain applications as well.
@@
 There is no perfect criteria to list top DApps on Ethereum blockchain, for the purpose of this research we analyzed the top 25 DApps based on recent user activities\footnote{List of decentralized applications \url{https://dappradar.com/dapps}}.
+%ICO is only in use when the time window is happenig.  this is based on the last 24hours activities 
+%justify why started with ICO and go to other apps
 
@@
 \end{figure}
+
+% Talk about how cryptokitties are similar to any other auctions .
 
@@
 
+%TODO: inline talk about what these solutions are good for and if they fit Status ICO
+
 %______________________________________________________________%

### 2018-09-06 frontrunning/Latex/sections/paper.tex
[frontrunning] Revised the Status ICO

--- 2018-09-06 frontrunning/Latex/sections/paper.tex
@@
 %______________________________________________________________%
-\section{Front-running on Bancor}
 
-Bancor is an Ethereum-based application that allows users to exchange their tokens without any counter-party risk.
-This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users.
-Smart Tokens can be bought and sold through the users smart contract at an automatically calculated price which displays supply and demand.
-Doing so, Bancor protocol provides continuous liquidity for digital assets without relying on an order book as there is no requirement to match sellers and buyers.
-Recently, researchers have shown that Bancor is vulnerable to front running attacks.
-Implemented on the Ethereum blockchain, when Bancor transactions are broadcast to the network, they sit in a pending transaction pool known as \textit{mempool} waiting for the miners to mine them.
-Since Bancor handles all the trades and exchanges on the Ethereum blockchain (unlike other existing decentralized exchanges), these transactions are all visible to the public for 16s (the average Ethereum blocktime) before being included within a block.
-This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favourable profits~\cite{BancorIs7:online}.
-As mentioned in Section~\ref{sec:who can front-run?} and same as every other Ethereum based application, Bancor transactions can be front run by miners and other regular (non-miner) users.
-There is an implementation of a Bancor front running attack in the Python programming language which represent how a non-miner user can front run other network participants \cite{NewTab13:online}.
+\section{Status ICO} 
+As discussed in~\ref{sec:Front Running on the Blockchains}, capped ICOs are considerable applications to be investigated in terms of the front-running attacks, Status ICO is such application.
+In June 2017, Status.im~\cite{statuswhitepaper} started its ICO and reached its cap within 3 hours, resulted in close to 300,000 Ether of funding.
+In order to prevent large investments to take place early and limit the amount of Ether deposited in an investment, the team at the Status ICO used a \textit{fair} token distribution method called \textit{dynamic ceiling} as an attempt to increase the time window for smaller investors.
+They implemented multiple caps --ceiling-- which each had a maximum amount that could be deposited.
+In this case, every deposit was checked by the smart contract and the exceeding amount was refunded to the sender while the accepted amount was sent to the Status.im wallet ~\cite{statusicoanalysis}.
+
+During the time the ICO was open for participation, there were reports of Ethereum network being unusable and transactions were not confirming.
+Further study showed that some mining pools might have been manipulating the network for their own profit.
+In addition, there were many transactions sent with higher gas price to front-run other transactions, however these transactions were failed due to the restriction in the ICO smart contract to reject any transactions with higher than 50GWei gas price (as an attempt to prevent the aforementioned front-running).
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.5\linewidth]{figures/Mining_pool_ratio.png}
+\caption{The percentage of Ethereum blocks mined between block 3903900 and 3908029, this is the time frame in which Status.im ICO was running.
+This percentage roughly shows the hashing power ratio each miner had at that time.
+\label{fig:mining_pool_ratio}} % IS THIS STATEMENT CORRECT?
+\end{figure}
+
+According to the analysis we carried out, it was discovered that the F2Pool, an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure ~\ref{fig:mining_pool_ratio}), sent 100 Ether to 30 new Ethereum addresses before Status.im ICO started.
+On the time the ICO was opened for participation, F2Pool constructed 31 transactions to the ICO token sale smart contract from the addresses they controlled --without broadcasting these transactions to the network-- and used their entire mining power to mine their own transactions.
+
+As shown in Figure~\ref{fig:Transactions_miners_while_status_ico_cut}, most of the top miners in the mentioned time frame, have mined almost the same number of failed and successful transactions which were directed toward Status.im token sale, however F2Pool's transactions indicate their successful transactions were equivalent to 10\% of the failed transactions, hence maximizing the mining rewards, on gas, while censoring other transactions to the token sale smart contract.
+
+%TODO: talk about the tools made to figure this out , it's ok to use jargons and technical terms. maybe a paragraph or two on this, with interfaces and service. ethereum-etl, google bigquery, ...
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.7\linewidth]{figures/Transactions_miners_while_status_ico_cut_only_icotx.png}
+\caption{This chart shows the miners behaviour on the time window that Status.im ICO was running.
+\textit{Successful Transactions} are the transactions that led to deposit and generation of Status.im tokens and \textit{Failed Transactions} are the transactions to the token sale smart contract that failed to retrieve any tokens, for varias reasons.
+It is clear that the number of successful transactions mined by F2Pool do not follow the random homogeneous pattern of the rest of the network.
+\label{fig:Transactions_miners_while_status_ico_cut}}
+\end{figure}
+
+%TODO: make pie charts for each mining pool, all non-status-ico transactions vs success-ico-transactions vs failed-ico=transactions
+
+%TODO: describe failed/ successful transactions, what they mean!
+
+By tracing the transactions from these 30 addresses, we found a explicit Interference of the F2Pool in this scenario.
+As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses were sent to Status.im ICO and mined by F2Pool.
+Once the dynamic ceiling algorithm refunded a portion of the sent funds back to these addresses, these funds were again sent back to F2Pool main address.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.7\linewidth]{figures/F2Pool_transactions_to_StatusICO_and_Refunds.png}
+\caption{F2Pool prior to Status.im ICO deposited 100 Ether in multiple new Ethereum addresses.
+On the time of the ICO they sent these deposits to Status ICO smart contract and prioritized mining of these transactions in their mining pool, this was to overcome the dynamic ceiling algorithm of the token sale smart contract.
+Later on they sent the refunded Ether back to their own address.
+[Graph made using Blockseer.com] \label{fig:f2poolfront-run}}
+\end{figure}
+
+Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their code to behave in a certain way to front-run other transactions and take advantage of the monetary profit.
+The dataset used for this analysis can be found on our GitHub repository.\footnote{Frontrunning Status.im ICO dataset: \url{http://github.com/TODO:ANONYMOUS}}
+%TODO: these might need more details and proofs. ask Jeremy about how to go on about this!
 
@@
 
-\subsection{Status ICO} \hfill\\ 
-\noindent As discussed in ~\ref{sec:Front Running on the Blockchains}, capped ICOs are a good application for front-running attacks.
-In June 2017, Status.im~\cite{statuswhitepaper} started their ICO and within 3 hours they reached their cap, resulted in close to 300,000 Ether of funding.
-They used a \textit{fair} token distribution method called \textit{Dynamic ceiling}, which was in place to prevent large investments to take place early and limited the amount of Ether deposited, this was an attempt to increase the time window for smaller investors.
-They implemented multiple caps --ceiling-- which each would have a maximum amount that can be deposited.
-In this case every deposit would be checked by the smart contract and the exceeding amount would be refunded to the sender while the accepted amount would be sent to the Status.im wallet ~\cite{statusicoanalysis}.
-On the time of the ICO there were reports of Ethereum network being unusable and transactions were not confirming.
-Further study showed that some mining pools might have been manipulating the network for their own profit.
-On the other note, There were many transactions sent with higher gasPrice to front-run other transactions, however these transactions failed due to the restriction in place in the ICO smart contract to reject any transactions with higher than 50GWei gasPrice in an attempt to prevent this kind of front-running.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.5\linewidth]{figures/Mining_pool_ratio.png}
-\caption{The percentage of Ethereum blocks mined between block 3903900 and 3908029, this is the time frame in which Status.im ICO was running.
-This percentage roughly shows the hashing power ratio each miner had at that time.
-\label{fig:mining_pool_ratio}} % IS THIS STATEMENT CORRECT?
-\end{figure}
-
-F2Pool, an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure ~\ref{fig:mining_pool_ratio}), sent 100 Ether to 30 new Ethereum addresses before Status.im ICO started.
-On the time the ICO started F2Pool constructed 31 transactions from the addresses they controlled to the ICO token sale smart contract --without broadcasting these transactions to the network-- and focused their mining power to mine their own transactions.
-As shown in Figure~\ref{fig:Transactions_miners_while_status_ico_cut}, most of the top miners in the mentioned time frame, have mined almost the same number of failed and successful transactions which were directed toward Status.im token sale, however F2Pool's transactions indicate their successful transactions were equivalent to 10\% of the failed transactions, hence maximizing the mining rewards, on gas, while censoring other transactions to the token sale smart contract.
-
-%TODO: talk about the tools made to figure this out , it's ok to use jargons and technical terms. maybe a paragraph or two on this, with interfaces and service. ethereum-etl, google bigquery, ...
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.7\linewidth]{figures/Transactions_miners_while_status_ico_cut_only_icotx.png}
-\caption{This chart shows the miners behaviour on the time window that Status.im ICO was running.
-\textit{Successful Transactions} are the transactions that led to deposit and generation of Status.im tokens and \textit{Failed Transactions} are the transactions to the token sale smart contract that failed to retrieve any tokens, for varias reasons.
-It is clear that the number of successful transactions mined by F2Pool do not follow the random homogeneous pattern of the rest of the network.
-\label{fig:Transactions_miners_while_status_ico_cut}}
-\end{figure}
-
-%TODO: make pie charts for each mining pool, all non-status-ico transactions vs success-ico-transactions vs failed-ico=transactions
-
-%TODO: describe failed/ successful transactions, what they mean!
-
-Involvement of F2Pool in this action becomes obvious when the transactions from these 30 addresses are traced.
-As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses where sent to Status.im ICO and mined by F2Pool.
-Once the dynamic ceiling algorithm refunded a portion of the sent funds back to these addresses, these funds were again sent back to F2Pool main address.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.7\linewidth]{figures/F2Pool_transactions_to_StatusICO_and_Refunds.png}
-\caption{F2Pool prior to Status.im ICO deposited 100 Ether in multiple new Ethereum addresses.
-On the time of the ICO they sent these deposits to Status ICO smart contract and prioritized mining of these transactions in their mining pool, this was to overcome the dynamic ceiling algorithm of the token sale smart contract.
-Later on they sent the refunded Ether back to their own address.
-[Graph made using Blockseer.com] \label{fig:f2poolfront-run}}
-\end{figure}
-
-Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their code to behave in certain way to front-run other transactions and result in monetary profit.
-The dataset used for this analysis can be found on our github repository\footnote{Frontrunning Status.im ICO dataset: \url{http://github.com/TODO:ANONYMOUS}}
-%TODO: these might need more details and proofs. ask Jeremy about how to go on about this!
+\subsubsection{Bancor}
+Bancor is an Ethereum-based application that allows users to exchange their tokens without any counter-party risk.
+This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users.
+Smart Tokens can be bought and sold through the users smart contract at an automatically calculated price which displays supply and demand.
+Doing so, Bancor protocol provides continuous liquidity for digital assets without relying on an order book as there is no requirement to match sellers and buyers.
+Recently, researchers have shown that Bancor is vulnerable to front running attacks.
+Implemented on the Ethereum blockchain, when Bancor transactions are broadcast to the network, they sit in a pending transaction pool known as \textit{mempool} waiting for the miners to mine them.
+Since Bancor handles all the trades and exchanges on the Ethereum blockchain (unlike other existing decentralized exchanges), these transactions are all visible to the public for 16s (the average Ethereum blocktime) before being included within a block.
+This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favourable profits~\cite{BancorIs7:online}.
+As mentioned in Section~\ref{sec:who can front-run?} and same as every other Ethereum based application, Bancor transactions can be front run by miners and other regular (non-miner) users.
+There is an implementation of a Bancor front running attack in the Python programming language which represent how a non-miner user can front run other network participants \cite{NewTab13:online}.
 

### 2018-09-06 frontrunning/Latex/setup/table.tex
[frontrunning] update dapps table and bib

@@
 															& LocalEthereum(14) \\
+															& 0x Protocol (23) \\
 															& Kyber (22) \\  \hline
@@
 															& dice2.win (20) \\ 
-															& Kyber (22) \\  \hline
-
-\multirow{2}{*}{\shortstack{High-Risk \\ (Ponzi Schemes and Lotteries)}}		& PoWH 3D (8)	 \\ 
+															& PoWH 3D (8)	 \\ 
 															& Ether Shrimp Farm(21) \\  \hline
 
-\multirow{2}{*}{Misc}												& 0x Protocol (23) \\
+\multirow{2}{*}{Name Services}												
 															& \textbf{Ethereum Name Service (24)}  \\  \hline
@@
 \end{tabular}
-\caption{\footnotesize{Top 25 DApps based on recent user activity from \texttt{Dappradar.com}.}\label{tab:top25dapps}}
+\caption{\footnotesize{Top 25 DApps based on recent user activity from \texttt{Dappradar.com} on September 4th, 2018.}\label{tab:top25dapps}}
 \end{table}

### 2018-09-06 frontrunning/Latex/sections/paper.tex
[frontrunning] status ico tools and technicalities

@@
 
+Ethereum blockchain contains all transaction ever made on Ethereum, however, it is not easy to see the behaviour of the participants and miners solely using the default clients nor online blockchain explorers.
+In order to get the required data, Ethereum blockchain data should be converted to a queryable format.
+For this case study, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation of the Ethereum protocol\url{https://github.com/ethereum/go-ethereum}, python script for extracting, transforming and loading ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery\footnote{A fast, highly scalable, cost-effective, and fully managed cloud data warehouse for analytics \url{https://cloud.google.com/bigquery/}}.
+Using this software stack, we were able to query for all the transactions and blocks within the window of Status.im ICO for further analysis which was mainly done by data analysis tool \texttt{Tableau}\footnote{Tableau is a data visualization software that is used for data science and business intelligence.\url{https://www.tableau.com/}}.
+A copy of this dataset and the findings can be found in \texttt{github.com / ANONYMOUS}.
+
 As shown in Figure~\ref{fig:Transactions_miners_while_status_ico_cut}, most of the top miners in the mentioned time frame, have mined almost the same number of failed and successful transactions which were directed toward Status.im token sale, however F2Pool's transactions indicate their successful transactions were equivalent to 10\% of the failed transactions, hence maximizing the mining rewards, on gas, while censoring other transactions to the token sale smart contract.
-
-%TODO: talk about the tools made to figure this out , it's ok to use jargons and technical terms. maybe a paragraph or two on this, with interfaces and service. ethereum-etl, google bigquery, ...
 
@@
 The dataset used for this analysis can be found on our GitHub repository.\footnote{Frontrunning Status.im ICO dataset: \url{http://github.com/TODO:ANONYMOUS}}
-%TODO: these might need more details and proofs. ask Jeremy about how to go on about this!
 
@@
 
-\subsection{OCase Studies}
+\subsection{Case Studies}
 

### 2018-09-07 frontrunning/Latex/sections/paper.tex
[frontrunning] On crypto-collectibles

@@
 % !TEX root = ../main.tex
-
+%______________________________________________________________%
 \section{Introduction}
@@
 
+%______________________________________________________________%
 \section{Preliminaries}
@@
 %___________________________________________________________%
-
 \section{Related Work}
@@
 In order to get the required data, Ethereum blockchain data should be converted to a queryable format.
-For this case study, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation of the Ethereum protocol\url{https://github.com/ethereum/go-ethereum}, python script for extracting, transforming and loading ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery\footnote{A fast, highly scalable, cost-effective, and fully managed cloud data warehouse for analytics \url{https://cloud.google.com/bigquery/}}.
+For this case study, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation of the Ethereum protocol\url{https://github.com/ethereum/go-ethereum}}, python script for extracting, transforming and loading ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery\footnote{A fast, highly scalable, cost-effective, and fully managed cloud data warehouse for analytics \url{https://cloud.google.com/bigquery/}}.
 Using this software stack, we were able to query for all the transactions and blocks within the window of Status.im ICO for further analysis which was mainly done by data analysis tool \texttt{Tableau}\footnote{Tableau is a data visualization software that is used for data science and business intelligence.\url{https://www.tableau.com/}}.
@@
 Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their code to behave in a certain way to front-run other transactions and take advantage of the monetary profit.
-The dataset used for this analysis can be found on our GitHub repository.\footnote{Frontrunning Status.im ICO dataset: \url{http://github.com/TODO:ANONYMOUS}}
+The dataset used for this analysis can be found on our GitHub repository.\footnote{Frontrunning Status.im ICO dataset: \url{http://github.com/TODO:ANONYMOUS}}.
+This analysis made us wonder, how many other DApps are vulnerable to front-running attack, who can front-run and what are the mitigation methods for decentral applications?
+
+As the result of this analysis, we discovered a wide range of blockchain front-running case studies that are yet to investigated.
+Therefore, in the next sections we dive deeper into blockchain specific front-running details and analyze top recent DApps for front-running attack vectors and possible solutions proposed to mitigate these issues.
 
@@
 Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this is known as \textbf{transaction reordering} attack.
-For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token, i.e.
-TKN, presumably if this transaction goes through, it causes the price of the purchased token to increase.
+For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token\ie TKN, presumably if this transaction goes through, it causes the price of the purchased token to increase.
 So the dishonest miner can step in front of this transaction and place his own buy order ahead.
@@
 
-%Some edits required here!
+%Some edits required here! @mahsa TODO
 
@@
 
-\subsection{Crypto-Collectibles auctions} \hfill\\ 
+%______________________________________________________________%
+\subsection{Crypto-Collectibles Games} \hfill\\
+
+%TODO: shayan: connect games to cryptokitties and other collectibles
+
 Crypto-Collectibles, also known as ERC-721 Non-Fungible Token Standard~\cite{erc721}, are one of the applications of Ethereum blockchain.
-Cryptokitties is known to be the most popular applications of ERC721 tokens~\cite{cryptokitties}.
-The main usage of these Cryptokitties is that users can breed them with each other and make new unique Cryptokitties, also they can buy or sell them through their main interface\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}}.
-See Figure~\ref{cryptokittie}.
+Cryptokitties is known to be one of the first and the most popular use cases of ERC721 tokens~\cite{cryptokitties}.
+Their marketcap reached more than 6 million dollars in the first months their launch.
+Crypto-Collectibles, are similar to ERC-20 tokens and can be listed on exchanges.
+Most of the front-running issues applied to the exchanges also apply to DApps using ERC-721 tokens.
+\\
+
+As an example Cryptokitties can be bred, bought or sold through the main interface\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}}. See Figure~\ref{cryptokittie}.
 To buy a cryptokittie, user sends a bid transaction \textit{bid(uint256 \_tokenId)} containing the cryptokittties ID which can be found either on their website or on the ERC721 token smart contract.
-This is similar to open auctions and everyone can see the bid value and what is the bid for, this transaction is visible from any other Ethereum node and could be easily front-run by sending the same transaction with higher gasPrice.
-%TODO: this needs a rewrite. 
+This is similar to open auctions, bid value and the object bidding on is visible to the network and any user could be easily front-run by sending the same transaction with higher gasPrice to replace the initial bidder.
 % https://etherscan.io/tx/0x62a76b7e345e8abd463487d0348c118a9314b197024e090fee7b1fbce434da40
@@
 
-% Talk about how cryptokitties are similar to any other auctions .
+%______________________________________________________________%
+
+%TODO: Shayan: Frontrunning on one of the gambling DAPPS from the table
 
 %______________________________________________________________%
-
 \section{How to stop Front-running?} %We have have the applicability of the solutions inline.
@@
 \emph{Traditional Front-running Prevention Methods}. regulations/enforcement/broker education/sealed order
-%@shayan: ^
+%@shayan: ^ TODO!
 
@@
 There are two main approaches to prevent front running, one to design a blockchain that is front-run resistant , and the other to design the application logics in a way that front running is not possible.
+%@shayan: ^ TODO!
 
+%______________________________________________________________%
 \subsection{Front-run Resistant Blockchain}
@@
 
+%@shayan TODO
+
 %NEEDS TO BE DONE:
@@
 Talk about this possible solution
+%MAHSA TODO
+%https://medium.com/loopring-protocol/dual-authoring-looprings-solution-to-front-running-d0fc9c348ef1
+% https://raw.githubusercontent.com/Loopring/whitepaper/master/en_whitepaper.pdf
 
@@
 
+%______________________________________________________________%
 \subsection{Application Design to Prevent Front-running}
@@
 %______________________________________________________________%
-
 \section{Concluding Remarks}

### 2018-09-07 frontrunning/Latex/sections/paper.tex
[frontrunning] cleaning the traditional front-running

@@
 
-% talk about the AMF frontrunning.
-
 As traditional frontrunning has been the subject of discussion for decades, there are many literatures on this subject.
@@
 
-%In actuality, front-running is more complex than this definition suggests.
-It encompasses at least three forms of conduct, each of which raises different regulatory and policy issues.9 They are: (1) trading by third parties who are tipped on an impending block trade ("tippee" trading); (2) transactions in which the owner or purchaser of the block trade itself engages in the offset- ting futures or options transaction as a means of "hedging" against price fluctuations caused by the block transaction ("self-front-running"); 1 ° and (3) transactions where a broker with knowledge of an impending customer block order trades ahead of that order for the broker's own profit ("trading ahead").
-% from JerryWMarkhamfront-running.pdf
-
-% More to read and add from : SECURITIES AND EXCHANGE COMMISSION Release No. 34-67079. pdf included in Related_Documents
+% More to read:  SECURITIES AND EXCHANGE COMMISSION Release No. 34-67079. pdf included in Related_Documents
 % https://www.sec.gov/about/annual_report/1988.pdf
@@
 \begin{quote}
-It seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge.
+It seems evident that such behavior on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge.
 \footnote{Securities Exchange Act Release No.
@@
 As defining what exactly is considered illegal front-running required more knowledge of how these new markets behave, \textit{CBoE} and other exchanges (and brokers) issued educational circulars for their members asserting that front-running violates existing rules, with some examples of what is considered front-running.
-However difference of opinion regarding the unfairness o front running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~cite{sec1978optionsmarket}.
+However difference of opinion regarding the unfairness of front running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~cite{sec1978optionsmarket}.
 
-Further reading on the early details on the history and challenges of detecting and regulating front-running can be found in~\cite{markham1988front} .
-% TODO: add a more recent publication here as well!
+Further reading on the early details on the history and challenges of detecting and regulating front-running can be found in~\cite{markham1988front} . %add a more recent publication here as well!
 

### 2018-09-07 frontrunning/Latex/sections/paper.tex
[frontrunning] Privacy preserving blockchains

@@
 
-%@shayan TODO
-
-%NEEDS TO BE DONE:
-Market participants are concerned about revealing information on their past trades, purchases, income, or liquidity needs (forget about market participants >> this leads to frontrunning)
-Shielded transactions in ZCash do not reveal the sender, receiver, the amount and the data included in the transactions, hence they cannot be seen by network participants to be front-run.
-Although this limits the functionality of the blockchain/smartcontracts/dapps
+Market participants are concerned about revealing information on their past trades, purchases, income, or liquidity needs.
+Privacy is a basic human right, that being said, there are limitations with the functionality of a system designed to preserve full privacy.
+However other than past transactions, real time transactions could leak informations about the sender or the intention of the order that could lead to front-running attacks.
+Privacy preserving blockchains try to solve the initial issue by keeping all the details of the transactions private, in some extent~\cite{miller2017empirical, kappos2018empirical}.
+As an example, ZCash~\cite{hopwood2016zcash}, uses two distinct type of addresses, transparent addresses and shielded addresses.
+Transparent addresses work similar to Bitcoin transactions, fully transparent about the sender and receiver addresses, the amount and included data.
+However shielded addresses are private and do not leak any information, this is great for privacy but not good for smart contracts capabilities.
+Smart contract functionality requires verification by the miners which require to know the input, functionality and output of smart contracts to be able to determine if the transaction is valid.
+Albeit by using cryptographic primitives such as zero-knowledge proofs this issue could also be resolved~\cite{kosba2016hawk}.
 

### 2018-09-07 frontrunning/Latex/sections/paper.tex
[frontrunning] Exchanges and some more

@@
 
-\subsubsection{Miners}
+\subsubsection{Miners} \labe{minersfrontrunning}
 Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this is known as \textbf{transaction reordering} attack.
@@
 \subsection{Case Studies}  
+As blockchain records are immutably recorded, there is enough historical data to analyze for possible front-running detection.There is no perfect criteria to list top DApps on Ethereum blockchain, for the purpose of this research we analyzed the top 25 DApps based on recent user activities\footnote{List of decentralized applications \url{https://dappradar.com/dapps}} in the first week of September 2018.
 
-As blockchain records are immutably recorded, there is enough historical data to analyze for possible front running detection.
-There is no perfect criteria to list top DApps on Ethereum blockchain, for the purpose of this research we analyzed the top 25 DApps based on recent user activities\footnote{List of decentralized applications \url{https://dappradar.com/dapps}}.
 %ICO is only in use when the time window is happenig.  this is based on the last 24hours activities 
 %justify why started with ICO and go to other apps
-
-%TODO: fix the table!  %mahsa: add MISC back to the table! %%%% put a seperate cell for name services and put the ENS
-% Mention that the categories were taken from that website (Dapp.com) OR recategorize categorize the table
 
@@
 
-\subsubsection{Bancor}
+\subsubsection{Exchanges}
+Exchanges such as EtherDelta\footnote{also known as ForkDelta for the UI \url{https://forkdelta.app/}}, are closest form to decentral exchanges, however their orderbooks are stored on a central server they control and shown on their user interface (website).
+Other than the fact that they can re-order or censor the orders on their servers, there are other risks of front-running nature in these designs.
+Similarly 0xProtocol uses \textit{Relayers} which act as the orderbook holders and are not prune to cheating.
+One main issue with these exchanges is \textit{cancellation grief}.
+Although the orderbooks are not in the smart contract, in order to prevent denial of service attacks, user needs to send a transaction to cancel her order.
+In this case, when an adversarial actor sees the cancellation transaction, he sends a fill order transactions with higher gasPrice to get in front of the cancellation order and take the order before it is cancelled.
+As mentioned in ~\ref{minersfrontrunning}, miners are in a better control to perform such attack.
+
+% can we talk about Velocity here? ~\cite{eskandari2017feasibility}
+
+%\subsubsection{Bancor} %TODO: mahsa 
 Bancor is an Ethereum-based application that allows users to exchange their tokens without any counter-party risk.
@@
 However, if the application is designed in a way that the fees of the orders are sent to the miner of the block, he would have no incentive to front-run the orders as he already gains enough financial benefit from acting fairly and executing the transactions on their correct order.
-
-%TODO: maybe remove this 
-%\noindent\emph{Eliminating Price Dynamics:} In the context of decentralized exchanges where orderly and fair execution of the orders (transactions) cannot be guaranteed,  another solution is to replace the order book with the \emph{limit order book}.
-In such design, orders are not executed automatically and an auction process helps the users to choose the orders they want to execute against.
-By doing so, even if the orders are front-run by other users or miners, there would be no price improvement and financial benefits as the orders are limited.
-
-Note that depending on the applications plans, there might exist design decisions which cause the system to be front-run resistant.
 For example, Malinova~\cite{Malinova} proposes a design for a decentral exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable.
 
+% one solution could be to remove multiple actors, meaning that on each "play" (order), the smart contract would be the market maker.
+it does not matter if there are multiple similar orders.
+similar to PoC of Velocity~\cite{eskandari2017feasibility}.
+Although there are other concerns about this specific design but not for front-running.
+
 Going back to Table~\ref{tab:top25dapps}, some DApps facilitate different methods to mitigate front-running issues.
-As an example LocalEthereum, a escrow-based exchange, uses challenge random values from the website to be included in the signature of the transaction (See ~\ref{code:localethereum}), hence removing any possibility of replay attack or possibility of any other address sending the similar order.
+As an example LocalEthereum, an escrow-based exchange, uses challenge random values from the website to be included in the signature of the transaction (See ~\ref{code:localethereum}), hence removing any possibility of replay attack or possibility of any other address sending the similar order.
 

### 2018-09-07 frontrunning/Latex/setup/table.tex
[frontrunning] Exchanges and some more

@@
 \multirow{6}{*}{Exchanges} 										& IDEX (1) \\ 
-															& ForkDelta, EtherDelta (2) \\
-															& \textbf{Bancor (7)} \\
+															& \textit{ForkDelta, EtherDelta (2)} \\
+															& \textit{Bancor (7)} \\
 															& The Token Store(13) \\
@@
 
-\multirow{9}{*}{\shortstack{Crypto-Collectible \\ Games \\ (ERC 721)}}		& \textbf{CryptoKitties (3)} \\  
+\multirow{9}{*}{\shortstack{Crypto-Collectible \\ Games \\ (ERC 721)}}		& \textit{CryptoKitties (3)} \\  
 															& Ethermon(4)\\
@@
 \multirow{2}{*}{Name Services}												
-															& \textbf{Ethereum Name Service (24)}  \\  \hline
+															& \textit{Ethereum Name Service (24)}  \\  \hline
 

### 2018-09-07 frontrunning/Latex/sections/paper.tex
[frontrunning] drawbacks of commitment schemes + libsubmarine and some other fixes

@@
 While looking at the possibility of front-running on other applications, we found interesting case studies that affects most of the top 25 decentral applications on Ethereum blockchain.
-
-%______________________________________________________________%
-%TODO: Censorship vs frontrunning ! can withholding a transaction be considered as frontrunning? 
-%using frontrunning losely, we do not want to defining what exactly front running is, but talking about possibiities of attacks in this nature and also how to prevent these from happening .
 
@@
 
+%______________________________________________________________%
+
 \section{On Blockchain Front-running}
@@
 
-\subsubsection{Miners} \labe{minersfrontrunning}
+\subsubsection{Miners} \label{minersfrontrunning}
 Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this is known as \textbf{transaction reordering} attack.
@@
 
-%TODO: figure for miners reordering attack. it should be just two blocks with transaction inside where the second "modified" one has the orders specifically to profit the miner.
-
 \begin{figure}[h]
@@
 %https://www.lucidchart.com/invitations/accept/c8768786-4a3f-4c78-b3c8-aa04a6b81d06
+
+%______________________________________________________________%
 
@@
 Since Bancor handles all the trades and exchanges on the Ethereum blockchain (unlike other existing decentralized exchanges), these transactions are all visible to the public for 16s (the average Ethereum blocktime) before being included within a block.
-This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favourable profits~\cite{BancorIs7:online}.
+This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favorable profits~\cite{BancorIs7:online}.
 As mentioned in Section~\ref{sec:who can front-run?} and same as every other Ethereum based application, Bancor transactions can be front run by miners and other regular (non-miner) users.
@@
 
-\noindent As mentioned in Section~\ref{sec:Front Running on the Blockchains}, although front-running attacks have been more showcased in the context of decentralized exchanges and trading systems, they are are not yet limited to the financial markets.
+\noindent As mentioned in Section~\ref{sec:Front Running on the Blockchains}, although front-running attacks have been more showcased in the context of decentralized exchanges and trading systems, they are not yet limited to the financial markets.
 Front-running can occur within other (non-financial) blockchain applications such as naming systems.
@@
 
-% PoC of front-running ghazal
-
 %______________________________________________________________%
 \subsection{Crypto-Collectibles Games} \hfill\\
-
-%TODO: shayan: connect games to cryptokitties and other collectibles
 
@@
 
+%Possibly remove this figure due to page limit
 \begin{figure}[h]
@@
 
-% TODO: also talk about drawbacks, more expensinve, more transactions, UX, forget to reveal.
-
-\subsubsection{Design Decision \#1: Commitment Scheme\newline} %talk about the drawbacks of this scheme: eg: you may forget to reveal. 
+\subsubsection{Design Decision \#1: Commitment Scheme\newline} \label{CommitmentScheme} %talk about the drawbacks of this scheme: eg: you may forget to reveal. 
 Commitment scheme is a cryptographic primitive that enables one to commit to a value --binding-- (\eg statement, document, data, \etc) while keeping it a secret and reveal the committed value on a later time~\cite{brassard1988minimum}.
@@
 Both these issues, albeit hiding the details of the order and preventing direct front-running, leak information to other participants which could lead to more sophisticated front-running attacks depending on the application design.
+On the other note, these method has some drawbacks, the user experience is not smooth and one might forget to reveal the committed transaction.
+In ENS commit-reveal process, if one forgets to reveal on the reveal phase, the committed funds are burnt and inaccessible there after.
+Also this scheme means two transaction are required for a functionality which is makes it more expensive to run.
 
@@
 By constructing a transaction from that address to the DApp and funding that address we fulfil the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}, see Figure~\ref{fig:LibSubmarine}.
+Drawbacks of this scheme are similar to ~\ref{CommitmentScheme}, with an addition of two more transactions to finalize the functionality, which results in more cost and complicated user experience.
 
@@
 
+%Possibly remove this code snippet due to page limit
 \begin{lstlisting}[basicstyle=\scriptsize\ttfamily,caption={Code snippet from LocalEthereum smart contract.

### 2018-09-07 frontrunning/Latex/sections/paper.tex
[frontrunning] some notes

--- 2018-09-07 frontrunning/Latex/sections/paper.tex
@@
 % !TEX root = ../main.tex
-%______________________________________________________________%
+
 \section{Introduction}
@@
 
-%______________________________________________________________%
 \section{Preliminaries}
@@
 \emph{Front-running} is analogous to any course of action during which a person benefits from prior access to inside or confidential market information about upcoming transactions and trades.
-The idea of front-running was originated back in stock markets.
+This problem can occur in both financial and non-financial systems, however, it is more noticeable within the trading and exchange systems as it was originated back in stock markets.
 In the old times, all the trades were executed on papers, so in case of receiving a large order from a client, the broker might say this loud and other people around the table could be informed.
 Therefore, a malicious trader would now run in front of that order and put his own transaction in-between (before the trade was executed) and profit from the price increase of the stock.
-This problem occurs when a group of market participants obtain non-public market information which allows them to front-run other users trades by putting their orders a head of those trades and benefit from advance knowledge of pending client orders
-Nowadays, there are a wide range of decentral applications implemented using blockchain technology.
-Being decentralized, there is no central version of information to be attacked, however, due to the inherent nature of the blockchain infrastructure, the data flow is transparent hence these applications are open to \emph{front-running} attacks.
-One such application is \textbf{Bancor} -- an Ethereum-based application that allows users to exchange their tokens without any counter-party risk.
-Researchers have shown that this financial blockchain application is open to a simple front-running attack.
-However, front-running vulnerability is not limited to the financial application and it can happen in other types of blockchain applications as well.
+In other words, a group of market participants obtain non-public market information which allows them to front-run other users trades by putting their orders a head of those trades and benefit from advance knowledge of pending client orders.
+The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty~\cite{liang2005distressed}.
+Any sort of front-running activity within the financial markets is considered as an unethical and illegal practice as it is unfairly beneficial for a few market participants who have the privilege of acting on this information and taking advantages at the expense of the investors.
 
@@
 %___________________________________________________________%
+
 \section{Related Work}
@@
 \subsection{Literature on Traditional Front-running}
+
+% talk about the AMF frontrunning.
 
@@
 
-% More to read:  SECURITIES AND EXCHANGE COMMISSION Release No. 34-67079. pdf included in Related_Documents
+%In actuality, front-running is more complex than this definition suggests.
+It encompasses at least three forms of conduct, each of which raises different regulatory and policy issues.9 They are: (1) trading by third parties who are tipped on an impending block trade ("tippee" trading); (2) transactions in which the owner or purchaser of the block trade itself engages in the offset- ting futures or options transaction as a means of "hedging" against price fluctuations caused by the block transaction ("self-front-running"); 1 ° and (3) transactions where a broker with knowledge of an impending customer block order trades ahead of that order for the broker's own profit ("trading ahead").
+% from JerryWMarkhamfront-running.pdf
+
+% More to read and add from : SECURITIES AND EXCHANGE COMMISSION Release No. 34-67079. pdf included in Related_Documents
 % https://www.sec.gov/about/annual_report/1988.pdf
@@
 \begin{quote}
-It seems evident that such behavior on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge.
+It seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge.
 \footnote{Securities Exchange Act Release No.
@@
 As defining what exactly is considered illegal front-running required more knowledge of how these new markets behave, \textit{CBoE} and other exchanges (and brokers) issued educational circulars for their members asserting that front-running violates existing rules, with some examples of what is considered front-running.
-However difference of opinion regarding the unfairness of front running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~cite{sec1978optionsmarket}.
+However difference of opinion regarding the unfairness o front running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~cite{sec1978optionsmarket}.
 
-Further reading on the early details on the history and challenges of detecting and regulating front-running can be found in~\cite{markham1988front} . %add a more recent publication here as well!
+Further reading on the early details on the history and challenges of detecting and regulating front-running can be found in~\cite{markham1988front} .
+% TODO: add a more recent publication here as well!
 
@@
 
-Ethereum blockchain contains all transaction ever made on Ethereum, however, it is not easy to see the behaviour of the participants and miners solely using the default clients nor online blockchain explorers.
-In order to get the required data, Ethereum blockchain data should be converted to a queryable format.
-For this case study, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation of the Ethereum protocol\url{https://github.com/ethereum/go-ethereum}}, python script for extracting, transforming and loading ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery\footnote{A fast, highly scalable, cost-effective, and fully managed cloud data warehouse for analytics \url{https://cloud.google.com/bigquery/}}.
-Using this software stack, we were able to query for all the transactions and blocks within the window of Status.im ICO for further analysis which was mainly done by data analysis tool \texttt{Tableau}\footnote{Tableau is a data visualization software that is used for data science and business intelligence.\url{https://www.tableau.com/}}.
-A copy of this dataset and the findings can be found in \texttt{github.com / ANONYMOUS}.
+As shown in Figure~\ref{fig:Transactions_miners_while_status_ico_cut}, most of the top miners in the mentioned time frame, have mined almost the same number of failed and successful transactions which were directed toward Status.im token sale, however F2Pool's transactions indicate their successful transactions were equivalent to 10\% of the failed transactions, hence maximizing the mining rewards, on gas, while censoring other transactions to the token sale smart contract.
 
-As shown in Figure~\ref{fig:Transactions_miners_while_status_ico_cut}, most of the top miners in the mentioned time frame, have mined almost the same number of failed and successful transactions which were directed toward Status.im token sale, however F2Pool's transactions indicate their successful transactions were equivalent to 10\% of the failed transactions, hence maximizing the mining rewards, on gas, while censoring other transactions to the token sale smart contract.
+%TODO: talk about the tools made to figure this out , it's ok to use jargons and technical terms. maybe a paragraph or two on this, with interfaces and service. ethereum-etl, google bigquery, ...
 
@@
 Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their code to behave in a certain way to front-run other transactions and take advantage of the monetary profit.
-The dataset used for this analysis can be found on our GitHub repository.\footnote{Frontrunning Status.im ICO dataset: \url{http://github.com/TODO:ANONYMOUS}}.
-This analysis made us wonder, how many other DApps are vulnerable to front-running attack, who can front-run and what are the mitigation methods for decentral applications?
-
-As the result of this analysis, we discovered a wide range of blockchain front-running case studies that are yet to investigated.
-Therefore, in the next sections we dive deeper into blockchain specific front-running details and analyze top recent DApps for front-running attack vectors and possible solutions proposed to mitigate these issues.
+The dataset used for this analysis can be found on our GitHub repository.\footnote{Frontrunning Status.im ICO dataset: \url{http://github.com/TODO:ANONYMOUS}}
+%TODO: these might need more details and proofs. ask Jeremy about how to go on about this!
 
@@
 Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this is known as \textbf{transaction reordering} attack.
-For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token\ie TKN, presumably if this transaction goes through, it causes the price of the purchased token to increase.
+For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token, i.e.
+TKN, presumably if this transaction goes through, it causes the price of the purchased token to increase.
 So the dishonest miner can step in front of this transaction and place his own buy order ahead.
@@
 
-\subsection{Case Studies}
+\subsection{OCase Studies}
 
@@
 
-%Some edits required here! @mahsa TODO
+%Some edits required here!
 
@@
 
-%______________________________________________________________%
-\subsection{Crypto-Collectibles Games} \hfill\\
-
-%TODO: shayan: connect games to cryptokitties and other collectibles
-
+\subsection{Crypto-Collectibles auctions} \hfill\\ 
 Crypto-Collectibles, also known as ERC-721 Non-Fungible Token Standard~\cite{erc721}, are one of the applications of Ethereum blockchain.
-Cryptokitties is known to be one of the first and the most popular use cases of ERC721 tokens~\cite{cryptokitties}.
-Their marketcap reached more than 6 million dollars in the first months their launch.
-Crypto-Collectibles, are similar to ERC-20 tokens and can be listed on exchanges.
-Most of the front-running issues applied to the exchanges also apply to DApps using ERC-721 tokens.
-\\
-
-As an example Cryptokitties can be bred, bought or sold through the main interface\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}}. See Figure~\ref{cryptokittie}.
+Cryptokitties is known to be the most popular applications of ERC721 tokens~\cite{cryptokitties}.
+The main usage of these Cryptokitties is that users can breed them with each other and make new unique Cryptokitties, also they can buy or sell them through their main interface\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}}.
+See Figure~\ref{cryptokittie}.
 To buy a cryptokittie, user sends a bid transaction \textit{bid(uint256 \_tokenId)} containing the cryptokittties ID which can be found either on their website or on the ERC721 token smart contract.
-This is similar to open auctions, bid value and the object bidding on is visible to the network and any user could be easily front-run by sending the same transaction with higher gasPrice to replace the initial bidder.
+This is similar to open auctions and everyone can see the bid value and what is the bid for, this transaction is visible from any other Ethereum node and could be easily front-run by sending the same transaction with higher gasPrice.
+%TODO: this needs a rewrite. 
 % https://etherscan.io/tx/0x62a76b7e345e8abd463487d0348c118a9314b197024e090fee7b1fbce434da40
@@
 
+% Talk about how cryptokitties are similar to any other auctions .
+
 %______________________________________________________________%
 
-%TODO: Shayan: Frontrunning on one of the gambling DAPPS from the table
-
-%______________________________________________________________%
 \section{How to stop Front-running?} %We have have the applicability of the solutions inline.
@@
 \emph{Traditional Front-running Prevention Methods}. regulations/enforcement/broker education/sealed order
-%@shayan: ^ TODO!
+%@shayan: ^
 
@@
 There are two main approaches to prevent front running, one to design a blockchain that is front-run resistant , and the other to design the application logics in a way that front running is not possible.
-%@shayan: ^ TODO!
 
-%______________________________________________________________%
 \subsection{Front-run Resistant Blockchain}
@@
 
-Market participants are concerned about revealing information on their past trades, purchases, income, or liquidity needs.
-Privacy is a basic human right, that being said, there are limitations with the functionality of a system designed to preserve full privacy.
-However other than past transactions, real time transactions could leak informations about the sender or the intention of the order that could lead to front-running attacks.
-Privacy preserving blockchains try to solve the initial issue by keeping all the details of the transactions private, in some extent~\cite{miller2017empirical, kappos2018empirical}.
-As an example, ZCash~\cite{hopwood2016zcash}, uses two distinct type of addresses, transparent addresses and shielded addresses.
-Transparent addresses work similar to Bitcoin transactions, fully transparent about the sender and receiver addresses, the amount and included data.
-However shielded addresses are private and do not leak any information, this is great for privacy but not good for smart contracts capabilities.
-Smart contract functionality requires verification by the miners which require to know the input, functionality and output of smart contracts to be able to determine if the transaction is valid.
-Albeit by using cryptographic primitives such as zero-knowledge proofs this issue could also be resolved~\cite{kosba2016hawk}.
+%NEEDS TO BE DONE:
+Market participants are concerned about revealing information on their past trades, purchases, income, or liquidity needs (forget about market participants >> this leads to frontrunning)
+Shielded transactions in ZCash do not reveal the sender, receiver, the amount and the data included in the transactions, hence they cannot be seen by network participants to be front-run.
+Although this limits the functionality of the blockchain/smartcontracts/dapps
 
@@
 Talk about this possible solution
-%MAHSA TODO
-%https://medium.com/loopring-protocol/dual-authoring-looprings-solution-to-front-running-d0fc9c348ef1
-% https://raw.githubusercontent.com/Loopring/whitepaper/master/en_whitepaper.pdf
 
@@
 
-%______________________________________________________________%
 \subsection{Application Design to Prevent Front-running}
@@
 %______________________________________________________________%
+
 \section{Concluding Remarks}

### 2018-09-07 frontrunning/Latex/sections/paper.tex
[frontrunning] Dual authoring solution

@@
 
-\subsubsection{Design Decision \#3: Loopring/Dual Authoring\newline}
-Talk about this possible solution
-%MAHSA TODO
-%https://medium.com/loopring-protocol/dual-authoring-looprings-solution-to-front-running-d0fc9c348ef1
-% https://raw.githubusercontent.com/Loopring/whitepaper/master/en_whitepaper.pdf
+\subsubsection{Design Decision \#3: Dual Authoring\newline}
 
-%TODO: research on more proposed solutions!
+Loopring is an open protocol proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}.
+This protocol operates a hybrid model with off-chain order management and communication and merely the order matching takes place on the chain.
+Using Loopring functionality, the users do not need to host their assets on the exchange and and instead they keep their assets in their blockchain wallet.
+For example, if a user A wants to exchange \emph{token A } to \emph{token B}, she keeps \emph{token A }  safe in her wallet and the Loopring protocol automatically broadcasts the order to the network after user's authorization.
+If user B wants to exchange, there would be match making miners on the Loopring protocol who matches the orders and swaps the tokens through a smart contract.
+To solve the front-running issue within th edecentralized exchanges, Loopring protocol proposes \emph{dual-authoring} scheme.
+This solution set two levels of authorization for orders - one for settlement, and one for order matching.
+In summary, in this scheme a wallet generates a pair of public key (auth-address) and private key (auth-key) for the user, these keys are differenet from the user's address and its corresponding private key.
+Then the wallet signs all the fields of the order (except the auth-key) using the owner's private key and sends the order, together with the auth-key to miner for matching.
+The miner verifies that auth-key and auth-address are associated as well as the order's signature.
+In this stage, orders are added to various rings;
+?each ring encapsulates all the fields and data of its containing orders (a ring can have 2 to 10 orders).
+Once a ring is established, the ring miner uses each order's auth-key to sign the hash of the ring.
+He also needs to sign the hash of the ring together with the mining parameters using his own private key.
+The miner then sends all the signatures to the Loopring smart contract (LPSC).
+Eventually, the Loopring protocol verifies each signatures against their corresponding auth-key of each order and does not accept the ring if the signatures are not valid.
+Doing so, it is assured that (i) the orders are be modified (because they are signed using the owner's private key), (ii) no other miner can mine the ring (because the miner's address is signed using his private key), and no user can front-run the orders within the ring (because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them).
 

### 2018-09-07 frontrunning/Latex/sections/paper.tex
[frontrunning] Edits on dual authoring

@@
 If user B wants to exchange, there would be match making miners on the Loopring protocol who matches the orders and swaps the tokens through a smart contract.
-To solve the front-running issue within th edecentralized exchanges, Loopring protocol proposes \emph{dual-authoring} scheme.
+To solve the front-running issue within the decentralized exchanges, Loopring protocol proposes \emph{dual-authoring} scheme.
 This solution set two levels of authorization for orders - one for settlement, and one for order matching.
-In summary, in this scheme a wallet generates a pair of public key (auth-address) and private key (auth-key) for the user, these keys are differenet from the user's address and its corresponding private key.
-Then the wallet signs all the fields of the order (except the auth-key) using the owner's private key and sends the order, together with the auth-key to miner for matching.
-The miner verifies that auth-key and auth-address are associated as well as the order's signature.
+In summary, in this scheme a wallet generates a pair of public key (auth-address) and private key (auth-key) for the user, these keys are different from the user's address and its corresponding private key.
+The address of order's owner, order parameters, and the auth-address are hashed.
+The hash value, which is called the order-hashed then is signed using the owner's private key.
+The signature of the ring-hash together with the auth-key are sent to the  miner for matching.
 In this stage, orders are added to various rings;
 ?each ring encapsulates all the fields and data of its containing orders (a ring can have 2 to 10 orders).
-Once a ring is established, the ring miner uses each order's auth-key to sign the hash of the ring.
+Once a ring is established, the ring miner uses each order's auth-key to sign the hash of the ring, together with his own address, and the mining parameters.
 He also needs to sign the hash of the ring together with the mining parameters using his own private key.

### 2018-09-10 frontrunning/Latex/sections/paper.tex
[frontrunning] gambling dapp + table fix

@@
 
-%TODO: Shayan: Frontrunning on one of the gambling DAPPS from the table
+\subsection{Gambling} \hfill\\ 
+Due to deterministic nature of blockchains, running gambling games based on randomness is close to impossible.
+There had been attempts to use block headers or such as the seed to randomness but almost all have failed as every data accessible to the smart contract at the time of execution, is also accessible to other smart contracts and they could predict the output on the run.
+Thus most of the current gambling games on Ethereum, rely on the human factor and network behavior rather than pure randomness.
+Because of these many infamous gambling games are now running on Ethereum network and front-running them requires a highly sophisticated methods.\\
+One of the most popular smart contracts on Ethereum blockchain belongs to a controversial gambling game named \texttt{Fomo3d}, also known as \textit{Exit Scam}\footnote{\url{https://exitscam.me/play}}.
+The aim of this game is to be the last person purchasing the key when the time goes to zero in which every ticket purchase increases the timer by 30 seconds.
+It was believed that because of the nature of the game, it will never end, however on August 22, 2018 the first round of the game ended and the winner took 10,469 Ether\footnote{First winner of Fomo3D, won 10,469 Ether \url{ https://etherscan.io/tx/0xe08a519c03cb0aed0e04b33104112d65fa1d3a48cd3aeab65f047b2abce9d508}}, equivalent to 2.1 Million dollars on the time of writing.
+It is believed that the winner, used a sophisticated approach to finish last~\cite{fomo3dhacker}.
+The winner deployed a few high gas consumption smart contracts prior to the win, when the timer of the game reached about 3 minutes, the winner bought 1 ticket and sent multiple high gasPrice transactions to aforementioned smart contracts to lure the miners to mine these highly profitable transactions.
+Luckily enough the winner was able to congest the network in a way that no other ticket purchases were mined in the 3 minutes window and the miners were focused on the high gasPriced transactions.
+All the details mentioned here are drawn from the transaction history on the blockchain and unless otherwise proven seem to be the way the winner acted to win the pot.
+%probably needs more work to be good enough. more resources will be out in the coming days !
 

### 2018-09-10 frontrunning/Latex/setup/table.tex
[frontrunning] gambling dapp + table fix

@@
 
-\multirow{6}{*}{Gambling}											& Fomo3D (5) \\  
+\multirow{8}{*}{Gambling}											& Fomo3D (5) \\  
 															& DailyDivs (6) \\ 
@@
 
-\multirow{2}{*}{Name Services}												
-															& \textit{Ethereum Name Service (24)}  \\  \hline
+\multirow{1}{*}{Name Services}									& \textit{Ethereum Name Service (24)}  \\  \hline
 

### 2018-09-10 frontrunning/Latex/sections/paper.tex
[frontrunning] minor changes

@@
 Due to deterministic nature of blockchains, running gambling games based on randomness is close to impossible.
-There had been attempts to use block headers or such as the seed to randomness but almost all have failed as every data accessible to the smart contract at the time of execution, is also accessible to other smart contracts and they could predict the output on the run.
-Thus most of the current gambling games on Ethereum, rely on the human factor and network behavior rather than pure randomness.
-Because of these many infamous gambling games are now running on Ethereum network and front-running them requires a highly sophisticated methods.\\
+There had been attempts to use block headers or such as the seed to randomness but almost all have failed as every data accessible to the smart contract at the time of execution, is also accessible to other smart contracts and they could predict the output on the run, thus prone to front-running and miner's manipulation.
+Many infamous gambling games are now running on Ethereum network and front-running them requires a level of sophistication and knowledge of the internal of the games and Ethereum.\\
 One of the most popular smart contracts on Ethereum blockchain belongs to a controversial gambling game named \texttt{Fomo3d}, also known as \textit{Exit Scam}\footnote{\url{https://exitscam.me/play}}.

### 2018-09-10 frontrunning/Latex/sections/paper.tex
[frontrunning] minor edits

@@
 This protocol operates a hybrid model with off-chain order management and communication and merely the order matching takes place on the chain.
-Using Loopring functionality, the users do not need to host their assets on the exchange and and instead they keep their assets in their blockchain wallet.
-For example, if a user A wants to exchange \emph{token A } to \emph{token B}, she keeps \emph{token A }  safe in her wallet and the Loopring protocol automatically broadcasts the order to the network after user's authorization.
+Using Loopring functionality, the users do not need to host their assets on the exchange and instead they keep their assets in their blockchain wallet.
+For example, if user A wants to exchange \emph{token A} with \emph{token B}, she keeps \emph{token A}  safe in her wallet and the Loopring protocol automatically broadcasts the order to the network after user's authorization.
 If user B wants to exchange, there would be match making miners on the Loopring protocol who matches the orders and swaps the tokens through a smart contract.

### 2018-09-10 frontrunning/Latex/sections/paper.tex
[frontrunning] Domain name frontrunning

@@
 \noindent As mentioned in Section~\ref{sec:Front Running on the Blockchains}, although front-running attacks have been more showcased in the context of decentralized exchanges and trading systems, they are not yet limited to the financial markets.
-Front-running can occur within other (non-financial) blockchain applications such as naming systems.
-Blockchain-based domain registrar have been introduced to eliminate the role of central parties \ie domain name system (DNS) which introduce single point of failures in the entire web.
+Front-running can also occur within other (non-financial) blockchain applications such as naming systems.
+Recently, many blockchain-based domain registrars have been designed and implemented to eliminate the role of central parties \ie domain name system (DNS) which itself introduces single point of failures in the entire web.
+Ethereum Name Service (ENS)\footnote{\url{https://ens.domains/}}, is the most popular decentral naming service that uses a sealed auction to facilitate the procedures of purchasing new \textit{.eth} domain names.
+These domains which can be resolved using any Ethereum web3 compatible browser.
+Although a sealed auction (\textit{startAuctionsAndBid}) is used while implementing the ENS, the deposit should be equal or bigger than the bid, this information leakage could be used to front-run the transaction with the same bid amount.
+By doing so the front-runner invalidates the original bid and hence registers the domain name himself.
+
+Although the implementation uses a sealed auction, \textit{startAuctionsAndBid}, the deposit should be equal or bigger than the bid, this information leakage could be used to front-run the transaction with the same bid amount.
+By doing so the front-runner invalidates the original bid.
+This is similar to traditional domain squatting where the service provider maliciously buys the domains upon domain availably check and before the user gets the chance to finish his order.
+Although the exact same attack is not feasible on blockchain naming services as querying already registered domains are instant and without leaking any information of the intention of the user to the network.
+
 One such system is Ghazal, an Ethereum-based naming and PKI system~\cite{moosavighazal}.

### 2018-09-10 frontrunning/Latex/sections/paper.tex
[frontrunning] More details added to domain frontrunning

@@
 
-%NOTE: @mahsa: is this considered a Historical evidence? should we talk about this somewhere else and maybe do a PoC on Ghazal for this section?
-\subsubsection{Domain Name Front-running} \hfill\\    %Following section talks about front-running in namespaces but limited to Ghazal.
-Will talk about NameCoin in the section of mitigations (commit & reveal method)
-
-%Jeremy's Comment: contrast ghazal vs ens, or try to have some historical evidence for namespace on the Ethereums. Try too make ghazal less central.
-%Jeremy's comments: also talk about the "private information retrieval" (Ian Goldberg's work at waterloo)
+\subsubsection{Domain Name Front-running} \hfill\\
 
@@
 Recently, many blockchain-based domain registrars have been designed and implemented to eliminate the role of central parties \ie domain name system (DNS) which itself introduces single point of failures in the entire web.
-Ethereum Name Service (ENS)\footnote{\url{https://ens.domains/}}, is the most popular decentral naming service that uses a sealed auction to facilitate the procedures of purchasing new \textit{.eth} domain names.
+Ethereum Name Service (ENS)\footnote{\url{https://ens.domains/}}, is the most popular decentral naming service that uses a sealed auction to facilitate the procedures of purchasing new \texttt{.eth} domain names.
 These domains which can be resolved using any Ethereum web3 compatible browser.
@@
 By doing so the front-runner invalidates the original bid and hence registers the domain name himself.
-
-Although the implementation uses a sealed auction, \textit{startAuctionsAndBid}, the deposit should be equal or bigger than the bid, this information leakage could be used to front-run the transaction with the same bid amount.
-By doing so the front-runner invalidates the original bid.
-This is similar to traditional domain squatting where the service provider maliciously buys the domains upon domain availably check and before the user gets the chance to finish his order.
-Although the exact same attack is not feasible on blockchain naming services as querying already registered domains are instant and without leaking any information of the intention of the user to the network.
-
-One such system is Ghazal, an Ethereum-based naming and PKI system~\cite{moosavighazal}.
-Ghazal users rely on the Ethereum blockchain to register their \texttt{.ghazal} domain names and bind certificates to those names.
+Ghazal is another Ethereum-based naming system that allows users to register \texttt{.ghazal} domain names and bind certificates to those names~\cite{moosavighazal}.
 In Ghazal model, a user would register domain name by executing the \textit{registerdomain} function from the Ghazal smart contract with the domain name in plain text as the function argument.
@@
 In this case, front-runners would monitor and identify domain names of interest, and sell it back to the other users with a higher price~\cite{sac022en33:online}.
+Front-running practice can happen in the traditional domain name system (DNS) as well.
+Domain name registrars can steal available domain names once seeing a query from users that looks up that domain's availability.
+In this case, the registrar can register the domain name ahead and sell it back to the user for a higher price.
 
-%Some edits required here! @mahsa TODO
-
-Ethereum Naming Service (ENS)\footnote{\url{https://ens.domains/}}, the most popular decentral naming service uses a sealed auction to purchase new domains with \textit{.eth} extension which can be resolved using any Ethereum web3 compatible browser.
-Although the implementation uses a sealed auction, \textit{startAuctionsAndBid}, the deposit should be equal or bigger than the bid, this information leakage could be used to front-run the transaction with the same bid amount.
-By doing so the front-runner invalidates the original bid.
-This is similar to traditional domain squatting where the service provider maliciously buys the domains upon domain availably check and before the user gets the chance to finish his order.
-Although the exact same attack is not feasible on blockchain naming services as querying already registered domains are instant and without leaking any information of the intention of the user to the network.
-%e.g: https://etherscan.io/enslookup?q=handshaker.eth
 %TODO: ian goberg: private information retrieval .

### 2018-09-12 frontrunning/Latex/sections/paper.tex
[frontrunning] Dual Authoring figure 1 added

@@
 This protocol operates a hybrid model with off-chain order management and communication and merely the order matching takes place on the chain.
-Using Loopring functionality, the users do not need to host their assets on the exchange and instead they keep their assets in their blockchain wallet.
-For example, if user A wants to exchange \emph{token A} with \emph{token B}, she keeps \emph{token A}  safe in her wallet and the Loopring protocol automatically broadcasts the order to the network after user's authorization.
-If user B wants to exchange, there would be match making miners on the Loopring protocol who matches the orders and swaps the tokens through a smart contract.
 To solve the front-running issue within the decentralized exchanges, Loopring protocol proposes \emph{dual-authoring} scheme.
@@
 Doing so, it is assured that (i) the orders are be modified (because they are signed using the owner's private key), (ii) no other miner can mine the ring (because the miner's address is signed using his private key), and no user can front-run the orders within the ring (because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them).
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.8\linewidth]{figures/Vulnerable_Loopring.png}
+\caption{Payload of submitRing Function. \label{fig:vulnerable_loopring}}
+\end{figure}
+
+The major scheme of front-running in Loopring (and any protocol for order-matching) are order-filch and ring-filch.
+Order-filch is when a front-runner steals one or more orders from a pending ring settlement transaction; and ring-filch is when a front-runner steals the entire ring from the pending transaction.
+
+%Using Loopring functionality, the users do not need to host their assets on the exchange and instead they keep their assets in their blockchain wallet.
+For example, if user A wants to exchange \emph{token A} with \emph{token B}, she keeps \emph{token A}  safe in her wallet and the Loopring protocol automatically broadcasts the order to the network after user's authorization.
+If user B wants to exchange, there would be match making miners on the Loopring protocol who matches the orders and swaps the tokens through a smart contract.
 

### 2018-09-12 frontrunning/Latex/sections/paper.tex
[frontrunning] More technical details on Loopring

@@
 This protocol operates a hybrid model with off-chain order management and communication and merely the order matching takes place on the chain.
-To solve the front-running issue within the decentralized exchanges, Loopring protocol proposes \emph{dual-authoring} scheme.
+To solve the front-running issue within the decentralized exchanges, Loopring protocol proposes \emph{dual-authoring} scheme.To achieve high liquidity and price improvement, Loopring ordered are grouped in \emph{ring order}.
+After the required signatures are provided by miner a and owner of the order, the miner sends the \emph{submitRing transaction} to the Loopring Smart Contract (LSC) for verification and settlement, see Figure~\ref{vulnerable_loopring}.
+While the \emph{submitRing transaction} sits unconfirmed in the mempool, any front-runner can create the a copy of this transaction with his address instead of the miner address and the signature of the hash of the ring using his own address.
+By paying a higher gasprice, block mines choose this transaction instead of the original \emph{submitRing transaction}.
+Using the dual authority scheme, the new version of Loopring protocol solves this issue.
+
 This solution set two levels of authorization for orders - one for settlement, and one for order matching.

### 2018-09-12 frontrunning/Latex/sections/paper.tex
[frontrunning] Second loopring's figure and more technical details added

--- 2018-09-10 frontrunning/Latex/sections/paper.tex
@@
 This protocol operates a hybrid model with off-chain order management and communication and merely the order matching takes place on the chain.
-Using Loopring functionality, the users do not need to host their assets on the exchange and instead they keep their assets in their blockchain wallet.
-For example, if user A wants to exchange \emph{token A} with \emph{token B}, she keeps \emph{token A}  safe in her wallet and the Loopring protocol automatically broadcasts the order to the network after user's authorization.
-If user B wants to exchange, there would be match making miners on the Loopring protocol who matches the orders and swaps the tokens through a smart contract.
-To solve the front-running issue within the decentralized exchanges, Loopring protocol proposes \emph{dual-authoring} scheme.
-This solution set two levels of authorization for orders - one for settlement, and one for order matching.
-In summary, in this scheme a wallet generates a pair of public key (auth-address) and private key (auth-key) for the user, these keys are different from the user's address and its corresponding private key.
-The address of order's owner, order parameters, and the auth-address are hashed.
-The hash value, which is called the order-hashed then is signed using the owner's private key.
-The signature of the ring-hash together with the auth-key are sent to the  miner for matching.
-In this stage, orders are added to various rings;
-?each ring encapsulates all the fields and data of its containing orders (a ring can have 2 to 10 orders).
-Once a ring is established, the ring miner uses each order's auth-key to sign the hash of the ring, together with his own address, and the mining parameters.
-He also needs to sign the hash of the ring together with the mining parameters using his own private key.
-The miner then sends all the signatures to the Loopring smart contract (LPSC).
-Eventually, the Loopring protocol verifies each signatures against their corresponding auth-key of each order and does not accept the ring if the signatures are not valid.
-Doing so, it is assured that (i) the orders are be modified (because they are signed using the owner's private key), (ii) no other miner can mine the ring (because the miner's address is signed using his private key), and no user can front-run the orders within the ring (because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them).
+To solve the front-running issue within the decentralized exchanges, Loopring protocol proposes \emph{dual-authoring} scheme.To achieve high liquidity and price improvement, Loopring orders are grouped in \emph{ring order}.
+After the required signatures are provided by miner a and owner of the order, see Figure~\ref{vulnerable_loopring}, the ring miner sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement.
+While the \emph{submitRing transaction} sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with his address instead of the ring miner's address and the sign the hash of the ring using his own private key.
+By paying a higher gasprice, block miners choose the front-runner's transaction instead of the original \emph{submitRing transaction}.
+However, Loopring's team solves this issue using the dual authority scheme in the new version of the Loopring protocol.
+This solution sets two levels of authorization for orders - one for settlement, and one for order matching.
+As it can be seen in Figure~\ref{not_vulnerable_loopring}, each owner of any order generates a pair of public key (auth-address) and private key (auth-key), which are different from his address and its corresponding private key.
+These auth-keys are used to sign the hash of the ring and will further prevent anyone from regenerating the same \emph{submitRing transaction}.
+The reason is that the auth-keys are only known to the miner of the ring as they are not part of on-chain transaction.
+Doing so, it is assured that (i) the orders are be modified (because they are signed using the owner's private key), (ii) no other miner can mine the ring (because the miner's address is signed using his private key), and no user can front-run the \emph{submitRing transaction} (because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them).
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.7\linewidth]{figures/Vulnerable_Loopring.png}
+\caption{\emph{submitRing} Transaction in the old version of the Loopring protocol.
+Any user can regenerate this transaction by replacing the miner's address with his address and signing the hash of the ring using his private key.
+\label{fig:vulnerable_loopring}}
+\end{figure}
+%https://www.lucidchart.com/invitations/accept/33d38ce9-4660-4743-806d-45c72f7e8393
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.7\linewidth]{figures/Dual_Authoring_Loopring.png}
+\caption{\emph{submitRing} Transaction in the new version of the Loopring protocol.
+Other users cannnot regenerate this transaction as they do not access auth-keys and hence are not able to create the signatures.
+\label{fig:not_vulnerable_loopring}}
+\end{figure}
+%https://www.lucidchart.com/invitations/accept/8dee869c-482c-433f-a901-8d041a1dc526
 %______________________________________________________________%

### 2018-09-12 frontrunning/Latex/sections/paper.tex
[frontrunning] fixes to dual authoring. although still vague.
- maybe we don't need this much details about dual authoring?
- figures need more clarification

@@
 This protocol operates a hybrid model with off-chain order management and communication and merely the order matching takes place on the chain.
-To solve the front-running issue within the decentralized exchanges, Loopring protocol proposes \emph{dual-authoring} scheme.To achieve high liquidity and price improvement, Loopring orders are grouped in \emph{ring order}.
-After the required signatures are provided by miner a and owner of the order, see Figure~\ref{vulnerable_loopring}, the ring miner sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement.
-While the \emph{submitRing transaction} sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with his address instead of the ring miner's address and the sign the hash of the ring using his own private key.
-By paying a higher gasprice, block miners choose the front-runner's transaction instead of the original \emph{submitRing transaction}.
-However, Loopring's team solves this issue using the dual authority scheme in the new version of the Loopring protocol.
+To achieve high liquidity and price improvement, Loopring orders are grouped in \emph{ring orders}.
+After the required signatures are provided by a miner and owner of the order, see Figure~\ref{fig:vulnerable_loopring}, the ring miner sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement.
+While the \emph{submitRing transaction} sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with his address instead of the ring miner's address and then sign the hash of the ring using his own private key.
+By paying a higher gasPrice, block miners choose the front-runner's transaction instead of the original \emph{submitRing transaction}.
+However, Loopring's team solves this issue using the \emph{dual-authoring} scheme in the new version of the Loopring protocol.
 This solution sets two levels of authorization for orders - one for settlement, and one for order matching.
-As it can be seen in Figure~\ref{not_vulnerable_loopring}, each owner of any order generates a pair of public key (auth-address) and private key (auth-key), which are different from his address and its corresponding private key.
+As it can be seen in Figure~\ref{fig:not_vulnerable_loopring}, each owner of any order generates a pair of public key (auth-address) and private key (auth-key), which are different from his address and its corresponding private key.
 These auth-keys are used to sign the hash of the ring and will further prevent anyone from regenerating the same \emph{submitRing transaction}.
 The reason is that the auth-keys are only known to the miner of the ring as they are not part of on-chain transaction.
-Doing so, it is assured that (i) the orders are be modified (because they are signed using the owner's private key), (ii) no other miner can mine the ring (because the miner's address is signed using his private key), and no user can front-run the \emph{submitRing transaction} (because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them).
+Doing so, it is assured that (i) the orders are not modified (because they are signed using the owner's private key), (ii) no other miner can mine the ring (because the miner's address is signed using his private key), and no user can front-run the \emph{submitRing transaction} (because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them).
 

### 2018-09-12 frontrunning/Latex/sections/paper.tex
[frontrunning] fix subsections + one fast round of typo fixing

@@
 
-%The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty~\cite{liang2005distressed}.
-Any sort of front-running activity wis considered as an unethical and illegal practice as it is unfairly beneficial for a few system participants who have the privilege of acting on this information and taking advantages at the expense of the investors.
-
-\subsection{How are Blockchain Applications Vulnerable to Front-running?} %which blockchain applications?
+\subsection{How are Blockchain Applications Vulnerable to Front-running?} 
 \label{sec:Front Running on the Blockchains}
-
-%Jeremy's Comments: Find some examples; you have to justify why you talked about only a specific group of examples.
-Need to have a criteria for what is vulnerable to frontrunning: like top ten dapps from specific blogs.
-Have a criteria.
 
@@
 Malinova and Park discuss different design settings for financial markets and trading platforms on decentral ledgers ~\cite{malinova2017market}.
-They argue that blockchain brings a new options of transparency which affects traders behaviour, specially in the presence of intermediary front-runners.
+They argue that blockchain brings a new options of transparency which affects traders behavior, specially in the presence of intermediary front-runners.
 They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make front-running costly and inefficient.
@@
 To do so, he would use the coin as an input of a transaction and broadcast it to the network, before the transaction gets validated and executed, he broadcasts another transaction associated with a higher transaction fee which spends the same input ~\cite{bamert2013have, karame2012double}.
-This adversarial behaviour is similar to the front-running attack where the attacker would front-run other users by paying a higher transaction fee when broadcasting his transactions to the network, hence a higher priority transaction for miners to include in the block they mine.
+This adversarial behavior is similar to the front-running attack where the attacker would front-run other users by paying a higher transaction fee when broadcasting his transactions to the network, hence a higher priority transaction for miners to include in the block they mine.
 
@@
 As discussed in~\ref{sec:Front Running on the Blockchains}, capped ICOs are considerable applications to be investigated in terms of the front-running attacks, Status ICO is such application.
-In June 2017, Status.im~\cite{statuswhitepaper} started its ICO and reached its cap within 3 hours, resulted in close to 300,000 Ether of funding.
+In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached its cap within 3 hours, resulted in close to 300,000 Ether of funding.
 In order to prevent large investments to take place early and limit the amount of Ether deposited in an investment, the team at the Status ICO used a \textit{fair} token distribution method called \textit{dynamic ceiling} as an attempt to increase the time window for smaller investors.
@@
 Further study showed that some mining pools might have been manipulating the network for their own profit.
-In addition, there were many transactions sent with higher gas price to front-run other transactions, however these transactions were failed due to the restriction in the ICO smart contract to reject any transactions with higher than 50GWei gas price (as an attempt to prevent the aforementioned front-running).
+In addition, there were many transactions sent with higher gas price to front-run other transactions, however these transactions were failed due to the restriction in the ICO smart contract to reject any transactions with higher than 50 \textit{GWei} gas price (as an attempt to prevent the aforementioned front-running).
 
@@
 
-Ethereum blockchain contains all transaction ever made on Ethereum, however, it is not easy to see the behaviour of the participants and miners solely using the default clients nor online blockchain explorers.
+Ethereum blockchain contains all transaction ever made on Ethereum, however, it is not easy to see the behavior of the participants and miners solely using the default clients nor online blockchain explorers.
 In order to get the required data, Ethereum blockchain data should be converted to a queryable format.
@@
 
-\subsubsection{Exchanges}
+\subsubsection{Exchanges.}
 Exchanges such as EtherDelta\footnote{also known as ForkDelta for the UI \url{https://forkdelta.app/}}, are closest form to decentral exchanges, however their orderbooks are stored on a central server they control and shown on their user interface (website).
@@
 
-\subsubsection{Domain Name Front-running} \hfill\\
-
+\subsubsection{Name Services.}
 \noindent As mentioned in Section~\ref{sec:Front Running on the Blockchains}, although front-running attacks have been more showcased in the context of decentralized exchanges and trading systems, they are not yet limited to the financial markets.
@@
 %______________________________________________________________%
-\subsection{Crypto-Collectibles Games} \hfill\\
+\subsubsection{Crypto-Collectibles Games.}
 
@@
 Cryptokitties is known to be one of the first and the most popular use cases of ERC721 tokens~\cite{cryptokitties}.
-Their marketcap reached more than 6 million dollars in the first months their launch.
+Their market cap reached more than 6 million dollars in the first months their launch.
 Crypto-Collectibles, are similar to ERC-20 tokens and can be listed on exchanges.
@@
 
-\subsection{Gambling} \hfill\\ 
+\subsubsection{Gambling.} 
 Due to deterministic nature of blockchains, running gambling games based on randomness is close to impossible.
@@
 In the traditional markets, front-running is considered unethical and also illegal.
-In the blockchain space, the designers of the decentral applications cannot rely on the justice system for unethical behaviour, and they must assume that each participant in the network acts rationally in their own self interest, the application will be operating in an adversarial environment~\cite{0xfrontrunning:online}.
+In the blockchain space, the designers of the decentral applications cannot rely on the justice system for unethical behavior, and they must assume that each participant in the network acts rationally in their own self interest, the application will be operating in an adversarial environment~\cite{0xfrontrunning:online}.
 A few decentral exchange projects such as \textit{EtherDelta} and \textit{0xProject}~\cite{warren20170x}, have proposed solutions for front-running, which is off-chain order books.
@@
 The details of how Submarine commitments work is outside the scope of this paper, however in summary, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality it is possible to generate one outgoing transaction from an address in which no private key exists.
-By constructing a transaction from that address to the DApp and funding that address we fulfil the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}, see Figure~\ref{fig:LibSubmarine}.
+By constructing a transaction from that address to the DApp and funding that address we fulfill the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}, see Figure~\ref{fig:LibSubmarine}.
 Drawbacks of this scheme are similar to ~\ref{CommitmentScheme}, with an addition of two more transactions to finalize the functionality, which results in more cost and complicated user experience.

### 2018-09-13 frontrunning/Latex/sections/paper.tex
[frontrunning] editted till section 5 (5 On Blockchain Front-running)

@@
 
-The concept of the \emph{front-running} goes back to the decades ago when financial instrument markets first started.
-Initially the trades required to be physically available in the exchange office to deliver the bids and offers, and traders, in the knowledge of future market change, would run in front of the others to get their orders in before the change in the market to profit from the change.
+The concept of the \emph{front-running} goes back to decades ago when financial instrument markets first started.
+Initially the traders required to be physically available in the exchange office to deliver the bids and offers, and some traders, in the knowledge of future market change, would run in front of the others to get their orders in before the change in the market to profit from the change.
 Clearly in such scenarios front-running was possible yet not detectable as a damaging activity.
-However with the rapid advances of the technology in the last few decades, trading is not happening in person anymore and a greater number of applications are now vulnerable to front-running.
-Furthermore, Blockchain technology has introduced transparency and open markets which led to a new threat of front-running and it inherently affects all decentral applications, whether financial or non-financial.
+However with the rapid advances of the technology in the last few decades, trading is not done in person anymore and new generation front-running was feasible through high speed networks.
+Furthermore, Blockchain technology has introduced transparency and open markets which led to a new era of front-running and it inherently affects all decentral applications, whether financial or non-financial.
 Arbitrage and Censorship, are also issues that had been linked to front-running attacks on blockchain.
-However, the goal of this paper is to provide a complete look at the front-running issues and thus the aforementioned will remain out of the scope of this research study.
+We started by looking at one specific case of front-running on Ethereum blockchain, However, the goal of this paper is to provide a complete look at the front-running issues.
+%and thus the aforementioned will remain out of the scope of this research study.
 There has been little quantitative analysis and research of the front-running issue in decentralized applications, we aim to take a thorough look into the history of the front-running, discuss multiple existing issues in the eco-system and systematize the proposed solutions, and eventually match these solutions to their suitable use cases.
@@
 
-%For the FC: \textbf{CASE STUDY} should be used in here, also in abstract, also at the end of intro section.
-% Why is this important.
 % PAPER BEING SOLD HERE
-%\textbf{Note to Change the structure of the paper: to pitch this paper as a case study, we can polish it as a Bancor case study: 1) here is the bancor project that we look at 2) we find that the issue is mostly the frontrunning 3) So we take a deep look into what is frontrunning 4) we find other case studies that are vulnerable and go through each case}
+%\textbf{Note to Change the structure of the paper: to pitch this paper as a case study, we can polish it as a status,im ico case study: 1) here is the status.im ico project that we look at 2) we find that the issue is mostly the frontrunning 3) So we take a deep look into what is frontrunning 4) we find other case studies that are vulnerable and go through each case}
 
@@
 Therefore, a malicious trader would now run in front of that order and put his own transaction in-between (before the trade was executed) and profit from the price increase of the stock.
-In other words, a group of market participants obtain non-public market information which allows them to front-run other users trades by putting their orders a head of those trades and benefit from advance knowledge of pending client orders.
+In other words, a group of market participants obtain non-public market information which allows them to front-run other user\'s trades by putting their orders ahead of those trades and benefit from advance knowledge of pending client orders.
 The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty~\cite{liang2005distressed}.
@@
 
-Blockchain technology has received an exceptional amount of attention since it was first introduced as the underlying technology of the cryptocurrency Bitcoin in Satoshi Nakamoto's (pseudonymous) 2008 white paper \cite{nakamoto2008bitcoin}.
-Many decentralized applications that are nowadays built on top of this technology represent the significance of the blockchain as it completely eliminates the single points of failures within any systems.
-However, blockchains have some inherent characteristic that leave them vulnerable to \emph{front running} behaviour.
+Blockchain technology has received an exceptional amount of attention since it was first introduced as the underlying technology of the cryptocurrency Bitcoin in 2008~\cite{nakamoto2008bitcoin}.
+Many decentralized applications that are built on top of this technology represent the significance of the blockchain as it completely eliminates the central point of failure within any systems.
+However, blockchains have some inherent characteristic that leave them vulnerable to \emph{front-running} behavior.
 Although this data structure is known to be publicly visible to every network participants, information is layered  and some of them are accessed only by insiders.
-Any network participants that runs a full node on the blockchain is able to obtain those information and as mentioned in Section~\ref{sec:What is front-running?}, this leaves the application vulnerable to front running.
-Decentralized exchanges are a group of blockchain financial applications where front running can be executed.
-Bancor \cite{hertzog2017bancor} is an example of such systems in which front-runners benefit from potential price increase of the market stocks (details are provided in Section ...).
+Any network participants that runs a full node on the blockchain is able to obtain those information and as mentioned in Section~\ref{sec:What is front-running?}, this leaves the application vulnerable to front-running.
+Decentralized exchanges are a group of blockchain financial applications where front-running can be executed.
+Bancor \cite{hertzog2017bancor} is an example of such systems in which front-runners benefit from potential price increase of the market stocks (details are provided in~\ref{sec:frontrunningExchanges}).
 Decentralized namespaces, as blockchain non-financial applications, are another example.
-Ghazal \cite{moosavighazal} is such system in which upon seeing a transaction from Alice to register \texttt{alice.com}, front runner can go ahead of her and register this domain name.
-He can later sell \texttt{alice.com} to Alice for a higher price and benefit from the price increase.
-Another application that is vulnerable to front running is Initial Coin Offering, ICO, smart contracts.
+Ethereum Name Service and Ghazal \cite{moosavighazal} are such systems in which upon seeing a transaction from Alice to register \texttt{alice.eth}, front-runner can go ahead of her and register this domain name.
+He can later sell \texttt{alice.eth} to Alice for a higher price and profit.
+Another application that is vulnerable to front-running is Initial Coin Offering (ICO) smart contracts.
 ICO is a method to distribute tokens based on the deposits of the native coin, Ether in the case of Ethereum.
@@
 This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to late comers on the open markets~\cite{zetzsche2018ico, li2018initial}.
-ICOs started to experiment with different fair capping methods, such as reverse dutch auction, dynamic ceilings, \eg ~\cite{kaal2017initial}.
+ICOs started to experiment with different fair capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}.
 This competition made ICOs a good opportunity for front-running attacks.
@@
 \section{Related Work}
-As the traditional front-running was originated to trading financial instruments most of the literature are focused on financial aspects of the markets. %TODO: expand this with something
+As the traditional front-running was originated in trading financial instruments most of the literature are focused on financial aspects of the markets.
+However, there are also a few policies regarding domain name registration front-running~\cite{sac022en33:online}
 
 \subsection{Literature on Traditional Front-running}
-
-As traditional frontrunning has been the subject of discussion for decades, there are many literatures on this subject.
+As traditional front-running has been the subject of discussion for decades, there are many literatures on this subject.
 Here we focus on the historical context and how the regulations evolved to be what they are today.\\
-Front-running was first appeared on the Chicago Board Options Exchange (\textit{CBoE})~\cite{markham1988front}, and was identified by \textit{Securities Exchange Commission} in 1977 as the following:
+Front-running was first appeared on the Chicago Board Options Exchange (\textit{CBoE})~\cite{markham1988front}, and was defined by \textit{Securities Exchange Commission} in 1977 as the following:
 \begin{quote}
@@
 
-On the years after there were ongoing discussions between self-regulatory exchanges (\eg \textit{CBoE}) and  \textit{SEC} to regulate, detect and define laws and regulations to deal with front-running~\cite{markham1988front}, with \textit{SEC} stating:
+On the years after there were ongoing discussions between self-regulatory exchanges (\eg \textit{CBoE}) and  \textit{SEC} to regulate, detect and define laws and policies to deal with front-running~\cite{markham1988front}, with \textit{SEC} stating:
 \begin{quote}
@@
 
-As defining what exactly is considered illegal front-running required more knowledge of how these new markets behave, \textit{CBoE} and other exchanges (and brokers) issued educational circulars for their members asserting that front-running violates existing rules, with some examples of what is considered front-running.
-However difference of opinion regarding the unfairness of front running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~cite{sec1978optionsmarket}.
+Defining what exactly was considered illegal front-running required more knowledge of how these new markets behaved.
+\textit{CBoE} and other exchanges (and brokers) issued educational circulars for their members asserting that front-running violates existing rules, with some examples of what is considered front-running.
+However difference of opinion regarding the unfairness of front-running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~cite{sec1978optionsmarket}.
 
@@
 \subsection{Literature on Blockchain Front-running}
-%NOTE (ASK JEREMY): decentral or decentralized?
 There are only a few research carried out on the front-running subject in the context of blockchain and decentral ledgers. \\
@@
 As mentioned in Section~\ref{sec:What is front-running?}, the information leakage results the entire system to be vulnerable to the front-running.
-They also propose a cryptographic approach to prevent any decentralized system from front-running.
-In this approach, which is similar to commit and reveal, a transaction hash (fingerprint) is broadcast to the network to secure time priority while not revealing the information.
+They also propose a cryptographic approach, similar to commit and reveal(~ref{CommitmentScheme}), to prevent front-running in decentral systems.
+%In this approach, which is similar to commit and reveal , a transaction hash (fingerprint) is broadcast to the network to secure time priority while not revealing the information.
 Once the hash is processed and assigned an index and timestamp, the transaction details are broadcast.
 This makes the transaction and its hash to be executed at their reserved time priority and not vulnerable to front-running.
-
 Malinova and Park discuss different design settings for financial markets and trading platforms on decentral ledgers ~\cite{malinova2017market}.
@@
 Upon submitting the bug bounty to the Hydra smart contract, one can front-run the bug report and claim the bounty instead of the original reporter.
-They propose \textit{Submarine Commitments} which is to conceal the bounty claim and the participatory factor.
-They claim submarine commitments ``are a stronger form of a commit-reveal scheme''.
+In order to mitigate this issue they proposed \textit{Submarine Commitments} (~\ref{submarineCommits}).
 
@@
 To do so, he would use the coin as an input of a transaction and broadcast it to the network, before the transaction gets validated and executed, he broadcasts another transaction associated with a higher transaction fee which spends the same input ~\cite{bamert2013have, karame2012double}.
-This adversarial behavior is similar to the front-running attack where the attacker would front-run other users by paying a higher transaction fee when broadcasting his transactions to the network, hence a higher priority transaction for miners to include in the block they mine.
+This adversarial behavior is similar to the front-running attack where the attacker front-runs his own transaction by paying a higher fee when broadcasting the second transaction.
 
@@
 \section{Status ICO} 
-As discussed in~\ref{sec:Front Running on the Blockchains}, capped ICOs are considerable applications to be investigated in terms of the front-running attacks, Status ICO is such application.
-In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached its cap within 3 hours, resulted in close to 300,000 Ether of funding.
-In order to prevent large investments to take place early and limit the amount of Ether deposited in an investment, the team at the Status ICO used a \textit{fair} token distribution method called \textit{dynamic ceiling} as an attempt to increase the time window for smaller investors.
-They implemented multiple caps --ceiling-- which each had a maximum amount that could be deposited.
-In this case, every deposit was checked by the smart contract and the exceeding amount was refunded to the sender while the accepted amount was sent to the Status.im wallet ~\cite{statusicoanalysis}.
+As discussed in~\ref{sec:Front Running on the Blockchains}, capped ICOs are considerable applications to be investigated in terms of the front-running attacks, \textit{Status.im} ICO is such application.
+In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached the defined cap within 3 hours, resulting in close to 300,000 Ether of funds.
+In order to prevent few large investments to buy up all the tokens and limit the amount of Ether deposited in an investment, they used a \textit{fair} token distribution method named \textit{Dynamic Ceiling} as an attempt to increase the time window for smaller investors.
+They implemented multiple caps --ceiling-- in which, each had a maximum amount that could be deposited in.
+In this case, every deposit was checked by the smart contract and the exceeding amount was refunded to the sender while the accepted amount was sent to their multisignature wallet address ~\cite{statusicoanalysis}.
 
-During the time the ICO was open for participation, there were reports of Ethereum network being unusable and transactions were not confirming.
+During the time the ICO was open for participation, there were reports of Ethereum network being unusuable and transactions were not confirming.
 Further study showed that some mining pools might have been manipulating the network for their own profit.
-In addition, there were many transactions sent with higher gas price to front-run other transactions, however these transactions were failed due to the restriction in the ICO smart contract to reject any transactions with higher than 50 \textit{GWei} gas price (as an attempt to prevent the aforementioned front-running).
+In addition, there were many transactions sent with higher gas price to front-run other transactions, however these transactions were failing due to the restriction in the ICO smart contract to reject any transactions with higher than 50 \textit{GWei} gas price (as an attempt to prevent the known front-running behavior).
 
@@
 According to the analysis we carried out, it was discovered that the F2Pool, an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure ~\ref{fig:mining_pool_ratio}), sent 100 Ether to 30 new Ethereum addresses before Status.im ICO started.
-On the time the ICO was opened for participation, F2Pool constructed 31 transactions to the ICO token sale smart contract from the addresses they controlled --without broadcasting these transactions to the network-- and used their entire mining power to mine their own transactions.
+On the time the ICO was opened for participation, F2Pool constructed 31 transactions to the ICO token sale smart contract from the addresses they controlled --without broadcasting these transactions to the network-- and used their entire mining power to mine their own transactions and also potentially failing high gas price transactions.
 
@@
 In order to get the required data, Ethereum blockchain data should be converted to a queryable format.
-For this case study, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation of the Ethereum protocol\url{https://github.com/ethereum/go-ethereum}}, python script for extracting, transforming and loading ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery\footnote{A fast, highly scalable, cost-effective, and fully managed cloud data warehouse for analytics \url{https://cloud.google.com/bigquery/}}.
+For this case study, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation of the Ethereum protocol\url{https://github.com/ethereum/go-ethereum}} for the full node, python script for extracting, transforming and loading ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery\footnote{A fast, highly scalable, cost-effective, and fully managed cloud data warehouse for analytics \url{https://cloud.google.com/bigquery/}}.
 Using this software stack, we were able to query for all the transactions and blocks within the window of Status.im ICO for further analysis which was mainly done by data analysis tool \texttt{Tableau}\footnote{Tableau is a data visualization software that is used for data science and business intelligence.\url{https://www.tableau.com/}}.
-A copy of this dataset and the findings can be found in \texttt{github.com / ANONYMOUS}.
+A copy of this dataset and the initial findings can be found in our Github repository\footnote{\url{github.com / ANONYMOUS}}.
 
 As shown in Figure~\ref{fig:Transactions_miners_while_status_ico_cut}, most of the top miners in the mentioned time frame, have mined almost the same number of failed and successful transactions which were directed toward Status.im token sale, however F2Pool's transactions indicate their successful transactions were equivalent to 10\% of the failed transactions, hence maximizing the mining rewards, on gas, while censoring other transactions to the token sale smart contract.
+The terminology used here is specific to smart contract transactions on Ethereum, by \textit{``failed transaction''} we mean the transactions in which the smart contract code flow rejected and threw an exception and by \textit{``successful transaction''} we mean the transactions that went through and received tokens from the smart contract.
 
@@
 \caption{This chart shows the miners behaviour on the time window that Status.im ICO was running.
-\textit{Successful Transactions} are the transactions that led to deposit and generation of Status.im tokens and \textit{Failed Transactions} are the transactions to the token sale smart contract that failed to retrieve any tokens, for varias reasons.
 It is clear that the number of successful transactions mined by F2Pool do not follow the random homogeneous pattern of the rest of the network.
@@
 
-%TODO: describe failed/ successful transactions, what they mean!
-
-By tracing the transactions from these 30 addresses, we found a explicit Interference of the F2Pool in this scenario.
-As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses were sent to Status.im ICO and mined by F2Pool.
-Once the dynamic ceiling algorithm refunded a portion of the sent funds back to these addresses, these funds were again sent back to F2Pool main address.
+By tracing the transactions from these 30 addresses, we found explicit Interference of the F2Pool\footnote{F2Pool Ethereum address was identified by their mining reward deposit address \url{https://etherscan.io/address/0x61c808d82a3ac53231750dadc13c777b59310bd9}} in this scenario.
+As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses were sent to Status.im ICO and mined by F2Pool themselves, where the dynamic ceiling algorithm refunded a portion of the deposited funds back to these addresses, these funds were sent back to F2Pool main address a few days after.
 
@@
 
-Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their code to behave in a certain way to front-run other transactions and take advantage of the monetary profit.
+Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their mining software to behave in a certain way to front-run other transactions and take advantage of the monetary profit.
 The dataset used for this analysis can be found on our GitHub repository.\footnote{Frontrunning Status.im ICO dataset: \url{http://github.com/TODO:ANONYMOUS}}.
-This analysis made us wonder, how many other DApps are vulnerable to front-running attack, who can front-run and what are the mitigation methods for decentral applications?
+This analysis made us wonder how many other DApps are vulnerable to front-running attack, who can front-run and what are the mitigation methods for decentral applications?
 
@@
 
-\subsubsection{Exchanges.}
+\subsubsection{Exchanges.} \label{sec:frontrunningExchanges}
 Exchanges such as EtherDelta\footnote{also known as ForkDelta for the UI \url{https://forkdelta.app/}}, are closest form to decentral exchanges, however their orderbooks are stored on a central server they control and shown on their user interface (website).
@@
 
-\subsubsection{Design Decision \#2: Submarine Commitments\newline}
+\subsubsection{Design Decision \#2: Submarine Commitments\newline}\label{submarineCommits}
 Submarine Commitments~\cite{breidenbach2018enter, submarinesendHD} are similar to the commitment schemes with some key differences such as hiding participatory factor and being fully collateralized.

### 2018-09-13 frontrunning/Latex/sections/paper.tex
[frontrunning] Traditional Front-running Prevention Methods

@@
 
-\subsection{Literature on Traditional Front-running}
+\subsection{Literature on Traditional Front-running}\label{traditionalFrontrunning}
 As traditional front-running has been the subject of discussion for decades, there are many literatures on this subject.
@@
 
-\emph{Traditional Front-running Prevention Methods}. regulations/enforcement/broker education/sealed order
-%@shayan: ^ TODO!
+\emph{Traditional Front-running Prevention Methods}.
+There are debates in traditional markets regarding the fact that Front-running is considered to be a form of insider trading which deemed to be illegal.
+Traditional methods to prevent front-running mainly involves after the fact investigation and legal action against the front-runners~\cite{LexisNexisLawSuit}.
+As mentioned in section~\ref{traditionalFrontrunning}, educating the employees were the first step taken to prevent such issues in traditional markets, however front-running became less likely to happen mainly because of the high fine and law suits against firms whom behaved in an unethical way.
+Other methods such as dark pools~\cite{zhu2014dark, buti2011diving} and sealed bids~\cite{radner1989sealed} were discussed and implemented in variety of regulated trading systems.
 
@@
 There are two main approaches to prevent front running, one to design a blockchain that is front-run resistant , and the other to design the application logics in a way that front running is not possible.
-%@shayan: ^ TODO!
-
 %______________________________________________________________%

### 2018-09-13 frontrunning/Latex/sections/paper.tex
[frontrunning] clean up traditional prevention methods

@@
 
-\emph{Blockchain front-running mitigation/prevention}.
-The traditional methods of preventing front-running are based on regulation and restrictions applied to the brokers and actors within the markets, such methods do not apply to blockchains, no enforcement methods, ...
+The traditional methods to prevent front-running does not apply to blockchain applications, as mainly they are based on central enforcement and limitations, also in case of blockchains the actors whom are front-running could be anonymous and the fear of lawsuits would not apply.
+\\
 

### 2018-09-13 frontrunning/Latex/sections/paper.tex
[frontrunning] notes from meeting sep 13, 2018

@@
 
-\subsection{What is Front-running?} %Definition of front-running
+\subsection{Traditional Front-running} %Definition of front-running
 \label{sec:What is front-running?}
@@
 
-\subsection{How are Blockchain Applications Vulnerable to Front-running?} 
-\label{sec:Front Running on the Blockchains}
-
-Blockchain technology has received an exceptional amount of attention since it was first introduced as the underlying technology of the cryptocurrency Bitcoin in 2008~\cite{nakamoto2008bitcoin}.
-Many decentralized applications that are built on top of this technology represent the significance of the blockchain as it completely eliminates the central point of failure within any systems.
-However, blockchains have some inherent characteristic that leave them vulnerable to \emph{front-running} behavior.
-Although this data structure is known to be publicly visible to every network participants, information is layered  and some of them are accessed only by insiders.
-Any network participants that runs a full node on the blockchain is able to obtain those information and as mentioned in Section~\ref{sec:What is front-running?}, this leaves the application vulnerable to front-running.
-Decentralized exchanges are a group of blockchain financial applications where front-running can be executed.
-Bancor \cite{hertzog2017bancor} is an example of such systems in which front-runners benefit from potential price increase of the market stocks (details are provided in~\ref{sec:frontrunningExchanges}).
-Decentralized namespaces, as blockchain non-financial applications, are another example.
-Ethereum Name Service and Ghazal \cite{moosavighazal} are such systems in which upon seeing a transaction from Alice to register \texttt{alice.eth}, front-runner can go ahead of her and register this domain name.
-He can later sell \texttt{alice.eth} to Alice for a higher price and profit.
-Another application that is vulnerable to front-running is Initial Coin Offering (ICO) smart contracts.
-ICO is a method to distribute tokens based on the deposits of the native coin, Ether in the case of Ethereum.
-After a few hacking incidents on high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered.
-This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to late comers on the open markets~\cite{zetzsche2018ico, li2018initial}.
-ICOs started to experiment with different fair capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}.
-This competition made ICOs a good opportunity for front-running attacks.
-In this paper we use multiple empirical examples to show possibility of front-running on DApps, for the sake of completeness, we use one incident on ICOs, and examples from the Top 25 DApps by recent user counts.
-%TODO: this last sentece is a bit weird here!
-
-%___________________________________________________________%
-\section{Related Work}
-As the traditional front-running was originated in trading financial instruments most of the literature are focused on financial aspects of the markets.
-However, there are also a few policies regarding domain name registration front-running~\cite{sac022en33:online}
-
-\subsection{Literature on Traditional Front-running}\label{traditionalFrontrunning}
+%\subsection{Literature on Traditional Front-running}\label{traditionalFrontrunning}
 As traditional front-running has been the subject of discussion for decades, there are many literatures on this subject.
@@
 
+\subsection{How are Blockchain Applications Vulnerable to Front-running?} 
+\label{sec:Front Running on the Blockchains}
+
+Blockchain technology has received an exceptional amount of attention since it was first introduced as the underlying technology of the cryptocurrency Bitcoin in 2008~\cite{nakamoto2008bitcoin}.
+Many decentralized applications that are built on top of this technology represent the significance of the blockchain as it completely eliminates the central point of failure within any systems.
+However, blockchains have some inherent characteristic that leave them vulnerable to \emph{front-running} behavior.
+Although this data structure is known to be publicly visible to every network participants, information is layered  and some of them are accessed only by insiders.
+Any network participants that runs a full node on the blockchain is able to obtain those information and as mentioned in Section~\ref{sec:What is front-running?}, this leaves the application vulnerable to front-running.
+Decentralized exchanges are a group of blockchain financial applications where front-running can be executed.
+Bancor \cite{hertzog2017bancor} is an example of such systems in which front-runners benefit from potential price increase of the market stocks (details are provided in~\ref{sec:frontrunningExchanges}).
+Decentralized namespaces, as blockchain non-financial applications, are another example.
+Ethereum Name Service and Ghazal \cite{moosavighazal} are such systems in which upon seeing a transaction from Alice to register \texttt{alice.eth}, front-runner can go ahead of her and register this domain name.
+He can later sell \texttt{alice.eth} to Alice for a higher price and profit.
+Another application that is vulnerable to front-running is Initial Coin Offering (ICO) smart contracts.
+ICO is a method to distribute tokens based on the deposits of the native coin, Ether in the case of Ethereum.
+After a few hacking incidents on high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered.
+This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to late comers on the open markets~\cite{zetzsche2018ico, li2018initial}.
+ICOs started to experiment with different fair capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}.
+This competition made ICOs a good opportunity for front-running attacks.
+In this paper we use multiple empirical examples to show possibility of front-running on DApps, for the sake of completeness, we use one incident on ICOs, and examples from the Top 25 DApps by recent user counts.
+%TODO: this last sentece is a bit weird here!
+
 \subsection{Literature on Blockchain Front-running}
@@
 
-%______________________________________________________________%
-
-\section{Status ICO} 
-As discussed in~\ref{sec:Front Running on the Blockchains}, capped ICOs are considerable applications to be investigated in terms of the front-running attacks, \textit{Status.im} ICO is such application.
-In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached the defined cap within 3 hours, resulting in close to 300,000 Ether of funds.
-In order to prevent few large investments to buy up all the tokens and limit the amount of Ether deposited in an investment, they used a \textit{fair} token distribution method named \textit{Dynamic Ceiling} as an attempt to increase the time window for smaller investors.
-They implemented multiple caps --ceiling-- in which, each had a maximum amount that could be deposited in.
-In this case, every deposit was checked by the smart contract and the exceeding amount was refunded to the sender while the accepted amount was sent to their multisignature wallet address ~\cite{statusicoanalysis}.
-
-During the time the ICO was open for participation, there were reports of Ethereum network being unusuable and transactions were not confirming.
-Further study showed that some mining pools might have been manipulating the network for their own profit.
-In addition, there were many transactions sent with higher gas price to front-run other transactions, however these transactions were failing due to the restriction in the ICO smart contract to reject any transactions with higher than 50 \textit{GWei} gas price (as an attempt to prevent the known front-running behavior).
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.5\linewidth]{figures/Mining_pool_ratio.png}
-\caption{The percentage of Ethereum blocks mined between block 3903900 and 3908029, this is the time frame in which Status.im ICO was running.
-This percentage roughly shows the hashing power ratio each miner had at that time.
-\label{fig:mining_pool_ratio}} % IS THIS STATEMENT CORRECT?
-\end{figure}
-
-According to the analysis we carried out, it was discovered that the F2Pool, an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure ~\ref{fig:mining_pool_ratio}), sent 100 Ether to 30 new Ethereum addresses before Status.im ICO started.
-On the time the ICO was opened for participation, F2Pool constructed 31 transactions to the ICO token sale smart contract from the addresses they controlled --without broadcasting these transactions to the network-- and used their entire mining power to mine their own transactions and also potentially failing high gas price transactions.
-
-Ethereum blockchain contains all transaction ever made on Ethereum, however, it is not easy to see the behavior of the participants and miners solely using the default clients nor online blockchain explorers.
-In order to get the required data, Ethereum blockchain data should be converted to a queryable format.
-For this case study, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation of the Ethereum protocol\url{https://github.com/ethereum/go-ethereum}} for the full node, python script for extracting, transforming and loading ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery\footnote{A fast, highly scalable, cost-effective, and fully managed cloud data warehouse for analytics \url{https://cloud.google.com/bigquery/}}.
-Using this software stack, we were able to query for all the transactions and blocks within the window of Status.im ICO for further analysis which was mainly done by data analysis tool \texttt{Tableau}\footnote{Tableau is a data visualization software that is used for data science and business intelligence.\url{https://www.tableau.com/}}.
-A copy of this dataset and the initial findings can be found in our Github repository\footnote{\url{github.com / ANONYMOUS}}.
-
-As shown in Figure~\ref{fig:Transactions_miners_while_status_ico_cut}, most of the top miners in the mentioned time frame, have mined almost the same number of failed and successful transactions which were directed toward Status.im token sale, however F2Pool's transactions indicate their successful transactions were equivalent to 10\% of the failed transactions, hence maximizing the mining rewards, on gas, while censoring other transactions to the token sale smart contract.
-The terminology used here is specific to smart contract transactions on Ethereum, by \textit{``failed transaction''} we mean the transactions in which the smart contract code flow rejected and threw an exception and by \textit{``successful transaction''} we mean the transactions that went through and received tokens from the smart contract.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.7\linewidth]{figures/Transactions_miners_while_status_ico_cut_only_icotx.png}
-\caption{This chart shows the miners behaviour on the time window that Status.im ICO was running.
-It is clear that the number of successful transactions mined by F2Pool do not follow the random homogeneous pattern of the rest of the network.
-\label{fig:Transactions_miners_while_status_ico_cut}}
-\end{figure}
-
-%TODO: make pie charts for each mining pool, all non-status-ico transactions vs success-ico-transactions vs failed-ico=transactions
-
-By tracing the transactions from these 30 addresses, we found explicit Interference of the F2Pool\footnote{F2Pool Ethereum address was identified by their mining reward deposit address \url{https://etherscan.io/address/0x61c808d82a3ac53231750dadc13c777b59310bd9}} in this scenario.
-As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses were sent to Status.im ICO and mined by F2Pool themselves, where the dynamic ceiling algorithm refunded a portion of the deposited funds back to these addresses, these funds were sent back to F2Pool main address a few days after.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.7\linewidth]{figures/F2Pool_transactions_to_StatusICO_and_Refunds.png}
-\caption{F2Pool prior to Status.im ICO deposited 100 Ether in multiple new Ethereum addresses.
-On the time of the ICO they sent these deposits to Status ICO smart contract and prioritized mining of these transactions in their mining pool, this was to overcome the dynamic ceiling algorithm of the token sale smart contract.
-Later on they sent the refunded Ether back to their own address.
-[Graph made using Blockseer.com] \label{fig:f2poolfront-run}}
-\end{figure}
-
-Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their mining software to behave in a certain way to front-run other transactions and take advantage of the monetary profit.
-The dataset used for this analysis can be found on our GitHub repository.\footnote{Frontrunning Status.im ICO dataset: \url{http://github.com/TODO:ANONYMOUS}}.
-This analysis made us wonder how many other DApps are vulnerable to front-running attack, who can front-run and what are the mitigation methods for decentral applications?
-
-As the result of this analysis, we discovered a wide range of blockchain front-running case studies that are yet to investigated.
-Therefore, in the next sections we dive deeper into blockchain specific front-running details and analyze top recent DApps for front-running attack vectors and possible solutions proposed to mitigate these issues.
-
-%______________________________________________________________%
+%
+%___________________________________________________________%
+%\section{Related Work}
+%As the traditional front-running was originated in trading financial instruments most of the literature are focused on financial aspects of the markets.
+However, there are also a few policies regarding domain name registration front-running~\cite{sac022en33:online}
 
@@
 
+%TODO: frontrunning categories: ICOs, non-ICOs  DApps. why we chose these, top recent activities.
+
 %______________________________________________________________%
 
-\subsection{Case Studies}  
+%TODO: but we missed ICOs becasue they are high intensity usage in short period of time and does not include in the list of the most used ones.
+%
+
+%______________________________________________________________%
+
+\section{Cases of Front-running in DApps}  
 As blockchain records are immutably recorded, there is enough historical data to analyze for possible front-running detection.There is no perfect criteria to list top DApps on Ethereum blockchain, for the purpose of this research we analyzed the top 25 DApps based on recent user activities\footnote{List of decentralized applications \url{https://dappradar.com/dapps}} in the first week of September 2018.
-
+%TODO:
 %ICO is only in use when the time window is happenig.  this is based on the last 24hours activities 
-%justify why started with ICO and go to other apps
+%justify why started with ICO and go to other apps . refrence to ICO section for actual justification
 
@@
 
+% everything that has a line up , someone can jump in the line and front-run
+% talk about velocity that seems to be not front-runnable but because of of the liquidity pool limitation, there can be an order that consumes the last chunk of liquidity "edge case" , to front run others and make their "option calls" fail
+
+%Tragedy of the commons
+
 % maybe inlcude 0xbitcoin ERC721 mineable tokens front-running!
@@
 
-\subsubsection{Exchanges.} \label{sec:frontrunningExchanges}
+\subsection{Markets and Exchanges.} \label{sec:frontrunningExchanges}
 Exchanges such as EtherDelta\footnote{also known as ForkDelta for the UI \url{https://forkdelta.app/}}, are closest form to decentral exchanges, however their orderbooks are stored on a central server they control and shown on their user interface (website).
@@
 
-\subsubsection{Name Services.}
+\subsection{Name Services.}
 \noindent As mentioned in Section~\ref{sec:Front Running on the Blockchains}, although front-running attacks have been more showcased in the context of decentralized exchanges and trading systems, they are not yet limited to the financial markets.
@@
 %______________________________________________________________%
-\subsubsection{Crypto-Collectibles Games.}
+\subsection{Crypto-Collectibles Games.}
 
@@
 
-\subsubsection{Gambling.} 
+\subsection{Gambling.} 
 Due to deterministic nature of blockchains, running gambling games based on randomness is close to impossible.
@@
 %______________________________________________________________%
+
+\section{Cases of Front-running in ICOs} 
+%icos are easy to be missed in the overall most used apps. 
+%Make subsections here. one for ico's and why they are important and not in the most used daaps ones. one for  status ico, and different ones for each part
+%justify why ICOs were missed in the previous section.
+argue why 100 other things like ICOs that were missing from the list .
+ICOs were missed becasue no ico was happening there, and also the website filteres through known applications, we could not think of any other scenarios that are similar to icos.
+
+As discussed in~\ref{sec:Front Running on the Blockchains}, capped ICOs are considerable applications to be investigated in terms of the front-running attacks, \textit{Status.im} ICO is such application.
+In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached the defined cap within 3 hours, resulting in close to 300,000 Ether of funds.
+In order to prevent few large investments to buy up all the tokens and limit the amount of Ether deposited in an investment, they used a \textit{fair} token distribution method named \textit{Dynamic Ceiling} as an attempt to increase the time window for smaller investors.
+They implemented multiple caps --ceiling-- in which, each had a maximum amount that could be deposited in.
+In this case, every deposit was checked by the smart contract and the exceeding amount was refunded to the sender while the accepted amount was sent to their multisignature wallet address ~\cite{statusicoanalysis}.
+
+During the time the ICO was open for participation, there were reports of Ethereum network being unusable and transactions were not confirming.
+Further study showed that some mining pools might have been manipulating the network for their own profit.
+In addition, there were many transactions sent with higher gas price to front-run other transactions, however these transactions were failing due to the restriction in the ICO smart contract to reject any transactions with higher than 50 \textit{GWei} gas price (as an attempt to prevent the known front-running behavior).
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.5\linewidth]{figures/Mining_pool_ratio.png}
+\caption{The percentage of Ethereum blocks mined between block 3903900 and 3908029, this is the time frame in which Status.im ICO was running.
+This percentage roughly shows the hashing power ratio each miner had at that time.
+\label{fig:mining_pool_ratio}} % IS THIS STATEMENT CORRECT?
+\end{figure}
+
+According to the analysis we carried out, it was discovered that the F2Pool, an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure ~\ref{fig:mining_pool_ratio}), sent 100 Ether to 30 new Ethereum addresses before Status.im ICO started.
+On the time the ICO was opened for participation, F2Pool constructed 31 transactions to the ICO token sale smart contract from the addresses they controlled --without broadcasting these transactions to the network-- and used their entire mining power to mine their own transactions and also potentially failing high gas price transactions.
+
+Ethereum blockchain contains all transaction ever made on Ethereum, however, it is not easy to see the behavior of the participants and miners solely using the default clients nor online blockchain explorers.
+In order to get the required data, Ethereum blockchain data should be converted to a queryable format.
+For this case study, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation of the Ethereum protocol\url{https://github.com/ethereum/go-ethereum}} for the full node, python script for extracting, transforming and loading ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery\footnote{A fast, highly scalable, cost-effective, and fully managed cloud data warehouse for analytics \url{https://cloud.google.com/bigquery/}}.
+Using this software stack, we were able to query for all the transactions and blocks within the window of Status.im ICO for further analysis which was mainly done by data analysis tool \texttt{Tableau}\footnote{Tableau is a data visualization software that is used for data science and business intelligence.\url{https://www.tableau.com/}}.
+A copy of this dataset and the initial findings can be found in our Github repository\footnote{\url{github.com / ANONYMOUS}}.
+
+As shown in Figure~\ref{fig:Transactions_miners_while_status_ico_cut}, most of the top miners in the mentioned time frame, have mined almost the same number of failed and successful transactions which were directed toward Status.im token sale, however F2Pool's transactions indicate their successful transactions were equivalent to 10\% of the failed transactions, hence maximizing the mining rewards, on gas, while censoring other transactions to the token sale smart contract.
+The terminology used here is specific to smart contract transactions on Ethereum, by \textit{``failed transaction''} we mean the transactions in which the smart contract code flow rejected and threw an exception and by \textit{``successful transaction''} we mean the transactions that went through and received tokens from the smart contract.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.7\linewidth]{figures/Transactions_miners_while_status_ico_cut_only_icotx.png}
+\caption{This chart shows the miners behaviour on the time window that Status.im ICO was running.
+It is clear that the number of successful transactions mined by F2Pool do not follow the random homogeneous pattern of the rest of the network.
+\label{fig:Transactions_miners_while_status_ico_cut}}
+\end{figure}
+
+%TODO: make pie charts for each mining pool, all non-status-ico transactions vs success-ico-transactions vs failed-ico=transactions
+
+By tracing the transactions from these 30 addresses, we found explicit Interference of the F2Pool\footnote{F2Pool Ethereum address was identified by their mining reward deposit address \url{https://etherscan.io/address/0x61c808d82a3ac53231750dadc13c777b59310bd9}} in this scenario.
+As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses were sent to Status.im ICO and mined by F2Pool themselves, where the dynamic ceiling algorithm refunded a portion of the deposited funds back to these addresses, these funds were sent back to F2Pool main address a few days after.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.7\linewidth]{figures/F2Pool_transactions_to_StatusICO_and_Refunds.png}
+\caption{F2Pool prior to Status.im ICO deposited 100 Ether in multiple new Ethereum addresses.
+On the time of the ICO they sent these deposits to Status ICO smart contract and prioritized mining of these transactions in their mining pool, this was to overcome the dynamic ceiling algorithm of the token sale smart contract.
+Later on they sent the refunded Ether back to their own address.
+[Graph made using Blockseer.com] \label{fig:f2poolfront-run}}
+\end{figure}
+
+Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their mining software to behave in a certain way to front-run other transactions and take advantage of the monetary profit.
+The dataset used for this analysis can be found on our GitHub repository.\footnote{Frontrunning Status.im ICO dataset: \url{http://github.com/TODO:ANONYMOUS}}.
+This analysis made us wonder how many other DApps are vulnerable to front-running attack, who can front-run and what are the mitigation methods for decentral applications?
+
+%TODO:
+%As the result of this analysis, we discovered a wide range of blockchain front-running case studies that are yet to investigated.
+Therefore, in the next sections we dive deeper into blockchain specific front-running details and analyze top recent DApps for front-running attack vectors and possible solutions proposed to mitigate these issues.
+
+%______________________________________________________________%
+
 \section{How to stop Front-running?} %We have have the applicability of the solutions inline.

### 2018-09-13 frontrunning/Latex/sections/paper.tex
[frontrunning] revisions on Intro

@@
 The concept of the \emph{front-running} goes back to decades ago when financial instrument markets first started.
-Initially the traders required to be physically available in the exchange office to deliver the bids and offers, and some traders, in the knowledge of future market change, would run in front of the others to get their orders in before the change in the market to profit from the change.
+Initially the traders required to be physically available in the exchange office to deliver the bids and offers, and some traders, in the knowledge of future market change, could run in front of the others to get their orders ahead of the change in the market to profit from the price change.
 Clearly in such scenarios front-running was possible yet not detectable as a damaging activity.
-However with the rapid advances of the technology in the last few decades, trading is not done in person anymore and new generation front-running was feasible through high speed networks.
-Furthermore, Blockchain technology has introduced transparency and open markets which led to a new era of front-running and it inherently affects all decentral applications, whether financial or non-financial.
-Arbitrage and Censorship, are also issues that had been linked to front-running attacks on blockchain.
-We started by looking at one specific case of front-running on Ethereum blockchain, However, the goal of this paper is to provide a complete look at the front-running issues.
-%and thus the aforementioned will remain out of the scope of this research study.
-There has been little quantitative analysis and research of the front-running issue in decentralized applications, we aim to take a thorough look into the history of the front-running, discuss multiple existing issues in the eco-system and systematize the proposed solutions, and eventually match these solutions to their suitable use cases.
-\footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".
-}
-
-% PAPER BEING SOLD HERE
-%\textbf{Note to Change the structure of the paper: to pitch this paper as a case study, we can polish it as a status,im ico case study: 1) here is the status.im ico project that we look at 2) we find that the issue is mostly the frontrunning 3) So we take a deep look into what is frontrunning 4) we find other case studies that are vulnerable and go through each case}
-
-%Decentral applications are on the rise with Turing complete blockchains maturing to handle high monetary value transactions.
-Tokenization mushroomed to a whole ecosystem of tokenized applications on the blockchain, these applications inherently become a market as tokens are in the core of them.
-We started looking at some of these applications, in specific \textit{Bancor}~\cite{hertzog2017bancor}, to look into possible issues rising from these new models.
-Transparency of blockchains, although being a good feature of them, opens up these markets to some attack vectors that might not be visible on the time of the application design, one main attack is known as \textbf{front-running}, whether financial or non-financial.
-Arbitrage and Censorship, are also issues arises from the designs on the blockchain technology and had been linked to front-running attacks, hence we use the term \textit{front-running] losely to talk about any transaction manupulation with the intention of getting other transactions in before the original transaction takes place.
-In this paper, our focus is to have a complete overview of front-running on the blockchain while analysing Bancor issues.
-While looking at the possibility of front-running on other applications, we found interesting case studies that affects most of the top 25 decentral applications on Ethereum blockchain.
+However, with the rapid advances of the technology in the last few decades, trading is not carried out in person anymore and new form of front-running is feasible through high speed networks.
+Furthermore, Blockchain technology has introduced transparency and open markets and leads to a new era of front-running which inherently affects all decentral applications, whether financial or non-financial.
+Arbitrage and Censorship, are also issues that have been linked to front-running attacks on blockchain \textit{(We need to talk about why these two are left out of the scope of this paper)}.
+Currently, there are quite a few decentral applications built on the blockchains, so in order for us to perform a thorough study on blockchain application front-running, we set a s specific criteria by using the top 25 decentral applications which have the highest recent user activities.\footnote{List of decentralized applications \url{https://dappradar.com/dapps}} Using this criteria, we successfully categorized these decentral application s into 5 principal categories on which we conduct our analysis.
+Surprisingly, there was no ICO (initial coin offering) included in the top 25 Dapps list by the time we fetched the data from the website.
+We believe the reason is because the ICOs are inherently different from other groups of Dapss as they are merely highly active during their offering periods and their user activity drops dramatically after the offerings period are over.
+Therefore, we  consider ICOs as another cases on which the front-running should be investigated (although they are not listed in the top 25 Dapps we use) \footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".}
 

### 2018-09-13 frontrunning/Latex/sections/paper.tex
[frontrunning] Revisions on Preliminaries

@@
 Surprisingly, there was no ICO (initial coin offering) included in the top 25 Dapps list by the time we fetched the data from the website.
-We believe the reason is because the ICOs are inherently different from other groups of Dapss as they are merely highly active during their offering periods and their user activity drops dramatically after the offerings period are over.
+We believe the reason is because the ICOs are inherently different from other groups of Daaps as they are merely highly active during their offering periods and their user activity drops dramatically after the offerings period are over.
 Therefore, we  consider ICOs as another cases on which the front-running should be investigated (although they are not listed in the top 25 Dapps we use) \footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".}
@@
 
-\subsection{Traditional Front-running} %Definition of front-running
+\subsection{Traditional Front-running} 
 \label{sec:What is front-running?}
@@
 \emph{Front-running} is analogous to any course of action during which a person benefits from prior access to inside or confidential market information about upcoming transactions and trades.
-This problem can occur in both financial and non-financial systems, however, it is more noticeable within the trading and exchange systems as it was originated back in stock markets.
+This problem can occur in both financial and non-financial systems, however, it is more noticeable within the trading and exchange systems as was originated back in the stock markets.
 In the old times, all the trades were executed on papers, so in case of receiving a large order from a client, the broker might say this loud and other people around the table could be informed.
-Therefore, a malicious trader would now run in front of that order and put his own transaction in-between (before the trade was executed) and profit from the price increase of the stock.
-In other words, a group of market participants obtain non-public market information which allows them to front-run other user\'s trades by putting their orders ahead of those trades and benefit from advance knowledge of pending client orders.
+Therefore, a malicious trader would run in front of that order and put his own transaction in-between (before the trade was executed) and hence profit from the price increase of the stock.
+In fact, a group of market participants obtain non-public market information which allows them to front-run other user\'s trades by putting their orders ahead of those trades and benefit from advance knowledge of pending client orders.
 The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty~\cite{liang2005distressed}.
@@
 
-%\subsection{Literature on Traditional Front-running}\label{traditionalFrontrunning}
+\subsection{Literature on Traditional Front-running}\label{traditionalFrontrunning}
 As traditional front-running has been the subject of discussion for decades, there are many literatures on this subject.
@@
 
-\subsection{How are Blockchain Applications Vulnerable to Front-running?} 
+\subsection{Blockchain Front-running} % for the unity of the paper, the previous title : How are Blockchain Applications Vulnerable to Front-running?
+is changed to "Blokcchain front-running", in this case the other section's name (on blockchain frontrunning, where we talk about miner and non miner frontrunning) needs to change to sth different and more descriptive.
 \label{sec:Front Running on the Blockchains}
@@
 Many decentralized applications that are built on top of this technology represent the significance of the blockchain as it completely eliminates the central point of failure within any systems.
-However, blockchains have some inherent characteristic that leave them vulnerable to \emph{front-running} behavior.
+However, blockchains have some inherent characteristic that leave them vulnerable to \emph{front-running} behaviour.
 Although this data structure is known to be publicly visible to every network participants, information is layered and some of them are accessed only by insiders.
@@
 Decentralized exchanges are a group of blockchain financial applications where front-running can be executed.
+%____________________________________________________________________
+%%% The following chunk seem to be redundant and weird. Should we keep it?? 
 Bancor \cite{hertzog2017bancor} is an example of such systems in which front-runners benefit from potential price increase of the market stocks (details are provided in~\ref{sec:frontrunningExchanges}).
@@
 %TODO: this last sentece is a bit weird here!
+%____________________________________________________________________
 
 \subsection{Literature on Blockchain Front-running}
-There are only a few research carried out on the front-running subject in the context of blockchain and decentral ledgers. \\
 
+Due to the novelty characteristics of the underlying technology (blockchains) and the issue of front-running, there are only a few research carried out on this subject in the context of blockchain and decentral ledgers.
+\\
 Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage~\cite{aune2017footprints}.
@@
 
-%
 %___________________________________________________________%
-%\section{Related Work}
-%As the traditional front-running was originated in trading financial instruments most of the literature are focused on financial aspects of the markets.
-However, there are also a few policies regarding domain name registration front-running~\cite{sac022en33:online}
 

### 2018-09-13 frontrunning/Latex/sections/paper.tex
[frontrunning] Fu;; round revision except the ICO section

@@
 \section{Introduction}
+\label{sec:intro}
 
@@
 Arbitrage and Censorship, are also issues that have been linked to front-running attacks on blockchain \textit{(We need to talk about why these two are left out of the scope of this paper)}.
-Currently, there are quite a few decentral applications built on the blockchains, so in order for us to perform a thorough study on blockchain application front-running, we set a s specific criteria by using the top 25 decentral applications which have the highest recent user activities.\footnote{List of decentralized applications \url{https://dappradar.com/dapps}} Using this criteria, we successfully categorized these decentral application s into 5 principal categories on which we conduct our analysis.
+Currently, there are quite a few decentral applications built on the blockchains, so in order for us to perform a thorough study on blockchain application front-running, we set a s specific criteria by using the top 25 decentral applications which have the highest recent user activities.\footnote{List of decentralized applications \url{https://dappradar.com/dapps}} Using this criteria, we successfully categorized these decentral applications into 4 principal categories on which we conduct our analysis.
 Surprisingly, there was no ICO (initial coin offering) included in the top 25 Dapps list by the time we fetched the data from the website.
@@
 
-\section{On Blockchain Front-running}
-
-\subsection{Who Can Front-run?}
+\section{Who are Blockchain Front-runners?} %\section{On Blockchain Front-running}
 \label{sec:who can front-run?}
@@
 %https://www.lucidchart.com/invitations/accept/c8768786-4a3f-4c78-b3c8-aa04a6b81d06
-
-%TODO: frontrunning categories: ICOs, non-ICOs  DApps. why we chose these, top recent activities.
-
 %______________________________________________________________%
@@
 \section{Cases of Front-running in DApps}
-As blockchain records are immutably recorded, there is enough historical data to analyze for possible front-running detection.There is no perfect criteria to list top DApps on Ethereum blockchain, for the purpose of this research we analyzed the top 25 DApps based on recent user activities\footnote{List of decentralized applications \url{https://dappradar.com/dapps}} in the first week of September 2018.
+
+As mentioned in the Section~\ref{sec:intro}, for the purpose of this research we retrieved the top 25 DApps based on recent user activities from \footnote{List of decentralized applications \url{https://dappradar.com/dapps}} in the first week of September 2018.
+We then categorize these applications into 4 principal groups of decentral applications (see Table~\ref{tab:top25dapps}).
+In this section, we take a deep look into one or two decentral applications from each category and pinpoint the technical details of front-running issue on each case.
+Although, no ICOs were spot in the list at the time it was retrieved, we will thoroughly discuss our analysis on how ICOs are highly vulnerable to front-running activities (see Section~\ref{sec:ICOsfrontrunning}).
+
 %TODO:
@@
 \input{setup/table}
-
-From these DApps we looked at one example per category, most of which had front-running issues, some more severe than the other.
-Although none of these DApps are ICO smart contracts, we believe with the number of ICOs done on Ethereum it is worth to mention one instance of front-running on these applications as well.
 
@@
 % mint: https://etherscan.io/tx/0x9883bc3ad018fd2b649982f88fbad7dc5abcb8f11c4f1d87ef814ba30c2b3428
+%______________________________________________________________%
+\subsection{Markets and Exchanges.} \label{sec:frontrunningExchanges}
 
-\subsection{Markets and Exchanges.} \label{sec:frontrunningExchanges}
-Exchanges such as EtherDelta\footnote{also known as ForkDelta for the UI \url{https://forkdelta.app/}}, are closest form to decentral exchanges, however their orderbooks are stored on a central server they control and shown on their user interface (website).
+Exchanges such as EtherDelta\footnote{also known as ForkDelta for the UI \url{https://forkdelta.app/}}, are closest form to decentral exchanges, however their order books are stored on a central server they control and shown on their user interface (website).
 Other than the fact that they can re-order or censor the orders on their servers, there are other risks of front-running nature in these designs.
@@
 
-%\subsubsection{Bancor} %TODO: mahsa 
-Bancor is an Ethereum-based application that allows users to exchange their tokens without any counter-party risk.
+Bancor is another Ethereum-based application that allows users to exchange their tokens without any counter-party risk.
 This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users.
@@
 There is an implementation of a Bancor front running attack in the Python programming language which represent how a non-miner user can front run other network participants \cite{NewTab13:online}.
+%______________________________________________________________%
+\subsection{Name Services.}
 
-\subsection{Name Services.}
-\noindent As mentioned in Section~\ref{sec:Front Running on the Blockchains}, although front-running attacks have been more showcased in the context of decentralized exchanges and trading systems, they are not yet limited to the financial markets.
+As mentioned in Section~\ref{sec:Front Running on the Blockchains}, although front-running attacks have been more showcased in the context of decentralized exchanges and trading systems, they are not yet limited to the financial markets.
 Front-running can also occur within other (non-financial) blockchain applications such as naming systems.
@@
 In this case, the registrar can register the domain name ahead and sell it back to the user for a higher price.
-
-%TODO: ian goberg: private information retrieval .
-talk about domain name frontrunning in the traditional sense and how goDaddy can steal the domain when queried for availablity.
-however in blockchain the queiry is private and does not reveal the intention that you want to buy the domain.
-View only / solidity code on how to enable this
-
 %______________________________________________________________%
@@
 \subsection{Gambling.}
+
 Due to deterministic nature of blockchains, running gambling games based on randomness is close to impossible.
@@
 
-\section{Cases of Front-running in ICOs} 
+\section{Cases of Front-running in ICOs}  %TODO Shayan: based on how we start the previous section (Cases of Front-running in DApps), rewrite the first paragraph of this section (just for coherency and unity) + try to have seperate subsection for each part to make it more compelling and interesting.
+\label{sec:ICOsfrontrunning}
+
 %icos are easy to be missed in the overall most used apps. 
@@
 This analysis made us wonder how many other DApps are vulnerable to front-running attack, who can front-run and what are the mitigation methods for decentral applications?
-
-%TODO:
-%As the result of this analysis, we discovered a wide range of blockchain front-running case studies that are yet to investigated.
-Therefore, in the next sections we dive deeper into blockchain specific front-running details and analyze top recent DApps for front-running attack vectors and possible solutions proposed to mitigate these issues.
 

### 2018-09-13 frontrunning/Latex/setup/table.tex
[frontrunning] notes from meeting sep 13, 2018
[frontrunning] Fu;; round revision except the ICO section

@@
 \end{tabular}
-\caption{\footnotesize{Top 25 DApps based on recent user activity from \texttt{Dappradar.com} on September 4th, 2018.}\label{tab:top25dapps}}
+\caption{\footnotesize{Top 25 DApps based on recent user activity from \texttt{Dappradar.com} on September 4th, 2018.
+Dapps that are represented in Italic format are analyzied and discussed in this paper.}\label{tab:top25dapps}}
 \end{table}
+
+%TODO: mention the ones in italic are the ones we talk about
 % ------------------------------------------------------------------------------------------------------------------------------------------------%

### 2018-09-13 frontrunning/Latex/sections/paper.tex
[frontrunning] ICO frontrunning

@@
 As mentioned in Section~\ref{sec:who can front-run?} and same as every other Ethereum based application, Bancor transactions can be front run by miners and other regular (non-miner) users.
-There is an implementation of a Bancor front running attack in the Python programming language which represent how a non-miner user can front run other network participants \cite{NewTab13:online}.
+There is an implementation of a Bancor front running attack in the Python programming language which represent how a non-miner user can front run other network participants~\cite{NewTab13:online}.
 %______________________________________________________________%
@@
 
-%icos are easy to be missed in the overall most used apps. 
-%Make subsections here. one for ico's and why they are important and not in the most used daaps ones. one for  status ico, and different ones for each part
-%justify why ICOs were missed in the previous section.
-argue why 100 other things like ICOs that were missing from the list .
-ICOs were missed becasue no ico was happening there, and also the website filteres through known applications, we could not think of any other scenarios that are similar to icos.
+There has been more than 3000 ICOs on Ethereum alone, estimated to exceed 75 billion dollars in the first half of 2018~\cite{zetzsche2018ico}.
+On our DApp samples there was not ICOs mainly because they tend to run for a short time with high number of participant and in the time of writing no ICOs have reached the top 25 DApps of \texttt{DAppradar.com}.
+Needless to say the importance of ICOs as an application of blockchain requires more in-depth analysis of front-running on these DApps.
+%ICOs due to the defined cap, are similar to our analogy of a queue line, people would line up to get in and there's a opportunity to front-run.
+Here we focus on one ICO that our preliminary research showed that there might be a front-running attack going on.
+There is no doubt that similar behaviour could be seen on other instances of ICOs or similar DApps if investigated.
 
+\subsection{\textit{Status.im} ICO}
 As discussed in~\ref{sec:Front Running on the Blockchains}, capped ICOs are considerable applications to be investigated in terms of the front-running attacks, \textit{Status.im} ICO is such application.
@@
 
+\subsection{Data Collection and Analysis}
 According to the analysis we carried out, it was discovered that the F2Pool, an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure ~\ref{fig:mining_pool_ratio}), sent 100 Ether to 30 new Ethereum addresses before Status.im ICO started.

### 2018-09-14 frontrunning/Latex/sections/paper.tex
[frontrunning] DoS Frontrunning

@@
 It was believed that because of the nature of the game, it will never end, however on August 22, 2018 the first round of the game ended and the winner took 10,469 Ether\footnote{First winner of Fomo3D, won 10,469 Ether \url{ https://etherscan.io/tx/0xe08a519c03cb0aed0e04b33104112d65fa1d3a48cd3aeab65f047b2abce9d508}}, equivalent to 2.1 Million dollars on the time of writing.
-It is believed that the winner, used a sophisticated approach to finish last~\cite{fomo3dhacker}.
+It is believed that the winner, used a sophisticated approach to finish last~\cite{fomo3dhacker}, we call this approach \textit{Denial-of-service Front-running}.
 The winner deployed a few high gas consumption smart contracts prior to the win, when the timer of the game reached about 3 minutes, the winner bought 1 ticket and sent multiple high gasPrice transactions to aforementioned smart contracts to lure the miners to mine these highly profitable transactions.
-Luckily enough the winner was able to congest the network in a way that no other ticket purchases were mined in the 3 minutes window and the miners were focused on the high gasPriced transactions.
+For a DoS front-running to work, attacker floods the network with high gasPrice transactions to prevent other transactions to go through.
+Luckily enough the winner was able to congest the network in a way that no other ticket purchases were mined in the 3 minutes window and the miners were prioritizing the high gasPriced transactions over other transactions.
 All the details mentioned here are drawn from the transaction history on the blockchain and unless otherwise proven seem to be the way the winner acted to win the pot.

### 2018-09-16 frontrunning/Latex/sections/paper.tex
[frontrunning] fix references and links

@@
 
-The concept of the \emph{front-running} goes back to decades ago when financial instrument markets first started.
+The concept of the \emph{front-running} is decades old starting with early financial markets.
 Initially the traders required to be physically available in the exchange office to deliver the bids and offers, and some traders, in the knowledge of future market change, could run in front of the others to get their orders ahead of the change in the market to profit from the price change.
 Clearly in such scenarios front-running was possible yet not detectable as a damaging activity.
-However, with the rapid advances of the technology in the last few decades, trading is not carried out in person anymore and new form of front-running is feasible through high speed networks.
+However, with the rapid advances of the technology in the last few decades, trading is not carried out in person anymore, new form of front-running is feasible through high speed networks.
 Furthermore, Blockchain technology has introduced transparency and open markets and leads to a new era of front-running which inherently affects all decentral applications, whether financial or non-financial.
@@
 Therefore, we  consider ICOs as another cases on which the front-running should be investigated (although they are not listed in the top 25 Dapps we use) \footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".}
+
+%Decentral applications are on the rise with Turing complete blockchains maturing to handle high monetary value transactions.
+Tokenization mushroomed to a whole ecosystem of tokenized applications on the blockchain, these applications inherently become a market as tokens are in the core of them.
+We started looking at some of these applications, in specific \textit{Bancor}~\cite{hertzog2017bancor}, to look into possible issues rising from these new models.
+Transparency of blockchains, although being a good feature of them, opens up these markets to some attack vectors that might not be visible on the time of the application design, one main attack is known as \textbf{front-running}, whether financial or non-financial.
+Arbitrage and Censorship, are also issues arises from the designs on the blockchain technology and had been linked to front-running attacks, hence we use the term \textit{front-running] losely to talk about any transaction manupulation with the intention of getting other transactions in before the original transaction takes place.
+In this paper, our focus is to have a complete overview of front-running on the blockchain while analysing Bancor issues.
+While looking at the possibility of front-running on other applications, we found interesting case studies that affects most of the top 25 decentral applications on Ethereum blockchain.
 
@@
 As mentioned in Section~\ref{sec:What is front-running?}, the information leakage results the entire system to be vulnerable to the front-running.
-They also propose a cryptographic approach, similar to commit and reveal(~ref{CommitmentScheme}), to prevent front-running in decentral systems.
+They also propose a cryptographic approach, similar to commit and reveal(~\ref{CommitmentScheme}), to prevent front-running in decentral systems.
 %In this approach, which is similar to commit and reveal , a transaction hash (fingerprint) is broadcast to the network to secure time priority while not revealing the information.
@@
 This makes the transaction and its hash to be executed at their reserved time priority and not vulnerable to front-running.
-Malinova and Park discuss different design settings for financial markets and trading platforms on decentral ledgers ~\cite{malinova2017market}.
+Malinova and Park discuss different design settings for financial markets and trading platforms on decentral ledgers~\cite{malinova2017market}.
 They argue that blockchain brings a new options of transparency which affects traders behavior, specially in the presence of intermediary front-runners.
@@
 \textit{Double-spend attack}, as the name implies, the adversary spends a coin more than one time.
-To do so, he would use the coin as an input of a transaction and broadcast it to the network, before the transaction gets validated and executed, he broadcasts another transaction associated with a higher transaction fee which spends the same input ~\cite{bamert2013have, karame2012double}.
+To do so, he would use the coin as an input of a transaction and broadcast it to the network, before the transaction gets validated and executed, he broadcasts another transaction associated with a higher transaction fee which spends the same input~\cite{bamert2013have, karame2012double}.
 This adversarial behavior is similar to the front-running attack where the attacker front-runs his own transaction by paying a higher fee when broadcasting the second transaction.
@@
 Here the miner sees the cancelation transaction and puts his own order in front of the cancellation transaction --transaction reordering-- to fill the order, potentially profiting from the order.
-They can also include the canceled transaction in their block to collect the full gas limit used by that transaction~\cite{CostofDecentralization:online}, see Figure~\ref{MinerFrontrunning}.
+They can also include the canceled transaction in their block to collect the full gas limit used by that transaction~\cite{CostofDecentralization:online}, see Figure~\ref{fig:MinerFrontrunning}.
 Front-running can also occur in non-financial smart contracts.
@@
 
-As an example Cryptokitties can be bred, bought or sold through the main interface\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}}. See Figure~\ref{cryptokittie}.
+As an example Cryptokitties can be bred, bought or sold through the main interface\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}}. See Figure~\ref{fig:cryptokittie}.
 To buy a cryptokittie, user sends a bid transaction \textit{bid(uint256 \_tokenId)} containing the cryptokittties ID which can be found either on their website or on the ERC721 token smart contract.
@@
 They implemented multiple caps --ceiling-- in which, each had a maximum amount that could be deposited in.
-In this case, every deposit was checked by the smart contract and the exceeding amount was refunded to the sender while the accepted amount was sent to their multisignature wallet address ~\cite{statusicoanalysis}.
+In this case, every deposit was checked by the smart contract and the exceeding amount was refunded to the sender while the accepted amount was sent to their multisignature wallet address~\cite{statusicoanalysis}.
 
@@
 However, if the application is designed in a way that the fees of the orders are sent to the miner of the block, he would have no incentive to front-run the orders as he already gains enough financial benefit from acting fairly and executing the transactions on their correct order.
-For example, Malinova~\cite{Malinova} proposes a design for a decentral exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable.
+For example, Malinova~\cite{malinova2017market} proposes a design for a decentral exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable.
 

### 2018-09-16 frontrunning/Latex/sections/paper.tex
[frontrunning] some edits and cleanup

@@
 Malinova and Park discuss different design settings for financial markets and trading platforms on decentral ledgers~\cite{malinova2017market}.
-They argue that blockchain brings a new options of transparency which affects traders behavior, specially in the presence of intermediary front-runners.
+They argue that blockchain brings a new options of transparency which affects traders behaviour, specially in the presence of intermediary front-runners.
 They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make front-running costly and inefficient.
@@
 To do so, he would use the coin as an input of a transaction and broadcast it to the network, before the transaction gets validated and executed, he broadcasts another transaction associated with a higher transaction fee which spends the same input~\cite{bamert2013have, karame2012double}.
-This adversarial behavior is similar to the front-running attack where the attacker front-runs his own transaction by paying a higher fee when broadcasting the second transaction.
+This adversarial behaviour is similar to the front-running attack where the attacker front-runs his own transaction by paying a higher fee when broadcasting the second transaction.
 
@@
 %https://www.lucidchart.com/invitations/accept/c8768786-4a3f-4c78-b3c8-aa04a6b81d06
-%______________________________________________________________%
-
-%TODO: but we missed ICOs becasue they are high intensity usage in short period of time and does not include in the list of the most used ones.
-%
 
@@
 Although, no ICOs were spot in the list at the time it was retrieved, we will thoroughly discuss our analysis on how ICOs are highly vulnerable to front-running activities (see Section~\ref{sec:ICOsfrontrunning}).
-
-%TODO:
-%ICO is only in use when the time window is happenig.  this is based on the last 24hours activities 
-%justify why started with ICO and go to other apps . refrence to ICO section for actual justification
 
@@
 
-% can we talk about Velocity here? ~\cite{eskandari2017feasibility}
+% can we talk about Velocity here?
+~\cite{eskandari2017feasibility} As the smart contract is the entity that acts as the market maker on regular cases with high liquidity front-running of the option calls do not result in any advantages, however, in the case of low balance of smart contracts pool of funds, the front-runner can front-run others to use up the remaining of the funds and make the rest of the option calls fail.
 
@@
 
-As mentioned in Section~\ref{sec:Front Running on the Blockchains}, although front-running attacks have been more showcased in the context of decentralized exchanges and trading systems, they are not yet limited to the financial markets.
+As mentioned in Section~\ref{sec:Front Running on the Blockchains}, although front-running attacks have been more showcased in the context of decentralized exchanges and trading systems, they are not limited to the financial markets.
 Front-running can also occur within other (non-financial) blockchain applications such as naming systems.
@@
 These domains which can be resolved using any Ethereum web3 compatible browser.
-Although a sealed auction (\textit{startAuctionsAndBid}) is used while implementing the ENS, the deposit should be equal or bigger than the bid, this information leakage could be used to front-run the transaction with the same bid amount.
+Although a sealed auction (\textit{startAuctionsAndBid()}) is used in ENS implementation, the deposit should be equal or bigger than the bid, this information leakage could be used to front-run the transaction with the same bid amount or slightly higher to over bid the initial sealed bid.
 By doing so the front-runner invalidates the original bid and hence registers the domain name himself.
@@
 In Ghazal model, a user would register domain name by executing the \textit{registerdomain} function from the Ghazal smart contract with the domain name in plain text as the function argument.
-As mentioned before, These transactions will sit in the mempool so that it would be mined by Ethereum miners and included in the block.
+As mentioned before, These transactions will sit in the mempool to be mined by Ethereum miners in a block.
 During this period in which the transaction is not yet confirmed, front-running attack can occur by (i) dishonest miners and/or (ii) regular non-miner user.
@@
 A regular non-miner node in the Ethereum network can front-run other user's \textit{registerdomain} at a good profit by paying higher transaction fees.
-This practice allows the adversarial party  to register an unregistered domain immediately after someone searched for it, and sell the domain name to the users for a higher price.
 Note that, domain name front-running also occurs in the vanilla system.
@@
 
-\section{Cases of Front-running in ICOs}  %TODO Shayan: based on how we start the previous section (Cases of Front-running in DApps), rewrite the first paragraph of this section (just for coherency and unity) + try to have seperate subsection for each part to make it more compelling and interesting.
-\label{sec:ICOsfrontrunning}
+\section{Cases of Front-running in ICOs}  \label{sec:ICOsfrontrunning}
 
@@
 
-%TODO: make pie charts for each mining pool, all non-status-ico transactions vs success-ico-transactions vs failed-ico=transactions
+% make pie charts for each mining pool, all non-status-ico transactions vs success-ico-transactions vs failed-ico=transactions
 
@@
 
-\section{How to stop Front-running?} %We have have the applicability of the solutions inline.
+\section{How to stop Front-running?} %We have the applicability of the solutions inline.
 
@@
 Depending on the Dapp design, either the order is collateralized, which means the commitment transaction includes the funds required for fulfilling the order, which will leak some information about the order, or is not collateralized and opens up the possibility of user never revealing the commitment, which will be considered as a DoS attack.
-Another use of such commitment scheme, is in decentralized naming systems, such as Ghazal or ENS.
-In this case, a user would send a commit transaction similar to a sealed bid, once the transaction is confirmed and the grace period is over, user would send a reveal transaction revealing the bid and also the details of the requested domain.
+Another use of such commitment scheme, is in decentralized naming systems, such as Namecoin~\cite{kalodner2015empirical}, Ethereum Name Service (ENS) or Ghazal.
+In this case, a user sends a commit transaction, which commits to the name hash, similar to a sealed bid.
+Once the transaction is confirmed and the grace period is over, user sends a reveal transaction revealing the bid and also the details of the requested domain.
 Using this scheme, one is able to hide information from the adversarial parties in the system and prevent them from front-running.
@@
 %Proof of burn methods ?
-%TODO: research on more possible solutions!
 
@@
 
-% Could talk about a tool / a framework to detect front-running
+% Could talk about future work on a tool / a framework to detect front-running
 

### 2018-09-16 frontrunning/Latex/sections/paper.tex
[frontrunning] more edits

@@
 
-Further reading on the early details on the history and challenges of detecting and regulating front-running can be found in~\cite{markham1988front} . %add a more recent publication here as well!
+Further reading on the early details on the history and challenges of detecting and regulating front-running can be found in~\cite{markham1988front} . %add a more recent publication?
 
@@
 This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users.
+ERC20 is the interface standard for implementing tokens on top of Ethereum~\cite{erc20}.
 Smart Tokens can be bought and sold through the users smart contract at an automatically calculated price which displays supply and demand.
@@
 They implemented multiple caps --ceiling-- in which, each had a maximum amount that could be deposited in.
-In this case, every deposit was checked by the smart contract and the exceeding amount was refunded to the sender while the accepted amount was sent to their multisignature wallet address~\cite{statusicoanalysis}.
+In this case, every deposit was checked by the smart contract and the exceeding amount was refunded to the sender while the accepted amount was sent to their multi-signature wallet address~\cite{statusicoanalysis}.
 
@@
 Further study showed that some mining pools might have been manipulating the network for their own profit.
-In addition, there were many transactions sent with higher gas price to front-run other transactions, however these transactions were failing due to the restriction in the ICO smart contract to reject any transactions with higher than 50 \textit{GWei} gas price (as an attempt to prevent the known front-running behavior).
+In addition, there were many transactions sent with higher gas price to front-run other transactions, however these transactions were failing due to the restriction in the ICO smart contract to reject any transactions with higher than 50 \textit{GWei} gas price (as an attempt to prevent the known front-running behaviour).
 
@@
 Depending on the Dapp design, either the order is collateralized, which means the commitment transaction includes the funds required for fulfilling the order, which will leak some information about the order, or is not collateralized and opens up the possibility of user never revealing the commitment, which will be considered as a DoS attack.
-Another use of such commitment scheme, is in decentralized naming systems, such as Namecoin~\cite{kalodner2015empirical}, Ethereum Name Service (ENS) or Ghazal.
+Another use of such commitment scheme, is in decentralized naming systems, such as Namecoin, Ethereum Name Service (ENS) or Ghazal.
 In this case, a user sends a commit transaction, which commits to the name hash, similar to a sealed bid.
-Once the transaction is confirmed and the grace period is over, user sends a reveal transaction revealing the bid and also the details of the requested domain.
+Once the transaction is confirmed and the grace period is over, user sends a reveal transaction revealing the bid and also the details of the requested domain~\cite{kalodner2015empirical}.
 Using this scheme, one is able to hide information from the adversarial parties in the system and prevent them from front-running.

### 2018-09-17 frontrunning/Latex/sections/paper.tex
[frontrunning] edits till section 3

@@
 \section{Introduction}
+
 \label{sec:intro}
+
+% @J : intro needs lots of love.
 
@@
 
-\emph{Front-running} is analogous to any course of action during which a person benefits from prior access to inside or confidential market information about upcoming transactions and trades.
-This problem can occur in both financial and non-financial systems, however, it is more noticeable within the trading and exchange systems as was originated back in the stock markets.
-In the old times, all the trades were executed on papers, so in case of receiving a large order from a client, the broker might say this loud and other people around the table could be informed.
+\emph{Front-running} is analogous to any course of action during which a person or entity benefits from prior access to inside or confidential market information about upcoming transactions and trades, albeit the problem can occur in both financial and non-financial systems.
+In traditional exchanges, traders would gather in same phsycal locations to announce their position in the market, in case of receiving a large order from a client, the broker might say this loud and other people around the table could be informed.
 Therefore, a malicious trader would run in front of that order and put his own transaction in-between (before the trade was executed) and hence profit from the price increase of the stock.
-In fact, a group of market participants obtain non-public market information which allows them to front-run other user\'s trades by putting their orders ahead of those trades and benefit from advance knowledge of pending client orders.
+%In fact, a group of market participants obtain non-public market information which allows them to front-run other user\'s trades by putting their orders ahead of those trades and benefit from advance knowledge of pending client orders.
 The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty~\cite{liang2005distressed}.
@@
 
-Further reading on the early details on the history and challenges of detecting and regulating front-running can be found in~\cite{markham1988front} . %add a more recent publication?
+Further reading on the early details on the history and challenges of detecting and regulating front-running is extensively written by Markham~\cite{markham1988front} . %add a more recent publication?
 
-Initially the front-running policies only applied to certain option markets, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{finra_2002}, which then in 2012 with the new amendment, FINRA Rule 5270, the front-running rule was extended to cover trading in an option, derivative, or other financial instruments overlying a security with some exceptions~\cite{sec2012frontrunning, finra_2012}.
+Initially the front-running policies only applied to certain option markets, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{finra_2002},  then again in 2012 with the new amendment, FINRA Rule 5270, the front-running rule was extended to cover trading in options, derivatives, or other financial instruments overlying a security with a few exceptions~\cite{sec2012frontrunning, finra_2012}.
 
@@
 Blockchain technology has received an exceptional amount of attention since it was first introduced as the underlying technology of the cryptocurrency Bitcoin in 2008~\cite{nakamoto2008bitcoin}.
-Many decentralized applications that are built on top of this technology represent the significance of the blockchain as it completely eliminates the central point of failure within any systems.
-However, blockchains have some inherent characteristic that leave them vulnerable to \emph{front-running} behaviour.
-Although this data structure is known to be publicly visible to every network participants, information is layered and some of them are accessed only by insiders.
-Any network participants that runs a full node on the blockchain is able to obtain those information and as mentioned in Section~\ref{sec:What is front-running?}, this leaves the application vulnerable to front-running.
-Decentralized exchanges are a group of blockchain financial applications where front-running can be executed.
+Many decentralized applications that are built on top of this technology represent the significance of the blockchain as it completely eliminates the central point of failure within the systems.
+However, blockchains have some inherent characteristic that leave them vulnerable to information leaks and \emph{front-running} behaviour.
+Although this data structure is known to be publicly visible to every network participants, information is layered and some of them are easier accessed only by insiders.
+Any network participants that runs a full node on the blockchain is able to obtain those information and as mentioned in section~\ref{sec:What is front-running?}, this leaves the application vulnerable to front-running.
+%Decentralized exchanges are a group of blockchain financial applications where front-running can be executed.
 %____________________________________________________________________
@@
 ICO is a method to distribute tokens based on the deposits of the native coin, Ether in the case of Ethereum.
-After a few hacking incidents on high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered.
+After a few hacking incidents of high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered.
 This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to late comers on the open markets~\cite{zetzsche2018ico, li2018initial}.
@@
 This competition made ICOs a good opportunity for front-running attacks.
-In this paper we use multiple empirical examples to show possibility of front-running on DApps, for the sake of completeness, we use one incident on ICOs, and examples from the Top 25 DApps by recent user counts.
-%TODO: this last sentece is a bit weird here!
+In this paper we use multiple empirical examples to show possibility of front-running on DApps.
+For the sake of completeness, we use one incident on ICOs, and examples from the Top 25 DApps by recent user counts based on \texttt{DAppRadar.com} ranking.
 %____________________________________________________________________
@@
 
-Due to the novelty characteristics of the underlying technology (blockchains) and the issue of front-running, there are only a few research carried out on this subject in the context of blockchain and decentral ledgers.
+Due to the novelty characteristics of the underlying technology (blockchain), there are only a few research carried out on the issue of front-running in the context of blockchain and decentral ledgers.
 \\
 Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage~\cite{aune2017footprints}.
-As mentioned in Section~\ref{sec:What is front-running?}, the information leakage results the entire system to be vulnerable to the front-running.
+As mentioned in section~\ref{sec:What is front-running?}, the information leakage results the entire system to be vulnerable to the front-running.
 They also propose a cryptographic approach, similar to commit and reveal(~\ref{CommitmentScheme}), to prevent front-running in decentral systems.
@@
 Upon submitting the bug bounty to the Hydra smart contract, one can front-run the bug report and claim the bounty instead of the original reporter.
-In order to mitigate this issue they proposed \textit{Submarine Commitments} (~\ref{submarineCommits}).
+In order to mitigate this issue they proposed \textit{Submarine Commitments} which we discuss further in section~\ref{submarineCommits}.
 

### 2018-09-17 frontrunning/Latex/sections/paper.tex
[frontrunning] edits till section 4

@@
 In general, all the network participants have the ability to front-run specific transactions that are sent to the network.
-However, miners can include any transactions they like into the block they attempt to mine.
+Also, miners can include any transactions they like into the block they attempt to mine.
 Thus, they possess special power in terms of front-running as opposed to other users of the network.
@@
 On the Ethereum blockchain, users have to pay for the computations in small amount of Ether called \textit{gas}~\cite{AccountT67:online}.
-The price that users pay for transactions (a.k.a.
-transaction fees) can increase or decrease how quickly miners will execute them and include them within the blocks they mine.
-This is because the Ethereum miners consume resources to process the transactions and so receive the transaction fees after creating the blocks.
+The price that users pay for transactions, \textit{gasPrice}, can increase or decrease how quickly miners will execute them and include them within the blocks they mine.
 Once seeing two identical transactions with different transaction fees, a rational miner will prioritize the transaction that pays higher gas price per unit of gas --gasPrice--, this is due to limited space in the blocks while maximizes their profit in the block they mine.
-Therefore, any regular users who run a full-node Ethereum client can front-run pending transactions by sending similar transaction with higher gas price, see Figure~\ref{fig:RegularFrontrunning}.
+Therefore, any regular users who run a full-node Ethereum client can front-run pending transactions by sending similar transaction with higher gas price, see figure~\ref{fig:RegularFrontrunning}.
 For example, in a decentral exchange, he can monitor the network and once seeing a pending \textit{buy} transaction which will further increase the price of the asset, a front-runner can send a transaction with a higher gas price and hope to have his transaction mined ahead of the original pending transaction.
@@
 Note that in this case, blockchain front-runners are visible to the network as they broadcast their transactions to all the network participants.
+The probability of success in such attach can be increased by flooding the network by transactions with higher than average gasPrice.
 
@@
 \subsubsection{Miners} \label{minersfrontrunning}
-Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this is known as \textbf{transaction reordering} attack.
+Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this in case of malicious reordering is known as \textbf{transaction reordering} attack.
 For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token\ie TKN, presumably if this transaction goes through, it causes the price of the purchased token to increase.
 So the dishonest miner can step in front of this transaction and place his own buy order ahead.
-He would simply create his \textit{buy} of 1000 TKN and include it in front of the previous \textit{buy} transaction of 1000 TKN in the block he mines.
-Doing so, he would receive a better rate than other network users, and afterwards can sell the assets he has bought and gain a price advantage at the expense of others.
-Similarly, a dishonest miner can sell his tokens in front, if he sees a pending \textit{sell} transaction.
-In an open source blockchain application, there is no rules on how transactions must be ordered and miners are free to mine transactions in any order they prefer.
-However, miners can only front-run transactions within the blocks they happen to mine.
-They could do this also by not broadcasting their own transactions to the network, this makes the miners to be less noticeable to the network when front-running.
+He would simply create his \textit{buy} of 1000 TKN and include it in front of the previous \textit{buy} transaction in the block he mines.
+Doing so, he would receive a better rate than other network users, and afterwards can sell the assets he has bought and gain a price advantage.
+It should be noted that miners can only front-run transactions within the blocks they happen to mine.
+They could do this also by not broadcasting their own transactions to the network before including it in the block, this makes the miners to be less noticeable to the network when front-running.
 Another example here is in the case of decentral exchanges and order cancellation.
@@
 In this case, when user decides that her order is not profitable anymore, she would send a cancelation transaction.
-Here the miner sees the cancelation transaction and puts his own order in front of the cancellation transaction --transaction reordering-- to fill the order, potentially profiting from the order.
-They can also include the canceled transaction in their block to collect the full gas limit used by that transaction~\cite{CostofDecentralization:online}, see Figure~\ref{fig:MinerFrontrunning}.
+Here the miner sees the cancelation transaction and puts his own transaction to fill that order in front of the cancellation transaction --transaction reordering--, potentially profiting from the order.
+He can also include the canceled transaction in the block to collect the full gas limit used by the cancel transaction~\cite{CostofDecentralization:online}, see figure~\ref{fig:MinerFrontrunning}.
 Front-running can also occur in non-financial smart contracts.
@@
 \includegraphics[width=0.7\linewidth]{figures/Miner_reorder_frontrun.png}
-\caption{The adversarial miner can monitor the Ethereum mempool for decentral exchange cancel orders and upon seeing the cancellation transaction, he puts his buy order before ahead.
-Doing so, the miner can profit from the underlying trade and also get the Gas included in the cancel transaction.
+\caption{The adversarial miner can monitor the Ethereum mempool for decentral exchange cancel orders and upon seeing the cancellation transaction, he puts his buy order prior to the cancel transaction.
+Doing so, the miner can profit from the underlying trade and also get the gas included in the cancel transaction.
 \label{fig:MinerFrontrunning}}

### 2018-09-17 frontrunning/Latex/sections/paper.tex
[frontrunning] edits till 4.2

@@
 
-\subsection{Blockchain Front-running} % for the unity of the paper, the previous title : How are Blockchain Applications Vulnerable to Front-running?
-is changed to "Blokcchain front-running", in this case the other section's name (on blockchain frontrunning, where we talk about miner and non miner frontrunning) needs to change to sth different and more descriptive.
-\label{sec:Front Running on the Blockchains}
+\subsection{Blockchain Front-running} \label{sec:Front Running on the Blockchains}
+
+% everything that has a line up , someone can jump in the line and front-run
 
@@
 
-As mentioned in the Section~\ref{sec:intro}, for the purpose of this research we retrieved the top 25 DApps based on recent user activities from \footnote{List of decentralized applications \url{https://dappradar.com/dapps}} in the first week of September 2018.
+As mentioned in the Section~\ref{sec:intro}, for the purpose of this research we retrieved the top 25 DApps based on recent user activities from \texttt{DAppradar.com}\footnote{List of decentralized applications \url{https://dappradar.com/dapps}} in the first week of September 2018.
 We then categorize these applications into 4 principal groups of decentral applications (see Table~\ref{tab:top25dapps}).
 In this section, we take a deep look into one or two decentral applications from each category and pinpoint the technical details of front-running issue on each case.
-Although, no ICOs were spot in the list at the time it was retrieved, we will thoroughly discuss our analysis on how ICOs are highly vulnerable to front-running activities (see Section~\ref{sec:ICOsfrontrunning}).
+Although, no ICOs were spotted in the list at the time it was retrieved, we will thoroughly discuss our analysis on how ICOs are highly vulnerable to front-running activities (see Section~\ref{sec:ICOsfrontrunning}).
 
@@
 
-% everything that has a line up , someone can jump in the line and front-run
+%______________________________________________________________%
+\subsection{Markets and Exchanges.} \label{sec:frontrunningExchanges}
+
 % talk about velocity that seems to be not front-runnable but because of of the liquidity pool limitation, there can be an order that consumes the last chunk of liquidity "edge case" , to front run others and make their "option calls" fail
@@
 
-% maybe inlcude 0xbitcoin ERC721 mineable tokens front-running!
-% mint: https://etherscan.io/tx/0x9883bc3ad018fd2b649982f88fbad7dc5abcb8f11c4f1d87ef814ba30c2b3428
-%______________________________________________________________%
-\subsection{Markets and Exchanges.} \label{sec:frontrunningExchanges}
-
-Exchanges such as EtherDelta\footnote{also known as ForkDelta for the UI \url{https://forkdelta.app/}}, are closest form to decentral exchanges, however their order books are stored on a central server they control and shown on their user interface (website).
+Exchanges such as EtherDelta\footnote{also known as ForkDelta for the UI \url{https://forkdelta.app/}}, are closest implementation to decentral exchanges, however their order books are stored on a central server they control and shown on their user interface (website).
 Other than the fact that they can re-order or censor the orders on their servers, there are other risks of front-running nature in these designs.
-Similarly 0xProtocol uses \textit{Relayers} which act as the orderbook holders and are not prune to cheating.
-One main issue with these exchanges is \textit{cancellation grief}.
+Similarly 0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the orderbook holders and are not prune to cheating.
+One main issue with these designs is the \textit{cancellation grief}.
 Although the orderbooks are not in the smart contract, in order to prevent denial of service attacks, user needs to send a transaction to cancel her order.
 In this case, when an adversarial actor sees the cancellation transaction, he sends a fill order transactions with higher gasPrice to get in front of the cancellation order and take the order before it is cancelled.
-As mentioned in ~\ref{minersfrontrunning}, miners are in a better control to perform such attack.
+As mentioned in ~\ref{minersfrontrunning}, miners are in a better position to perform such attack.
 
@@
 Doing so, Bancor protocol provides continuous liquidity for digital assets without relying on an order book as there is no requirement to match sellers and buyers.
-Recently, researchers have shown that Bancor is vulnerable to front running attacks.
-Implemented on the Ethereum blockchain, when Bancor transactions are broadcast to the network, they sit in a pending transaction pool known as \textit{mempool} waiting for the miners to mine them.
-Since Bancor handles all the trades and exchanges on the Ethereum blockchain (unlike other existing decentralized exchanges), these transactions are all visible to the public for 16s (the average Ethereum blocktime) before being included within a block.
-This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favorable profits~\cite{BancorIs7:online}.
-As mentioned in Section~\ref{sec:who can front-run?} and same as every other Ethereum based application, Bancor transactions can be front run by miners and other regular (non-miner) users.
-There is an implementation of a Bancor front running attack in the Python programming language which represent how a non-miner user can front run other network participants~\cite{NewTab13:online}.
+Implemented on the Ethereum blockchain, when transactions are broadcast to the network, they sit in a pending transaction pool known as \textit{mempool} waiting for the miners to mine them.
+Since Bancor handles all the trades and exchanges on the Ethereum blockchain (unlike other existing decentralized exchanges), these transactions are all visible to the public for some time before being included within a block.
+This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favourable profits~\cite{BancorIs7:online}.
+Researchers have shown and implemented proof of concept code to front-run Banco as a regular non-miner user~\cite{NewTab13:online}.
+
 %______________________________________________________________%

### 2018-09-17 frontrunning/Latex/sections/paper.tex
[frontrunning] edits till section 5

@@
 
-As mentioned in Section~\ref{sec:Front Running on the Blockchains}, although front-running attacks have been more showcased in the context of decentralized exchanges and trading systems, they are not limited to the financial markets.
-Front-running can also occur within other (non-financial) blockchain applications such as naming systems.
-Recently, many blockchain-based domain registrars have been designed and implemented to eliminate the role of central parties \ie domain name system (DNS) which itself introduces single point of failures in the entire web.
+Front-running can also occur within non-financial blockchain applications such as naming systems.
+Recently, many blockchain-based domain registrars have been designed and implemented to eliminate the role of central parties \ie domain name system (DNS) which itself introduced single point of failures to the entire web.
 Ethereum Name Service (ENS)\footnote{\url{https://ens.domains/}}, is the most popular decentral naming service that uses a sealed auction to facilitate the procedures of purchasing new \texttt{.eth} domain names.
-These domains which can be resolved using any Ethereum web3 compatible browser.
-Although a sealed auction (\textit{startAuctionsAndBid()}) is used in ENS implementation, the deposit should be equal or bigger than the bid, this information leakage could be used to front-run the transaction with the same bid amount or slightly higher to over bid the initial sealed bid.
+Although sealed auction method is used in ENS implementation, the normal work flow uses \textit{startAuctionsAndBid()} with the deposit equal or higher than the bid, this information leakage could be used to front-run the transaction with the same bid amount or slightly higher to out bid the initial sealed bid.
 By doing so the front-runner invalidates the original bid and hence registers the domain name himself.
 Ghazal is another Ethereum-based naming system that allows users to register \texttt{.ghazal} domain names and bind certificates to those names~\cite{moosavighazal}.
-In Ghazal model, a user would register domain name by executing the \textit{registerdomain} function from the Ghazal smart contract with the domain name in plain text as the function argument.
-As mentioned before, These transactions will sit in the mempool to be mined by Ethereum miners in a block.
-During this period in which the transaction is not yet confirmed, front-running attack can occur by (i) dishonest miners and/or (ii) regular non-miner user.
-In the first case, a miner would intercept the \textit{registerdomain} transaction and register that name ahead of the user.
-A regular non-miner node in the Ethereum network can front-run other user's \textit{registerdomain} at a good profit by paying higher transaction fees.
-Note that, domain name front-running also occurs in the vanilla system.
-In this case, front-runners would monitor and identify domain names of interest, and sell it back to the other users with a higher price~\cite{sac022en33:online}.
-Front-running practice can happen in the traditional domain name system (DNS) as well.
-Domain name registrars can steal available domain names once seeing a query from users that looks up that domain's availability.
+As Ghazal is using a registration method in plain text, it is susceptible to front-running.
+Note that front-running domain names has been a subject of discussion outside the context of blockchian applications before~\cite{sac022en33:online}.
+Domain name registrars can steal available domain names upon seeing a query from an interested user for the availability of the domain.
 In this case, the registrar can register the domain name ahead and sell it back to the user for a higher price.
@@
 
-Crypto-Collectibles, also known as ERC-721 Non-Fungible Token Standard~\cite{erc721}, are one of the applications of Ethereum blockchain.
-Cryptokitties is known to be one of the first and the most popular use cases of ERC721 tokens~\cite{cryptokitties}.
-Their market cap reached more than 6 million dollars in the first months their launch.
+Crypto-Collectibles, also known as \textit{ERC-721 Non-Fungible Token Standard}~\cite{erc721}, are one of the applications of Ethereum blockchain.
+Cryptokitties are known to be one of the first and the most popular use cases of ERC721 tokens~\cite{cryptokitties}.
+Their market cap reached more than 6 million dollars in the first few months their launch, however declined soon after.
 Crypto-Collectibles, are similar to ERC-20 tokens and can be listed on exchanges.
@@
 
-As an example Cryptokitties can be bred, bought or sold through the main interface\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}}. See Figure~\ref{fig:cryptokittie}.
+As an example Cryptokitties can be bred, bought or sold through the main interface\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}}. %see Figure~\ref{fig:cryptokittie}.
 To buy a cryptokittie, user sends a bid transaction \textit{bid(uint256 \_tokenId)} containing the cryptokittties ID which can be found either on their website or on the ERC721 token smart contract.
@@
 \centering
-\includegraphics[width=0.4\linewidth]{figures/cryptokittie842912.png}
+\includegraphics[width=0.3\linewidth]{figures/cryptokittie842912.png}
 \caption{ Cryptokitty Number 842912 \label{fig:cryptokittie}}
@@
 Due to deterministic nature of blockchains, running gambling games based on randomness is close to impossible.
-There had been attempts to use block headers or such as the seed to randomness but almost all have failed as every data accessible to the smart contract at the time of execution, is also accessible to other smart contracts and they could predict the output on the run, thus prone to front-running and miner's manipulation.
+There had been attempts to use block headers or such as the seed to randomness but almost all have failed as every data accessible to the smart contract at the time of execution, is also accessible to other smart contracts and they could predict the output on the run, thus prone to front-running and miner\'s manipulation.
 Many infamous gambling games are now running on Ethereum network and front-running them requires a level of sophistication and knowledge of the internal of the games and Ethereum.\\
 One of the most popular smart contracts on Ethereum blockchain belongs to a controversial gambling game named \texttt{Fomo3d}, also known as \textit{Exit Scam}\footnote{\url{https://exitscam.me/play}}.
-The aim of this game is to be the last person purchasing the key when the time goes to zero in which every ticket purchase increases the timer by 30 seconds.
-It was believed that because of the nature of the game, it will never end, however on August 22, 2018 the first round of the game ended and the winner took 10,469 Ether\footnote{First winner of Fomo3D, won 10,469 Ether \url{ https://etherscan.io/tx/0xe08a519c03cb0aed0e04b33104112d65fa1d3a48cd3aeab65f047b2abce9d508}}, equivalent to 2.1 Million dollars on the time of writing.
+The aim of this game is to be the last person purchasing the key when the timer goes to zero in which every ticket purchase increases the timer by 30 seconds.
+It was believed that because of the nature of the game, it will never end, however on August 22, 2018 the first round of the game ended and the winner taking 10,469 Ether\footnote{First winner of Fomo3D, won 10,469 Ether \url{ https://etherscan.io/tx/0xe08a519c03cb0aed0e04b33104112d65fa1d3a48cd3aeab65f047b2abce9d508}}, equivalent to 2.1 Million dollars on the time of writing.
 It is believed that the winner, used a sophisticated approach to finish last~\cite{fomo3dhacker}, we call this approach \textit{Denial-of-service Front-running}.

### 2018-09-17 frontrunning/Latex/setup/table.tex
[frontrunning] minor fix to the table

@@
 \multirow{6}{*}{Exchanges} 										& IDEX (1) \\ 
-															& \textit{ForkDelta, EtherDelta (2)} \\
-															& \textit{Bancor (7)} \\
+															& \textit{ForkDelta, EtherDelta}(2) \\
+															& \textit{Bancor}(7) \\
 															& The Token Store(13) \\
 															& LocalEthereum(14) \\
-															& 0x Protocol (23) \\
+															& \textit{0x Protocol}(23) \\
 															& Kyber (22) \\  \hline
 
-\multirow{9}{*}{\shortstack{Crypto-Collectible \\ Games \\ (ERC 721)}}		& \textit{CryptoKitties (3)} \\  
+\multirow{9}{*}{\shortstack{Crypto-Collectible \\ Games \\ (ERC 721)}}		& \textit{CryptoKitties}(3) \\  
 															& Ethermon(4)\\
@@
 
-\multirow{8}{*}{Gambling}											& Fomo3D (5) \\  
+\multirow{8}{*}{Gambling}											& \textit{Fomo3D} (5) \\  
 															& DailyDivs (6) \\ 
@@
 
-\multirow{1}{*}{Name Services}									& \textit{Ethereum Name Service (24)}  \\  \hline
+\multirow{1}{*}{Name Services}									& \textit{Ethereum Name Service}(24)  \\  \hline
 

### 2018-09-17 frontrunning/Latex/sections/paper.tex
[frontrunning] grammar(ly) fixes

@@
 The concept of the \emph{front-running} is decades old starting with early financial markets.
-Initially the traders required to be physically available in the exchange office to deliver the bids and offers, and some traders, in the knowledge of future market change, could run in front of the others to get their orders ahead of the change in the market to profit from the price change.
-Clearly in such scenarios front-running was possible yet not detectable as a damaging activity.
-However, with the rapid advances of the technology in the last few decades, trading is not carried out in person anymore, new form of front-running is feasible through high speed networks.
+Initially, the traders required to be physically available in the exchange office to deliver the bids and offers, and some traders, in the knowledge of future market change, could run in front of the others to get their orders ahead of the change in the market to profit from the price change.
+Clearly, in such scenarios front-running was possible yet not detectable as a damaging activity.
+However, with the rapid advances of the technology in the last few decades, trading is not carried out in person anymore, a new form of front-running is feasible through high-speed networks.
 Furthermore, Blockchain technology has introduced transparency and open markets and leads to a new era of front-running which inherently affects all decentral applications, whether financial or non-financial.
 Arbitrage and Censorship, are also issues that have been linked to front-running attacks on blockchain \textit{(We need to talk about why these two are left out of the scope of this paper)}.
-Currently, there are quite a few decentral applications built on the blockchains, so in order for us to perform a thorough study on blockchain application front-running, we set a s specific criteria by using the top 25 decentral applications which have the highest recent user activities.\footnote{List of decentralized applications \url{https://dappradar.com/dapps}} Using this criteria, we successfully categorized these decentral applications into 4 principal categories on which we conduct our analysis.
+Currently, there are quite a few decentral applications built on the blockchains, so in order for us to perform a thorough study on blockchain application front-running, we set a specific criteria by using the top 25 decentral applications which have the highest recent user activities.\footnote{List of decentralized applications \url{https://dappradar.com/dapps}} Using this criteria, we successfully categorized these decentral applications into 4 principal categories on which we conduct our analysis.
 Surprisingly, there was no ICO (initial coin offering) included in the top 25 Dapps list by the time we fetched the data from the website.
-We believe the reason is because the ICOs are inherently different from other groups of Daaps as they are merely highly active during their offering periods and their user activity drops dramatically after the offerings period are over.
-Therefore, we  consider ICOs as another cases on which the front-running should be investigated (although they are not listed in the top 25 Dapps we use) \footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".}
+We believe the reason is that the ICOs are inherently different from other groups of Daaps as they are merely highly active during their offering periods and their user activity drops dramatically after the offerings period are over.
+Therefore, we  consider ICOs as other cases on which the front-running should be investigated (although they are not listed in the top 25 Dapps we use) \footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".}
 
@@
 Tokenization mushroomed to a whole ecosystem of tokenized applications on the blockchain, these applications inherently become a market as tokens are in the core of them.
-We started looking at some of these applications, in specific \textit{Bancor}~\cite{hertzog2017bancor}, to look into possible issues rising from these new models.
+We started looking at some of these applications, in specific \textit{Bancor}~\cite{hertzog2017bancor}, to look into possible issues arising from these new models.
 Transparency of blockchains, although being a good feature of them, opens up these markets to some attack vectors that might not be visible on the time of the application design, one main attack is known as \textbf{front-running}, whether financial or non-financial.
-Arbitrage and Censorship, are also issues arises from the designs on the blockchain technology and had been linked to front-running attacks, hence we use the term \textit{front-running] losely to talk about any transaction manupulation with the intention of getting other transactions in before the original transaction takes place.
-In this paper, our focus is to have a complete overview of front-running on the blockchain while analysing Bancor issues.
-While looking at the possibility of front-running on other applications, we found interesting case studies that affects most of the top 25 decentral applications on Ethereum blockchain.
+Arbitrage and Censorship, are also issues arises from the designs on the blockchain technology and had been linked to front-running attacks, hence we use the term \textit{front-running] loosely to talk about any transaction manipulation with the intention of getting other transactions in before the original transaction takes place.
+In this paper, our focus is to have a complete overview of front-running on the blockchain while analyzing Bancor issues.
+While looking at the possibility of front-running on other applications, we found interesting case studies that affect most of the top 25 decentral applications on Ethereum blockchain.
 
@@
 \emph{Front-running} is analogous to any course of action during which a person or entity benefits from prior access to inside or confidential market information about upcoming transactions and trades, albeit the problem can occur in both financial and non-financial systems.
-In traditional exchanges, traders would gather in same phsycal locations to announce their position in the market, in case of receiving a large order from a client, the broker might say this loud and other people around the table could be informed.
+In traditional exchanges, traders would gather in same physical locations to announce their position in the market, in case of receiving a large order from a client, the broker might say this loud and other people around the table could be informed.
 Therefore, a malicious trader would run in front of that order and put his own transaction in-between (before the trade was executed) and hence profit from the price increase of the stock.
-%In fact, a group of market participants obtain non-public market information which allows them to front-run other user\'s trades by putting their orders ahead of those trades and benefit from advance knowledge of pending client orders.
+%In fact, a group of market participants obtain non-public market information which allows them to front-run other user\'s trades by putting their orders ahead of those trades and benefit from the advance knowledge of pending client orders.
 The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty~\cite{liang2005distressed}.
@@
 \subsection{Literature on Traditional Front-running}\label{traditionalFrontrunning}
-As traditional front-running has been the subject of discussion for decades, there are many literatures on this subject.
+As traditional front-running has been the subject of discussion for decades, there are many works of literature on this subject.
 Here we focus on the historical context and how the regulations evolved to be what they are today.\\
@@
 \begin{quote}
-The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.
+The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.
 ~\cite{sec1978optionsmarket}
@@
 14156, November 19, 1977, (Letter from George A.
-Fitzsimmons, Secretary, Securities and Exchange Commission to Joseph W.
+Fitzsimmons, Secretary, Securities, and Exchange Commission to Joseph W.
 Sullivan, President  CBoE).}
@@
 \textit{CBoE} and other exchanges (and brokers) issued educational circulars for their members asserting that front-running violates existing rules, with some examples of what is considered front-running.
-However difference of opinion regarding the unfairness of front-running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~cite{sec1978optionsmarket}.
+However, the difference of opinion regarding the unfairness of front-running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~cite{sec1978optionsmarket}.
 
@@
 
-% everything that has a line up , someone can jump in the line and front-run
+% everything that has a lineup, someone can jump in the line and front-run
 
@@
 Many decentralized applications that are built on top of this technology represent the significance of the blockchain as it completely eliminates the central point of failure within the systems.
-However, blockchains have some inherent characteristic that leave them vulnerable to information leaks and \emph{front-running} behaviour.
+However, blockchains have some inherent characteristic that leaves them vulnerable to information leaks and \emph{front-running} behaviour.
 Although this data structure is known to be publicly visible to every network participants, information is layered and some of them are easier accessed only by insiders.
-Any network participants that runs a full node on the blockchain is able to obtain those information and as mentioned in section~\ref{sec:What is front-running?}, this leaves the application vulnerable to front-running.
+Any network participants that runs a full node on the blockchain is able to obtain that information and as mentioned in section~\ref{sec:What is front-running?}, this leaves the application vulnerable to front-running.
 %Decentralized exchanges are a group of blockchain financial applications where front-running can be executed.
@@
 %%% The following chunk seem to be redundant and weird. Should we keep it?? 
-Bancor \cite{hertzog2017bancor} is an example of such systems in which front-runners benefit from potential price increase of the market stocks (details are provided in~\ref{sec:frontrunningExchanges}).
+Bancor \cite{hertzog2017bancor} is an example of such systems in which front-runners benefit from the potential price increase of the market stocks (details are provided in~\ref{sec:frontrunningExchanges}).
 Decentralized namespaces, as blockchain non-financial applications, are another example.
@@
 After a few hacking incidents of high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered.
-This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to late comers on the open markets~\cite{zetzsche2018ico, li2018initial}.
+This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to latecomers on the open markets~\cite{zetzsche2018ico, li2018initial}.
 ICOs started to experiment with different fair capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}.
 This competition made ICOs a good opportunity for front-running attacks.
-In this paper we use multiple empirical examples to show possibility of front-running on DApps.
+In this paper, we use multiple empirical examples to show the possibility of front-running on DApps.
 For the sake of completeness, we use one incident on ICOs, and examples from the Top 25 DApps by recent user counts based on \texttt{DAppRadar.com} ranking.
@@
 Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage~\cite{aune2017footprints}.
-As mentioned in section~\ref{sec:What is front-running?}, the information leakage results the entire system to be vulnerable to the front-running.
+As mentioned in section~\ref{sec:What is front-running?}, the information leakage results in the entire system to be vulnerable to the front-running.
 They also propose a cryptographic approach, similar to commit and reveal(~\ref{CommitmentScheme}), to prevent front-running in decentral systems.
-%In this approach, which is similar to commit and reveal , a transaction hash (fingerprint) is broadcast to the network to secure time priority while not revealing the information.
+%In this approach, which is similar to commit and reveal, a transaction hash (fingerprint) is broadcast to the network to secure time priority while not revealing the information.
 Once the hash is processed and assigned an index and timestamp, the transaction details are broadcast.
@@
 Malinova and Park discuss different design settings for financial markets and trading platforms on decentral ledgers~\cite{malinova2017market}.
-They argue that blockchain brings a new options of transparency which affects traders behaviour, specially in the presence of intermediary front-runners.
+They argue that blockchain brings new options of transparency which affects traders behaviour, especially in the presence of intermediary front-runners.
 They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make front-running costly and inefficient.
@@
 
-One of the properties of Blockchain technology was to overcome double-spend, however this does not apply for fast payments and zero-confirmation transactions.
+One of the properties of Blockchain technology was to overcome double-spend, however, this does not apply for fast payments and zero-confirmation transactions.
 \textit{Double-spend attack}, as the name implies, the adversary spends a coin more than one time.
@@
 
-Blockchain, as a secure ledger, gives the impression of ultimate secure platform for decentral applications and one might not consider implementing the application with security in mind.
+Blockchain, as a secure ledger, gives the impression of an ultimate secure platform for decentral applications and one might not consider implementing the application with security in mind.
 In general, all the network participants have the ability to front-run specific transactions that are sent to the network.
@@
 \subsubsection{Blockchain Participants}
-Any regular (miner or non-miner) user can front-run other transactions in the network.
+Any regular (miner or non-miner) the user can front-run other transactions in the network.
 For regular users to front-run others on the blockchain, they need to be well connected to other nodes on the network.
 Doing so, they are able to listen to the network and monitor all transactions that are broadcast.
-On the Ethereum blockchain, users have to pay for the computations in small amount of Ether called \textit{gas}~\cite{AccountT67:online}.
+On the Ethereum blockchain, users have to pay for the computations in a small amount of Ether called \textit{gas}~\cite{AccountT67:online}.
 The price that users pay for transactions, \textit{gasPrice}, can increase or decrease how quickly miners will execute them and include them within the blocks they mine.
-Once seeing two identical transactions with different transaction fees, a rational miner will prioritize the transaction that pays higher gas price per unit of gas --gasPrice--, this is due to limited space in the blocks while maximizes their profit in the block they mine.
+Once seeing two identical transactions with different transaction fees, a rational miner will prioritize the transaction that pays a higher gas price per unit of gas --gasPrice--, this is due to limited space in the blocks while maximizes their profit in the block they mine.
 Therefore, any regular users who run a full-node Ethereum client can front-run pending transactions by sending similar transaction with higher gas price, see figure~\ref{fig:RegularFrontrunning}.
@@
 He would simply create his \textit{buy} of 1000 TKN and include it in front of the previous \textit{buy} transaction in the block he mines.
-Doing so, he would receive a better rate than other network users, and afterwards can sell the assets he has bought and gain a price advantage.
+Doing so, he would receive a better rate than other network users, and afterward can sell the assets he has bought and gained a price advantage.
 It should be noted that miners can only front-run transactions within the blocks they happen to mine.
-They could do this also by not broadcasting their own transactions to the network before including it in the block, this makes the miners to be less noticeable to the network when front-running.
+They could do this also by not broadcasting their own transactions to the network before including it in the block, this makes the miners be less noticeable to the network when front-running.
 Another example here is in the case of decentral exchanges and order cancellation.
 Every exchange should have the functionality to cancel the orders, especially for a volatile market.
-In this case, when user decides that her order is not profitable anymore, she would send a cancelation transaction.
+In this case, when the user decides that her order is not profitable anymore, she would send a cancelation transaction.
 Here the miner sees the cancelation transaction and puts his own transaction to fill that order in front of the cancellation transaction --transaction reordering--, potentially profiting from the order.
@@
 Front-running can also occur in non-financial smart contracts.
-As an example, smart contract which adds all the participants to a party invite list, could only be closed by the smart contract owner.
-In this case when the owner sends the transaction to close the list, a miner can include his own list of participants before the close transaction in the block he mines.
+As an example, a smart contract which adds all the participants to a party invite list could only be closed by the smart contract owner.
+In this case, when the owner sends the transaction to close the list, a miner can include his own list of participants before the close transaction in the block he mines.
 This is an issue with the design of the smart contracts and is known as transaction-ordering dependence vulnerability~\cite{luu2016making}.
@@
 In this section, we take a deep look into one or two decentral applications from each category and pinpoint the technical details of front-running issue on each case.
-Although, no ICOs were spotted in the list at the time it was retrieved, we will thoroughly discuss our analysis on how ICOs are highly vulnerable to front-running activities (see Section~\ref{sec:ICOsfrontrunning}).
+Although no ICOs were spotted on the list at the time it was retrieved, we will thoroughly discuss our analysis of how ICOs are highly vulnerable to front-running activities (see Section~\ref{sec:ICOsfrontrunning}).
 
@@
 
-% talk about velocity that seems to be not front-runnable but because of of the liquidity pool limitation, there can be an order that consumes the last chunk of liquidity "edge case" , to front run others and make their "option calls" fail
+% talk about velocity that seems to be not front-runnable but because of the liquidity pool limitation, there can be an order that consumes the last chunk of liquidity ``edge case'', to front run others and make their "option calls" fail
 
@@
 
-Exchanges such as EtherDelta\footnote{also known as ForkDelta for the UI \url{https://forkdelta.app/}}, are closest implementation to decentral exchanges, however their order books are stored on a central server they control and shown on their user interface (website).
+Exchanges such as EtherDelta\footnote{also known as ForkDelta for the UI \url{https://forkdelta.app/}}, is the closest implementation to decentral exchanges, however their order books are stored on a central server they control and shown on their user interface (website).
 Other than the fact that they can re-order or censor the orders on their servers, there are other risks of front-running nature in these designs.
-Similarly 0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the orderbook holders and are not prune to cheating.
+Similarly 0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the order book holders and are not prone to cheating.
 One main issue with these designs is the \textit{cancellation grief}.
-Although the orderbooks are not in the smart contract, in order to prevent denial of service attacks, user needs to send a transaction to cancel her order.
-In this case, when an adversarial actor sees the cancellation transaction, he sends a fill order transactions with higher gasPrice to get in front of the cancellation order and take the order before it is cancelled.
-As mentioned in ~\ref{minersfrontrunning}, miners are in a better position to perform such attack.
+Although the order books are not in the smart contract, in order to prevent denial of service attacks, the user needs to send a transaction to cancel her order.
+In this case, when an adversarial actor sees the cancellation transaction, he sends a fill order transactions with higher gasPrice to get in front of the cancellation order and take the order before it is canceled.
+As mentioned in ~\ref{minersfrontrunning}, miners are in a better position to perform such an attack.
 
@@
 Bancor is another Ethereum-based application that allows users to exchange their tokens without any counter-party risk.
-This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users.
+This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that is always available to users.
 ERC20 is the interface standard for implementing tokens on top of Ethereum~\cite{erc20}.
@@
 Since Bancor handles all the trades and exchanges on the Ethereum blockchain (unlike other existing decentralized exchanges), these transactions are all visible to the public for some time before being included within a block.
-This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favourable profits~\cite{BancorIs7:online}.
-Researchers have shown and implemented proof of concept code to front-run Banco as a regular non-miner user~\cite{NewTab13:online}.
+This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favorable profits~\cite{BancorIs7:online}.
+Researchers have shown and implemented a proof of concept code to front-run Banco as a regular non-miner user~\cite{NewTab13:online}.
 
@@
 Front-running can also occur within non-financial blockchain applications such as naming systems.
-Recently, many blockchain-based domain registrars have been designed and implemented to eliminate the role of central parties \ie domain name system (DNS) which itself introduced single point of failures to the entire web.
+Recently, many blockchain-based domain registrars have been designed and implemented to eliminate the role of central parties \ie domain name system (DNS) which itself introduced the single point of failures to the entire web.
 Ethereum Name Service (ENS)\footnote{\url{https://ens.domains/}}, is the most popular decentral naming service that uses a sealed auction to facilitate the procedures of purchasing new \texttt{.eth} domain names.
-Although sealed auction method is used in ENS implementation, the normal work flow uses \textit{startAuctionsAndBid()} with the deposit equal or higher than the bid, this information leakage could be used to front-run the transaction with the same bid amount or slightly higher to out bid the initial sealed bid.
+Although sealed auction method is used in ENS implementation, the normal workflow uses \textit{startAuctionsAndBid()} with the deposit equal or higher than the bid, this information leakage could be used to front-run the transaction with the same bid amount or slightly higher to outbid the initial sealed bid.
 By doing so the front-runner invalidates the original bid and hence registers the domain name himself.
@@
 
-Crypto-Collectibles, also known as \textit{ERC-721 Non-Fungible Token Standard}~\cite{erc721}, are one of the applications of Ethereum blockchain.
+Crypto-Collectibles, also known as \textit{ERC-721 Non-Fungible Token Standard}~\cite{erc721}, is one of the applications of Ethereum blockchain.
 Cryptokitties are known to be one of the first and the most popular use cases of ERC721 tokens~\cite{cryptokitties}.
-Their market cap reached more than 6 million dollars in the first few months their launch, however declined soon after.
+Their market cap reached more than 6 million dollars in the first few months their launch, however, declined soon after.
 Crypto-Collectibles, are similar to ERC-20 tokens and can be listed on exchanges.
@@
 As an example Cryptokitties can be bred, bought or sold through the main interface\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}}. %see Figure~\ref{fig:cryptokittie}.
-To buy a cryptokittie, user sends a bid transaction \textit{bid(uint256 \_tokenId)} containing the cryptokittties ID which can be found either on their website or on the ERC721 token smart contract.
+To buy a cryptokittie, the user sends a bid transaction \textit{bid(uint256 \_tokenId)} containing the cryptokittties ID which can be found either on their website or on the ERC721 token smart contract.
 This is similar to open auctions, bid value and the object bidding on is visible to the network and any user could be easily front-run by sending the same transaction with higher gasPrice to replace the initial bidder.
@@
 
-Due to deterministic nature of blockchains, running gambling games based on randomness is close to impossible.
-There had been attempts to use block headers or such as the seed to randomness but almost all have failed as every data accessible to the smart contract at the time of execution, is also accessible to other smart contracts and they could predict the output on the run, thus prone to front-running and miner\'s manipulation.
+Due to the deterministic nature of blockchains, running gambling games based on randomness is close to impossible.
+There had been attempts to use block headers or such as the seed of randomness but almost all have failed as every data accessible to the smart contract at the time of execution, is also accessible to other smart contracts and they could predict the output on the run, thus prone to front-running and miner\'s manipulation.
 Many infamous gambling games are now running on Ethereum network and front-running them requires a level of sophistication and knowledge of the internal of the games and Ethereum.\\
@@
 It is believed that the winner, used a sophisticated approach to finish last~\cite{fomo3dhacker}, we call this approach \textit{Denial-of-service Front-running}.
-The winner deployed a few high gas consumption smart contracts prior to the win, when the timer of the game reached about 3 minutes, the winner bought 1 ticket and sent multiple high gasPrice transactions to aforementioned smart contracts to lure the miners to mine these highly profitable transactions.
-For a DoS front-running to work, attacker floods the network with high gasPrice transactions to prevent other transactions to go through.
+The winner deployed a few high gas consumption smart contracts prior to the win when the timer of the game reached about 3 minutes, the winner bought 1 ticket and sent multiple high gasPrice transactions to aforementioned smart contracts to lure the miners to mine these highly profitable transactions.
+For a DoS front-running to work, the attacker floods the network with high gasPrice transactions to prevent other transactions to go through.
 Luckily enough the winner was able to congest the network in a way that no other ticket purchases were mined in the 3 minutes window and the miners were prioritizing the high gasPriced transactions over other transactions.
 All the details mentioned here are drawn from the transaction history on the blockchain and unless otherwise proven seem to be the way the winner acted to win the pot.
-%probably needs more work to be good enough. more resources will be out in the coming days !
+%probably needs more work to be good enough. more resources will be out in the coming days!
 
@@
 
-There has been more than 3000 ICOs on Ethereum alone, estimated to exceed 75 billion dollars in the first half of 2018~\cite{zetzsche2018ico}.
-On our DApp samples there was not ICOs mainly because they tend to run for a short time with high number of participant and in the time of writing no ICOs have reached the top 25 DApps of \texttt{DAppradar.com}.
-Needless to say the importance of ICOs as an application of blockchain requires more in-depth analysis of front-running on these DApps.
-%ICOs due to the defined cap, are similar to our analogy of a queue line, people would line up to get in and there's a opportunity to front-run.
+There have been more than 3000 ICOs on Ethereum alone, estimated to exceed 75 billion dollars in the first half of 2018~\cite{zetzsche2018ico}.
+On our DApp samples, there was not ICOs mainly because they tend to run for a short time with a high number of participant and in the time of writing no ICOs have reached the top 25 DApps of \texttt{DAppradar.com}.
+Needless to say, the importance of ICOs as an application of blockchain requires more in-depth analysis of front-running on these DApps.
+%ICOs due to the defined cap is similar to our analogy of a queue line, people would line up to get in and there's an opportunity to front-run.
 Here we focus on one ICO that our preliminary research showed that there might be a front-running attack going on.
-There is no doubt that similar behaviour could be seen on other instances of ICOs or similar DApps if investigated.
+There is no doubt that similar behaviour could be seen in other instances of ICOs or similar DApps if investigated.
 
 \subsection{\textit{Status.im} ICO}
-As discussed in~\ref{sec:Front Running on the Blockchains}, capped ICOs are considerable applications to be investigated in terms of the front-running attacks, \textit{Status.im} ICO is such application.
+As discussed in~\ref{sec:Front Running on the Blockchains}, capped ICOs are considerable applications to be investigated in terms of the front-running attacks, \textit{Status.im} ICO is such an application.
 In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached the defined cap within 3 hours, resulting in close to 300,000 Ether of funds.
@@
 Further study showed that some mining pools might have been manipulating the network for their own profit.
-In addition, there were many transactions sent with higher gas price to front-run other transactions, however these transactions were failing due to the restriction in the ICO smart contract to reject any transactions with higher than 50 \textit{GWei} gas price (as an attempt to prevent the known front-running behaviour).
+In addition, there were many transactions sent with a higher gas price to front-run other transactions, however, these transactions were failing due to the restriction in the ICO smart contract to reject any transactions with higher than 50 \textit{GWei} gas price (as an attempt to prevent the known front-running behaviour).
 

### 2018-09-17 frontrunning/Latex/sections/paper.tex
[frontrunning] edits till section 6

@@
 On our DApp samples, there was not ICOs mainly because they tend to run for a short time with a high number of participant and in the time of writing no ICOs have reached the top 25 DApps of \texttt{DAppradar.com}.
-Needless to say, the importance of ICOs as an application of blockchain requires more in-depth analysis of front-running on these DApps.
+Needless to say, the importance of ICOs as an application of blockchain requires more in-depth analysis of front-running on these type of DApps.
 %ICOs due to the defined cap is similar to our analogy of a queue line, people would line up to get in and there's an opportunity to front-run.
-Here we focus on one ICO that our preliminary research showed that there might be a front-running attack going on.
+Here we focus on one ICO that our preliminary research showed that there might have been a front-running incident.
 There is no doubt that similar behaviour could be seen in other instances of ICOs or similar DApps if investigated.
@@
 As discussed in~\ref{sec:Front Running on the Blockchains}, capped ICOs are considerable applications to be investigated in terms of the front-running attacks, \textit{Status.im} ICO is such an application.
-In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached the defined cap within 3 hours, resulting in close to 300,000 Ether of funds.
-In order to prevent few large investments to buy up all the tokens and limit the amount of Ether deposited in an investment, they used a \textit{fair} token distribution method named \textit{Dynamic Ceiling} as an attempt to increase the time window for smaller investors.
+In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached the predefined cap within 3 hours, resulting in close to 300,000 Ether of funds.
+In order to prevent few large investments to buy up all the tokens and limit the amount of Ether deposited in an investment, they used a \textit{fair} token distribution method named \textit{Dynamic Ceiling} as an attempt to increase the opprotunity window for smaller investors.
 They implemented multiple caps --ceiling-- in which, each had a maximum amount that could be deposited in.
@@
 According to the analysis we carried out, it was discovered that the F2Pool, an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure ~\ref{fig:mining_pool_ratio}), sent 100 Ether to 30 new Ethereum addresses before Status.im ICO started.
-On the time the ICO was opened for participation, F2Pool constructed 31 transactions to the ICO token sale smart contract from the addresses they controlled --without broadcasting these transactions to the network-- and used their entire mining power to mine their own transactions and also potentially failing high gas price transactions.
+On the time the ICO was opened for participation, F2Pool constructed 31 transactions to the ICO token sale smart contract from the addresses they controlled --without broadcasting these transactions to the network-- and used their entire mining power to mine their own transactions and some other potentially failing high gas price transactions.
 
-Ethereum blockchain contains all transaction ever made on Ethereum, however, it is not easy to see the behavior of the participants and miners solely using the default clients nor online blockchain explorers.
+Ethereum blockchain contains all transaction ever made on Ethereum, however, it is not easy to see the behaviour of the participants and miners solely using the default clients nor online blockchain explorers.
 In order to get the required data, Ethereum blockchain data should be converted to a queryable format.
-For this case study, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation of the Ethereum protocol\url{https://github.com/ethereum/go-ethereum}} for the full node, python script for extracting, transforming and loading ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery\footnote{A fast, highly scalable, cost-effective, and fully managed cloud data warehouse for analytics \url{https://cloud.google.com/bigquery/}}.
-Using this software stack, we were able to query for all the transactions and blocks within the window of Status.im ICO for further analysis which was mainly done by data analysis tool \texttt{Tableau}\footnote{Tableau is a data visualization software that is used for data science and business intelligence.\url{https://www.tableau.com/}}.
+For this case study, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation\url{https://github.com/ethereum/go-ethereum}} for the full node, python script for extracting, transforming and loading ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery\footnote{\url{https://cloud.google.com/bigquery/}}.
+Using this software stack, we were able to query for all the transactions and blocks within the window of Status.im ICO for further analysis which was mainly done by data analysis tool \texttt{Tableau}\footnote{\url{https://www.tableau.com/}}.
 A copy of this dataset and the initial findings can be found in our Github repository\footnote{\url{github.com / ANONYMOUS}}.
 
-As shown in Figure~\ref{fig:Transactions_miners_while_status_ico_cut}, most of the top miners in the mentioned time frame, have mined almost the same number of failed and successful transactions which were directed toward Status.im token sale, however F2Pool's transactions indicate their successful transactions were equivalent to 10\% of the failed transactions, hence maximizing the mining rewards, on gas, while censoring other transactions to the token sale smart contract.
+As shown in Figure~\ref{fig:Transactions_miners_while_status_ico_cut}, most of the top miners in the mentioned time frame, have mined almost the same number of failed and successful transactions which were directed toward Status.im token sale, however F2Pool's transactions indicate their successful transactions were equivalent to 10\% of the failed transactions, hence maximizing the mining rewards on gas, while censoring other transactions to the token sale smart contract.
 The terminology used here is specific to smart contract transactions on Ethereum, by \textit{``failed transaction''} we mean the transactions in which the smart contract code flow rejected and threw an exception and by \textit{``successful transaction''} we mean the transactions that went through and received tokens from the smart contract.
@@
 
-Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their mining software to behave in a certain way to front-run other transactions and take advantage of the monetary profit.
-The dataset used for this analysis can be found on our GitHub repository.\footnote{Frontrunning Status.im ICO dataset: \url{http://github.com/TODO:ANONYMOUS}}.
-This analysis made us wonder how many other DApps are vulnerable to front-running attack, who can front-run and what are the mitigation methods for decentral applications?
-
+Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their mining software to behave in a certain way to front-run other transactions and gain monetary profit.
+The dataset used for this analysis can be found on our GitHub repository.\footnote{Front-running Status.im ICO dataset: \url{http://github.com/ANONYMOUS}}.
 %______________________________________________________________%

### 2018-09-17 frontrunning/Latex/sections/paper.tex
[frontrunning] finish one round edits + more citations

@@
 
-In the traditional markets, front-running is considered unethical and also illegal.
-In the blockchain space, the designers of the decentral applications cannot rely on the justice system for unethical behavior, and they must assume that each participant in the network acts rationally in their own self interest, the application will be operating in an adversarial environment~\cite{0xfrontrunning:online}.
+In the traditional markets, front-running is considered unethical and illegal.
+In the blockchain space, the designers of the decentral applications cannot rely on the justice system for preventing unethical behavior, and they must assume that each participant in the network acts rationally in their own self interest, the application will be operating in an adversarial environment~\cite{0xfrontrunning:online}.
 A few decentral exchange projects such as \textit{EtherDelta} and \textit{0xProject}~\cite{warren20170x}, have proposed solutions for front-running, which is off-chain order books.
-The methods discussed within these projects prevent blockchain network participants from front running the orders as the orders are private and not known to the network and will not be broadcasted.
+The methods discussed within these projects prevent blockchain network participants from front-running the orders as the orders are private and not known to the network and will not be broadcasted.
 However they are introducing third parties, \eg relayers in 0xproject, to be managing the orders with the promise not to reorder or front-run other orders.
@@
 \emph{Traditional Front-running Prevention Methods}.
-There are debates in traditional markets regarding the fact that Front-running is considered to be a form of insider trading which deemed to be illegal.
+There are debates in traditional markets regarding the fact that front-running is considered to be a form of insider trading which deemed to be illegal.
 Traditional methods to prevent front-running mainly involves after the fact investigation and legal action against the front-runners~\cite{LexisNexisLawSuit}.
-As mentioned in section~\ref{traditionalFrontrunning}, educating the employees were the first step taken to prevent such issues in traditional markets, however front-running became less likely to happen mainly because of the high fine and law suits against firms whom behaved in an unethical way.
+As mentioned in section~\ref{traditionalFrontrunning}, defining front-running and educating the employees were the first step taken to prevent such issues in traditional markets, however front-running became less likely to happen mainly because of the high fine and law suits against firms whom behaved in an unethical way.
 Other methods such as dark pools~\cite{zhu2014dark, buti2011diving} and sealed bids~\cite{radner1989sealed} were discussed and implemented in variety of regulated trading systems.
@@
 
-There are two main approaches to prevent front running, one to design a blockchain that is front-run resistant , and the other to design the application logics in a way that front running is not possible.
+There are two main approaches to prevent front-running blockchains: one to design a blockchain that is front-run resistant, and the other to design the application logics in a way that front-running is not possible.
 %______________________________________________________________%
 \subsection{Front-run Resistant Blockchain}
-What does this mean to have a front-run resistant blockchain?
-There are technical difficulties to achieve such solutions as there are unknown factors within such network designs (corner/edge cases).
+There are technical difficulties to achieve such solutions as there are unknown factors within such network designs and requires testing every corner and edge case scenarios.
 In this section, we describe the potential solutions using which, one can design and implement a decentral application that is resistant to front-running.
@@
 \subsubsection{Design Decision \#1: Fixed Transaction Ordering\newline}
-
 One possible solution to fix current blockchains in regards to transaction reordering by miners has been proposed by da Silva~\etal~\cite{fixedordering2018silva}.
-This solution consists of an algorithm, known as Fixed Transaction Ordering and Admission (FTOA) algorithm, in the consensus protocol that enforces the order of the transactions.
+This solution consists of an algorithm, known as Fixed Transaction Ordering and Admission (FTOA) algorithm, in the consensus protocol that enforces the order of the transactions in the mined blocks.
 
 \subsubsection{Design Decision \#2:Privacy Preserving Blockchain\newline}
-
 Market participants are concerned about revealing information on their past trades, purchases, income, or liquidity needs.
 Privacy is a basic human right, that being said, there are limitations with the functionality of a system designed to preserve full privacy.
-However other than past transactions, real time transactions could leak informations about the sender or the intention of the order that could lead to front-running attacks.
-Privacy preserving blockchains try to solve the initial issue by keeping all the details of the transactions private, in some extent~\cite{miller2017empirical, kappos2018empirical}.
+However other than past transactions, real time transactions would leak informations about the sender or the intention of the order that could lead to front-running attacks.
+Privacy preserving blockchains try to solve the initial issue by keeping all the details of the transactions private (in some extent~\cite{miller2017empirical, kappos2018empirical}).
 As an example, ZCash~\cite{hopwood2016zcash}, uses two distinct type of addresses, transparent addresses and shielded addresses.
@@
 
-\subsubsection{Design Decision \#3: Dual Authoring\newline}
-
+\subsubsection{Design Decision \#3: Dual Authoring\newline} % S 2 M: this is still vague, it requires better explanation.
 Loopring is an open protocol proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}.
@@
 By paying a higher gasPrice, block miners choose the front-runner's transaction instead of the original \emph{submitRing transaction}.
-However, Loopring's team solves this issue using the \emph{dual-authoring} scheme in the new version of the Loopring protocol.
+However, in the new version of Loopring protocol this issue is resolves using the \emph{dual-authoring} scheme.
 This solution sets two levels of authorization for orders - one for settlement, and one for order matching.
@@
 These auth-keys are used to sign the hash of the ring and will further prevent anyone from regenerating the same \emph{submitRing transaction}.
-The reason is that the auth-keys are only known to the miner of the ring as they are not part of on-chain transaction.
-Doing so, it is assured that (i) the orders are not modified (because they are signed using the owner's private key), (ii) no other miner can mine the ring (because the miner's address is signed using his private key), and no user can front-run the \emph{submitRing transaction} (because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them).
+The reason is that the auth-keys are only known to the miner of the ring as they are not part of the on-chain transaction.
+Doing so, it is assured that (i) the orders are not modified (because they are signed by the owner), (ii) no other miner can mine the ring (because the miner's address is signed by the initial miner), and no user can front-run the \emph{submitRing transaction} (because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them).
+
+% S 2 M: Also I'm not sure about the figures. they do not add enough clarity to the text.
 
@@
 
-Another method to prevent front-running activities is to design the applications, whether they are decentralized (Dapps) or centralized, in such a way that no information would be available to the malicious parties to enable them to front-run the other users.
-Followings discuss the two techniques which can be used by the Apps/DApps developers while designing the systems to prevent front-running activities.
+Another method to prevent front-running activities is to design the applications in such a way that there is no information leakage to the malicious parties to enable them to front-run  other users.
+Followings discuss a few techniques which can be used by the DApp developers while designing the systems to mitigate front-running issues.
 
-\subsubsection{Design Decision \#1: Commitment Scheme\newline} \label{CommitmentScheme} %talk about the drawbacks of this scheme: eg: you may forget to reveal. 
+\subsubsection{Design Decision \#1: Commitment Scheme\newline} \label{CommitmentScheme}
 Commitment scheme is a cryptographic primitive that enables one to commit to a value --binding-- (\eg statement, document, data, \etc) while keeping it a secret and reveal the committed value on a later time~\cite{brassard1988minimum}.
 Commitment scheme is a robust method to prevent information leakage from the sensitive transactions.
-This could be done by simply broadcasting the hash value of the committed data and later on revealing the values that would be hashed to the committed hash, see Figure~\ref{fig:commitReveal}.
+This could be done by simply submiting the hash value of the committed data to a smart contract and later on revealing the values linked to the committed hash, see Figure~\ref{fig:commitReveal}.
 In the case of decentral exchanges, user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, user sends reveal transaction revealing the order details which will be executed in a fair order.
-Depending on the Dapp design, either the order is collateralized, which means the commitment transaction includes the funds required for fulfilling the order, which will leak some information about the order, or is not collateralized and opens up the possibility of user never revealing the commitment, which will be considered as a DoS attack.
-Another use of such commitment scheme, is in decentralized naming systems, such as Namecoin, Ethereum Name Service (ENS) or Ghazal.
+This method is not perfect, depending on the DApp design, either the order is collateralized, that means the commitment transaction includes the funds required for fulfilling the order, which will leak some information about the order, or is not collateralized and opens up the possibility of user never revealing the commitment, which will be vulnerable to Denial-of-Service attacks.
+Another use of such commitment scheme, is in decentralized naming systems, such as Namecoin, Ethereum Name Service (ENS).
 In this case, a user sends a commit transaction, which commits to the name hash, similar to a sealed bid.
@@
 On the other note, these method has some drawbacks, the user experience is not smooth and one might forget to reveal the committed transaction.
-In ENS commit-reveal process, if one forgets to reveal on the reveal phase, the committed funds are burnt and inaccessible there after.
+In ENS commit-reveal process, if one forgets to reveal in the reveal phase, the committed funds are burnt and inaccessible there after.
 Also this scheme means two transaction are required for a functionality which is makes it more expensive to run.
@@
 \includegraphics[width=0.5\linewidth]{figures/commit-reveal.png}
-\caption{ Commit and Reveal.
+\caption{Commit and Reveal.
 User sends a commitment transaction with the hash of the data, After the commitment period is over, user sends her reveal transaction to the DApp revealing the information that matches the commitment.
@@
 Submarine Commitments~\cite{breidenbach2018enter, submarinesendHD} are similar to the commitment schemes with some key differences such as hiding participatory factor and being fully collateralized.
-However, they could be design in other ways to suit the need of the DApp.
 With submarine send, it is possible to hide sender, receiver, value and data, the commitment transaction is identical to a transaction to a newly generated address.
@@
 
-The details of how Submarine commitments work is outside the scope of this paper, however in summary, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality it is possible to generate one outgoing transaction from an address in which no private key exists.
+The details of how Submarine commitments work is outside the scope of this paper, however in short, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality it is possible to generate one outgoing transaction from an address of which no private key exists.
 By constructing a transaction from that address to the DApp and funding that address we fulfill the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}, see Figure~\ref{fig:LibSubmarine}.
+However, this could be design in other ways to suit the need of the DApp.
 Drawbacks of this scheme are similar to ~\ref{CommitmentScheme}, with an addition of two more transactions to finalize the functionality, which results in more cost and complicated user experience.
@@
 \includegraphics[width=0.5\linewidth]{figures/LibSubmarine.png}
-\caption{ Submarine Send~\cite{libsubmarine}.
+\caption{Submarine Send~\cite{libsubmarine}.
 User generates an \textit{Unlock} transaction from which the commitment address is retrieved.
@@
 \subsubsection{Design Decision \#3: Logic Specific Solutions\newline}
-To prevent front-running, one can design the application in a way that it is not possible to be front-run:
+There is no perfect generic solution to this issue as of now, however to prevent front-running, one can design the application in a way that it is not possible to be front-run:
 
-\noindent\emph{Eliminating Time-Order Dependency:} The applications can be designed to not rely on the time for the orders to be executed.
-For example when designing a decentral exchange, one can use \emph{the call market design} instead of a time-sensitive order book.
-In a call market design, the arrival time of the orders do not matter as they are executed in batches [cite Jeremy's prediction markets paper].
+\noindent\emph{Eliminating Time-Order Dependency:} The applications can be designed not to rely on the time for the orders to be executed.
+For example when designing a decentral exchange, one can use \emph{the call market} design instead of a time-sensitive order book.
+In a call market design, the arrival time of the orders do not matter as they are executed in batches~\cite{clark2014decentralizing}.
 
-\noindent\emph{Disincentivizing Front-running Actors:} This solution, which is economic rather than technical, is to disincentives the miners by paying them.
-As mentioned, the main reasons for miners to front-run the other orders is the financial gain they receive on the price improvement.
-However, if the application is designed in a way that the fees of the orders are sent to the miner of the block, he would have no incentive to front-run the orders as he already gains enough financial benefit from acting fairly and executing the transactions on their correct order.
+\noindent\emph{Disincentivizing Front-running Actors:} This solution, which is economic rather than technical, is to disincentives the miners by paying them the fees.
+If the application is designed in a way that the fees of the orders are sent to the miner of the block, he would have less incentive to front-run the orders as he already gains enough financial benefit from acting fairly and executing the transactions on their correct order.
 For example, Malinova~\cite{malinova2017market} proposes a design for a decentral exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable.

### 2018-09-17 frontrunning/Latex/sections/paper.tex
[frontrunning] minor fixes. still 19 pages :barber:

@@
 Arbitrage and Censorship, are also issues that have been linked to front-running attacks on blockchain \textit{(We need to talk about why these two are left out of the scope of this paper)}.
-Currently, there are quite a few decentral applications built on the blockchains, so in order for us to perform a thorough study on blockchain application front-running, we set a specific criteria by using the top 25 decentral applications which have the highest recent user activities.\footnote{List of decentralized applications \url{https://dappradar.com/dapps}} Using this criteria, we successfully categorized these decentral applications into 4 principal categories on which we conduct our analysis.
-Surprisingly, there was no ICO (initial coin offering) included in the top 25 Dapps list by the time we fetched the data from the website.
+Currently, there are quite a few decentral applications built on the blockchains, so in order for us to perform a thorough study on blockchain application front-running, we set a specific criteria by using the top 25 decentral applications which have the highest recent user activities.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} Using this criteria, we successfully categorized these decentral applications into 4 principal categories on which we conduct our analysis.
+Surprisingly, there was no ICO (initial coin offering) included in the top 25 DApps list by the time we fetched the data from the website.
 We believe the reason is that the ICOs are inherently different from other groups of Daaps as they are merely highly active during their offering periods and their user activity drops dramatically after the offerings period are over.
-Therefore, we  consider ICOs as other cases on which the front-running should be investigated (although they are not listed in the top 25 Dapps we use) \footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".}
+Therefore, we  consider ICOs as other cases on which the front-running should be investigated (although they are not listed in the top 25 DApps we use) \footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".}
 
@@
 
-As mentioned in the Section~\ref{sec:intro}, for the purpose of this research we retrieved the top 25 DApps based on recent user activities from \texttt{DAppradar.com}\footnote{List of decentralized applications \url{https://dappradar.com/dapps}} in the first week of September 2018.
-We then categorize these applications into 4 principal groups of decentral applications (see Table~\ref{tab:top25dapps}).
+As mentioned in the Section~\ref{sec:intro}, for the purpose of this research we retrieved the top 25 DApps based on recent user activities from \texttt{DAppradar.com}\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} in the first week of September 2018.
+We then categorize these applications into 4 principal groups of decentral applications (see Table~\ref{tab:top25DApps}).
 In this section, we take a deep look into one or two decentral applications from each category and pinpoint the technical details of front-running issue on each case.
@@
 There have been more than 3000 ICOs on Ethereum alone, estimated to exceed 75 billion dollars in the first half of 2018~\cite{zetzsche2018ico}.
-On our DApp samples, there was not ICOs mainly because they tend to run for a short time with a high number of participant and in the time of writing no ICOs have reached the top 25 DApps of \texttt{DAppradar.com}.
+On our DApp samples, there was not ICOs mainly because they tend to run for a short time with a high number of participant and in the time of writing no ICOs have reached the top 25 DApps of \texttt{DAppRadar.com}.
 Needless to say, the importance of ICOs as an application of blockchain requires more in-depth analysis of front-running on these type of DApps.
@@
 In the traditional markets, front-running is considered unethical and illegal.
-In the blockchain space, the designers of the decentral applications cannot rely on the justice system for preventing unethical behavior, and they must assume that each participant in the network acts rationally in their own self interest, the application will be operating in an adversarial environment~\cite{0xfrontrunning:online}.
+In the blockchain space, the designers of the decentral applications cannot rely on the justice system for preventing unethical behavior, and they must assume that each participant in the network acts rationally in their own self-interest, the application will be operating in an adversarial environment~\cite{0xfrontrunning:online}.
 A few decentral exchange projects such as \textit{EtherDelta} and \textit{0xProject}~\cite{warren20170x}, have proposed solutions for front-running, which is off-chain order books.
@@
 Traditional methods to prevent front-running mainly involves after the fact investigation and legal action against the front-runners~\cite{LexisNexisLawSuit}.
-As mentioned in section~\ref{traditionalFrontrunning}, defining front-running and educating the employees were the first step taken to prevent such issues in traditional markets, however front-running became less likely to happen mainly because of the high fine and law suits against firms whom behaved in an unethical way.
-Other methods such as dark pools~\cite{zhu2014dark, buti2011diving} and sealed bids~\cite{radner1989sealed} were discussed and implemented in variety of regulated trading systems.
+As mentioned in section~\ref{traditionalFrontrunning}, defining front-running and educating the employees were the first step taken to prevent such issues in traditional markets, however, front-running became less likely to happen mainly because of the high fine and lawsuits against firms who behaved in an unethical way.
+Other methods such as dark pools~\cite{zhu2014dark, buti2011diving} and sealed bids~\cite{radner1989sealed} were discussed and implemented in a variety of regulated trading systems.
 
-The traditional methods to prevent front-running does not apply to blockchain applications, as mainly they are based on central enforcement and limitations, also in case of blockchains the actors whom are front-running could be anonymous and the fear of lawsuits would not apply.
+The traditional methods to prevent front-running does not apply to blockchain applications, as mainly they are based on central enforcement and limitations, also in case of blockchains the actors who are front-running could be anonymous and the fear of lawsuits would not apply.
 \\
@@
 
-\subsubsection{Design Decision \#2:Privacy Preserving Blockchain\newline}
+\subsubsection{Design Decision \#2:Privacy-Preserving Blockchain\newline}
 Market participants are concerned about revealing information on their past trades, purchases, income, or liquidity needs.
-Privacy is a basic human right, that being said, there are limitations with the functionality of a system designed to preserve full privacy.
-However other than past transactions, real time transactions would leak informations about the sender or the intention of the order that could lead to front-running attacks.
-Privacy preserving blockchains try to solve the initial issue by keeping all the details of the transactions private (in some extent~\cite{miller2017empirical, kappos2018empirical}).
+Privacy is a basic human right, that being said, there are limitations to the functionality of a system designed to preserve full privacy.
+However other than past transactions, real-time transactions would leak information about the sender or the intention of the order that could lead to front-running attacks.
+Privacy-preserving blockchains try to solve the initial issue by keeping all the details of the transactions private (in some extent~\cite{miller2017empirical, kappos2018empirical}).
 As an example, ZCash~\cite{hopwood2016zcash}, uses two distinct type of addresses, transparent addresses and shielded addresses.
@@
 However shielded addresses are private and do not leak any information, this is great for privacy but not good for smart contracts capabilities.
-Smart contract functionality requires verification by the miners which require to know the input, functionality and output of smart contracts to be able to determine if the transaction is valid.
+Smart contract functionality requires verification by the miners which require to know the input, functionality, and output of smart contracts to be able to determine if the transaction is valid.
 Albeit by using cryptographic primitives such as zero-knowledge proofs this issue could also be resolved~\cite{kosba2016hawk}.
@@
 By paying a higher gasPrice, block miners choose the front-runner's transaction instead of the original \emph{submitRing transaction}.
-However, in the new version of Loopring protocol this issue is resolves using the \emph{dual-authoring} scheme.
+However, in the new version of Loopring protocol, this issue is resolves using the \emph{dual-authoring} scheme.
 This solution sets two levels of authorization for orders - one for settlement, and one for order matching.
-As it can be seen in Figure~\ref{fig:not_vulnerable_loopring}, each owner of any order generates a pair of public key (auth-address) and private key (auth-key), which are different from his address and its corresponding private key.
+As it can be seen in Figure~\ref{fig:not_vulnerable_loopring}, each owner of an order generates a pair of public key (auth-address) and private key (auth-key), which are different from his address and its corresponding private key.
 These auth-keys are used to sign the hash of the ring and will further prevent anyone from regenerating the same \emph{submitRing transaction}.
@@
 \subsubsection{Design Decision \#1: Commitment Scheme\newline} \label{CommitmentScheme}
-Commitment scheme is a cryptographic primitive that enables one to commit to a value --binding-- (\eg statement, document, data, \etc) while keeping it a secret and reveal the committed value on a later time~\cite{brassard1988minimum}.
-Commitment scheme is a robust method to prevent information leakage from the sensitive transactions.
-This could be done by simply submiting the hash value of the committed data to a smart contract and later on revealing the values linked to the committed hash, see Figure~\ref{fig:commitReveal}.
-In the case of decentral exchanges, user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, user sends reveal transaction revealing the order details which will be executed in a fair order.
+The commitment scheme is a cryptographic primitive that enables one to commit to a value --binding-- (\eg statement, document, data, \etc) while keeping it a secret and reveal the committed value on a later time~\cite{brassard1988minimum}.
+The commitment scheme is a robust method to prevent information leakage from the sensitive transactions.
+This could be done by simply submitting the hash value of the committed data to a smart contract and later on revealing the values linked to the committed hash, see Figure~\ref{fig:commitReveal}.
+In the case of decentral exchanges, the user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, the user sends reveal transaction revealing the order details which will be executed in a fair order.
 This method is not perfect, depending on the DApp design, either the order is collateralized, that means the commitment transaction includes the funds required for fulfilling the order, which will leak some information about the order, or is not collateralized and opens up the possibility of user never revealing the commitment, which will be vulnerable to Denial-of-Service attacks.
-Another use of such commitment scheme, is in decentralized naming systems, such as Namecoin, Ethereum Name Service (ENS).
+Another use of such a commitment scheme is in decentralized naming systems, such as Namecoin, Ethereum Name Service (ENS).
 In this case, a user sends a commit transaction, which commits to the name hash, similar to a sealed bid.
-Once the transaction is confirmed and the grace period is over, user sends a reveal transaction revealing the bid and also the details of the requested domain~\cite{kalodner2015empirical}.
+Once the transaction is confirmed and the grace period is over, the user sends a reveal transaction revealing the bid and also the details of the requested domain~\cite{kalodner2015empirical}.
 Using this scheme, one is able to hide information from the adversarial parties in the system and prevent them from front-running.
-Similar approach applies to on-chain voting as well ~\cite{adChainPLCRVoting}, using sealed votes, voters can make sure their votes are hidden until a later date, however their participation and weight of the vote are publicly known.
+A similar approach applies to on-chain voting as well ~\cite{adChainPLCRVoting}, using sealed votes, voters can make sure their votes are hidden until a later date, however, their participation and weight of the vote are publicly known.
 Other than the collateralization issue for the commit and reveal scheme, another obvious issue is the participatory factor.
@@
 On the other note, these method has some drawbacks, the user experience is not smooth and one might forget to reveal the committed transaction.
-In ENS commit-reveal process, if one forgets to reveal in the reveal phase, the committed funds are burnt and inaccessible there after.
-Also this scheme means two transaction are required for a functionality which is makes it more expensive to run.
+In the ENS commit-reveal process, if one forgets to reveal in the reveal phase, the committed funds are burnt and inaccessible thereafter.
+Also, this scheme means two transactions are required for a functionality which makes it more expensive to run.
 
@@
 Submarine Commitments~\cite{breidenbach2018enter, submarinesendHD} are similar to the commitment schemes with some key differences such as hiding participatory factor and being fully collateralized.
-With submarine send, it is possible to hide sender, receiver, value and data, the commitment transaction is identical to a transaction to a newly generated address.
+With submarine send, it is possible to hide sender, receiver, value, and data, the commitment transaction is identical to a transaction to a newly generated address.
 Submarine sends could be a solution for sealed-bid auctions on the blockchain to hide the existence of the bids for other participants.
@@
 By constructing a transaction from that address to the DApp and funding that address we fulfill the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}, see Figure~\ref{fig:LibSubmarine}.
-However, this could be design in other ways to suit the need of the DApp.
+However, this could be designed in other ways to suit the need of the DApp.
 Drawbacks of this scheme are similar to ~\ref{CommitmentScheme}, with an addition of two more transactions to finalize the functionality, which results in more cost and complicated user experience.
@@
 \subsubsection{Design Decision \#3: Logic Specific Solutions\newline}
-There is no perfect generic solution to this issue as of now, however to prevent front-running, one can design the application in a way that it is not possible to be front-run:
+There is no perfect generic solution to this issue as of now, however, to prevent front-running, one can design the application in a way that it is not possible to be front-run:
 
@@
 For example when designing a decentral exchange, one can use \emph{the call market} design instead of a time-sensitive order book.
-In a call market design, the arrival time of the orders do not matter as they are executed in batches~\cite{clark2014decentralizing}.
+In a call market design, the arrival time of the orders does not matter as they are executed in batches~\cite{clark2014decentralizing}.
 
@@
 
-Going back to Table~\ref{tab:top25dapps}, some DApps facilitate different methods to mitigate front-running issues.
-As an example LocalEthereum, an escrow-based exchange, uses challenge random values from the website to be included in the signature of the transaction (See ~\ref{code:localethereum}), hence removing any possibility of replay attack or possibility of any other address sending the similar order.
+Going back to Table~\ref{tab:top25DApps}, some DApps facilitate different methods to mitigate front-running issues.
+As an example, LocalEthereum, an escrow-based exchange, uses challenge random values from the website to be included in the signature of the transaction (See ~\ref{code:localethereum}), hence removing any possibility of replay attack or the possibility of any other address sending the similar order.
 
-%Possibly remove this code snippet due to page limit
+%Possibly remove this code snippet due to page limit . don't forget to remove the refrence to it ^
 \begin{lstlisting}[basicstyle=\scriptsize\ttfamily,caption={Code snippet from LocalEthereum smart contract.

### 2018-09-17 frontrunning/Latex/setup/table.tex
[frontrunning] minor fixes. still 19 pages :barber:

@@
 \end{tabular}
-\caption{\footnotesize{Top 25 DApps based on recent user activity from \texttt{Dappradar.com} on September 4th, 2018.
-Dapps that are represented in Italic format are analyzied and discussed in this paper.}\label{tab:top25dapps}}
+\caption{\footnotesize{Top 25 DApps based on recent user activity from \texttt{DAppRadar.com} on September 4th, 2018.
+DApps that are represented in Italic format are analyzied and discussed in this paper.}\label{tab:top25DApps}}
 \end{table}

### 2018-09-17 auditing/Latex/sections/00-abstract.tex
[auditing] template ready

% !TEX root = ../main.tex
\begin{abstract}

Abstract goes here.

\end{abstract}

### 2018-09-17 auditing/Latex/sections/01-intro.tex
[auditing] template ready

% !TEX root = ../main.tex
\section{Introductory Remarks}

Blah blah blah.

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =

\paragraph{Scope.} 
Blah blah blah.

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =

%\paragraph{Contributions.} 
%Our primary contributions are as follows.
%
%\begin{enumerate}
%
%\item Blah blah blah.
%
%\item Blah blah blah. 
%
%\item Blah blah blah. 
%
%\end{enumerate}

### 2018-09-17 atomic-swaps/atomic-swaps-paper/intro.tex

@@
 The risk of one party losing their assets is minimized.
-The concept of atomic swaps, which provides safe and quick trades, is being discussed since 2013\cite{altcoin}.
+The concept of atomic swaps, which provides safe and quick trades, has been discussed since 2013\cite{altcoin}.
 Atomic swaps can be on-chain or off-chain.
 Off-chain swaps are instant, private and they almost doesn't incur any fees.
-Both type of swaps utilize hashed-time-locked-contracts (HTLCs) to guarantee that a party can't take any funds before providing his fund.
+%Both type of swaps utilize hashed-time-locked-contracts (HTLCs) to guarantee that a party can't take any funds before providing his fund.
 
@@
 
-\section{Our Implementation}
+%\section{Our Implementation}
+%
+%\begin{itemize}
+%  \item ETH to ERC20 token atomic swap is implemented.
+%  \item ERC20 to ERC20 token atomic swap is implemented.
+%  \item One contract can perform several swaps. Each swap is assigned a swapID.
+%  \item Each swap has three states: OPEN, CLOSED or EXPIRED.
+%\end{itemize}
+%
+%\begin{figure}[h!]
+%\centering
+%\includegraphics[width=1\textwidth]{approve}
+%\caption{ETH to ERC20 with approve}
+%\label{fig:withapprove}
+%\vspace{-10pt}
+%\end{figure}
+%
+%\begin{figure}[h!]
+%\centering
+%\includegraphics[width=1\textwidth]{withoutapprove}
+%\caption{ETH to ERC20-like without approve}
+%\label{fig:withoutapprove}
+%\vspace{-10pt}
+%\end{figure}
+%
+%\begin{figure}[h!]
+%	\centering
+%	\includegraphics[width=1\textwidth]{ERC20toERC223}
+%	\caption{ERC20 to ERC223}
+%	\label{fig:ERC20toERC223}
+%	\vspace{-10pt}
+%\end{figure}
+%
+%\begin{figure}[h!]
+%	\centering
+%	\includegraphics[width=1\textwidth]{ERC223toERC223}
+%	\caption{ERC223 to ERC223}
+%	\label{fig:ERC223toERC223}
+%	\vspace{-10pt}
+%\end{figure}
+%
+%\begin{figure}[h!]
+%	\centering
+%	\includegraphics[width=1\textwidth]{ETHtoERC223}
+%	\caption{ETH to ERC223}
+%	\label{fig:ETHtoERC223}
+%	\vspace{-10pt}
+%\end{figure}
+%
+%\section{Comparison of Token Standards}
+%\subsection{ERC721}
+%non-fungible, ERC20 compatible
+%\subsection{ERC223}
+%ERC20 has the problem of "non-recovarable" coins
+%ERC20 needs to execute two functions to transfer coins: approve and transferFrom. ERC223 consumes half the amount of gas than the amount needed to transfer an ERC20 token.
+%ERC223 offers 3 improvements:
+%\begin{itemize}
+%  \item no lost tokens
+%  \item reject non-supported tokens
+%  \item energy saving
+%\end{itemize}
+%
+%tokenFallback: the receiving contract has a chance to do some work.
+%\subsection{ERC777}
 
-\begin{itemize}
-  \item ETH to ERC20 token atomic swap is implemented.
-  \item ERC20 to ERC20 token atomic swap is implemented.
-  \item One contract can perform several swaps. Each swap is assigned a swapID.
-  \item Each swap has three states: OPEN, CLOSED or EXPIRED.
-\end{itemize}
+\section{Background}
+ERC stands for Ethereum Request for Comment~\cite{comparison}.
+The emergence of ERC20 tokens in 2015 made the token creation much easier.
+There are six main functions in the interface~\cite{ERC20}: totalSupply, balanceOf, transfer, transferFrom, approve and allowance.
+Transfer moves a certain amount of tokens to a given adress.
+TransferFrom transfers tokens from one token contract to another.
+Approve functions specifies the amount of tokens that can be withdrawn from an account.
+There is a significant shortcoming of current ERC20 implementation: a party may send tokens to a contract that it doesn't intend to.
+In this case, the party won't be able get its tokens back.
 
-\begin{figure}[h!]
-\centering
-\includegraphics[width=1\textwidth]{approve}
-\caption{ETH to ERC20 with approve}
-\label{fig:withapprove}
-\vspace{-10pt}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=1\textwidth]{withoutapprove}
-\caption{ETH to ERC20-like without approve}
-\label{fig:withoutapprove}
-\vspace{-10pt}
-\end{figure}
-
-\begin{figure}[h!]
-	\centering
-	\includegraphics[width=1\textwidth]{ERC20toERC223}
-	\caption{ERC20 to ERC223}
-	\label{fig:ERC20toERC223}
-	\vspace{-10pt}
-\end{figure}
-
-\begin{figure}[h!]
-	\centering
-	\includegraphics[width=1\textwidth]{ERC223toERC223}
-	\caption{ERC223 to ERC223}
-	\label{fig:ERC223toERC223}
-	\vspace{-10pt}
-\end{figure}
-
-\begin{figure}[h!]
-	\centering
-	\includegraphics[width=1\textwidth]{ETHtoERC223}
-	\caption{ETH to ERC223}
-	\label{fig:ETHtoERC223}
-	\vspace{-10pt}
-\end{figure}
-
-\section{Comparison of Token Standards}
-\subsection{ERC721}
-non-fungible, ERC20 compatible
-\subsection{ERC223}
-ERC20 has the problem of "non-recovarable" coins
-ERC20 needs to execute two functions to transfer coins: approve and transferFrom. ERC223 consumes half the amount of gas than the amount needed to transfer an ERC20 token.
-ERC223 offers 3 improvements:
-\begin{itemize}
-  \item no lost tokens
-  \item reject non-supported tokens
-  \item energy saving
-\end{itemize}
-
-tokenFallback: the receiving contract has a chance to do some work.
-\subsection{ERC777}
+ERC223 addresses the aforementioned problem that ERC20 has~\cite{ERC223}.
+ERC223's transfer function prevents lost tokens, as it prevents transferring tokens to contracts which are not expecting them.
+ERC223 token transfer works similar to the ETH transactions.
+If a party tries to transfer tokes to a non-receiver contract, an exception will be thrown.
+ERC223's transfer function is more efficient than ERC20's approve and transferFrom, as it consumes less gas.
 
@@
 Table~\ref{Table:Comparison of different swaps} illustrates the possible settings and compares the amount of transactions required for each case.
+%The involving parties in the swap are named as maker and taker in accordance with the financial terminology, where maker is the party that provides the token or ETH and taker is the party that wants to buy token or ETH from the maker.
+The class determines certain characteristics of the swap.
+Approve means that the approve function in the token interface is used and without approve corresponds to the opposite case.
+Both approve and without approve class type swaps are not collateralized due to the properties of the ERC20 token.
+Hybrid refers to the  case where one party collateralizes its assets and the other doesn't.
 
@@
   \hline
-   maker & taker & class & order transactions (margin) & account (onetime) transactions (fixed) \\ \hline
+   maker & taker & class & order transactions  & account (onetime)  \\
+   & & &(margin) &  transactions (fixed) \\ \hline
    ERC20 & ETH & approve & 2 & 4 \\ \hline
@@
    ERC20 & ERC223 & hybrid & 2 & 5 \\ \hline
-   ERC223 & ERC223 & collateralized & 2 & 5\\ \hline
+   ERC223 & ERC223 & collateralized & 3 & 4\\ \hline
 \end{tabular}
@@
 \end{table}\label{Table:Comparison of different swaps}
-\textbf{ERC20 to ETH:} This setting is described in Figure~\ref{fig:withapprove}.
-Somebody deploys the swap contract.
+\textbf{ERC20 to ETH:}  Somebody deploys the swap contract.
 For each atomic swap between two parties, somebody (who may or may not be one of the transacting parties) initiates a swap object within the swap contract.
@@
 
-\textbf{ERC20 to ERC20:} For the fixed transactions, we have 5 in total as the other token holder should also approve the amount of tokens to be spent.
+\textbf{ERC20 to ERC20:} All the transactions described in the setting for ETH to ERC20 swap are also observed in this case.
+In addition to those, for the fixed transactions, we have 5 in total as the other token holder should also approve the amount of tokens to be spent.
 
-\textbf{ERC20-like to ETH:} This setting is described in Figure~\ref{fig:withoutapprove}. For this setting, the approve function in the ERC20 interface is not used.
+\textbf{ERC20-like to ETH:} For this setting, the approve function in the ERC20 interface is not used.
+Similar to the ETH to ERC20 case, we have 4 transactions in total, that consists of deploying the swap contract, initializing the swap object, calling the settle function to send ETH and transfer of tokens to the swap contract.
+Deploying the swap contract and transferring the tokens to swap contract are considered as the fixed transactions, as a party can transfer more tokens than a single swap requires, which allows the involving parties to perform several swaps.
 
-\textbf{ERC20-like to ERC20-like:}
+\textbf{ERC20-like to ERC20-like:} The token standard used in this case is defined as ERC20-like, as the approve function that is defined in the ERC20 interface is not utilized.
+Apart from the 2 fixed transactions (deploying the swap contract and transferring the tokens to the swap contract), there are 3 more transactions in this case.
+The approve function is replaced by a function that consists of two parts: token holder initiates transfer from swap contract and the transfer from the token contract takes place.
+This should be performed by both parties.
+And the last one is the settle function that finalizes the swap.
+
+\textbf{ERC223 to ETH:} The ERC223 interface allows the parties to collateralize the tokens.
+However, the ETH is not collateralized.
+This case is defined as hybrid.
+In addition to the fixed transactions, there are two more transactions that needs to be performed at each swap.
+First transaction calls the transfer and the tokenfallback to let the swap contract know about the swap.
+Second transaction is the settle function where the ETH owner sends ETH to the swap contract and the swap contract sends the ETH to the token owner.
+As a last step of the transaction function, swap contract triggers the token contract to send the tokens to the ETH holder.
+
+\textbf{ERC20 to ERC223:} Deploying the swap contract and transferring the tokens to the swap contract are counted as fixed transactions.
+In addition to them, settling the swap (sending the ETH to the token owner and sending the tokens to the ETH owner) and the tokenFallback function that acts similar to the approve function in ERC20 are the order transactions as they have to be performed every time a swap occurs.
+The class of the swap is defined as hybrid, since the ERC223 tokens are collateralized, while the ERC20 tokens are not.
+
+\textbf{ERC223 to ERC223:} Once the swap is initialized, both parties must invoke the transfer function of their corresponding token contracts in order to transfer the tokens to the swap contract.
+Settlement can then be triggered by either party and the swap is executed.
+This type of swap is fully collateralized and takes 4 transactions total.
+Three of the transactions must occur with each swap, while the initialization of the swap contract need only be carried out once.
+Unlike with an ERC20 swap, it is not straightforward to escrow multiple swaps worth of ERC223 tokens with a single transaction.
+
+\section{Conclusion}
+Atomic swaps can be realized in different settings.

### 2018-09-18 frontrunning/Latex/sections/abstract.tex
[frontrunning] Abstract and minor changes

--- 2018-09-17 auditing/Latex/sections/00-abstract.tex
@@
 % !TEX root = ../main.tex
+
 \begin{abstract}
 
-Abstract goes here.
+We consider \textit{Front-running} to be any course of action during which an entity benefits from prior access to privileged market information about upcoming transactions and trades.
+Front-running has been an issue in traditional financial instrument markets since 70's.
+Lately, with the advent of the blockchain technology, front-running resurfaced in new forms, due to decentralization and transparency.
+In this paper, we consider instances of front-running across the top 25 decentral applications (DApps) deployed on Ethereum.
+Additionally, we carry out detailed analysis of Status.im Initial Coin Offering (ICO) and show evidence of abnormal miner's behaviour indicative of front-running token purchases.
+Furthermore, we introduce a framework for categorizing proposed solutions to front-running and examine the applicability to the identified issues.
 

### 2018-09-18 frontrunning/Latex/sections/paper.tex
[frontrunning] Abstract and minor changes

@@
 \textit{CBoE} and other exchanges (and brokers) issued educational circulars for their members asserting that front-running violates existing rules, with some examples of what is considered front-running.
-However, the difference of opinion regarding the unfairness of front-running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~cite{sec1978optionsmarket}.
+However, the difference of opinion regarding the unfairness of front-running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~\cite{sec1978optionsmarket}.
 

### 2018-09-20 frontrunning/Latex/sections/abstract.tex
Some edits

--- 2018-09-17 auditing/Latex/sections/00-abstract.tex
@@
 % !TEX root = ../main.tex
+
 \begin{abstract}
 
-Abstract goes here.
+We consider \textit{front-running} to be a course of action where an entity benefits from prior access to privileged market information about upcoming transactions and trades.
+Front-running has been an issue in traditional financial instrument markets since the 1970's.
+With the advent of the blockchain technology, front-running resurfaced in new forms we explore here, due blockchain's decentralized and transparent nature.
+In this paper, we consider instances of front-running across the top 25 decentral applications (DApps) deployed on Ethereum.
+Additionally, we carry out detailed analysis of \textsf{Status.im} initial coin offering (ICO) and show evidence of abnormal miner's behaviour indicative of front-running token purchases.
+Finally, we introduce a framework for categorizing proposed solutions to front-running and examine the applicability to the identified issues.
 

### 2018-09-20 frontrunning/Latex/sections/paper.tex
Some edits

@@
 
-The concept of the \emph{front-running} is decades old starting with early financial markets.
+The concept of  \emph{front-running} is decades old starting with early financial markets.
 Initially, the traders required to be physically available in the exchange office to deliver the bids and offers, and some traders, in the knowledge of future market change, could run in front of the others to get their orders ahead of the change in the market to profit from the price change.
@@
 There have been more than 3000 ICOs on Ethereum alone, estimated to exceed 75 billion dollars in the first half of 2018~\cite{zetzsche2018ico}.
-On our DApp samples, there was not ICOs mainly because they tend to run for a short time with a high number of participant and in the time of writing no ICOs have reached the top 25 DApps of \texttt{DAppRadar.com}.
-Needless to say, the importance of ICOs as an application of blockchain requires more in-depth analysis of front-running on these type of DApps.
+In Table~\ref{top25DApps}, no ICO is represented in the top 25.
+This is because they tend to be high in activity for a short duration only---namely during their sale.
+Since no major ICO was active on the day that we sampled \texttt{DAppRadar.com}, the ICO category falls through our sampling method.
+However we identify this as a major category and study it here.
+
+%. Needless to say, the importance of ICOs as an application of blockchain requires more in-depth analysis of front-running on these type of DApps.
+
 %ICOs due to the defined cap is similar to our analogy of a queue line, people would line up to get in and there's an opportunity to front-run.
-Here we focus on one ICO that our preliminary research showed that there might have been a front-running incident.
+
+%Here we focus on one ICO that our preliminary research showed that there might have been a front-running incident.
 There is no doubt that similar behaviour could be seen in other instances of ICOs or similar DApps if investigated.
@@
 \subsection{\textit{Status.im} ICO}
-As discussed in~\ref{sec:Front Running on the Blockchains}, capped ICOs are considerable applications to be investigated in terms of the front-running attacks, \textit{Status.im} ICO is such an application.
+As discussed in Section~\ref{sec:Front Running on the Blockchains}, capped ICOs are considerable applications to be investigated in terms of the front-running attacks, \textit{Status.im} ICO is such an application.
 In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached the predefined cap within 3 hours, resulting in close to 300,000 Ether of funds.

### 2018-09-20 auditing/Latex/sections/00-abstract.tex
[auditing] transition to Latex. till Section 3

@@
 
-Abstract goes here.
+The emergence of cryptocurrencies, like Bitcoin, and blockchain technologies, like Ethereum, have matured to a point that commercial firms operating in this space have begun to seek financial audits.
+At the time of writing, auditing firms are hesitant to audit such firms for a variety of reasons with a common underlying theme: the blockchain market introduces novel, technically sophisticated, and risky propositions.
+In this paper, we critically analyze the purported roadblocks to auditing blockchain firms, using a cross-disciplinary approach to bring cryptographers and auditors on the same page.
 

### 2018-09-20 auditing/Latex/sections/01-intro.tex
[auditting] some overall paper structure in Latex
[auditing] transition to Latex. till Section 3

@@
 
-Blah blah blah.
+In certain common circumstances, firms operating in the blockchain space will require their financial statements to be audited by an external firm.
+Annual audits are legally mandatory for publicly traded companies in most countries, and audits might also be required when a firm borrows from a bank or raises capital from investors.
+Auditing is a timely subject as, at the time of writing, major auditing firms are hesitating to provide certification to a wide range of businesses in the blockchain sector due to a perception of insurmountable business risk associated with these clients.
+This creates friction for firms wanting to raise capital in traditional ways.
+
+When assessing whether or not to take on a new client, auditors lack experience in this sector and therefore are unable to develop expectations of financial performance as a way of challenging financial statement assumptions.
+Due to the complex and rapidly changing technological environment, auditors are also unable to keep pace with the changes and develop the in-depth knowledge of their clients\' businesses required for performing an audit.
+Finally, auditors are wary of accepting clients that hold a significant amount of cryptoassets as this space is largely unregulated.
+A lack of third-party oversight puts an onus on the auditor, further increasing their risk exposure.
+
+In this paper we explore why and provide a comprehensive overview of the challenges auditors perceive as novel, we form parallels to auditing approaches used today, and critically assess the extent to which these challenges are barriers.
+Altogether, we find that while this environment is new, the challenges presented are different incarnations of issues already addressed on traditional audit clients.
+Therefore, we conclude that many entities in this space are auditable, subject to certain caveats.
+
+\paragraph{\textbf{Methodology.}} To ensure a comprehensive overview of the changes facing auditors of companies deploying blockchain technologies, we first used structured brainstorming within our multidisciplinary research team, which includes expertise in both auditing and blockchain technologies.
+Once our preliminary list of challenges were established, we vetted our results through informal discussions with over a dozen individuals working in the field, including at the Big Four and mid-sized accounting firms, and used these interviews to augment our list.
+The contribution of this paper is to provide a comprehensive list of challenges, rather than determining the relative importance of each or any broader concepts across the industry---thus we did not find it necessary to apply qualitative data analysis (\eg grounded theory) to the interviews; instead, we simply extracted the challenges raised which we initially missed.
+
+\paragraph{\textbf{Relevance.}} Our work can viewed as a case study of cryptographers working with an outside profession for addressing a real-world problem.
+The result is not a new protocol but a two-way knowledge transfer between professions that we hope is interesting to this audience.
+While displacing auditors is occasionally a target of cryptographers~\cite{narula_zkledger, dagher_provisions}, auditing itself is also occasionally studied directly at venues like Financial Cryptography
 
@@
 
-\paragraph{Scope.} 
-Blah blah blah.
+\section{Preliminaries and Related Work}
+Financial statements are prepared by a firm to summarize its assets and liabilities at year-end, the resulting changes in firm equity, and the firm’s income/profits, expenses/losses, and cash flows across the year.
+Because the firm generally wants to present the most optimistic view of its financial health, the firm may hire an auditor to ensure it is a realistic picture of the company's financial performance.
+In doing so, auditors are expected to comply with Generally Accepted Auditing Standards (GAAS) and the Code of Conduct of their professional order.
+In addition to an audited statement, the firm will produce quarterly statements that are reviewed by a third party auditor to a less rigorous standard.
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+%------------------------------------------------------------------------------------------------
+\subsection{Primary Stakeholders in an Audit}
 
-%\paragraph{Contributions.} 
-%Our primary contributions are as follows.
-%
-%\begin{enumerate}
-%
-%\item Blah blah blah.
-%
-%\item Blah blah blah. 
-%
-%\item Blah blah blah. 
-%
-%\end{enumerate}
+\paragraph{Firm Management.} Financial statements are prepared by and remain the responsibility of firm management.
+Many assumptions and estimates are required to prepare this report.
+A firm's CEO and CFO must certify the adequacy and effectiveness of the firm's internal controls over financial reporting, which poses a reputational risk for firm directors as they will be held accountable for financial statements that are misstated.
+Management will seek an audit to comply with regulatory requirements, or because they feel it will give them a competitive advantage over non-audited firms in raising capital and lowering their lending rates.
+In a market where auditors are reluctant or audits are expensive, firms can use their ability to obtain audited financial statements as a barrier against new entrants to the blockchain sector.
+
+\paragraph{Auditor.} The auditor for a given firm is selected by the firm itself.
+When an auditor provides an audit opinion, there is always a chance that fraud or misrepresentation went undetected in the statements.
+If this fraud is subsequently uncovered, the auditor could be liable for substantial penalties.
+For instance, Deloitte LLP paid a settlement of \$150M for failure to find fraud at mortgage broker Taylor, Bean \& Whitaker~\cite{FTDeloitte2018}.
+
+\paragraph{Investors.} The primary users of financial statements are external investors who make decisions about whether or not to lend money or invest capital in a target firm.
+Investors use financial statements to assess their potential return on investment.
+Although \textit{caveat emptor} is an important consideration, investors rely on the existence of an auditor's report as a signal of the reliability of financial disclosures.
+
+\paragraph{Financial Regulators.} Regulators span different government agencies with a spectrum of concerns including financial fraud, taxation, anti-money laundering, and know your customer rules.
+Financial audits are central to the role of security regulators, who require publicly traded firms to obtain an annual unqualified audit opinion on their financial statements for consumer protection.
+Failure to do so, would put the company offside with the regulators\' requirements and could result in the company\'s shares being placed on cease-trade.
+
+%------------------------------------------------------------------------------------------------
+\subsection{Cryptoassets and firms that hold them}
+The central component of a financial report is the firm’s balance sheet which lists assets and liabilities.
+We use the term \textit{cryptoasset} and \textit{cryptoliability} to refer to items whose value are contingent on blockchain technologies.
+Cryptoassets include cryptocurrencies and other tokens of tradeable value.
+Without loss of generality, we assume cryptocurrencies are native to their underlying blockchain, can be transacted directly, and are used to pay fees for transaction execution.
+Bitcoin and Ether are examples.
+For blockchains that allow developers to deploy custom decentralized apps, the apps might issue and manage the ownership of a custom tokens.
+In the case of Ethereum, these tokens are often ERC20 tokens, where ERC20 is sometimes misunderstood to mean what the token represents; rather, ERC20 is a technical standard about how token transactions are invoked.
+
+What a token represents varies across applications but includes at least of the following major categories.
+(1) Access tokens: a service is developed which requires its own custom tokens for using the service; (2) Backed tokens: a token issuer claims to be holding something valuable (material or digital) in reserve, and the token represents a claim on these reserves; (3) Equity tokens: a firm issues tokens to represent ownership shares of the company; and (4) Collectable tokens: the token itself is offered as a contemporary collector’s item.
+Digital tokens of these types predate blockchains; for example, (1) Linden dollars, (2) E-Gold, and (4) URLs are arguably examples.
+Equities (3) are almost entirely dematerialized (\eg paper stock certificates are rare) but operate closer to (2) with a central depository.
+
+Tokens and cryptocurrencies are issued to an initial set of owners through any mechanism of the issuer’s choosing.
+A popular option is auctioning a set of tokens to the public in an ``initial coin offering'' or ICO.
+This is intended to resemble the initial public offering (IPO) of a firm’s stock, but ICOs often lack any consumer protection or regulatory compliance.
+An ICO of an access token might raise capital for developing or improving the service that will use these tokens.
+Buyers obtain such tokens to lock in the purchase price (hedging) or for speculation.
+
+Any action that results in a firm borrowing a cryptoasset results in an offsetting cryptoliability.
+For example, an exchange service that holds bitcoin or tokens on behalf of its clients has both an asset (the cryptoasset it holds in its possession) and a liability (the obligation to repay its clients).
+Tokens could represent a debt instrument, like a bond, commercial paper, or repurchase agreement.
+In a recent pilot, a blockchain-based certificate of deposit was issued.
+This creates an asset for the investors (Western Assets, Pfitzer, etc.) and a liability for the issuer (National Bank of Canada with J.P.
+Morgan).
+
+Bitcoin and Ether are native to their blockchains.
+Other assets or liabilities are digital representations of an off-blockchain asset or liability.
+One example would be the recognition of a land deed on a blockchain in the form of a token.
+The blockchain must be invoked during the audit to validate ownership, the land itself is obviously not on the blockchain.
+
+To illustrate how a firm might come to possess a cryptoasset, consider four examples of firms that have actually sought audits or regulatory exemptions from audits\footnote{[Anonymized] Based on data provided to us by the financial regulator in the region where the authors work.}.
+A mining firm will invest in specialized computing equipment and electricity to generate cryptocurrencies it will hold as assets.
+An exchange service will hold demand deposits of cryptocurrencies or tokens, as well as governmental currencies, and allow its users to trade them.
+An investment fund will hold a portfolio of cryptoassets (\eg TIQ101-CF is 50\% bitcoin, 35\% ether, 15\% litecoin [c]) and sell shares to investors through a standard financial platform.
+Finally a firm initiating a token sale will raise capital in cryptocurrencies, held as an asset, in return for tokens that are not generally liabilities (it may also reserve some tokens as an additional asset).
+
+% [c] : https://3iq.ca/wp-content/uploads/2017/3iq-om-summary-en.pdf  <-- is this confidential? it is on public web but it says not to be distrubuted in public?
+
+%------------------------------------------------------------------------------------------------
+\subsection{Presentation of Cryptoassets}
+A financial report will classify assets and liabilities according to categories established by the auditing standards adhered to in the firm\'s reporting country (American Generally Accepted Accounting Principles in the United States and International Financial Reporting Standards (IFRS) in many other countries).
+The following discussion will apply IFRS although the considerations under US GAAP are similar.
+
+%ASK Erica for GAAP and IFRS references
+
+\paragraph{Cryptoassets.} IFRS do not provide specific standards for how to account for cryptoassets therefore their presentation is based on existing standards that were not conceived with the nature of these assets in mind.
+This results in a presentation of cryptoassets that does not necessarily reflect the underlying economic reality of the assets at hand.
+For instance, an investment portfolio that holds a combination of Bitcoin and Google stock for long-term capital appreciation purposes, would report the Bitcoin as an intangible asset and the Google stock as a short-term investment.
+The Google stock would be presented at its fair market value and any gains and losses on this investment would be immediately reported as part of net profit.
+
+The Bitcoin, on the other hand, would be presented as an intangible asset.
+This investment could either be presented at historical cost (what the company paid for the Bitcoin) or revalued to its fair market value.
+If the Bitcoin is reported at cost, any increases in value would not be recorded until the asset is sold (decreases in value below cost would be reported immediately).
+If the Bitcoin is reported at fair market value, any increases in value would be reported in Other Comprehensive Income, a special category that does not fall into net profit.
+This means that while the investment fund holds two investments, Bitcoin and Google stock, both for long-term growth purposes, the current standards would not allow these investments to recorded on the same basis.
+This also means that increases in value of Bitcoin or other cryptoassets are not recorded as part of net profit, which obfuscates a company\'s annual reported earnings and undermines their usefulness for investors.
+
+\paragraph{ICOs.} Currently, there is no guidance on how to account for proceeds raised during an ICO.
+During an ICO, a company issues its tokens in exchange for fiat or other cryptoassets, depending on the offering.
+However, the presentation of these funds will depend on what the ICO holder is entitled to receive in exchange for whatever they have given up.
+
+If the tokens received represent  a residual interest in the issuing firm, the tokens would be presented as part of share capital, like would be the case for traditional share issuances.
+However, most ICOs are not set out to give the holder an interest in the company as a whole, but rather represent an interest in a specific project.
+If the holder is owed some type of obligation, like access to a marketplace or participation in an, then recognition of the funds received as a liability would be appropriate.
+
+Under rare cases, the proceeds could be reported as revenue if the funds received do not qualify as either share capital or represent some ongoing obligation towards the ICO holder.
+However, we expect these instances to be fairly rare as it is unlikely that an investor would contribute to an ICO and not expect something of value in return.
+
+\paragraph{Legal Status.} One challenge for regulators can be determining whether or not a token is, in fact, a security for legal purposes and, therefore, whether or not regulation applies.
+Existing securities law is not clear on how to classify tokens and different classifications will apply to coins with different characteristics.
+To date, not a single ICO has been approved by the SEC~\cite{SECICO2017}.
+In Canada, securities regularities have approved several ICOs through a regulatory fast-track program.
+In Quebec, the provincial regulator approved the ICO of Impak Finance.
+In doing so, the regulator labeled the ICO\'s token, \textit{ImpakCoin}, as a security and waived several filing requirements, including the need for a prospectus, to facilitate the launch.
+Despite a desire for Canadian regulators to foster innovation through fast-track programs, securities regulators remain skeptical and have issued a notice cautioning investors of the risks in this sector~\cite{CSAICO2017}.
+
+\subsection{Takeaway}
+Several parties, including auditors, management and regulators, have an interest in ensuring that entities in the crypto space can obtain an audit, namely to satisfy regulatory requirements in order to attract capital.
+However, issues surrounding the presentation and measurement of these items on the financial statements undermine the potential information content of these statements.
+
+The following sections will present key issues that currently are troubling auditors and provide solutions or directions for future research.

### 2018-09-20 frontrunning/Latex/setup/table.tex

@@
 \centering
-\begin{tabular}{|c|c|}
+\begin{tabular}{|c|l|}
 \hline
-\textbf{DApp Category}    											& \textbf{DApp Names (Rank)} \\  \hline
+\textbf{DApp Category}    											& \textbf{Names (Ranking)} \\  \hline
 \multirow{6}{*}{Exchanges} 										& IDEX (1) \\ 
-															& \textit{ForkDelta, EtherDelta}(2) \\
-															& \textit{Bancor}(7) \\
-															& The Token Store(13) \\
-															& LocalEthereum(14) \\
-															& \textit{0x Protocol}(23) \\
+															& \textit{ForkDelta, EtherDelta} (2) \\
+															& \textit{Bancor} (7) \\
+															& The Token Store (13) \\
+															& LocalEthereum (14) \\
+															& \textit{0x Protocol} (23) \\
 															& Kyber (22) \\  \hline
 
-\multirow{9}{*}{\shortstack{Crypto-Collectible \\ Games \\ (ERC 721)}}		& \textit{CryptoKitties}(3) \\  
-															& Ethermon(4)\\
+\multirow{9}{*}{\shortstack{Crypto-Collectible \\ Games \\ (ERC 721)}}		& \textit{CryptoKitties} (3) \\  
+															& Ethermon (4)\\
 															& Cryptogirl (9)\\
 															& Gods Unchained TCG (12)\\
-															& Blockchain Cuties(15)\\
+															& Blockchain Cuties (15)\\
 															& ETH.TOWN! (16)\\
@@
 															& MLBCrypto Baseball (19)\\
-															& HyperDragons(25)\\ \hline
+															& HyperDragons (25)\\ \hline
 
@@
 															& FairDapp (11)\\
-															& Zethr(17) \\
+															& Zethr (17) \\
 															& dice2.win (20) \\ 
 															& PoWH 3D (8)	 \\ 
-															& Ether Shrimp Farm(21) \\  \hline
+															& Ether Shrimp Farm (21) \\  \hline
 
-\multirow{1}{*}{Name Services}									& \textit{Ethereum Name Service}(24)  \\  \hline
+\multirow{1}{*}{Name Services}									& \textit{Ethereum Name Service} (24)  \\  \hline
 
 \end{tabular}
-\caption{\footnotesize{Top 25 DApps based on recent user activity from \texttt{DAppRadar.com} on September 4th, 2018.
-DApps that are represented in Italic format are analyzied and discussed in this paper.}\label{tab:top25DApps}}
+\caption{\footnotesize{Top 25 DApps based on recent user activity from \texttt{DAppRadar.com} on September 4th, 2018. We discuss the DAps that are in italics.}\label{tab:top25DApps}}
 \end{table}

### 2018-09-20 auditing/Latex/sections/01-intro.tex
[auditing] till section 4 + fix citations and special characters

@@
 When assessing whether or not to take on a new client, auditors lack experience in this sector and therefore are unable to develop expectations of financial performance as a way of challenging financial statement assumptions.
-Due to the complex and rapidly changing technological environment, auditors are also unable to keep pace with the changes and develop the in-depth knowledge of their clients\' businesses required for performing an audit.
+Due to the complex and rapidly changing technological environment, auditors are also unable to keep pace with the changes and develop the in-depth knowledge of their clients\textquotesingle  businesses required for performing an audit.
 Finally, auditors are wary of accepting clients that hold a significant amount of cryptoassets as this space is largely unregulated.
@@
 The result is not a new protocol but a two-way knowledge transfer between professions that we hope is interesting to this audience.
-While displacing auditors is occasionally a target of cryptographers~\cite{narula_zkledger, dagher_provisions}, auditing itself is also occasionally studied directly at venues like Financial Cryptography
+While displacing auditors is occasionally a target of cryptographers~\cite{narula2018zkledger,dagher2015provisions}, auditing itself is also occasionally studied directly at venues like Financial Cryptography
 
@@
 Financial audits are central to the role of security regulators, who require publicly traded firms to obtain an annual unqualified audit opinion on their financial statements for consumer protection.
-Failure to do so, would put the company offside with the regulators\' requirements and could result in the company\'s shares being placed on cease-trade.
+Failure to do so, would put the company offside with the regulators\textquotesingle  requirements and could result in the company\textquotesingle s shares being placed on cease-trade.
 
@@
 \subsection{Presentation of Cryptoassets}
-A financial report will classify assets and liabilities according to categories established by the auditing standards adhered to in the firm\'s reporting country (American Generally Accepted Accounting Principles in the United States and International Financial Reporting Standards (IFRS) in many other countries).
+A financial report will classify assets and liabilities according to categories established by the auditing standards adhered to in the firm\textquotesingle s reporting country (American Generally Accepted Accounting Principles in the United States and International Financial Reporting Standards (IFRS) in many other countries).
 The following discussion will apply IFRS although the considerations under US GAAP are similar.
@@
 This means that while the investment fund holds two investments, Bitcoin and Google stock, both for long-term growth purposes, the current standards would not allow these investments to recorded on the same basis.
-This also means that increases in value of Bitcoin or other cryptoassets are not recorded as part of net profit, which obfuscates a company\'s annual reported earnings and undermines their usefulness for investors.
+This also means that increases in value of Bitcoin or other cryptoassets are not recorded as part of net profit, which obfuscates a company\textquotesingle s annual reported earnings and undermines their usefulness for investors.
 
@@
 In Quebec, the provincial regulator approved the ICO of Impak Finance.
-In doing so, the regulator labeled the ICO\'s token, \textit{ImpakCoin}, as a security and waived several filing requirements, including the need for a prospectus, to facilitate the launch.
+In doing so, the regulator labeled the ICO\textquotesingle s token, \textit{ImpakCoin}, as a security and waived several filing requirements, including the need for a prospectus, to facilitate the launch.
 Despite a desire for Canadian regulators to foster innovation through fast-track programs, securities regulators remain skeptical and have issued a notice cautioning investors of the risks in this sector~\cite{CSAICO2017}.
+
+%------------------------------------------------------------------------------------------------
 

### 2018-09-20 auditing/Latex/sections/02-body.tex
[auditting] some overall paper structure in Latex
[auditing] till section 4 + fix citations and special characters

--- 2018-09-17 auditing/Latex/sections/01-intro.tex
@@
 % !TEX root = ../main.tex
-\section{Introductory Remarks}
+\section{Key Issue: Existence of Assets and Occurence of Transactions}
 
-Blah blah blah.
+Auditors need to establish that assets and liabilities reported at a point in time are real and that the transactions reported over the year did, in fact, take place.
+The auditor must also ensure that the transactions were neither fraudulent nor illegal and had a legitimate business purpose.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Issue: Meta-information.} Assets and liabilities that are transacted on a publicly readable blockchain record basic details, like times and values, but auditors require further information to validate the nature of a transaction.
+For example, assume an employee\textquotesingle s salary is paid in Bitcoin.
+Bitcoin\textquotesingle s blockchain shows that a transaction occurred but it does not specify it as a salary; nor does it confirm basic details like the number of hours paid, if the nominal amount is BTC or a spot conversion from a governmental currency, and what deductions for tax or benefits were applied.
+Most importantly, it does not confirm the amount the employee was paid accurately reflects the number of hours worked at the authorized pay rate.
+Therefore, the company either requires a verbose secondary ledger to track these details or a Decentralized Application (DApp).
+This issue also underscores how, despite the immutability of the blockchain, the auditor remains necessary to validate the legitimacy of transactions.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Issue: Off-Blockchain Transactions.} Transactions may involve the exchange of cryptoassets for off-blockchain assets.
+For instance, a company may pay its supplier in Bitcoin for a shipment of raw materials.
+Although the Bitcoin is blockchain-native and that side of the transaction benefits from the consensus algorithm, the blockchain cannot verify that the right quantity or quality of raw materials were received in exchange for the consideration paid.
+Therefore, given that half of this transaction occurred off-blockchain, it would need to be audited like a traditional raw materials purchase.
+
+Given that financial statements report the summary of a company\textquotesingle s activities at a point in time or over the course of a certain period, the cutoff of transactions is also an important consideration.
+For instance, in the example above, if the auditor is verifying a company\textquotesingle s transactions for the year ended December 31, 2017, they must ensure that the Bitcoin was paid and the raw material was received before the end of the year to record the purchase in the 2017 fiscal year.
+Although the blockchain confirms the date the Bitcoin was paid, it cannot guarantee when the merchandise was received as this happens off-blockchain.
+Therefore, the cutoff of the transaction would be subject to traditional auditing methods.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Issue: Finality.} While blockchains are touted as immutable, the finality property (like all security properties) is subject to assumptions.
+Immutability of a blockchain is subject to consensus taken across miners according to computational ability.
+Consensus is not instant: a transaction might be included and then quickly dropped as consensus forms between different proposed chains.
+And it is never guaranteed to be final: an agreement within the computational majority of miners can unroll past transactions, For example, Ethereum\textquotesingle s miners branched the main blockchain to modify some past transactions~\cite{dupont2017experiments}.
+The challenge of finality was an important design consideration in the Bank of Canada\textquotesingle s Project Jasper which sought to establish a Distributed Wholesale Payment Systems.
+``Project Jasper was structured so that a transfer of [digital currency] was equivalent to a full and irrevocable transfer of the underlying claim on central bank deposits.” Given that on the Ethereum blockchain, transactions can be reversed, the work around for Project Jasper was to implement a “design feature (which) relates to the issuance of (digital currency) and is therefore independent of the platforms upon which Jasper was built.''~\cite{chapman2017project}.
+
+The issue of revocability is not uncommon for accountants.
+In many cases, sales agreements provide customers with the option to return merchandise within a pre-established period.
+When recording revenue, the accountant much estimate the percentage of returns and factor this into the amount of revenue to be recorded.
+The same concept could be applied for the issue of finality.
+The firm could estimate the amount of returns or reversals that are likely to occur and factor this into their transaction recognition.
+Alternatively, auditors could establish a generally accepted threshold (for instance, number of days) after which a transaction would be considered final.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Issue: Completeness.} Firms generally do not hide assets as this undermines their reported financial health, however a firm might hide an asset to shift its acquisition forward in time.
+Additionally, hiding liabilities promotes a firm\textquotesingle s solvency.
+Therefore, auditors are charged with determining that they have obtained the full measure of a firm\textquotesingle s transactions to ensure the completeness of the information under analysis.
+
+In a blockchain-enabled world, the blockchain contains the record of all transactions carried out during the year.
+If the auditor has a list of all the keys that belong to the entity under audit, they can easily obtain an account of all the transactions carried out on the blockchain during the period.
+However, this still raises the issue that the client may possess other, unreported keys, or have entered into side-arrangements with related parties.
+This risk is also present in traditional audits.
+While these challenges are magnified on a blockchain is magnified due to the pseudo-anonymity of this environment, the underlying challenge remains the same as it would in a traditional audit.
+
+There is always the possibility that, for instance, a client has not reported all keys in his possession to the auditor.
+Therefore, transactions on those keys would not be part of the known set of information under audit.
+However, this situation is not unlike a traditional audit.
+The client may have unreported bank accounts at a different bank than their usual institution that the auditor would not know about.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Issue: Transaction Complexity.} Bitcoin and Ethereum transact native currency according to established protocols, and Ethereum-based tokens gravitate toward standards as well.
+However nothing prevents DApps from transacting in complex ways.
+For example, one proposed DApp for crowdfunding projects would allow stakeholders to split off into a smaller DApp, taking a share of the assets from the parent DApp with it~\cite{dupont2017experiments}.
+Another example would be the Lightning Network~{poon2016bitcoin} which is second layer, off blockchain payment network that was implemented for scaling Bitcoin to increase throughput.
+The Lightning Network is more complex than simple Bitcoin payments and involves payment channels and routings.
+
+While firms may complicate their transactions either for economic benefits in order to obfuscate the true nature of their transactions, the onus is on the firm under audit to operate in an auditable fashion.
+In other words, while it is the auditor\textquotesingle s responsibility to design procedures to gain comfort over an entity\textquotesingle s operations, it is the responsibility of management to implement controls and procedures to ensure that the entity is audit-ready.
+Therefore, some complex operations, while economically sound, may be avoided to ensure the audibility of operations.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Issue: Transaction Pointers.} Blockchain transactions need to be uniquely identified to be pointed at by secondary financial records.
+Due to an implementation fault in Bitcoin, transactions broadcasted with one identifier might end up in the blockchain with a different identifier, which could lead a firm to conclude a transaction did not take place when in fact it did, but under an unexpected identifier~\cite{andrychowicz2015malleability} Some firms went bankrupt when their automated system kept honouring refund requests from a malicious entity claiming the refunds were not going through~\cite{trautman2014virtual,decker2014bitcoin}.
+The larger lesson here is that auditors cannot always safely abstract away low level implementation details.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Issue: Occurrence.} In order to validate that cryptoasset transactions actually took place during the year, auditors will look to reproduce the transactions carried out.
+By obtaining a listing of the client\textquotesingle s cryptographic keys, the blockchain can provide a complete history of the transactions that occurred during the year.
+Due to the immutable nature of the blockchain, the auditor can be assured that the transaction did take place as described.
+However, the auditor will still need to validate meta-information surrounding the transaction (see above) to validate the transaction\textquotesingle s reasonability.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Takeaway:} This section demonstrates that due to the immutable nature of the blockchain and its ability to report the totality of transactions conducted during the period, this technology provides a record upon which the auditor can obtain evidence to ascertain the occurrence of transactions.
+However, the auditor will continue to need to rely on external sources such as a verbose secondary ledger to validate the legitimacy and business purpose of those transactions.
 
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-
-\paragraph{Scope.} 
-Blah blah blah.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-
-%\paragraph{Contributions.} 
-%Our primary contributions are as follows.
-%
-%\begin{enumerate}
-%
-%\item Blah blah blah.
-%
-%\item Blah blah blah. 
-%
-%\item Blah blah blah. 
-%
-%\end{enumerate}

### 2018-09-20 auditing/Latex/sections/02-body.tex
[auditing] until section 5

@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+
+\section{Key Issue: Ownership}
+In addition to being satisfied with the existence of cryptoassets, auditors must be satisfied that the assets reported on the company’s balance sheet do in fact belong to the company.
+For traditional assets, firms might store assets with a custodian.
+This does not eliminate the issue of ownership, it simply shifts the concern from the firm’s audit to the audits of central custodians.
+Banks and organizations who provide custodial services are required to have robust internal controls over the safeguarding of assets in their care, and provide audited report supporting the reliability of their controls.
+
+\paragraph{Issue: Cryptographic keys.} For most cryptoassets, the asset is considered owned by Alice if Alice possesses a private signing key that can be used to sign a transfer of the asset.
+Through decentralized apps, alternative notions of ownership are possible to define, but this idea of a signing key is foundational and seen in bitcoin, ether, ERC20 tokens, etc.
+(not to mention earlier e-cash proposals dating back to the 1980s).
+Thus demonstrating knowledge of this key is necessary (but not sufficient, as we will discuss shortly) to demonstrating ownership.
+The most direct technique is to use a zero knowledge proof of knowledge of this private key, and staple in some information identifying the context of the proof.
+For standard proofs, this is cryptographically equivalent to simply signing a challenge message with the key\footnote{A Schnorr Sigma-protocol with the challenge hashed in using Fiat-Shamir is exactly a Schnorr signature and closely related to an ECDSA signature.}.
+Folklore protocols of sending small cash amounts from an allegedly owned account to the auditor to demonstrate control are also commonly noted in the literature (and used in at least one occasion [cite]).
+This offers similar security but adds ethical complexities for the auditor.
+% TODO: It requires more cryptography citations here! 
+% What to cite for the [cite] placeholder
+We note that while this cryptographic proof is necessary, it is not sufficient.
+What it proves is that the purported owner has access to the person holding the signing key.
+A malicious company might arrange for the owner of cryptoassets to engage in signing statements or moving test amounts fraudulently on their behalf.
+This issue is not new: an insolvent retail store might borrow inventory from elsewhere to inflate its assets during an audit, which will in this case involve a physical visit and inventory check by the auditor.
+Auditors mitigate this by arranging a common date for all audits of physical inventory, and similarly, cryptographic audits might be synchronized on a fixed schedule to prevent the same assets from being counted for different companies in different audits~\cite{dagher2015provisions}.
+
+\paragraph{Issue: Design Transparency.} For cryptoassets that are native to a blockchain, like Bitcoin or Ether, ownership is implemented at the protocol level and has been vetted over the lifetime of the blockchain.
+However many assets are created and owned through decentralized apps.
+Coding standards, such as the ERC20 token standard in Ethereum, might be followed but this standard only specifies necessary ways of transacting the tokens, not the mechanics of what ownership means.
+These mechanics can become complicated.
+For example, the DAO maintained ether and two types of tokens (DAO tokens and reward tokens) across four different internal accounts, and holders of DAO tokens could split off balances from these accounts into a new (two token, four account) DAO, in addition to certain types of withdrawals.
+Establishing ownership requires understanding the internal accounting of the applications maintaining the assets.
+
+\paragraph{Issue: Self-custodianship.} Cryptocurrency advocates point to its non-reliance on trusted third parties as key to its appeal [cite: CHI paper].
+Thus, the use of a custodian for cryptoassets (or more specifically, the private keys controlling the assets) is controversial.
+The advantage of a custodian is that it might more quickly specialize in security than end users, and this is certainly true for some users [cite: MIT].
+Self-custodianship of non-digital assets, such as diamonds for a jewelry retailer or cash for a currency exchange, is already a concern for financial auditors.
+Further, custodianship over cryptographic keys is a financial factor in other sectors, such as certificate authorities like Versign or Symantec which maintain keys critical to HTTPS and DNSSEC [cite].
+To date, no blockchain custodian or exchange has been able to produce a report that supports the reliability of their internal controls in order to provide auditors with comfort over the sufficiency of their systems.
+Therefore, auditors cannot rely on the internal controls present at custodians to obtain comfort over the ownership assertion.
+
+\paragraph{Takeaway:} In order for auditors to validate ownership, they must rely on cryptographic proofs as a first step.
+However, in order to avoid double-counting of keys, an industry standard common date should be arranged to provide a generally agreed upon ``state of the world'' where keyholders can demonstrate ownership.

### 2018-09-20 auditing/Latex/sections/02-body.tex
[auditing] < section 6

@@
 
+%---------+++++++++++++++++++-----------------
 \paragraph{Issue: Cryptographic keys.} For most cryptoassets, the asset is considered owned by Alice if Alice possesses a private signing key that can be used to sign a transfer of the asset.
@@
 For standard proofs, this is cryptographically equivalent to simply signing a challenge message with the key\footnote{A Schnorr Sigma-protocol with the challenge hashed in using Fiat-Shamir is exactly a Schnorr signature and closely related to an ECDSA signature.}.
-Folklore protocols of sending small cash amounts from an allegedly owned account to the auditor to demonstrate control are also commonly noted in the literature (and used in at least one occasion [cite]).
+Folklore protocols of sending small cash amounts from an allegedly owned account to the auditor to demonstrate control are also commonly noted in the literature (and used in at least one occasion \todo{[cite]}).
 This offers similar security but adds ethical complexities for the auditor.
-% TODO: It requires more cryptography citations here! 
+\todo{ It requires more cryptography citations here!  }
 % What to cite for the [cite] placeholder
@@
 
+%---------+++++++++++++++++++-----------------
 \paragraph{Issue: Design Transparency.} For cryptoassets that are native to a blockchain, like Bitcoin or Ether, ownership is implemented at the protocol level and has been vetted over the lifetime of the blockchain.
@@
 
-\paragraph{Issue: Self-custodianship.} Cryptocurrency advocates point to its non-reliance on trusted third parties as key to its appeal [cite: CHI paper].
+%---------+++++++++++++++++++-----------------
+\paragraph{Issue: Self-custodianship.} Cryptocurrency advocates point to its non-reliance on trusted third parties as key to its appeal \todo{[cite: CHI paper]}.
 Thus, the use of a custodian for cryptoassets (or more specifically, the private keys controlling the assets) is controversial.
-The advantage of a custodian is that it might more quickly specialize in security than end users, and this is certainly true for some users [cite: MIT].
+The advantage of a custodian is that it might more quickly specialize in security than end users, and this is certainly true for some users \todo{[cite: MIT]}.
 Self-custodianship of non-digital assets, such as diamonds for a jewelry retailer or cash for a currency exchange, is already a concern for financial auditors.
-Further, custodianship over cryptographic keys is a financial factor in other sectors, such as certificate authorities like Versign or Symantec which maintain keys critical to HTTPS and DNSSEC [cite].
+Further, custodianship over cryptographic keys is a financial factor in other sectors, such as certificate authorities like Versign or Symantec which maintain keys critical to HTTPS and DNSSEC \todo{[cite]}.
 To date, no blockchain custodian or exchange has been able to produce a report that supports the reliability of their internal controls in order to provide auditors with comfort over the sufficiency of their systems.
@@
 
+%---------+++++++++++++++++++-----------------
 \paragraph{Takeaway:} In order for auditors to validate ownership, they must rely on cryptographic proofs as a first step.
 However, in order to avoid double-counting of keys, an industry standard common date should be arranged to provide a generally agreed upon ``state of the world'' where keyholders can demonstrate ownership.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+
+\section{Key Issue: Valuation}
+
+When values are reported on financial statements, they must be reported in the functional currency of the firm, meaning the primary governmental currency used.
+A challenge for blockchain entities is to determine the valuation of cryptoassets on the financial statement date or the conversion rate for sales and expenditures made throughout the year.
+Auditors must be satisfied that the values reported in the financial statements are accurate and represent the underlying economic reality.
+While fair valuation is important for establishing a firm’s financial health, it is also important for auditors to use in determining what to focus on during the audit itself.
+The objective of an audit is to certify that the financial statements are free of material misstatement.
+This does not mean that the statements are free of all errors; it merely means that the statements are free of errors that could substantially change the opinion of an informed user.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Issue: Fair value.} A significant obstacle for obtaining audited financial statements is the determination of a fair value for cryptoassets.
+For foreign currencies, firms value them at the closing rate on the transaction date, as reported by the Central Bank in which the firm operates.
+No universal central bank offers rates for currency-like cryptoassets.
+At the time of writing, one Fortune 500 financial firm, CME, offers a daily reference rate for Bitcoin, but not other cryptocurrencies or cryptoassets.
+Without an authoritative reference rate, current market quotes may be considered.
+According to IFRS 13~\cite{ifrs201113}, fair value is measured using the ``principal market for the asset or liability; or  in the absence of a principal market, in the most advantageous market for the asset or liability.'' The principal market for a cryptoasset may not be apparent.
+For instance, a company may purchase cryptoassets from several different exchanges or parties.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Issue: Bans.} There regulatory rules for cryptoassets differ based on the jurisdiction; for instance, cryptoassets are absolutely banned in Algeria, Bolivia, and Pakistan (among others), and implicitly banned under investor protection rules in Colombia, Saudi Arabia, and China (among others)~\cite{cryptoLegalityWiki}.
+Also there are banking limitations for companies dealing directly with cryptoassets in some other countries such as Canada, India and Thailand.
+This limitation impacts the valuation of cryptoassets on hand.
+For instance, assume a company acquires a token when it is legal to do so, and several months later, the government prohibits companies in that nation from holding that token.
+While this token may be traded in other parts of the world, the fair market value to its holder in the restrictive nation is arguably zero as their ability to use or sell the token is limited.
+Therefore, when determining the fair value of assets at hand, the auditor must consider the regulatory environment surrounding cryptoassets.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Issue: Inadequate Liquidity.} While bitcoin and ether enjoy around-the-clock trading across many markets, lesser known coins, tokens, assets, or liabilities may trade slowly, in low volumes.
+Generally speaking, low liquidity results in stale last sale prices, and large bid-ask spreads.
+This challenging but not unprecedented in financial auditing: privately held stocks and over-the-counter financial instruments share a similar profile.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Issue: Geographical Variation.} Because bitcoin can be moved digitally without any geographic restrictions, it should be the case that any variation in bitcoin prices across exchanges would be consumed by arbitrageurs.
+However, empirically this is not the case due to fees, settlement delays, and other frictions with exchange services \todo{[cite]}.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Issue: Fungibility.} Blockchains generally preserve a full transaction record for each (division of a) cryptoasset.
+This may lead to price discrepancies between equal amounts of cryptoassets, where assets with clear provenance might be preferred to assets with long transaction records involving unknown entities and possible fraud, theft, or other issues that might legally encumber the current holder of the asset.
+The materiality of a premium for ``clean'' cryptoassets is an open research question; some markets for fresh bitcoin were announced but never materialized \todo{[c]}.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Issue: Volatility.} Assuming the valuation of cryptoassets can be made, it is important to consider how stable this valuation will be over time.
+The cryptoasset with the richest historical data is bitcoin and by any standard measure of volatility, its volatility currently exceeds the most traded currencies and commodities.
+If a firm’s balance sheet consists of a large unbalanced\footnote{An exchange service that holds bitcoin on behalf of its users will have the bitcoin listed as both an asset and a liability, thus they are balanced and price movements have no impact on their solvency.} cryptoassets or cryptoliabilities, price movements significantly impact its financial health and even its solvency.
+A comparable scenario is a financial firm holding exotic, volatile securities or derivatives---in these cases, auditors might ``stress test'' the firm’s balance sheet under different valuations.
+Starting with bitcoin and moving to other cryptoassets, researchers should consider procedures for the ``shelf life'' of valuations and realistic stress tests.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Issue: Financial Projections.} Financial statements are prepared under the assumption that the reporting entity will continue operating for at least 12 months after the balance sheet date.
+Auditors are required to perform procedures to verify the reasonableness of this assumption.
+For instance, the auditors could examine projections where the cryptoassets the firm holds increase or decrease in value, however this may be difficult due to  the high volatility of cryptoassets.
+Bitcoin, for instance, increased 10-fold over the last half of 2017.
+The problem is even more substantial for companies that hold alt-coins which may have thin markets and short histories upon which to compare financial projections.
+A remedy would be the disclosure of significant assumptions underlying these projections to satisfy financial statement users of the company’s projected financial health.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Takeaway:} While the valuation of cryptoassets with large trading volumes like Bitcoin and Ether would be fairly straightforward by referring to values in an active market, the valuation of coins with low liquidity may be more difficult.
+However, by using financial modelling using different assumptions for volatility, this challenge is not insurmountable.

### 2018-09-20 auditing/Latex/sections/02-body.tex
[auditing] < section 7

@@
 \section{Key Issue: Ownership}
-In addition to being satisfied with the existence of cryptoassets, auditors must be satisfied that the assets reported on the company’s balance sheet do in fact belong to the company.
+In addition to being satisfied with the existence of cryptoassets, auditors must be satisfied that the assets reported on the company\textquotesingle s balance sheet do in fact belong to the company.
 For traditional assets, firms might store assets with a custodian.
-This does not eliminate the issue of ownership, it simply shifts the concern from the firm’s audit to the audits of central custodians.
+This does not eliminate the issue of ownership, it simply shifts the concern from the firm\textquotesingle s audit to the audits of central custodians.
 Banks and organizations who provide custodial services are required to have robust internal controls over the safeguarding of assets in their care, and provide audited report supporting the reliability of their controls.
@@
 \section{Key Issue: Valuation}
-
 When values are reported on financial statements, they must be reported in the functional currency of the firm, meaning the primary governmental currency used.
@@
 Auditors must be satisfied that the values reported in the financial statements are accurate and represent the underlying economic reality.
-While fair valuation is important for establishing a firm’s financial health, it is also important for auditors to use in determining what to focus on during the audit itself.
+While fair valuation is important for establishing a firm\textquotesingle s financial health, it is also important for auditors to use in determining what to focus on during the audit itself.
 The objective of an audit is to certify that the financial statements are free of material misstatement.
@@
 The cryptoasset with the richest historical data is bitcoin and by any standard measure of volatility, its volatility currently exceeds the most traded currencies and commodities.
-If a firm’s balance sheet consists of a large unbalanced\footnote{An exchange service that holds bitcoin on behalf of its users will have the bitcoin listed as both an asset and a liability, thus they are balanced and price movements have no impact on their solvency.} cryptoassets or cryptoliabilities, price movements significantly impact its financial health and even its solvency.
-A comparable scenario is a financial firm holding exotic, volatile securities or derivatives---in these cases, auditors might ``stress test'' the firm’s balance sheet under different valuations.
+If a firm\textquotesingle s balance sheet consists of a large unbalanced\footnote{An exchange service that holds bitcoin on behalf of its users will have the bitcoin listed as both an asset and a liability, thus they are balanced and price movements have no impact on their solvency.} cryptoassets or cryptoliabilities, price movements significantly impact its financial health and even its solvency.
+A comparable scenario is a financial firm holding exotic, volatile securities or derivatives---in these cases, auditors might ``stress test'' the firm\textquotesingle s balance sheet under different valuations.
 Starting with bitcoin and moving to other cryptoassets, researchers should consider procedures for the ``shelf life'' of valuations and realistic stress tests.
@@
 The problem is even more substantial for companies that hold alt-coins which may have thin markets and short histories upon which to compare financial projections.
-A remedy would be the disclosure of significant assumptions underlying these projections to satisfy financial statement users of the company’s projected financial health.
+A remedy would be the disclosure of significant assumptions underlying these projections to satisfy financial statement users of the company\textquotesingle s projected financial health.
 
@@
 However, by using financial modelling using different assumptions for volatility, this challenge is not insurmountable.
+
+\section{Other Auditing Issues}
+
+\paragraph{Issue: Reliability of Blockchain Records.} Another challenge for auditors is determining what type of evidence or records constitute sufficient and appropriate audit evidence.
+In other words, an auditor must be satisfied that the records on the blockchain are reliable.
+How can we satisfy auditors that blockchain records are reliable
+
+\begin{enumerate}
+\item How can we rely on blockchain?
+Has anyone tested it?
+For example, maybe Bitcoin is reliable due to large user base but what about more niche blockchain?
+How can I validate accuracy of mining procedures?
+Reliability of transaction records?
+How do I know that changes to blockchain code made and not undermine reliability?
+\end{enumerate}
+\todo{there are some comments on the google docs regarding this subsection that should be addressed?}
+Traditionally, auditors depend on obtaining audit evidence from external parties as it is deemed as more objective or trustworthy than internal firm documents.
+For example, auditors will obtain confirmation from a bank of the amount of cash held at year end (a third party) rather than rely on internal records of banking transactions.
+Auditors traditionally rely on banks, investment companies, and lawyers as conventional sources of external confirmations.
+However, a risk always exists that there is fraud or error at these institutions.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Issue: Technical Literacy of Accounting Professionals.} To carry out an audit, auditors must possess sufficient knowledge in a subject area to understand the subject matter under audit and be able to question its underlying assumptions.
+This can be achieved through industry specialization, training or by relying on subject matter experts to provide knowledge in a particular area.
+Presently, many auditors are refusing mandates in the blockchain sector due to a lack of technological know-how regarding how to effectively carry out these audits.
+The risk of taking on such an audit (referred to as \textit{audit risk}) is too high, especially given numerous recent frauds in this sector.
+For instance, PinCoin raised over \$660M in an ICO before the management team vanished~\cite{techcrunchscammers}.
+However, this issue can be overcome by engaging multidisciplinary teams that can leverage the business knowledge of auditors with the technical know-how of computer scientists.
+These types of teams will also provide auditors with increased awareness of security threats.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Issue: What is an expert?} Oftentimes auditors rely on experts to provide assistance in auditing highly specialized asset classes.
+For instance, auditors often engage Chartered Business Valuators to assist in the evaluation of property like land and buildings.
+These professionals are engaged due to their subject matter expertise and experience in the field.
+In the blockchain sector, it is unlikely that any one individual would constitute an expert for audit purposes.
+Given that this sector has barely been in existence for a decade, if may be difficult to assess what constitutes an experienced or non-experienced professional.
+Furthermore, auditors are required to perform procedures to assess the assumptions used by the expert.
+The more likely alternative would be to engage multidisciplinary teams that have expertise in cryptography, security and business to assist the auditor in obtaining comfort over specialized blockchain assets and liabilities.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Issue: Financial Literacy of Technology Professionals} While auditors must learn more about the technology, managers of companies in the blockchain space must also learn about the internal controls required to safeguard against errors, misappropriation of assets and fraud.
+Given that financial statements are ultimately the responsibility of management and that senior management must certify the internal controls as part of the financial statement disclosures, managers have an incentive to implement a control environment that promotes a strong tone at the top, ethical conduct, and oversight of the financial reporting function.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Issue: Internal Controls.} It is necessary for a firm to be able to demonstrate the existence and ownership of its crypto-assets, however it must further demonstrate that it has adequate procedures in place to prevent or detect fraud and theft.
+Consider a firm holding DAO tokens.
+Internally, it must ensure proper controls over the signing keys these DAO tokens are assigned to.
+External to the firm, the DAO application maintaining these tokens on Ethereum\textquotesingle s blockchain must itself be secure (which in the case of the DAO, it was not).
+Auditing internal procedures over cryptographic keys is not unprecedented---maintaining certificate authority keys is critical to some security firm\textquotesingle s financial prospects (a security breach at one firm, \textit{DigiNotar}, bankrupted it~\cite{zetter2011diginotar}).
+Symantec\textquotesingle s self-custodianship over these keys involves elaborate security ceremonies whenever they are required \todo{[Cite]}.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Issue: Materiality.} Materiality is considered to be any value that is significant enough to have an impact on the user\textquotesingle s decision-making, and GAAS dictates that materiality for profitable entities be set at 5\% of pre-tax income.
+This means that, in aggregate, the sum of identified and extrapolated errors identified by auditors during their audit cannot exceed 5\% of pre-tax income for a clean opinion to be issued.
+However, companies may manipulate their selection of accounting policies to influence their net income in order to increase materiality.
+This means auditors would only look at items over a higher threshold, leaving smaller amounts subject to a lower level of scrutiny and greater opportunity for fraud or error.
+However, this issue is possible for all clients and therefore auditors would be aware of and design procedures to address this risk for all mandates.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Issue: Forks and Airdrops.} Existing accounting standards do not contemplate how to account for non-reciprocal transfers of assets like in the case of forks or airdrops.
+For example, in August 2017, when a hard fork created Bitcoin Cash from Bitcoin, holders of Bitcoin had two types of assets on hand.
+Bitcoin Cash was not paid for but resulted from a split between the two currencies.
+However, if existing accounting standards require the measurement of transactions at historical cost (what was paid for the assets), then recipients of Bitcoin Cash would report this new asset on their books at a value of \$0.
+Certainly, this does not represent the true value acquired through the fork.
+Therefore, auditors must address the issue of an accounting standard that does not contemplate how to measure the value of cryptoassets when considering whether the financial statements they are reporting on are accurate in all substantial respects.
+More commonly for ERC-20 tokens on Ethereum, the recipient of the tokens don\textquotesingle t have the option to reject the deposits nor would get notified of the new tokens received, which could result in issues with completeness.
+
+%---------+++++++++++++++++++-----------------
+\paragraph{Issue: Detection of Fraud.} An auditor conducting an audit in accordance with GAAS is responsible for obtaining reasonable assurance that the financial statements taken as a whole are free from material misstatement, whether caused by fraud or error.
+Owing to the inherent limitations of an audit, there is an unavoidable risk that some material misstatements or fraud may not be detected, even though the audit is properly planned and performed in accordance with GAAS.
+Due to the complex and rapidly changing nature of this sector, auditors are especially weary of fraud risk in this area.
+However, not all frauds that occur this space are new kinds of fraud.
+For instance, Ponzi schemes which have existed since they were perfected by Charles Ponzi in the early twentieth century~\cite{ponzi2001rise}.
+In 2017, OneCoin was found to have raised over \$350M of funds from investors for an ICO that was a Ponzi scheme~\cite{atlanticCryptoPonzi2017}.
+Stories like this only reinforce the perception in the auditing community of the dangers of operating in this space.
+However, auditors can protect themselves by ensuring that they only work with reputable clients.
+Managers can demonstrate their commitment to sound business practices by adopting controls that ensure KYC and AML rules are adhered to.

### 2018-09-20 auditing/Latex/sections/01-intro.tex
[auditing] until section 5
[auditing] < section 6
[auditing] done with transition + fixed citations

@@
 In addition to an audited statement, the firm will produce quarterly statements that are reviewed by a third party auditor to a less rigorous standard.
+
+\todo{Note that there are auditing and accounting papers in the bib/zotero that have not been cited here!}
 
@@
 The following discussion will apply IFRS although the considerations under US GAAP are similar.
-
-%ASK Erica for GAAP and IFRS references
+\todo{ GAAP and IFRS citations  }
 
@@
 This results in a presentation of cryptoassets that does not necessarily reflect the underlying economic reality of the assets at hand.
-For instance, an investment portfolio that holds a combination of Bitcoin and Google stock for long-term capital appreciation purposes, would report the Bitcoin as an intangible asset and the Google stock as a short-term investment.
+For instance, an investment portfolio that holds a combination of Bitcoin and Google stock for long-term capital appreciation purposes, would report the Bitcoin as an intangible asset~\cite{RCGTIFRsCrypto2018} and the Google stock as a short-term investment.
 The Google stock would be presented at its fair market value and any gains and losses on this investment would be immediately reported as part of net profit.

### 2018-09-20 auditing/Latex/sections/02-body.tex
[auditing] done with transition + fixed citations

@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-
 \section{Key Issue: Valuation}
@@
 
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
 \section{Other Auditing Issues}
@@
 \begin{enumerate}
-\item How can we rely on blockchain?
+\item[$\bullet$] How can we rely on blockchain?
 Has anyone tested it?
@@
 Managers can demonstrate their commitment to sound business practices by adopting controls that ensure KYC and AML rules are adhered to.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+\section{Discussion and Research Agenda}
+\todo{Check out the notes on the google docs regarding this section}
+
+Overall, this paper has demonstrated that, in comparison to traditional audits, audits of clients that hold material amounts of cryptoassets are complex but not impossible.
+For instance, while current accounting standards result in the presentation of an accounting fiction that is not always linked to the underlying use of crypto, adequate note disclosure can provide financial statement users with sufficient information in order to understand the underlying crypto operations.
+
+From our discussions with practitioners, existence, valuation and ownership were often cited as the three main stumbling blocks to providing an audit opinion.
+However, we argue that these issues are not insurmountable if industry guidelines are put into place to allow auditors to verify their client’s cryptographic keys against a “state of the world” at a generally accepted point in time.
+Verifying existence and ownership largely hinges on an auditor’s ability to verify the contents of a client’s cryptographic keys.
+However, the auditor must be certain that these keys in fact belong to the client and do not simply represent access to an account.
+Once ownership has been proven, the auditor can rely on the immutable properties of the blockchain to verify existence as the blockchain provides the entire record of transactions since the blockchain’s inception.
+The issue of key sharing is important but is not unlike a situation in the real world where a related party could give the entity under audit a large sum of cash to hold at year end and report on their financial statement to buoy their financial performance.
+
+Volatility does complicate the valuation of alt-coins and other coins with low trading volumes.
+However, many other exotic securities exist where accountants rely on complex financial modelling to determine a price.
+
+In sum, this paper argues that although auditors are right to be cautious to enter a new sector where clients not be initiated to the importance of internal controls and where numerous frauds have recently been perpetrated, audits are possible.
+Audit risk can be reduced through proper vetting of clients and management teams.
+Alternatively, accounting firms can provide advisory services to clients in anticipation of going public in order to ensure that these clients implement robust internal controls to support their financial reporting function.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+\section{Concluding Remarks}
+
+\todo{Check out the notes on the google docs regarding this section}

### 2018-09-20 auditing/Latex/sections/01-intro.tex
[auditing] minor changes

@@
 An exchange service will hold demand deposits of cryptocurrencies or tokens, as well as governmental currencies, and allow its users to trade them.
-An investment fund will hold a portfolio of cryptoassets (\eg TIQ101-CF is 50\% bitcoin, 35\% ether, 15\% litecoin [c]) and sell shares to investors through a standard financial platform.
+An investment fund will hold a portfolio of cryptoassets (\eg TIQ101-CF is 50\% bitcoin, 35\% ether, 15\% litecoin \todo{[c]: look at the comment below in latex}) and sell shares to investors through a standard financial platform.
 Finally a firm initiating a token sale will raise capital in cryptocurrencies, held as an asset, in return for tokens that are not generally liabilities (it may also reserve some tokens as an additional asset).

### 2018-09-20 auditing/Latex/sections/02-body.tex
[auditing] minor changes

@@
 \end{enumerate}
-\todo{there are some comments on the google docs regarding this subsection that should be addressed?}
+
+\todo{there are some comments on the google docs regarding this subsection that should be addressed(?)}
+
 Traditionally, auditors depend on obtaining audit evidence from external parties as it is deemed as more objective or trustworthy than internal firm documents.

### 2018-09-20 auditing/Latex/sections/01-intro.tex
[auditing] reflect Erica's modifications

@@
 
-\paragraph{Cryptoassets.} IFRS do not provide specific standards for how to account for cryptoassets therefore their presentation is based on existing standards that were not conceived with the nature of these assets in mind.
+\paragraph{Cryptoassets.} IFRS does not provide specific standards for how to account for cryptoassets therefore their presentation is based on existing standards that were not conceived with the nature of these assets in mind.
 This results in a presentation of cryptoassets that does not necessarily reflect the underlying economic reality of the assets at hand.
@@
 To date, not a single ICO has been approved by the SEC~\cite{SECICO2017}.
-In Canada, securities regularities have approved several ICOs through a regulatory fast-track program.
-In Quebec, the provincial regulator approved the ICO of Impak Finance.
-In doing so, the regulator labeled the ICO\textquotesingle s token, \textit{ImpakCoin}, as a security and waived several filing requirements, including the need for a prospectus, to facilitate the launch.
+In Canada, securities regularities have approved several ICOs through a regulatory fast-track program~\cite{fastTrackICOImpakt}.
 Despite a desire for Canadian regulators to foster innovation through fast-track programs, securities regulators remain skeptical and have issued a notice cautioning investors of the risks in this sector~\cite{CSAICO2017}.

### 2018-09-20 auditing/Latex/sections/02-body.tex
[auditing] reflect Erica's modifications

@@
 Therefore, the company either requires a verbose secondary ledger to track these details or a Decentralized Application (DApp).
-This issue also underscores how, despite the immutability of the blockchain, the auditor remains necessary to validate the legitimacy of transactions.
 
@@
 Therefore, given that half of this transaction occurred off-blockchain, it would need to be audited like a traditional raw materials purchase.
-
-Given that financial statements report the summary of a company\textquotesingle s activities at a point in time or over the course of a certain period, the cutoff of transactions is also an important consideration.
-For instance, in the example above, if the auditor is verifying a company\textquotesingle s transactions for the year ended December 31, 2017, they must ensure that the Bitcoin was paid and the raw material was received before the end of the year to record the purchase in the 2017 fiscal year.
-Although the blockchain confirms the date the Bitcoin was paid, it cannot guarantee when the merchandise was received as this happens off-blockchain.
-Therefore, the cutoff of the transaction would be subject to traditional auditing methods.
 
@@
 If the auditor has a list of all the keys that belong to the entity under audit, they can easily obtain an account of all the transactions carried out on the blockchain during the period.
-However, this still raises the issue that the client may possess other, unreported keys, or have entered into side-arrangements with related parties.
+However, this still raises the issue that the client may have entered into side-arrangements with related parties.
 This risk is also present in traditional audits.
@@
 %---------+++++++++++++++++++-----------------
-\paragraph{Issue: What is an expert?} Oftentimes auditors rely on experts to provide assistance in auditing highly specialized asset classes.
+%\paragraph{Issue: What is an expert?} Oftentimes auditors rely on experts to provide assistance in auditing highly specialized asset classes.
 For instance, auditors often engage Chartered Business Valuators to assist in the evaluation of property like land and buildings.

### 2018-09-20 frontrunning/Latex/sections/paper.tex
edits

@@
 % @J : intro needs lots of love.
+% Jeremy: Will work on this very last, once I know what the paper is actually about :)
 
@@
 
-\emph{Front-running} is analogous to any course of action during which a person or entity benefits from prior access to inside or confidential market information about upcoming transactions and trades, albeit the problem can occur in both financial and non-financial systems.
-In traditional exchanges, traders would gather in same physical locations to announce their position in the market, in case of receiving a large order from a client, the broker might say this loud and other people around the table could be informed.
-Therefore, a malicious trader would run in front of that order and put his own transaction in-between (before the trade was executed) and hence profit from the price increase of the stock.
-%In fact, a group of market participants obtain non-public market information which allows them to front-run other user\'s trades by putting their orders ahead of those trades and benefit from the advance knowledge of pending client orders.
-The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty~\cite{liang2005distressed}.
-Any sort of front-running activity within the financial markets is considered as an unethical and illegal practice as it is unfairly beneficial for a few market participants who have the privilege of acting on this information and taking advantages at the expense of the investors.
+\emph{Front-running} is a course of action where someone benefits from early access to market information about upcoming transactions and trades, typically because of a privileged position along the transmission of this information.
+The problem can occur in both financial and non-financial systems.
+In traditional stock exchanges, floor traders might overhear a broker's negotiation with her client over a large purchase, and literally race the broker to buy first, potentially profiting when the large sale temporarily reduces supply of the stock.
+Brokers might also frontrun their own client's orders by purchasing stock for themselves between receiving the instruction to purchase from the client and actually executing the purchase (similar techniques can be used for large sell orders).
+Front-running is unethical and illegal in jurisdictions with mature securities regulation.
+
+% Jeremy: I don't real;y understand the below so dropping if no one protests. 
+%The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty~\cite{liang2005distressed}.
 
 \subsection{Literature on Traditional Front-running}\label{traditionalFrontrunning}
-As traditional front-running has been the subject of discussion for decades, there are many works of literature on this subject.
+%As traditional front-running has been the subject of discussion for decades, there are many works of literature on this subject.
 Here we focus on the historical context and how the regulations evolved to be what they are today.\\
-Front-running was first appeared on the Chicago Board Options Exchange (\textit{CBoE})~\cite{markham1988front}, and was defined by \textit{Securities Exchange Commission} in 1977 as the following:
+Front-running was first observed on the Chicago Board Options Exchange (\textit{CBoE})~\cite{markham1988front}, and was defined by Securities Exchange Commission \textit{(SEC)} in 1977 as:
 \begin{quote}
-The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.
-~\cite{sec1978optionsmarket}
+The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}
 \end{quote}
@@
 
-On the years after there were ongoing discussions between self-regulatory exchanges (\eg \textit{CBoE}) and \textit{SEC} to regulate, detect and define laws and policies to deal with front-running~\cite{markham1988front}, with \textit{SEC} stating:
-\begin{quote}
-It seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge.
-\footnote{Securities Exchange Act Release No.
+Self-regulating exchanges (\eg \textit{CBoE}) and the \textit{SEC} spent the ensuing years planning how to detect and outlaw front-running practices~\cite{markham1988front}.
+The \textit{SEC} stated: ``It seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge.\footnote{Securities Exchange Act Release No.
 14156, November 19, 1977, (Letter from George A.
 Fitzsimmons, Secretary, Securities, and Exchange Commission to Joseph W.
-Sullivan, President  CBoE).}
-\end{quote}
+Sullivan, President  CBoE).}'' The \textit{CBoE} tried to educate their members on existing rules, however differences in opinion regarding the unfairness of front-running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~\cite{sec1978optionsmarket}.
 
-Defining what exactly was considered illegal front-running required more knowledge of how these new markets behaved.
-\textit{CBoE} and other exchanges (and brokers) issued educational circulars for their members asserting that front-running violates existing rules, with some examples of what is considered front-running.
-However, the difference of opinion regarding the unfairness of front-running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~\cite{sec1978optionsmarket}.
+We refer the reader interested in further details on the early regulatory history of front-running to Markham~\cite{markham1988front}.
+Initially front-running policies applied only to certain option markets.
+In 2002, the rule was expanded to cover all security futures~\cite{finra_2002}.
+In 2012, it was expanded further with the new amendment, FINRA Rule 5270, to cover trading in options, derivatives, or other financial instruments overlying a security with only a few exceptions~\cite{sec2012frontrunning, finra_2012}.
 
-Further reading on the early details on the history and challenges of detecting and regulating front-running is extensively written by Markham~\cite{markham1988front} . %add a more recent publication?
-
-Initially the front-running policies only applied to certain option markets, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{finra_2002},  then again in 2012 with the new amendment, FINRA Rule 5270, the front-running rule was extended to cover trading in options, derivatives, or other financial instruments overlying a security with a few exceptions~\cite{sec2012frontrunning, finra_2012}.
-
-\subsection{Blockchain Front-running} \label{sec:Front Running on the Blockchains}
+\subsection{Background on Blockchain Front-running} \label{sec:Front Running on the Blockchains}
 

### 2018-09-21 frontrunning/Latex/sections/paper.tex
more changes

@@
 
-The concept of  \emph{front-running} is decades old starting with early financial markets.
+Blockchain technology enables smart contracts or decentralized applications (DApps).
+Function calls (or transactions) to the DApp are processed by a decentralized network.
+Transactions are finalized in stages: they (generally) first relay around the network, then are selected by a miner and put into a valid block, and finally the block is well-enough incorporated that is unlikely to be reorganized.
+Front-running is an attack where a malicious node observes a transaction after it is broadcast but before it is finalized, and attempts to have its own transaction confirmed before or instead of the observed transaction.
+Whether this attack is beneficial depends on the logic of the DApp itself.
+
+In this paper, we perform a number of case studies of DApps on Ethereum (a popular blockchain supporting DApps) that are volnerable to front-running attacks.
+We draw the cases from the top 25 most active DApps,\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} as well as ICOs which are absent from this list during a sampling period.
+xxx tend to appear on this list when they are actively issued.
+benefit of this attack varies on what the DApps is doing but, this attack .
+
+%The concept of  \emph{front-running} is decades old starting with early financial markets.
 Initially, the traders required to be physically available in the exchange office to deliver the bids and offers, and some traders, in the knowledge of future market change, could run in front of the others to get their orders ahead of the change in the market to profit from the price change.
@@
 
+As a preview, in Section~\ref{sec:frontrunningExchanges}), we examine Bancor~\cite{hertzog2017bancor}, a decentralized exchange that operates similar to traditional stock markets and is likewise volunerable to front-running.
+Domain name frontrunning occurs when a user uses a domain registrar to inquire if a domain is available for purchase, and the query triggers the registrar to purchase the domain in anticipation that it can sell it to the user.
+In Section~\ref{sec:ens}, we examine decentralized namespaces like Ethereum Name Service and academic works like Ghazal~\cite{moosavighazal} where relaying nodes and miners see Alice's attempt to purchase a domain name before it is finalized in a block.
+A front-running node might try to supersede her transaction.
+In Section~\ref{sec:ICOsfrontrunning}, we look at Initial Coin Offerings (ICOs).
+After a few hacking incidents of high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered.
+This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to latecomers on the open markets~\cite{zetzsche2018ico, li2018initial}.
+ICOs started to experiment with different fair capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}.
+We show empirical evidence of a miner purchasing tokens ahead of other users.
+
 %Decentral applications are on the rise with Turing complete blockchains maturing to handle high monetary value transactions.
@@
 %______________________________________________________________%
-\section{Preliminaries}
+\section{Preliminaries \& Related Work}
 
@@
 Here we focus on the historical context and how the regulations evolved to be what they are today.\\
-Front-running was first observed on the Chicago Board Options Exchange (\textit{CBoE})~\cite{markham1988front}, and was defined by Securities Exchange Commission \textit{(SEC)} in 1977 as:
-\begin{quote}
-The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}
-\end{quote}
+Front-running was first observed on the Chicago Board Options Exchange (\textit{CBoE})~\cite{markham1988front}, and was defined by Securities Exchange Commission \textit{(SEC)} in 1977 as: ``The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}''
 
@@
 
-Blockchain technology has received an exceptional amount of attention since it was first introduced as the underlying technology of the cryptocurrency Bitcoin in 2008~\cite{nakamoto2008bitcoin}.
-Many decentralized applications that are built on top of this technology represent the significance of the blockchain as it completely eliminates the central point of failure within the systems.
-However, blockchains have some inherent characteristic that leaves them vulnerable to information leaks and \emph{front-running} behaviour.
-Although this data structure is known to be publicly visible to every network participants, information is layered and some of them are easier accessed only by insiders.
-Any network participants that runs a full node on the blockchain is able to obtain that information and as mentioned in section~\ref{sec:What is front-running?}, this leaves the application vulnerable to front-running.
-%Decentralized exchanges are a group of blockchain financial applications where front-running can be executed.
-%____________________________________________________________________
-%%% The following chunk seem to be redundant and weird. Should we keep it?? 
-Bancor \cite{hertzog2017bancor} is an example of such systems in which front-runners benefit from the potential price increase of the market stocks (details are provided in~\ref{sec:frontrunningExchanges}).
-Decentralized namespaces, as blockchain non-financial applications, are another example.
-Ethereum Name Service and Ghazal \cite{moosavighazal} are such systems in which upon seeing a transaction from Alice to register \texttt{alice.eth}, front-runner can go ahead of her and register this domain name.
-He can later sell \texttt{alice.eth} to Alice for a higher price and profit.
-Another application that is vulnerable to front-running is Initial Coin Offering (ICO) smart contracts.
-ICO is a method to distribute tokens based on the deposits of the native coin, Ether in the case of Ethereum.
-After a few hacking incidents of high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered.
-This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to latecomers on the open markets~\cite{zetzsche2018ico, li2018initial}.
-ICOs started to experiment with different fair capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}.
-This competition made ICOs a good opportunity for front-running attacks.
-In this paper, we use multiple empirical examples to show the possibility of front-running on DApps.
-For the sake of completeness, we use one incident on ICOs, and examples from the Top 25 DApps by recent user counts based on \texttt{DAppRadar.com} ranking.
+In one sense, blockchain technology (which was introduced via Bitcoin in 2008~\cite{nakamoto2008bitcoin}) strives to disintermediate certain central parties that would participate in a transaction.
+However, blockchains also introduce new participants in the relaying and finalization (\ie mining) of transactions.
+Any network participant that runs a full node on the blockchain is able to obtain proposed transactions before they are added to the blockchain and miners are free in the transactions they select for inclusion in their attempted blocks.
+This can leave blockchain applications vulnerable to front-running, as we will see through the several case studies detailed in this paper.
+
 %____________________________________________________________________
@@
 
-Due to the novelty characteristics of the underlying technology (blockchain), there are only a few research carried out on the issue of front-running in the context of blockchain and decentral ledgers.
-\\
-Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage~\cite{aune2017footprints}.
-As mentioned in section~\ref{sec:What is front-running?}, the information leakage results in the entire system to be vulnerable to the front-running.
-They also propose a cryptographic approach, similar to commit and reveal(~\ref{CommitmentScheme}), to prevent front-running in decentral systems.
+Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage~\cite{aune2017footprints}.They also propose a cryptographic approach, similar to commit and reveal (see Section~\ref{CommitmentScheme}) to prevent front-running.
+%As mentioned in section~\ref{sec:What is front-running?}, the information leakage results in the entire system to be vulnerable to the front-running.
 %In this approach, which is similar to commit and reveal, a transaction hash (fingerprint) is broadcast to the network to secure time priority while not revealing the information.
@@
 This makes the transaction and its hash to be executed at their reserved time priority and not vulnerable to front-running.
-Malinova and Park discuss different design settings for financial markets and trading platforms on decentral ledgers~\cite{malinova2017market}.
+Malinova and Park discuss different design settings for financial markets and trading platforms on decentralized ledgers~\cite{malinova2017market}.
 They argue that blockchain brings new options of transparency which affects traders behaviour, especially in the presence of intermediary front-runners.
 They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make front-running costly and inefficient.
-
 Breidenbach~\etal~\cite{breidenbach2018enter} face the front-running issue in the context of automating bug bounties for smart contracts.
 Upon submitting the bug bounty to the Hydra smart contract, one can front-run the bug report and claim the bounty instead of the original reporter.
-In order to mitigate this issue they proposed \textit{Submarine Commitments} which we discuss further in section~\ref{submarineCommits}.
+In order to mitigate this issue they proposed \textit{Submarine Commitments} which extend commit and reveal; we discuss them further in Section~\ref{submarineCommits}.
 
-One of the properties of Blockchain technology was to overcome double-spend, however, this does not apply for fast payments and zero-confirmation transactions.
-\textit{Double-spend attack}, as the name implies, the adversary spends a coin more than one time.
-To do so, he would use the coin as an input of a transaction and broadcast it to the network, before the transaction gets validated and executed, he broadcasts another transaction associated with a higher transaction fee which spends the same input~\cite{bamert2013have, karame2012double}.
-This adversarial behaviour is similar to the front-running attack where the attacker front-runs his own transaction by paying a higher fee when broadcasting the second transaction.
+Double-spending attacks in Bitcoin have been studied~\cite{bamert2013have, karame2012double} where a user broadcasts a transaction and is able to obtain some off-blockchain good or service before the transaction has actually been (fully) confirmed.
+The user can then broadcast a competing transaction that sends the same unspent coins to herself, perhaps using higher transaction fees, arrangements with miners, or artefacts of the network topology to have the second transaction confirmed instead of the first.
+We think of this as a type of front-running.
+
+In the cryptographic literature, front-running attacks are modelled by allowing a `rushing' adversary to interact with the protocol.
+In particular, ideal functionalities of blockchains (such as those used in simulation-based proofs) need to capture this adversarial capability, assuming the real blockchain does not address front-running.
+Literature like the Bitcoin Backbone~\cite{} and Hawk~\cite{} capture this.
+
+%\textblue{Equate front-running to a rushing adversary in the crypto literature and cite the fact that UC models of blockchains capture front-running attacks: cite Bitcoin Backbone paper and Hawk paper in particular.}
 
@@
 %______________________________________________________________%
-\subsection{Name Services.}
+\subsection{Name Services.}\label{sec:ens}
 

### 2018-09-22 frontrunning/Latex/sections/paper.tex
edits

@@
 Front-running is an attack where a malicious node observes a transaction after it is broadcast but before it is finalized, and attempts to have its own transaction confirmed before or instead of the observed transaction.
-Whether this attack is beneficial depends on the logic of the DApp itself.
 
-In this paper, we perform a number of case studies of DApps on Ethereum (a popular blockchain supporting DApps) that are volnerable to front-running attacks.
-We draw the cases from the top 25 most active DApps,\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} as well as ICOs which are absent from this list during a sampling period.
-xxx tend to appear on this list when they are actively issued.
-benefit of this attack varies on what the DApps is doing but, this attack .
+The mechanics of frontrunning works on all DApps but front-running is not beneficial on all DApps; it depends on its internal logic as well as any mitigations it might implement.
+This paper is a series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps).
+We study DApps from each category of the top 25 most active\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} to assess their vulnerability to front-running attacks.
+We also study initial coin offerings (ICOs), which by happenstance, did not appear in the top 25 on our sample day.
+Proposals to eliminate or mitigate frontrunning from DApps are scattered across forums, proposed standards (called EIPs in Ethereum) and academic papers; we systemize them here.
 
@@
 
-As a preview, in Section~\ref{sec:frontrunningExchanges}), we examine Bancor~\cite{hertzog2017bancor}, a decentralized exchange that operates similar to traditional stock markets and is likewise volunerable to front-running.
+\textblue{[tk]} As a preview, in Section~\ref{sec:frontrunningExchanges}), we examine Bancor~\cite{hertzog2017bancor}, a decentralized exchange that operates similar to traditional stock markets and is likewise vulnerable to front-running.
 Domain name frontrunning occurs when a user uses a domain registrar to inquire if a domain is available for purchase, and the query triggers the registrar to purchase the domain in anticipation that it can sell it to the user.
@@
 
-Blockchain, as a secure ledger, gives the impression of an ultimate secure platform for decentral applications and one might not consider implementing the application with security in mind.
+%Blockchain, as a secure ledger, gives the impression of an ultimate secure platform for decentral applications and one might not consider implementing the application with security in mind.
 In general, all the network participants have the ability to front-run specific transactions that are sent to the network.
@@
 
-\subsubsection{Blockchain Participants}
+\paragraph{Full Nodes.}
 Any regular (miner or non-miner) the user can front-run other transactions in the network.
@@
 
-\subsubsection{Miners} \label{minersfrontrunning}
+\paragraph{Miners.} \label{minersfrontrunning}
 Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this in case of malicious reordering is known as \textbf{transaction reordering} attack.

### 2018-09-24 frontrunning/Latex/sections/paper.tex
took a long time to get here, but now into the TOP 25 section :+1:

@@
 % !TEX root = ../main.tex
-%______________________________________________________________%
-\section{Introduction}
 
-\label{sec:intro}
-
-% @J : intro needs lots of love.
-% Jeremy: Will work on this very last, once I know what the paper is actually about :)
+\section{Introduction} \label{sec:intro}
 
@@
 
-The mechanics of frontrunning works on all DApps but front-running is not beneficial on all DApps; it depends on its internal logic as well as any mitigations it might implement.
-This paper is a series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps).
-We study DApps from each category of the top 25 most active\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} to assess their vulnerability to front-running attacks.
+The mechanics of frontrunning works on all DApps but front-running is not necessarily beneficial, depending on the DApp's internal logic and/or  as any mitigations it might implement.
+Therefore DApps need to be studied individually or in categories.
+This paper is a series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps) from each category of the top 25 most active.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} We do case studies on decentralized exchanges (\eg Bancor), crypto-collectables (\eg CryptoKitties), gambling services (\eg Fomo3D), and decentralized name services (\eg Ethereum Name Service).
 We also study initial coin offerings (ICOs), which by happenstance, did not appear in the top 25 on our sample day.
-Proposals to eliminate or mitigate frontrunning from DApps are scattered across forums, proposed standards (called EIPs in Ethereum) and academic papers; we systemize them here.
-
-%The concept of  \emph{front-running} is decades old starting with early financial markets.
-Initially, the traders required to be physically available in the exchange office to deliver the bids and offers, and some traders, in the knowledge of future market change, could run in front of the others to get their orders ahead of the change in the market to profit from the price change.
-Clearly, in such scenarios front-running was possible yet not detectable as a damaging activity.
-However, with the rapid advances of the technology in the last few decades, trading is not carried out in person anymore, a new form of front-running is feasible through high-speed networks.
-Furthermore, Blockchain technology has introduced transparency and open markets and leads to a new era of front-running which inherently affects all decentral applications, whether financial or non-financial.
-Arbitrage and Censorship, are also issues that have been linked to front-running attacks on blockchain \textit{(We need to talk about why these two are left out of the scope of this paper)}.
-Currently, there are quite a few decentral applications built on the blockchains, so in order for us to perform a thorough study on blockchain application front-running, we set a specific criteria by using the top 25 decentral applications which have the highest recent user activities.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} Using this criteria, we successfully categorized these decentral applications into 4 principal categories on which we conduct our analysis.
-Surprisingly, there was no ICO (initial coin offering) included in the top 25 DApps list by the time we fetched the data from the website.
-We believe the reason is that the ICOs are inherently different from other groups of Daaps as they are merely highly active during their offering periods and their user activity drops dramatically after the offerings period are over.
-Therefore, we  consider ICOs as other cases on which the front-running should be investigated (although they are not listed in the top 25 DApps we use) \footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".}
-
-\textblue{[tk]} As a preview, in Section~\ref{sec:frontrunningExchanges}), we examine Bancor~\cite{hertzog2017bancor}, a decentralized exchange that operates similar to traditional stock markets and is likewise vulnerable to front-running.
-Domain name frontrunning occurs when a user uses a domain registrar to inquire if a domain is available for purchase, and the query triggers the registrar to purchase the domain in anticipation that it can sell it to the user.
-In Section~\ref{sec:ens}, we examine decentralized namespaces like Ethereum Name Service and academic works like Ghazal~\cite{moosavighazal} where relaying nodes and miners see Alice's attempt to purchase a domain name before it is finalized in a block.
-A front-running node might try to supersede her transaction.
-In Section~\ref{sec:ICOsfrontrunning}, we look at Initial Coin Offerings (ICOs).
 After a few hacking incidents of high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered.
@@
 ICOs started to experiment with different fair capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}.
-We show empirical evidence of a miner purchasing tokens ahead of other users.
+We show empirical evidence of a miner purchasing tokens ahead of other users in Status.im.
+Finally, proposals to eliminate or mitigate frontrunning from DApps are scattered across forums, proposed standards (called EIPs in Ethereum) and academic papers; we systemize them the last section.
 
-%Decentral applications are on the rise with Turing complete blockchains maturing to handle high monetary value transactions.
-Tokenization mushroomed to a whole ecosystem of tokenized applications on the blockchain, these applications inherently become a market as tokens are in the core of them.
-We started looking at some of these applications, in specific \textit{Bancor}~\cite{hertzog2017bancor}, to look into possible issues arising from these new models.
-Transparency of blockchains, although being a good feature of them, opens up these markets to some attack vectors that might not be visible on the time of the application design, one main attack is known as \textbf{front-running}, whether financial or non-financial.
-Arbitrage and Censorship, are also issues arises from the designs on the blockchain technology and had been linked to front-running attacks, hence we use the term \textit{front-running] loosely to talk about any transaction manipulation with the intention of getting other transactions in before the original transaction takes place.
-In this paper, our focus is to have a complete overview of front-running on the blockchain while analyzing Bancor issues.
-While looking at the possibility of front-running on other applications, we found interesting case studies that affect most of the top 25 decentral applications on Ethereum blockchain.
+% = = = = = = = = = = = = = = = = = = = = = = = = = = %
+% = = = Preliminaries
+% = = = = = = = = = = = = = = = = = = = = = = = = = = %
 
-%______________________________________________________________%
 \section{Preliminaries \& Related Work}
@@
 In traditional stock exchanges, floor traders might overhear a broker's negotiation with her client over a large purchase, and literally race the broker to buy first, potentially profiting when the large sale temporarily reduces supply of the stock.
-Brokers might also frontrun their own client's orders by purchasing stock for themselves between receiving the instruction to purchase from the client and actually executing the purchase (similar techniques can be used for large sell orders).
+A malicious broker might also front-run their own client's orders by purchasing stock for themselves between receiving the instruction to purchase from the client and actually executing the purchase (similar techniques can be used for large sell orders).
 Front-running is unethical and illegal in jurisdictions with mature securities regulation.
 
-% Jeremy: I don't real;y understand the below so dropping if no one protests. 
-%The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty~\cite{liang2005distressed}.
+Cases of front-running are sometimes difficult to distinguish from related concepts like insider trading and arbitrage.
+In front-running, a person sees a concrete transaction that is set to execute and reacts to it before it actually executes.
+If the person instead has access to more general privileged information that might predict future transactions, but is not reacting at the actual pending trades, we would classify this activity as insider trading.
+If the person reacts after the trade is executed, or information is made public, and profits from being the fastest to react, this is considered arbitrage and is both legal and encouraged because it helps markets integrate new information into prices quickly.
 
 \subsection{Literature on Traditional Front-running}\label{traditionalFrontrunning}
-%As traditional front-running has been the subject of discussion for decades, there are many works of literature on this subject.
-Here we focus on the historical context and how the regulations evolved to be what they are today.\\
 Front-running was first observed on the Chicago Board Options Exchange (\textit{CBoE})~\cite{markham1988front}, and was defined by Securities Exchange Commission \textit{(SEC)} in 1977 as: ``The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}''
-
-% More to read:  SECURITIES AND EXCHANGE COMMISSION Release No. 34-67079. pdf included in Related_Documents
-% https://www.sec.gov/about/annual_report/1988.pdf
 
@@
 
-% everything that has a lineup, someone can jump in the line and front-run
+In one sense, blockchain technology (which was introduced via Bitcoin in 2008~\cite{nakamoto2008bitcoin}) strives to disintermediate certain central parties that would participate in a transaction.
+However, blockchains also introduce new participants in the relaying and finalization (\ie mining) of transactions that can act as front-runners.
+Any user monitoring blockchain network transactions (\eg running a full node) can see a unconfirmed transactions and broadcast a reactionary transaction that might be confirmed ahead of the original transaction ...
 
-In one sense, blockchain technology (which was introduced via Bitcoin in 2008~\cite{nakamoto2008bitcoin}) strives to disintermediate certain central parties that would participate in a transaction.
-However, blockchains also introduce new participants in the relaying and finalization (\ie mining) of transactions.
-Any network participant that runs a full node on the blockchain is able to obtain proposed transactions before they are added to the blockchain and miners are free in the transactions they select for inclusion in their attempted blocks.
-This can leave blockchain applications vulnerable to front-running, as we will see through the several case studies detailed in this paper.
-
-%____________________________________________________________________
+ that is well-connected front-run other transactions in the network.
+For regular users to front-run others on the blockchain, they need to be well connected to other nodes on the network.
+Doing so, they are able to listen to the network and monitor all transactions that are broadcast.
+On the Ethereum blockchain, users have to pay for the computations in a small amount of Ether called \textit{gas}~\cite{AccountT67:online}.
+The price that users pay for transactions, \textit{gasPrice}, can increase or decrease how quickly miners will execute them and include them within the blocks they mine.
+Once seeing two identical transactions with different transaction fees, a rational miner will prioritize the transaction that pays a higher gas price per unit of gas --gasPrice--, this is due to limited space in the blocks while maximizes their profit in the block they mine.
+Therefore, any regular users who run a full-node Ethereum client can front-run pending transactions by sending similar transaction with higher gas price.
+Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this in case of malicious reordering is known as \textbf{transaction reordering} attack.
 
@@
 Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage~\cite{aune2017footprints}.They also propose a cryptographic approach, similar to commit and reveal (see Section~\ref{CommitmentScheme}) to prevent front-running.
-%As mentioned in section~\ref{sec:What is front-running?}, the information leakage results in the entire system to be vulnerable to the front-running.
-%In this approach, which is similar to commit and reveal, a transaction hash (fingerprint) is broadcast to the network to secure time priority while not revealing the information.
-Once the hash is processed and assigned an index and timestamp, the transaction details are broadcast.
-This makes the transaction and its hash to be executed at their reserved time priority and not vulnerable to front-running.
 Malinova and Park discuss different design settings for financial markets and trading platforms on decentralized ledgers~\cite{malinova2017market}.
@@
 
-%\textblue{Equate front-running to a rushing adversary in the crypto literature and cite the fact that UC models of blockchains capture front-running attacks: cite Bitcoin Backbone paper and Hawk paper in particular.}
-
-%___________________________________________________________%
-
-\section{Who are Blockchain Front-runners?} %\section{On Blockchain Front-running}
-\label{sec:who can front-run?}
-
-%Blockchain, as a secure ledger, gives the impression of an ultimate secure platform for decentral applications and one might not consider implementing the application with security in mind.
-In general, all the network participants have the ability to front-run specific transactions that are sent to the network.
-Also, miners can include any transactions they like into the block they attempt to mine.
-Thus, they possess special power in terms of front-running as opposed to other users of the network.
-In the following, we discuss and compare the two groups of blockchain potential front-runners.
-
-\paragraph{Full Nodes.}
-Any regular (miner or non-miner) the user can front-run other transactions in the network.
-For regular users to front-run others on the blockchain, they need to be well connected to other nodes on the network.
-Doing so, they are able to listen to the network and monitor all transactions that are broadcast.
-On the Ethereum blockchain, users have to pay for the computations in a small amount of Ether called \textit{gas}~\cite{AccountT67:online}.
-The price that users pay for transactions, \textit{gasPrice}, can increase or decrease how quickly miners will execute them and include them within the blocks they mine.
-Once seeing two identical transactions with different transaction fees, a rational miner will prioritize the transaction that pays a higher gas price per unit of gas --gasPrice--, this is due to limited space in the blocks while maximizes their profit in the block they mine.
-Therefore, any regular users who run a full-node Ethereum client can front-run pending transactions by sending similar transaction with higher gas price, see figure~\ref{fig:RegularFrontrunning}.
-For example, in a decentral exchange, he can monitor the network and once seeing a pending \textit{buy} transaction which will further increase the price of the asset, a front-runner can send a transaction with a higher gas price and hope to have his transaction mined ahead of the original pending transaction.
-By doing so, he achieves a better rate from the buyer.
-Note that in this case, blockchain front-runners are visible to the network as they broadcast their transactions to all the network participants.
-The probability of success in such attach can be increased by flooding the network by transactions with higher than average gasPrice.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.7\linewidth]{figures/Regular_frontrunning.png}
-\caption{The Adversary up on seeing the Buy order, sends his own buy order with higher gas to front-run the first order. \label{fig:RegularFrontrunning}} 
-\end{figure}
-%https://www.lucidchart.com/invitations/accept/f8ca2662-5269-425d-9deb-deb14af2aac7
-
-\paragraph{Miners.} \label{minersfrontrunning}
-Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this in case of malicious reordering is known as \textbf{transaction reordering} attack.
-For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token\ie TKN, presumably if this transaction goes through, it causes the price of the purchased token to increase.
-So the dishonest miner can step in front of this transaction and place his own buy order ahead.
-He would simply create his \textit{buy} of 1000 TKN and include it in front of the previous \textit{buy} transaction in the block he mines.
-Doing so, he would receive a better rate than other network users, and afterward can sell the assets he has bought and gained a price advantage.
-It should be noted that miners can only front-run transactions within the blocks they happen to mine.
-They could do this also by not broadcasting their own transactions to the network before including it in the block, this makes the miners be less noticeable to the network when front-running.
-Another example here is in the case of decentral exchanges and order cancellation.
-Every exchange should have the functionality to cancel the orders, especially for a volatile market.
-In this case, when the user decides that her order is not profitable anymore, she would send a cancelation transaction.
-Here the miner sees the cancelation transaction and puts his own transaction to fill that order in front of the cancellation transaction --transaction reordering--, potentially profiting from the order.
-He can also include the canceled transaction in the block to collect the full gas limit used by the cancel transaction~\cite{CostofDecentralization:online}, see figure~\ref{fig:MinerFrontrunning}.
-Front-running can also occur in non-financial smart contracts.
-As an example, a smart contract which adds all the participants to a party invite list could only be closed by the smart contract owner.
-In this case, when the owner sends the transaction to close the list, a miner can include his own list of participants before the close transaction in the block he mines.
-This is an issue with the design of the smart contracts and is known as transaction-ordering dependence vulnerability~\cite{luu2016making}.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.7\linewidth]{figures/Miner_reorder_frontrun.png}
-\caption{The adversarial miner can monitor the Ethereum mempool for decentral exchange cancel orders and upon seeing the cancellation transaction, he puts his buy order prior to the cancel transaction.
-Doing so, the miner can profit from the underlying trade and also get the gas included in the cancel transaction.
-\label{fig:MinerFrontrunning}}
-\end{figure}
-%https://www.lucidchart.com/invitations/accept/c8768786-4a3f-4c78-b3c8-aa04a6b81d06
-
-%______________________________________________________________%
+% = = = = = = = = = = = = = = = = = = = = = = = = = = %
+% = = = TOP 25
+% = = = = = = = = = = = = = = = = = = = = = = = = = = %
 
 \section{Cases of Front-running in DApps}  
-
-As mentioned in the Section~\ref{sec:intro}, for the purpose of this research we retrieved the top 25 DApps based on recent user activities from \texttt{DAppradar.com}\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} in the first week of September 2018.
-We then categorize these applications into 4 principal groups of decentral applications (see Table~\ref{tab:top25DApps}).
-In this section, we take a deep look into one or two decentral applications from each category and pinpoint the technical details of front-running issue on each case.
-Although no ICOs were spotted on the list at the time it was retrieved, we will thoroughly discuss our analysis of how ICOs are highly vulnerable to front-running activities (see Section~\ref{sec:ICOsfrontrunning}).
-
 \input{setup/table}
 
-%______________________________________________________________%
+To find example DApps to study, we use the top 25 DApps based on recent user activity from \texttt{DAppradar.com} and sampled it in in the first week of September 2018.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} User activity is admittedly an imperfect metric for finding the `most significant' DApps: significant DApps might be lower volume overall or for extended periods of time (\eg ICOs, which we remedy by studying independently in Section~\ref{sec:ICOsfrontrunning}).
+However user activity is arguably the best objective criteria for which data is readily available, the list captures our intuition about which DApps are significant, and it is at least better than an ad hoc approach.
+Using the dataset, we categorized the top 25 applications into 4 principal use cases.
+The details are given in Table~\ref{tab:top25DApps}.
+
 \subsection{Markets and Exchanges.} \label{sec:frontrunningExchanges}
@@
 %Tragedy of the commons
-
+The first category of DApp in Table~\ref{tab:top25DApps} is exchanges. 
 Exchanges such as EtherDelta\footnote{also known as ForkDelta for the UI \url{https://forkdelta.app/}}, is the closest implementation to decentral exchanges, however their order books are stored on a central server they control and shown on their user interface (website).
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.7\linewidth]{figures/Regular_frontrunning.png}
+\caption{The Adversary up on seeing the Buy order, sends his own buy order with higher gas to front-run the first order. \label{fig:RegularFrontrunning}} 
+\end{figure}
+%https://www.lucidchart.com/invitations/accept/f8ca2662-5269-425d-9deb-deb14af2aac7
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.7\linewidth]{figures/Miner_reorder_frontrun.png}
+\caption{The adversarial miner can monitor the Ethereum mempool for decentral exchange cancel orders and upon seeing the cancellation transaction, he puts his buy order prior to the cancel transaction.
+Doing so, the miner can profit from the underlying trade and also get the gas included in the cancel transaction.
+\label{fig:MinerFrontrunning}}
+\end{figure}
+%https://www.lucidchart.com/invitations/accept/c8768786-4a3f-4c78-b3c8-aa04a6b81d06
+
+see figure~\ref{fig:RegularFrontrunning}.
+For example, in a decentral exchange, he can monitor the network and once seeing a pending \textit{buy} transaction which will further increase the price of the asset, a front-runner can send a transaction with a higher gas price and hope to have his transaction mined ahead of the original pending transaction.
+By doing so, he achieves a better rate from the buyer.
+Note that in this case, blockchain front-runners are visible to the network as they broadcast their transactions to all the network participants.
+The probability of success in such attach can be increased by flooding the network by transactions with higher than average gasPrice.
+
+For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token\ie TKN, presumably if this transaction goes through, it causes the price of the purchased token to increase.
+So the dishonest miner can step in front of this transaction and place his own buy order ahead.
+He would simply create his \textit{buy} of 1000 TKN and include it in front of the previous \textit{buy} transaction in the block he mines.
+Doing so, he would receive a better rate than other network users, and afterward can sell the assets he has bought and gained a price advantage.
+It should be noted that miners can only front-run transactions within the blocks they happen to mine.
+They could do this also by not broadcasting their own transactions to the network before including it in the block, this makes the miners be less noticeable to the network when front-running.
+
+Another example here is in the case of decentral exchanges and order cancellation.
+Every exchange should have the functionality to cancel the orders, especially for a volatile market.
+In this case, when the user decides that her order is not profitable anymore, she would send a cancelation transaction.
+Here the miner sees the cancelation transaction and puts his own transaction to fill that order in front of the cancellation transaction --transaction reordering--, potentially profiting from the order.
+He can also include the canceled transaction in the block to collect the full gas limit used by the cancel transaction~\cite{CostofDecentralization:online}, see figure~\ref{fig:MinerFrontrunning}.
+Front-running can also occur in non-financial smart contracts.
+As an example, a smart contract which adds all the participants to a party invite list could only be closed by the smart contract owner.
+In this case, when the owner sends the transaction to close the list, a miner can include his own list of participants before the close transaction in the block he mines.
+This is an issue with the design of the smart contracts and is known as transaction-ordering dependence vulnerability~\cite{luu2016making}.
+
 Bancor is another Ethereum-based application that allows users to exchange their tokens without any counter-party risk.
@@
 This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favorable profits~\cite{BancorIs7:online}.
-Researchers have shown and implemented a proof of concept code to front-run Banco as a regular non-miner user~\cite{NewTab13:online}.
+Researchers have shown and implemented a proof of concept code to front-run Bancor as a regular non-miner user~\cite{NewTab13:online}.
 
 %______________________________________________________________%
-\subsection{Name Services.}\label{sec:ens}
+\subsection{Crypto-Collectibles Games.}
 
-Front-running can also occur within non-financial blockchain applications such as naming systems.
-Recently, many blockchain-based domain registrars have been designed and implemented to eliminate the role of central parties \ie domain name system (DNS) which itself introduced the single point of failures to the entire web.
-Ethereum Name Service (ENS)\footnote{\url{https://ens.domains/}}, is the most popular decentral naming service that uses a sealed auction to facilitate the procedures of purchasing new \texttt{.eth} domain names.
-Although sealed auction method is used in ENS implementation, the normal workflow uses \textit{startAuctionsAndBid()} with the deposit equal or higher than the bid, this information leakage could be used to front-run the transaction with the same bid amount or slightly higher to outbid the initial sealed bid.
-By doing so the front-runner invalidates the original bid and hence registers the domain name himself.
-Ghazal is another Ethereum-based naming system that allows users to register \texttt{.ghazal} domain names and bind certificates to those names~\cite{moosavighazal}.
-As Ghazal is using a registration method in plain text, it is susceptible to front-running.
-Note that front-running domain names has been a subject of discussion outside the context of blockchian applications before~\cite{sac022en33:online}.
-Domain name registrars can steal available domain names upon seeing a query from an interested user for the availability of the domain.
-In this case, the registrar can register the domain name ahead and sell it back to the user for a higher price.
-%______________________________________________________________%
-\subsection{Crypto-Collectibles Games.}
+The second category of DApp in Table~\ref{tab:top25DApps} is crypto-collectables.
 
@@
 
+The third category of DApp in Table~\ref{tab:top25DApps} is gambling services.
+
 Due to the deterministic nature of blockchains, running gambling games based on randomness is close to impossible.
@@
 %______________________________________________________________%
+\subsection{Name Services.}\label{sec:ens}
+
+The final category of DApp in Table~\ref{tab:top25DApps} is name services.
+
+Front-running can also occur within non-financial blockchain applications such as naming systems.
+Recently, many blockchain-based domain registrars have been designed and implemented to eliminate the role of central parties \ie domain name system (DNS) which itself introduced the single point of failures to the entire web.
+Ethereum Name Service (ENS)\footnote{\url{https://ens.domains/}}, is the most popular decentral naming service that uses a sealed auction to facilitate the procedures of purchasing new \texttt{.eth} domain names.
+Although sealed auction method is used in ENS implementation, the normal workflow uses \textit{startAuctionsAndBid()} with the deposit equal or higher than the bid, this information leakage could be used to front-run the transaction with the same bid amount or slightly higher to outbid the initial sealed bid.
+By doing so the front-runner invalidates the original bid and hence registers the domain name himself.
+Ghazal is another Ethereum-based naming system that allows users to register \texttt{.ghazal} domain names and bind certificates to those names~\cite{moosavighazal}.
+As Ghazal is using a registration method in plain text, it is susceptible to front-running.
+Note that front-running domain names has been a subject of discussion outside the context of blockchian applications before~\cite{sac022en33:online}.
+Domain name registrars can steal available domain names upon seeing a query from an interested user for the availability of the domain.
+In this case, the registrar can register the domain name ahead and sell it back to the user for a higher price.
+
+%% = = = = = = = = = = = = = = = = = = = = = = = = = = %
+% = = = ICOs
+% = = = = = = = = = = = = = = = = = = = = = = = = = = %%
 
@@
 %______________________________________________________________%
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = %
+% = = = Mitigations
+% = = = = = = = = = = = = = = = = = = = = = = = = = = %
 

### 2018-09-24 frontrunning/Latex/sections/paper.tex
[frontrunning] Loopring polished

@@
 
-\subsubsection{Design Decision \#3: Dual Authoring\newline} % S 2 M: this is still vague, it requires better explanation.
-Loopring is an open protocol proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}.
-This protocol operates a hybrid model with off-chain order management and communication and merely the order matching takes place on the chain.
-To achieve high liquidity and price improvement, Loopring orders are grouped in \emph{ring orders}.
-After the required signatures are provided by a miner and owner of the order, see Figure~\ref{fig:vulnerable_loopring}, the ring miner sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement.
+\subsubsection{Design Decision \#3: Dual Authoring\newline} Loopring is an open protocol proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}.
+This protocol operates a hybrid model with off-chain order management and communication while only the order matching takes place on the chain.
+In this protocol, the orders are grouped in \emph{ring orders} immediately after they are sent by the users.
+Next, the required signatures are provided by a miner and owner of the order, see Figure~\ref{fig:vulnerable_loopring}.
+Eventually, the ring miner sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement.
 While the \emph{submitRing transaction} sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with his address instead of the ring miner's address and then sign the hash of the ring using his own private key.
 By paying a higher gasPrice, block miners choose the front-runner's transaction instead of the original \emph{submitRing transaction}.
-However, in the new version of Loopring protocol, this issue is resolves using the \emph{dual-authoring} scheme.
+To solve this issue, the new version of Loopring protocol uses the \emph{dual-authoring} scheme.
 This solution sets two levels of authorization for orders - one for settlement, and one for order matching.
@@
 Doing so, it is assured that (i) the orders are not modified (because they are signed by the owner), (ii) no other miner can mine the ring (because the miner's address is signed by the initial miner), and no user can front-run the \emph{submitRing transaction} (because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them).
-
-% S 2 M: Also I'm not sure about the figures. they do not add enough clarity to the text.
 

### 2018-09-24 auditing/Latex/sections/01-intro.tex
[auditing] edit and citations till 2.3

@@
 When assessing whether or not to take on a new client, auditors lack experience in this sector and therefore are unable to develop expectations of financial performance as a way of challenging financial statement assumptions.
-Due to the complex and rapidly changing technological environment, auditors are also unable to keep pace with the changes and develop the in-depth knowledge of their clients\textquotesingle  businesses required for performing an audit.
+Due to the complex and rapidly changing technological environment, auditors are also unable to keep pace with the changes and develop the in-depth knowledge of their clients{'}  businesses required for performing an audit.
 Finally, auditors are wary of accepting clients that hold a significant amount of cryptoassets as this space is largely unregulated.
@@
 \paragraph{\textbf{Methodology.}} To ensure a comprehensive overview of the changes facing auditors of companies deploying blockchain technologies, we first used structured brainstorming within our multidisciplinary research team, which includes expertise in both auditing and blockchain technologies.
-Once our preliminary list of challenges were established, we vetted our results through informal discussions with over a dozen individuals working in the field, including at the Big Four and mid-sized accounting firms, and used these interviews to augment our list.
+Once our preliminary list of challenges was established, we vetted our results through informal discussions with over a dozen individuals working in the field, including at the Big Four\footnote{The Big Four are the four biggest auditing firms in the world which includes, Ernst \& Young (EY), Deloitte \& Touche, KPMG and PricewaterhouseCoopers (PwC).} and mid-sized accounting firms, and used these interviews to augment our list.
 The contribution of this paper is to provide a comprehensive list of challenges, rather than determining the relative importance of each or any broader concepts across the industry---thus we did not find it necessary to apply qualitative data analysis (\eg grounded theory) to the interviews; instead, we simply extracted the challenges raised which we initially missed.
 
-\paragraph{\textbf{Relevance.}} Our work can viewed as a case study of cryptographers working with an outside profession for addressing a real-world problem.
-The result is not a new protocol but a two-way knowledge transfer between professions that we hope is interesting to this audience.
-While displacing auditors is occasionally a target of cryptographers~\cite{narula2018zkledger,dagher2015provisions}, auditing itself is also occasionally studied directly at venues like Financial Cryptography
+\paragraph{\textbf{Relevance.}} Our work can be viewed as a case study of cryptographers working with an outside profession for addressing a real-world problem.
+The result is not a new protocol but a two-way knowledge transfer between professions.
+While displacing auditors is occasionally a target of cryptographers~\cite{narula2018zkledger,dagher2015provisions}, auditing itself is also occasionally studied directly at venues like Financial Cryptography~\cite{grigg2000financial}.
 
@@
 \section{Preliminaries and Related Work}
-Financial statements are prepared by a firm to summarize its assets and liabilities at year-end, the resulting changes in firm equity, and the firm’s income/profits, expenses/losses, and cash flows across the year.
-Because the firm generally wants to present the most optimistic view of its financial health, the firm may hire an auditor to ensure it is a realistic picture of the company's financial performance.
-In doing so, auditors are expected to comply with Generally Accepted Auditing Standards (GAAS) and the Code of Conduct of their professional order.
+Financial statements are prepared by a firm to summarize its assets and liabilities at year-end, the resulting changes in firm equity, and the firm{'}s revenue, expenses, and cash flows across the year.
+Because the firm generally wants to present the most optimistic view of its financial health, the firm may hire an auditor to ensure it is a realistic picture of the company{'}s financial performance.
+In doing so, auditors are expected to comply with Generally Accepted Auditing Standards (GAAS) and the Code of Conduct of their professional order~\cite{strother1975establishment}.
 In addition to an audited statement, the firm will produce quarterly statements that are reviewed by a third party auditor to a less rigorous standard.
 
-\todo{Note that there are auditing and accounting papers in the bib/zotero that have not been cited here!}
-
+%NOTE: Note that there are auditing and accounting papers in the bib/zotero that have not been cited here! {blaze1998compliance}
 %------------------------------------------------------------------------------------------------
@@
 Many assumptions and estimates are required to prepare this report.
-A firm's CEO and CFO must certify the adequacy and effectiveness of the firm's internal controls over financial reporting, which poses a reputational risk for firm directors as they will be held accountable for financial statements that are misstated.
+A firm's CEO and CFO must certify the adequacy and effectiveness of the firm{'}s internal controls over financial reporting, which poses a reputational risk for firm directors as they will be held accountable for financial statements that are misstated.
 Management will seek an audit to comply with regulatory requirements, or because they feel it will give them a competitive advantage over non-audited firms in raising capital and lowering their lending rates.
@@
 Investors use financial statements to assess their potential return on investment.
-Although \textit{caveat emptor} is an important consideration, investors rely on the existence of an auditor's report as a signal of the reliability of financial disclosures.
+Although \textit{caveat emptor} is an important consideration, investors rely on the existence of an auditor{'}s report as a signal of the reliability of financial disclosures.
 
-\paragraph{Financial Regulators.} Regulators span different government agencies with a spectrum of concerns including financial fraud, taxation, anti-money laundering, and know your customer rules.
+\paragraph{Financial Regulators.} Regulators span different government agencies with a spectrum of concerns including financial fraud, taxation, anti-money laundering, and know your customer (KYC) rules.
 Financial audits are central to the role of security regulators, who require publicly traded firms to obtain an annual unqualified audit opinion on their financial statements for consumer protection.
-Failure to do so, would put the company offside with the regulators\textquotesingle  requirements and could result in the company\textquotesingle s shares being placed on cease-trade.
+Failure to do so, would put the company offside with the regulators{'} requirements and could result in the company{'}s shares being placed on cease-trade.
 
@@
 \subsection{Cryptoassets and firms that hold them}
-The central component of a financial report is the firm’s balance sheet which lists assets and liabilities.
+The central component of a financial report is the firm{’}s balance sheet which lists assets and liabilities.
 We use the term \textit{cryptoasset} and \textit{cryptoliability} to refer to items whose value are contingent on blockchain technologies.
 Cryptoassets include cryptocurrencies and other tokens of tradeable value.
-Without loss of generality, we assume cryptocurrencies are native to their underlying blockchain, can be transacted directly, and are used to pay fees for transaction execution.
-Bitcoin and Ether are examples.
-For blockchains that allow developers to deploy custom decentralized apps, the apps might issue and manage the ownership of a custom tokens.
-In the case of Ethereum, these tokens are often ERC20 tokens, where ERC20 is sometimes misunderstood to mean what the token represents; rather, ERC20 is a technical standard about how token transactions are invoked.
+Without loss of generality, we assume cryptocurrencies are native to their underlying blockchain, can be transacted directly, and are used to pay fees for transaction execution, \eg Bitcoin and Ether.
+For blockchains that allow developers to deploy custom decentralized applications, the applications might issue and manage the ownership of custom tokens.
+In the case of Ethereum, these tokens are often \textit{ERC20} tokens~\cite{erc20}, where \textit{ERC20} is sometimes misunderstood to mean what the token represents; rather, \textit{ERC20} is a technical standard about how token transactions are invoked.
 
-What a token represents varies across applications but includes at least of the following major categories.
-(1) Access tokens: a service is developed which requires its own custom tokens for using the service; (2) Backed tokens: a token issuer claims to be holding something valuable (material or digital) in reserve, and the token represents a claim on these reserves; (3) Equity tokens: a firm issues tokens to represent ownership shares of the company; and (4) Collectable tokens: the token itself is offered as a contemporary collector’s item.
-Digital tokens of these types predate blockchains; for example, (1) Linden dollars, (2) E-Gold, and (4) URLs are arguably examples.
-Equities (3) are almost entirely dematerialized (\eg paper stock certificates are rare) but operate closer to (2) with a central depository.
+What a token represents varies across applications but includes at least one of the following major categories.
+\textit{(1) Access tokens}: a service is developed which requires its own custom tokens for using the service; \textit{(2) Backed tokens}: a token issuer claims to be holding something valuable (material or digital) in reserve, and the token represents a claim on these reserves; \textit{(3) Equity tokens}: a firm issues tokens to represent ownership shares of the company; and \textit{(4) Collectable tokens}: the token itself is offered as a contemporary collector{’}s item (\eg \textit{ERC721}~\cite{erc721}).
+Digital tokens of these types predate blockchains; for example, \textit{Linden dollars}, \textit{E-Gold}, and \textit{(4)} URLs are arguably examples.
+Equities \textit{(3)} are almost entirely dematerialized (\eg paper stock certificates are rare) but operate closer to \textit{(2)} with a central depository.
 
-Tokens and cryptocurrencies are issued to an initial set of owners through any mechanism of the issuer’s choosing.
-A popular option is auctioning a set of tokens to the public in an ``initial coin offering'' or ICO.
-This is intended to resemble the initial public offering (IPO) of a firm’s stock, but ICOs often lack any consumer protection or regulatory compliance.
+Tokens and cryptocurrencies are issued to an initial set of owners through any mechanism of the issuer{'}s choosing.
+A popular option is auctioning a set of tokens to the public in an ``Initial Coin Offering'' or ICO.
+This is intended to resemble the ``Initial Public Offering'' (IPO) of a firm{'}s stock, but ICOs often lack any consumer protection or regulatory compliance.
 An ICO of an access token might raise capital for developing or improving the service that will use these tokens.
@@
 Tokens could represent a debt instrument, like a bond, commercial paper, or repurchase agreement.
-In a recent pilot, a blockchain-based certificate of deposit was issued.
+In a recent pilot, a blockchain-based certificate of deposit was issued~\cite{NBCJPMorganBlockchain}.
 This creates an asset for the investors (Western Assets, Pfitzer, etc.) and a liability for the issuer (National Bank of Canada with J.P.
@@
 An exchange service will hold demand deposits of cryptocurrencies or tokens, as well as governmental currencies, and allow its users to trade them.
-An investment fund will hold a portfolio of cryptoassets (\eg TIQ101-CF is 50\% bitcoin, 35\% ether, 15\% litecoin \todo{[c]: look at the comment below in latex}) and sell shares to investors through a standard financial platform.
-Finally a firm initiating a token sale will raise capital in cryptocurrencies, held as an asset, in return for tokens that are not generally liabilities (it may also reserve some tokens as an additional asset).
+An investment fund will hold a portfolio of cryptoassets (\eg TIQ101-CF is 50\% bitcoin, 35\% ether, 15\% litecoin \todo{[cite-confidential\?]}) and sell shares to investors through a standard financial platform.
+Finally, a firm initiating a token sale will raise capital in cryptocurrencies, held as an asset, in return for tokens that are not generally liabilities (it may also reserve some tokens as an additional asset).
 
@@
 \subsection{Presentation of Cryptoassets}
-A financial report will classify assets and liabilities according to categories established by the auditing standards adhered to in the firm\textquotesingle s reporting country (American Generally Accepted Accounting Principles in the United States and International Financial Reporting Standards (IFRS) in many other countries).
+A financial report will classify assets and liabilities according to categories established by the auditing standards adhered to in the firm{'}s reporting country (American Generally Accepted Accounting Principles in the United States and International Financial Reporting Standards (IFRS) in many other countries).
 The following discussion will apply IFRS although the considerations under US GAAP are similar.
@@
 This means that while the investment fund holds two investments, Bitcoin and Google stock, both for long-term growth purposes, the current standards would not allow these investments to recorded on the same basis.
-This also means that increases in value of Bitcoin or other cryptoassets are not recorded as part of net profit, which obfuscates a company\textquotesingle s annual reported earnings and undermines their usefulness for investors.
+This also means that increases in value of Bitcoin or other cryptoassets are not recorded as part of net profit, which obfuscates a company{'}s annual reported earnings and undermines their usefulness for investors.
 

### 2018-09-24 auditing/Latex/sections/01-intro.tex
[auditing] edits till section 3 Key Issue

@@
 An exchange service will hold demand deposits of cryptocurrencies or tokens, as well as governmental currencies, and allow its users to trade them.
-An investment fund will hold a portfolio of cryptoassets (\eg TIQ101-CF is 50\% bitcoin, 35\% ether, 15\% litecoin \todo{[cite-confidential\?]}) and sell shares to investors through a standard financial platform.
+An investment fund will hold a portfolio of cryptoassets (\eg TIQ101-CF is 50\% bitcoin, 35\% ether, 15\% litecoin \todo{[cite-confidential?]}) and sell shares to investors through a standard financial platform.
 Finally, a firm initiating a token sale will raise capital in cryptocurrencies, held as an asset, in return for tokens that are not generally liabilities (it may also reserve some tokens as an additional asset).
@@
 The following discussion will apply IFRS although the considerations under US GAAP are similar.
-\todo{ GAAP and IFRS citations  }
+% \todo{ GAAP and IFRS citations  }
 
-\paragraph{Cryptoassets.} IFRS does not provide specific standards for how to account for cryptoassets therefore their presentation is based on existing standards that were not conceived with the nature of these assets in mind.
+\paragraph{Cryptoassets.} IFRS does not provide specific standards for how to account for cryptoassets, therefore, their presentation is based on existing standards that were not conceived with the nature of these assets in mind.
 This results in a presentation of cryptoassets that does not necessarily reflect the underlying economic reality of the assets at hand.
-For instance, an investment portfolio that holds a combination of Bitcoin and Google stock for long-term capital appreciation purposes, would report the Bitcoin as an intangible asset~\cite{RCGTIFRsCrypto2018} and the Google stock as a short-term investment.
-The Google stock would be presented at its fair market value and any gains and losses on this investment would be immediately reported as part of net profit.
-
-The Bitcoin, on the other hand, would be presented as an intangible asset.
-This investment could either be presented at historical cost (what the company paid for the Bitcoin) or revalued to its fair market value.
+For instance, an investment portfolio that holds a combination of Bitcoin and Google stock for long-term capital appreciation purposes would report the Bitcoin as an intangible asset~\cite{RCGTIFRsCrypto2018} and the Google stock as a short-term investment.
+The Google stock would be presented at its fair market value and any gains and losses on this investment would be immediately reported as part of the net profit.
+The Bitcoin, on the other hand, could either be presented at historical cost (what the company paid for the Bitcoin) or revalued to its fair market value.
 If the Bitcoin is reported at cost, any increases in value would not be recorded until the asset is sold (decreases in value below cost would be reported immediately).
-If the Bitcoin is reported at fair market value, any increases in value would be reported in Other Comprehensive Income, a special category that does not fall into net profit.
+If the Bitcoin is reported at fair market value, any increases in value would be reported in \textit{Other Comprehensive Income}, a special category that does not fall into the net profit.
 This means that while the investment fund holds two investments, Bitcoin and Google stock, both for long-term growth purposes, the current standards would not allow these investments to recorded on the same basis.
-This also means that increases in value of Bitcoin or other cryptoassets are not recorded as part of net profit, which obfuscates a company{'}s annual reported earnings and undermines their usefulness for investors.
+This also means that increases in the value of Bitcoin or other cryptoassets are not recorded as part of the net profit, which obfuscates a company{'}s annual reported earnings and undermines their usefulness for investors.
 
@@
 However, most ICOs are not set out to give the holder an interest in the company as a whole, but rather represent an interest in a specific project.
-If the holder is owed some type of obligation, like access to a marketplace or participation in an, then recognition of the funds received as a liability would be appropriate.
+If the token holder is owed some type of obligation, like access to a marketplace or participation in application , then recognition of the funds received as a liability would be appropriate.
 
-Under rare cases, the proceeds could be reported as revenue if the funds received do not qualify as either share capital or represent some ongoing obligation towards the ICO holder.
+Under rare cases, the proceeds could be reported as revenue if the funds received do not qualify as either share capital or represent some ongoing obligation towards the token holder.
 However, we expect these instances to be fairly rare as it is unlikely that an investor would contribute to an ICO and not expect something of value in return.

### 2018-09-24 auditing/Latex/sections/02-body.tex
conc point form
[audit] edit till section 4

@@
 \paragraph{Issue: Meta-information.} Assets and liabilities that are transacted on a publicly readable blockchain record basic details, like times and values, but auditors require further information to validate the nature of a transaction.
-For example, assume an employee\textquotesingle s salary is paid in Bitcoin.
-Bitcoin\textquotesingle s blockchain shows that a transaction occurred but it does not specify it as a salary; nor does it confirm basic details like the number of hours paid, if the nominal amount is BTC or a spot conversion from a governmental currency, and what deductions for tax or benefits were applied.
+For example, assume an employee{'}s salary is paid in Bitcoin.
+Bitcoin{'}s blockchain shows that a transaction occurred but it does not specify it as a salary; nor does it confirm basic details like the number of hours paid, if the nominal amount is BTC or a spot conversion from a governmental currency, and what deductions for tax or benefits were applied.
 Most importantly, it does not confirm the amount the employee was paid accurately reflects the number of hours worked at the authorized pay rate.
@@
 Consensus is not instant: a transaction might be included and then quickly dropped as consensus forms between different proposed chains.
-And it is never guaranteed to be final: an agreement within the computational majority of miners can unroll past transactions, For example, Ethereum\textquotesingle s miners branched the main blockchain to modify some past transactions~\cite{dupont2017experiments}.
-The challenge of finality was an important design consideration in the Bank of Canada\textquotesingle s Project Jasper which sought to establish a Distributed Wholesale Payment Systems.
-``Project Jasper was structured so that a transfer of [digital currency] was equivalent to a full and irrevocable transfer of the underlying claim on central bank deposits.” Given that on the Ethereum blockchain, transactions can be reversed, the work around for Project Jasper was to implement a “design feature (which) relates to the issuance of (digital currency) and is therefore independent of the platforms upon which Jasper was built.''~\cite{chapman2017project}.
+And it is never guaranteed to be final: an agreement within the computational majority of miners can unroll past transactions, For example, Ethereum{'}s miners branched the main blockchain to modify some past transactions to reverse a hacked DApp transactions~\cite{dupont2017experiments}.
+The challenge of finality was an important design consideration in the Bank of Canada{'}s Project Jasper~\cite{chapman2017project} which sought to establish a Distributed Wholesale Payment Systems.
+``Project Jasper was structured so that a transfer of [digital currency] was equivalent to a full and irrevocable transfer of the underlying claim on central bank deposits.'' Given that on the Ethereum blockchain, transactions could be reversed, the work around for Project Jasper was to implement a ``design feature (which) relates to the issuance of (digital currency) and is therefore independent of the platforms upon which Jasper was built.''.
 
@@
 Alternatively, auditors could establish a generally accepted threshold (for instance, number of days) after which a transaction would be considered final.
+%we could discuss the practice of transaction confirmation for 6+ blocks here as well
 
@@
 \paragraph{Issue: Completeness.} Firms generally do not hide assets as this undermines their reported financial health, however a firm might hide an asset to shift its acquisition forward in time.
-Additionally, hiding liabilities promotes a firm\textquotesingle s solvency.
-Therefore, auditors are charged with determining that they have obtained the full measure of a firm\textquotesingle s transactions to ensure the completeness of the information under analysis.
+Additionally, hiding liabilities promotes a firm{'}s solvency.
+Therefore, auditors are charged with determining that they have obtained the full measure of a firm{'}s transactions to ensure the completeness of the information under analysis.
 
@@
 However, this still raises the issue that the client may have entered into side-arrangements with related parties.
-This risk is also present in traditional audits.
-While these challenges are magnified on a blockchain is magnified due to the pseudo-anonymity of this environment, the underlying challenge remains the same as it would in a traditional audit.
+While these challenges are magnified on a blockchain due to the pseudo-anonymity of this environment, the underlying challenge remains the same as it would in a traditional audit.
 
@@
 For example, one proposed DApp for crowdfunding projects would allow stakeholders to split off into a smaller DApp, taking a share of the assets from the parent DApp with it~\cite{dupont2017experiments}.
-Another example would be the Lightning Network~{poon2016bitcoin} which is second layer, off blockchain payment network that was implemented for scaling Bitcoin to increase throughput.
+Another example would be the Lightning Network~\cite{poon2016bitcoin} which is a second layer, off blockchain payment network that was implemented for scaling Bitcoin to increase its throughput.
 The Lightning Network is more complex than simple Bitcoin payments and involves payment channels and routings.
@@
 While firms may complicate their transactions either for economic benefits in order to obfuscate the true nature of their transactions, the onus is on the firm under audit to operate in an auditable fashion.
-In other words, while it is the auditor\textquotesingle s responsibility to design procedures to gain comfort over an entity\textquotesingle s operations, it is the responsibility of management to implement controls and procedures to ensure that the entity is audit-ready.
+In other words, while it is the auditor{'}s responsibility to design procedures to gain comfort over an entity{'}s operations, it is the responsibility of management to implement controls and procedures to ensure that the entity is audit-ready.
 Therefore, some complex operations, while economically sound, may be avoided to ensure the audibility of operations.
@@
 \paragraph{Issue: Transaction Pointers.} Blockchain transactions need to be uniquely identified to be pointed at by secondary financial records.
-Due to an implementation fault in Bitcoin, transactions broadcasted with one identifier might end up in the blockchain with a different identifier, which could lead a firm to conclude a transaction did not take place when in fact it did, but under an unexpected identifier~\cite{andrychowicz2015malleability} Some firms went bankrupt when their automated system kept honouring refund requests from a malicious entity claiming the refunds were not going through~\cite{trautman2014virtual,decker2014bitcoin}.
+Due to an implementation fault in Bitcoin, transactions broadcasted with one identifier might end up in the blockchain with a different identifier -- Transaction Malleability --, which could lead a firm to conclude a transaction did not take place when in fact it did, but under an unexpected identifier~\cite{andrychowicz2015malleability}.
+Some firms went bankrupt when their automated system kept honouring refund requests from a malicious entity claiming the refunds were not going through~\cite{trautman2014virtual,decker2014bitcoin}.
 The larger lesson here is that auditors cannot always safely abstract away low level implementation details.
@@
 %---------+++++++++++++++++++-----------------
-\paragraph{Issue: Occurrence.} In order to validate that cryptoasset transactions actually took place during the year, auditors will look to reproduce the transactions carried out.
-By obtaining a listing of the client\textquotesingle s cryptographic keys, the blockchain can provide a complete history of the transactions that occurred during the year.
+\paragraph{Issue: Occurrence.} \todo{This contradicts some of the points mentioned in Transaction Pointers and Finality, also the point made here is also mentioned there.
+My suggestion is to remove this Issue or merge it with one of the above} In order to validate that cryptoasset transactions actually took place during the year, auditors will look to reproduce the transactions carried out.
+By obtaining a listing of the client{'}s cryptographic keys, the blockchain can provide a complete history of the transactions that occurred during the year.
 Due to the immutable nature of the blockchain, the auditor can be assured that the transaction did take place as described.
-However, the auditor will still need to validate meta-information surrounding the transaction (see above) to validate the transaction\textquotesingle s reasonability.
+However, the auditor will still need to validate meta-information surrounding the transaction (see above) to validate the transaction{'}s reasonability.
 
@@
 \section{Key Issue: Ownership}
-In addition to being satisfied with the existence of cryptoassets, auditors must be satisfied that the assets reported on the company\textquotesingle s balance sheet do in fact belong to the company.
+In addition to being satisfied with the existence of cryptoassets, auditors must be satisfied that the assets reported on the company{'}s balance sheet do in fact belong to the company.
 For traditional assets, firms might store assets with a custodian.
-This does not eliminate the issue of ownership, it simply shifts the concern from the firm\textquotesingle s audit to the audits of central custodians.
+This does not eliminate the issue of ownership, it simply shifts the concern from the firm{'}s audit to the audits of central custodians.
 Banks and organizations who provide custodial services are required to have robust internal controls over the safeguarding of assets in their care, and provide audited report supporting the reliability of their controls.
@@
 Auditors must be satisfied that the values reported in the financial statements are accurate and represent the underlying economic reality.
-While fair valuation is important for establishing a firm\textquotesingle s financial health, it is also important for auditors to use in determining what to focus on during the audit itself.
+While fair valuation is important for establishing a firm{'}s financial health, it is also important for auditors to use in determining what to focus on during the audit itself.
 The objective of an audit is to certify that the financial statements are free of material misstatement.
@@
 The cryptoasset with the richest historical data is bitcoin and by any standard measure of volatility, its volatility currently exceeds the most traded currencies and commodities.
-If a firm\textquotesingle s balance sheet consists of a large unbalanced\footnote{An exchange service that holds bitcoin on behalf of its users will have the bitcoin listed as both an asset and a liability, thus they are balanced and price movements have no impact on their solvency.} cryptoassets or cryptoliabilities, price movements significantly impact its financial health and even its solvency.
-A comparable scenario is a financial firm holding exotic, volatile securities or derivatives---in these cases, auditors might ``stress test'' the firm\textquotesingle s balance sheet under different valuations.
+If a firm{'}s balance sheet consists of a large unbalanced\footnote{An exchange service that holds bitcoin on behalf of its users will have the bitcoin listed as both an asset and a liability, thus they are balanced and price movements have no impact on their solvency.} cryptoassets or cryptoliabilities, price movements significantly impact its financial health and even its solvency.
+A comparable scenario is a financial firm holding exotic, volatile securities or derivatives---in these cases, auditors might ``stress test'' the firm{'}s balance sheet under different valuations.
 Starting with bitcoin and moving to other cryptoassets, researchers should consider procedures for the ``shelf life'' of valuations and realistic stress tests.
@@
 The problem is even more substantial for companies that hold alt-coins which may have thin markets and short histories upon which to compare financial projections.
-A remedy would be the disclosure of significant assumptions underlying these projections to satisfy financial statement users of the company\textquotesingle s projected financial health.
+A remedy would be the disclosure of significant assumptions underlying these projections to satisfy financial statement users of the company{'}s projected financial health.
 
@@
 Internally, it must ensure proper controls over the signing keys these DAO tokens are assigned to.
-External to the firm, the DAO application maintaining these tokens on Ethereum\textquotesingle s blockchain must itself be secure (which in the case of the DAO, it was not).
-Auditing internal procedures over cryptographic keys is not unprecedented---maintaining certificate authority keys is critical to some security firm\textquotesingle s financial prospects (a security breach at one firm, \textit{DigiNotar}, bankrupted it~\cite{zetter2011diginotar}).
-Symantec\textquotesingle s self-custodianship over these keys involves elaborate security ceremonies whenever they are required \todo{[Cite]}.
+External to the firm, the DAO application maintaining these tokens on Ethereum{'}s blockchain must itself be secure (which in the case of the DAO, it was not).
+Auditing internal procedures over cryptographic keys is not unprecedented---maintaining certificate authority keys is critical to some security firm{'}s financial prospects (a security breach at one firm, \textit{DigiNotar}, bankrupted it~\cite{zetter2011diginotar}).
+Symantec{'}s self-custodianship over these keys involves elaborate security ceremonies whenever they are required \todo{[Cite]}.
 
 %---------+++++++++++++++++++-----------------
-\paragraph{Issue: Materiality.} Materiality is considered to be any value that is significant enough to have an impact on the user\textquotesingle s decision-making, and GAAS dictates that materiality for profitable entities be set at 5\% of pre-tax income.
+\paragraph{Issue: Materiality.} Materiality is considered to be any value that is significant enough to have an impact on the user{'}s decision-making, and GAAS dictates that materiality for profitable entities be set at 5\% of pre-tax income.
 This means that, in aggregate, the sum of identified and extrapolated errors identified by auditors during their audit cannot exceed 5\% of pre-tax income for a clean opinion to be issued.
@@
 Therefore, auditors must address the issue of an accounting standard that does not contemplate how to measure the value of cryptoassets when considering whether the financial statements they are reporting on are accurate in all substantial respects.
-More commonly for ERC-20 tokens on Ethereum, the recipient of the tokens don\textquotesingle t have the option to reject the deposits nor would get notified of the new tokens received, which could result in issues with completeness.
+More commonly for ERC-20 tokens on Ethereum, the recipient of the tokens don{'}t have the option to reject the deposits nor would get notified of the new tokens received, which could result in issues with completeness.
 
@@
 \todo{Check out the notes on the google docs regarding this section}
+
+% Non-trivial
+% Not infeasible
+% Onus on firm not auditor -> move away over time

### 2018-09-24 auditing/Latex/sections/02-body.tex
[auditing] edits and citations till section 5

@@
 This does not eliminate the issue of ownership, it simply shifts the concern from the firm{'}s audit to the audits of central custodians.
-Banks and organizations who provide custodial services are required to have robust internal controls over the safeguarding of assets in their care, and provide audited report supporting the reliability of their controls.
+Banks and organizations who provide custodial services are required to have robust internal controls over the safeguarding of assets in their care and provide audited report supporting the reliability of their controls.
 
@@
 The most direct technique is to use a zero knowledge proof of knowledge of this private key, and staple in some information identifying the context of the proof.
-For standard proofs, this is cryptographically equivalent to simply signing a challenge message with the key\footnote{A Schnorr Sigma-protocol with the challenge hashed in using Fiat-Shamir is exactly a Schnorr signature and closely related to an ECDSA signature.}.
+For standard proofs, this is cryptographically equivalent to simply signing a challenge message with the key\footnote{A Schnorr Sigma-protocol with the challenge hashed in using Fiat-Shamir is exactly a Schnorr signature and closely related to an ECDSA signature.\todo{CITE}}.
 Folklore protocols of sending small cash amounts from an allegedly owned account to the auditor to demonstrate control are also commonly noted in the literature (and used in at least one occasion \todo{[cite]}).
 This offers similar security but adds ethical complexities for the auditor.
-\todo{ It requires more cryptography citations here!  }
+\todo{ It requires more [cryptography] citations here! ~\cite{swire_uses_nodate,blaze1998compliance,kohlas_reasoning_nodate} }
 % What to cite for the [cite] placeholder
@@
 A malicious company might arrange for the owner of cryptoassets to engage in signing statements or moving test amounts fraudulently on their behalf.
-This issue is not new: an insolvent retail store might borrow inventory from elsewhere to inflate its assets during an audit, which will in this case involve a physical visit and inventory check by the auditor.
+This issue is not new: an insolvent retail store might borrow inventory from elsewhere to inflate its assets during an audit, which will, in this case, involve a physical visit and inventory check by the auditor.
 Auditors mitigate this by arranging a common date for all audits of physical inventory, and similarly, cryptographic audits might be synchronized on a fixed schedule to prevent the same assets from being counted for different companies in different audits~\cite{dagher2015provisions}.
@@
 These mechanics can become complicated.
-For example, the DAO maintained ether and two types of tokens (DAO tokens and reward tokens) across four different internal accounts, and holders of DAO tokens could split off balances from these accounts into a new (two token, four account) DAO, in addition to certain types of withdrawals.
+For example, the DAO~\cite{jentzsch2016decentralized} maintained ether and two types of tokens (DAO tokens and reward tokens) across four different internal accounts, and holders of DAO tokens could split off balances from these accounts into a new (two tokens, four accounts) DAO, in addition to certain types of withdrawals.
 Establishing ownership requires understanding the internal accounting of the applications maintaining the assets.
@@
 %---------+++++++++++++++++++-----------------
-\paragraph{Issue: Self-custodianship.} Cryptocurrency advocates point to its non-reliance on trusted third parties as key to its appeal \todo{[cite: CHI paper]}.
+\paragraph{Issue: Self-custodianship.} Cryptocurrency advocates point to its non-reliance on trusted third parties as the key to its appeal \todo{[cite: CHI paper]}.
 Thus, the use of a custodian for cryptoassets (or more specifically, the private keys controlling the assets) is controversial.
@@
 Self-custodianship of non-digital assets, such as diamonds for a jewelry retailer or cash for a currency exchange, is already a concern for financial auditors.
-Further, custodianship over cryptographic keys is a financial factor in other sectors, such as certificate authorities like Versign or Symantec which maintain keys critical to HTTPS and DNSSEC \todo{[cite]}.
+Further, custodianship over cryptographic keys is a financial factor in other sectors, such as certificate authorities like Verisign or Symantec which maintain keys critical to HTTPS and DNSSEC \todo{[cite]}.
 To date, no blockchain custodian or exchange has been able to produce a report that supports the reliability of their internal controls in order to provide auditors with comfort over the sufficiency of their systems.

### 2018-09-25 frontrunning/Latex/sections/paper.tex
Moving to ICO (everything in blue needs more explanation)

@@
 The price that users pay for transactions, \textit{gasPrice}, can increase or decrease how quickly miners will execute them and include them within the blocks they mine.
-Once seeing two identical transactions with different transaction fees, a rational miner will prioritize the transaction that pays a higher gas price per unit of gas --gasPrice--, this is due to limited space in the blocks while maximizes their profit in the block they mine.
+Once seeing two identical transactions with different transaction fees, a rational miner will prioritize the transaction that pays a higher gas price per unit of gas, \textsf{gasPrice}, due to limited space in the blocks.
 Therefore, any regular users who run a full-node Ethereum client can front-run pending transactions by sending similar transaction with higher gas price.
@@
 
-Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage~\cite{aune2017footprints}.They also propose a cryptographic approach, similar to commit and reveal (see Section~\ref{CommitmentScheme}) to prevent front-running.
+Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to market information leakage~\cite{aune2017footprints}.They also propose a cryptographic approach, similar to commit and reveal (see Section~\ref{CommitmentScheme}) to prevent front-running.
 Malinova and Park discuss different design settings for financial markets and trading platforms on decentralized ledgers~\cite{malinova2017market}.
@@
 
-\subsection{Markets and Exchanges.} \label{sec:frontrunningExchanges}
+% = = =
+
+\subsection{Markets and Exchanges} \label{sec:frontrunningExchanges}
 
@@
 %Tragedy of the commons
-The first category of DApp in Table~\ref{tab:top25DApps} is exchanges. 
-Exchanges such as EtherDelta\footnote{also known as ForkDelta for the UI \url{https://forkdelta.app/}}, is the closest implementation to decentral exchanges, however their order books are stored on a central server they control and shown on their user interface (website).
-Other than the fact that they can re-order or censor the orders on their servers, there are other risks of front-running nature in these designs.
-Similarly 0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the order book holders and are not prone to cheating.
-One main issue with these designs is the \textit{cancellation grief}.
-Although the order books are not in the smart contract, in order to prevent denial of service attacks, the user needs to send a transaction to cancel her order.
-In this case, when an adversarial actor sees the cancellation transaction, he sends a fill order transactions with higher gasPrice to get in front of the cancellation order and take the order before it is canceled.
-As mentioned in ~\ref{minersfrontrunning}, miners are in a better position to perform such an attack.
 
@@
 ~\cite{eskandari2017feasibility} As the smart contract is the entity that acts as the market maker on regular cases with high liquidity front-running of the option calls do not result in any advantages, however, in the case of low balance of smart contracts pool of funds, the front-runner can front-run others to use up the remaining of the funds and make the rest of the option calls fail.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.7\linewidth]{figures/Miner_reorder_frontrun.png}
+\caption{The adversarial miner can monitor the Ethereum mempool for decentralized exchange cancel orders and upon seeing the cancellation transaction, he puts his buy order prior to the cancel transaction.
+Doing so, the miner can profit from the underlying trade and also get the gas included in the cancel transaction.
+\label{fig:MinerFrontrunning}}
+\end{figure}
+%https://www.lucidchart.com/invitations/accept/c8768786-4a3f-4c78-b3c8-aa04a6b81d06
+
+The first category of DApp in Table~\ref{tab:top25DApps} is exchanges.
+Exchanges such as EtherDelta\footnote{also known as ForkDelta for the UI \url{https://forkdelta.app/}}, purport to implement a decentralized exchange, however their order books are stored on a central server they control and shown on their users with a website interface.
+Central exchanges can front-run orders in the traditional sense, as well as re-order or block orders on their servers.
+0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the order book holders \textblue{and are not prone to cheating.} One main issue with the relay design is \textit{cancellation grief}.
+To \textblue{prevent denial of service attacks}, the user needs to send a transaction to cancel her order.
+In this case, an adversarial actor many see a pending  cancellation transaction, and send  a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled.
+This is illustrated in Figure~\ref{fig:MinerFrontrunning}.
 
@@
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.7\linewidth]{figures/Miner_reorder_frontrun.png}
-\caption{The adversarial miner can monitor the Ethereum mempool for decentral exchange cancel orders and upon seeing the cancellation transaction, he puts his buy order prior to the cancel transaction.
-Doing so, the miner can profit from the underlying trade and also get the gas included in the cancel transaction.
-\label{fig:MinerFrontrunning}}
-\end{figure}
-%https://www.lucidchart.com/invitations/accept/c8768786-4a3f-4c78-b3c8-aa04a6b81d06
+Designing truly decentralized exchanges, where the orderbook is implemented directly on a public blockchain, is being pursued by a number of projects [\textblue{cite github page}].
+These designs generally face the following attack (illustrated in Figure~\ref{fig:RegularFrontrunning}).
+An adversary can monitor the network with a full node for pending \textit{buy} (or \textit{sell}) transactions which could increase (or \textit{decrease}) the future price of the asset.
+A front-runner can send a competing orders with a higher gas price, and hope to have her transactions mined ahead of the original pending transaction.
+The benefits of doing this vary.
+If the original bid is a large market order (\ie it will execute at any price), the adversary can front-run a pair of limit orders that will bid near the best offer price and offer at a higher price.
+If these execute ahead of the market order, the front-runner profits by scalping the price of the shares.
+If the adversary has pre-existing offers likely to be reached by the market order, she could front-run a cancelation and a new offer at a higher price.
+A simpler attack would be to guage the demand for trades at a given price by the number of pending orders, and to front-run at the same price in hopes that the market demand is the result of accurate new market information.
+Miners are in the best position to conduct these attacks as they hold fine-grained control over the exact set of transactions that will execute and in what order and can mix in their own (late) transactions without broadcasting them.
+Miners do however have to commit to what their own transactions will be before beginning the proof of work required to solve a block.
 
-see figure~\ref{fig:RegularFrontrunning}.
-For example, in a decentral exchange, he can monitor the network and once seeing a pending \textit{buy} transaction which will further increase the price of the asset, a front-runner can send a transaction with a higher gas price and hope to have his transaction mined ahead of the original pending transaction.
-By doing so, he achieves a better rate from the buyer.
-Note that in this case, blockchain front-runners are visible to the network as they broadcast their transactions to all the network participants.
-The probability of success in such attach can be increased by flooding the network by transactions with higher than average gasPrice.
-
-For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token\ie TKN, presumably if this transaction goes through, it causes the price of the purchased token to increase.
-So the dishonest miner can step in front of this transaction and place his own buy order ahead.
-He would simply create his \textit{buy} of 1000 TKN and include it in front of the previous \textit{buy} transaction in the block he mines.
-Doing so, he would receive a better rate than other network users, and afterward can sell the assets he has bought and gained a price advantage.
-It should be noted that miners can only front-run transactions within the blocks they happen to mine.
-They could do this also by not broadcasting their own transactions to the network before including it in the block, this makes the miners be less noticeable to the network when front-running.
-
-Another example here is in the case of decentral exchanges and order cancellation.
-Every exchange should have the functionality to cancel the orders, especially for a volatile market.
-In this case, when the user decides that her order is not profitable anymore, she would send a cancelation transaction.
-Here the miner sees the cancelation transaction and puts his own transaction to fill that order in front of the cancellation transaction --transaction reordering--, potentially profiting from the order.
-He can also include the canceled transaction in the block to collect the full gas limit used by the cancel transaction~\cite{CostofDecentralization:online}, see figure~\ref{fig:MinerFrontrunning}.
-Front-running can also occur in non-financial smart contracts.
+% Front-running can also occur in non-financial smart contracts.
 As an example, a smart contract which adds all the participants to a party invite list could only be closed by the smart contract owner.
@@
 Bancor is another Ethereum-based application that allows users to exchange their tokens without any counter-party risk.
-This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that is always available to users.
-ERC20 is the interface standard for implementing tokens on top of Ethereum~\cite{erc20}.
-Smart Tokens can be bought and sold through the users smart contract at an automatically calculated price which displays supply and demand.
-Doing so, Bancor protocol provides continuous liquidity for digital assets without relying on an order book as there is no requirement to match sellers and buyers.
+This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}.
+Smart tokens are ERC20-compatible and can be bought or sold through a DApp-based dealer that is always available and implements a market scoring rule to manage its prices.
+Doing so, Bancor provides continuous liquidity for digital assets without relying on brokers to match buyers with sellers.
 Implemented on the Ethereum blockchain, when transactions are broadcast to the network, they sit in a pending transaction pool known as \textit{mempool} waiting for the miners to mine them.
 Since Bancor handles all the trades and exchanges on the Ethereum blockchain (unlike other existing decentralized exchanges), these transactions are all visible to the public for some time before being included within a block.
-This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favorable profits~\cite{BancorIs7:online}.
+This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions \textblue{and gain favorable profits}~\cite{BancorIs7:online}.
 Researchers have shown and implemented a proof of concept code to front-run Bancor as a regular non-miner user~\cite{NewTab13:online}.
 
-%______________________________________________________________%
-\subsection{Crypto-Collectibles Games.}
+% = = =
+
+\subsection{Crypto-Collectibles Games}
 
 The second category of DApp in Table~\ref{tab:top25DApps} is crypto-collectables.
-
-Crypto-Collectibles, also known as \textit{ERC-721 Non-Fungible Token Standard}~\cite{erc721}, is one of the applications of Ethereum blockchain.
-Cryptokitties are known to be one of the first and the most popular use cases of ERC721 tokens~\cite{cryptokitties}.
-Their market cap reached more than 6 million dollars in the first few months their launch, however, declined soon after.
-Crypto-Collectibles, are similar to ERC-20 tokens and can be listed on exchanges.
-Most of the front-running issues applied to the exchanges also apply to DApps using ERC-721 tokens.
-\\
-
-As an example Cryptokitties can be bred, bought or sold through the main interface\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}}. %see Figure~\ref{fig:cryptokittie}.
-To buy a cryptokittie, the user sends a bid transaction \textit{bid(uint256 \_tokenId)} containing the cryptokittties ID which can be found either on their website or on the ERC721 token smart contract.
-This is similar to open auctions, bid value and the object bidding on is visible to the network and any user could be easily front-run by sending the same transaction with higher gasPrice to replace the initial bidder.
+Consider Cryptokitties,\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}} the most active DApp in this category and third most active overall.
+Each cryptokitty (see Appendix~\ref{app:cryptokitty}) is a cartoon kitten with a set of unique features to distinguish it from other cryptokitties, some features more rare and harder to obtain.
+They can be bought, sold, or bred with other cryptokitties.
+At the Ethereum level, the kitty is a token implemented with \textit{ERC-721: Non-Fungible Token Standard}~\cite{erc721}.
+The market cap of cryptokitty tokens peaked at more than 6 million dollars in the first few months their launch, however, has declined since.
+ERC-721 are similar enough to ERC-20 tokens that they can be listed on exchanges setup for ERC-20.
+To buy a cryptokittie, the user sends the following bid transaction: \texttt{bid(uint256 \_tokenId)}.
+It contains the cryptokittty's ID which can be found either on their website or on the ERC721 token smart contract.
+\textblue{This is similar to open auctions, bid value and the object bidding on is visible to the network and any user could be easily front-run by sending the same transaction with higher gasPrice to replace the initial bidder.}
 % https://etherscan.io/tx/0x62a76b7e345e8abd463487d0348c118a9314b197024e090fee7b1fbce434da40
 
-%Possibly remove this figure due to page limit
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.3\linewidth]{figures/cryptokittie842912.png}
-\caption{ Cryptokitty Number 842912 \label{fig:cryptokittie}}
-\end{figure}
+% The blue above needs expansion with further details.
 
-%______________________________________________________________%
+% = = =
 
@@
 The third category of DApp in Table~\ref{tab:top25DApps} is gambling services.
+While a large category of gambling games are based on random outcomes, DApps do not have unique access to an unpredictable data stream to harvest for randomness.
+Any candidate (such as block headers) source of randomness is accessible to all DApp functions and can also be manipulated to an extent by miners.
 
-Due to the deterministic nature of blockchains, running gambling games based on randomness is close to impossible.
-There had been attempts to use block headers or such as the seed of randomness but almost all have failed as every data accessible to the smart contract at the time of execution, is also accessible to other smart contracts and they could predict the output on the run, thus prone to front-running and miner\'s manipulation.
-Many infamous gambling games are now running on Ethereum network and front-running them requires a level of sophistication and knowledge of the internal of the games and Ethereum.\\
-One of the most popular smart contracts on Ethereum blockchain belongs to a controversial gambling game named \texttt{Fomo3d}, also known as \textit{Exit Scam}\footnote{\url{https://exitscam.me/play}}.
-The aim of this game is to be the last person purchasing the key when the timer goes to zero in which every ticket purchase increases the timer by 30 seconds.
-It was believed that because of the nature of the game, it will never end, however on August 22, 2018 the first round of the game ended and the winner taking 10,469 Ether\footnote{First winner of Fomo3D, won 10,469 Ether \url{ https://etherscan.io/tx/0xe08a519c03cb0aed0e04b33104112d65fa1d3a48cd3aeab65f047b2abce9d508}}, equivalent to 2.1 Million dollars on the time of writing.
-It is believed that the winner, used a sophisticated approach to finish last~\cite{fomo3dhacker}, we call this approach \textit{Denial-of-service Front-running}.
-The winner deployed a few high gas consumption smart contracts prior to the win when the timer of the game reached about 3 minutes, the winner bought 1 ticket and sent multiple high gasPrice transactions to aforementioned smart contracts to lure the miners to mine these highly profitable transactions.
-For a DoS front-running to work, the attacker floods the network with high gasPrice transactions to prevent other transactions to go through.
-Luckily enough the winner was able to congest the network in a way that no other ticket purchases were mined in the 3 minutes window and the miners were prioritizing the high gasPriced transactions over other transactions.
-All the details mentioned here are drawn from the transaction history on the blockchain and unless otherwise proven seem to be the way the winner acted to win the pot.
+\textsf{Fomo3D} is an example of a game style (known as \textsf{Exit Scam}\footnote{\url{https://exitscam.me/play}}) not based on random outcomes, and it is the most active game on Ethereum in our sample.
+The aim of this game is to be the last person to have purchased a ticket when a timer goes to zero in a scenario where anyone can buy a ticket and each purchase increases the timer by 30 seconds.
+Many speculated such a game would never end but on August 22, 2018, the first round of the game ended with the winner collecting 10,469 Ether\footnote{The first winner of Fomo3D, won 10,469 Ether \url{ https://etherscan.io/tx/0xe08a519c03cb0aed0e04b33104112d65fa1d3a48cd3aeab65f047b2abce9d508}} equivalent to \$2.1M USD at the time.
+Blockchain forensics indicate a sophisticated winning strategy to frontrun new ticket purchases~\cite{fomo3dhacker} that would reset the counter.
+The winner appears to have started by deploying some high gas consumption DApps unrelated to the game.
+When the timer of the game reached about 3 minutes, the winner bought 1 ticket and then sent multiple high gasPrice transactions to her own DApps.
+These transactions congested the network and bribed miners to prioritize them ahead of any new ticket purchases in \textsf{Fomo3D}.
+
 %probably needs more work to be good enough. more resources will be out in the coming days!
 
-%______________________________________________________________%
+% Is this the same as order flooding in HFT?
+
+% = = =
+
 \subsection{Name Services.}\label{sec:ens}
 
-The final category of DApp in Table~\ref{tab:top25DApps} is name services.
-
-Front-running can also occur within non-financial blockchain applications such as naming systems.
-Recently, many blockchain-based domain registrars have been designed and implemented to eliminate the role of central parties \ie domain name system (DNS) which itself introduced the single point of failures to the entire web.
-Ethereum Name Service (ENS)\footnote{\url{https://ens.domains/}}, is the most popular decentral naming service that uses a sealed auction to facilitate the procedures of purchasing new \texttt{.eth} domain names.
-Although sealed auction method is used in ENS implementation, the normal workflow uses \textit{startAuctionsAndBid()} with the deposit equal or higher than the bid, this information leakage could be used to front-run the transaction with the same bid amount or slightly higher to outbid the initial sealed bid.
-By doing so the front-runner invalidates the original bid and hence registers the domain name himself.
-Ghazal is another Ethereum-based naming system that allows users to register \texttt{.ghazal} domain names and bind certificates to those names~\cite{moosavighazal}.
-As Ghazal is using a registration method in plain text, it is susceptible to front-running.
-Note that front-running domain names has been a subject of discussion outside the context of blockchian applications before~\cite{sac022en33:online}.
-Domain name registrars can steal available domain names upon seeing a query from an interested user for the availability of the domain.
-In this case, the registrar can register the domain name ahead and sell it back to the user for a higher price.
+The final category in Table~\ref{tab:top25DApps} is name services, which are primarily aimed at displacing central parties involved in web domain registration (\eg ICAAN and registrars) and resolution (\eg DNS).
+For simple name services (such as some academic work like Ghazal~\cite{moosavighazal}), domains purchases are transactions and network monitors can front-run other users attempting to register domains.
+This parallels front-running attacks seen in regular (non-blockchain) domain registration~\cite{sac022en33:online}.
+\textsf{Ethereum Name Service (ENS)}\footnote{\url{https://ens.domains/}} is the most active naming service on Ethereum.
+Instead of allowing new  \texttt{.eth} domain names to be purchased directly, they are put up for a sealed bid auction.
+\textblue{Although sealed auction method is used in ENS implementation, the normal workflow uses \texttt{startAuctionsAndBid()} with the deposit equal or higher than the bid, this information leakage could be used to front-run the transaction with the same bid amount or slightly higher to outbid the initial sealed bid.
+By doing so the front-runner invalidates the original bid and hence registers the domain name himself.}
 
@@
 % = = = ICOs
-% = = = = = = = = = = = = = = = = = = = = = = = = = = %%
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = %
 
@@
 
+\textblue{Cite Princeton paper on Namecoin for frontrunning mitigation using commit/reveal.}
+
 \begin{figure}[h]

### 2018-09-25 auditing/Latex/sections/02-body.tex
[auditing] edit and citations till section 6

@@
 \paragraph{Issue: Bans.} There regulatory rules for cryptoassets differ based on the jurisdiction; for instance, cryptoassets are absolutely banned in Algeria, Bolivia, and Pakistan (among others), and implicitly banned under investor protection rules in Colombia, Saudi Arabia, and China (among others)~\cite{cryptoLegalityWiki}.
-Also there are banking limitations for companies dealing directly with cryptoassets in some other countries such as Canada, India and Thailand.
+Also, there are banking limitations for companies dealing directly with cryptoassets in some other countries such as Canada, India, and Thailand.
 This limitation impacts the valuation of cryptoassets on hand.
@@
 %---------+++++++++++++++++++-----------------
-\paragraph{Issue: Inadequate Liquidity.} While bitcoin and ether enjoy around-the-clock trading across many markets, lesser known coins, tokens, assets, or liabilities may trade slowly, in low volumes.
-Generally speaking, low liquidity results in stale last sale prices, and large bid-ask spreads.
+\paragraph{Issue: Inadequate Liquidity.} While bitcoin and ether enjoy around-the-clock trading across many markets, lesser-known coins, tokens, assets, or liabilities may trade slowly, in low volumes.
+Generally speaking, low liquidity results in stale last sale prices and large bid-ask spreads.
 This challenging but not unprecedented in financial auditing: privately held stocks and over-the-counter financial instruments share a similar profile.
@@
 %---------+++++++++++++++++++-----------------
-\paragraph{Issue: Geographical Variation.} Because bitcoin can be moved digitally without any geographic restrictions, it should be the case that any variation in bitcoin prices across exchanges would be consumed by arbitrageurs.
+\paragraph{Issue: Geographical Variation.} Because cryptoassets(\eg bitcoin) can be moved digitally without any geographic restrictions, it should be the case that any variation in cryptoasset prices across exchanges would be consumed by arbitrageurs.
 However, empirically this is not the case due to fees, settlement delays, and other frictions with exchange services \todo{[cite]}.
@@
 This may lead to price discrepancies between equal amounts of cryptoassets, where assets with clear provenance might be preferred to assets with long transaction records involving unknown entities and possible fraud, theft, or other issues that might legally encumber the current holder of the asset.
-The materiality of a premium for ``clean'' cryptoassets is an open research question; some markets for fresh bitcoin were announced but never materialized \todo{[c]}.
+The materiality of a premium for ``clean'' cryptoassets is an open research question; some markets for fresh bitcoin were announced but never materialized~\cite{moser2014towards}.
 
@@
 Auditors are required to perform procedures to verify the reasonableness of this assumption.
-For instance, the auditors could examine projections where the cryptoassets the firm holds increase or decrease in value, however this may be difficult due to  the high volatility of cryptoassets.
+For instance, the auditors could examine projections where the cryptoassets the firm holds increase or decrease in value, however, this may be difficult due to the high volatility of cryptoassets.
 Bitcoin, for instance, increased 10-fold over the last half of 2017.
-The problem is even more substantial for companies that hold alt-coins which may have thin markets and short histories upon which to compare financial projections.
+The problem is even more substantial for companies that hold other cryptocurrencies, alt-coins, which may have thin markets and short histories upon which to compare financial projections.
 A remedy would be the disclosure of significant assumptions underlying these projections to satisfy financial statement users of the company{'}s projected financial health.

### 2018-09-25 frontrunning/Latex/sections/paper.tex
moving to mitigations

@@
 
-Blockchain technology enables smart contracts or decentralized applications (DApps).
+Blockchain technology enables decentralized applications (DApps) or smart contracts.
 Function calls (or transactions) to the DApp are processed by a decentralized network.
@@
 \subsection{Literature on Traditional Front-running}\label{traditionalFrontrunning}
-Front-running was first observed on the Chicago Board Options Exchange (\textit{CBoE})~\cite{markham1988front}, and was defined by Securities Exchange Commission \textit{(SEC)} in 1977 as: ``The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}''
-
-Self-regulating exchanges (\eg \textit{CBoE}) and the \textit{SEC} spent the ensuing years planning how to detect and outlaw front-running practices~\cite{markham1988front}.
+Front-running originates on the Chicago Board Options Exchange (\textit{CBoE}) \cite{markham1988front}.
+The Securities Exchange Commission \textit{(SEC)} in 1977 defines it as: ``The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{A block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}'' Self-regulating exchanges (\eg \textit{CBoE}) and the \textit{SEC} spent the ensuing years planning how to detect and outlaw front-running practices~\cite{markham1988front}.
 The \textit{SEC} stated: ``It seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge.\footnote{Securities Exchange Act Release No.
@@
 Fitzsimmons, Secretary, Securities, and Exchange Commission to Joseph W.
-Sullivan, President  CBoE).}'' The \textit{CBoE} tried to educate their members on existing rules, however differences in opinion regarding the unfairness of front-running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~\cite{sec1978optionsmarket}.
-
-We refer the reader interested in further details on the early regulatory history of front-running to Markham~\cite{markham1988front}.
-Initially front-running policies applied only to certain option markets.
+Sullivan, President  CBoE).}'' The \textit{CBoE} tried to educate their members on existing rules, however differences in opinion regarding the unfairness of front-running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action~\cite{sec1978optionsmarket} until the SEC began regulation.
+We refer the reader interested in further details on this early regulatory history to Markham~\cite{markham1988front}.
+The first front-running policies applied only to certain option markets.
 In 2002, the rule was expanded to cover all security futures~\cite{finra_2002}.
@@
 Doing so, they are able to listen to the network and monitor all transactions that are broadcast.
-On the Ethereum blockchain, users have to pay for the computations in a small amount of Ether called \textit{gas}~\cite{AccountT67:online}.
-The price that users pay for transactions, \textit{gasPrice}, can increase or decrease how quickly miners will execute them and include them within the blocks they mine.
+On the Ethereum blockchain, users have to pay for the computations in a small amount of Ether called \textsf{gas}~\cite{AccountT67:online}.
+The price that users pay for transactions, \textsf{gasPrice}, can increase or decrease how quickly miners will execute them and include them within the blocks they mine.
 Once seeing two identical transactions with different transaction fees, a rational miner will prioritize the transaction that pays a higher gas price per unit of gas, \textsf{gasPrice}, due to limited space in the blocks.
 Therefore, any regular users who run a full-node Ethereum client can front-run pending transactions by sending similar transaction with higher gas price.
-Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this in case of malicious reordering is known as \textbf{transaction reordering} attack.
+Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this in case of malicious reordering is known as \textsf{transaction reordering} attack.
 
@@
 In particular, ideal functionalities of blockchains (such as those used in simulation-based proofs) need to capture this adversarial capability, assuming the real blockchain does not address front-running.
-Literature like the Bitcoin Backbone~\cite{} and Hawk~\cite{} capture this.
+\textblue{Literature like the Bitcoin Backbone~\cite{} and Hawk~\cite{} capture this.}
 
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
 \centering
 \includegraphics[width=0.7\linewidth]{figures/Miner_reorder_frontrun.png}
-\caption{The adversarial miner can monitor the Ethereum mempool for decentralized exchange cancel orders and upon seeing the cancellation transaction, he puts his buy order prior to the cancel transaction.
+\caption{\scriptsize The adversarial miner can monitor the Ethereum mempool for decentralized exchange cancel orders and upon seeing the cancellation transaction, he puts his buy order prior to the cancel transaction.
 Doing so, the miner can profit from the underlying trade and also get the gas included in the cancel transaction.
@@
 The first category of DApp in Table~\ref{tab:top25DApps} is exchanges.
-Exchanges such as EtherDelta\footnote{also known as ForkDelta for the UI \url{https://forkdelta.app/}}, purport to implement a decentralized exchange, however their order books are stored on a central server they control and shown on their users with a website interface.
+Exchanges such as EtherDelta\footnote{Also known as ForkDelta for the UI \url{https://forkdelta.app/}}, purport to implement a decentralized exchange, however their order books are stored on a central server they control and shown on their users with a website interface.
 Central exchanges can front-run orders in the traditional sense, as well as re-order or block orders on their servers.
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
 \centering
 \includegraphics[width=0.7\linewidth]{figures/Regular_frontrunning.png}
-\caption{The Adversary up on seeing the Buy order, sends his own buy order with higher gas to front-run the first order. \label{fig:RegularFrontrunning}} 
+\caption{\scriptsize The Adversary up on seeing the Buy order, sends his own buy order with higher gas to front-run the first order. \label{fig:RegularFrontrunning}} 
 \end{figure}
@@
 
-There have been more than 3000 ICOs on Ethereum alone, estimated to exceed 75 billion dollars in the first half of 2018~\cite{zetzsche2018ico}.
-In Table~\ref{top25DApps}, no ICO is represented in the top 25.
-This is because they tend to be high in activity for a short duration only---namely during their sale.
-Since no major ICO was active on the day that we sampled \texttt{DAppRadar.com}, the ICO category falls through our sampling method.
-However we identify this as a major category and study it here.
+Initial coin offerings (ICOs) have changed how blockchain firms raise capital.
+More than 3000 ICOs have been held on Ethereum, and the market capitalization of these tokens appear to exceed \$75B USD in the first half of 2018~\cite{zetzsche2018ico}.
+At the DApp level, tokens are offered in short term sales that see high transaction activity while the sale is on-going and then ICO activity tappers off to occasional owner transfers.
+When we collected the top 25 most active DApps on \texttt{DAppRadar.com}, no significant ICOs were in the initial sale stage.
+Despite the ICO category falls through our sampling method, we identify it as a major category of DApp and study it here.
 
@@
 \subsection{\textit{Status.im} ICO}
-As discussed in Section~\ref{sec:Front Running on the Blockchains}, capped ICOs are considerable applications to be investigated in terms of the front-running attacks, \textit{Status.im} ICO is such an application.
+To deal with demand, ICOs will cap sales in a variety of ways to mitigate front-running attacks.
 In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached the predefined cap within 3 hours, resulting in close to 300,000 Ether of funds.
-In order to prevent few large investments to buy up all the tokens and limit the amount of Ether deposited in an investment, they used a \textit{fair} token distribution method named \textit{Dynamic Ceiling} as an attempt to increase the opprotunity window for smaller investors.
-They implemented multiple caps --ceiling-- in which, each had a maximum amount that could be deposited in.
+In order to prevent few large investments to buy up all the tokens and limit the amount of Ether deposited in an investment, they used a `fair' token distribution method they called a \textit{Dynamic Ceiling} as an attempt to increase the opportunity for smaller investors.
+They implemented multiple caps or ceilings in which, each had a maximum amount that could be deposited in.
 In this case, every deposit was checked by the smart contract and the exceeding amount was refunded to the sender while the accepted amount was sent to their multi-signature wallet address~\cite{statusicoanalysis}.
@@
 Further study showed that some mining pools might have been manipulating the network for their own profit.
-In addition, there were many transactions sent with a higher gas price to front-run other transactions, however, these transactions were failing due to the restriction in the ICO smart contract to reject any transactions with higher than 50 \textit{GWei} gas price (as an attempt to prevent the known front-running behaviour).
+In addition, there were many transactions sent with a higher gas price to front-run other transactions, however, these transactions were failing due to the restriction in the ICO smart contract to reject any transactions with higher than 50 \textit{GWei} gas price (another mitigation against frontrunning).
 
-\begin{figure}[h]
+\begin{figure}[t]
 \centering
 \includegraphics[width=0.5\linewidth]{figures/Mining_pool_ratio.png}
-\caption{The percentage of Ethereum blocks mined between block 3903900 and 3908029, this is the time frame in which Status.im ICO was running.
+\caption{\scriptsize The percentage of Ethereum blocks mined between block 3903900 and 3908029, this is the time frame in which Status.im ICO was running.
 This percentage roughly shows the hashing power ratio each miner had at that time.
@@
 \subsection{Data Collection and Analysis}
-According to the analysis we carried out, it was discovered that the F2Pool, an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure ~\ref{fig:mining_pool_ratio}), sent 100 Ether to 30 new Ethereum addresses before Status.im ICO started.
-On the time the ICO was opened for participation, F2Pool constructed 31 transactions to the ICO token sale smart contract from the addresses they controlled --without broadcasting these transactions to the network-- and used their entire mining power to mine their own transactions and some other potentially failing high gas price transactions.
+According to analysis we carried out, we discovered that the F2Pool---an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure~\ref{fig:mining_pool_ratio})---sent 100 Ether to 30 new Ethereum addresses before the Status.im ICO started.
+When the token sale opened, F2Pool contsructed 31 transactions to the ICO token sale smart contract from the addresses these new address, without broadcasting these transactions to the network.
+They used their entire mining power to mine their own transactions and some other potentially failing high gas price transactions.
 
-Ethereum blockchain contains all transaction ever made on Ethereum, however, it is not easy to see the behaviour of the participants and miners solely using the default clients nor online blockchain explorers.
-In order to get the required data, Ethereum blockchain data should be converted to a queryable format.
-For this case study, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation\url{https://github.com/ethereum/go-ethereum}} for the full node, python script for extracting, transforming and loading ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery\footnote{\url{https://cloud.google.com/bigquery/}}.
-Using this software stack, we were able to query for all the transactions and blocks within the window of Status.im ICO for further analysis which was mainly done by data analysis tool \texttt{Tableau}\footnote{\url{https://www.tableau.com/}}.
-A copy of this dataset and the initial findings can be found in our Github repository\footnote{\url{github.com / ANONYMOUS}}.
+Ethereum's blockchain contains all transaction ever made on Ethereum.
+While the default client and online blockchain explorers offer some limited querying, in order to analyze this case, we built our own database.
+Specifically, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation\url{https://github.com/ethereum/go-ethereum}} for the full node, a python script for extracting, transforming and loading ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery.\footnote{\url{https://cloud.google.com/bigquery/}} Using this software stack, we were able to isolate transactions within the Status.im ICO sale.
+We used data analysis tool \texttt{Tableau}.\footnote{\url{https://www.tableau.com/}} A copy of this dataset and the initial findings can be found in our Github repository.\footnote{\url{github.com/} Removed for anonymity.}
 
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
 \centering
-\includegraphics[width=0.7\linewidth]{figures/Transactions_miners_while_status_ico_cut_only_icotx.png}
-\caption{This chart shows the miners behaviour on the time window that Status.im ICO was running.
+\includegraphics[width=0.9\linewidth]{figures/Transactions_miners_while_status_ico_cut_only_icotx.png}
+\caption{\scriptsize This chart shows the miners behaviour on the time window that Status.im ICO was running.
 It is clear that the number of successful transactions mined by F2Pool do not follow the random homogeneous pattern of the rest of the network.
@@
 
-By tracing the transactions from these 30 addresses, we found explicit Interference of the F2Pool\footnote{F2Pool Ethereum address was identified by their mining reward deposit address \url{https://etherscan.io/address/0x61c808d82a3ac53231750dadc13c777b59310bd9}} in this scenario.
-As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses were sent to Status.im ICO and mined by F2Pool themselves, where the dynamic ceiling algorithm refunded a portion of the deposited funds back to these addresses, these funds were sent back to F2Pool main address a few days after.
-
-\begin{figure}[h]
+\begin{figure}[t]
 \centering
 \includegraphics[width=0.7\linewidth]{figures/F2Pool_transactions_to_StatusICO_and_Refunds.png}
-\caption{F2Pool prior to Status.im ICO deposited 100 Ether in multiple new Ethereum addresses.
+\caption{\scriptsize F2Pool prior to Status.im ICO deposited 100 Ether in multiple new Ethereum addresses.
 On the time of the ICO they sent these deposits to Status ICO smart contract and prioritized mining of these transactions in their mining pool, this was to overcome the dynamic ceiling algorithm of the token sale smart contract.
@@
 
+By tracing the transactions from these 30 addresses, we found explicit interference by the F2Pool\footnote{F2Pool Ethereum address was identified by their mining reward deposit address \url{https://etherscan.io/address/0x61c808d82a3ac53231750dadc13c777b59310bd9}} in this scenario.
+As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses were sent to Status.im ICO and mined by F2Pool themselves, where the dynamic ceiling algorithm refunded a portion of the deposited funds back to these addresses, these funds were sent back to F2Pool main address a few days after.
 Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their mining software to behave in a certain way to front-run other transactions and gain monetary profit.
-The dataset used for this analysis can be found on our GitHub repository.\footnote{Front-running Status.im ICO dataset: \url{http://github.com/ANONYMOUS}}.
+
 %______________________________________________________________%
@@
 
-In the traditional markets, front-running is considered unethical and illegal.
-In the blockchain space, the designers of the decentral applications cannot rely on the justice system for preventing unethical behavior, and they must assume that each participant in the network acts rationally in their own self-interest, the application will be operating in an adversarial environment~\cite{0xfrontrunning:online}.
-A few decentral exchange projects such as \textit{EtherDelta} and \textit{0xProject}~\cite{warren20170x}, have proposed solutions for front-running, which is off-chain order books.
+There are two main approaches to mitigating front-running on blockchains: one is to design a blockchain that is front-run resistant, and the other to design the application logic in a way that front-running is not profitable.
+This can be done in addition to any legal remedies that might be enforceable.
+We note, but consider out-of-scope, approaches that introduce trusted parties to centralize time-sensitive functionalities (\eg exchanges \textit{EtherDelta} and \textit{0xProject} use off-chain order books~\cite{warren20170x,0xfrontrunning:online}).
+
+%In the traditional markets, front-running is considered unethical and illegal.
+In the blockchain space, the designers of the decentral applications cannot rely on the justice system for preventing unethical behavior, and they must assume that each participant in the network acts rationally in their own self-interest, the application will be operating in an adversarial environment.
+
+%A few decentral exchange projects such as \textit{EtherDelta} and \textit{0xProject}~\cite{warren20170x}, have proposed solutions for front-running, which is off-chain order books.
 The methods discussed within these projects prevent blockchain network participants from front-running the orders as the orders are private and not known to the network and will not be broadcasted.
@@
 
-\emph{Traditional Front-running Prevention Methods}.
-There are debates in traditional markets regarding the fact that front-running is considered to be a form of insider trading which deemed to be illegal.
-Traditional methods to prevent front-running mainly involves after the fact investigation and legal action against the front-runners~\cite{LexisNexisLawSuit}.
-As mentioned in section~\ref{traditionalFrontrunning}, defining front-running and educating the employees were the first step taken to prevent such issues in traditional markets, however, front-running became less likely to happen mainly because of the high fine and lawsuits against firms who behaved in an unethical way.
-Other methods such as dark pools~\cite{zhu2014dark, buti2011diving} and sealed bids~\cite{radner1989sealed} were discussed and implemented in a variety of regulated trading systems.
-
-The traditional methods to prevent front-running does not apply to blockchain applications, as mainly they are based on central enforcement and limitations, also in case of blockchains the actors who are front-running could be anonymous and the fear of lawsuits would not apply.
-\\
-
-There are two main approaches to prevent front-running blockchains: one to design a blockchain that is front-run resistant, and the other to design the application logics in a way that front-running is not possible.
 %______________________________________________________________%
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
 \centering
-\includegraphics[width=0.7\linewidth]{figures/Vulnerable_Loopring.png}
-\caption{\emph{submitRing} Transaction in the old version of the Loopring protocol.
+\includegraphics[width=0.9\linewidth]{figures/Vulnerable_Loopring.png}
+\caption{\scriptsize \emph{submitRing} Transaction in the old version of the Loopring protocol.
 Any user can regenerate this transaction by replacing the miner's address with his address and signing the hash of the ring using his private key.
@@
 %https://www.lucidchart.com/invitations/accept/33d38ce9-4660-4743-806d-45c72f7e8393
-\begin{figure}[h]
+\begin{figure}[t]
 \centering
 \includegraphics[width=0.7\linewidth]{figures/Dual_Authoring_Loopring.png}
-\caption{\emph{submitRing} Transaction in the new version of the Loopring protocol.
+\caption{\scriptsize \emph{submitRing} Transaction in the new version of the Loopring protocol.
 Other users cannnot regenerate this transaction as they do not access auth-keys and hence are not able to create the signatures.
@@
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.5\linewidth]{figures/commit-reveal.png}
-\caption{Commit and Reveal.
-User sends a commitment transaction with the hash of the data, After the commitment period is over, user sends her reveal transaction to the DApp revealing the information that matches the commitment.
-\label{fig:commitReveal}}
-\end{figure}
-%https://www.lucidchart.com/invitations/accept/3cd4c865-83d4-4c71-9a4a-f2e870f2db2c
+\textblue{Cite Princeton paper on Namecoin for frontrunning mitigation using commit/reveal.}
 
@@
 
-\textblue{Cite Princeton paper on Namecoin for frontrunning mitigation using commit/reveal.}
-
-\begin{figure}[h]
+\begin{figure}[t]
 \centering
 \includegraphics[width=0.5\linewidth]{figures/LibSubmarine.png}
-\caption{Submarine Send~\cite{libsubmarine}.
+\caption{\scriptsize Submarine Send~\cite{libsubmarine}.
 User generates an \textit{Unlock} transaction from which the commitment address is retrieved.
@@
 Going back to Table~\ref{tab:top25DApps}, some DApps facilitate different methods to mitigate front-running issues.
-As an example, LocalEthereum, an escrow-based exchange, uses challenge random values from the website to be included in the signature of the transaction (See ~\ref{code:localethereum}), hence removing any possibility of replay attack or the possibility of any other address sending the similar order.
-
-%Possibly remove this code snippet due to page limit . don't forget to remove the refrence to it ^
-\begin{lstlisting}[basicstyle=\scriptsize\ttfamily,caption={Code snippet from LocalEthereum smart contract.
-Values V,R and S are set by LocalEtherem to have a valid signature, also the tradeHash uses buyer and seller addresses, mitigating the possibility of front-running by a third party.},label={code:localethereum},float]
-    function createEscrow(bytes16 _tradeID, address _seller, address _buyer, uint256 _value, uint16 _fee,
-					uint32 _paymentWindowInSeconds, uint32 _expiry, uint8 _v, bytes32 _r, bytes32 _s) 
-        payable external {
-        bytes32 _tradeHash = keccak256(abi.encodePacked(_tradeID, _seller, _buyer, _value, _fee));
-	...
-        // A signature (v, r and s) must come from localethereum to open an escrow
-        bytes32 _invitationHash = keccak256(abi.encodePacked(
-            _tradeHash,
-            _paymentWindowInSeconds,
-            _expiry
-        )); 
-\end{lstlisting}
+As an example, LocalEthereum, an escrow-based exchange, uses challenge random values from the website to be included in the signature of the transaction (See Code ~\ref{code:localethereum} in Appendix~\ref{app:code}), hence removing any possibility of replay attack or the possibility of any other address sending the similar order.
 
@@
 %______________________________________________________________%
-\section{Concluding Remarks}
+%\section{Concluding Remarks}
 

### 2018-09-25 auditing/Latex/sections/02-body.tex
[auditing] Done with edits. last section needs work.

@@
 How can we satisfy auditors that blockchain records are reliable
+ \todo{This subsection needs some cutting, has duplicate points and not obvious what the main objective is.
+there are some comments on the google docs regarding this subsection that should be addressed}
 
@@
 \end{enumerate}
-
-\todo{there are some comments on the google docs regarding this subsection that should be addressed(?)}
 
@@
 Given that financial statements are ultimately the responsibility of management and that senior management must certify the internal controls as part of the financial statement disclosures, managers have an incentive to implement a control environment that promotes a strong tone at the top, ethical conduct, and oversight of the financial reporting function.
+%TODO: could say something about/cite : blaze1998compliance
 
@@
 Internally, it must ensure proper controls over the signing keys these DAO tokens are assigned to.
-External to the firm, the DAO application maintaining these tokens on Ethereum{'}s blockchain must itself be secure (which in the case of the DAO, it was not).
-Auditing internal procedures over cryptographic keys is not unprecedented---maintaining certificate authority keys is critical to some security firm{'}s financial prospects (a security breach at one firm, \textit{DigiNotar}, bankrupted it~\cite{zetter2011diginotar}).
+External to the firm, the DAO application maintaining these tokens on Ethereum{'}s blockchain must itself be secure (which in the case of the DAO, it was not~\cite{dupont2017experiments}).
+Auditing internal procedures over cryptographic keys is not unprecedented---maintaining certificate authority keys is critical to some security firm{'}s financial prospects (a security breach at one firm, \textit{DigiNotar} led to its bankruptcy ~\cite{zetter2011diginotar}).
 Symantec{'}s self-custodianship over these keys involves elaborate security ceremonies whenever they are required \todo{[Cite]}.
@@
 For example, in August 2017, when a hard fork created Bitcoin Cash from Bitcoin, holders of Bitcoin had two types of assets on hand.
-Bitcoin Cash was not paid for but resulted from a split between the two currencies.
+Bitcoin Cash was not paid for but resulted from a split between the two cryptocurrencies.
 However, if existing accounting standards require the measurement of transactions at historical cost (what was paid for the assets), then recipients of Bitcoin Cash would report this new asset on their books at a value of \$0.
@@
 Therefore, auditors must address the issue of an accounting standard that does not contemplate how to measure the value of cryptoassets when considering whether the financial statements they are reporting on are accurate in all substantial respects.
-More commonly for ERC-20 tokens on Ethereum, the recipient of the tokens don{'}t have the option to reject the deposits nor would get notified of the new tokens received, which could result in issues with completeness.
+More commonly for ERC20 tokens on Ethereum, the recipient of the tokens don{'}t have the option to reject the deposits nor would get notified of the new tokens received, which could result in issues with completeness.
 
@@
 However, not all frauds that occur this space are new kinds of fraud.
-For instance, Ponzi schemes which have existed since they were perfected by Charles Ponzi in the early twentieth century~\cite{ponzi2001rise}.
+For instance, Ponzi schemes have existed since they were perfected by Charles Ponzi in the early twentieth century~\cite{ponzi2001rise}.
 In 2017, OneCoin was found to have raised over \$350M of funds from investors for an ICO that was a Ponzi scheme~\cite{atlanticCryptoPonzi2017}.
-Stories like this only reinforce the perception in the auditing community of the dangers of operating in this space.
+Stories like this~\cite{vasek2015analyzing} only reinforce the perception in the auditing community of the dangers of operating in this space.
 However, auditors can protect themselves by ensuring that they only work with reputable clients.

### 2018-09-25 frontrunning/Latex/main.tex
[frontrunning] Preliminary- What is frontrunning + related docs
[frontrunning] minor changes and some notes
[frontrunning] Abstract and minor changes
Some edits
Moving to ICO (everything in blue needs more explanation)

@@
 \documentclass[envcountsect]{llncs}
-\sloppy
 \pagestyle{headings} 
@@
 \input{setup/macros}
-\input{setup/table}
 
@@
 
-\title{\Large \bf Frontrunning}
-%\author{}
-
-%\author{}
-\institute{Concordia University}
-
+\title{The paper on blockchain front-running}
+\author{}
+\institute{}
 \maketitle
@@
 
+\clearpage
 \bibliography{bib/Frontrunning_Ref}
@@
 
-\clearpage
 \appendix
 
+\section{CryptoKitty} \label{app:cryptokitty}
+
+%Possibly remove this figure due to page limit
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.3\linewidth]{figures/cryptokittie842912.png}
+\caption{ Cryptokitty Number 842912 \label{fig:cryptokittie}}
+\end{figure}
+
+Figure~\ref{fig:cryptokittie} shows an example of a Cryptokitty.
+
+\section{LocalEthereum} \label{app:code}
+
+%Possibly remove this code snippet due to page limit . don't forget to remove the refrence to it ^
+\begin{lstlisting}[basicstyle=\scriptsize\ttfamily,caption={Code snippet from LocalEthereum smart contract.
+Values V,R and S are set by LocalEtherem to have a valid signature, also the tradeHash uses buyer and seller addresses, mitigating the possibility of front-running by a third party.},label={code:localethereum},float]
+    function createEscrow(bytes16 _tradeID, address _seller, address _buyer, uint256 _value, uint16 _fee,
+					uint32 _paymentWindowInSeconds, uint32 _expiry, uint8 _v, bytes32 _r, bytes32 _s) 
+        payable external {
+        bytes32 _tradeHash = keccak256(abi.encodePacked(_tradeID, _seller, _buyer, _value, _fee));
+	...
+        // A signature (v, r and s) must come from localethereum to open an escrow
+        bytes32 _invitationHash = keccak256(abi.encodePacked(
+            _tradeHash,
+            _paymentWindowInSeconds,
+            _expiry
+        )); 
+\end{lstlisting}
+
+Code~\ref{code:localethereum} shows a mitigation technique employed by LocalEthereum.
+
+\section{Traditional Front-running Prevention Methods}
+
+There are debates in traditional markets regarding the fact that front-running is considered to be a form of insider trading which deemed to be illegal.
+Traditional methods to prevent front-running mainly involves after the fact investigation and legal action against the front-runners~\cite{LexisNexisLawSuit}.
+As mentioned in section~\ref{traditionalFrontrunning}, defining front-running and educating the employees were the first step taken to prevent such issues in traditional markets, however, front-running became less likely to happen mainly because of the high fine and lawsuits against firms who behaved in an unethical way.
+Other methods such as dark pools~\cite{zhu2014dark, buti2011diving} and sealed bids~\cite{radner1989sealed} were discussed and implemented in a variety of regulated trading systems.
+The traditional methods to prevent front-running does not apply to blockchain applications, as mainly they are based on central enforcement and limitations, also in case of blockchains the actors who are front-running could be anonymous and the fear of lawsuits would not apply.
+
+\section{Commit-and-Reveal}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.5\linewidth]{figures/commit-reveal.png}
+\caption{\scriptsize Commit and Reveal.
+User sends a commitment transaction with the hash of the data, After the commitment period is over, user sends her reveal transaction to the DApp revealing the information that matches the commitment.
+\label{fig:commitReveal}}
+\end{figure}
+%https://www.lucidchart.com/invitations/accept/3cd4c865-83d4-4c71-9a4a-f2e870f2db2c
+
+Figure~\ref{fig:commitReveal} illustrates the commit/reveal approach.
+
 \end{document}

### 2018-09-25 frontrunning/Latex/sections/paper.tex

@@
 In particular, ideal functionalities of blockchains (such as those used in simulation-based proofs) need to capture this adversarial capability, assuming the real blockchain does not address front-running.
-\textblue{Literature like the Bitcoin Backbone~\cite{} and Hawk~\cite{} capture this.}
+See \eg \textblue{the Bitcoin Backbone~\cite{}} and Hawk~\cite{kosba2016hawk}.
 
@@
 
-%______________________________________________________________%
-
 % = = = = = = = = = = = = = = = = = = = = = = = = = = %
@@
 
-%In the traditional markets, front-running is considered unethical and illegal.
-In the blockchain space, the designers of the decentral applications cannot rely on the justice system for preventing unethical behavior, and they must assume that each participant in the network acts rationally in their own self-interest, the application will be operating in an adversarial environment.
+% = = =
 
-%A few decentral exchange projects such as \textit{EtherDelta} and \textit{0xProject}~\cite{warren20170x}, have proposed solutions for front-running, which is off-chain order books.
-The methods discussed within these projects prevent blockchain network participants from front-running the orders as the orders are private and not known to the network and will not be broadcasted.
-However they are introducing third parties, \eg relayers in 0xproject, to be managing the orders with the promise not to reorder or front-run other orders.
+\subsection{Front-Running Resistant Blockchains}
+There are technical difficulties to achieve such solutions as there are unknown factors within such network designs and requires testing every corner and edge case scenarios.
+In this section, we describe the potential solutions using which, one can design and implement a decentralized application that is resistant to front-running.
 
-%______________________________________________________________%
-\subsection{Front-run Resistant Blockchain}
-There are technical difficulties to achieve such solutions as there are unknown factors within such network designs and requires testing every corner and edge case scenarios.
-In this section, we describe the potential solutions using which, one can design and implement a decentral application that is resistant to front-running.
+\paragraph{Design Decision \#1: Fixed Transaction Ordering.} da Silva~\etal~\cite{fixedordering2018silva} proposes an algorithm, known as Fixed Transaction Ordering and Admission (FTOA) algorithm, in the consensus protocol that enforces the order of the transactions in the mined blocks to eliminate transaction reordering by miners.
+\textblue{How exactly does this fix front-running?}
 
-\subsubsection{Design Decision \#1: Fixed Transaction Ordering\newline}
-One possible solution to fix current blockchains in regards to transaction reordering by miners has been proposed by da Silva~\etal~\cite{fixedordering2018silva}.
-This solution consists of an algorithm, known as Fixed Transaction Ordering and Admission (FTOA) algorithm, in the consensus protocol that enforces the order of the transactions in the mined blocks.
-
-\subsubsection{Design Decision \#2:Privacy-Preserving Blockchain\newline}
-Market participants are concerned about revealing information on their past trades, purchases, income, or liquidity needs.
+\paragraph{Design Decision \#2:Privacy-Preserving Blockchains.} %Market participants are concerned about revealing information on their past trades, purchases, income, or liquidity needs.
 Privacy is a basic human right, that being said, there are limitations to the functionality of a system designed to preserve full privacy.
 However other than past transactions, real-time transactions would leak information about the sender or the intention of the order that could lead to front-running attacks.
-Privacy-preserving blockchains try to solve the initial issue by keeping all the details of the transactions private (in some extent~\cite{miller2017empirical, kappos2018empirical}).
+Privacy-preserving blockchains strive (to some extent~\cite{miller2017empirical, kappos2018empirical}) to keep all details of transactions private, including participants and amounts.
 As an example, ZCash~\cite{hopwood2016zcash}, uses two distinct type of addresses, transparent addresses and shielded addresses.
 Transparent addresses work similar to Bitcoin transactions, fully transparent about the sender and receiver addresses, the amount and included data.
-However shielded addresses are private and do not leak any information, this is great for privacy but not good for smart contracts capabilities.
-Smart contract functionality requires verification by the miners which require to know the input, functionality, and output of smart contracts to be able to determine if the transaction is valid.
-Albeit by using cryptographic primitives such as zero-knowledge proofs this issue could also be resolved~\cite{kosba2016hawk}.
-
-\subsubsection{Design Decision \#3: Dual Authoring\newline} Loopring is an open protocol proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}.
-This protocol operates a hybrid model with off-chain order management and communication while only the order matching takes place on the chain.
-In this protocol, the orders are grouped in \emph{ring orders} immediately after they are sent by the users.
-Next, the required signatures are provided by a miner and owner of the order, see Figure~\ref{fig:vulnerable_loopring}.
-Eventually, the ring miner sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement.
-While the \emph{submitRing transaction} sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with his address instead of the ring miner's address and then sign the hash of the ring using his own private key.
-By paying a higher gasPrice, block miners choose the front-runner's transaction instead of the original \emph{submitRing transaction}.
-To solve this issue, the new version of Loopring protocol uses the \emph{dual-authoring} scheme.
-This solution sets two levels of authorization for orders - one for settlement, and one for order matching.
-As it can be seen in Figure~\ref{fig:not_vulnerable_loopring}, each owner of an order generates a pair of public key (auth-address) and private key (auth-key), which are different from his address and its corresponding private key.
-These auth-keys are used to sign the hash of the ring and will further prevent anyone from regenerating the same \emph{submitRing transaction}.
-The reason is that the auth-keys are only known to the miner of the ring as they are not part of the on-chain transaction.
-Doing so, it is assured that (i) the orders are not modified (because they are signed by the owner), (ii) no other miner can mine the ring (because the miner's address is signed by the initial miner), and no user can front-run the \emph{submitRing transaction} (because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them).
+However shielded addresses are private and do not leak any of this information.
+While this works for simple transactions, building similar shields for DApps is subject to on-going research~\cite{kosba2016hawk}.
+\textblue{How exactly does this fix front-running?}
 
@@
 %https://www.lucidchart.com/invitations/accept/8dee869c-482c-433f-a901-8d041a1dc526
-%______________________________________________________________%
+
+\paragraph{Design Decision \#3: Dual Authoring.} Loopring is an open protocol proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}.
+This protocol operates a hybrid model with off-chain order management and communication while only the order matching takes place on the chain.
+In this protocol, the orders are grouped in \emph{ring orders} immediately after they are sent by the users.
+Next, the required signatures are provided by a miner and owner of the order, see Figure~\ref{fig:vulnerable_loopring}.
+Eventually, the ring miner sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement.
+While the \emph{submitRing transaction} sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with his address instead of the ring miner's address and then sign the hash of the ring using his own private key.
+By paying a higher gasPrice, block miners choose the front-runner's transaction instead of the original \emph{submitRing transaction}.
+To solve this issue, the new version of Loopring protocol uses the \emph{dual-authoring} scheme.
+This solution sets two levels of authorization for orders - one for settlement, and one for order matching.
+As it can be seen in Figure~\ref{fig:not_vulnerable_loopring}, each owner of an order generates a pair of public key (auth-address) and private key (auth-key), which are different from his address and its corresponding private key.
+These auth-keys are used to sign the hash of the ring and will further prevent anyone from regenerating the same \emph{submitRing transaction}.
+The reason is that the auth-keys are only known to the miner of the ring as they are not part of the on-chain transaction.
+Doing so, it is assured that (i) the orders are not modified because they are signed by the owner, (ii) no other miner can mine the ring because the miner's address is signed by the initial miner, and (iii) no user can front-run the \emph{submitRing transaction} because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them.
+
+% = = =
+
 \subsection{Application Design to Prevent Front-running}
 
-Another method to prevent front-running activities is to design the applications in such a way that there is no information leakage to the malicious parties to enable them to front-run other users.
-Followings discuss a few techniques which can be used by the DApp developers while designing the systems to mitigate front-running issues.
+Front-running can be tackled at the blockchain layer, as seen in the previous section, or mitigations can be build at the DApp level as seen here.
 
-\subsubsection{Design Decision \#1: Commitment Scheme\newline} \label{CommitmentScheme}
-The commitment scheme is a cryptographic primitive that enables one to commit to a value --binding-- (\eg statement, document, data, \etc) while keeping it a secret and reveal the committed value on a later time~\cite{brassard1988minimum}.
+\paragraph{Design Decision \#1: Commit / Reveal.} \label{CommitmentScheme}
+A commitment scheme is a cryptographic primitive that enables one to commit to a value (\eg a statement, document, data, \etc) while keeping it a secret and open it (and only it) at a later time of the commiter's choosing~\cite{brassard1988minimum}.
 The commitment scheme is a robust method to prevent information leakage from the sensitive transactions.
 This could be done by simply submitting the hash value of the committed data to a smart contract and later on revealing the values linked to the committed hash, see Figure~\ref{fig:commitReveal}.
-In the case of decentral exchanges, the user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, the user sends reveal transaction revealing the order details which will be executed in a fair order.
+In the case of decentralized exchanges, the user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, the user sends reveal transaction revealing the order details which will be executed in a fair order.
 This method is not perfect, depending on the DApp design, either the order is collateralized, that means the commitment transaction includes the funds required for fulfilling the order, which will leak some information about the order, or is not collateralized and opens up the possibility of user never revealing the commitment, which will be vulnerable to Denial-of-Service attacks.
@@
 In the ENS commit-reveal process, if one forgets to reveal in the reveal phase, the committed funds are burnt and inaccessible thereafter.
-Also, this scheme means two transactions are required for a functionality which makes it more expensive to run.
-
-\textblue{Cite Princeton paper on Namecoin for frontrunning mitigation using commit/reveal.}
-
-\subsubsection{Design Decision \#2: Submarine Commitments\newline}\label{submarineCommits}
-Submarine Commitments~\cite{breidenbach2018enter, submarinesendHD} are similar to the commitment schemes with some key differences such as hiding participatory factor and being fully collateralized.
-With submarine send, it is possible to hide sender, receiver, value, and data, the commitment transaction is identical to a transaction to a newly generated address.
-Submarine sends could be a solution for sealed-bid auctions on the blockchain to hide the existence of the bids for other participants.
-
-The details of how Submarine commitments work is outside the scope of this paper, however in short, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality it is possible to generate one outgoing transaction from an address of which no private key exists.
-By constructing a transaction from that address to the DApp and funding that address we fulfill the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}, see Figure~\ref{fig:LibSubmarine}.
-However, this could be designed in other ways to suit the need of the DApp.
-Drawbacks of this scheme are similar to ~\ref{CommitmentScheme}, with an addition of two more transactions to finalize the functionality, which results in more cost and complicated user experience.
+Also, this scheme means two transactions are required for a functionality which makes it more expensive.
 
@@
 
-\subsubsection{Design Decision \#3: Logic Specific Solutions\newline}
+\paragraph{Design Decision \#2: Submarine Commitments.}\label{submarineCommits}
+Submarine Commitments~\cite{breidenbach2018enter, submarinesendHD} are similar to the commitment schemes with some key differences such as hiding participatory factor and being fully collateralized.
+With submarine send, it is possible to hide sender, receiver, value, and data, the commitment transaction is identical to a transaction to a newly generated address.
+Submarine sends could be a solution for sealed-bid auctions on the blockchain to hide the existence of the bids for other participants.
+
+The details of how Submarine commitments work is outside the scope of this paper, however in short, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality it is possible to generate one outgoing transaction from an address of which no private key exists.
+By constructing a transaction from that address to the DApp and funding that address we fulfill the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}, see Figure~\ref{fig:LibSubmarine}.
+However, this could be designed in other ways to suit the need of the DApp.
+Drawbacks of this scheme are similar to ~\ref{CommitmentScheme}, with an addition of two more transactions to finalize the functionality, which results in more cost and complicated user experience.
+
+\paragraph{Design Decision \#3: Use-Case Specific Solutions.}
 There is no perfect generic solution to this issue as of now, however, to prevent front-running, one can design the application in a way that it is not possible to be front-run:
 
-\noindent\emph{Eliminating Time-Order Dependency:} The applications can be designed not to rely on the time for the orders to be executed.
-For example when designing a decentral exchange, one can use \emph{the call market} design instead of a time-sensitive order book.
+\begin{compactlist}
+
+\item \emph{Eliminating Time-Order Dependency:} The applications can be designed not to rely on the time for the orders to be executed.
+For example when designing a decentralized exchange, one can use \emph{the call market} design instead of a time-sensitive order book.
 In a call market design, the arrival time of the orders does not matter as they are executed in batches~\cite{clark2014decentralizing}.
 
-\noindent\emph{Disincentivizing Front-running Actors:} This solution, which is economic rather than technical, is to disincentives the miners by paying them the fees.
+\item \emph{Disincentivizing Front-running Actors:} This solution, which is economic rather than technical, is to disincentives the miners by paying them the fees.
 If the application is designed in a way that the fees of the orders are sent to the miner of the block, he would have less incentive to front-run the orders as he already gains enough financial benefit from acting fairly and executing the transactions on their correct order.
-For example, Malinova~\cite{malinova2017market} proposes a design for a decentral exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable.
+For example, Malinova~\cite{malinova2017market} proposes a design for a decentralized exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable.
+
+ \end{compactlist}
 
@@
 As an example, LocalEthereum, an escrow-based exchange, uses challenge random values from the website to be included in the signature of the transaction (See Code ~\ref{code:localethereum} in Appendix~\ref{app:code}), hence removing any possibility of replay attack or the possibility of any other address sending the similar order.
+\textblue{is this not its own entry?}
 
@@
 
-%______________________________________________________________%
-%\section{Concluding Remarks}
+% = = = = = = = = = = = = = = = = = = = = = = = = = = %
+% = = = Conc
+% = = = = = = = = = = = = = = = = = = = = = = = = = = %
+
+\section{Concluding Remarks}
+
+Front-running is a pervasive issue in Ethereum DApps.
+While some DApp-level application logic could be built to mitigate these attacks, its ubiquity across different DApp categories suggests mitigations at the blockchain-level would perhaps be more effective.
+We highlight this as an important research area.
 

### 2018-09-25 frontrunning/Latex/setup/table.tex

@@
+% !TEX root = ../main.tex
+
 % ------------------------------------------------------------------------------------------------------------------------------------------------%
@@
 \centering
+\scriptsize
 \begin{tabular}{|c|l|}
+
 \hline
@@
 \multirow{6}{*}{Exchanges} 										& IDEX (1) \\ 
-															& \textit{ForkDelta, EtherDelta} (2) \\
-															& \textit{Bancor} (7) \\
+															& \textbf{ForkDelta, EtherDelta} (2) \\
+															& \textbf{Bancor} (7) \\
 															& The Token Store (13) \\
 															& LocalEthereum (14) \\
-															& \textit{0x Protocol} (23) \\
-															& Kyber (22) \\  \hline
+															& Kyber (22) \\ 
+															& \textbf{0x Protocol} (23) \\ \hline
 
-\multirow{9}{*}{\shortstack{Crypto-Collectible \\ Games \\ (ERC 721)}}		& \textit{CryptoKitties} (3) \\  
+\multirow{9}{*}{\shortstack{Crypto-Collectible \\ Games \\ (ERC 721)}}		& \textbf{CryptoKitties} (3) \\  
 															& Ethermon (4)\\
@@
 
-\multirow{8}{*}{Gambling}											& \textit{Fomo3D} (5) \\  
-															& DailyDivs (6) \\ 
+\multirow{8}{*}{Gambling}											& \textbf{Fomo3D} (5) \\  
+															& DailyDivs (6) \\																								& PoWH 3D (8)	 \\ 
 															& FomoWar (10) \\
@@
 															& dice2.win (20) \\ 
-															& PoWH 3D (8)	 \\ 
 															& Ether Shrimp Farm (21) \\  \hline
 
-\multirow{1}{*}{Name Services}									& \textit{Ethereum Name Service} (24)  \\  \hline
+\multirow{1}{*}{Name Services}									& \textbf{Ethereum Name Service} (24)  \\  \hline
 
 \end{tabular}
-\caption{\footnotesize{Top 25 DApps based on recent user activity from \texttt{DAppRadar.com} on September 4th, 2018. We discuss the DAps that are in italics.}\label{tab:top25DApps}}
+\caption{\footnotesize{Top 25 DApps based on recent user activity from \texttt{DAppRadar.com} on September 4th, 2018. We discuss the DApps that are in bold.}\label{tab:top25DApps}}
 \end{table}

### 2018-09-25 frontrunning/Latex/sections/paper.tex
Ok on pause for now

@@
 
-Front-running can be tackled at the blockchain layer, as seen in the previous section, or mitigations can be build at the DApp level as seen here.
+Front-running can be tackled at the blockchain layer, as seen in the previous section, or mitigations can be built at the DApp level as seen here.
 
 \paragraph{Design Decision \#1: Commit / Reveal.} \label{CommitmentScheme}
-A commitment scheme is a cryptographic primitive that enables one to commit to a value (\eg a statement, document, data, \etc) while keeping it a secret and open it (and only it) at a later time of the commiter's choosing~\cite{brassard1988minimum}.
-The commitment scheme is a robust method to prevent information leakage from the sensitive transactions.
-This could be done by simply submitting the hash value of the committed data to a smart contract and later on revealing the values linked to the committed hash, see Figure~\ref{fig:commitReveal}.
-In the case of decentralized exchanges, the user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, the user sends reveal transaction revealing the order details which will be executed in a fair order.
-This method is not perfect, depending on the DApp design, either the order is collateralized, that means the commitment transaction includes the funds required for fulfilling the order, which will leak some information about the order, or is not collateralized and opens up the possibility of user never revealing the commitment, which will be vulnerable to Denial-of-Service attacks.
-Another use of such a commitment scheme is in decentralized naming systems, such as Namecoin, Ethereum Name Service (ENS).
-In this case, a user sends a commit transaction, which commits to the name hash, similar to a sealed bid.
+A commitment scheme is a cryptographic primitive that enables one to commit to a value (\eg a statement, document, data, \etc) while keeping it a secret, and then open it (and only it) at a later time of the committer's choosing~\cite{brassard1988minimum}.
+A common approach is to submit the hash value of the data to be committed, potentially with a random nonce (for predictable data), to a smart contract and later reveal the original data and nonce which can be verified to hash to the commitment.
+See Figure~\ref{fig:commitReveal} in Appendix~\ref{app:cr}.
+
+An early use of commit/reveal is Namecoin, a Bitcoin-forked blockchain for name services~\cite{kalodner2015empirical}.
+A user sends a commit transaction, which commits to the name hash, similar to a sealed bid.
 Once the transaction is confirmed and the grace period is over, the user sends a reveal transaction revealing the bid and also the details of the requested domain~\cite{kalodner2015empirical}.
 Using this scheme, one is able to hide information from the adversarial parties in the system and prevent them from front-running.
-A similar approach applies to on-chain voting as well ~\cite{adChainPLCRVoting}, using sealed votes, voters can make sure their votes are hidden until a later date, however, their participation and weight of the vote are publicly known.
+
+In the case of decentralized exchanges, users can use commit/reveal for bids, where commitments are placed in an ordered queue and executed in a later round after a reveal.
+This mitigation seems to require further research.
+One trader strategy is to flood orders at the commitment stage, but then only selectively and adaptively choose which to reveal.
+Collateralization is another challenge, where revealed bids may simply be intentions to execute but additional transactions are required to move the money or tokens; a transaction that can also be aborted early.
+One mitigation to early aborts is having users post a fidelity bond that can be automatically dispensed if they fail to fully execute committed transactions (as used in~\cite{} \textblue{Cite paddy's paper on boardroom voting on ethereum}).
+Commit/reveal is also seen in on-chain voting~\cite{adChainPLCRVoting}.
+Using sealed votes, voters can make sure their votes are hidden until a later date, however, their participation and weight of the vote are publicly known.
+
 Other than the collateralization issue for the commit and reveal scheme, another obvious issue is the participatory factor.
@@
 \paragraph{Design Decision \#2: Submarine Commitments.}\label{submarineCommits}
-Submarine Commitments~\cite{breidenbach2018enter, submarinesendHD} are similar to the commitment schemes with some key differences such as hiding participatory factor and being fully collateralized.
+Submarine Commitments~\cite{breidenbach2018enter, submarinesendHD} extend basic commit/reveal functionality with additional properties.
+In particular, they hide the DApp being invoked during the commit phase and also ensure that revealed transactions that send funds are fully collateralized.
 With submarine send, it is possible to hide sender, receiver, value, and data, the commitment transaction is identical to a transaction to a newly generated address.
 Submarine sends could be a solution for sealed-bid auctions on the blockchain to hide the existence of the bids for other participants.
-
-The details of how Submarine commitments work is outside the scope of this paper, however in short, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality it is possible to generate one outgoing transaction from an address of which no private key exists.
-By constructing a transaction from that address to the DApp and funding that address we fulfill the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}, see Figure~\ref{fig:LibSubmarine}.
+The details of how Submarine commitments work could fill an entire paper, however in short, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality, it is possible to generate one outgoing transaction from an address of which no private key exists.
+By constructing a transaction from that address to the DApp and funding that address we fulfill the commitment phase.
+By revealing the details and broadcasting the constructed transaction we reveal the commitment~\cite{libsubmarine}.
+See Figure~\ref{fig:LibSubmarine}.
 However, this could be designed in other ways to suit the need of the DApp.
-Drawbacks of this scheme are similar to ~\ref{CommitmentScheme}, with an addition of two more transactions to finalize the functionality, which results in more cost and complicated user experience.
+Drawbacks of this scheme are similar to commit/reveal, with the addition of two more transactions to finalize a transaction, which adds cost and complexity to the user experience.
 
@@
 \item \emph{Eliminating Time-Order Dependency:} The applications can be designed not to rely on the time for the orders to be executed.
-For example when designing a decentralized exchange, one can use \emph{the call market} design instead of a time-sensitive order book.
-In a call market design, the arrival time of the orders does not matter as they are executed in batches~\cite{clark2014decentralizing}.
+For example when designing a decentralized exchange, one can use a \emph{the call market} design instead of a time-sensitive order book~\cite{clark2014decentralizing} to side-step and disincentivize front-running by miners.
+In a call market design, the arrival time of orders do not matter as they are executed in batches.
 
-\item \emph{Disincentivizing Front-running Actors:} This solution, which is economic rather than technical, is to disincentives the miners by paying them the fees.
-If the application is designed in a way that the fees of the orders are sent to the miner of the block, he would have less incentive to front-run the orders as he already gains enough financial benefit from acting fairly and executing the transactions on their correct order.
-For example, Malinova~\cite{malinova2017market} proposes a design for a decentralized exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable.
+\item \emph{Disincentivizing Front-running Actors:} The call market solution also pivots profitable gains that front-running miners stand to gain into fees that they collect~\cite{clark2014decentralizing}, removing the financial incentive to front-run.
+To the same end, Malinova~\cite{malinova2017market} propose a design for a decentralized exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable.
+\textblue{this is what it does, how does it do it?}
+
+\item \emph{\textblue{Technique}:} LocalEthereum, an escrow-based exchange, uses challenge random values from the website to be included in the signature of the transaction (See Code ~\ref{code:localethereum} in Appendix~\ref{app:code}), hence removing any possibility of replay attack or the possibility of any other address modifying key information in the order.
+\textblue{how does this solve front-running?}
 
@@
 Although there are other concerns about this specific design but not for front-running.
-
-Going back to Table~\ref{tab:top25DApps}, some DApps facilitate different methods to mitigate front-running issues.
-As an example, LocalEthereum, an escrow-based exchange, uses challenge random values from the website to be included in the signature of the transaction (See Code ~\ref{code:localethereum} in Appendix~\ref{app:code}), hence removing any possibility of replay attack or the possibility of any other address sending the similar order.
-\textblue{is this not its own entry?}
 

### 2018-09-25 frontrunning/Latex/main.tex
Ok on pause for now
[frontrunning] fix appendix figure placements

@@
 %Possibly remove this figure due to page limit
-\begin{figure}[t]
+\begin{figure}[!htb]
 \centering
@@
 \begin{lstlisting}[basicstyle=\scriptsize\ttfamily,caption={Code snippet from LocalEthereum smart contract.
-Values V,R and S are set by LocalEtherem to have a valid signature, also the tradeHash uses buyer and seller addresses, mitigating the possibility of front-running by a third party.},label={code:localethereum},float]
+Values V,R and S are set by LocalEtherem to have a valid signature, also the tradeHash uses buyer and seller addresses, mitigating the possibility of front-running by a third party.},label={code:localethereum}]
     function createEscrow(bytes16 _tradeID, address _seller, address _buyer, uint256 _value, uint16 _fee,
@@
 
-Code~\ref{code:localethereum} shows a mitigation technique employed by LocalEthereum.
+Code~\ref{code:localethereum} shows a mitigation technique employed by LocalEthereum. \\
 
@@
 
-\section{Commit-and-Reveal}
+\section{Commit-and-Reveal} \label{app:cr}
 
-\begin{figure}[t]
+\begin{figure}[!htb]
 \centering

### 2018-09-25 frontrunning/Latex/sections/paper.tex
[frontrunning] last comments

@@
 
+%maybe move this to appendix
 \subsection{Literature on Traditional Front-running}\label{traditionalFrontrunning}
@@
 
+%make them more pointy, shorten it. mainly the first paragraph
 Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to market information leakage~\cite{aune2017footprints}.They also propose a cryptographic approach, similar to commit and reveal (see Section~\ref{CommitmentScheme}) to prevent front-running.
@@
 In particular, ideal functionalities of blockchains (such as those used in simulation-based proofs) need to capture this adversarial capability, assuming the real blockchain does not address front-running.
-See \eg \textblue{the Bitcoin Backbone~\cite{}} and Hawk~\cite{kosba2016hawk}.
+See \eg \textblue{the Bitcoin Backbone~\cite{garay2015bitcoin}} and Hawk~\cite{kosba2016hawk}.
 
@@
 The first category of DApp in Table~\ref{tab:top25DApps} is exchanges.
-Exchanges such as EtherDelta\footnote{Also known as ForkDelta for the UI \url{https://forkdelta.app/}}, purport to implement a decentralized exchange, however their order books are stored on a central server they control and shown on their users with a website interface.
+Exchanges such as EtherDelta\footnote{Also known as ForkDelta for the UI \url{https://forkdelta.app/}}, purport to implement a decentralized exchange, however their order books are stored on a central server they control and shown to their users with a website interface.
 Central exchanges can front-run orders in the traditional sense, as well as re-order or block orders on their servers.
-0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the order book holders \textblue{and are not prone to cheating.} One main issue with the relay design is \textit{cancellation grief}.
-To \textblue{prevent denial of service attacks}, the user needs to send a transaction to cancel her order.
-In this case, an adversarial actor many see a pending  cancellation transaction, and send  a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled.
+0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the order book holders and could front-run the orders they relay.
+One method of price manipulation on such markets is to flood the market with orders and cancel them when there are filling orders --taker's griefing--, to prevent such attacks, the user needs to send a transaction to cancel each order.
+In this case, when an adversarial actor sees a pending  cancellation transaction, he sends a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled, this is known as \textit{cancellation grief}.
 This is illustrated in Figure~\ref{fig:MinerFrontrunning}.
@@
 
+%similar to market, ens cause they are auctions. generalizing to auction front-running. auction-front-running
+%exapand the front-running attack...
+
+% refer from ens stuff back here
+
 % The blue above needs expansion with further details.
@@
 Many speculated such a game would never end but on August 22, 2018, the first round of the game ended with the winner collecting 10,469 Ether\footnote{The first winner of Fomo3D, won 10,469 Ether \url{ https://etherscan.io/tx/0xe08a519c03cb0aed0e04b33104112d65fa1d3a48cd3aeab65f047b2abce9d508}} equivalent to \$2.1M USD at the time.
-Blockchain forensics indicate a sophisticated winning strategy to frontrun new ticket purchases~\cite{fomo3dhacker} that would reset the counter.
+Blockchain forensics indicate a sophisticated winning strategy to front-run new ticket purchases~\cite{fomo3dhacker} that would reset the counter.
 The winner appears to have started by deploying some high gas consumption DApps unrelated to the game.
@@
 By doing so the front-runner invalidates the original bid and hence registers the domain name himself.}
+
+%too dense. need more explanation. --> explain what sealed auction is? whatsealed mean, refer to cryptokitties. what is actually bein auctions who deposits and what.  how ens actually works . 
+% two ways to add bid to an auction, start an auction and bid. but otehr method is that. whta sealed mean, domain is sealed but not anything else.  ENS auction details and then say . 
+%same price the first transaction would win, front-running. 
+%explain more on ENS auction
 
@@
 \textblue{How exactly does this fix front-running?}
+%why this solves or makes it harder to front-run. to front run you need to know what values are there but if it is dark it's harder
 
@@
 
+%The first solution was to prevent front-running, but then it was attacked so they updated the solution. this new solution also could be attacked. 
 \paragraph{Design Decision \#3: Dual Authoring.} Loopring is an open protocol proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}.
@@
 \textblue{this is what it does, how does it do it?}
+% make it more obvious how they do this. how they changed it
 
+%find a home for localethereum. explain the scenario where this actually works, how it can be front-run in original scenario, how this prevents front-running.
 \item \emph{\textblue{Technique}:} LocalEthereum, an escrow-based exchange, uses challenge random values from the website to be included in the signature of the transaction (See Code ~\ref{code:localethereum} in Appendix~\ref{app:code}), hence removing any possibility of replay attack or the possibility of any other address modifying key information in the order.

### 2018-09-25 frontrunning/Latex/sections/paper.tex
[frontrunning] edits on Loopring

@@
 %The first solution was to prevent front-running, but then it was attacked so they updated the solution. this new solution also could be attacked. 
-\paragraph{Design Decision \#3: Dual Authoring.} Loopring is an open protocol proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}.
-This protocol operates a hybrid model with off-chain order management and communication while only the order matching takes place on the chain.
+\paragraph{Design Decision \#3: Dual Authoring.} This scheme is proposed to solve the front-running issue within Loopring -- a decentralized exchange protocol proposed by Wang~\etal~\cite{wang2018loopring}.
+In this protocol, orders are grouped in \emph{ring orders} once they are sent by the users.
+After the required signatures are provided by the ring miner, he sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement (see Figure~\ref{fig:vulnerable_loopring}).
+While this transaction sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with his address instead of the ring miner's address.
+By paying a higher gasPrice, the front-runner's transaction is executed before the original \emph{submitRing transaction}.
+Using the dual authoring solution, it is infeasible to regenerate the \emph{submitRing transaction} as the users have to sign the orders using their private keys (auth-keys), which are only known to the ring miner and not any other user (see Figure~\ref{fig:not_vulnerable_loopring}).
+% Loopring protocol is proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}.
 In this protocol, the orders are grouped in \emph{ring orders} immediately after they are sent by the users.
@@
 By paying a higher gasPrice, block miners choose the front-runner's transaction instead of the original \emph{submitRing transaction}.
-To solve this issue, the new version of Loopring protocol uses the \emph{dual-authoring} scheme.
+%To solve this issue, the new version of Loopring protocol uses the \emph{dual-authoring} scheme.
 This solution sets two levels of authorization for orders - one for settlement, and one for order matching.

### 2018-09-25 frontrunning/Latex/sections/paper.tex
[frontrunning] Edits

@@
 
-The mechanics of frontrunning works on all DApps but front-running is not necessarily beneficial, depending on the DApp's internal logic and/or  as any mitigations it might implement.
+The mechanics of front-running works on all DApps but front-running is not necessarily beneficial, depending on the DApp's internal logic and/or  as any mitigations it might implement.
 Therefore DApps need to be studied individually or in categories.
@@
 We show empirical evidence of a miner purchasing tokens ahead of other users in Status.im.
-Finally, proposals to eliminate or mitigate frontrunning from DApps are scattered across forums, proposed standards (called EIPs in Ethereum) and academic papers; we systemize them the last section.
+Finally, proposals to eliminate or mitigate front-running from DApps are scattered across forums, proposed standards (called EIPs in Ethereum) and academic papers; we systemize them the last section.
 
@@
 
-Designing truly decentralized exchanges, where the orderbook is implemented directly on a public blockchain, is being pursued by a number of projects [\textblue{cite github page}].
+Designing truly decentralized exchanges, where the order book is implemented directly on a public blockchain, is being pursued by a number of projects [\textblue{cite github page}].
 These designs generally face the following attack (illustrated in Figure~\ref{fig:RegularFrontrunning}).
@@
 If the adversary has pre-existing offers likely to be reached by the market order, she could front-run a cancelation and a new offer at a higher price.
-A simpler attack would be to guage the demand for trades at a given price by the number of pending orders, and to front-run at the same price in hopes that the market demand is the result of accurate new market information.
+A simpler attack would be to gauge the demand for trades at a given price by the number of pending orders, and to front-run at the same price in hopes that the market demand is the result of accurate new market information.
 Miners are in the best position to conduct these attacks as they hold fine-grained control over the exact set of transactions that will execute and in what order and can mix in their own (late) transactions without broadcasting them.
@@
 Further study showed that some mining pools might have been manipulating the network for their own profit.
-In addition, there were many transactions sent with a higher gas price to front-run other transactions, however, these transactions were failing due to the restriction in the ICO smart contract to reject any transactions with higher than 50 \textit{GWei} gas price (another mitigation against frontrunning).
+In addition, there were many transactions sent with a higher gas price to front-run other transactions, however, these transactions were failing due to the restriction in the ICO smart contract to reject any transactions with higher than 50 \textit{GWei} gas price (another mitigation against front-running).
 
@@
 According to analysis we carried out, we discovered that the F2Pool---an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure~\ref{fig:mining_pool_ratio})---sent 100 Ether to 30 new Ethereum addresses before the Status.im ICO started.
-When the token sale opened, F2Pool contsructed 31 transactions to the ICO token sale smart contract from the addresses these new address, without broadcasting these transactions to the network.
+When the token sale opened, F2Pool constructed 31 transactions to the ICO token sale smart contract from the addresses these new address, without broadcasting these transactions to the network.
 They used their entire mining power to mine their own transactions and some other potentially failing high gas price transactions.
@@
 While the default client and online blockchain explorers offer some limited querying, in order to analyze this case, we built our own database.
-Specifically, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation\url{https://github.com/ethereum/go-ethereum}} for the full node, a python script for extracting, transforming and loading ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery.\footnote{\url{https://cloud.google.com/bigquery/}} Using this software stack, we were able to isolate transactions within the Status.im ICO sale.
+Specifically, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation\url{https://github.com/ethereum/go-ethereum}} for the full node, a python script for extracting, transforming and loading Ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery.\footnote{\url{https://cloud.google.com/bigquery/}} Using this software stack, we were able to isolate transactions within the Status.im ICO sale.
 We used data analysis tool \texttt{Tableau}.\footnote{\url{https://www.tableau.com/}} A copy of this dataset and the initial findings can be found in our Github repository.\footnote{\url{github.com/} Removed for anonymity.}
@@
 \caption{\scriptsize \emph{submitRing} Transaction in the new version of the Loopring protocol.
-Other users cannnot regenerate this transaction as they do not access auth-keys and hence are not able to create the signatures.
+Other users cannot regenerate this transaction as they do not access auth-keys and hence are not able to create the signatures.
 \label{fig:not_vulnerable_loopring}}
@@
 Collateralization is another challenge, where revealed bids may simply be intentions to execute but additional transactions are required to move the money or tokens; a transaction that can also be aborted early.
-One mitigation to early aborts is having users post a fidelity bond that can be automatically dispensed if they fail to fully execute committed transactions (as used in~\cite{} \textblue{Cite paddy's paper on boardroom voting on ethereum}).
+One mitigation to early aborts is having users post a fidelity bond that can be automatically dispensed if they fail to fully execute committed transactions (as used in~\cite{mccorry2017smart}).
 Commit/reveal is also seen in on-chain voting~\cite{adChainPLCRVoting}.

### 2018-09-25 frontrunning/Latex/sections/paper.tex
[frontrunning] some changes

--- 2018-09-25 frontrunning/Latex/sections/paper.tex
@@
 One method of price manipulation on such markets is to flood the market with orders and cancel them when there are filling orders --taker's griefing--, to prevent such attacks, the user needs to send a transaction to cancel each order.
-In this case, when an adversarial actor sees a pending  cancellation transaction, he sends a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled, this is known as \textit{cancellation grief}.
+The reason for canceling order could be the unprofitability of the order due to price change, In this case, when an adversarial actor sees a pending  cancellation transaction, he sends a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled, this is known as \textit{cancellation grief}.
 This is illustrated in Figure~\ref{fig:MinerFrontrunning}.
@@
 
-Designing truly decentralized exchanges, where the orderbook is implemented directly on a public blockchain, is being pursued by a number of projects [\textblue{cite github page}].
+Designing truly decentralized exchanges, where the orderbook is implemented directly on a public blockchain, is being pursued by a number of projects~\cite{inDEXgithub}.
 These designs generally face the following attack (illustrated in Figure~\ref{fig:RegularFrontrunning}).
@@
 Since Bancor handles all the trades and exchanges on the Ethereum blockchain (unlike other existing decentralized exchanges), these transactions are all visible to the public for some time before being included within a block.
-This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions \textblue{and gain favorable profits}~\cite{BancorIs7:online}.
+This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions, in which they can gain favorable profits by buying before the order and fill the original order with slightly higher price~\cite{BancorIs7:online}.
 Researchers have shown and implemented a proof of concept code to front-run Bancor as a regular non-miner user~\cite{NewTab13:online}.
@@
 It contains the cryptokittty's ID which can be found either on their website or on the ERC721 token smart contract.
-\textblue{This is similar to open auctions, bid value and the object bidding on is visible to the network and any user could be easily front-run by sending the same transaction with higher gasPrice to replace the initial bidder.}
+This is similar to open auctions and markets front-running, bid value and the object bidding on is visible to the network and any user could be easily front-run by sending the same transaction with higher gasPrice to replace the initial bidder.
+The front-runner can see there is an interest in an specific cryptokittie and by buying it and auctioning it at higher price can profit from the transaction.
+%we call this auction-frontrunning.
 % https://etherscan.io/tx/0x62a76b7e345e8abd463487d0348c118a9314b197024e090fee7b1fbce434da40
-
-%similar to market, ens cause they are auctions. generalizing to auction front-running. auction-front-running
-%exapand the front-running attack...
-
-% refer from ens stuff back here
 

### 2018-09-25 frontrunning/Latex/sections/paper.tex

--- 2018-09-25 frontrunning/Latex/sections/paper.tex
@@
 
-Designing truly decentralized exchanges, where the order book is implemented directly on a public blockchain, is being pursued by a number of projects [\textblue{cite github page}].
+Designing truly decentralized exchanges, where the order book is implemented directly on a public blockchain, is being pursued by a number of projects~\cite{inDEXgithub}.
 These designs generally face the following attack (illustrated in Figure~\ref{fig:RegularFrontrunning}).
@@
 If the adversary has pre-existing offers likely to be reached by the market order, she could front-run a cancelation and a new offer at a higher price.
-A simpler attack would be to gauge the demand for trades at a given price by the number of pending orders, and to front-run at the same price in hopes that the market demand is the result of accurate new market information.
+A simpler attack would be to guage the demand for trades at a given price by the number of pending orders, and to front-run at the same price in hopes that the market demand is the result of accurate new market information.
 Miners are in the best position to conduct these attacks as they hold fine-grained control over the exact set of transactions that will execute and in what order and can mix in their own (late) transactions without broadcasting them.

### 2018-09-25 frontrunning/Latex/sections/paper.tex
[frontrunning] fix loopring section

@@
 After the required signatures are provided by the ring miner, he sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement (see Figure~\ref{fig:vulnerable_loopring}).
-While this transaction sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with his address instead of the ring miner's address.
-By paying a higher gasPrice, the front-runner's transaction is executed before the original \emph{submitRing transaction}.
-Using the dual authoring solution, it is infeasible to regenerate the \emph{submitRing transaction} as the users have to sign the orders using their private keys (auth-keys), which are only known to the ring miner and not any other user (see Figure~\ref{fig:not_vulnerable_loopring}).
+While this transaction sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with higher gasPrice and his address instead of the ring miner's address.
+Using the proposed \textit{dual authoring} solution in the new version of Loopring, regeneration of the \emph{submitRing transaction} is challenging as the users have to sign the orders using their secondary private keys (auth-keys), which are only known to the ring miner and not other users (see Figure~\ref{fig:not_vulnerable_loopring}).
+
 % Loopring protocol is proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}.

### 2018-09-25 frontrunning/Latex/sections/paper.tex
[frontrunning] edits up to \subsection Front-Running Resistant Blockchains

@@
 The mechanics of front-running works on all DApps but front-running is not necessarily beneficial, depending on the DApp's internal logic and/or as any mitigations it might implement.
-Therefore DApps need to be studied individually or in categories.
-This paper is a series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps) from each category of the top 25 most active.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} We do case studies on decentralized exchanges (\eg Bancor), crypto-collectables (\eg CryptoKitties), gambling services (\eg Fomo3D), and decentralized name services (\eg Ethereum Name Service).
+Therefore, DApps need to be studied individually or in categories.
+This paper is a series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps) from each category of the top 25 most active.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} We do case studies on decentralized exchanges (\eg Bancor), crypto-collectibles (\eg CryptoKitties), gambling services (\eg Fomo3D), and decentralized name services (\eg Ethereum Name Service).
 We also study initial coin offerings (ICOs), which by happenstance, did not appear in the top 25 on our sample day.
@@
 Cases of front-running are sometimes difficult to distinguish from related concepts like insider trading and arbitrage.
-In front-running, a person sees a concrete transaction that is set to execute and reacts to it before it actually executes.
+In front-running, a person sees a concrete transaction that is set to execute and reacts to it before it actually gets executed.
 If the person instead has access to more general privileged information that might predict future transactions, but is not reacting at the actual pending trades, we would classify this activity as insider trading.
@@
 However, blockchains also introduce new participants in the relaying and finalization (\ie mining) of transactions that can act as front-runners.
-Any user monitoring blockchain network transactions (\eg running a full node) can see a unconfirmed transactions and broadcast a reactionary transaction that might be confirmed ahead of the original transaction ...
-
- that is well-connected front-run other transactions in the network.
+Any user monitoring blockchain network transactions (\eg running a full node) can see a unconfirmed transactions and broadcast a reactionary transaction that might be confirmed ahead of the original transaction.
 For regular users to front-run others on the blockchain, they need to be well connected to other nodes on the network.
@@
 
-To find example DApps to study, we use the top 25 DApps based on recent user activity from \texttt{DAppradar.com} and sampled it in in the first week of September 2018.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} User activity is admittedly an imperfect metric for finding the `most significant' DApps: significant DApps might be lower volume overall or for extended periods of time (\eg ICOs, which we remedy by studying independently in Section~\ref{sec:ICOsfrontrunning}).
-However user activity is arguably the best objective criteria for which data is readily available, the list captures our intuition about which DApps are significant, and it is at least better than an ad hoc approach.
+To find example DApps to study, we use the top 25 DApps based on recent user activity from \texttt{DAppradar.com} and sample it in in the first week of September 2018.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} User activity is admittedly an imperfect metric for finding the `most significant' DApps: significant DApps might be lower volume overall or for extended periods of time (\eg ICOs, which we remedy by studying independently in Section~\ref{sec:ICOsfrontrunning}).
+However, user activity is arguably the best objective criteria for which data is readily available, the list captures our intuition about which DApps are significant, and it is at least better than an ad hoc approach.
 Using the dataset, we categorized the top 25 applications into 4 principal use cases.
@@
 Since Bancor handles all the trades and exchanges on the Ethereum blockchain (unlike other existing decentralized exchanges), these transactions are all visible to the public for some time before being included within a block.
-This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions, in which they can gain favorable profits by buying before the order and fill the original order with slightly higher price~\cite{BancorIs7:online}.
+This leaves Bancor vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions, in which they can gain favourable profits by buying before the order and fill the original order with slightly higher price~\cite{BancorIs7:online}.
 Researchers have shown and implemented a proof of concept code to front-run Bancor as a regular non-miner user~\cite{NewTab13:online}.
@@
 Consider Cryptokitties,\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}} the most active DApp in this category and third most active overall.
-Each cryptokitty (see Appendix~\ref{app:cryptokitty}) is a cartoon kitten with a set of unique features to distinguish it from other cryptokitties, some features more rare and harder to obtain.
+Each cryptokitty (see Appendix~\ref{app:cryptokitty}) is a cartoon kitten with a set of unique features to distinguish it from other cryptokitties, some features are more rare and harder to obtain.
 They can be bought, sold, or bred with other cryptokitties.
@@
 \subsection{Front-Running Resistant Blockchains}
-There are technical difficulties to achieve such solutions as there are unknown factors within such network designs and requires testing every corner and edge case scenarios.
-In this section, we describe the potential solutions using which, one can design and implement a decentralized application that is resistant to front-running.
+\textblue{Do we need to keep this sentence?
+There are technical difficulties to achieve such solutions as there are unknown factors within such network designs and requires testing every corner and edge case scenarios.} In this section, we describe the potential solutions using which, one can design and implement a decentralized application that is resistant to front-running.
 

### 2018-09-25 frontrunning/Latex/sections/appendix.tex
[frontrunning] more fixes, separate appendix from main

% !TEX root = ../main.tex

\appendix

\section{CryptoKitty} \label{app:cryptokitty}

%Possibly remove this figure due to page limit
\begin{figure}[!htb]
\centering
\includegraphics[width=0.3\linewidth]{figures/cryptokittie842912.png}
\caption{ Cryptokitty Number 842912 \label{fig:cryptokittie}}
\end{figure}

Figure~\ref{fig:cryptokittie} shows an example of a Cryptokitty.

\section{LocalEthereum} \label{app:code}

%Possibly remove this code snippet due to page limit . don't forget to remove the refrence to it ^
\begin{lstlisting}[basicstyle=\scriptsize\ttfamily,caption={Code snippet from LocalEthereum smart contract. Values V,R and S are set by LocalEtherem to have a valid signature, also the tradeHash uses buyer and seller addresses, mitigating the possibility of front-running by a third party.},label={code:localethereum}]
    function createEscrow(bytes16 _tradeID, address _seller, address _buyer, uint256 _value, uint16 _fee,
					uint32 _paymentWindowInSeconds, uint32 _expiry, uint8 _v, bytes32 _r, bytes32 _s) 
        payable external {
        bytes32 _tradeHash = keccak256(abi.encodePacked(_tradeID, _seller, _buyer, _value, _fee));
	...
        // A signature (v, r and s) must come from localethereum to open an escrow
        bytes32 _invitationHash = keccak256(abi.encodePacked(
            _tradeHash,
            _paymentWindowInSeconds,
            _expiry
        )); 
\end{lstlisting}

Code~\ref{code:localethereum} shows a mitigation technique employed by LocalEthereum. \\

\section{Traditional Front-running Prevention Methods}

There are debates in traditional markets regarding the fact that front-running is considered to be a form of insider trading which deemed to be illegal. Traditional methods to prevent front-running mainly involves after the fact investigation and legal action against the front-runners~\cite{LexisNexisLawSuit}. As mentioned in section~\ref{traditionalFrontrunning}, defining front-running and educating the employees were the first step taken to prevent such issues in traditional markets, however, front-running became less likely to happen mainly because of the high fine and lawsuits against firms who behaved in an unethical way. Other methods such as dark pools~\cite{zhu2014dark, buti2011diving} and sealed bids~\cite{radner1989sealed} were discussed and implemented in a variety of regulated trading systems. The traditional methods to prevent front-running does not apply to blockchain applications, as mainly they are based on central enforcement and limitations, also in case of blockchains the actors who are front-running could be anonymous and the fear of lawsuits would not apply.

\section{Commit-and-Reveal} \label{app:cr}

\begin{figure}[!htb]
\centering
\includegraphics[width=0.5\linewidth]{figures/commit-reveal.png}
\caption{\scriptsize Commit and Reveal. User sends a commitment transaction with the hash of the data, After the commitment period is over, user sends her reveal transaction to the DApp revealing the information that matches the commitment. \label{fig:commitReveal}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/3cd4c865-83d4-4c71-9a4a-f2e870f2db2c

Figure~\ref{fig:commitReveal} illustrates the commit/reveal approach.

### 2018-09-25 frontrunning/Latex/sections/paper.tex
[frontrunning] more fixes, separate appendix from main

--- 2018-09-25 frontrunning/Latex/sections/paper.tex
@@
 
-\subsection{Crypto-Collectibles Games}
+\subsection{Crypto-Collectibles Games}\label{sec:cryptogames}
 
@@
 \textsf{Ethereum Name Service (ENS)}\footnote{\url{https://ens.domains/}} is the most active naming service on Ethereum.
-Instead of allowing new  \texttt{.eth} domain names to be purchased directly, they are put up for a sealed bid auction.
+Instead of allowing new \texttt{.eth} domain names to be purchased directly, they are put up for a sealed bid auction which seals the domain name in the bids, but not the bid amount.
+The common way of getting a domain is to call \texttt{startAuctionsAndBid()} in ENS auction smart contract, which leaks the hash of the domain name and the initial bid amount in the auction.
+Users are allowed to bid for 48 hours before the 48-hour reveal phase begins, in which bidders must send a transaction to reveal their bids for a specific domain in auction.
+It is possible for user to front-run other reveal bids with the same bid amount or slightly higher to outbid the initial sealed bid.
+The auction model is similar to crypto-collectibles auctions in \ref{sec:cryptogames}
+
 \textblue{Although sealed auction method is used in ENS implementation, the normal workflow uses \texttt{startAuctionsAndBid()} with the deposit equal or higher than the bid, this information leakage could be used to front-run the transaction with the same bid amount or slightly higher to outbid the initial sealed bid.
 By doing so the front-runner invalidates the original bid and hence registers the domain name himself.}
-
-%too dense. need more explanation. --> explain what sealed auction is? whatsealed mean, refer to cryptokitties. what is actually bein auctions who deposits and what.  how ens actually works . 
-% two ways to add bid to an auction, start an auction and bid. but otehr method is that. whta sealed mean, domain is sealed but not anything else.  ENS auction details and then say . 
-%same price the first transaction would win, front-running. 
-%explain more on ENS auction
 
@@
 To the same end, Malinova~\cite{malinova2017market} propose a design for a decentralized exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable.
-\textblue{this is what it does, how does it do it?}
-% make it more obvious how they do this. how they changed it
+They split big investments into smaller ones using intermediaries --liquidity demander-- and liquidity providers to achieve this.
 
 %find a home for localethereum. explain the scenario where this actually works, how it can be front-run in original scenario, how this prevents front-running.
-\item \emph{\textblue{Technique}:} LocalEthereum, an escrow-based exchange, uses challenge random values from the website to be included in the signature of the transaction (See Code ~\ref{code:localethereum} in Appendix~\ref{app:code}), hence removing any possibility of replay attack or the possibility of any other address modifying key information in the order.
-\textblue{how does this solve front-running?}
-
+\item \emph{Trusted party:} It is possible to use a central trusted party, to mitigate the risks of front-running on the DApp design.
+As an example, LocalEthereum, an escrow-based exchange, facilitates the website as the match making service for the exchange orders, and challenge random values from the website to be included in the signature of the transaction (See Code ~\ref{code:localethereum} in Appendix~\ref{app:code}), hence removing any possibility of replay attack or the possibility of any other address modifying key information in the order.
+This method prevents network observers to be able to make a new transaction with the defined values as the third party will be the final entity approving the transaction.
  \end{compactlist}
@@
 Although there are other concerns about this specific design but not for front-running.
-
-%Proof of burn methods ?
 

### 2018-09-25 frontrunning/Latex/sections/paper.tex
[frontrunning] full round edit

@@
 An early use of commit/reveal is Namecoin, a Bitcoin-forked blockchain for name services~\cite{kalodner2015empirical}.
-A user sends a commit transaction, which commits to the name hash, similar to a sealed bid.
+In Namecoin, a user sends a commit transaction which commits to the name hash, similar to a sealed bid.
 Once the transaction is confirmed and the grace period is over, the user sends a reveal transaction revealing the bid and also the details of the requested domain~\cite{kalodner2015empirical}.
@@
 Commit/reveal is also seen in on-chain voting~\cite{adChainPLCRVoting}.
-Using sealed votes, voters can make sure their votes are hidden until a later date, however, their participation and weight of the vote are publicly known.
+Using sealed votes, voters can assure their votes are hidden until a later date, however, their participation and weight of the vote are publicly known.
 
 Other than the collateralization issue for the commit and reveal scheme, another obvious issue is the participatory factor.
-For anyone watching the DApp address, there will be a direct transaction from the user to the DApp address, It will be obvious that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme.
+For anyone watching the DApp address, there will be a direct transaction from the user to the DApp address, revealing the fact that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme.
 Both these issues, albeit hiding the details of the order and preventing direct front-running, leak information to other participants which could lead to more sophisticated front-running attacks depending on the application design.
@@
 In particular, they hide the DApp being invoked during the commit phase and also ensure that revealed transactions that send funds are fully collateralized.
-With submarine send, it is possible to hide sender, receiver, value, and data, the commitment transaction is identical to a transaction to a newly generated address.
+With submarine send, it is possible to hide sender, receiver, value, and data, so the commitment transaction is identical to a transaction to a newly generated address.
 Submarine sends could be a solution for sealed-bid auctions on the blockchain to hide the existence of the bids for other participants.
@@
 \item \emph{Disincentivizing Front-running Actors:} The call market solution also pivots profitable gains that front-running miners stand to gain into fees that they collect~\cite{clark2014decentralizing}, removing the financial incentive to front-run.
-To the same end, Malinova~\cite{malinova2017market} propose a design for a decentralized exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable.
+To the same end, Malinova~\cite{malinova2017market} proposes a design for a decentralized exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable.
 They split big investments into smaller ones using intermediaries --liquidity demander-- and liquidity providers to achieve this.

### 2018-09-25 frontrunning/Latex/sections/paper.tex
[frontrunning] more blue reflections

--- 2018-09-25 frontrunning/Latex/sections/paper.tex
@@
 
-\paragraph{Design Decision \#1: Fixed Transaction Ordering.} da Silva~\etal~\cite{fixedordering2018silva} proposes an algorithm, known as Fixed Transaction Ordering and Admission (FTOA) algorithm, in the consensus protocol that enforces the order of the transactions in the mined blocks to eliminate transaction reordering by miners.
-\textblue{How exactly does this fix front-running?}
+\paragraph{Design Decision \#1: Fixed Transaction Ordering.} da Silva~\etal~\cite{fixedordering2018silva} proposes an algorithm, known as Fixed Transaction Ordering and Admission (FTOA) algorithm, in the consensus protocol that enforces the order of the transactions in the mined blocks, using logical timestamps in a Byzantine setting, to eliminate transaction reordering by miners.
+This is a theoretical solution and will not be trivial to implement in the current Byzantine consensus protocols.
 
-\paragraph{Design Decision \#2:Privacy-Preserving Blockchains.} %Market participants are concerned about revealing information on their past trades, purchases, income, or liquidity needs.
-Privacy is a basic human right, that being said, there are limitations to the functionality of a system designed to preserve full privacy.
-However other than past transactions, real-time transactions would leak information about the sender or the intention of the order that could lead to front-running attacks.
-Privacy-preserving blockchains strive (to some extent~\cite{miller2017empirical, kappos2018empirical}) to keep all details of transactions private, including participants and amounts.
+\paragraph{Design Decision \#2:Privacy-Preserving Blockchains.} Privacy-preserving blockchains strive (to some extent~\cite{miller2017empirical, kappos2018empirical}) to keep all details of transactions private, including participants and amounts.
 As an example, ZCash~\cite{hopwood2016zcash}, uses two distinct type of addresses, transparent addresses and shielded addresses.
@@
 While this works for simple transactions, building similar shields for DApps is subject to on-going research~\cite{kosba2016hawk}.
-\textblue{How exactly does this fix front-running?}
-%why this solves or makes it harder to front-run. to front run you need to know what values are there but if it is dark it's harder
+With the possibility of having private smart contracts in such a setting, it could be feasible to achieve a front-run resistance blockchain, however the functionality of the smart contracts could be limited.
 

### 2018-09-25 frontrunning/Latex/sections/paper.tex
[frontrunning] merging sentences + edits

--- 2018-09-25 frontrunning/Latex/sections/paper.tex
@@
 
-In one sense, blockchain technology (which was introduced via Bitcoin in 2008~\cite{nakamoto2008bitcoin}) strives to disintermediate certain central parties that would participate in a transaction.
+In one sense, blockchain technology (which was introduced via Bitcoin in 2008~\cite{nakamoto2008bitcoin}) strives to disintermediate certain central parties that participate in a transaction.
 However, blockchains also introduce new participants in the relaying and finalization (\ie mining) of transactions that can act as front-runners.
 Any user monitoring blockchain network transactions (\eg running a full node) can see a unconfirmed transactions and broadcast a reactionary transaction that might be confirmed ahead of the original transaction.
-For regular users to front-run others on the blockchain, they need to be well connected to other nodes on the network.
-Doing so, they are able to listen to the network and monitor all transactions that are broadcast.
+For regular users to front-run others on the blockchain, they need to be well connected to other nodes on the network and listen to the network to monitor all transactions that are broadcast.
 On the Ethereum blockchain, users have to pay for the computations in a small amount of Ether called \textsf{gas}~\cite{AccountT67:online}.
 The price that users pay for transactions, \textsf{gasPrice}, can increase or decrease how quickly miners will execute them and include them within the blocks they mine.
-Once seeing two identical transactions with different transaction fees, a rational miner will prioritize the transaction that pays a higher gas price per unit of gas, \textsf{gasPrice}, due to limited space in the blocks.
-Therefore, any regular users who run a full-node Ethereum client can front-run pending transactions by sending similar transaction with higher gas price.
-Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this in case of malicious reordering is known as \textsf{transaction reordering} attack.
+Once seeing two identical transactions with different transaction fees, a rational miner will prioritize the transaction that pays a higher gas price, due to limited space in the blocks.
+Therefore, any regular user who runs a full-node Ethereum client can front-run pending transactions by sending similar transaction with higher gas price.
+Also, blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this in case of malicious reordering is known as \textsf{transaction reordering} attack.
 
@@
 \subsection{Front-Running Resistant Blockchains}
-\textblue{Do we need to keep this sentence?
-There are technical difficulties to achieve such solutions as there are unknown factors within such network designs and requires testing every corner and edge case scenarios.} In this section, we describe the potential solutions using which, one can design and implement a decentralized application that is resistant to front-running.
+In this section, we describe the potential solutions using which, one can design and implement a decentralized application that is resistant to front-running.
+Note that, the existing technical difficulties make these solutions hard to achieve as it requires designers to test edge case scenarios.
 

### 2018-09-25 frontrunning/Latex/sections/paper.tex
[frontrunning] minor edits

--- 2018-09-25 frontrunning/Latex/sections/paper.tex
@@
 The auction model is similar to crypto-collectibles auctions in \ref{sec:cryptogames}
-
-\textblue{Although sealed auction method is used in ENS implementation, the normal workflow uses \texttt{startAuctionsAndBid()} with the deposit equal or higher than the bid, this information leakage could be used to front-run the transaction with the same bid amount or slightly higher to outbid the initial sealed bid.
-By doing so the front-runner invalidates the original bid and hence registers the domain name himself.}
 

### 2018-09-25 frontrunning/Latex/sections/paper.tex
[frontrunning] more merging

--- 2018-09-25 frontrunning/Latex/sections/paper.tex
@@
 
-Bancor is another Ethereum-based application that allows users to exchange their tokens without any counter-party risk.
+Bancor is another DApp that allows users to exchange their tokens without any counter-party risk.
 This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}.
@@
 Implemented on the Ethereum blockchain, when transactions are broadcast to the network, they sit in a pending transaction pool known as \textit{mempool} waiting for the miners to mine them.
-Since Bancor handles all the trades and exchanges on the Ethereum blockchain (unlike other existing decentralized exchanges), these transactions are all visible to the public for some time before being included within a block.
+Since Bancor handles all the trades and exchanges on the chain (unlike other existing decentralized exchanges), these transactions are all visible to the public for some time before being included within a block.
 This leaves Bancor vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions, in which they can gain favourable profits by buying before the order and fill the original order with slightly higher price~\cite{BancorIs7:online}.
@@
 It is possible for user to front-run other reveal bids with the same bid amount or slightly higher to outbid the initial sealed bid.
-The auction model is similar to crypto-collectibles auctions in \ref{sec:cryptogames}
+The auction model is similar to crypto-collectibles auctions in \ref{sec:cryptogames}.
 
@@
 
-\paragraph{Design Decision \#1: Fixed Transaction Ordering.} da Silva~\etal~\cite{fixedordering2018silva} proposes an algorithm, known as Fixed Transaction Ordering and Admission (FTOA) algorithm, in the consensus protocol that enforces the order of the transactions in the mined blocks, using logical timestamps in a Byzantine setting, to eliminate transaction reordering by miners.
-This is a theoretical solution and will not be trivial to implement in the current Byzantine consensus protocols.
+\paragraph{Design Decision \#1: Fixed Transaction Ordering.} da Silva~\etal~\cite{fixedordering2018silva} proposes an algorithm, known as Fixed Transaction Ordering and Admission (FTOA), in the consensus protocol that enforces the order of the transactions in the mined blocks, using logical timestamps in a Byzantine setting, to eliminate transaction reordering by miners.
+This is a theoretical solution and is not trivial to implement in the current Byzantine consensus protocols.
 
 \paragraph{Design Decision \#2:Privacy-Preserving Blockchains.} Privacy-preserving blockchains strive (to some extent~\cite{miller2017empirical, kappos2018empirical}) to keep all details of transactions private, including participants and amounts.
-As an example, ZCash~\cite{hopwood2016zcash}, uses two distinct type of addresses, transparent addresses and shielded addresses.
+As an example, ZCash~\cite{hopwood2016zcash} uses two distinct types of addresses, transparent and shielded addresses.
 Transparent addresses work similar to Bitcoin transactions, fully transparent about the sender and receiver addresses, the amount and included data.
-However shielded addresses are private and do not leak any of this information.
-While this works for simple transactions, building similar shields for DApps is subject to on-going research~\cite{kosba2016hawk}.
+However shielded addresses are private and do not leak any information.
+While this solution works for simple transactions, building similar shields for DApps is subject to on-going research~\cite{kosba2016hawk}.
 With the possibility of having private smart contracts in such a setting, it could be feasible to achieve a front-run resistance blockchain, however the functionality of the smart contracts could be limited.
@@
 
-An early use of commit/reveal is Namecoin, a Bitcoin-forked blockchain for name services~\cite{kalodner2015empirical}.
+An early use of this scheme is Namecoin, a Bitcoin-forked blockchain for name services~\cite{kalodner2015empirical}.
 In Namecoin, a user sends a commit transaction which commits to the name hash, similar to a sealed bid.
 Once the transaction is confirmed and the grace period is over, the user sends a reveal transaction revealing the bid and also the details of the requested domain~\cite{kalodner2015empirical}.
-Using this scheme, one is able to hide information from the adversarial parties in the system and prevent them from front-running.
+Hence, user is able to hide information from the adversarial parties in the system and prevent front-running attacks.
 
@@
 
-Other than the collateralization issue for the commit and reveal scheme, another obvious issue is the participatory factor.
+The participatory factor is another issue for commitment scheme.
 For anyone watching the DApp address, there will be a direct transaction from the user to the DApp address, revealing the fact that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme.

### 2018-09-25 frontrunning/Latex/sections/paper.tex

@@
 In particular, ideal functionalities of blockchains (such as those used in simulation-based proofs) need to capture this adversarial capability, assuming the real blockchain does not address front-running.
-See \eg \textblue{the Bitcoin Backbone~\cite{garay2015bitcoin}} and Hawk~\cite{kosba2016hawk}.
+See \eg~\cite{garay2015bitcoin} and Hawk~\cite{kosba2016hawk}.
 
@@
 The auction model is similar to crypto-collectibles auctions in \ref{sec:cryptogames}.
-
-\textblue{Although sealed auction method is used in ENS implementation, the normal workflow uses \texttt{startAuctionsAndBid()} with the deposit equal or higher than the bid, this information leakage could be used to front-run the transaction with the same bid amount or slightly higher to outbid the initial sealed bid.
-By doing so the front-runner invalidates the original bid and hence registers the domain name himself.}
 

### 2018-09-25 auditing/Latex/sections/00-abstract.tex
Audit clean up

@@
 
-The emergence of cryptocurrencies, like Bitcoin, and blockchain technologies, like Ethereum, have matured to a point that commercial firms operating in this space have begun to seek financial audits.
+The emergence of cryptocurrencies (\eg Bitcoin) and block\-chain technologies (\eg Ethereum) have matured to a point that commercial firms operating in this space are seeking audits of their financial statements.
 At the time of writing, auditing firms are hesitant to audit such firms for a variety of reasons with a common underlying theme: the blockchain market introduces novel, technically sophisticated, and risky propositions.

### 2018-09-25 auditing/Latex/sections/01-intro.tex
Audit clean up

@@
 
-In certain common circumstances, firms operating in the blockchain space will require their financial statements to be audited by an external firm.
+A number of firms operate with blockchain-based assets, liabilities, and/or transactions.
+In certain common circumstances, these firms will require their financial statements to be validated by a financial auditor.
 Annual audits are legally mandatory for publicly traded companies in most countries, and audits might also be required when a firm borrows from a bank or raises capital from investors.
@@
 
-When assessing whether or not to take on a new client, auditors lack experience in this sector and therefore are unable to develop expectations of financial performance as a way of challenging financial statement assumptions.
-Due to the complex and rapidly changing technological environment, auditors are also unable to keep pace with the changes and develop the in-depth knowledge of their clients{'}  businesses required for performing an audit.
+When assessing whether or not to take on a new client, auditors who lack experience in this sector will be unable to develop expectations of financial performance as a way of challenging financial statement assumptions.
+Due to the complex and rapidly changing technological environment, auditors are also unable to keep pace with the changes and develop the in-depth knowledge of their clients'  businesses required for performing an audit.
 Finally, auditors are wary of accepting clients that hold a significant amount of cryptoassets as this space is largely unregulated.
@@
 In this paper we explore why and provide a comprehensive overview of the challenges auditors perceive as novel, we form parallels to auditing approaches used today, and critically assess the extent to which these challenges are barriers.
-Altogether, we find that while this environment is new, the challenges presented are different incarnations of issues already addressed on traditional audit clients.
+Altogether, we find that while this environment is new, the challenges presented are different incarnations of issues already addressed with traditional audit clients.
 Therefore, we conclude that many entities in this space are auditable, subject to certain caveats.
 
-\paragraph{\textbf{Methodology.}} To ensure a comprehensive overview of the changes facing auditors of companies deploying blockchain technologies, we first used structured brainstorming within our multidisciplinary research team, which includes expertise in both auditing and blockchain technologies.
+\paragraph{\textbf{Methodology.}} To ensure a comprehensive overview of the changes facing auditors, we first used structured brainstorming within our multidisciplinary research team, which includes expertise in both auditing and blockchain technologies.
 Once our preliminary list of challenges was established, we vetted our results through informal discussions with over a dozen individuals working in the field, including at the Big Four\footnote{The Big Four are the four biggest auditing firms in the world which includes, Ernst \& Young (EY), Deloitte \& Touche, KPMG and PricewaterhouseCoopers (PwC).} and mid-sized accounting firms, and used these interviews to augment our list.
-The contribution of this paper is to provide a comprehensive list of challenges, rather than determining the relative importance of each or any broader concepts across the industry---thus we did not find it necessary to apply qualitative data analysis (\eg grounded theory) to the interviews; instead, we simply extracted the challenges raised which we initially missed.
+The contribution of this paper is to provide a comprehensive list of challenges, rather than determining the relative importance of each or any broader concepts across the industry---thus we did not find it necessary to apply qualitative data analysis (\eg grounded theory) to the interviews; instead, we simply extracted the challenges raised.
 
-\paragraph{\textbf{Relevance.}} Our work can be viewed as a case study of cryptographers working with an outside profession for addressing a real-world problem.
+\paragraph{\textbf{Relevance.}} Our work can be viewed as a case study of cryptographers working with an outside profession to address a real-world problem.
 The result is not a new protocol but a two-way knowledge transfer between professions.
-While displacing auditors is occasionally a target of cryptographers~\cite{narula2018zkledger,dagher2015provisions}, auditing itself is also occasionally studied directly at venues like Financial Cryptography~\cite{grigg2000financial}.
+While displacing auditors is occasionally a target of cryptographers~\cite{dagher2015provisions,narula2018zkledger}, auditing itself is also occasionally studied directly at venues like Financial Cryptography~\cite{Swi97,BFS98,grigg2000financial}.
 
@@
 \section{Preliminaries and Related Work}
-Financial statements are prepared by a firm to summarize its assets and liabilities at year-end, the resulting changes in firm equity, and the firm{'}s revenue, expenses, and cash flows across the year.
+Financial statements are prepared by a firm to summarize: its assets and liabilities at year-end, the resulting changes in firm equity, and the firm{'}s revenue, expenses, and cash flows across the year.
 Because the firm generally wants to present the most optimistic view of its financial health, the firm may hire an auditor to ensure it is a realistic picture of the company{'}s financial performance.
 In doing so, auditors are expected to comply with Generally Accepted Auditing Standards (GAAS) and the Code of Conduct of their professional order~\cite{strother1975establishment}.
-In addition to an audited statement, the firm will produce quarterly statements that are reviewed by a third party auditor to a less rigorous standard.
+In addition to an annual audited statement, the firm will produce quarterly statements that are reviewed by a third party auditor to a less rigorous standard.
 
-%NOTE: Note that there are auditing and accounting papers in the bib/zotero that have not been cited here! {blaze1998compliance}
 %------------------------------------------------------------------------------------------------
@@
 A firm's CEO and CFO must certify the adequacy and effectiveness of the firm{'}s internal controls over financial reporting, which poses a reputational risk for firm directors as they will be held accountable for financial statements that are misstated.
-Management will seek an audit to comply with regulatory requirements, or because they feel it will give them a competitive advantage over non-audited firms in raising capital and lowering their lending rates.
-In a market where auditors are reluctant or audits are expensive, firms can use their ability to obtain audited financial statements as a barrier against new entrants to the blockchain sector.
+Management will agree to an audit to comply with regulatory requirements, or because they feel it will give them a competitive advantage over non-audited firms in raising capital and lowering their lending rates.
+In the blockchain market where auditors are reluctant and/or audits are expensive, firms can use their ability to obtain audited financial statements as a barrier against new entrants to the sector.
 
@@
 Investors use financial statements to assess their potential return on investment.
-Although \textit{caveat emptor} is an important consideration, investors rely on the existence of an auditor{'}s report as a signal of the reliability of financial disclosures.
+Although \textit{caveat emptor}\footnote{Latin: Let the buyer beware.} is a consideration, investors rely on the existence of an auditor{'}s report as a signal of the reliability of financial disclosures.
 
@@
 \subsection{Cryptoassets and firms that hold them}
-The central component of a financial report is the firm{’}s balance sheet which lists assets and liabilities.
-We use the term \textit{cryptoasset} and \textit{cryptoliability} to refer to items whose value are contingent on blockchain technologies.
+The central component of a financial report is the firm's balance sheet which lists assets and liabilities.
+We use the term \textit{cryptoasset} and \textit{cryptoliability} to refer to items contingent on blockchain technologies.
 Cryptoassets include cryptocurrencies and other tokens of tradeable value.
-Without loss of generality, we assume cryptocurrencies are native to their underlying blockchain, can be transacted directly, and are used to pay fees for transaction execution, \eg Bitcoin and Ether.
+Without loss of generality, we assume cryptocurrencies are native to their underlying blockchain, can be transacted directly, and are used to pay fees for transaction execution (\eg bitcoin and ether).
 For blockchains that allow developers to deploy custom decentralized applications, the applications might issue and manage the ownership of custom tokens.
-In the case of Ethereum, these tokens are often \textit{ERC20} tokens~\cite{erc20}, where \textit{ERC20} is sometimes misunderstood to mean what the token represents; rather, \textit{ERC20} is a technical standard about how token transactions are invoked.
+In the case of ethereum, these tokens are often \textit{ERC20} tokens~\cite{erc20}, where \textit{ERC20} is sometimes misunderstood to mean what the token represents; rather, \textit{ERC20} is a technical standard about how token transactions are invoked.
 
-What a token represents varies across applications but includes at least one of the following major categories.
-\textit{(1) Access tokens}: a service is developed which requires its own custom tokens for using the service; \textit{(2) Backed tokens}: a token issuer claims to be holding something valuable (material or digital) in reserve, and the token represents a claim on these reserves; \textit{(3) Equity tokens}: a firm issues tokens to represent ownership shares of the company; and \textit{(4) Collectable tokens}: the token itself is offered as a contemporary collector{’}s item (\eg \textit{ERC721}~\cite{erc721}).
-Digital tokens of these types predate blockchains; for example, \textit{Linden dollars}, \textit{E-Gold}, and \textit{(4)} URLs are arguably examples.
-Equities \textit{(3)} are almost entirely dematerialized (\eg paper stock certificates are rare) but operate closer to \textit{(2)} with a central depository.
+What the token actually represents depends on the application, but major categories include the following.
+\textit{(1) Access tokens}: a service is developed which requires its own custom tokens for using the service; \textit{(2) Backed tokens}: a token issuer claims to be holding something valuable (material or digital) in reserve, and the token represents a claim on these reserves; \textit{(3) Equity tokens}: a firm issues tokens to represent ownership shares of the company; and \textit{(4) Collectable tokens}: the token itself is offered as a contemporary collector's item (\eg \textit{ERC721}~\cite{erc721}).
+Digital tokens of these types predate blockchains; for example, \textsf{Linden Dollars}, \textsf{E-Gold}, and URLs are arguably examples of (1), (2), and (4) respectively.
+Equities are almost entirely dematerialized (\eg paper stock certificates are rare) but operate closer to (2) with a central depository (\eg DTCC) and holding company (\eg Cede \& Co.).
 
-Tokens and cryptocurrencies are issued to an initial set of owners through any mechanism of the issuer{'}s choosing.
+Tokens are issued to an initial set of owners through any mechanism of the issuer{'}s choosing.
 A popular option is auctioning a set of tokens to the public in an ``Initial Coin Offering'' or ICO.
@@
 An ICO of an access token might raise capital for developing or improving the service that will use these tokens.
-Buyers obtain such tokens to lock in the purchase price (hedging) or for speculation.
+Buyers seem to obtain such tokens to lock in the purchase price (\ie utility hedging) or because they believe they can sell for a profit (\ie speculation).
+Backed tokens are digital representations of an off-blockchain asset or liability.
+One example would be the recognition of a land deed on a blockchain in the form of a token.
+The blockchain must be invoked during the audit to validate ownership, the land itself is obviously not on the blockchain.
+The token issuer is trusted to ensure the token is a valid claim on what it represents.
 
 Any action that results in a firm borrowing a cryptoasset results in an offsetting cryptoliability.
-For example, an exchange service that holds bitcoin or tokens on behalf of its clients has both an asset (the cryptoasset it holds in its possession) and a liability (the obligation to repay its clients).
-Tokens could represent a debt instrument, like a bond, commercial paper, or repurchase agreement.
+For example, an exchange service that holds bitcoin or tokens on behalf of its clients has both an asset (the cryptoasset it holds `in street name') and a liability (the obligation to repay it's client the cryptoasset on-demand).
+In the future, tokens could represent a debt instrument, like a bond, commercial paper, or repurchase agreement.
 In a recent pilot, a blockchain-based certificate of deposit was issued~\cite{NBCJPMorganBlockchain}.
@@
 
-Bitcoin and Ether are native to their blockchains.
-Other assets or liabilities are digital representations of an off-blockchain asset or liability.
-One example would be the recognition of a land deed on a blockchain in the form of a token.
-The blockchain must be invoked during the audit to validate ownership, the land itself is obviously not on the blockchain.
-
-To illustrate how a firm might come to possess a cryptoasset, consider four examples of firms that have actually sought audits or regulatory exemptions from audits\footnote{[Anonymized] Based on data provided to us by the financial regulator in the region where the authors work.}.
-A mining firm will invest in specialized computing equipment and electricity to generate cryptocurrencies it will hold as assets.
+It might seem esoteric for a real-world, profitable firm today to actually be holding a material amount of cryptoassets.
+Consider four illustrative examples of firms that have actually sought audits or regulatory exemptions from audits.\footnote{[Anonymized] Based on data provided to us by the financial regulator in the region where the authors work.} A mining firm will invest in specialized computing equipment and electricity to generate cryptocurrencies it will hold as assets.
 An exchange service will hold demand deposits of cryptocurrencies or tokens, as well as governmental currencies, and allow its users to trade them.
-An investment fund will hold a portfolio of cryptoassets (\eg TIQ101-CF is 50\% bitcoin, 35\% ether, 15\% litecoin \todo{[cite-confidential?]}) and sell shares to investors through a standard financial platform.
+An investment fund will hold a portfolio of cryptoassets (\eg TIQ101-CF is 50\% bitcoin, 35\% ether, 15\% litecoin~\cite{3iq18}) and sell shares to investors through a standard financial platform.
 Finally, a firm initiating a token sale will raise capital in cryptocurrencies, held as an asset, in return for tokens that are not generally liabilities (it may also reserve some tokens as an additional asset).
-
-% [c] : https://3iq.ca/wp-content/uploads/2017/3iq-om-summary-en.pdf  <-- is this confidential? it is on public web but it says not to be distrubuted in public?
 
@@
 \subsection{Presentation of Cryptoassets}
-A financial report will classify assets and liabilities according to categories established by the auditing standards adhered to in the firm{'}s reporting country (American Generally Accepted Accounting Principles in the United States and International Financial Reporting Standards (IFRS) in many other countries).
-The following discussion will apply IFRS although the considerations under US GAAP are similar.
-% \todo{ GAAP and IFRS citations  }
+A financial report will classify assets and liabilities according to categories established by the auditing standards adhered to in the firm{'}s reporting country.
+This is the \textit{American Generally Accepted Accounting Principles} in the United States, and the \textit{International Financial Reporting Standards (IFRS)} in many other countries.
+Without loss of generality, we will consider IFRS.
 
@@
 This results in a presentation of cryptoassets that does not necessarily reflect the underlying economic reality of the assets at hand.
-For instance, an investment portfolio that holds a combination of Bitcoin and Google stock for long-term capital appreciation purposes would report the Bitcoin as an intangible asset~\cite{RCGTIFRsCrypto2018} and the Google stock as a short-term investment.
+For instance, an investment portfolio that holds a combination of bitcoin and Google stock for long-term capital appreciation purposes would report the bitcoin as an intangible asset~\cite{RCGTIFRsCrypto2018} and the Google stock as a short-term investment.
 The Google stock would be presented at its fair market value and any gains and losses on this investment would be immediately reported as part of the net profit.
-The Bitcoin, on the other hand, could either be presented at historical cost (what the company paid for the Bitcoin) or revalued to its fair market value.
-If the Bitcoin is reported at cost, any increases in value would not be recorded until the asset is sold (decreases in value below cost would be reported immediately).
-If the Bitcoin is reported at fair market value, any increases in value would be reported in \textit{Other Comprehensive Income}, a special category that does not fall into the net profit.
-This means that while the investment fund holds two investments, Bitcoin and Google stock, both for long-term growth purposes, the current standards would not allow these investments to recorded on the same basis.
-This also means that increases in the value of Bitcoin or other cryptoassets are not recorded as part of the net profit, which obfuscates a company{'}s annual reported earnings and undermines their usefulness for investors.
+The bitcoin, on the other hand, could either be presented at historical cost (what the company paid for the bitcoin) or revalued to its fair market value.
+If the bitcoin is reported at cost, any increases in value would not be recorded until the asset is sold (decreases in value below cost would be reported immediately).
+If the bitcoin is reported at fair market value, any increases in value would be reported in \textit{Other Comprehensive Income}, a special category that does not fall into the net profit.
+This means that while the investment fund holds two investments, bitcoin and Google stock, both for long-term growth purposes, the current standards would not allow these investments to recorded on the same basis.
+This also means that increases in the value of bitcoin or other cryptoassets are not recorded as part of the net profit, which obfuscates a company{'}s annual reported earnings and undermines their usefulness for investors.
 
@@
 However, most ICOs are not set out to give the holder an interest in the company as a whole, but rather represent an interest in a specific project.
-If the token holder is owed some type of obligation, like access to a marketplace or participation in application , then recognition of the funds received as a liability would be appropriate.
+If the token holder is owed some type of obligation, like access to a marketplace or participation in application, then recognition of the funds received as a liability would be appropriate.
+Under rare cases, the proceeds could be reported as revenue if the funds received do not qualify as either share capital or represent some ongoing obligation towards the token holder.
 
-Under rare cases, the proceeds could be reported as revenue if the funds received do not qualify as either share capital or represent some ongoing obligation towards the token holder.
-However, we expect these instances to be fairly rare as it is unlikely that an investor would contribute to an ICO and not expect something of value in return.
+% Jeremy: Actually I think this is the case unfortunitely
+% However, we expect these instances to be fairly rare as it is unlikely that an investor would contribute to an ICO and not expect something of value in return.
 
@@
 However, issues surrounding the presentation and measurement of these items on the financial statements undermine the potential information content of these statements.
-
-The following sections will present key issues that currently are troubling auditors and provide solutions or directions for future research.
+In the rest of the paper, we will present key issues that currently are troubling auditors.

### 2018-09-25 auditing/Latex/sections/02-body.tex
Audit clean up

@@
 % !TEX root = ../main.tex
-\section{Key Issue: Existence of Assets and Occurence of Transactions}
+\section{Key Issue: Existence of Assets}
 
@@
 The challenge of finality was an important design consideration in the Bank of Canada{'}s Project Jasper~\cite{chapman2017project} which sought to establish a Distributed Wholesale Payment Systems.
-``Project Jasper was structured so that a transfer of [digital currency] was equivalent to a full and irrevocable transfer of the underlying claim on central bank deposits.'' Given that on the Ethereum blockchain, transactions could be reversed, the work around for Project Jasper was to implement a ``design feature (which) relates to the issuance of (digital currency) and is therefore independent of the platforms upon which Jasper was built.''.
+``Project Jasper was structured so that a transfer of [digital currency] was equivalent to a full and irrevocable transfer of the underlying claim on central bank deposits.'' Given that on the Ethereum blockchain, transactions could be reversed, the work around for Project Jasper was to implement a ``design feature (which) relates to the issuance of (digital currency) and is therefore independent of the platforms upon which Jasper was built.''
 
@@
 The firm could estimate the amount of returns or reversals that are likely to occur and factor this into their transaction recognition.
-Alternatively, auditors could establish a generally accepted threshold (for instance, number of days) after which a transaction would be considered final.
+Alternatively, auditors could establish a generally accepted threshold (for instance, 6 blocks is commonly used in bitcoin) after which a transaction would be considered final.
 %we could discuss the practice of transaction confirmation for 6+ blocks here as well
@@
 \paragraph{Issue: Transaction Pointers.} Blockchain transactions need to be uniquely identified to be pointed at by secondary financial records.
-Due to an implementation fault in Bitcoin, transactions broadcasted with one identifier might end up in the blockchain with a different identifier -- Transaction Malleability --, which could lead a firm to conclude a transaction did not take place when in fact it did, but under an unexpected identifier~\cite{andrychowicz2015malleability}.
+Due to an implementation fault in Bitcoin, transactions broadcast with one identifier might end up in the blockchain with a different identifier.
+Known as transaction malleability, firms might erroneously conclude a transaction did not take place when in fact it did under an unexpected identifier~\cite{andrychowicz2015malleability}.
 Some firms went bankrupt when their automated system kept honouring refund requests from a malicious entity claiming the refunds were not going through~\cite{trautman2014virtual,decker2014bitcoin}.
-The larger lesson here is that auditors cannot always safely abstract away low level implementation details.
+The larger lesson here is that auditors cannot always safely abstract away low-level implementation details.
 
 %---------+++++++++++++++++++-----------------
-\paragraph{Issue: Occurrence.} \todo{This contradicts some of the points mentioned in Transaction Pointers and Finality, also the point made here is also mentioned there.
+%\paragraph{Issue: Occurrence.} \todo{This contradicts some of the points mentioned in Transaction Pointers and Finality, also the point made here is also mentioned there.
 My suggestion is to remove this Issue or merge it with one of the above} In order to validate that cryptoasset transactions actually took place during the year, auditors will look to reproduce the transactions carried out.
@@
 %---------+++++++++++++++++++-----------------
-\paragraph{Takeaway:} This section demonstrates that due to the immutable nature of the blockchain and its ability to report the totality of transactions conducted during the period, this technology provides a record upon which the auditor can obtain evidence to ascertain the occurrence of transactions.
+\paragraph{Takeaway.} This section demonstrates that due to the immutable nature of the blockchain and its ability to report the totality of transactions conducted during the period, this technology provides a record upon which the auditor can obtain evidence to ascertain the occurrence of transactions.
 However, the auditor will continue to need to rely on external sources such as a verbose secondary ledger to validate the legitimacy and business purpose of those transactions.
@@
 %---------+++++++++++++++++++-----------------
-\paragraph{Issue: Cryptographic keys.} For most cryptoassets, the asset is considered owned by Alice if Alice possesses a private signing key that can be used to sign a transfer of the asset.
+\paragraph{Issue: Cryptographic keys.} For most cryptoassets, the asset is considered owned by Alice if Alice possesses a private signing key that can be used to sign a transfer of the asset~\cite{Swi97,BFS98,KM99}.
 Through decentralized apps, alternative notions of ownership are possible to define, but this idea of a signing key is foundational and seen in bitcoin, ether, ERC20 tokens, etc.
@@
 The most direct technique is to use a zero knowledge proof of knowledge of this private key, and staple in some information identifying the context of the proof.
-For standard proofs, this is cryptographically equivalent to simply signing a challenge message with the key\footnote{A Schnorr Sigma-protocol with the challenge hashed in using Fiat-Shamir is exactly a Schnorr signature and closely related to an ECDSA signature.\todo{CITE}}.
-Folklore protocols of sending small cash amounts from an allegedly owned account to the auditor to demonstrate control are also commonly noted in the literature (and used in at least one occasion \todo{[cite]}).
+For standard proofs, this is cryptographically equivalent to simply signing a challenge message with the key\footnote{A Schnorr Sigma-protocol with the challenge hashed in using Fiat-Shamir is exactly a Schnorr signature and closely related to an ECDSA signature.}.
+Folklore protocols of sending small cash amounts from an allegedly owned account to the auditor to demonstrate control are also commonly noted in the literature.
 This offers similar security but adds ethical complexities for the auditor.
-\todo{ It requires more [cryptography] citations here! ~\cite{swire_uses_nodate,blaze1998compliance,kohlas_reasoning_nodate} }
-% What to cite for the [cite] placeholder
+
 We note that while this cryptographic proof is necessary, it is not sufficient.
@@
 %---------+++++++++++++++++++-----------------
-\paragraph{Issue: Self-custodianship.} Cryptocurrency advocates point to its non-reliance on trusted third parties as the key to its appeal \todo{[cite: CHI paper]}.
+\paragraph{Issue: Self-custodianship.} Cryptocurrency advocates point to its non-reliance on trusted third parties as the key to its appeal~\cite{GCL16}.
 Thus, the use of a custodian for cryptoassets (or more specifically, the private keys controlling the assets) is controversial.
-The advantage of a custodian is that it might more quickly specialize in security than end users, and this is certainly true for some users \todo{[cite: MIT]}.
+The advantage of a custodian is that one firm can specialize in security rather than all end users.
 Self-custodianship of non-digital assets, such as diamonds for a jewelry retailer or cash for a currency exchange, is already a concern for financial auditors.
-Further, custodianship over cryptographic keys is a financial factor in other sectors, such as certificate authorities like Verisign or Symantec which maintain keys critical to HTTPS and DNSSEC \todo{[cite]}.
+Custodianship over cryptographic keys is a factor in other sectors, such as certificate authorities like Verisign or Symantec which maintain keys critical to HTTPS and DNSSEC~\cite{clark2013sok}.
 To date, no blockchain custodian or exchange has been able to produce a report that supports the reliability of their internal controls in order to provide auditors with comfort over the sufficiency of their systems.
@@
 
+% Might have to soften "to date..." sentence
+
 %---------+++++++++++++++++++-----------------
-\paragraph{Takeaway:} In order for auditors to validate ownership, they must rely on cryptographic proofs as a first step.
+\paragraph{Takeaway.} In order for auditors to validate ownership, they must rely on cryptographic proofs as a first step.
 However, in order to avoid double-counting of keys, an industry standard common date should be arranged to provide a generally agreed upon ``state of the world'' where keyholders can demonstrate ownership.
@@
 \paragraph{Issue: Geographical Variation.} Because cryptoassets(\eg bitcoin) can be moved digitally without any geographic restrictions, it should be the case that any variation in cryptoasset prices across exchanges would be consumed by arbitrageurs.
-However, empirically this is not the case due to fees, settlement delays, and other frictions with exchange services \todo{[cite]}.
+However, empirically this is not the case due to fees, settlement delays, and other frictions with exchange services~\cite{KS17}.
+Reporting standards do not account for geographic variation.
 
@@
 %---------+++++++++++++++++++-----------------
-\paragraph{Takeaway:} While the valuation of cryptoassets with large trading volumes like Bitcoin and Ether would be fairly straightforward by referring to values in an active market, the valuation of coins with low liquidity may be more difficult.
+\paragraph{Takeaway.} While the valuation of cryptoassets with large trading volumes like Bitcoin and Ether would be fairly straightforward by referring to values in an active market, the valuation of coins with low liquidity may be more difficult.
 However, by using financial modelling using different assumptions for volatility, this challenge is not insurmountable.
@@
 
-\paragraph{Issue: Reliability of Blockchain Records.} Another challenge for auditors is determining what type of evidence or records constitute sufficient and appropriate audit evidence.
+%---------+++++++++++++++++++-----------------
+
+%\paragraph{Issue: Reliability of Blockchain Records.} Another challenge for auditors is determining what type of evidence or records constitute sufficient and appropriate audit evidence.
 In other words, an auditor must be satisfied that the records on the blockchain are reliable.
 How can we satisfy auditors that blockchain records are reliable
- \todo{This subsection needs some cutting, has duplicate points and not obvious what the main objective is.
+% \todo{This subsection needs some cutting, has duplicate points and not obvious what the main objective is.
 there are some comments on the google docs regarding this subsection that should be addressed}
-
-\begin{enumerate}
-\item[$\bullet$] How can we rely on blockchain?
+%
+%\begin{enumerate}
+%\item[$\bullet$] How can we rely on blockchain?
 Has anyone tested it?
@@
 How do I know that changes to blockchain code made and not undermine reliability?
-\end{enumerate}
-
-Traditionally, auditors depend on obtaining audit evidence from external parties as it is deemed as more objective or trustworthy than internal firm documents.
+%\end{enumerate}
+%
+%Traditionally, auditors depend on obtaining audit evidence from external parties as it is deemed as more objective or trustworthy than internal firm documents.
 For example, auditors will obtain confirmation from a bank of the amount of cash held at year end (a third party) rather than rely on internal records of banking transactions.
@@
 %---------+++++++++++++++++++-----------------
-\paragraph{Issue: Financial Literacy of Technology Professionals} While auditors must learn more about the technology, managers of companies in the blockchain space must also learn about the internal controls required to safeguard against errors, misappropriation of assets and fraud.
+\paragraph{Issue: Financial Literacy of Technology Professionals.} While auditors must learn more about the technology, managers of companies in the blockchain space must also learn about the internal controls required to safeguard against errors, misappropriation of assets and fraud.
 Given that financial statements are ultimately the responsibility of management and that senior management must certify the internal controls as part of the financial statement disclosures, managers have an incentive to implement a control environment that promotes a strong tone at the top, ethical conduct, and oversight of the financial reporting function.
@@
 Auditing internal procedures over cryptographic keys is not unprecedented---maintaining certificate authority keys is critical to some security firm{'}s financial prospects (a security breach at one firm, \textit{DigiNotar} led to its bankruptcy ~\cite{zetter2011diginotar}).
-Symantec{'}s self-custodianship over these keys involves elaborate security ceremonies whenever they are required \todo{[Cite]}.
+Symantec{'}s self-custodianship over these keys involves elaborate security ceremonies whenever they are required~\cite{Goo12}.
 
@@
 Due to the complex and rapidly changing nature of this sector, auditors are especially weary of fraud risk in this area.
-However, not all frauds that occur this space are new kinds of fraud.
+Not all frauds that occur this space are new kinds of fraud.
 For instance, Ponzi schemes have existed since they were perfected by Charles Ponzi in the early twentieth century~\cite{ponzi2001rise}.
@@
 \section{Discussion and Research Agenda}
-\todo{Check out the notes on the google docs regarding this section}
+
+%\todo{Check out the notes on the google docs regarding this section}
 
@@
 
-\todo{Check out the notes on the google docs regarding this section}
+Blockchain technology provides novel, non-trivial issues for financial auditors, however these issues are in no way insurmountable and in many ways parallel challenging conditions seen in other sectors.
+We conclude that many entities in this space are auditable.
+We also wish to note that the firm is ultimately the entity seeking the audit, auditors are not seeking the firm, and therefore the onus to ensure financial disclosures are readably auditable by non-specialists auditors really lies with the firm itself.
+For example, a firm might not want to use a custodian for cryptocurrencies for philosophical reasons, and overtime, the technical literacy of auditors will advance to where self-custodianship may be commonplace, however firms seeking audits in the short-term may need to invest time and resources into internal controls, financial reporting mechanisms, and third parties to enable less friction for auditors.
 

### 2018-09-25 frontrunning/Latex/sections/paper.tex
[frontrunning] add appendix references

@@
 There are two main approaches to mitigating front-running on blockchains: one is to design a blockchain that is front-run resistant, and the other to design the application logic in a way that front-running is not profitable.
-This can be done in addition to any legal remedies that might be enforceable.
+This can be done in addition to any legal remedies that might be enforceable (See Appendix ~\ref{app:traditionalprevention}).
 We note, but consider out-of-scope, approaches that introduce trusted parties to centralize time-sensitive functionalities (\eg exchanges \textit{EtherDelta} and \textit{0xProject} use off-chain order books~\cite{warren20170x,0xfrontrunning:online}).
@@
 \item \emph{Trusted party:} It is possible to use a central trusted party, to mitigate the risks of front-running on the DApp design.
-As an example, LocalEthereum, an escrow-based exchange, facilitates the website as the match making service for the exchange orders, and challenge random values from the website to be included in the signature of the transaction (See Code ~\ref{code:localethereum} in Appendix~\ref{app:code}), hence removing any possibility of replay attack or the possibility of any other address modifying key information in the order.
+As an example, LocalEthereum, an escrow-based exchange, facilitates the website as the match making service for the exchange orders, and challenge random values from the website to be included in the signature of the transaction (See Code ~\ref{code:localethereum} in Appendix~\ref{app:localethereum}), hence removing any possibility of replay attack or the possibility of any other address modifying key information in the order.
 This method prevents network observers to be able to make a new transaction with the defined values as the third party will be the final entity approving the transaction.

### 2018-09-26 frontrunning/Latex/sections/abstract.tex
NOt sure what this is anymore
[frontrunning] final round on abstract and intro

@@
 Front-running has been an issue in traditional financial instrument markets since the 1970's.
-With the advent of the blockchain technology, front-running resurfaced in new forms we explore here, due blockchain's decentralized and transparent nature.
+With the advent of the blockchain technology, front-running resurfaced in new forms we explore here, due to blockchain's decentralized and transparent nature.
 In this paper, we consider instances of front-running across the top 25 decentral applications (DApps) deployed on Ethereum.
-Additionally, we carry out detailed analysis of \textsf{Status.im} initial coin offering (ICO) and show evidence of abnormal miner's behaviour indicative of front-running token purchases.
+Additionally, we carry out a detailed analysis of \textsf{Status.im} initial coin offering (ICO) and show evidence of abnormal miner's behaviour indicative of front-running token purchases.
 Finally, we introduce a framework for categorizing proposed solutions to front-running and examine the applicability to the identified issues.

### 2018-09-26 frontrunning/Latex/sections/paper.tex
[frontrunning] final round on abstract and intro

@@
 Function calls (or transactions) to the DApp are processed by a decentralized network.
-Transactions are finalized in stages: they (generally) first relay around the network, then are selected by a miner and put into a valid block, and finally the block is well-enough incorporated that is unlikely to be reorganized.
+Transactions are finalized in stages: they (generally) first relay around the network, then are selected by a miner and put into a valid block, and finally, the block is well-enough incorporated that is unlikely to be reorganized.
 Front-running is an attack where a malicious node observes a transaction after it is broadcast but before it is finalized, and attempts to have its own transaction confirmed before or instead of the observed transaction.
@@
 Therefore, DApps need to be studied individually or in categories.
-This paper is a series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps) from each category of the top 25 most active.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} We do case studies on decentralized exchanges (\eg Bancor), crypto-collectibles (\eg CryptoKitties), gambling services (\eg Fomo3D), and decentralized name services (\eg Ethereum Name Service).
+This paper is a series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps) from each category of the top 25 most active, based on user activity.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} We do case studies on decentralized exchanges (\eg Bancor), crypto-collectibles (\eg CryptoKitties), gambling services (\eg Fomo3D), and decentralized name services (\eg Ethereum Name Service).
 We also study initial coin offerings (ICOs), which by happenstance, did not appear in the top 25 on our sample day.
@@
 This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to latecomers on the open markets~\cite{zetzsche2018ico, li2018initial}.
-ICOs started to experiment with different fair capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}.
+ICOs started to experiment with different \textit{fair} capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}.
 We show empirical evidence of a miner purchasing tokens ahead of other users in Status.im.
-Finally, proposals to eliminate or mitigate front-running from DApps are scattered across forums, proposed standards (called EIPs in Ethereum) and academic papers; we systemize them the last section.
+Finally, proposals to eliminate or mitigate front-running from DApps are scattered across forums, proposed standards (called EIPs in Ethereum) and academic papers; we systemize them in the last section.
 

### 2018-09-26 frontrunning/Latex/sections/paper.tex
fixed caption fonts

--- 2018-09-25 frontrunning/Latex/sections/paper.tex
@@
 \includegraphics[width=0.7\linewidth]{figures/Miner_reorder_frontrun.png}
-\caption{\scriptsize The adversarial miner can monitor the Ethereum mempool for decentralized exchange cancel orders and upon seeing the cancellation transaction, he puts his buy order prior to the cancel transaction.
+\caption{ The adversarial miner can monitor the Ethereum mempool for decentralized exchange cancel orders and upon seeing the cancellation transaction, he puts his buy order prior to the cancel transaction.
 Doing so, the miner can profit from the underlying trade and also get the gas included in the cancel transaction.
@@
 \includegraphics[width=0.7\linewidth]{figures/Regular_frontrunning.png}
-\caption{\scriptsize The Adversary up on seeing the Buy order, sends his own buy order with higher gas to front-run the first order. \label{fig:RegularFrontrunning}} 
+\caption{ The Adversary up on seeing the Buy order, sends his own buy order with higher gas to front-run the first order. \label{fig:RegularFrontrunning}} 
 \end{figure}
@@
 \includegraphics[width=0.5\linewidth]{figures/Mining_pool_ratio.png}
-\caption{\scriptsize The percentage of Ethereum blocks mined between block 3903900 and 3908029, this is the time frame in which Status.im ICO was running.
+\caption{ The percentage of Ethereum blocks mined between block 3903900 and 3908029, this is the time frame in which Status.im ICO was running.
 This percentage roughly shows the hashing power ratio each miner had at that time.
@@
 \includegraphics[width=0.9\linewidth]{figures/Transactions_miners_while_status_ico_cut_only_icotx.png}
-\caption{\scriptsize This chart shows the miners behaviour on the time window that Status.im ICO was running.
+\caption{ This chart shows the miners behaviour on the time window that Status.im ICO was running.
 It is clear that the number of successful transactions mined by F2Pool do not follow the random homogeneous pattern of the rest of the network.
@@
 \includegraphics[width=0.7\linewidth]{figures/F2Pool_transactions_to_StatusICO_and_Refunds.png}
-\caption{\scriptsize F2Pool prior to Status.im ICO deposited 100 Ether in multiple new Ethereum addresses.
+\caption{ F2Pool prior to Status.im ICO deposited 100 Ether in multiple new Ethereum addresses.
 On the time of the ICO they sent these deposits to Status ICO smart contract and prioritized mining of these transactions in their mining pool, this was to overcome the dynamic ceiling algorithm of the token sale smart contract.
@@
 \includegraphics[width=0.9\linewidth]{figures/Vulnerable_Loopring.png}
-\caption{\scriptsize \emph{submitRing} Transaction in the old version of the Loopring protocol.
+\caption{ \emph{submitRing} Transaction in the old version of the Loopring protocol.
 Any user can regenerate this transaction by replacing the miner's address with his address and signing the hash of the ring using his private key.
@@
 \includegraphics[width=0.7\linewidth]{figures/Dual_Authoring_Loopring.png}
-\caption{\scriptsize \emph{submitRing} Transaction in the new version of the Loopring protocol.
+\caption{ \emph{submitRing} Transaction in the new version of the Loopring protocol.
 Other users cannot regenerate this transaction as they do not access auth-keys and hence are not able to create the signatures.
@@
 \includegraphics[width=0.5\linewidth]{figures/LibSubmarine.png}
-\caption{\scriptsize Submarine Send~\cite{libsubmarine}.
+\caption{ Submarine Send~\cite{libsubmarine}.
 User generates an \textit{Unlock} transaction from which the commitment address is retrieved.

### 2018-09-26 frontrunning/Latex/sections/paper.tex
[frontrunning] final round till section 3

--- 2018-09-26 frontrunning/Latex/sections/paper.tex
@@
 The problem can occur in both financial and non-financial systems.
-In traditional stock exchanges, floor traders might overhear a broker's negotiation with her client over a large purchase, and literally race the broker to buy first, potentially profiting when the large sale temporarily reduces supply of the stock.
+In traditional stock exchanges, floor traders might overhear a broker's negotiation with her client over a large purchase, and literally race the broker to buy first, potentially profiting when the large sale temporarily reduces the supply of the stock.
 A malicious broker might also front-run their own client's orders by purchasing stock for themselves between receiving the instruction to purchase from the client and actually executing the purchase (similar techniques can be used for large sell orders).
@@
 If the person instead has access to more general privileged information that might predict future transactions, but is not reacting at the actual pending trades, we would classify this activity as insider trading.
-If the person reacts after the trade is executed, or information is made public, and profits from being the fastest to react, this is considered arbitrage and is both legal and encouraged because it helps markets integrate new information into prices quickly.
+If the person reacts after the trade is executed, or information is made public, and profits from being the fastest to react, this is considered arbitrage and is legal and encouraged because it helps markets integrate new information into prices quickly.
 
@@
 Fitzsimmons, Secretary, Securities, and Exchange Commission to Joseph W.
-Sullivan, President  CBoE).}'' The \textit{CBoE} tried to educate their members on existing rules, however differences in opinion regarding the unfairness of front-running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action~\cite{sec1978optionsmarket} until the SEC began regulation.
+Sullivan, President  CBoE).}'' The \textit{CBoE} tried to educate their members on existing rules, however, differences in opinion regarding the unfairness of front-running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action~\cite{sec1978optionsmarket} until the SEC began regulation.
 We refer the reader interested in further details on this early regulatory history to Markham~\cite{markham1988front}.
@@
 However, blockchains also introduce new participants in the relaying and finalization (\ie mining) of transactions that can act as front-runners.
-Any user monitoring blockchain network transactions (\eg running a full node) can see a unconfirmed transactions and broadcast a reactionary transaction that might be confirmed ahead of the original transaction.
+Any user monitoring blockchain network transactions (\eg running a full node) can see an unconfirmed transactions and broadcast a reactionary transaction that might be confirmed ahead of the original transaction.
 For regular users to front-run others on the blockchain, they need to be well connected to other nodes on the network and listen to the network to monitor all transactions that are broadcast.
@@
 Once seeing two identical transactions with different transaction fees, a rational miner will prioritize the transaction that pays a higher gas price, due to limited space in the blocks.
-Therefore, any regular user who runs a full-node Ethereum client can front-run pending transactions by sending similar transaction with higher gas price.
+Therefore, any regular user who runs a full-node Ethereum client can front-run pending transactions by sending similar transaction with a higher gas price.
 Also, blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this in case of malicious reordering is known as \textsf{transaction reordering} attack.
@@
 %make them more pointy, shorten it. mainly the first paragraph
-Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to market information leakage~\cite{aune2017footprints}.They also propose a cryptographic approach, similar to commit and reveal (see Section~\ref{CommitmentScheme}) to prevent front-running.
+
+Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to market information leakage~\cite{aune2017footprints}.
+They also propose a cryptographic approach, similar to commit and reveal (see Section~\ref{CommitmentScheme}) to prevent front-running.
 Malinova and Park discuss different design settings for financial markets and trading platforms on decentralized ledgers~\cite{malinova2017market}.
@@
 
-Double-spending attacks in Bitcoin have been studied~\cite{bamert2013have, karame2012double} where a user broadcasts a transaction and is able to obtain some off-blockchain good or service before the transaction has actually been (fully) confirmed.
-The user can then broadcast a competing transaction that sends the same unspent coins to herself, perhaps using higher transaction fees, arrangements with miners, or artefacts of the network topology to have the second transaction confirmed instead of the first.
+Double-spending attacks in Bitcoin have also been studied~\cite{bamert2013have, karame2012double} where a user broadcasts a transaction and is able to obtain some off-blockchain good or service before the transaction has actually been (fully) confirmed.
+The user can then broadcast a competing transaction that sends the same unspent coins to herself, perhaps using higher transaction fees, arrangements with miners or artifacts of the network topology to have the second transaction confirmed instead of the first.
 We think of this as a type of front-running.

### 2018-09-26 auditing/Latex/sections/02-body.tex
final round of edits

@@
 \paragraph{Issue: Meta-information.} Assets and liabilities that are transacted on a publicly readable blockchain record basic details, like times and values, but auditors require further information to validate the nature of a transaction.
-For example, assume an employee{'}s salary is paid in Bitcoin.
+For example, assume an employee{'}s salary is paid in bitcoin.
 Bitcoin{'}s blockchain shows that a transaction occurred but it does not specify it as a salary; nor does it confirm basic details like the number of hours paid, if the nominal amount is BTC or a spot conversion from a governmental currency, and what deductions for tax or benefits were applied.
 Most importantly, it does not confirm the amount the employee was paid accurately reflects the number of hours worked at the authorized pay rate.
-Therefore, the company either requires a verbose secondary ledger to track these details or a Decentralized Application (DApp).
+Therefore, the company either requires a verbose secondary ledger to track these details or a decentralized application (DApp).
 
@@
 \paragraph{Issue: Off-Blockchain Transactions.} Transactions may involve the exchange of cryptoassets for off-blockchain assets.
-For instance, a company may pay its supplier in Bitcoin for a shipment of raw materials.
-Although the Bitcoin is blockchain-native and that side of the transaction benefits from the consensus algorithm, the blockchain cannot verify that the right quantity or quality of raw materials were received in exchange for the consideration paid.
+For instance, a company may pay its supplier in bitcoin for a shipment of raw materials.
+Although the bitcoin is blockchain-native and that side of the transaction benefits from the consensus algorithm, the blockchain cannot verify that the right quantity or quality of raw materials were received in exchange for the consideration paid.
 Therefore, given that half of this transaction occurred off-blockchain, it would need to be audited like a traditional raw materials purchase.
@@
 And it is never guaranteed to be final: an agreement within the computational majority of miners can unroll past transactions, For example, Ethereum{'}s miners branched the main blockchain to modify some past transactions to reverse a hacked DApp transactions~\cite{dupont2017experiments}.
-The challenge of finality was an important design consideration in the Bank of Canada{'}s Project Jasper~\cite{chapman2017project} which sought to establish a Distributed Wholesale Payment Systems.
-``Project Jasper was structured so that a transfer of [digital currency] was equivalent to a full and irrevocable transfer of the underlying claim on central bank deposits.'' Given that on the Ethereum blockchain, transactions could be reversed, the work around for Project Jasper was to implement a ``design feature (which) relates to the issuance of (digital currency) and is therefore independent of the platforms upon which Jasper was built.''
+The challenge of finality was an important design consideration in the Bank of Canada{'}s Project Jasper~\cite{chapman2017project} which sought to establish a distributed large value payment system.
+``Project Jasper was structured so that a transfer of [digital currency] was equivalent to a full and irrevocable transfer of the underlying claim on central bank deposits.'' Given that on the Ethereum blockchain, transactions could be reversed with consensus of the miners, the work around for Project Jasper was to implement a ``design feature (which) relates to the issuance of (digital currency) and is therefore independent of the platforms upon which Jasper was built.''
 
@@
 In many cases, sales agreements provide customers with the option to return merchandise within a pre-established period.
-When recording revenue, the accountant much estimate the percentage of returns and factor this into the amount of revenue to be recorded.
+When recording revenue, the accountant must estimate the expected number of returns and factor this into the amount of revenue to be recorded.
 The same concept could be applied for the issue of finality.
 The firm could estimate the amount of returns or reversals that are likely to occur and factor this into their transaction recognition.
-Alternatively, auditors could establish a generally accepted threshold (for instance, 6 blocks is commonly used in bitcoin) after which a transaction would be considered final.
-%we could discuss the practice of transaction confirmation for 6+ blocks here as well
+Alternatively, auditors could establish a generally accepted threshold (for instance, 6 blocks is commonly used in Bitcoin) after which a transaction would be considered final.
 
@@
 For example, one proposed DApp for crowdfunding projects would allow stakeholders to split off into a smaller DApp, taking a share of the assets from the parent DApp with it~\cite{dupont2017experiments}.
-Another example would be the Lightning Network~\cite{poon2016bitcoin} which is a second layer, off blockchain payment network that was implemented for scaling Bitcoin to increase its throughput.
-The Lightning Network is more complex than simple Bitcoin payments and involves payment channels and routings.
-
+Another example would be the Lightning Network~\cite{poon2016bitcoin} which is a second layer, off-blockchain payment network that was implemented for scaling bitcoin and enabling micro-transactions.
+Lightning transactions are more complex than simple bitcoin payments, involving payment channels routed through multiple parties that may not be finalized.
 While firms may complicate their transactions either for economic benefits in order to obfuscate the true nature of their transactions, the onus is on the firm under audit to operate in an auditable fashion.
 In other words, while it is the auditor{'}s responsibility to design procedures to gain comfort over an entity{'}s operations, it is the responsibility of management to implement controls and procedures to ensure that the entity is audit-ready.
-Therefore, some complex operations, while economically sound, may be avoided to ensure the audibility of operations.
+Therefore, some complex operations, while economically sound, might be avoided to ensure the audibility of operations.
 
@@
 %---------+++++++++++++++++++-----------------
-\paragraph{Issue: Cryptographic keys.} For most cryptoassets, the asset is considered owned by Alice if Alice possesses a private signing key that can be used to sign a transfer of the asset~\cite{Swi97,BFS98,KM99}.
+\paragraph{Issue: Cryptographic keys.} For most cryptoassets, the asset is considered owned by Alice if Alice possesses a private signing key that can be used to sign a transfer of the asset.
 Through decentralized apps, alternative notions of ownership are possible to define, but this idea of a signing key is foundational and seen in bitcoin, ether, ERC20 tokens, etc.
-(not to mention earlier e-cash proposals dating back to the 1980s).
+(not to mention earlier e-cash proposals dating back to the 1980s~\cite{Swi97,BFS98,KM99}).
 Thus demonstrating knowledge of this key is necessary (but not sufficient, as we will discuss shortly) to demonstrating ownership.
-The most direct technique is to use a zero knowledge proof of knowledge of this private key, and staple in some information identifying the context of the proof.
-For standard proofs, this is cryptographically equivalent to simply signing a challenge message with the key\footnote{A Schnorr Sigma-protocol with the challenge hashed in using Fiat-Shamir is exactly a Schnorr signature and closely related to an ECDSA signature.}.
-Folklore protocols of sending small cash amounts from an allegedly owned account to the auditor to demonstrate control are also commonly noted in the literature.
+The most direct cryptographic technique is to use a zero knowledge proof of knowledge of this private key, and staple in some information identifying the context of the proof.
+For standard proofs, this is cryptographically equivalent to simply signing a challenge message with the key.\footnote{A Schnorr Sigma-protocol with the challenge hashed in using Fiat-Shamir is exactly a Schnorr signature and closely related to an ECDSA signature.} Folklore protocols of sending small cash amounts from an allegedly owned account to the auditor to demonstrate control are also commonly noted in the literature.
 This offers similar security but adds ethical complexities for the auditor.
@@
 A malicious company might arrange for the owner of cryptoassets to engage in signing statements or moving test amounts fraudulently on their behalf.
-This issue is not new: an insolvent retail store might borrow inventory from elsewhere to inflate its assets during an audit, which will, in this case, involve a physical visit and inventory check by the auditor.
+This issue is not new: an insolvent retail store might borrow inventory from elsewhere to inflate its assets during the physical visit and inventory check done when auditing retailers.
 Auditors mitigate this by arranging a common date for all audits of physical inventory, and similarly, cryptographic audits might be synchronized on a fixed schedule to prevent the same assets from being counted for different companies in different audits~\cite{dagher2015provisions}.
@@
 %---------+++++++++++++++++++-----------------
-\paragraph{Issue: Design Transparency.} For cryptoassets that are native to a blockchain, like Bitcoin or Ether, ownership is implemented at the protocol level and has been vetted over the lifetime of the blockchain.
+\paragraph{Issue: Design transparency.} For cryptoassets that are native to a blockchain, like bitcoin or ether, ownership is implemented at the protocol level and has been vetted over the lifetime of the blockchain.
 However many assets are created and owned through decentralized apps.
@@
 These mechanics can become complicated.
-For example, the DAO~\cite{jentzsch2016decentralized} maintained ether and two types of tokens (DAO tokens and reward tokens) across four different internal accounts, and holders of DAO tokens could split off balances from these accounts into a new (two tokens, four accounts) DAO, in addition to certain types of withdrawals.
+For example, the DAO~\cite{jentzsch2016decentralized} maintained ether and two types of tokens (DAO tokens and reward tokens) across four different internal accounts, and holders of DAO tokens could split off balances from these accounts into a new (two token-, four account-) DAO, in addition to certain types of withdrawals.
 Establishing ownership requires understanding the internal accounting of the applications maintaining the assets.
@@
 No universal central bank offers rates for currency-like cryptoassets.
-At the time of writing, one Fortune 500 financial firm, CME, offers a daily reference rate for Bitcoin, but not other cryptocurrencies or cryptoassets.
+At the time of writing, one Fortune 500 financial firm, CME, offers a daily reference rate for bitcoin, but not other cryptocurrencies or cryptoassets.
 Without an authoritative reference rate, current market quotes may be considered.
@@
 %---------+++++++++++++++++++-----------------
-\paragraph{Issue: Geographical Variation.} Because cryptoassets(\eg bitcoin) can be moved digitally without any geographic restrictions, it should be the case that any variation in cryptoasset prices across exchanges would be consumed by arbitrageurs.
+\paragraph{Issue: Geographical Variation.} Because cryptoassets (\eg bitcoin) can be moved digitally without any geographic restrictions, it should be the case that any variation in cryptoasset prices across exchanges would be consumed by arbitrageurs.
 However, empirically this is not the case due to fees, settlement delays, and other frictions with exchange services~\cite{KS17}.
@@
 \paragraph{Issue: Fungibility.} Blockchains generally preserve a full transaction record for each (division of a) cryptoasset.
-This may lead to price discrepancies between equal amounts of cryptoassets, where assets with clear provenance might be preferred to assets with long transaction records involving unknown entities and possible fraud, theft, or other issues that might legally encumber the current holder of the asset.
-The materiality of a premium for ``clean'' cryptoassets is an open research question; some markets for fresh bitcoin were announced but never materialized~\cite{moser2014towards}.
+This may lead to price discrepancies between equal amounts of cryptoassets, where assets with clear provenance might be preferred to assets with long transaction records involving unknown entities and possible fraud, theft, or other issues that might legally encumber the current holder of the asset~\cite{moser2014towards}.
+The materiality of a premium for ``clean'' cryptoassets is an open research question; some markets for fresh bitcoin were announced but never materialized.
 
@@
 \paragraph{Issue: Volatility.} Assuming the valuation of cryptoassets can be made, it is important to consider how stable this valuation will be over time.
-The cryptoasset with the richest historical data is bitcoin and by any standard measure of volatility, its volatility currently exceeds the most traded currencies and commodities.
-If a firm{'}s balance sheet consists of a large unbalanced\footnote{An exchange service that holds bitcoin on behalf of its users will have the bitcoin listed as both an asset and a liability, thus they are balanced and price movements have no impact on their solvency.} cryptoassets or cryptoliabilities, price movements significantly impact its financial health and even its solvency.
+The cryptoasset with the richest historical data is bitcoin and by any standard measure of volatility, bitcoin's current volatility exceeds most traded currencies and commodities.
+If a firm{'}s balance sheet contains large unbalanced\footnote{An exchange service that holds bitcoin on behalf of its users will have the bitcoin listed as both an asset and a liability, thus they are balanced and price movements have no impact on their solvency.} cryptoassets or cryptoliabilities, price movements significantly impact its financial health and even its solvency.
 A comparable scenario is a financial firm holding exotic, volatile securities or derivatives---in these cases, auditors might ``stress test'' the firm{'}s balance sheet under different valuations.
-Starting with bitcoin and moving to other cryptoassets, researchers should consider procedures for the ``shelf life'' of valuations and realistic stress tests.
+Starting with bitcoin and moving to other cryptoassets, researchers should consider procedures for the ``shelf life'' of valuations and design realistic stress tests.
 
@@
 %---------+++++++++++++++++++-----------------
-\paragraph{Takeaway.} While the valuation of cryptoassets with large trading volumes like Bitcoin and Ether would be fairly straightforward by referring to values in an active market, the valuation of coins with low liquidity may be more difficult.
+\paragraph{Takeaway.} While the valuation of cryptoassets with large trading volumes like bitcoin and ether would be fairly straightforward by referring to values in an active market, the valuation of coins with low liquidity may be more difficult.
 However, by using financial modelling using different assumptions for volatility, this challenge is not insurmountable.
@@
 Has anyone tested it?
-For example, maybe Bitcoin is reliable due to large user base but what about more niche blockchain?
+For example, maybe bitcoin is reliable due to large user base but what about more niche blockchain?
 How can I validate accuracy of mining procedures?
@@
 External to the firm, the DAO application maintaining these tokens on Ethereum{'}s blockchain must itself be secure (which in the case of the DAO, it was not~\cite{dupont2017experiments}).
-Auditing internal procedures over cryptographic keys is not unprecedented---maintaining certificate authority keys is critical to some security firm{'}s financial prospects (a security breach at one firm, \textit{DigiNotar} led to its bankruptcy ~\cite{zetter2011diginotar}).
+Auditing internal procedures over cryptographic keys is not unprecedented---maintaining certificate authority keys for HTTPS is critical to some security firm{'}s financial prospects (a security breach at one firm, \textit{DigiNotar} led to its bankruptcy ~\cite{zetter2011diginotar}).
 Symantec{'}s self-custodianship over these keys involves elaborate security ceremonies whenever they are required~\cite{Goo12}.
@@
 \paragraph{Issue: Forks and Airdrops.} Existing accounting standards do not contemplate how to account for non-reciprocal transfers of assets like in the case of forks or airdrops.
-For example, in August 2017, when a hard fork created Bitcoin Cash from Bitcoin, holders of Bitcoin had two types of assets on hand.
+For example, in August 2017, when a hard fork created Bitcoin Cash from bitcoin, holders of bitcoin had two types of assets on hand.
 Bitcoin Cash was not paid for but resulted from a split between the two cryptocurrencies.
@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-\section{Discussion and Research Agenda}
+\section{Discussion}
 
@@
 
-From our discussions with practitioners, existence, valuation and ownership were often cited as the three main stumbling blocks to providing an audit opinion.
-However, we argue that these issues are not insurmountable if industry guidelines are put into place to allow auditors to verify their client’s cryptographic keys against a “state of the world” at a generally accepted point in time.
-Verifying existence and ownership largely hinges on an auditor’s ability to verify the contents of a client’s cryptographic keys.
+From our discussions with practitioners, the three most cited stumbling blocks to providing an audit opinion were existence, valuation and ownership.
+However, we argue that these issues are not insurmountable if industry guidelines are put into place to allow auditors to verify their client's cryptographic keys against a `state of the world' at a generally accepted point in time.
+Verifying existence and ownership largely hinges on an auditor'۪s ability to verify the possession of cryptographic keys.
 However, the auditor must be certain that these keys in fact belong to the client and do not simply represent access to an account.
-Once ownership has been proven, the auditor can rely on the immutable properties of the blockchain to verify existence as the blockchain provides the entire record of transactions since the blockchain’s inception.
+Once ownership has been proven, the auditor can rely on the immutable properties of the blockchain to verify existence as the blockchain provides the entire record of transactions since the blockchain's inception.
 The issue of key sharing is important but is not unlike a situation in the real world where a related party could give the entity under audit a large sum of cash to hold at year end and report on their financial statement to buoy their financial performance.
-
-Volatility does complicate the valuation of alt-coins and other coins with low trading volumes.
+Volatility complicates the valuation of alt-coins and other coins with low trading volumes.
 However, many other exotic securities exist where accountants rely on complex financial modelling to determine a price.

### 2018-09-26 frontrunning/Latex/sections/paper.tex
[frontrunning] final round til section 4

@@
 
-\emph{Front-running} is a course of action where someone benefits from early access to market information about upcoming transactions and trades, typically because of a privileged position along the transmission of this information.
-The problem can occur in both financial and non-financial systems.
+\emph{Front-running} is a course of action where someone benefits from early access to market information about upcoming transactions and trades, typically because of a privileged position along the transmission of this information and is applicable to both financial and non-financial systems.
 In traditional stock exchanges, floor traders might overhear a broker's negotiation with her client over a large purchase, and literally race the broker to buy first, potentially profiting when the large sale temporarily reduces the supply of the stock.
@@
 In 2002, the rule was expanded to cover all security futures~\cite{finra_2002}.
-In 2012, it was expanded further with the new amendment, FINRA Rule 5270, to cover trading in options, derivatives, or other financial instruments overlying a security with only a few exceptions~\cite{sec2012frontrunning, finra_2012}.
+In 2012, it was expanded further with the new amendment, FINRA Rule 5270, to cover trading in options, derivatives, or other financial instruments overlying a security with only a few exceptions~\cite{sec2012frontrunning,finra_2012}.
 
@@
 
-To find example DApps to study, we use the top 25 DApps based on recent user activity from \texttt{DAppradar.com} and sample it in in the first week of September 2018.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} User activity is admittedly an imperfect metric for finding the `most significant' DApps: significant DApps might be lower volume overall or for extended periods of time (\eg ICOs, which we remedy by studying independently in Section~\ref{sec:ICOsfrontrunning}).
+To find example DApps to study, we use the top 25 DApps based on recent user activity from \texttt{DAppradar.com} and sample it in the first week of September 2018\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}}.
+User activity is admittedly an imperfect metric for finding the `most significant' DApps: significant DApps might be lower volume overall or for extended periods of time (\eg ICOs, which we remedy by studying independently in Section~\ref{sec:ICOsfrontrunning}).
 However, user activity is arguably the best objective criteria for which data is readily available, the list captures our intuition about which DApps are significant, and it is at least better than an ad hoc approach.
@@
 
-% talk about velocity that seems to be not front-runnable but because of the liquidity pool limitation, there can be an order that consumes the last chunk of liquidity ``edge case'', to front run others and make their "option calls" fail
-
+% talk about velocity ~\cite{eskandari2017feasibility} that seems to be not front-runnable but because of the liquidity pool limitation, there can be an order that consumes the last chunk of liquidity ``edge case'', to front run others and make their "option calls" fail
 %Tragedy of the commons
-
-% can we talk about Velocity here?
-~\cite{eskandari2017feasibility} As the smart contract is the entity that acts as the market maker on regular cases with high liquidity front-running of the option calls do not result in any advantages, however, in the case of low balance of smart contracts pool of funds, the front-runner can front-run others to use up the remaining of the funds and make the rest of the option calls fail.
+% the smart contract is the entity that acts as the market maker on regular cases with high liquidity front-running of the option calls do not result in any advantages, however, in the case of low balance of smart contracts pool of funds, the front-runner can front-run others to use up the remaining of the funds and make the rest of the option calls fail.
 
@@
 \includegraphics[width=0.7\linewidth]{figures/Miner_reorder_frontrun.png}
-\caption{ The adversarial miner can monitor the Ethereum mempool for decentralized exchange cancel orders and upon seeing the cancellation transaction, he puts his buy order prior to the cancel transaction.
+\caption{ The adversarial miner can monitor the Ethereum mempool for decentral exchange cancel orders and upon seeing the cancellation transaction, he puts his buy order prior to the cancel transaction.
 Doing so, the miner can profit from the underlying trade and also get the gas included in the cancel transaction.
@@
 The first category of DApp in Table~\ref{tab:top25DApps} is exchanges.
-Exchanges such as EtherDelta\footnote{Also known as ForkDelta for the UI \url{https://forkdelta.app/}}, purport to implement a decentralized exchange, however their order books are stored on a central server they control and shown to their users with a website interface.
+Exchanges such as EtherDelta\footnote{Also known as ForkDelta for the UI \url{https://forkdelta.app/}}, purport to implement a decentralized exchange, however, their order books are stored on a central server they control and shown to their users with a website interface.
 Central exchanges can front-run orders in the traditional sense, as well as re-order or block orders on their servers.
 0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the order book holders and could front-run the orders they relay.
-One method of price manipulation on such markets is to flood the market with orders and cancel them when there are filling orders --taker's griefing--, to prevent such attacks, the user needs to send a transaction to cancel each order.
-The reason for canceling order could be the unprofitability of the order due to price change, In this case, when an adversarial actor sees a pending  cancellation transaction, he sends a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled, this is known as \textit{cancellation grief}.
+One method of price manipulation on financial markets is to flood the market with orders and cancel them when there are filling orders --taker's griefing--, to prevent such attacks, the user needs to send a transaction to cancel each of his orders.
+The reason for canceling order could be the unprofitability of the order due to price change.
+In this case, when an adversarial actor sees a pending cancellation transaction, he sends a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled, this is known as \textit{cancellation grief}.
 This is illustrated in Figure~\ref{fig:MinerFrontrunning}.
@@
 \includegraphics[width=0.7\linewidth]{figures/Regular_frontrunning.png}
-\caption{ The Adversary up on seeing the Buy order, sends his own buy order with higher gas to front-run the first order. \label{fig:RegularFrontrunning}} 
+\caption{The Adversary upon seeing the Buy order sends his own buy order with higher gas to front-run the first order. \label{fig:RegularFrontrunning}} 
 \end{figure}
@@
 An adversary can monitor the network with a full node for pending \textit{buy} (or \textit{sell}) transactions which could increase (or \textit{decrease}) the future price of the asset.
-A front-runner can send a competing orders with a higher gas price, and hope to have her transactions mined ahead of the original pending transaction.
+A front-runner can send a competing order with a higher gas price and hope to have her transactions mined ahead of the original pending transaction.
 The benefits of doing this vary.
@@
 If the adversary has pre-existing offers likely to be reached by the market order, she could front-run a cancelation and a new offer at a higher price.
-A simpler attack would be to gauge the demand for trades at a given price by the number of pending orders, and to front-run at the same price in hopes that the market demand is the result of accurate new market information.
+A simpler attack would be to gauge the demand for trades at a given price by the number of pending orders and to front-run at the same price in hopes that the market demand is the result of the accurate new market information.
 Miners are in the best position to conduct these attacks as they hold fine-grained control over the exact set of transactions that will execute and in what order and can mix in their own (late) transactions without broadcasting them.
@@
 Bancor is another DApp that allows users to exchange their tokens without any counter-party risk.
-This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}.
-Smart tokens are ERC20-compatible and can be bought or sold through a DApp-based dealer that is always available and implements a market scoring rule to manage its prices.
-Doing so, Bancor provides continuous liquidity for digital assets without relying on brokers to match buyers with sellers.
+The protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}.
+Smart tokens are ERC20-compatible that can be bought or sold through a DApp-based dealer that is always available and implements a market scoring rule to manage its prices.
+Bancor provides continuous liquidity for digital assets without relying on brokers to match buyers with sellers.
 Implemented on the Ethereum blockchain, when transactions are broadcast to the network, they sit in a pending transaction pool known as \textit{mempool} waiting for the miners to mine them.
@@
 This leaves Bancor vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions, in which they can gain favourable profits by buying before the order and fill the original order with slightly higher price~\cite{BancorIs7:online}.
-Researchers have shown and implemented a proof of concept code to front-run Bancor as a regular non-miner user~\cite{NewTab13:online}.
+Researchers have shown and implemented a proof of concept code to front-run Bancor as a non-miner user~\cite{NewTab13:online}.
 
@@
 The second category of DApp in Table~\ref{tab:top25DApps} is crypto-collectables.
-Consider Cryptokitties,\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}} the most active DApp in this category and third most active overall.
-Each cryptokitty (see Appendix~\ref{app:cryptokitty}) is a cartoon kitten with a set of unique features to distinguish it from other cryptokitties, some features are more rare and harder to obtain.
+Consider Cryptokitties\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}}, the most active DApp in this category and third most active overall.
+Each kitty (see Appendix~\ref{app:cryptokitty}) is a cartoon kitten with a set of unique features to distinguish it from other cryptokitties, some features are rarer and harder to obtain.
 They can be bought, sold, or bred with other cryptokitties.
 At the Ethereum level, the kitty is a token implemented with \textit{ERC-721: Non-Fungible Token Standard}~\cite{erc721}.
-The market cap of cryptokitty tokens peaked at more than 6 million dollars in the first few months their launch, however, has declined since.
-ERC-721 are similar enough to ERC-20 tokens that they can be listed on exchanges setup for ERC-20.
-To buy a cryptokittie, the user sends the following bid transaction: \texttt{bid(uint256 \_tokenId)}.
-It contains the cryptokittty's ID which can be found either on their website or on the ERC721 token smart contract.
-This is similar to open auctions and markets front-running, bid value and the object bidding on is visible to the network and any user could be easily front-run by sending the same transaction with higher gasPrice to replace the initial bidder.
-The front-runner can see there is an interest in an specific cryptokittie and by buying it and auctioning it at higher price can profit from the transaction.
+The market cap of cryptokitties peaked at more than 6 million dollars in the first few months of their launch, however, it has declined since.
+ERC-721 are similar enough to ERC-20 tokens that they can be listed on exchanges that are ERC-20 compatible.
+To buy a kitty, the user sends the following bid transaction: \texttt{bid(uint256 \_tokenId)}.
+It contains the kitty's ID which can be found either on their website or on the ERC721 token smart contract.
+This is similar to open auctions and markets on section~\ref{sec:frontrunningExchanges}, bid value and the object bidding on is visible to the network and any user could  easily front-run by sending the same transaction with higher gasPrice to replace the initial bidder.
+The front-runner can see there is an interest in a specific kitty and by buying it and auctioning it at a higher price can profit from the transaction.
 %we call this auction-frontrunning.
 % https://etherscan.io/tx/0x62a76b7e345e8abd463487d0348c118a9314b197024e090fee7b1fbce434da40
-
-% The blue above needs expansion with further details.
 
@@
 
-%probably needs more work to be good enough. more resources will be out in the coming days!
-
 % Is this the same as order flooding in HFT?
@@
 \textsf{Ethereum Name Service (ENS)}\footnote{\url{https://ens.domains/}} is the most active naming service on Ethereum.
-Instead of allowing new \texttt{.eth} domain names to be purchased directly, they are put up for a sealed bid auction which seals the domain name in the bids, but not the bid amount.
-The common way of getting a domain is to call \texttt{startAuctionsAndBid()} in ENS auction smart contract, which leaks the hash of the domain name and the initial bid amount in the auction.
-Users are allowed to bid for 48 hours before the 48-hour reveal phase begins, in which bidders must send a transaction to reveal their bids for a specific domain in auction.
-It is possible for user to front-run other reveal bids with the same bid amount or slightly higher to outbid the initial sealed bid.
+Instead of allowing new \texttt{.eth} domain names to be purchased directly, they are put up for a sealed bid auction which seals the domain name in the bids, but not the bid amounts.
+The most common way of getting a domain is to call \texttt{startAuctionsAndBid()} in ENS auction smart contract, which leaks the hash of the domain name and the initial bid amount in the auction.
+Users are allowed to bid for 48 hours before the 48-hour reveal phase begins, in which bidders must send a transaction to reveal their bids for a specific domain in the auction.
+It is possible for a user to front-run other bids with the same bid amount by revealing first.
 The auction model is similar to crypto-collectibles auctions in \ref{sec:cryptogames}.

### 2018-09-26 auditing/Latex/sections/01-intro.tex

@@
 The result is not a new protocol but a two-way knowledge transfer between professions.
-While displacing auditors is occasionally a target of cryptographers~\cite{dagher2015provisions,narula2018zkledger}, auditing itself is also occasionally studied directly at venues like Financial Cryptography~\cite{Swi97,BFS98,grigg2000financial}.
+While displacing auditors is occasionally a target of cryptographers~\cite{dagher2015provisions,narula2018zkledger}, auditing itself is also occasionally studied directly~\cite{grigg2000financial} or indirectly~\cite{Swi97,BFS98} at venues like Financial Cryptography.
 
@@
 For blockchains that allow developers to deploy custom decentralized applications, the applications might issue and manage the ownership of custom tokens.
-In the case of ethereum, these tokens are often \textit{ERC20} tokens~\cite{erc20}, where \textit{ERC20} is sometimes misunderstood to mean what the token represents; rather, \textit{ERC20} is a technical standard about how token transactions are invoked.
+In the case of Ethereum, these tokens are often \textit{ERC20} tokens~\cite{erc20}, where \textit{ERC20} is sometimes misunderstood to mean what the token represents; rather, \textit{ERC20} is a technical standard about how token transactions are invoked.
 

### 2018-09-26 frontrunning/Latex/sections/paper.tex
[frontrunning] till section 5

@@
 More than 3000 ICOs have been held on Ethereum, and the market capitalization of these tokens appear to exceed \$75B USD in the first half of 2018~\cite{zetzsche2018ico}.
-At the DApp level, tokens are offered in short term sales that see high transaction activity while the sale is on-going and then ICO activity tappers off to occasional owner transfers.
+At the DApp level, tokens are offered in short-term sales that see high transaction activity while the sale is on-going and then ICO activity tapers off to occasional owner transfers.
 When we collected the top 25 most active DApps on \texttt{DAppRadar.com}, no significant ICOs were in the initial sale stage.
@@
 
-%. Needless to say, the importance of ICOs as an application of blockchain requires more in-depth analysis of front-running on these type of DApps.
-
-%ICOs due to the defined cap is similar to our analogy of a queue line, people would line up to get in and there's an opportunity to front-run.
-
-%Here we focus on one ICO that our preliminary research showed that there might have been a front-running incident.
-There is no doubt that similar behaviour could be seen in other instances of ICOs or similar DApps if investigated.
-
 \subsection{\textit{Status.im} ICO}
-To deal with demand, ICOs will cap sales in a variety of ways to mitigate front-running attacks.
-In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached the predefined cap within 3 hours, resulting in close to 300,000 Ether of funds.
-In order to prevent few large investments to buy up all the tokens and limit the amount of Ether deposited in an investment, they used a `fair' token distribution method they called a \textit{Dynamic Ceiling} as an attempt to increase the opportunity for smaller investors.
-They implemented multiple caps or ceilings in which, each had a maximum amount that could be deposited in.
+To deal with demand, ICOs cap sales in a variety of ways to mitigate front-running attacks.
+In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached the predefined cap within 3 hours, collecting close to 300,000 Ether.
+In order to prevent wealthy investors purchasing all the tokens and limit the amount of Ether deposited in each investment, they used a \textit{fair} token distribution method called \textit{Dynamic Ceiling} as an attempt to increase the opportunity for smaller investors.
+They implemented multiple caps (ceilings) in which, each had a maximum amount that could be deposited in.
 In this case, every deposit was checked by the smart contract and the exceeding amount was refunded to the sender while the accepted amount was sent to their multi-signature wallet address~\cite{statusicoanalysis}.
@@
 According to analysis we carried out, we discovered that the F2Pool---an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure~\ref{fig:mining_pool_ratio})---sent 100 Ether to 30 new Ethereum addresses before the Status.im ICO started.
-When the token sale opened, F2Pool constructed 31 transactions to the ICO token sale smart contract from the addresses these new address, without broadcasting these transactions to the network.
+When the ICO opened, F2Pool constructed 31 transactions to the ICO smart contract from these new address, without broadcasting the transactions to the network.
 They used their entire mining power to mine their own transactions and some other potentially failing high gas price transactions.
@@
 Ethereum's blockchain contains all transaction ever made on Ethereum.
-While the default client and online blockchain explorers offer some limited querying, in order to analyze this case, we built our own database.
-Specifically, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation\url{https://github.com/ethereum/go-ethereum}} for the full node, a python script for extracting, transforming and loading Ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery.\footnote{\url{https://cloud.google.com/bigquery/}} Using this software stack, we were able to isolate transactions within the Status.im ICO sale.
+While the default client and online blockchain explorers offer some limited query capabilities, in order to analyze this case, we built our own database.
+Specifically, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation\url{https://github.com/ethereum/go-ethereum}} for the full node, a python script for extracting, transforming and loading Ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery.\footnote{\url{https://cloud.google.com/bigquery/}} Using this software stack, we were able to isolate transactions within the Status.im ICO.
 We used data analysis tool \texttt{Tableau}.\footnote{\url{https://www.tableau.com/}} A copy of this dataset and the initial findings can be found in our Github repository.\footnote{\url{github.com/} Removed for anonymity.}
@@
 By tracing the transactions from these 30 addresses, we found explicit interference by the F2Pool\footnote{F2Pool Ethereum address was identified by their mining reward deposit address \url{https://etherscan.io/address/0x61c808d82a3ac53231750dadc13c777b59310bd9}} in this scenario.
-As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses were sent to Status.im ICO and mined by F2Pool themselves, where the dynamic ceiling algorithm refunded a portion of the deposited funds back to these addresses, these funds were sent back to F2Pool main address a few days after.
+As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses were sent to Status.im ICO and mined by F2Pool themselves, where the dynamic ceiling algorithm refunded a portion of the deposited funds back to these addresses, these funds were sent back to F2Pool main address a few days after and the tokens were aggregated later on in one single address.
 Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their mining software to behave in a certain way to front-run other transactions and gain monetary profit.

### 2018-09-26 frontrunning/Latex/sections/appendix.tex
[frontrunning] add appendix references
[frontrunning] Done! (I'm done, paper could use more work but... la-di-da)

@@
 
+\section{Appendix}
 \appendix
@@
 
-\section{LocalEthereum} \label{app:code}
+\section{LocalEthereum} \label{app:localethereum}
 
@@
 
-\section{Traditional Front-running Prevention Methods}
+\section{Traditional Front-running Prevention Methods} \label{app:traditionalprevention}
 
@@
 As mentioned in section~\ref{traditionalFrontrunning}, defining front-running and educating the employees were the first step taken to prevent such issues in traditional markets, however, front-running became less likely to happen mainly because of the high fine and lawsuits against firms who behaved in an unethical way.
-Other methods such as dark pools~\cite{zhu2014dark, buti2011diving} and sealed bids~\cite{radner1989sealed} were discussed and implemented in a variety of regulated trading systems.
+Other methods such as dark pools~\cite{zhu2014dark,buti2011diving} and sealed bids~\cite{radner1989sealed} were discussed and implemented in a variety of regulated trading systems.
 The traditional methods to prevent front-running does not apply to blockchain applications, as mainly they are based on central enforcement and limitations, also in case of blockchains the actors who are front-running could be anonymous and the fear of lawsuits would not apply.

### 2018-09-26 frontrunning/Latex/sections/paper.tex
[frontrunning] Done! (I'm done, paper could use more work but... la-di-da)

@@
 After a few hacking incidents of high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered.
-This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to latecomers on the open markets~\cite{zetzsche2018ico, li2018initial}.
+This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to latecomers on the open markets~\cite{zetzsche2018ico,li2018initial}.
 ICOs started to experiment with different \textit{fair} capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}.
@@
 
-Double-spending attacks in Bitcoin have also been studied~\cite{bamert2013have, karame2012double} where a user broadcasts a transaction and is able to obtain some off-blockchain good or service before the transaction has actually been (fully) confirmed.
+Double-spending attacks in Bitcoin have also been studied~\cite{bamert2013have,karame2012double} where a user broadcasts a transaction and is able to obtain some off-blockchain good or service before the transaction has actually been (fully) confirmed.
 The user can then broadcast a competing transaction that sends the same unspent coins to herself, perhaps using higher transaction fees, arrangements with miners or artifacts of the network topology to have the second transaction confirmed instead of the first.
@@
 
-\paragraph{Design Decision \#2:Privacy-Preserving Blockchains.} Privacy-preserving blockchains strive (to some extent~\cite{miller2017empirical, kappos2018empirical}) to keep all details of transactions private, including participants and amounts.
+\paragraph{Design Decision \#2:Privacy-Preserving Blockchains.}
+Privacy-preserving blockchains strive (to some extent~\cite{miller2017empirical,kappos2018empirical}) to keep all details of transactions private, including participants and amounts.
 As an example, ZCash~\cite{hopwood2016zcash} uses two distinct types of addresses, transparent and shielded addresses.
 Transparent addresses work similar to Bitcoin transactions, fully transparent about the sender and receiver addresses, the amount and included data.
-However shielded addresses are private and do not leak any information.
+However, shielded addresses are private and do not leak any information.
 While this solution works for simple transactions, building similar shields for DApps is subject to on-going research~\cite{kosba2016hawk}.
-With the possibility of having private smart contracts in such a setting, it could be feasible to achieve a front-run resistance blockchain, however the functionality of the smart contracts could be limited.
+With the possibility of having private smart contracts in such a setting, it could be feasible to achieve a front-run resistance blockchain, however, the functionality of the smart contracts could be limited.
 
@@
 \paragraph{Design Decision \#3: Dual Authoring.} This scheme is proposed to solve the front-running issue within Loopring -- a decentralized exchange protocol proposed by Wang~\etal~\cite{wang2018loopring}.
-In this protocol, orders are grouped in \emph{ring orders} once they are sent by the users.
-After the required signatures are provided by the ring miner, he sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement (see Figure~\ref{fig:vulnerable_loopring}).
+In the first version of this protocol, orders are grouped in \emph{ring orders} once they are sent by the users.
+After the required signatures are provided by the \textit{ring miner}, he sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement (see Figure~\ref{fig:vulnerable_loopring}).
 While this transaction sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with higher gasPrice and his address instead of the ring miner's address.
-Using the proposed \textit{dual authoring} solution in the new version of Loopring, regeneration of the \emph{submitRing transaction} is challenging as the users have to sign the orders using their secondary private keys (auth-keys), which are only known to the ring miner and not other users (see Figure~\ref{fig:not_vulnerable_loopring}).
+Using the proposed \textit{dual authoring} solution in the new version of Loopring, regeneration of the \emph{submitRing transaction} is infeasible as the users have to sign the orders using their secondary private keys (auth-keys), which are only known to the ring miner and not other users (see Figure~\ref{fig:not_vulnerable_loopring}).
 
@@
 Once the transaction is confirmed and the grace period is over, the user sends a reveal transaction revealing the bid and also the details of the requested domain~\cite{kalodner2015empirical}.
-Hence, user is able to hide information from the adversarial parties in the system and prevent front-running attacks.
+Hence, the user is able to hide information from the adversarial parties in the system and prevent front-running attacks.
 
@@
 
-The participatory factor is another issue for commitment scheme.
+The participatory factor is another issue for the commitment scheme.
 For anyone watching the DApp address, there will be a direct transaction from the user to the DApp address, revealing the fact that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme.
@@
 \paragraph{Design Decision \#2: Submarine Commitments.}\label{submarineCommits}
-Submarine Commitments~\cite{breidenbach2018enter, submarinesendHD} extend basic commit/reveal functionality with additional properties.
+Submarine Commitments~\cite{breidenbach2018enter,submarinesendHD} extend basic commit/reveal functionality with additional properties.
 In particular, they hide the DApp being invoked during the commit phase and also ensure that revealed transactions that send funds are fully collateralized.
@@
 For example when designing a decentralized exchange, one can use a \emph{the call market} design instead of a time-sensitive order book~\cite{clark2014decentralizing} to side-step and disincentivize front-running by miners.
-In a call market design, the arrival time of orders do not matter as they are executed in batches.
+In a call market design, the arrival time of orders does not matter as they are executed in batches.
 
@@
 
-%find a home for localethereum. explain the scenario where this actually works, how it can be front-run in original scenario, how this prevents front-running.
 \item \emph{Trusted party:} It is possible to use a central trusted party, to mitigate the risks of front-running on the DApp design.
-As an example, LocalEthereum, an escrow-based exchange, facilitates the website as the match making service for the exchange orders, and challenge random values from the website to be included in the signature of the transaction (See Code ~\ref{code:localethereum} in Appendix~\ref{app:localethereum}), hence removing any possibility of replay attack or the possibility of any other address modifying key information in the order.
+As an example, LocalEthereum, an escrow-based exchange, facilitates the website as the matchmaking service for the exchange orders, and uses challenge random values from the website to be included in the signature of the transaction (See Code ~\ref{code:localethereum} in Appendix~\ref{app:localethereum}), hence removing any possibility of replay attack or the possibility of any other address modifying key information in the order.
 This method prevents network observers to be able to make a new transaction with the defined values as the third party will be the final entity approving the transaction.

### 2018-09-26 auditing/Latex/main.tex
[auditing] transition to Latex. till Section 3
Audit clean up
More draft-like (needs ack from JMSB people)

--- 2018-05-28 frontrunning/Latex/main.tex
@@
 \input{setup/macros}
-\input{setup/table}
-
+\usepackage{draftwatermark}
+\SetWatermarkAngle{90}
+\SetWatermarkHorCenter{0.2\textwidth}
+\SetWatermarkColor{blue}
+\SetWatermarkText{Working Draft}
 % = = = = = Title = = = = = %
@@
 
-\title{\Large \bf Frontrunning}
-%\author{}
+\title{\Large \bf A first look at auditing in a blockchain world}
 
-%\author{}
-\institute{Concordia University}
+\author{
+	Erica Pimentel\inst{1},
+	Emilio Boulianne\inst{1},
+	Shayan Eskandari\inst{2},
+	Jeremy Clark\inst{2}
+	}
+
+\institute{
+	\textsuperscript{1} John Molson School of Business,
+	\textsuperscript{2} Gina Cody School of Engineering and Computer Science\\ Concordia University
+	}
 
@@
 
-\input{sections/abstract}
+\input{sections/00-abstract}
 
@@
 
-\input{sections/paper}
+\input{sections/01-intro}
+\input{sections/02-body}
 
@@
 
-\bibliography{bib/Frontrunning_Ref}
+\section{Acknowledgements}
+
+The authors thank the Autorit\'e des March\'es Financiers (AMF) for sponsoring this research through the Education and Good Governance Fund (EGGF).
+
+% = = = = = Bibliography = = = = = %
+
+\bibliography{bib/auditing}
 %\nocite{*}

### 2018-09-28 frontrunning/Latex/sections/paper.tex
[frontrunning] add 0x review citation

@@
 0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the order book holders and could front-run the orders they relay.
-One method of price manipulation on financial markets is to flood the market with orders and cancel them when there are filling orders --taker's griefing--, to prevent such attacks, the user needs to send a transaction to cancel each of his orders.
+One method of price manipulation on financial markets is to flood the market with orders and cancel them when there are filling orders --taker's griefing--~\cite{consesnsys0xReview2017}, to prevent such attacks, the user needs to send a transaction to cancel each of his orders.
 The reason for canceling order could be the unprofitability of the order due to price change.

### 2018-09-28 frontrunning/Latex/main.tex
[frontrunning] more fixes, separate appendix from main
ack

--- 2018-05-28 frontrunning/Latex/main.tex
@@
 \input{setup/macros}
-\input{setup/table}
+
+\usepackage{draftwatermark}
+\SetWatermarkAngle{90}
+\SetWatermarkHorCenter{0.2\textwidth}
+\SetWatermarkColor{blue}
+\SetWatermarkText{Working Draft}
 
@@
 
-\title{\Large \bf Frontrunning}
-%\author{}
+\title{The paper on blockchain front-running}
+\author{Shayan Eskandari, Seyedehmahsa Moosavi, \and Jeremy Clark}
 
-%\author{}
-\institute{Concordia University}
+\institute{
+	Gina Cody School of Engineering and Computer Science\\ Concordia University
+	}
 
@@
 
+% = = = = = Ack = = = = = %
+
+\subsubsection*{Acknowledgements.}
+The authors thank the Autorit\'e des March\'es Financiers (AMF) for sponsoring this research through the Education and Good Governance Fund (EGGF), as well as NSERC through a Discovery Grant.
+
 % = = = = = Bibliography = = = = = %
 
+\clearpage
 \bibliography{bib/Frontrunning_Ref}
@@
 
-\clearpage
-\appendix
+\input{sections/appendix}
 

### 2018-11-30 frontrunning/Latex/sections/paper.tex
ack
[Front-running] Update tentative title, add solution mindmap, remove loopring figures

@@
 
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.9\linewidth]{figures/solutions_mindmap.png}
+\caption{ \emph{Solutions Mindmap}  \label{fig:solutions_mindmap.png}}
+\end{figure}
+%https://drive.mindmup.com/map/1u27BpAgU2CVy4BUf33cTRsOzJ01W3Gl2
+
 There are two main approaches to mitigating front-running on blockchains: one is to design a blockchain that is front-run resistant, and the other to design the application logic in a way that front-running is not profitable.
@@
 
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.9\linewidth]{figures/Vulnerable_Loopring.png}
-\caption{ \emph{submitRing} Transaction in the old version of the Loopring protocol.
+%\begin{figure}[t]
+%\centering
+%\includegraphics[width=0.9\linewidth]{figures/Vulnerable_Loopring.png}
+%\caption{ \emph{submitRing} Transaction in the old version of the Loopring protocol.
 Any user can regenerate this transaction by replacing the miner's address with his address and signing the hash of the ring using his private key.
 \label{fig:vulnerable_loopring}}
-\end{figure}
+%\end{figure}
 %https://www.lucidchart.com/invitations/accept/33d38ce9-4660-4743-806d-45c72f7e8393
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.7\linewidth]{figures/Dual_Authoring_Loopring.png}
-\caption{ \emph{submitRing} Transaction in the new version of the Loopring protocol.
+%\begin{figure}[t]
+%\centering
+%\includegraphics[width=0.7\linewidth]{figures/Dual_Authoring_Loopring.png}
+%\caption{ \emph{submitRing} Transaction in the new version of the Loopring protocol.
 Other users cannot regenerate this transaction as they do not access auth-keys and hence are not able to create the signatures.
 \label{fig:not_vulnerable_loopring}}
-\end{figure}
+%\end{figure}
 %https://www.lucidchart.com/invitations/accept/8dee869c-482c-433f-a901-8d041a1dc526
@@
 % Could talk about future work on a tool / a framework to detect front-running
-
-%\subsubsection*{Acknowledgements.}

### 2018-12-05 frontrunning/Latex/sections/abstract.tex
[frontrunning] few edits here and there

@@
 With the advent of the blockchain technology, front-running resurfaced in new forms we explore here, due to blockchain's decentralized and transparent nature.
-In this paper, we consider instances of front-running across the top 25 decentral applications (DApps) deployed on Ethereum.
+In this paper, we draw from a scattered body of knowledge and instances of front-running across the top 25 decentral applications (DApps) deployed on Ethereum.
 Additionally, we carry out a detailed analysis of \textsf{Status.im} initial coin offering (ICO) and show evidence of abnormal miner's behaviour indicative of front-running token purchases.
+Developers don't have the mindset to design DApps with front-running in mind.
+This is an attempt to bring forward the subject and make them more aware of these type of attacks.
 Finally, we introduce a framework for categorizing proposed solutions to front-running and examine the applicability to the identified issues.
-
 \end{abstract}

### 2018-12-05 frontrunning/Latex/sections/paper.tex
[frontrunning] few edits here and there

@@
 Therefore, DApps need to be studied individually or in categories.
-This paper is a series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps) from each category of the top 25 most active, based on user activity.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} We do case studies on decentralized exchanges (\eg Bancor), crypto-collectibles (\eg CryptoKitties), gambling services (\eg Fomo3D), and decentralized name services (\eg Ethereum Name Service).
+In this paper we draw from a scattered body of knowledge regarding front-running attacks on blockchain applications and proposed solutions, with series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps) from each category of the top 25 most active, based on user activity.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} We do case studies on decentralized exchanges (\eg Bancor), crypto-collectibles (\eg CryptoKitties), gambling services (\eg Fomo3D), and decentralized name services (\eg Ethereum Name Service).
 We also study initial coin offerings (ICOs), which by happenstance, did not appear in the top 25 on our sample day.
@@
 In 2012, it was expanded further with the new amendment, FINRA Rule 5270, to cover trading in options, derivatives, or other financial instruments overlying a security with only a few exceptions~\cite{sec2012frontrunning,finra_2012}.
+
+% we can say other illegal activities in the tranditional system, such as wash trading, ...
+(notes from AMF) could fall under our definition of front running on blockchain apps, as the transparency and public nature of the transactions could result in any actor to be involved in such trades?
+does it make sense?
 

### 2018-12-05 frontrunning/Latex/sections/paper.tex
[frontrunning] Bitcoin cash transaction ordering

@@
 This is a theoretical solution and is not trivial to implement in the current Byzantine consensus protocols.
+An implementation of fixed transaction ordering is Canonical Transaction Ordering Rule (CTOR) introduced in November 2018 fork of Bitcoin cash, which indicates an order in which blocks are valid based on the order of the transactions in them; coinbase first, then ascending lexicographic order based on transaction ID~\cite{bitcoinABC2018CTOR}.
+This solution can potentially mitigate the re-ordering attack by miners, however it does not prevent it fully.
 

### 2018-12-05 frontrunning/Latex/sections/paper.tex
[frontrunning] minor changes

--- 2018-12-05 frontrunning/Latex/sections/paper.tex
@@
 \centering
-\includegraphics[width=0.9\linewidth]{figures/Transactions_miners_while_status_ico_cut_only_icotx.png}
+\includegraphics[width=0.7\linewidth]{figures/Transactions_miners_while_status_ico_cut_only_icotx.png}
 \caption{ This chart shows the miners behaviour on the time window that Status.im ICO was running.
@@
 \centering
-\includegraphics[width=0.7\linewidth]{figures/F2Pool_transactions_to_StatusICO_and_Refunds.png}
+\includegraphics[width=0.6\linewidth]{figures/F2Pool_transactions_to_StatusICO_and_Refunds.png}
 \caption{ F2Pool prior to Status.im ICO deposited 100 Ether in multiple new Ethereum addresses.
@@
 \centering
-\includegraphics[width=0.9\linewidth]{figures/solutions_mindmap.png}
+\includegraphics[width=0.7\linewidth]{figures/solutions_mindmap.png}
 \caption{ \emph{Solutions Mindmap}  \label{fig:solutions_mindmap.png}}
@@
 This is a theoretical solution and is not trivial to implement in the current Byzantine consensus protocols.
+An implementation of fixed transaction ordering is Canonical Transaction Ordering Rule (CTOR) introduced in November 2018 fork of Bitcoin cash, which indicates an order in which blocks are valid based on the order of the transactions in them; coinbase first, then ascending lexicographic order based on transaction hash~\cite{bitcoinABC2018CTOR}.
+This solution can potentially mitigate the re-ordering attack by miners, however it does not prevent it fully.
+%NOTE: the two solutions above are both on the transaction ordering, however Silva's solution requires a logical timestamp, and CTOR uses sorting based on transaction hash.
 

### 2018-12-06 frontrunning/Latex/sections/paper.tex
[frontrunning] reorganize solutions

@@
 Finally, proposals to eliminate or mitigate front-running from DApps are scattered across forums, proposed standards (called EIPs in Ethereum) and academic papers; we systemize them in the last section.
+
+% Developers don't have the mindset to design DApps with front-running in mind. This is an attempt to bring forward the subject and make them more aware of these type of attacks
 
@@
 
-\section{How to stop Front-running?} %We have the applicability of the solutions inline.
+\section{Key Mitigations} %We have the applicability of the solutions inline.
 
@@
 
-There are two main approaches to mitigating front-running on blockchains: one is to design a blockchain that is front-run resistant, and the other to design the application logic in a way that front-running is not profitable.
+We encounter a number of main approaches to mitigate front-running attacks on blockchains: we summerize the main approaches.
+
+one is to design a blockchain that is front-run resistant, and the other to design the application logic in a way that front-running is not profitable.
 This can be done in addition to any legal remedies that might be enforceable (See Appendix ~\ref{app:traditionalprevention}).
@@
 
-\subsection{Front-Running Resistant Blockchains}
 In this section, we describe the potential solutions using which, one can design and implement a decentralized application that is resistant to front-running.
 Note that, the existing technical difficulties make these solutions hard to achieve as it requires designers to test edge case scenarios.
+
+%\subsection{Front-Running Resistant Blockchains}
+\subsection{Transaction Queue}
 
@@
 %NOTE: the two solutions above are both on the transaction ordering, however Silva's solution requires a logical timestamp, and CTOR uses sorting based on transaction hash.
+
+\subsection{Confidentiality}
 
@@
 With the possibility of having private smart contracts in such a setting, it could be feasible to achieve a front-run resistance blockchain, however, the functionality of the smart contracts could be limited.
-
-%\begin{figure}[t]
-%\centering
-%\includegraphics[width=0.9\linewidth]{figures/Vulnerable_Loopring.png}
-%\caption{ \emph{submitRing} Transaction in the old version of the Loopring protocol.
-Any user can regenerate this transaction by replacing the miner's address with his address and signing the hash of the ring using his private key.
-\label{fig:vulnerable_loopring}}
-%\end{figure}
-%https://www.lucidchart.com/invitations/accept/33d38ce9-4660-4743-806d-45c72f7e8393
-%\begin{figure}[t]
-%\centering
-%\includegraphics[width=0.7\linewidth]{figures/Dual_Authoring_Loopring.png}
-%\caption{ \emph{submitRing} Transaction in the new version of the Loopring protocol.
-Other users cannot regenerate this transaction as they do not access auth-keys and hence are not able to create the signatures.
-\label{fig:not_vulnerable_loopring}}
-%\end{figure}
-%https://www.lucidchart.com/invitations/accept/8dee869c-482c-433f-a901-8d041a1dc526
-
-%The first solution was to prevent front-running, but then it was attacked so they updated the solution. this new solution also could be attacked. 
-\paragraph{Design Decision \#3: Dual Authoring.} This scheme is proposed to solve the front-running issue within Loopring -- a decentralized exchange protocol proposed by Wang~\etal~\cite{wang2018loopring}.
-In the first version of this protocol, orders are grouped in \emph{ring orders} once they are sent by the users.
-After the required signatures are provided by the \textit{ring miner}, he sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement (see Figure~\ref{fig:vulnerable_loopring}).
-While this transaction sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with higher gasPrice and his address instead of the ring miner's address.
-Using the proposed \textit{dual authoring} solution in the new version of Loopring, regeneration of the \emph{submitRing transaction} is infeasible as the users have to sign the orders using their secondary private keys (auth-keys), which are only known to the ring miner and not other users (see Figure~\ref{fig:not_vulnerable_loopring}).
-
-% Loopring protocol is proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}.
-In this protocol, the orders are grouped in \emph{ring orders} immediately after they are sent by the users.
-Next, the required signatures are provided by a miner and owner of the order, see Figure~\ref{fig:vulnerable_loopring}.
-Eventually, the ring miner sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement.
-While the \emph{submitRing transaction} sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with his address instead of the ring miner's address and then sign the hash of the ring using his own private key.
-By paying a higher gasPrice, block miners choose the front-runner's transaction instead of the original \emph{submitRing transaction}.
-%To solve this issue, the new version of Loopring protocol uses the \emph{dual-authoring} scheme.
-This solution sets two levels of authorization for orders - one for settlement, and one for order matching.
-As it can be seen in Figure~\ref{fig:not_vulnerable_loopring}, each owner of an order generates a pair of public key (auth-address) and private key (auth-key), which are different from his address and its corresponding private key.
-These auth-keys are used to sign the hash of the ring and will further prevent anyone from regenerating the same \emph{submitRing transaction}.
-The reason is that the auth-keys are only known to the miner of the ring as they are not part of the on-chain transaction.
-Doing so, it is assured that (i) the orders are not modified because they are signed by the owner, (ii) no other miner can mine the ring because the miner's address is signed by the initial miner, and (iii) no user can front-run the \emph{submitRing transaction} because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them.
-
-% = = =
-
-\subsection{Application Design to Prevent Front-running}
-
-Front-running can be tackled at the blockchain layer, as seen in the previous section, or mitigations can be built at the DApp level as seen here.
 
@@
 
+%\begin{figure}[t]
+%\centering
+%\includegraphics[width=0.9\linewidth]{figures/Vulnerable_Loopring.png}
+%\caption{ \emph{submitRing} Transaction in the old version of the Loopring protocol.
+Any user can regenerate this transaction by replacing the miner's address with his address and signing the hash of the ring using his private key.
+\label{fig:vulnerable_loopring}}
+%\end{figure}
+%https://www.lucidchart.com/invitations/accept/33d38ce9-4660-4743-806d-45c72f7e8393
+%\begin{figure}[t]
+%\centering
+%\includegraphics[width=0.7\linewidth]{figures/Dual_Authoring_Loopring.png}
+%\caption{ \emph{submitRing} Transaction in the new version of the Loopring protocol.
+Other users cannot regenerate this transaction as they do not access auth-keys and hence are not able to create the signatures.
+\label{fig:not_vulnerable_loopring}}
+%\end{figure}
+%https://www.lucidchart.com/invitations/accept/8dee869c-482c-433f-a901-8d041a1dc526
+
+%The first solution was to prevent front-running, but then it was attacked so they updated the solution. this new solution also could be attacked.
+
+\subsection{Design Practices}
+
 \paragraph{Design Decision \#3: Use-Case Specific Solutions.}
@@
 
+\paragraph{Design Decision \#3: Dual Authoring.} This scheme is proposed to solve the front-running issue within Loopring -- a decentralized exchange protocol proposed by Wang~\etal~\cite{wang2018loopring}.
+In the first version of this protocol, orders are grouped in \emph{ring orders} once they are sent by the users.
+After the required signatures are provided by the \textit{ring miner}, he sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement (see Figure~\ref{fig:vulnerable_loopring}).
+While this transaction sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with higher gasPrice and his address instead of the ring miner's address.
+Using the proposed \textit{dual authoring} solution in the new version of Loopring, regeneration of the \emph{submitRing transaction} is infeasible as the users have to sign the orders using their secondary private keys (auth-keys), which are only known to the ring miner and not other users (see Figure~\ref{fig:not_vulnerable_loopring}).
+
+% Loopring protocol is proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}.
+In this protocol, the orders are grouped in \emph{ring orders} immediately after they are sent by the users.
+Next, the required signatures are provided by a miner and owner of the order, see Figure~\ref{fig:vulnerable_loopring}.
+Eventually, the ring miner sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement.
+While the \emph{submitRing transaction} sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with his address instead of the ring miner's address and then sign the hash of the ring using his own private key.
+By paying a higher gasPrice, block miners choose the front-runner's transaction instead of the original \emph{submitRing transaction}.
+%To solve this issue, the new version of Loopring protocol uses the \emph{dual-authoring} scheme.
+This solution sets two levels of authorization for orders - one for settlement, and one for order matching.
+As it can be seen in Figure~\ref{fig:not_vulnerable_loopring}, each owner of an order generates a pair of public key (auth-address) and private key (auth-key), which are different from his address and its corresponding private key.
+These auth-keys are used to sign the hash of the ring and will further prevent anyone from regenerating the same \emph{submitRing transaction}.
+The reason is that the auth-keys are only known to the miner of the ring as they are not part of the on-chain transaction.
+Doing so, it is assured that (i) the orders are not modified because they are signed by the owner, (ii) no other miner can mine the ring because the miner's address is signed by the initial miner, and (iii) no user can front-run the \emph{submitRing transaction} because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them.
+
+% = = =
+
+%\subsection{Application Design to Prevent Front-running}
+%
+%Front-running can be tackled at the blockchain layer, as seen in the previous section, or mitigations can be built at the DApp level as seen here.
+
 % = = = = = = = = = = = = = = = = = = = = = = = = = = %

### 2018-12-06 auditing/Latex/main.tex
ack
changes

@@
 
-\section{Acknowledgements}
+\subsection*{Acknowledgements}
 
 The authors thank the Autorit\'e des March\'es Financiers (AMF) for sponsoring this research through the Education and Good Governance Fund (EGGF).
+Additionally the first author acknowledges funding from SSHRC, the second author from the Manulife Professorship in Financial Planning at JMSB, and the fourth author from an NSERC Discovery Grant.
+The paper was greatly improved by feedback from \ldots TBD.
+The information, opinions and advice presented in this paper are the sole responsibility of the authors.
 
-% = = = = = Bibliography = = = = = %
+% = = = = = Bibliography = = = = =
 

### 2018-12-06 frontrunning/Latex/sections/paper.tex
changes

@@
 
-We encounter a number of main approaches to mitigate front-running attacks on blockchains: we summerize the main approaches.
+As we studied front-running attacks on blockchain, we also encountered a number of ways of preventing, detecting, or mitigating front-running attacks.
+Instead of providing the details of exact solutions which will change over time, we extract the main principles or primitives that address the attack.
+A particular system may implement more in a layered mitigation approach.
 
-one is to design a blockchain that is front-run resistant, and the other to design the application logic in a way that front-running is not profitable.
-This can be done in addition to any legal remedies that might be enforceable (See Appendix ~\ref{app:traditionalprevention}).
-We note, but consider out-of-scope, approaches that introduce trusted parties to centralize time-sensitive functionalities (\eg exchanges \textit{EtherDelta} and \textit{0xProject} use off-chain order books~\cite{warren20170x,0xfrontrunning:online}).
+We classify the mitigations into three main categories.
+In the first category, the blockchain removes the miner's ability to arbitrarily order transactions and tries to enforce some ordering, or queue, for the transactions.
+In the second category, cryptographic techniques are used to limit the visibility of transactions, giving the potential front-running less information to base their strategy on.
+In the final category, dapps are designed from the bottom-up to remove the importance of transaction ordering or time in their operations.
 
-% = = =
-
-In this section, we describe the potential solutions using which, one can design and implement a decentralized application that is resistant to front-running.
-Note that, the existing technical difficulties make these solutions hard to achieve as it requires designers to test edge case scenarios.
+We also note that for dapps that are legally well-formed (\eg with identified parties and a clear jurisdiction), front-running attacks can violate laws, which is its own deterrent.
+We do not discuss this further here; see Appendix ~\ref{app:traditionalprevention}.
 
@@
 
-\paragraph{Design Decision \#1: Fixed Transaction Ordering.} da Silva~\etal~\cite{fixedordering2018silva} proposes an algorithm, known as Fixed Transaction Ordering and Admission (FTOA), in the consensus protocol that enforces the order of the transactions in the mined blocks, using logical timestamps in a Byzantine setting, to eliminate transaction reordering by miners.
+% Jeremy: to do
+
+Transaction chaining -> resolve conflicts -> topological order/sort (also consider total order) -> cf UTXOs
+
+FIFO -> consensus on FI -> possible in theory
+-> could be solved with TTP -> censorship still possible (completeness issue)
+
+FI_O -> FIRO -> deterministic random order -> manipulatable (malleability in the collection and your own items in the collection and maybe and other items in the collection) -> CTOR
+
+%\paragraph{Design Decision \#1: Fixed Transaction Ordering.} da Silva~\etal~\cite{fixedordering2018silva} proposes an algorithm, known as Fixed Transaction Ordering and Admission (FTOA), in the consensus protocol that enforces the order of the transactions in the mined blocks, using logical timestamps in a Byzantine setting, to eliminate transaction reordering by miners.
 This is a theoretical solution and is not trivial to implement in the current Byzantine consensus protocols.
+
 An implementation of fixed transaction ordering is Canonical Transaction Ordering Rule (CTOR) introduced in November 2018 fork of Bitcoin cash, which indicates an order in which blocks are valid based on the order of the transactions in them; coinbase first, then ascending lexicographic order based on transaction hash~\cite{bitcoinABC2018CTOR}.
@@
 
+We note, but consider out-of-scope, approaches that introduce trusted parties to centralize time-sensitive functionalities (\eg exchanges \textit{EtherDelta} and \textit{0xProject} use off-chain order books~\cite{warren20170x,0xfrontrunning:online}).
+
 % Loopring protocol is proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}.

### 2018-12-07 frontrunning/Latex/sections/paper.tex
tod written

@@
 In the final category, dapps are designed from the bottom-up to remove the importance of transaction ordering or time in their operations.
-
 We also note that for dapps that are legally well-formed (\eg with identified parties and a clear jurisdiction), front-running attacks can violate laws, which is its own deterrent.
@@
 %\subsection{Front-Running Resistant Blockchains}
-\subsection{Transaction Queue}
+\subsection{Collection Sequencing}
 
-% Jeremy: to do
+Miners on Ethereum store pending transactions in a pool and draw from them when forming a block.
+As the term `pool' implies, there is no instinct order to how transactions are drawn from the pool and miners are free to sequence them arbitrarily.\footnote{Sometimes the pool is called a `queue.' It is important to note is a misnomer as queues use a first-in-first-out sequence.} This enables certain kinds of front-running, in particular transactions the miner will place before a pending transaction.
+A number of proposals attempt to thwart this attack by enforcing a rule about how to sequence transactions.
 
-Transaction chaining -> resolve conflicts -> topological order/sort (also consider total order) -> cf UTXOs
+First-in-first-out (FIFO) is generally not possible on a distributed network because transactions can reach different nodes in a different order.
+While the network could form a consensus based on locally observed FIFO, but this would increase the rate of orphaned blocks, as well as adding complexity to the protocol.
+A trusted third party could be used to assign sequential numbers to transactions (and sign them), but this is contrary to the blockchain's core innovation of distributed trust.
 
-FIFO -> consensus on FI -> possible in theory
--> could be solved with TTP -> censorship still possible (completeness issue)
+An alternative is to sequence transactions psuedorandomly.
+This can be seen in proposals like Canonical Transaction Ordering Rule (CTOR) in Bitcoin cash which adds transactions in lexicographical order according to their hash~\cite{bitcoinABC2018CTOR}.
+Note that Bitcoin cash does not have a front-running problem for most standard transactions.
+While this could be used by Ethereum to make front-running statistically difficult, the protection is marginal at best and might even exacerbate attacks.
+A front-runner can construct multiple equivalent transactions, with slightly different values, until she finds a candidate that positions her transaction a desirable location in the resulting sequence.
+She broadcasts only this transaction and now miners that include her transaction will position in front of transactions they heard about much earlier.
 
-FI_O -> FIRO -> deterministic random order -> manipulatable (malleability in the collection and your own items in the collection and maybe and other items in the collection) -> CTOR
+Finally, transactions themselves could enforce order.
+In particular, they could point to the current state of the contract and only execute on that exact state.
+This transaction chaining only prevents certain sub-types of front-running.
+For example, it could prevent scalping attacks: if Alice buys from a marketplace that matches her order to Bob with a price improvement, a miner could buy from Bob first and then execute Alice's original transaction which results in her being matched to Alice instead.
+Alternatively, if Alice registers an interesting-looking domain name, transaction chaining does not stop a miner from replacing Alice's request with her own.
+Transaction chaining would likely lead to more orphaned transactions for active contracts, as only one state-changing transaction would be allowed per state.
 
@@
 
-An implementation of fixed transaction ordering is Canonical Transaction Ordering Rule (CTOR) introduced in November 2018 fork of Bitcoin cash, which indicates an order in which blocks are valid based on the order of the transactions in them; coinbase first, then ascending lexicographic order based on transaction hash~\cite{bitcoinABC2018CTOR}.
+%An implementation of fixed transaction ordering is Canonical Transaction Ordering Rule (CTOR) introduced in November 2018 fork of Bitcoin cash, which indicates an order in which blocks are valid based on the order of the transactions in them; coinbase first, then ascending lexicographic order based on transaction hash~\cite{bitcoinABC2018CTOR}.
 This solution can potentially mitigate the re-ordering attack by miners, however it does not prevent it fully.

### 2018-12-07 frontrunning/Latex/main.tex
[Front-running] Update tentative title, add solution mindmap, remove loopring figures
changes
some more edits

@@
 
-\usepackage{draftwatermark}
-\SetWatermarkAngle{90}
-\SetWatermarkHorCenter{0.2\textwidth}
-\SetWatermarkColor{blue}
-\SetWatermarkText{Working Draft}
+%\usepackage{draftwatermark}
+%\SetWatermarkAngle{90}
+%\SetWatermarkHorCenter{0.2\textwidth}
+%\SetWatermarkColor{blue}
+%\SetWatermarkText{Working Draft}
 
@@
 
-\title{The paper on blockchain front-running}
-\author{Shayan Eskandari, Seyedehmahsa Moosavi, \and Jeremy Clark}
-
-\institute{
-	Gina Cody School of Engineering and Computer Science\\ Concordia University
-	}
-
+\title{SoK: Transparent Dishonesty. Front-running attacks on Blockchain. }
+%\author{Shayan Eskandari, Seyedehmahsa Moosavi, \and Jeremy Clark}
+%\institute{Gina Cody School of Engineering and Computer Science\\ Concordia University}
 \maketitle
@@
 
-\subsubsection*{Acknowledgements.}
-The authors thank the Autorit\'e des March\'es Financiers (AMF) for sponsoring this research through the Education and Good Governance Fund (EGGF), as well as NSERC through a Discovery Grant.
+%\subsubsection*{Acknowledgements.}
+%The authors thank the Autorit\'e des March\'es Financiers (AMF) for sponsoring this research through the Education and Good Governance Fund (EGGF), as well as NSERC through a Discovery Grant.
 

### 2018-12-07 frontrunning/Latex/sections/paper.tex
some more edits

@@
 
-\begin{figure}[t]
-\centering 
-\includegraphics[width=0.7\linewidth]{figures/solutions_mindmap.png}
-\caption{ \emph{Solutions Mindmap}  \label{fig:solutions_mindmap.png}}
-\end{figure}
+%\begin{figure}[t]
+%\centering 
+%\includegraphics[width=0.7\linewidth]{figures/solutions_mindmap.png}
+%\caption{ \emph{Solutions Mindmap}  \label{fig:solutions_mindmap.png}}
+%\end{figure}
 %https://drive.mindmup.com/map/1u27BpAgU2CVy4BUf33cTRsOzJ01W3Gl2
@@
 %\subsection{Front-Running Resistant Blockchains}
-\subsection{Collection Sequencing}
+\subsection{Transaction Sequencing}
 
-Miners on Ethereum store pending transactions in a pool and draw from them when forming a block.
+Ethereum miners store pending transactions in pools and draw from them when forming blocks.
 As the term `pool' implies, there is no instinct order to how transactions are drawn from the pool and miners are free to sequence them arbitrarily.\footnote{Sometimes the pool is called a `queue.' It is important to note is a misnomer as queues use a first-in-first-out sequence.} This enables certain kinds of front-running, in particular transactions the miner will place before a pending transaction.
@@
 First-in-first-out (FIFO) is generally not possible on a distributed network because transactions can reach different nodes in a different order.
-While the network could form a consensus based on locally observed FIFO, but this would increase the rate of orphaned blocks, as well as adding complexity to the protocol.
+While the network could form a consensus based on locally observed FIFO, this would increase the rate of orphaned blocks, as well as adding complexity to the protocol.
 A trusted third party could be used to assign sequential numbers to transactions (and sign them), but this is contrary to the blockchain's core innovation of distributed trust.
+None the less, some exchanges will centralize time-sensitive functionalities (\eg  \textit{EtherDelta} and \textit{0xProject}) in off-chain order books~\cite{warren20170x,0xfrontrunning:online}).
 
@@
 A front-runner can construct multiple equivalent transactions, with slightly different values, until she finds a candidate that positions her transaction a desirable location in the resulting sequence.
-She broadcasts only this transaction and now miners that include her transaction will position in front of transactions they heard about much earlier.
+She broadcasts only this transaction and now miners that include her transaction will position it in front of transactions they heard about much earlier.
 
@@
 For example, it could prevent scalping attacks: if Alice buys from a marketplace that matches her order to Bob with a price improvement, a miner could buy from Bob first and then execute Alice's original transaction which results in her being matched to Alice instead.
-Alternatively, if Alice registers an interesting-looking domain name, transaction chaining does not stop a miner from replacing Alice's request with her own.
+By contrast, if Alice registers an interesting-looking domain name, transaction chaining does not stop a miner from replacing Alice's request with her own.
 Transaction chaining would likely lead to more orphaned transactions for active contracts, as only one state-changing transaction would be allowed per state.
@@
 
-\paragraph{Design Decision \#2:Privacy-Preserving Blockchains.}
-Privacy-preserving blockchains strive (to some extent~\cite{miller2017empirical,kappos2018empirical}) to keep all details of transactions private, including participants and amounts.
+\paragraph{Privacy-Preserving Blockchains.}
+
+All transaction details in Bitcoin are make public and participant identities are only lightly protected.
+A number of techniques increase confidentiality [CT, bulletproofs] and anonymity [zerocoin, monero, etc] for cryptocurrencies.
+A current research direction is extending these protections to DApps.
+It is tempting to think that a confidential DApp would not permit front-running, as the front-runner would not know the details of the transaction she is front-running.
+However there are some nuances here to explore.
+
+A DApp includes the following components: (1) the code of the DApp, (2) the current state of the DApp, (3) the name of a function being invoked, (4) the parameters supplied to the function, and (5) the identity of the sender.
+Confidentiality applied to a DApp could mean different levels of protection for each of these.
+For front-running, function calls (3,4) are the most important, however function calls could be inferred from state changes (2).
+Hawk~\cite{kosba2016hawk} and Eiden [c] are examples of (2,3,4)-confidentiality (with limitations we are glossing over).
+
+The applicability of privacy-preserving blockchains needs to be evaluated on a case-by-case base.
+For example, one method used by traditional financial exchanges in dealing with front-running from high frequency traders is a dark market: essentially a (2,3,4)-confidential order book maintained by a trusted party.
+A DApp could disintermediate this trusted party.
+Users whose balances are effected by changes in the contract's state would need to be able to learn this information.
+As a contrasting example, consider again decentralized domain registration: keeping the state confidential defeats the entire purpose of the DApp.
+Only protecting function calls is ineffective as the state change itself reveals which domain is attempting to be registered.
+
+%Privacy-preserving blockchains strive (to some extent~\cite{miller2017empirical,kappos2018empirical}) to keep all details of transactions private, including participants and amounts.
 As an example, ZCash~\cite{hopwood2016zcash} uses two distinct types of addresses, transparent and shielded addresses.
@@
 However, shielded addresses are private and do not leak any information.
-While this solution works for simple transactions, building similar shields for DApps is subject to on-going research~\cite{kosba2016hawk}.
+While this solution works for simple transactions, building similar shields for DApps is subject to on-going research~\cite{}.
 With the possibility of having private smart contracts in such a setting, it could be feasible to achieve a front-run resistance blockchain, however, the functionality of the smart contracts could be limited.
 
-\paragraph{Design Decision \#1: Commit / Reveal.} \label{CommitmentScheme}
+\paragraph{Commit/Reveal.}
+
+While confidentiality appears insufficient for solving domain name front-running alone, a hybrid approach of sequencing and confidentiality can be effective, and is in fact an example of an older cryptographic trick known as commit/reveal.
+The essence of the approach is to protect the function call, \ie (3,4)-confidentiality, until the function is enqueued in sequence of functions to be executed.
+Once the sequence is finalized, the confidentiality is lifted and the function can only be executed in the place is was given (or, generally speaking, not at all).
+
 A commitment scheme is a cryptographic primitive that enables one to commit to a value (\eg a statement, document, data, \etc) while keeping it a secret, and then open it (and only it) at a later time of the committer's choosing~\cite{brassard1988minimum}.
@@
 
-\paragraph{Design Decision \#2: Submarine Commitments.}\label{submarineCommits}
 Submarine Commitments~\cite{breidenbach2018enter,submarinesendHD} extend basic commit/reveal functionality with additional properties.
@@
 
-%\begin{figure}[t]
-%\centering
-%\includegraphics[width=0.9\linewidth]{figures/Vulnerable_Loopring.png}
-%\caption{ \emph{submitRing} Transaction in the old version of the Loopring protocol.
-Any user can regenerate this transaction by replacing the miner's address with his address and signing the hash of the ring using his private key.
-\label{fig:vulnerable_loopring}}
-%\end{figure}
-%https://www.lucidchart.com/invitations/accept/33d38ce9-4660-4743-806d-45c72f7e8393
-%\begin{figure}[t]
-%\centering
-%\includegraphics[width=0.7\linewidth]{figures/Dual_Authoring_Loopring.png}
-%\caption{ \emph{submitRing} Transaction in the new version of the Loopring protocol.
-Other users cannot regenerate this transaction as they do not access auth-keys and hence are not able to create the signatures.
-\label{fig:not_vulnerable_loopring}}
-%\end{figure}
-%https://www.lucidchart.com/invitations/accept/8dee869c-482c-433f-a901-8d041a1dc526
-
-%The first solution was to prevent front-running, but then it was attacked so they updated the solution. this new solution also could be attacked.
-
 \subsection{Design Practices}
 
-\paragraph{Design Decision \#3: Use-Case Specific Solutions.}
-There is no perfect generic solution to this issue as of now, however, to prevent front-running, one can design the application in a way that it is not possible to be front-run:
+Front-running can be tackled at the blockchain layer, as seen in the previous section, or mitigations can be built at the DApp level as seen here.
 
-\begin{compactlist}
-
-\item \emph{Eliminating Time-Order Dependency:} The applications can be designed not to rely on the time for the orders to be executed.
+The applications can be designed not to rely on the time for the orders to be executed.
 For example when designing a decentralized exchange, one can use a \emph{the call market} design instead of a time-sensitive order book~\cite{clark2014decentralizing} to side-step and disincentivize front-running by miners.
@@
 
-\item \emph{Disincentivizing Front-running Actors:} The call market solution also pivots profitable gains that front-running miners stand to gain into fees that they collect~\cite{clark2014decentralizing}, removing the financial incentive to front-run.
+The call market solution also pivots profitable gains that front-running miners stand to gain into fees that they collect~\cite{clark2014decentralizing}, removing the financial incentive to front-run.
 To the same end, Malinova~\cite{malinova2017market} proposes a design for a decentralized exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable.
 They split big investments into smaller ones using intermediaries --liquidity demander-- and liquidity providers to achieve this.
-
-\item \emph{Trusted party:} It is possible to use a central trusted party, to mitigate the risks of front-running on the DApp design.
-As an example, LocalEthereum, an escrow-based exchange, facilitates the website as the matchmaking service for the exchange orders, and uses challenge random values from the website to be included in the signature of the transaction (See Code ~\ref{code:localethereum} in Appendix~\ref{app:localethereum}), hence removing any possibility of replay attack or the possibility of any other address modifying key information in the order.
-This method prevents network observers to be able to make a new transaction with the defined values as the third party will be the final entity approving the transaction.
- \end{compactlist}
 
@@
 %TODO: inline talk about what these solutions are good for and if they fit Status ICO
-
-\paragraph{Design Decision \#3: Dual Authoring.} This scheme is proposed to solve the front-running issue within Loopring -- a decentralized exchange protocol proposed by Wang~\etal~\cite{wang2018loopring}.
-In the first version of this protocol, orders are grouped in \emph{ring orders} once they are sent by the users.
-After the required signatures are provided by the \textit{ring miner}, he sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement (see Figure~\ref{fig:vulnerable_loopring}).
-While this transaction sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with higher gasPrice and his address instead of the ring miner's address.
-Using the proposed \textit{dual authoring} solution in the new version of Loopring, regeneration of the \emph{submitRing transaction} is infeasible as the users have to sign the orders using their secondary private keys (auth-keys), which are only known to the ring miner and not other users (see Figure~\ref{fig:not_vulnerable_loopring}).
-
-We note, but consider out-of-scope, approaches that introduce trusted parties to centralize time-sensitive functionalities (\eg exchanges \textit{EtherDelta} and \textit{0xProject} use off-chain order books~\cite{warren20170x,0xfrontrunning:online}).
-
-% Loopring protocol is proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}.
-In this protocol, the orders are grouped in \emph{ring orders} immediately after they are sent by the users.
-Next, the required signatures are provided by a miner and owner of the order, see Figure~\ref{fig:vulnerable_loopring}.
-Eventually, the ring miner sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement.
-While the \emph{submitRing transaction} sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with his address instead of the ring miner's address and then sign the hash of the ring using his own private key.
-By paying a higher gasPrice, block miners choose the front-runner's transaction instead of the original \emph{submitRing transaction}.
-%To solve this issue, the new version of Loopring protocol uses the \emph{dual-authoring} scheme.
-This solution sets two levels of authorization for orders - one for settlement, and one for order matching.
-As it can be seen in Figure~\ref{fig:not_vulnerable_loopring}, each owner of an order generates a pair of public key (auth-address) and private key (auth-key), which are different from his address and its corresponding private key.
-These auth-keys are used to sign the hash of the ring and will further prevent anyone from regenerating the same \emph{submitRing transaction}.
-The reason is that the auth-keys are only known to the miner of the ring as they are not part of the on-chain transaction.
-Doing so, it is assured that (i) the orders are not modified because they are signed by the owner, (ii) no other miner can mine the ring because the miner's address is signed by the initial miner, and (iii) no user can front-run the \emph{submitRing transaction} because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them.
-
-% = = =
-
-%\subsection{Application Design to Prevent Front-running}
-%
-%Front-running can be tackled at the blockchain layer, as seen in the previous section, or mitigations can be built at the DApp level as seen here.
 

### 2018-12-07 frontrunning/Latex/sections/paper.tex
[frontrunning] some edits + citations

@@
 Ethereum miners store pending transactions in pools and draw from them when forming blocks.
-As the term `pool' implies, there is no instinct order to how transactions are drawn from the pool and miners are free to sequence them arbitrarily.\footnote{Sometimes the pool is called a `queue.' It is important to note is a misnomer as queues use a first-in-first-out sequence.} This enables certain kinds of front-running, in particular transactions the miner will place before a pending transaction.
+As the term `pool' implies, there is no instinct order to how transactions are drawn from the pool and miners are free to sequence them arbitrarily.\footnote{Sometimes the pool is called a `queue.' It is important to note is a misnomer as queues use a first-in-first-out sequence.} This enables certain kinds of front-running, in particular transactions the miner will place before a pending transaction\footnote{The vanilla Go-Ethereum implementation, prioritizes transactions based on their gas price and nonce~\cite{EthMinerTxOrder}}.
 A number of proposals attempt to thwart this attack by enforcing a rule about how to sequence transactions.
@@
 An alternative is to sequence transactions psuedorandomly.
-This can be seen in proposals like Canonical Transaction Ordering Rule (CTOR) in Bitcoin cash which adds transactions in lexicographical order according to their hash~\cite{bitcoinABC2018CTOR}.
-Note that Bitcoin cash does not have a front-running problem for most standard transactions.
+This can be seen in proposals like Canonical Transaction Ordering Rule (CTOR) by Bitcoin Cash ABC which adds transactions in lexicographical order according to their hash~\cite{bitcoinABC2018CTOR}.
+Note that Bitcoin does not have a front-running problem for most standard transactions.
 While this could be used by Ethereum to make front-running statistically difficult, the protection is marginal at best and might even exacerbate attacks.
@@
 
-%An implementation of fixed transaction ordering is Canonical Transaction Ordering Rule (CTOR) introduced in November 2018 fork of Bitcoin cash, which indicates an order in which blocks are valid based on the order of the transactions in them; coinbase first, then ascending lexicographic order based on transaction hash~\cite{bitcoinABC2018CTOR}.
-This solution can potentially mitigate the re-ordering attack by miners, however it does not prevent it fully.
-%NOTE: the two solutions above are both on the transaction ordering, however Silva's solution requires a logical timestamp, and CTOR uses sorting based on transaction hash.
-
 \subsection{Confidentiality}
@@
 All transaction details in Bitcoin are make public and participant identities are only lightly protected.
-A number of techniques increase confidentiality [CT, bulletproofs] and anonymity [zerocoin, monero, etc] for cryptocurrencies.
+A number of techniques increase confidentiality~\cite{bunzBulletproofs,maxwell2015confidential} and anonymity [zerocoin, monero, etc] for cryptocurrencies.
 A current research direction is extending these protections to DApps.

### 2018-12-08 frontrunning/Latex/sections/paper.tex
more updates

--- 2018-12-07 frontrunning/Latex/sections/paper.tex
@@
 
-A DApp includes the following components: (1) the code of the DApp, (2) the current state of the DApp, (3) the name of a function being invoked, (4) the parameters supplied to the function, and (5) the identity of the sender.
+A DApp includes the following components: (1) the code of the DApp, (2) the current state of the DApp, (3) the name of the function being invoked, (4) the parameters supplied to the function, (5) the address of the contract the function is being invoked on, and (6) the identity of the sender.
 Confidentiality applied to a DApp could mean different levels of protection for each of these.
@@
 Users whose balances are effected by changes in the contract's state would need to be able to learn this information.
-As a contrasting example, consider again decentralized domain registration: keeping the state confidential defeats the entire purpose of the DApp.
-Only protecting function calls is ineffective as the state change itself reveals which domain is attempting to be registered.
+Further, if the contract addresses are known (no 5-confidentiality), front-runners can know about the traffic pattern of calls to contracts which could be sufficient grounds for attack; for example, if each asset on an exchange has its own market contract, this leaks trade volume information.
+As a contrasting example, consider again decentralized domain registration: hiding state changes (2-confidentiality) defeats the entire purpose of the DApp, and protecting function calls is ineffective with a public state change since the state itself reveals the domain being registered.
 
@@
 While confidentiality appears insufficient for solving domain name front-running alone, a hybrid approach of sequencing and confidentiality can be effective, and is in fact an example of an older cryptographic trick known as commit/reveal.
-The essence of the approach is to protect the function call, \ie (3,4)-confidentiality, until the function is enqueued in sequence of functions to be executed.
-Once the sequence is finalized, the confidentiality is lifted and the function can only be executed in the place is was given (or, generally speaking, not at all).
+The essence of the approach is to protect the function call (\eg (3,4)- or (4)-confidentiality) until the function is enqueued in sequence of functions to be executed.
+Once the sequence is established, the confidentiality is lifted and the function can only be executed in the place is was given (or, generally speaking, not at all).
 
-A commitment scheme is a cryptographic primitive that enables one to commit to a value (\eg a statement, document, data, \etc) while keeping it a secret, and then open it (and only it) at a later time of the committer's choosing~\cite{brassard1988minimum}.
-A common approach is to submit the hash value of the data to be committed, potentially with a random nonce (for predictable data), to a smart contract and later reveal the original data and nonce which can be verified to hash to the commitment.
-See Figure~\ref{fig:commitReveal} in Appendix~\ref{app:cr}.
+Recall that a commitment scheme enables one to commit to a digital value (\eg a statement, transaction, data, \etc) while keeping it a secret (\textit{hiding}), and then open it (and only it: \textit{binding}) at a later time of the committer's choosing~\cite{brassard1988minimum}.
+A common approach (conjectured to be hiding) is to submit the cryptographic hash of the value with a random nonce (for low entropy data) to a smart contract, and later reveal the original value and nonce which can be verified by the contract to correctly hash to the commitment (see Figure~\ref{fig:commitReveal} in Appendix~\ref{app:cr}).
 
-An early use of this scheme is Namecoin, a Bitcoin-forked blockchain for name services~\cite{kalodner2015empirical}.
-In Namecoin, a user sends a commit transaction which commits to the name hash, similar to a sealed bid.
-Once the transaction is confirmed and the grace period is over, the user sends a reveal transaction revealing the bid and also the details of the requested domain~\cite{kalodner2015empirical}.
-Hence, the user is able to hide information from the adversarial parties in the system and prevent front-running attacks.
+An early application of this scheme to blockchain is Namecoin, a Bitcoin-forked DApp for name services~\cite{kalodner2015empirical}.
+In Namecoin, a user sends a commit transaction which registers a new hidden domain name, similar to a sealed bid.
+Once this first transaction is confirmed, a time delay begins.
+After the delay, a second transaction reveals the details of the requested domain.
+This prevent front-running if the reveal transaction is confirmed faster than an adversarial node or miner can redo the entire process.
 
-In the case of decentralized exchanges, users can use commit/reveal for bids, where commitments are placed in an ordered queue and executed in a later round after a reveal.
-This mitigation seems to require further research.
-One trader strategy is to flood orders at the commitment stage, but then only selectively and adaptively choose which to reveal.
-Collateralization is another challenge, where revealed bids may simply be intentions to execute but additional transactions are required to move the money or tokens; a transaction that can also be aborted early.
-One mitigation to early aborts is having users post a fidelity bond that can be automatically dispensed if they fail to fully execute committed transactions (as used in~\cite{mccorry2017smart}).
-Commit/reveal is also seen in on-chain voting~\cite{adChainPLCRVoting}.
+Commit/reveal is a two round protocol, and aborting after the first round (early aborts) could be an issue for this (along with most multi-round cryptographic protocols).
+For example, in a financial exchange where the number of other orders might be in a predictable interval, an adversary can spray the sequence (\ie a price-time priority queue) with multiple committed transactions and no intention of executing them all.
+She then only reveal the ones that result in an advantageous trade.\footnote{This is analogous to behaviour in traditional financial markets where high frequency traders will make and cancel orders at many price points.
+If they can cancel faster than someone can execute it---someone who has only seen the order and not the cancelation---then the victim reveals their price information.} There are other ways of aborting; if payments are required but not collateralized, the aborting party can ensure that payment is not available for transfer.
+One mitigation to early aborts that blockchain is uniquely positioned to make is having users post a fidelity bond of a certain amount of cryptocurrency that can be automatically dispensed if they fail to fully execute committed transactions (this is used in multi-round blockchain voting~\cite{mccorry2017smart}).
+Finally we note that any multiple round protocol will have usability challenges: users must be aware that participating in the first round is not sufficient for completing their intention.
+
+% Jeremy: doesn't seem related to front-running
+%Commit/reveal is also seen in on-chain voting~\cite{adChainPLCRVoting}.
 Using sealed votes, voters can assure their votes are hidden until a later date, however, their participation and weight of the vote are publicly known.
 
-The participatory factor is another issue for the commitment scheme.
+% Jeremy: moved up to confidentiality as this is not specific to commit/reveal but applicable to any mitigation
+%The participatory factor is another issue for the commitment scheme.
 For anyone watching the DApp address, there will be a direct transaction from the user to the DApp address, revealing the fact that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme.
@@
 
-Submarine Commitments~\cite{breidenbach2018enter,submarinesendHD} extend basic commit/reveal functionality with additional properties.
-In particular, they hide the DApp being invoked during the commit phase and also ensure that revealed transactions that send funds are fully collateralized.
-With submarine send, it is possible to hide sender, receiver, value, and data, so the commitment transaction is identical to a transaction to a newly generated address.
+\paragraph{Enhanced Commit/Reveal.} Submarine Commitments~\cite{breidenbach2018enter,submarinesendHD} extend basic commit/reveal functionality with additional properties for Ethereum smart contracts: (1) they initially hide the contract address being invoked, providing (3,4,5)-confidentiality during the commit phase; and (2) they ensure that if a revealed transaction sent funds, the funds were fully collateralized at commit time and are available to the receiving smart contract.
+
+% Jeremy: Merge this into the caption so there is one stand-alone description
+%With submarine send, it is possible to hide sender, receiver, value, and data, so the commitment transaction is identical to a transaction to a newly generated address.
 Submarine sends could be a solution for sealed-bid auctions on the blockchain to hide the existence of the bids for other participants.
@@
 
-Front-running can be tackled at the blockchain layer, as seen in the previous section, or mitigations can be built at the DApp level as seen here.
-
-The applications can be designed not to rely on the time for the orders to be executed.
-For example when designing a decentralized exchange, one can use a \emph{the call market} design instead of a time-sensitive order book~\cite{clark2014decentralizing} to side-step and disincentivize front-running by miners.
+The final main category of mitigation is to assume front-running is unpreventable and to thus responsively redesign the functionality of the DApp to remove any benefit from front-running.
+For example, when designing a decentralized exchange, one can use a call market design instead of a time-sensitive order book~\cite{clark2014decentralizing} to side-step and disincentivize front-running by miners.
 In a call market design, the arrival time of orders does not matter as they are executed in batches.
-
-The call market solution also pivots profitable gains that front-running miners stand to gain into fees that they collect~\cite{clark2014decentralizing}, removing the financial incentive to front-run.
+The call market solution pivots profitable gains that front-running miners stand to gain into fees that they collect~\cite{clark2014decentralizing}, removing the financial incentive to front-run.
 To the same end, Malinova~\cite{malinova2017market} proposes a design for a decentralized exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable.
@@
 Although there are other concerns about this specific design but not for front-running.
-
 %TODO: inline talk about what these solutions are good for and if they fit Status ICO

### 2018-12-08 frontrunning/Latex/sections/paper.tex
some other edits

@@
 %make them more pointy, shorten it. mainly the first paragraph
+% Jeremy: agree with above, also should be organized into subjects not just a list of papers
 
+Front-running is mentioned in passing in many papers and we try to 
 Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to market information leakage~\cite{aune2017footprints}.
-They also propose a cryptographic approach, similar to commit and reveal (see Section~\ref{CommitmentScheme}) to prevent front-running.
+They also propose a cryptographic approach, similar to commit and reveal (see Section~\ref{sec:comm}) to prevent front-running.
 Malinova and Park discuss different design settings for financial markets and trading platforms on decentralized ledgers~\cite{malinova2017market}.
@@
 Upon submitting the bug bounty to the Hydra smart contract, one can front-run the bug report and claim the bounty instead of the original reporter.
-In order to mitigate this issue they proposed \textit{Submarine Commitments} which extend commit and reveal; we discuss them further in Section~\ref{submarineCommits}.
+In order to mitigate this issue they proposed \textit{Submarine Commitments} which extend commit and reveal; we discuss them further in Section~\ref{sec:comm}.
 
-Double-spending attacks in Bitcoin have also been studied~\cite{bamert2013have,karame2012double} where a user broadcasts a transaction and is able to obtain some off-blockchain good or service before the transaction has actually been (fully) confirmed.
+Double-spending attacks in Bitcoin are related to front-running~\cite{bamert2013have,karame2012double}.
+In this attack, a user broadcasts a transaction and is able to obtain some off-blockchain good or service before the transaction has actually been (fully) confirmed.
 The user can then broadcast a competing transaction that sends the same unspent coins to herself, perhaps using higher transaction fees, arrangements with miners or artifacts of the network topology to have the second transaction confirmed instead of the first.
-We think of this as a type of front-running.
+This can be considered a form of self-front-running.
 
@@
 In particular, ideal functionalities of blockchains (such as those used in simulation-based proofs) need to capture this adversarial capability, assuming the real blockchain does not address front-running.
-See \eg~\cite{garay2015bitcoin} and Hawk~\cite{kosba2016hawk}.
+See \eg Bitcoin backbone~\cite{garay2015bitcoin} and Hawk~\cite{kosba2016hawk}.
 
@@
 \paragraph{Commit/Reveal.}
+\label{sec:comm}
 

### 2018-12-08 frontrunning/Latex/sections/paper.tex
related work fixes

@@
 
-%make them more pointy, shorten it. mainly the first paragraph
-% Jeremy: agree with above, also should be organized into subjects not just a list of papers
+Given the purpose of this entire paper is systemizing the existing literature, we do not re-enumerate the literature here.
+However, we note two things.
+First, we are not aware of any other systematic study of this issue.
+Second, front-running is related to two concepts that are often not considered front-running per se: double-spending and rushing adversaries.
 
-Front-running is mentioned in passing in many papers and we try to 
-Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to market information leakage~\cite{aune2017footprints}.
+% Jeremy: redistribute this to the relevant section
+%Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to market information leakage~\cite{aune2017footprints}.
 They also propose a cryptographic approach, similar to commit and reveal (see Section~\ref{sec:comm}) to prevent front-running.
-Malinova and Park discuss different design settings for financial markets and trading platforms on decentralized ledgers~\cite{malinova2017market}.
-They argue that blockchain brings new options of transparency which affects traders behaviour, especially in the presence of intermediary front-runners.
-They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make front-running costly and inefficient.
-Breidenbach~\etal~\cite{breidenbach2018enter} face the front-running issue in the context of automating bug bounties for smart contracts.
+
+% Jeremy: this is well described already, but we should use the bug-bounty example (citing this) somewhere in the paper as it is a nice example
+%Breidenbach~\etal~\cite{breidenbach2018enter} face the front-running issue in the context of automating bug bounties for smart contracts.
 Upon submitting the bug bounty to the Hydra smart contract, one can front-run the bug report and claim the bounty instead of the original reporter.
 In order to mitigate this issue they proposed \textit{Submarine Commitments} which extend commit and reveal; we discuss them further in Section~\ref{sec:comm}.
+
+% Jeremy: The following two paragraphs are fine
 
@@
 The call market solution pivots profitable gains that front-running miners stand to gain into fees that they collect~\cite{clark2014decentralizing}, removing the financial incentive to front-run.
-To the same end, Malinova~\cite{malinova2017market} proposes a design for a decentralized exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable.
+
+% Jeremy: This needs some clarification; what exactly is the principle they are applying???
+Malinova and Park discuss different design settings for financial markets and trading platforms on decentralized ledgers~\cite{malinova2017market}.
+They argue that blockchain brings new options of transparency which affects traders behaviour, especially in the presence of intermediary front-runners.
+They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make front-running costly and inefficient.
+Specifically they use economic models in their trading market design to make front-running expensive and more costly than profitable.
 They split big investments into smaller ones using intermediaries --liquidity demander-- and liquidity providers to achieve this.
@@
 Although there are other concerns about this specific design but not for front-running.
+
 %TODO: inline talk about what these solutions are good for and if they fit Status ICO

### 2018-12-08 frontrunning/Latex/sections/paper.tex
[frontrunning] bcash abc ref

--- 2018-12-08 frontrunning/Latex/sections/paper.tex
@@
 An alternative is to sequence transactions psuedorandomly.
-This can be seen in proposals like Canonical Transaction Ordering Rule (CTOR) in Bitcoin cash which adds transactions in lexicographical order according to their hash~\cite{bitcoinABC2018CTOR}.
-Note that Bitcoin cash does not have a front-running problem for most standard transactions.
+This can be seen in proposals like Canonical Transaction Ordering Rule (CTOR) by Bitcoin Cash ABC~\cite{bitcoincashabcFork} which adds transactions in lexicographical order according to their hash~\cite{bitcoinABC2018CTOR}.
+Note that Bitcoin does not have a front-running problem for most standard transactions.
 While this could be used by Ethereum to make front-running statistically difficult, the protection is marginal at best and might even exacerbate attacks.
@@
 
-A DApp includes the following components: (1) the code of the DApp, (2) the current state of the DApp, (3) the name of the function being invoked, (4) the parameters supplied to the function, (5) the address of the contract the function is being invoked on, and (6) the identity of the sender.
+A DApp includes the following components: (1) the code of the DApp, (2) the current state of the DApp, (3) the name of a function being invoked, (4) the parameters supplied to the function, and (5) the identity of the sender.
 Confidentiality applied to a DApp could mean different levels of protection for each of these.
@@
 Users whose balances are effected by changes in the contract's state would need to be able to learn this information.
-Further, if the contract addresses are known (no 5-confidentiality), front-runners can know about the traffic pattern of calls to contracts which could be sufficient grounds for attack; for example, if each asset on an exchange has its own market contract, this leaks trade volume information.
-As a contrasting example, consider again decentralized domain registration: hiding state changes (2-confidentiality) defeats the entire purpose of the DApp, and protecting function calls is ineffective with a public state change since the state itself reveals the domain being registered.
+As a contrasting example, consider again decentralized domain registration: keeping the state confidential defeats the entire purpose of the DApp.
+Only protecting function calls is ineffective as the state change itself reveals which domain is attempting to be registered.
 
@@
 While confidentiality appears insufficient for solving domain name front-running alone, a hybrid approach of sequencing and confidentiality can be effective, and is in fact an example of an older cryptographic trick known as commit/reveal.
-The essence of the approach is to protect the function call (\eg (3,4)- or (4)-confidentiality) until the function is enqueued in sequence of functions to be executed.
-Once the sequence is established, the confidentiality is lifted and the function can only be executed in the place is was given (or, generally speaking, not at all).
+The essence of the approach is to protect the function call, \ie (3,4)-confidentiality, until the function is enqueued in sequence of functions to be executed.
+Once the sequence is finalized, the confidentiality is lifted and the function can only be executed in the place is was given (or, generally speaking, not at all).
 
-Recall that a commitment scheme enables one to commit to a digital value (\eg a statement, transaction, data, \etc) while keeping it a secret (\textit{hiding}), and then open it (and only it: \textit{binding}) at a later time of the committer's choosing~\cite{brassard1988minimum}.
-A common approach (conjectured to be hiding) is to submit the cryptographic hash of the value with a random nonce (for low entropy data) to a smart contract, and later reveal the original value and nonce which can be verified by the contract to correctly hash to the commitment (see Figure~\ref{fig:commitReveal} in Appendix~\ref{app:cr}).
+A commitment scheme is a cryptographic primitive that enables one to commit to a value (\eg a statement, document, data, \etc) while keeping it a secret, and then open it (and only it) at a later time of the committer's choosing~\cite{brassard1988minimum}.
+A common approach is to submit the hash value of the data to be committed, potentially with a random nonce (for predictable data), to a smart contract and later reveal the original data and nonce which can be verified to hash to the commitment.
+See Figure~\ref{fig:commitReveal} in Appendix~\ref{app:cr}.
 
-An early application of this scheme to blockchain is Namecoin, a Bitcoin-forked DApp for name services~\cite{kalodner2015empirical}.
-In Namecoin, a user sends a commit transaction which registers a new hidden domain name, similar to a sealed bid.
-Once this first transaction is confirmed, a time delay begins.
-After the delay, a second transaction reveals the details of the requested domain.
-This prevent front-running if the reveal transaction is confirmed faster than an adversarial node or miner can redo the entire process.
+An early use of this scheme is Namecoin, a Bitcoin-forked blockchain for name services~\cite{kalodner2015empirical}.
+In Namecoin, a user sends a commit transaction which commits to the name hash, similar to a sealed bid.
+Once the transaction is confirmed and the grace period is over, the user sends a reveal transaction revealing the bid and also the details of the requested domain~\cite{kalodner2015empirical}.
+Hence, the user is able to hide information from the adversarial parties in the system and prevent front-running attacks.
 
-Commit/reveal is a two round protocol, and aborting after the first round (early aborts) could be an issue for this (along with most multi-round cryptographic protocols).
-For example, in a financial exchange where the number of other orders might be in a predictable interval, an adversary can spray the sequence (\ie a price-time priority queue) with multiple committed transactions and no intention of executing them all.
-She then only reveal the ones that result in an advantageous trade.\footnote{This is analogous to behaviour in traditional financial markets where high frequency traders will make and cancel orders at many price points.
-If they can cancel faster than someone can execute it---someone who has only seen the order and not the cancelation---then the victim reveals their price information.} There are other ways of aborting; if payments are required but not collateralized, the aborting party can ensure that payment is not available for transfer.
-One mitigation to early aborts that blockchain is uniquely positioned to make is having users post a fidelity bond of a certain amount of cryptocurrency that can be automatically dispensed if they fail to fully execute committed transactions (this is used in multi-round blockchain voting~\cite{mccorry2017smart}).
-Finally we note that any multiple round protocol will have usability challenges: users must be aware that participating in the first round is not sufficient for completing their intention.
-
-% Jeremy: doesn't seem related to front-running
-%Commit/reveal is also seen in on-chain voting~\cite{adChainPLCRVoting}.
+In the case of decentralized exchanges, users can use commit/reveal for bids, where commitments are placed in an ordered queue and executed in a later round after a reveal.
+This mitigation seems to require further research.
+One trader strategy is to flood orders at the commitment stage, but then only selectively and adaptively choose which to reveal.
+Collateralization is another challenge, where revealed bids may simply be intentions to execute but additional transactions are required to move the money or tokens; a transaction that can also be aborted early.
+One mitigation to early aborts is having users post a fidelity bond that can be automatically dispensed if they fail to fully execute committed transactions (as used in~\cite{mccorry2017smart}).
+Commit/reveal is also seen in on-chain voting~\cite{adChainPLCRVoting}.
 Using sealed votes, voters can assure their votes are hidden until a later date, however, their participation and weight of the vote are publicly known.
 
-% Jeremy: moved up to confidentiality as this is not specific to commit/reveal but applicable to any mitigation
-%The participatory factor is another issue for the commitment scheme.
+The participatory factor is another issue for the commitment scheme.
 For anyone watching the DApp address, there will be a direct transaction from the user to the DApp address, revealing the fact that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme.
@@
 \includegraphics[width=0.5\linewidth]{figures/LibSubmarine.png}
-\caption{Submarine Send~\cite{libsubmarine}.
+\caption{ Submarine Send~\cite{libsubmarine}.
 User generates an \textit{Unlock} transaction from which the commitment address is retrieved.
@@
 
-\paragraph{Enhanced Commit/Reveal.} Submarine Commitments~\cite{breidenbach2018enter,submarinesendHD} extend basic commit/reveal functionality with additional properties for Ethereum smart contracts: (1) they initially hide the contract address being invoked, providing (3,4,5)-confidentiality during the commit phase; and (2) they ensure that if a revealed transaction sent funds, the funds were fully collateralized at commit time and are available to the receiving smart contract.
-
-% Jeremy: Merge this into the caption so there is one stand-alone description
-%With submarine send, it is possible to hide sender, receiver, value, and data, so the commitment transaction is identical to a transaction to a newly generated address.
+Submarine Commitments~\cite{breidenbach2018enter,submarinesendHD} extend basic commit/reveal functionality with additional properties.
+In particular, they hide the DApp being invoked during the commit phase and also ensure that revealed transactions that send funds are fully collateralized.
+With submarine send, it is possible to hide sender, receiver, value, and data, so the commitment transaction is identical to a transaction to a newly generated address.
 Submarine sends could be a solution for sealed-bid auctions on the blockchain to hide the existence of the bids for other participants.
@@
 
-The final main category of mitigation is to assume front-running is unpreventable and to thus responsively redesign the functionality of the DApp to remove any benefit from front-running.
-For example, when designing a decentralized exchange, one can use a call market design instead of a time-sensitive order book~\cite{clark2014decentralizing} to side-step and disincentivize front-running by miners.
+Front-running can be tackled at the blockchain layer, as seen in the previous section, or mitigations can be built at the DApp level as seen here.
+
+The applications can be designed not to rely on the time for the orders to be executed.
+For example when designing a decentralized exchange, one can use a \emph{the call market} design instead of a time-sensitive order book~\cite{clark2014decentralizing} to side-step and disincentivize front-running by miners.
 In a call market design, the arrival time of orders does not matter as they are executed in batches.
-The call market solution pivots profitable gains that front-running miners stand to gain into fees that they collect~\cite{clark2014decentralizing}, removing the financial incentive to front-run.
+
+The call market solution also pivots profitable gains that front-running miners stand to gain into fees that they collect~\cite{clark2014decentralizing}, removing the financial incentive to front-run.
 To the same end, Malinova~\cite{malinova2017market} proposes a design for a decentralized exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable.

### 2018-12-08 frontrunning/Latex/sections/paper.tex
[frontrunning] wrapping up libsubmarine

@@
 \caption{Submarine Send~\cite{libsubmarine}.
-User generates an \textit{Unlock} transaction from which the commitment address is retrieved.
-By funding the \textit{commitment address}, user is committed to the unlock transaction.
-After the commitment transaction, in the reveal phase, user sends the \textit{reveal transaction} to the DApp and then after she can broadcast the Unlock transaction to unlock the funds in the commitment address.
-Finally after the "Auction'' is over, anyone can call \textit{Finalize} function to finalize the process.
+User generates an \textit{Unlock} transaction from which the commitment address is retrieved using ECDSA ECRecover.
+By \textsf(1) funding the \textit{commitment address}, user is committed to the unlock transaction.
+In the reveal phase, \textsf(2) user sends the \textit{reveal transaction} to the DApp, revealing the nature of the commitment transaction.
+\textsf(3) Then after she can broadcast the Unlock transaction to unlock the funds in the commitment address.
+\textsf(4) Finally after the "Auction'' is over, anyone can call \textit{Finalize} function to finalize the process.
 \label{fig:LibSubmarine}}
@@
 
-\paragraph{Enhanced Commit/Reveal.} Submarine Commitments~\cite{breidenbach2018enter,submarinesendHD} extend basic commit/reveal functionality with additional properties for Ethereum smart contracts: (1) they initially hide the contract address being invoked, providing (3,4,5)-confidentiality during the commit phase; and (2) they ensure that if a revealed transaction sent funds, the funds were fully collateralized at commit time and are available to the receiving smart contract.
-
-% Jeremy: Merge this into the caption so there is one stand-alone description
-%With submarine send, it is possible to hide sender, receiver, value, and data, so the commitment transaction is identical to a transaction to a newly generated address.
-Submarine sends could be a solution for sealed-bid auctions on the blockchain to hide the existence of the bids for other participants.
-The details of how Submarine commitments work could fill an entire paper, however in short, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality, it is possible to generate one outgoing transaction from an address of which no private key exists.
-By constructing a transaction from that address to the DApp and funding that address we fulfill the commitment phase.
-By revealing the details and broadcasting the constructed transaction we reveal the commitment~\cite{libsubmarine}.
+\paragraph{Enhanced Commit/Reveal.} Submarine Commitments~\cite{libsubmarine,submarinesendHD} extend the confidentiality of the commit and reveal, so that the commitment transaction is identical to a transaction to a newly generated Ethereum address.
+(1) they initially hide the contract address being invoked, providing (3,4,5)-confidentiality during the commit phase; and (2) they ensure that if a revealed transaction sent funds, the funds were fully collateralized at commit time and are available to the receiving smart contract.
 See Figure~\ref{fig:LibSubmarine}.
-However, this could be designed in other ways to suit the need of the DApp.
-Drawbacks of this scheme are similar to commit/reveal, with the addition of two more transactions to finalize a transaction, which adds cost and complexity to the user experience.
 

### 2018-12-08 frontrunning/Latex/sections/paper.tex
[frontrunning] editing Malinova mitigation

@@
 \centering
-\includegraphics[width=0.5\linewidth]{figures/LibSubmarine.png}
+\includegraphics[width=0.7\linewidth]{figures/LibSubmarine.png}
 \caption{Submarine Send~\cite{libsubmarine}.
@@
 % Jeremy: This needs some clarification; what exactly is the principle they are applying???
-Malinova and Park discuss different design settings for financial markets and trading platforms on decentralized ledgers~\cite{malinova2017market}.
-They argue that blockchain brings new options of transparency which affects traders behaviour, especially in the presence of intermediary front-runners.
-They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make front-running costly and inefficient.
-Specifically they use economic models in their trading market design to make front-running expensive and more costly than profitable.
-They split big investments into smaller ones using intermediaries --liquidity demander-- and liquidity providers to achieve this.
+%Shayan: Is this better?
+they basically use economical model for welfare of the traders in a transparent environment.
+To extend the idea more, we need to dive in their economical model which I think is out of scope of this paper.
+Malinova and Park discuss different design setting for financial markets and trading platforms to mitigate front-running~\cite{malinova2017market}.
+They model indirect trading costs on search and trading at decentralized exchanges to make front-running costly and inefficient.
+They split big investments into smaller ones using intermediaries --liquidity demander-- and liquidity providers.
+To prevent front-running, the liquidity demander offers the liquidity-providing trader an incentive; establishing an equilibrium behaviour, in which front-runner needs to pay more incentives to come in front of the original trade, making front-running not too profitable.
 

### 2018-12-08 frontrunning/Latex/sections/paper.tex
[frontrunning] more edits + citations

@@
 All transaction details in Bitcoin are make public and participant identities are only lightly protected.
-A number of techniques increase confidentiality~\cite{bunzBulletproofs,maxwell2015confidential} and anonymity [zerocoin, monero, etc] for cryptocurrencies.
+A number of techniques increase confidentiality~\cite{bunzBulletproofs,maxwell2015confidential} and anonymity ~\cite{miers2013zerocoin,monerosite} for cryptocurrencies.
 A current research direction is extending these protections to DApps.
@@
 User generates an \textit{Unlock} transaction from which the commitment address is retrieved using ECDSA ECRecover.
-By \textsf(1) funding the \textit{commitment address}, user is committed to the unlock transaction.
-In the reveal phase, \textsf(2) user sends the \textit{reveal transaction} to the DApp, revealing the nature of the commitment transaction.
-\textsf(3) Then after she can broadcast the Unlock transaction to unlock the funds in the commitment address.
-\textsf(4) Finally after the "Auction'' is over, anyone can call \textit{Finalize} function to finalize the process.
+By \textsf{1.} funding the \textit{commitment address}, user is committed to the unlock transaction.
+In the reveal phase, \textsf{2.} user sends the \textit{reveal transaction} to the DApp, revealing the nature of the commitment transaction.
+\textsf{3.} Then after she can broadcast the Unlock transaction to unlock the funds in the commitment address.
+\textsf{4.} Finally after the "Auction'' is over, anyone can call \textit{Finalize} function to finalize the process.
 \label{fig:LibSubmarine}}

### 2018-12-08 frontrunning/Latex/sections/paper.tex
[frontrunning] some edits

@@
 The price that users pay for transactions, \textsf{gasPrice}, can increase or decrease how quickly miners will execute them and include them within the blocks they mine.
-Once seeing two identical transactions with different transaction fees, a rational miner will prioritize the transaction that pays a higher gas price, due to limited space in the blocks.
+Once seeing two identical transactions with different transaction fees, a rational miner, due to limited space in the blocks, will prioritize the transaction that pays a higher gas price, this is also known as gas auctions~\cite{frontrunme}.
 Therefore, any regular user who runs a full-node Ethereum client can front-run pending transactions by sending similar transaction with a higher gas price.
@@
 For example, in a financial exchange where the number of other orders might be in a predictable interval, an adversary can spray the sequence (\ie a price-time priority queue) with multiple committed transactions and no intention of executing them all.
-She then only reveal the ones that result in an advantageous trade.\footnote{This is analogous to behaviour in traditional financial markets where high frequency traders will make and cancel orders at many price points.
+She then only reveal the ones that result in an advantageous trade.\footnote{This is analogous to behaviour in traditional financial markets where high frequency traders will make and cancel orders at many price points --flash orders or pinging--.
 If they can cancel faster than someone can execute it---someone who has only seen the order and not the cancelation---then the victim reveals their price information.} There are other ways of aborting; if payments are required but not collateralized, the aborting party can ensure that payment is not available for transfer.
@@
 To extend the idea more, we need to dive in their economical model which I think is out of scope of this paper.
-Malinova and Park discuss different design setting for financial markets and trading platforms to mitigate front-running~\cite{malinova2017market}.
+Malinova and Park discuss similar design consideration for financial markets and trading platforms to mitigate front-running~\cite{malinova2017market}.
 They model indirect trading costs on search and trading at decentralized exchanges to make front-running costly and inefficient.

### 2018-12-09 frontrunning/Latex/sections/paper.tex
[frontrunning] todo Aztec
[frontrunning] (Aztec) edits mostly citations

@@
 All transaction details in Bitcoin are make public and participant identities are only lightly protected.
-A number of techniques increase confidentiality~\cite{bunzBulletproofs,maxwell2015confidential} and anonymity ~\cite{miers2013zerocoin,monerosite} for cryptocurrencies.
-A current research direction is extending these protections to DApps.
+A number of techniques increase confidentiality~\cite{bunzBulletproofs,maxwell2015confidential} and anonymity ~\cite{miers2013zerocoin,cryptoeprint2015,sasson2014zerocash} for cryptocurrencies.
+A current research direction is extending these protections to DApps, \eg AZTEC protocol~\cite{aztec2018}.
 It is tempting to think that a confidential DApp would not permit front-running, as the front-runner would not know the details of the transaction she is front-running.
@@
 For front-running, function calls (3,4) are the most important, however function calls could be inferred from state changes (2).
-Hawk~\cite{kosba2016hawk} and Eiden [c] are examples of (2,3,4)-confidentiality (with limitations we are glossing over).
+Hawk~\cite{kosba2016hawk} and Ekiden~\cite{cheng2018ekiden} are examples of (2,3,4)-confidentiality (with limitations we are glossing over).
 
@@
 As a contrasting example, consider again decentralized domain registration: hiding state changes (2-confidentiality) defeats the entire purpose of the DApp, and protecting function calls is ineffective with a public state change since the state itself reveals the domain being registered.
+
+%Shayan: maybe just a reference ^ suffices! 
+%A recent attempt to build confidential transactions for DApps, is AZTEC protocol~\cite{aztec2018}.
+Similar to ZCash ~\cite{hopwood2016zcash}, it uses the concept of encrypted ‘notes’ and join-split transactions.
+ZCash uses two distinct types of addresses, transparent and shielded addresses, where in AZTEC, user transfers her ERC20 tokens into encrypted notes.
+Users can transfer these notes by destroying the unspent notes and creating new notes for the new owners, where the sum of the old notes should be equal to the sum of the new notes.
+%Shayan: Talk about AZTEC confidential transactions and their approach for CT.
+it will be possible to do dark pool style transactions within Ethereum dapps however they would still expose some information such as sender, receiver (exposes 5,6), hides (3,4?).
+https://medium.com/aztec-protocol/confidential-transactions-have-arrived-a-dive-into-the-aztec-protocol-a1794c00c009
 

### 2018-12-12 frontrunning/Latex/sections/appendix.tex
changes
some more edits
[frontrunning] some edits + citations + pdf of attacks outlined

@@
 
+\clearpage
 \section{Appendix}
 \appendix
+
+\textblue{\textbf{Note to Reviewers:}} If accepted, the camera-ready version will link to a full version of the paper on eprint that will include the information in this appendix.
+We include it here for reference.
 
@@
 There are debates in traditional markets regarding the fact that front-running is considered to be a form of insider trading which deemed to be illegal.
-Traditional methods to prevent front-running mainly involves after the fact investigation and legal action against the front-runners~\cite{LexisNexisLawSuit}.
+Traditional methods to prevent front-running mainly involves after the fact investigation and legal action against the front-runners~\cite{FTFrontrunning18}.
 As mentioned in section~\ref{traditionalFrontrunning}, defining front-running and educating the employees were the first step taken to prevent such issues in traditional markets, however, front-running became less likely to happen mainly because of the high fine and lawsuits against firms who behaved in an unethical way.
@@
 Figure~\ref{fig:commitReveal} illustrates the commit/reveal approach.
+
+%\section{Loop-ring}
+
+%\paragraph{Design Decision \#3: Dual Authoring.} This scheme is proposed to solve the front-running issue within Loopring -- a decentralized exchange protocol proposed by Wang~\etal~\cite{wang2018loopring}.
+In the first version of this protocol, orders are grouped in \emph{ring orders} once they are sent by the users.
+After the required signatures are provided by the \textit{ring miner}, he sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement (see Figure~\ref{fig:vulnerable_loopring}).
+While this transaction sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with higher gasPrice and his address instead of the ring miner's address.
+Using the proposed \textit{dual authoring} solution in the new version of Loopring, regeneration of the \emph{submitRing transaction} is infeasible as the users have to sign the orders using their secondary private keys (auth-keys), which are only known to the ring miner and not other users (see Figure~\ref{fig:not_vulnerable_loopring}).
+% Loopring protocol is proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}.
+In this protocol, the orders are grouped in \emph{ring orders} immediately after they are sent by the users.
+Next, the required signatures are provided by a miner and owner of the order, see Figure~\ref{fig:vulnerable_loopring}.
+Eventually, the ring miner sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement.
+While the \emph{submitRing transaction} sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with his address instead of the ring miner's address and then sign the hash of the ring using his own private key.
+By paying a higher gasPrice, block miners choose the front-runner's transaction instead of the original \emph{submitRing transaction}.
+%To solve this issue, the new version of Loopring protocol uses the \emph{dual-authoring} scheme.
+This solution sets two levels of authorization for orders - one for settlement, and one for order matching.
+As it can be seen in Figure~\ref{fig:not_vulnerable_loopring}, each owner of an order generates a pair of public key (auth-address) and private key (auth-key), which are different from his address and its corresponding private key.
+These auth-keys are used to sign the hash of the ring and will further prevent anyone from regenerating the same \emph{submitRing transaction}.
+The reason is that the auth-keys are only known to the miner of the ring as they are not part of the on-chain transaction.
+Doing so, it is assured that (i) the orders are not modified because they are signed by the owner, (ii) no other miner can mine the ring because the miner's address is signed by the initial miner, and (iii) no user can front-run the \emph{submitRing transaction} because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them.
+
+%\begin{figure}[t]
+%\centering
+%\includegraphics[width=0.9\linewidth]{figures/Vulnerable_Loopring.png}
+%\caption{ \emph{submitRing} Transaction in the old version of the Loopring protocol.
+Any user can regenerate this transaction by replacing the miner's address with his address and signing the hash of the ring using his private key.
+\label{fig:vulnerable_loopring}}
+%\end{figure}
+%https://www.lucidchart.com/invitations/accept/33d38ce9-4660-4743-806d-45c72f7e8393
+%\begin{figure}[t]
+%\centering
+%\includegraphics[width=0.7\linewidth]{figures/Dual_Authoring_Loopring.png}
+%\caption{ \emph{submitRing} Transaction in the new version of the Loopring protocol.
+Other users cannot regenerate this transaction as they do not access auth-keys and hence are not able to create the signatures.
+\label{fig:not_vulnerable_loopring}}
+%\end{figure}
+%https://www.lucidchart.com/invitations/accept/8dee869c-482c-433f-a901-8d041a1dc526
+
+%The first solution was to prevent front-running, but then it was attacked so they updated the solution. this new solution also could be attacked.

### 2018-12-12 frontrunning/Latex/sections/paper.tex
[frontrunning] some edits + citations + pdf of attacks outlined

@@
 Therefore, DApps need to be studied individually or in categories.
-In this paper we draw from a scattered body of knowledge regarding front-running attacks on blockchain applications and proposed solutions, with series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps) from each category of the top 25 most active, based on user activity.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} We do case studies on decentralized exchanges (\eg Bancor), crypto-collectibles (\eg CryptoKitties), gambling services (\eg Fomo3D), and decentralized name services (\eg Ethereum Name Service).
+In this paper we draw from a scattered body of knowledge regarding front-running attacks on blockchain applications and proposed solutions, with series of case studies of DApps deployed on Ethereum\footnote{Selected DApps from each category of the top 25 most active, based on user activity gathered from DAppRadar \url{https://DAppradar.com/DApps}} (a popular blockchain supporting DApps).
+We do case studies on decentralized exchanges (\eg Bancor), crypto-collectibles (\eg CryptoKitties), gambling services (\eg Fomo3D), and decentralized name services (\eg Ethereum Name Service).
 We also study initial coin offerings (ICOs), which by happenstance, did not appear in the top 25 on our sample day.
@@
 In 2012, it was expanded further with the new amendment, FINRA Rule 5270, to cover trading in options, derivatives, or other financial instruments overlying a security with only a few exceptions~\cite{sec2012frontrunning,finra_2012}.
+Similar issues have been seen in domain industry~\cite{sac022en33,edelman2009front} as well.
 
@@
 0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the order book holders and could front-run the orders they relay.
-One method of price manipulation on financial markets is to flood the market with orders and cancel them when there are filling orders --taker's griefing--~\cite{consesnsys0xReview2017}, to prevent such attacks, the user needs to send a transaction to cancel each of his orders.
+As seen in traditional financial markets, one method to manipulation the spot price of an asset, is to flood the market with orders and cancel them when there are filling orders --taker's griefing~\cite{consesnsys0xReview2017}.
+As mentioned putting an order in the current decentralized exchange is free, but to prevent taker's griefing attacks, the user needs to send a transaction to cancel each of his orders.
 The reason for canceling order could be the unprofitability of the order due to price change.
-In this case, when an adversarial actor sees a pending cancellation transaction, he sends a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled, this is known as \textit{cancellation grief}.
+In this case, when an adversarial actor sees a pending cancellation transaction, he sends a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled, this is known as \textit{\todo{cancellation grief}}.
 This is illustrated in Figure~\ref{fig:MinerFrontrunning}.
@@
 ERC-721 are similar enough to ERC-20 tokens that they can be listed on exchanges that are ERC-20 compatible.
-To buy a kitty, the user sends the following bid transaction: \texttt{bid(uint256 \_tokenId)}.
+To buy a kitty from their main website, the user sends the following bid transaction: \texttt{bid(uint256 \_tokenId)}.
 It contains the kitty's ID which can be found either on their website or on the ERC721 token smart contract.
@@
 The third category of DApp in Table~\ref{tab:top25DApps} is gambling services.
-While a large category of gambling games are based on random outcomes, DApps do not have unique access to an unpredictable data stream to harvest for randomness.
+While a large category of gambling games are based on random outcomes, DApps do not have unique access to an unpredictable data stream to harvest for randomness~\cite{pierrot2018malleability}.
 Any candidate (such as block headers) source of randomness is accessible to all DApp functions and can also be manipulated to an extent by miners.
@@
 Many speculated such a game would never end but on August 22, 2018, the first round of the game ended with the winner collecting 10,469 Ether\footnote{The first winner of Fomo3D, won 10,469 Ether \url{ https://etherscan.io/tx/0xe08a519c03cb0aed0e04b33104112d65fa1d3a48cd3aeab65f047b2abce9d508}} equivalent to \$2.1M USD at the time.
-Blockchain forensics indicate a sophisticated winning strategy to front-run new ticket purchases~\cite{fomo3dhacker} that would reset the counter.
-The winner appears to have started by deploying some high gas consumption DApps unrelated to the game.
+Blockchain forensics indicate a sophisticated winning strategy to front-run new ticket purchases~\cite{fomo3dhacker,fomo3dmedium} that would reset the counter.
+The winner appears to have started by deploying many high gas consumption DApps unrelated to the game.
 When the timer of the game reached about 3 minutes, the winner bought 1 ticket and then sent multiple high gasPrice transactions to her own DApps.
@@
 A number of techniques increase confidentiality~\cite{bunzBulletproofs,maxwell2015confidential} and anonymity ~\cite{miers2013zerocoin,cryptoeprint2015,sasson2014zerocash} for cryptocurrencies.
-A current research direction is extending these protections to DApps, \eg AZTEC protocol~\cite{aztec2018}.
+A current research direction is extending these protections to DApps~\cite{aztec2018,ZoeEth2017}.
 It is tempting to think that a confidential DApp would not permit front-running, as the front-runner would not know the details of the transaction she is front-running.

### 2018-12-12 frontrunning/Latex/sections/paper.tex
[frontrunning] a full run on the figures and table. saved more than half a page

@@
 
+\begin{figure}[t]
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,bottom},capbesidewidth=0.3\linewidth}}]{figure}[\FBwidth]
+{\caption{The adversarial miner monitors the Ethereum mempool for decentralized exchange transactions.
+Upon spotting a profitable cancellation transaction, he puts his buy order prior to the cancel transaction in the block he mines.
+Doing so, the miner can profit from the underlying trade and also get the gas included in the cancel transaction.}\label{fig:MinerFrontrunning}}
+{\includegraphics[width=\linewidth]{figures/Miner_reorder_frontrun.png}}
+\end{figure}
+%https://www.lucidchart.com/invitations/accept/c8768786-4a3f-4c78-b3c8-aa04a6b81d06
+
 \subsection{Literature on Blockchain Front-running}
@@
 
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.7\linewidth]{figures/Miner_reorder_frontrun.png}
-\caption{ The adversarial miner can monitor the Ethereum mempool for decentral exchange cancel orders and upon seeing the cancellation transaction, he puts his buy order prior to the cancel transaction.
-Doing so, the miner can profit from the underlying trade and also get the gas included in the cancel transaction.
-\label{fig:MinerFrontrunning}}
-\end{figure}
-%https://www.lucidchart.com/invitations/accept/c8768786-4a3f-4c78-b3c8-aa04a6b81d06
-
 The first category of DApp in Table~\ref{tab:top25DApps} is exchanges.
@@
 
+%Shayan -> Jeremy: Not sure if this figure adds value to the paper. I edited and looked at this for so long that it lost its meaning. I'll come back to it tomorrow.
 \begin{figure}[t]
-\centering
-\includegraphics[width=0.7\linewidth]{figures/Regular_frontrunning.png}
-\caption{The Adversary upon seeing the Buy order sends his own buy order with higher gas to front-run the first order. \label{fig:RegularFrontrunning}}
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={left,top},capbesidewidth=0.3\linewidth}}]{figure}[\FBwidth]
+{\caption{The front-runner upon spotting the profitable transaction \textit{Buy(1000)} sends his own transaction with higher gas price to bribe the miners to prioritize his transaction over initial transaction.}\label{fig:RegularFrontrunning}}
+{\includegraphics[width=1.1\linewidth]{figures/Regular_frontrunning.png}}
 \end{figure}
@@
 \begin{figure}[t]
-\centering
-\includegraphics[width=0.5\linewidth]{figures/Mining_pool_ratio.png}
-\caption{ The percentage of Ethereum blocks mined between block 3903900 and 3908029, this is the time frame in which Status.im ICO was running.
-This percentage roughly shows the hashing power ratio each miner had at that time.
-\label{fig:mining_pool_ratio}} % IS THIS STATEMENT CORRECT?
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={left,bottom},capbesidewidth=0.35\linewidth}}]{figure}[\FBwidth]
+{\caption{The percentage of Ethereum blocks mined between block 3903900 and 3908029, this is the time frame in which Status.im ICO was running.
+This percentage roughly shows the hashing power ratio each miner had at that time.}\label{fig:mining_pool_ratio}}
+{\includegraphics[width=1.1\linewidth]{figures/Mining_pool_ratio.png}}
 \end{figure}
@@
 \begin{figure}[t]
-\centering
-\includegraphics[width=0.7\linewidth]{figures/Transactions_miners_while_status_ico_cut_only_icotx.png}
-\caption{ This chart shows the miners behaviour on the time window that Status.im ICO was running.
-It is clear that the number of successful transactions mined by F2Pool do not follow the random homogeneous pattern of the rest of the network.
-\label{fig:Transactions_miners_while_status_ico_cut}}
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={left,bottom},capbesidewidth=0.3\linewidth}}]{figure}[\FBwidth]
+{\caption{This chart shows the miners behaviour on the time window that Status.im ICO was running.
+It is clear that the number of successful transactions mined by F2Pool do not follow the random homogeneous pattern of the rest of the network.}\label{fig:Transactions_miners_while_status_ico_cut}}
+{\includegraphics[width=1.1\linewidth]{figures/Transactions_miners_while_status_ico_cut_only_icotx.png}}
 \end{figure}
 
-% make pie charts for each mining pool, all non-status-ico transactions vs success-ico-transactions vs failed-ico=transactions
-
 \begin{figure}[t]
-\centering
-\includegraphics[width=0.6\linewidth]{figures/F2Pool_transactions_to_StatusICO_and_Refunds.png}
-\caption{ F2Pool prior to Status.im ICO deposited 100 Ether in multiple new Ethereum addresses.
-On the time of the ICO they sent these deposits to Status ICO smart contract and prioritized mining of these transactions in their mining pool, this was to overcome the dynamic ceiling algorithm of the token sale smart contract.
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={left,top},capbesidewidth=0.5\linewidth}}]{figure}[\FBwidth]
+{\caption{Prior to \textit{Status.im} ICO  \textit{F2Pool} deposited 100 Ether in multiple new Ethereum addresses.
+On the time of the ICO transactions were sent from these addresses to \textit{Status} ICO smart contract and were prioritized their mining pool and received \textit{ERC20} tokens.
+This method was used to overcome the dynamic ceiling algorithm of the ICO smart contract.
 Later on they sent the refunded Ether back to their own address.
-[Graph made using Blockseer.com] \label{fig:f2poolfront-run}}
+[Graph made using Blockseer.com]}\label{fig:f2poolfront-run}}
+{\includegraphics[width=0.8\linewidth]{figures/F2Pool_transactions_to_StatusICO_and_Refunds.png}}
 \end{figure}
@@
 
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.7\linewidth]{figures/LibSubmarine.png}
-\caption{Submarine Send~\cite{libsubmarine}.
+%\begin{figure}[t]
+%\centering
+%\includegraphics[width=0.7\linewidth]{figures/LibSubmarine.png}
+%\caption{Submarine Send~\cite{libsubmarine}.
 User generates an \textit{Unlock} transaction from which the commitment address is retrieved using ECDSA ECRecover.
@@
 \label{fig:LibSubmarine}}
+%\end{figure}
+
+\begin{figure}[t]
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={left,bottom},capbesidewidth=0.5\linewidth}}]{figure}[\FBwidth]
+{\caption{Submarine Send~\cite{libsubmarine}.
+User generates an \textit{Unlock} transaction from which the commitment address is retrieved using ECDSA ECRecover.
+\textsf{1.} by funding the \textit{commitment address},user is committed to the transaction.
+\textsf{2.} User sends the \textit{reveal transaction} to the DApp, revealing the nature of the commitment transaction.
+\textsf{3.} She broadcasts the \textit{unlock transaction} to unlock the funds in the commitment address.
+\textsf{4.} After the \textit{"Auction''} is over, anyone can call \textit{Finalize} function to finalize the process.}\label{fig:LibSubmarine}}
+{\includegraphics[width=\linewidth]{figures/LibSubmarine.png}}
 \end{figure}

### 2018-12-12 frontrunning/Latex/setup/table.tex
[frontrunning] a full run on the figures and table. saved more than half a page

@@
 \begin{table}[t]
-\centering
-\scriptsize
-\begin{tabular}{|c|l|}
+\captionsetup{justification = centering, singlelinecheck = false}
+{\caption{Top 25 DApps based on recent user activity from \texttt{DAppRadar.com} on September 4th, 2018. The DApps that are in bold are discussed in this paper.}\label{tab:top25DApps}}
+\begin{tabular}{|c|c|l|}
 
@@
 \end{tabular}
-\caption{\footnotesize{Top 25 DApps based on recent user activity from \texttt{DAppRadar.com} on September 4th, 2018. We discuss the DApps that are in bold.}\label{tab:top25DApps}}
+\vspace{1em}
 \end{table}

### 2018-12-13 frontrunning/Latex/sections/paper.tex
[frontrunning] fix a footnote on a caption

@@
 This method was used to overcome the dynamic ceiling algorithm of the ICO smart contract.
-Later on they sent the refunded Ether back to their own address.
-[Graph made using Blockseer.com]}\label{fig:f2poolfront-run}}
+Later on they sent the refunded Ether back to their own address.\protect\footnotemark \label{fig:f2poolfront-run}}}
 {\includegraphics[width=0.8\linewidth]{figures/F2Pool_transactions_to_StatusICO_and_Refunds.png}}
 \end{figure}
+
+\footnotetext{Graph was made using \url{Blockseer.com}}
 

### 2018-12-13 frontrunning/Latex/sections/paper.tex
taxonomy

--- 2018-12-12 frontrunning/Latex/sections/paper.tex
@@
 In 2012, it was expanded further with the new amendment, FINRA Rule 5270, to cover trading in options, derivatives, or other financial instruments overlying a security with only a few exceptions~\cite{sec2012frontrunning,finra_2012}.
-Similar issues have been seen in domain industry~\cite{sac022en33,edelman2009front} as well.
+Similar issues have been seen in domain industry~\cite{sac022en33:online,edelman2009front} as well.
 
@@
 See \eg Bitcoin backbone~\cite{garay2015bitcoin} and Hawk~\cite{kosba2016hawk}.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = %
+% = = = Taxonomy 
+% = = = = = = = = = = = = = = = = = = = = = = = = = = %
+
+\section{A Taxonomy of Front-running Attacks}
+
+As we will illustrate with examples through-out the paper, front-running attacks can often be reduced to one of a few basic templates.
+First we consider what the adversary is trying to accomplish (without worrying about how) and we distinguish three cases: displacement, insertion, and suppression attacks.
+In all three cases, Alice is trying to invoke a function on a contract that is in a particular state, and Mallory will try to invoke her own function call on that contract in that particular state before Alice.
+
+In a \textit{displacement attack}, after Mallory runs her function, Alice's function is either orphaned or runs with no meaningful effect.
+Examples of displacement include: Alice trying to register a domain name and Mallory registering it first; Alice trying to submit a bug to receive a bounty and Mallory stealing it and submitting it first~\cite{}; and Alice trying to submit a bid in an auction and Mallory copying it.
+In some cases, Alice's function and Mallory's function are different: \eg Alice trying to cancel an offer and Mallory fulfilling the offer first.
+We call this \textit{asymmetric displacement}.
+Finally, in some cases, Mallory is trying to run a large set of functions: for example Alice and others are trying to buy a limited set of shares offered by a firm on a blockchain.
+We call this \textit{bulk displacement}.
+
+In an \textit{insertion attack}, after Mallory runs her function, the state of the contract is changed and she needs Alice's original function to run on this modified state.
+For example, if Alice places a purchase order on a blockchain asset at a higher price than the best offer, Mallory will insert two transactions: she will purchase at the best offer price and then offer the same asset for sale at Alice's slightly higher purchase price.
+If Alice's transaction is then run after, Mallory will profit on the price difference without having to hold the asset.
+
+In a \textit{suppression attack}, after Mallory runs her function, she tries to delay Alice from running her function.
+After the delay, she is invariant to whether Alice functions runs or not.
+We only observe this attack pattern in one DApp and the details are quite specific to it, so we defer discussion until Section~\ref{sec:gambling}.
+
+Finally, we note that in addition to the three things the front-runner wants to accomplish, there are three basic mechanisms to accomplishing them: (1) miners can choose transaction order, (2) non-miners can prioritize their later transactions over earlier transactions with higher gas fees, and (3) well-positioned network nodes can try to influence how transactions are propagated through the network.
 
@@
 \subsection{Gambling.}
+\label{sec:gambling}
 

### 2018-12-13 frontrunning/Latex/sections/paper.tex
intro squeeze

@@
 Therefore, DApps need to be studied individually or in categories.
-In this paper we draw from a scattered body of knowledge regarding front-running attacks on blockchain applications and proposed solutions, with series of case studies of DApps deployed on Ethereum\footnote{Selected DApps from each category of the top 25 most active, based on user activity gathered from DAppRadar \url{https://DAppradar.com/DApps}} (a popular blockchain supporting DApps).
+In this paper we draw from a scattered body of knowledge regarding front-running attacks on blockchain applications and proposed solutions, with series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps).
 We do case studies on decentralized exchanges (\eg Bancor), crypto-collectibles (\eg CryptoKitties), gambling services (\eg Fomo3D), and decentralized name services (\eg Ethereum Name Service).
-We also study initial coin offerings (ICOs), which by happenstance, did not appear in the top 25 on our sample day.
-After a few hacking incidents of high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered.
-This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to latecomers on the open markets~\cite{zetzsche2018ico,li2018initial}.
-ICOs started to experiment with different \textit{fair} capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}.
-We show empirical evidence of a miner purchasing tokens ahead of other users in Status.im.
-Finally, proposals to eliminate or mitigate front-running from DApps are scattered across forums, proposed standards (called EIPs in Ethereum) and academic papers; we systemize them in the last section.
+We also study initial coin offerings (ICOs).
+Finally, we provide a categorization of  techniques to eliminate or mitigate front-running including transaction sequencing, cryptographic techniques like commit/reveal, and redesigning the functioning of the DApp to provide the same utility while removing time dependencies.
+
+% Jeremy: We give this later so that is fine
+%\footnote{Selected DApps from each category of the top 25 most active, based on user activity gathered from DAppRadar \url{https://DAppradar.com/DApps}}
 
@@
 
+After a few hacking incidents of high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered.
+This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to latecomers on the open markets~\cite{zetzsche2018ico,li2018initial}.
+ICOs started to experiment with different \textit{fair} capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}.
+We show empirical evidence of a miner purchasing tokens ahead of other users in Status.im.
+
 \subsection{\textit{Status.im} ICO}

### 2018-12-13 frontrunning/Latex/sections/abstract.tex
Revert "intro squeeze"
This reverts commit 7f46728a2437d5c4018b4177b0e990c1b3d6c4b7.

@@
 Front-running has been an issue in traditional financial instrument markets since the 1970's.
-With the advent of the blockchain technology, front-running resurfaced in new forms we explore here, due to blockchain's decentralized and transparent nature.
-In this paper, we draw from a scattered body of knowledge and instances of front-running across the top 25 decentral applications (DApps) deployed on Ethereum.
+With the advent of the blockchain technology, front-running has resurfaced in new forms we explore here, instigated by blockchain's decentralized and transparent nature.
+In this paper, we draw from a scattered body of knowledge and instances of front-running across the top 25 most active decentral applications (DApps) deployed on Ethereum.
 Additionally, we carry out a detailed analysis of \textsf{Status.im} initial coin offering (ICO) and show evidence of abnormal miner's behaviour indicative of front-running token purchases.

### 2018-12-13 frontrunning/Latex/sections/abstract.tex
into squeeze again

@@
 Additionally, we carry out a detailed analysis of \textsf{Status.im} initial coin offering (ICO) and show evidence of abnormal miner's behaviour indicative of front-running token purchases.
-Developers don't have the mindset to design DApps with front-running in mind.
-This is an attempt to bring forward the subject and make them more aware of these type of attacks.
-Finally, we introduce a framework for categorizing proposed solutions to front-running and examine the applicability to the identified issues.
+Finally, we map proposed solutions to front-running into useful categories.
 \end{abstract}
+
+% Jeremy: Commenting out this, too opinionated
+
+% Developers don't have the mindset to design DApps with front-running in mind. This is an attempt to bring forward the subject and make them more aware of these type of attacks.

### 2018-12-13 frontrunning/Latex/sections/paper.tex
more eidts and squeezing

@@
 In 2012, it was expanded further with the new amendment, FINRA Rule 5270, to cover trading in options, derivatives, or other financial instruments overlying a security with only a few exceptions~\cite{sec2012frontrunning,finra_2012}.
-Similar issues have been seen in domain industry~\cite{sac022en33:online,edelman2009front} as well.
+Similar issues have been seen with domain names~\cite{sac022en33:online,edelman2009front} as well.
 
@@
 
-In one sense, blockchain technology (which was introduced via Bitcoin in 2008~\cite{nakamoto2008bitcoin}) strives to disintermediate certain central parties that participate in a transaction.
+\begin{figure}[t]
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,bottom},capbesidewidth=0.3\linewidth}}]{figure}[\FBwidth]
+{\caption{The adversarial miner monitors the Ethereum mempool for decentralized exchange transactions.
+Upon spotting a profitable cancellation transaction, he puts his buy order prior to the cancel transaction in the block he mines.
+Doing so, the miner can profit from the underlying trade and also get the gas included in the cancel transaction.}\label{fig:MinerFrontrunning}}
+{\includegraphics[width=\linewidth]{figures/Miner_reorder_frontrun.png}}
+\end{figure}
+%https://www.lucidchart.com/invitations/accept/c8768786-4a3f-4c78-b3c8-aa04a6b81d06
+
+In one sense, blockchain technology (introduced via Bitcoin in 2008~\cite{nakamoto2008bitcoin}) strives to disintermediate certain central parties that participate in a transaction.
 However, blockchains also introduce new participants in the relaying and finalization (\ie mining) of transactions that can act as front-runners.
@@
 
-\begin{figure}[t]
-\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,bottom},capbesidewidth=0.3\linewidth}}]{figure}[\FBwidth]
-{\caption{The adversarial miner monitors the Ethereum mempool for decentralized exchange transactions.
-Upon spotting a profitable cancellation transaction, he puts his buy order prior to the cancel transaction in the block he mines.
-Doing so, the miner can profit from the underlying trade and also get the gas included in the cancel transaction.}\label{fig:MinerFrontrunning}}
-{\includegraphics[width=\linewidth]{figures/Miner_reorder_frontrun.png}}
-\end{figure}
-%https://www.lucidchart.com/invitations/accept/c8768786-4a3f-4c78-b3c8-aa04a6b81d06
+% Jeremy: Merge this
+%Finally, we note that in addition to the three things the front-runner wants to accomplish, there are three basic mechanisms to accomplishing them: (1) miners can choose transaction order, (2) non-miners can prioritize their later transactions over earlier transactions with higher gas fees, and (3) well-positioned network nodes can try to influence how transactions are propagated through the network.
 
@@
 \section{A Taxonomy of Front-running Attacks}
+\label{sec:taxonomy}
 
@@
 We only observe this attack pattern in one DApp and the details are quite specific to it, so we defer discussion until Section~\ref{sec:gambling}.
-
-Finally, we note that in addition to the three things the front-runner wants to accomplish, there are three basic mechanisms to accomplishing them: (1) miners can choose transaction order, (2) non-miners can prioritize their later transactions over earlier transactions with higher gas fees, and (3) well-positioned network nodes can try to influence how transactions are propagated through the network.
 
@@
 
-% Is this the same as order flooding in HFT?
+We classify this in the unique category of a suppression attack in our taxonomy (see Section~\ref{sec:taxonomy}).
+At first glance, it seemed like an asymmetric/bulk displacement attack on any new ticket purchase transactions.
+However the key difference is that the front-runner does not care about the execution of her transactions---if miners mined empty blocks for three minutes, that would be fine as well.
+Thus, front-running in this case is not the end-goal of the adversary, the way it is in each other category, but is rather a means to an end.
 
@@
 Ethereum miners store pending transactions in pools and draw from them when forming blocks.
-As the term `pool' implies, there is no instinct order to how transactions are drawn from the pool and miners are free to sequence them arbitrarily.\footnote{Sometimes the pool is called a `queue.' It is important to note is a misnomer as queues use a first-in-first-out sequence.} This enables certain kinds of front-running, in particular transactions the miner will place before a pending transaction\footnote{The vanilla Go-Ethereum implementation, prioritizes transactions based on their gas price and nonce~\cite{EthMinerTxOrder}}.
+As the term `pool' implies, there is no intrinsic order to how transactions are drawn and miners are free to sequence them arbitrarily.\footnote{Sometimes the pool is called a `queue.' It is important to note is a misnomer as queues enforce a first-in-first-out sequence.} The vanilla Go-Ethereum (geth) implementation prioritizes transactions based on their gas price and nonce~\cite{EthMinerTxOrder}.
+Because no rule is enforced, miners can sequence transactions in advantageous ways.
 A number of proposals attempt to thwart this attack by enforcing a rule about how to sequence transactions.
@@
 First-in-first-out (FIFO) is generally not possible on a distributed network because transactions can reach different nodes in a different order.
-While the network could form a consensus based on locally observed FIFO, this would increase the rate of orphaned blocks, as well as adding complexity to the protocol.
-A trusted third party could be used to assign sequential numbers to transactions (and sign them), but this is contrary to the blockchain's core innovation of distributed trust.
-None the less, some exchanges will centralize time-sensitive functionalities (\eg  \textit{EtherDelta} and \textit{0xProject}) in off-chain order books~\cite{warren20170x,0xfrontrunning:online}).
+While the network could theoretically form a consensus based on locally observed FIFO, this would increase the rate of orphaned blocks, as well as adding complexity to the protocol.
+A trusted third party can be used to assign sequential numbers to transactions (and sign them), but this is contrary to blockchain's core innovation of distributed trust.
+None the less, some exchanges do centralize time-sensitive functionalities (\eg  \textit{EtherDelta} and \textit{0xProject}) in off-chain order books~\cite{warren20170x,0xfrontrunning:online}.
 
-An alternative is to sequence transactions psuedorandomly.
+One alternative is to sequence transactions psuedorandomly.
 This can be seen in proposals like Canonical Transaction Ordering Rule (CTOR) by Bitcoin Cash ABC~\cite{bitcoincashabcFork} which adds transactions in lexicographical order according to their hash~\cite{bitcoinABC2018CTOR}.
@@
 
-The final main category of mitigation is to assume front-running is unpreventable and to thus responsively redesign the functionality of the DApp to remove any benefit from front-running.
-For example, when designing a decentralized exchange, one can use a call market design instead of a time-sensitive order book~\cite{clark2014decentralizing} to side-step and disincentivize front-running by miners.
+The final main category of mitigation is to assume front-running is unpreventable and to thus responsively redesign the functionality of the DApp to remove any benefit from it.
+For example, when designing a decentralized exchange, one can use a call market design instead of a time-sensitive order book~\cite{clark2014decentralizing} to side-step and disincentivize front-running.
 In a call market design, the arrival time of orders does not matter as they are executed in batches.
@@
 
-% Jeremy: This needs some clarification; what exactly is the principle they are applying???
-%Shayan: Is this better?
-they basically use economical model for welfare of the traders in a transparent environment.
-To extend the idea more, we need to dive in their economical model which I think is out of scope of this paper.
 Malinova and Park discuss similar design consideration for financial markets and trading platforms to mitigate front-running~\cite{malinova2017market}.
@@
 To prevent front-running, the liquidity demander offers the liquidity-providing trader an incentive; establishing an equilibrium behaviour, in which front-runner needs to pay more incentives to come in front of the original trade, making front-running not too profitable.
-
-% one solution could be to remove multiple actors, meaning that on each "play" (order), the smart contract would be the market maker.
-it does not matter if there are multiple similar orders.
-similar to PoC of Velocity~\cite{eskandari2017feasibility}.
-Although there are other concerns about this specific design but not for front-running.
-
-%TODO: inline talk about what these solutions are good for and if they fit Status ICO
 

### 2018-12-13 frontrunning/Latex/sections/paper.tex
[frontrunning] fix typo and caption placement

@@
 \begin{figure}[t]
-\floatbox[{\capbeside\thisfloatsetup{capbesideposition={left,bottom},capbesidewidth=0.3\linewidth}}]{figure}[\FBwidth]
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={left,top},capbesidewidth=0.3\linewidth}}]{figure}[\FBwidth]
 {\caption{This chart shows the miners behaviour on the time window that Status.im ICO was running.
@@
 \begin{figure}[t]
-\floatbox[{\capbeside\thisfloatsetup{capbesideposition={left,top},capbesidewidth=0.5\linewidth}}]{figure}[\FBwidth]
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,bottom},capbesidewidth=0.5\linewidth}}]{figure}[\FBwidth]
 {\caption{Prior to \textit{Status.im} ICO  \textit{F2Pool} deposited 100 Ether in multiple new Ethereum addresses.
@@
 
-\footnotetext{Graph was made using \url{Blockseer.com}}
+\footnotetext{Graph was made using \url{Blockseer.com} blockchain explorer.}
 

### 2018-12-13 frontrunning/Latex/sections/paper.tex
some minor edits

--- 2018-12-13 frontrunning/Latex/sections/paper.tex
@@
 Instead of providing the details of exact solutions which will change over time, we extract the main principles or primitives that address the attack.
-A particular system may implement more in a layered mitigation approach.
+A particular system may implement more than one in a layered mitigation approach.
 
@@
 This can be seen in proposals like Canonical Transaction Ordering Rule (CTOR) by Bitcoin Cash ABC~\cite{bitcoincashabcFork} which adds transactions in lexicographical order according to their hash~\cite{bitcoinABC2018CTOR}.
-Note that Bitcoin does not have a front-running problem for most standard transactions.
+Note that Bitcoin does not have a front-running problem for standard transactions.
 While this could be used by Ethereum to make front-running statistically difficult, the protection is marginal at best and might even exacerbate attacks.
@@
 Finally, transactions themselves could enforce order.
-In particular, they could point to the current state of the contract and only execute on that exact state.
-This transaction chaining only prevents certain sub-types of front-running.
-For example, it could prevent scalping attacks: if Alice buys from a marketplace that matches her order to Bob with a price improvement, a miner could buy from Bob first and then execute Alice's original transaction which results in her being matched to Alice instead.
-By contrast, if Alice registers an interesting-looking domain name, transaction chaining does not stop a miner from replacing Alice's request with her own.
-Transaction chaining would likely lead to more orphaned transactions for active contracts, as only one state-changing transaction would be allowed per state.
+For example, they could specify the current state of the contract as the only state to execute on.
+This transaction chaining only prevents certain types of front-running; \ie it prevents insertion attacks but not displacement attacks (recall our taxonomy in Section~\ref{sec:taxonomy}).
+As transaction chaining only allows one state-changing transaction per state, at most one of a set of concurrent transactions can be confirmed.
 

### 2018-12-13 frontrunning/Latex/sections/paper.tex
more minor

@@
 For example, in a financial exchange where the number of other orders might be in a predictable interval, an adversary can spray the sequence (\ie a price-time priority queue) with multiple committed transactions and no intention of executing them all.
-She then only reveal the ones that result in an advantageous trade.\footnote{This is analogous to behaviour in traditional financial markets where high frequency traders will make and cancel orders at many price points --flash orders or pinging--.
+She then only reveal the ones that result in an advantageous trade.\footnote{This is analogous to behaviour in traditional financial markets where high frequency traders will make and cancel orders at many price points (flash orders or pinging).
 If they can cancel faster than someone can execute it---someone who has only seen the order and not the cancelation---then the victim reveals their price information.} There are other ways of aborting; if payments are required but not collateralized, the aborting party can ensure that payment is not available for transfer.
@@
 \paragraph{Enhanced Commit/Reveal.} Submarine Commitments~\cite{libsubmarine,submarinesendHD} extend the confidentiality of the commit and reveal, so that the commitment transaction is identical to a transaction to a newly generated Ethereum address.
-(1) they initially hide the contract address being invoked, providing (3,4,5)-confidentiality during the commit phase; and (2) they ensure that if a revealed transaction sent funds, the funds were fully collateralized at commit time and are available to the receiving smart contract.
+They initially hide the contract address being invoked, providing (3,4,5)-confidentiality during the commit phase; and they ensure that if a revealed transaction sent funds, the funds were fully collateralized at commit time and are available to the receiving smart contract.
 See Figure~\ref{fig:LibSubmarine}.

### 2018-12-13 frontrunning/Latex/sections/paper.tex
minor edits + running textidote

@@
 Front-running originates on the Chicago Board Options Exchange (\textit{CBoE}) \cite{markham1988front}.
-The Securities Exchange Commission \textit{(SEC)} in 1977 defines it as: ``The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{A block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}'' Self-regulating exchanges (\eg \textit{CBoE}) and the \textit{SEC} spent the ensuing years planning how to detect and outlaw front-running practices~\cite{markham1988front}.
+The Securities Exchange Commission \textit{(SEC)} in 1977 defines it as: ``The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{A block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily changes the price.} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}'' Self-regulating exchanges (\eg \textit{CBoE}) and the \textit{SEC} spent the ensuing years planning how to detect and outlaw front-running practices~\cite{markham1988front}.
 The \textit{SEC} stated: ``It seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge.\footnote{Securities Exchange Act Release No.
@@
 
-To find example DApps to study, we use the top 25 DApps based on recent user activity from \texttt{DAppradar.com} and sample it in the first week of September 2018\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}}.
+To find example DApps to study, we use the top 25 DApps based on recent user activity from \texttt{DAppradar.com} and sample it in the first week of September 2018\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}.}.
 User activity is admittedly an imperfect metric for finding the `most significant' DApps: significant DApps might be lower volume overall or for extended periods of time (\eg ICOs, which we remedy by studying independently in Section~\ref{sec:ICOsfrontrunning}).
@@
 The first category of DApp in Table~\ref{tab:top25DApps} is exchanges.
-Exchanges such as EtherDelta\footnote{Also known as ForkDelta for the UI \url{https://forkdelta.app/}}, purport to implement a decentralized exchange, however, their order books are stored on a central server they control and shown to their users with a website interface.
+Exchanges such as EtherDelta\footnote{Also known as ForkDelta for the UI \url{https://forkdelta.app/}.}, purport to implement a decentralized exchange, however, their order books are stored on a central server they control and shown to their users with a website interface.
 Central exchanges can front-run orders in the traditional sense, as well as re-order or block orders on their servers.
@@
 The second category of DApp in Table~\ref{tab:top25DApps} is crypto-collectables.
-Consider Cryptokitties\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}}, the most active DApp in this category and third most active overall.
+Consider Cryptokitties\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}.}, the most active DApp in this category and third most active overall.
 Each kitty (see Appendix~\ref{app:cryptokitty}) is a cartoon kitten with a set of unique features to distinguish it from other cryptokitties, some features are rarer and harder to obtain.
@@
 It contains the kitty's ID which can be found either on their website or on the ERC721 token smart contract.
-This is similar to open auctions and markets on section~\ref{sec:frontrunningExchanges}, bid value and the object bidding on is visible to the network and any user could  easily front-run by sending the same transaction with higher gasPrice to replace the initial bidder.
+This is similar to open auctions and markets on Section~\ref{sec:frontrunningExchanges}, bid value and the object bidding on is visible to the network and any user could  easily front-run by sending the same transaction with higher gasPrice to replace the initial bidder.
 The front-runner can see there is an interest in a specific kitty and by buying it and auctioning it at a higher price can profit from the transaction.
@@
 
-\textsf{Fomo3D} is an example of a game style (known as \textsf{Exit Scam}\footnote{\url{https://exitscam.me/play}}) not based on random outcomes, and it is the most active game on Ethereum in our sample.
+\textsf{Fomo3D} is an example of a game style (known as \textsf{Exit Scam}\footnote{\url{https://exitscam.me/play}.}) not based on random outcomes, and it is the most active game on Ethereum in our sample.
 The aim of this game is to be the last person to have purchased a ticket when a timer goes to zero in a scenario where anyone can buy a ticket and each purchase increases the timer by 30 seconds.
-Many speculated such a game would never end but on August 22, 2018, the first round of the game ended with the winner collecting 10,469 Ether\footnote{The first winner of Fomo3D, won 10,469 Ether \url{ https://etherscan.io/tx/0xe08a519c03cb0aed0e04b33104112d65fa1d3a48cd3aeab65f047b2abce9d508}} equivalent to \$2.1M USD at the time.
+Many speculated such a game would never end but on August 22, 2018, the first round of the game ended with the winner collecting 10,469 Ether\footnote{The first winner of Fomo3D, won 10,469 Ether \url{ https://etherscan.io/tx/0xe08a519c03cb0aed0e04b33104112d65fa1d3a48cd3aeab65f047b2abce9d508}.} equivalent to \$2.1M USD at the time.
 Blockchain forensics indicate a sophisticated winning strategy to front-run new ticket purchases~\cite{fomo3dhacker,fomo3dmedium} that would reset the counter.
@@
 While the default client and online blockchain explorers offer some limited query capabilities, in order to analyze this case, we built our own database.
-Specifically, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation\url{https://github.com/ethereum/go-ethereum}} for the full node, a python script for extracting, transforming and loading Ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery.\footnote{\url{https://cloud.google.com/bigquery/}} Using this software stack, we were able to isolate transactions within the Status.im ICO.
+Specifically, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation\url{https://github.com/ethereum/go-ethereum}.} for the full node, a python script for extracting, transforming and loading Ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery.\footnote{\url{https://cloud.google.com/bigquery/}} Using this software stack, we were able to isolate transactions within the Status.im ICO.
 We used data analysis tool \texttt{Tableau}.\footnote{\url{https://www.tableau.com/}} A copy of this dataset and the initial findings can be found in our Github repository.\footnote{\url{github.com/} Removed for anonymity.}
@@
 
-By tracing the transactions from these 30 addresses, we found explicit interference by the F2Pool\footnote{F2Pool Ethereum address was identified by their mining reward deposit address \url{https://etherscan.io/address/0x61c808d82a3ac53231750dadc13c777b59310bd9}} in this scenario.
+By tracing the transactions from these 30 addresses, we found explicit interference by the F2Pool\footnote{F2Pool Ethereum address was identified by their mining reward deposit address \url{https://etherscan.io/address/0x61c808d82a3ac53231750dadc13c777b59310bd9}.} in this scenario.
 As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses were sent to Status.im ICO and mined by F2Pool themselves, where the dynamic ceiling algorithm refunded a portion of the deposited funds back to these addresses, these funds were sent back to F2Pool main address a few days after and the tokens were aggregated later on in one single address.

### 2018-12-13 frontrunning/Latex/sections/abstract.tex
minor edits + running textidote
grammarly

@@
 We consider \textit{front-running} to be a course of action where an entity benefits from prior access to privileged market information about upcoming transactions and trades.
-Front-running has been an issue in traditional financial instrument markets since the 1970's.
+Front-running has been an issue in financial instrument markets since the 1970s.
 With the advent of the blockchain technology, front-running has resurfaced in new forms we explore here, instigated by blockchain's decentralized and transparent nature.
-In this paper, we draw from a scattered body of knowledge and instances of front-running across the top 25 most active decentral applications (DApps) deployed on Ethereum.
+In this paper, we draw from a scattered body of knowledge and instances of front-running across the top 25 most active decentral applications (DApps) deployed on Ethereum blockchain.
 Additionally, we carry out a detailed analysis of \textsf{Status.im} initial coin offering (ICO) and show evidence of abnormal miner's behaviour indicative of front-running token purchases.
-Finally, we map proposed solutions to front-running into useful categories.
+Finally, we map the proposed solutions to front-running into useful categories.
 \end{abstract}

### 2018-12-13 frontrunning/Latex/sections/paper.tex
grammarly

@@
 Function calls (or transactions) to the DApp are processed by a decentralized network.
-Transactions are finalized in stages: they (generally) first relay around the network, then are selected by a miner and put into a valid block, and finally, the block is well-enough incorporated that is unlikely to be reorganized.
+Transactions are finalized in stages: they (generally) first relay around the network, then selected by a miner and put into a valid block, and finally, the block is well-enough incorporated that is unlikely to be reorganized.
 Front-running is an attack where a malicious node observes a transaction after it is broadcast but before it is finalized, and attempts to have its own transaction confirmed before or instead of the observed transaction.
@@
 Therefore, DApps need to be studied individually or in categories.
-In this paper we draw from a scattered body of knowledge regarding front-running attacks on blockchain applications and proposed solutions, with series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps).
+In this paper, we draw from a scattered body of knowledge regarding front-running attacks on blockchain applications and proposed solutions, with series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps).
 We do case studies on decentralized exchanges (\eg Bancor), crypto-collectibles (\eg CryptoKitties), gambling services (\eg Fomo3D), and decentralized name services (\eg Ethereum Name Service).
@@
 In front-running, a person sees a concrete transaction that is set to execute and reacts to it before it actually gets executed.
-If the person instead has access to more general privileged information that might predict future transactions, but is not reacting at the actual pending trades, we would classify this activity as insider trading.
+If the person instead has access to more general privileged information that might predict future transactions but is not reacting at the actual pending trades, we would classify this activity as insider trading.
 If the person reacts after the trade is executed, or information is made public, and profits from being the fastest to react, this is considered arbitrage and is legal and encouraged because it helps markets integrate new information into prices quickly.
@@
 Front-running originates on the Chicago Board Options Exchange (\textit{CBoE}) \cite{markham1988front}.
-The Securities Exchange Commission \textit{(SEC)} in 1977 defines it as: ``The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{A block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily changes the price.} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}'' Self-regulating exchanges (\eg \textit{CBoE}) and the \textit{SEC} spent the ensuing years planning how to detect and outlaw front-running practices~\cite{markham1988front}.
+The Securities Exchange Commission \textit{(SEC)} in 1977 defines it as: ``The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{A block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily change the price.} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}'' Self-regulating exchanges (\eg \textit{CBoE}) and the \textit{SEC} spent the ensuing years planning how to detect and outlaw front-running practices~\cite{markham1988front}.
 The \textit{SEC} stated: ``It seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge.\footnote{Securities Exchange Act Release No.
@@
 
-% we can say other illegal activities in the tranditional system, such as wash trading, ...
-(notes from AMF) could fall under our definition of front running on blockchain apps, as the transparency and public nature of the transactions could result in any actor to be involved in such trades?
+% we can say other illegal activities in the traditional system, such as wash trading, ...
+(notes from AMF) could fall under our definition of front-running on blockchain apps, as the transparency and public nature of the transactions could result in any actor to be involved in such trades?
 does it make sense?
@@
 However, blockchains also introduce new participants in the relaying and finalization (\ie mining) of transactions that can act as front-runners.
-Any user monitoring blockchain network transactions (\eg running a full node) can see an unconfirmed transactions and broadcast a reactionary transaction that might be confirmed ahead of the original transaction.
+Any user monitoring blockchain network transactions (\eg running a full node) can see an unconfirmed transaction and broadcast a reactionary transaction that might be confirmed ahead of the original transaction.
 For regular users to front-run others on the blockchain, they need to be well connected to other nodes on the network and listen to the network to monitor all transactions that are broadcast.
@@
 
-In the cryptographic literature, front-running attacks are modelled by allowing a `rushing' adversary to interact with the protocol.
+In the cryptographic literature, front-running attacks are modeled by allowing a `rushing' adversary to interact with the protocol.
 In particular, ideal functionalities of blockchains (such as those used in simulation-based proofs) need to capture this adversarial capability, assuming the real blockchain does not address front-running.
@@
 
-As we will illustrate with examples through-out the paper, front-running attacks can often be reduced to one of a few basic templates.
-First we consider what the adversary is trying to accomplish (without worrying about how) and we distinguish three cases: displacement, insertion, and suppression attacks.
+As we will illustrate with examples throughout the paper, front-running attacks can often be reduced to one of a few basic templates.
+First, we consider what the adversary is trying to accomplish (without worrying about how) and we distinguish three cases: displacement, insertion, and suppression attacks.
 In all three cases, Alice is trying to invoke a function on a contract that is in a particular state, and Mallory will try to invoke her own function call on that contract in that particular state before Alice.
@@
 We call this \textit{asymmetric displacement}.
-Finally, in some cases, Mallory is trying to run a large set of functions: for example Alice and others are trying to buy a limited set of shares offered by a firm on a blockchain.
+Finally, in some cases, Mallory is trying to run a large set of functions: for example, Alice and others are trying to buy a limited set of shares offered by a firm on a blockchain.
 We call this \textit{bulk displacement}.
@@
 0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the order book holders and could front-run the orders they relay.
-As seen in traditional financial markets, one method to manipulation the spot price of an asset, is to flood the market with orders and cancel them when there are filling orders --taker's griefing~\cite{consesnsys0xReview2017}.
+As seen in traditional financial markets, one method to manipulation the spot price of an asset is to flood the market with orders and cancel them when there are filling orders --taker's griefing~\cite{consesnsys0xReview2017}.
 As mentioned putting an order in the current decentralized exchange is free, but to prevent taker's griefing attacks, the user needs to send a transaction to cancel each of his orders.
@@
 Since Bancor handles all the trades and exchanges on the chain (unlike other existing decentralized exchanges), these transactions are all visible to the public for some time before being included within a block.
-This leaves Bancor vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions, in which they can gain favourable profits by buying before the order and fill the original order with slightly higher price~\cite{BancorIs7:online}.
+This leaves Bancor vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions, in which they can gain favorable profits by buying before the order and fill the original order with slightly higher price~\cite{BancorIs7:online}.
 Researchers have shown and implemented a proof of concept code to front-run Bancor as a non-miner user~\cite{NewTab13:online}.
@@
 At first glance, it seemed like an asymmetric/bulk displacement attack on any new ticket purchase transactions.
-However the key difference is that the front-runner does not care about the execution of her transactions---if miners mined empty blocks for three minutes, that would be fine as well.
-Thus, front-running in this case is not the end-goal of the adversary, the way it is in each other category, but is rather a means to an end.
+However, the key difference is that the front-runner does not care about the execution of her transactions---if miners mined empty blocks for three minutes, that would be fine as well.
+Thus, front-running, in this case, is not the end-goal of the adversary, the way it is in each other category but is rather a means to an end.
 
@@
 \subsection{Data Collection and Analysis}
-According to analysis we carried out, we discovered that the F2Pool---an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure~\ref{fig:mining_pool_ratio})---sent 100 Ether to 30 new Ethereum addresses before the Status.im ICO started.
+According to the analysis we carried out, we discovered that the F2Pool---an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure~\ref{fig:mining_pool_ratio})---sent 100 Ether to 30 new Ethereum addresses before the Status.im ICO started.
 When the ICO opened, F2Pool constructed 31 transactions to the ICO smart contract from these new address, without broadcasting the transactions to the network.
@@
 
-As we studied front-running attacks on blockchain, we also encountered a number of ways of preventing, detecting, or mitigating front-running attacks.
+As we studied front-running attacks on the blockchain, we also encountered a number of ways of preventing, detecting or mitigating front-running attacks.
 Instead of providing the details of exact solutions which will change over time, we extract the main principles or primitives that address the attack.
@@
 In the second category, cryptographic techniques are used to limit the visibility of transactions, giving the potential front-running less information to base their strategy on.
-In the final category, dapps are designed from the bottom-up to remove the importance of transaction ordering or time in their operations.
-We also note that for dapps that are legally well-formed (\eg with identified parties and a clear jurisdiction), front-running attacks can violate laws, which is its own deterrent.
+In the final category, DApps are designed from the bottom-up to remove the importance of transaction ordering or time in their operations.
+We also note that for DApps that are legally well-formed (\eg with identified parties and a clear jurisdiction), front-running attacks can violate laws, which is its own deterrent.
 We do not discuss this further here; see Appendix ~\ref{app:traditionalprevention}.
@@
 
-One alternative is to sequence transactions psuedorandomly.
+One alternative is to sequence transactions pseudorandomly.
 This can be seen in proposals like Canonical Transaction Ordering Rule (CTOR) by Bitcoin Cash ABC~\cite{bitcoincashabcFork} which adds transactions in lexicographical order according to their hash~\cite{bitcoinABC2018CTOR}.
@@
 
-Finally, transactions themselves could enforce order.
+Finally, the transactions themselves could enforce an order.
 For example, they could specify the current state of the contract as the only state to execute on.
@@
 
-All transaction details in Bitcoin are make public and participant identities are only lightly protected.
+All transaction details in Bitcoin are made public and participant identities are only lightly protected.
 A number of techniques increase confidentiality~\cite{bunzBulletproofs,maxwell2015confidential} and anonymity ~\cite{miers2013zerocoin,cryptoeprint2015,sasson2014zerocash} for cryptocurrencies.
@@
 It is tempting to think that a confidential DApp would not permit front-running, as the front-runner would not know the details of the transaction she is front-running.
-However there are some nuances here to explore.
+However, there are some nuances here to explore.
 
@@
 Confidentiality applied to a DApp could mean different levels of protection for each of these.
-For front-running, function calls (3,4) are the most important, however function calls could be inferred from state changes (2).
+For front-running, function calls (3,4) are the most important, however, function calls could be inferred from state changes (2).
 Hawk~\cite{kosba2016hawk} and Ekiden~\cite{cheng2018ekiden} are examples of (2,3,4)-confidentiality (with limitations we are glossing over).
@@
 The applicability of privacy-preserving blockchains needs to be evaluated on a case-by-case base.
-For example, one method used by traditional financial exchanges in dealing with front-running from high frequency traders is a dark market: essentially a (2,3,4)-confidential order book maintained by a trusted party.
+For example, one method used by traditional financial exchanges in dealing with front-running from high-frequency traders is a dark market: essentially a (2,3,4)-confidential order book maintained by a trusted party.
 A DApp could disintermediate this trusted party.
-Users whose balances are effected by changes in the contract's state would need to be able to learn this information.
+Users whose balances are affected by changes in the contract's state would need to be able to learn this information.
 Further, if the contract addresses are known (no 5-confidentiality), front-runners can know about the traffic pattern of calls to contracts which could be sufficient grounds for attack; for example, if each asset on an exchange has its own market contract, this leaks trade volume information.
@@
 %Shayan: maybe just a reference ^ suffices! 
-%A recent attempt to build confidential transactions for DApps, is AZTEC protocol~\cite{aztec2018}.
+%A recent attempt to build confidential transactions for DApps is AZTEC protocol~\cite{aztec2018}.
 Similar to ZCash ~\cite{hopwood2016zcash}, it uses the concept of encrypted ‘notes’ and join-split transactions.
-ZCash uses two distinct types of addresses, transparent and shielded addresses, where in AZTEC, user transfers her ERC20 tokens into encrypted notes.
+ZCash uses two distinct types of addresses, transparent and shielded addresses, wherein AZTEC, the user transfers her ERC20 tokens into encrypted notes.
 Users can transfer these notes by destroying the unspent notes and creating new notes for the new owners, where the sum of the old notes should be equal to the sum of the new notes.
 %Shayan: Talk about AZTEC confidential transactions and their approach for CT.
-it will be possible to do dark pool style transactions within Ethereum dapps however they would still expose some information such as sender, receiver (exposes 5,6), hides (3,4?).
+it will be possible to do dark pool-style transactions within Ethereum DApps however they would still expose some information such as sender, receiver (exposes 5,6), hides (3,4?).
 https://medium.com/aztec-protocol/confidential-transactions-have-arrived-a-dive-into-the-aztec-protocol-a1794c00c009
@@
 
-While confidentiality appears insufficient for solving domain name front-running alone, a hybrid approach of sequencing and confidentiality can be effective, and is in fact an example of an older cryptographic trick known as commit/reveal.
-The essence of the approach is to protect the function call (\eg (3,4)- or (4)-confidentiality) until the function is enqueued in sequence of functions to be executed.
-Once the sequence is established, the confidentiality is lifted and the function can only be executed in the place is was given (or, generally speaking, not at all).
+While confidentiality appears insufficient for solving domain name front-running alone, a hybrid approach of sequencing and confidentiality can be effective and is, in fact, an example of an older cryptographic trick known as commit/reveal.
+The essence of the approach is to protect the function call (\eg (3,4)- or (4)-confidentiality) until the function is enqueued in a sequence of functions to be executed.
+Once the sequence is established, the confidentiality is lifted and the function can only be executed in the place it was given (or, generally speaking, not at all).
 
@@
 After the delay, a second transaction reveals the details of the requested domain.
-This prevent front-running if the reveal transaction is confirmed faster than an adversarial node or miner can redo the entire process.
+This prevents front-running if the reveal transaction is confirmed faster than an adversarial node or miner can redo the entire process.
 
-Commit/reveal is a two round protocol, and aborting after the first round (early aborts) could be an issue for this (along with most multi-round cryptographic protocols).
+Commit/reveal is a two-round protocol, and aborting after the first round (early aborts) could be an issue for this (along with most multi-round cryptographic protocols).
 For example, in a financial exchange where the number of other orders might be in a predictable interval, an adversary can spray the sequence (\ie a price-time priority queue) with multiple committed transactions and no intention of executing them all.
-She then only reveal the ones that result in an advantageous trade.\footnote{This is analogous to behaviour in traditional financial markets where high frequency traders will make and cancel orders at many price points (flash orders or pinging).
+She then only reveal the ones that result in an advantageous trade.\footnote{This is analogous to behavior in traditional financial markets where high-frequency traders will make and cancel orders at many price points (flash orders or pinging).
 If they can cancel faster than someone can execute it---someone who has only seen the order and not the cancelation---then the victim reveals their price information.} There are other ways of aborting; if payments are required but not collateralized, the aborting party can ensure that payment is not available for transfer.
 One mitigation to early aborts that blockchain is uniquely positioned to make is having users post a fidelity bond of a certain amount of cryptocurrency that can be automatically dispensed if they fail to fully execute committed transactions (this is used in multi-round blockchain voting~\cite{mccorry2017smart}).
-Finally we note that any multiple round protocol will have usability challenges: users must be aware that participating in the first round is not sufficient for completing their intention.
+Finally, we note that any multiple round protocol will have usability challenges: users must be aware that participating in the first round is not sufficient for completing their intention.
 
@@
 They split big investments into smaller ones using intermediaries --liquidity demander-- and liquidity providers.
-To prevent front-running, the liquidity demander offers the liquidity-providing trader an incentive; establishing an equilibrium behaviour, in which front-runner needs to pay more incentives to come in front of the original trade, making front-running not too profitable.
+To prevent front-running, the liquidity demander offers the liquidity-providing trader an incentive; establishing an equilibrium behavior, in which front-runner needs to pay more incentives to come in front of the original trade, making front-running not too profitable.
 

### 2018-12-13 frontrunning/Latex/sections/abstract.tex
minor edit

@@
 In this paper, we draw from a scattered body of knowledge and instances of front-running across the top 25 most active decentral applications (DApps) deployed on Ethereum blockchain.
-Additionally, we carry out a detailed analysis of \textsf{Status.im} initial coin offering (ICO) and show evidence of abnormal miner's behaviour indicative of front-running token purchases.
+Additionally, we carry out a detailed analysis of \textsf{Status.im} initial coin offering (ICO) and show evidence of abnormal miner's behavior indicative of front-running token purchases.
 Finally, we map the proposed solutions to front-running into useful categories.

### 2018-12-14 frontrunning/Latex/sections/paper.tex
[frontrunning] one round edits till Crypto-Collectibles and sprinkle the Taxonomy

@@
 Therefore, DApps need to be studied individually or in categories.
-In this paper, we draw from a scattered body of knowledge regarding front-running attacks on blockchain applications and proposed solutions, with series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps).
+In this paper, we draw from a scattered body of knowledge regarding front-running attacks on blockchain applications and the proposed solutions, with series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps).
 We do case studies on decentralized exchanges (\eg Bancor), crypto-collectibles (\eg CryptoKitties), gambling services (\eg Fomo3D), and decentralized name services (\eg Ethereum Name Service).
@@
 
-\emph{Front-running} is a course of action where someone benefits from early access to market information about upcoming transactions and trades, typically because of a privileged position along the transmission of this information and is applicable to both financial and non-financial systems.
+Traditional \emph{Front-running} is a course of action where someone benefits from early access to market information about upcoming transactions and trades, typically because of a privileged position along the transmission of this information and is applicable to both financial and non-financial systems.
 In traditional stock exchanges, floor traders might overhear a broker's negotiation with her client over a large purchase, and literally race the broker to buy first, potentially profiting when the large sale temporarily reduces the supply of the stock.
@@
 Front-running originates on the Chicago Board Options Exchange (\textit{CBoE}) \cite{markham1988front}.
-The Securities Exchange Commission \textit{(SEC)} in 1977 defines it as: ``The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{A block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily change the price.} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}'' Self-regulating exchanges (\eg \textit{CBoE}) and the \textit{SEC} spent the ensuing years planning how to detect and outlaw front-running practices~\cite{markham1988front}.
+The Securities Exchange Commission \textit{(SEC)} in 1977 defined it as: ``The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{A block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily change the price.} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}'' Self-regulating exchanges (\eg \textit{CBoE}) and the \textit{SEC} spent the ensuing years planning how to detect and outlaw front-running practices~\cite{markham1988front}.
 The \textit{SEC} stated: ``It seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge.\footnote{Securities Exchange Act Release No.
@@
 Fitzsimmons, Secretary, Securities, and Exchange Commission to Joseph W.
-Sullivan, President  CBoE).}'' The \textit{CBoE} tried to educate their members on existing rules, however, differences in opinion regarding the unfairness of front-running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action~\cite{sec1978optionsmarket} until the SEC began regulation.
+Sullivan, President  CBoE).}'' The \textit{CBoE} tried to educate their members on existing rules, however, differences in opinion regarding the unfairness of front-running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action~\cite{sec1978optionsmarket} until the SEC began the regulation.
 We refer the reader interested in further details on this early regulatory history to Markham~\cite{markham1988front}.
@@
 Any user monitoring blockchain network transactions (\eg running a full node) can see an unconfirmed transaction and broadcast a reactionary transaction that might be confirmed ahead of the original transaction.
-For regular users to front-run others on the blockchain, they need to be well connected to other nodes on the network and listen to the network to monitor all transactions that are broadcast.
+For regular users to front-run others on the blockchain, they need to be well connected to other nodes on the network and monitor all transactions that are broadcast.
 On the Ethereum blockchain, users have to pay for the computations in a small amount of Ether called \textsf{gas}~\cite{AccountT67:online}.
@@
 Therefore, any regular user who runs a full-node Ethereum client can front-run pending transactions by sending similar transaction with a higher gas price.
-Also, blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this in case of malicious reordering is known as \textsf{transaction reordering} attack.
+Also, blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this case of malicious reordering is known as \textsf{transaction reordering attack}~\cite{luu2016making}.
 
@@
 The user can then broadcast a competing transaction that sends the same unspent coins to herself, perhaps using higher transaction fees, arrangements with miners or artifacts of the network topology to have the second transaction confirmed instead of the first.
-This can be considered a form of self-front-running.
+This can be considered a form of \textsf{self-front-running}.
 
@@
 As we will illustrate with examples throughout the paper, front-running attacks can often be reduced to one of a few basic templates.
-First, we consider what the adversary is trying to accomplish (without worrying about how) and we distinguish three cases: displacement, insertion, and suppression attacks.
+First, we consider what the adversary is trying to accomplish (without worrying about how) and we distinguish three cases: \textit{displacement}, \textit{insertion}, and \textit{suppression} attacks.
 In all three cases, Alice is trying to invoke a function on a contract that is in a particular state, and Mallory will try to invoke her own function call on that contract in that particular state before Alice.
@@
 In a \textit{displacement attack}, after Mallory runs her function, Alice's function is either orphaned or runs with no meaningful effect.
-Examples of displacement include: Alice trying to register a domain name and Mallory registering it first; Alice trying to submit a bug to receive a bounty and Mallory stealing it and submitting it first~\cite{}; and Alice trying to submit a bid in an auction and Mallory copying it.
+Examples of displacement include: Alice trying to register a domain name and Mallory registering it first; Alice trying to submit a bug to receive a bounty and Mallory stealing it and submitting it first \cite{breidenbach2018enter}; and Alice trying to submit a bid in an auction and Mallory copying it.
 In some cases, Alice's function and Mallory's function are different: \eg Alice trying to cancel an offer and Mallory fulfilling the offer first.
 We call this \textit{asymmetric displacement}.
-Finally, in some cases, Mallory is trying to run a large set of functions: for example, Alice and others are trying to buy a limited set of shares offered by a firm on a blockchain.
+Finally, in some cases, Mallory is trying to run a large set of functions: \eg Alice and others are trying to buy a limited set of shares offered by a firm on a blockchain.
 We call this \textit{bulk displacement}.
@@
 The first category of DApp in Table~\ref{tab:top25DApps} is exchanges.
-Exchanges such as EtherDelta\footnote{Also known as ForkDelta for the UI \url{https://forkdelta.app/}.}, purport to implement a decentralized exchange, however, their order books are stored on a central server they control and shown to their users with a website interface.
+Exchanges such as EtherDelta\footnote{Also known as ForkDelta for the UI \url{https://forkdelta.app/}.}, purport to implement a decentralized exchange, however, their order books are stored on a central server they control and shown to their users using a website interface.
 Central exchanges can front-run orders in the traditional sense, as well as re-order or block orders on their servers.
 0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the order book holders and could front-run the orders they relay.
-As seen in traditional financial markets, one method to manipulation the spot price of an asset is to flood the market with orders and cancel them when there are filling orders --taker's griefing~\cite{consesnsys0xReview2017}.
-As mentioned putting an order in the current decentralized exchange is free, but to prevent taker's griefing attacks, the user needs to send a transaction to cancel each of his orders.
-The reason for canceling order could be the unprofitability of the order due to price change.
-In this case, when an adversarial actor sees a pending cancellation transaction, he sends a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled, this is known as \textit{\todo{cancellation grief}}.
+As seen in traditional financial markets, one method to manipulation the spot price of an asset is to flood the market with orders and cancel them when there are filling orders --taker's griefing--~\cite{consesnsys0xReview2017}.
+As mentioned, putting an order in the current decentralized exchange is off-blockchain and free, but to prevent taker's griefing attacks, the user needs to send a transaction to cancel each of his orders.
+The reason for canceling an order could be the unprofitability of the order due to price change.
+In this case, when an adversarial actor sees a pending cancellation transaction, conducts an front-running \textit{asymmetric displacement} attack to get in front of the cancellation order and take the order before it is canceled, this is also known as \textit{cancellation grief}.
 This is illustrated in Figure~\ref{fig:MinerFrontrunning}.
@@
 An adversary can monitor the network with a full node for pending \textit{buy} (or \textit{sell}) transactions which could increase (or \textit{decrease}) the future price of the asset.
-A front-runner can send a competing order with a higher gas price and hope to have her transactions mined ahead of the original pending transaction.
+A front-runner using a \textit{insertion attack} can send a competing order with a higher gas price and hope to have her transactions mined ahead of the original pending transaction.
 The benefits of doing this vary.
@@
 Bancor provides continuous liquidity for digital assets without relying on brokers to match buyers with sellers.
-Implemented on the Ethereum blockchain, when transactions are broadcast to the network, they sit in a pending transaction pool known as \textit{mempool} waiting for the miners to mine them.
-Since Bancor handles all the trades and exchanges on the chain (unlike other existing decentralized exchanges), these transactions are all visible to the public for some time before being included within a block.
-This leaves Bancor vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions, in which they can gain favorable profits by buying before the order and fill the original order with slightly higher price~\cite{BancorIs7:online}.
+Since Bancor handles all the trades and exchanges on the blockchain, these transactions are all visible to the public for some time before being included within a block.
+This leaves Bancor vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions, in which they can gain favorable profits by conducting \textit{insertion attacks}~\cite{BancorIs7:online}.
 Researchers have shown and implemented a proof of concept code to front-run Bancor as a non-miner user~\cite{NewTab13:online}.

### 2018-12-14 frontrunning/Latex/sections/paper.tex
[frontrunning] Done (till Key Mitigations)

@@
 They can be bought, sold, or bred with other cryptokitties.
-At the Ethereum level, the kitty is a token implemented with \textit{ERC-721: Non-Fungible Token Standard}~\cite{erc721}.
+At the Ethereum level, the kitty is a token implemented as an \textit{ERC-721: Non-Fungible Token Standard}~\cite{erc721}.
 The market cap of cryptokitties peaked at more than 6 million dollars in the first few months of their launch, however, it has declined since.
@@
 It contains the kitty's ID which can be found either on their website or on the ERC721 token smart contract.
-This is similar to open auctions and markets on Section~\ref{sec:frontrunningExchanges}, bid value and the object bidding on is visible to the network and any user could easily front-run by sending the same transaction with higher gasPrice to replace the initial bidder.
-The front-runner can see there is an interest in a specific kitty and by buying it and auctioning it at a higher price can profit from the transaction.
-%we call this auction-frontrunning.
+This is similar to open auctions and markets on Section~\ref{sec:frontrunningExchanges}, bid value and the object bidding on is visible to the network and any user could easily front-run using \textit{displacement attack}.
+The front-runner can see there is an interest in a specific kitty, and by buying it and auctioning it at a higher price can profit from the transaction.
 % https://etherscan.io/tx/0x62a76b7e345e8abd463487d0348c118a9314b197024e090fee7b1fbce434da40
@@
 
-\subsection{Gambling.}
+\subsection{Gambling}
 \label{sec:gambling}
@@
 While a large category of gambling games are based on random outcomes, DApps do not have unique access to an unpredictable data stream to harvest for randomness~\cite{pierrot2018malleability}.
-Any candidate (such as block headers) source of randomness is accessible to all DApp functions and can also be manipulated to an extent by miners.
+Any candidate source of randomness (such as block headers) is accessible to all DApp functions and can also be manipulated to an extent by miners.
 
-\textsf{Fomo3D} is an example of a game style (known as \textsf{Exit Scam}\footnote{\url{https://exitscam.me/play}.}) not based on random outcomes, and it is the most active game on Ethereum in our sample.
-The aim of this game is to be the last person to have purchased a ticket when a timer goes to zero in a scenario where anyone can buy a ticket and each purchase increases the timer by 30 seconds.
+\textsf{Fomo3D} is an example of a game style (also known as \textsf{Exit Scam}\footnote{\url{https://exitscam.me/play}.}) not based on random outcomes, and it is the most active game on Ethereum in our sample.
+The aim of this game is to be the last person to have purchased a ticket when a timer goes to zero, in a scenario where anyone can buy a ticket and each purchase increases the timer by 30 seconds.
 Many speculated such a game would never end but on August 22, 2018, the first round of the game ended with the winner collecting 10,469 Ether\footnote{The first winner of Fomo3D, won 10,469 Ether \url{ https://etherscan.io/tx/0xe08a519c03cb0aed0e04b33104112d65fa1d3a48cd3aeab65f047b2abce9d508}.} equivalent to \$2.1M USD at the time.
-Blockchain forensics indicate a sophisticated winning strategy to front-run new ticket purchases~\cite{fomo3dhacker,fomo3dmedium} that would reset the counter.
+Blockchain forensics indicate a sophisticated winning strategy to front-run new ticket purchases~\cite{fomo3dhacker,fomo3dmedium}.
 The winner appears to have started by deploying many high gas consumption DApps unrelated to the game.
@@
 However, the key difference is that the front-runner does not care about the execution of her transactions---if miners mined empty blocks for three minutes, that would be fine as well.
-Thus, front-running, in this case, is not the end-goal of the adversary, the way it is in each other category but is rather a means to an end.
+Thus, front-running, in this case, is not the end-goal of the adversary the way it is in each other category, but is rather a means to an end.
 
@@
 
-\subsection{Name Services.}\label{sec:ens}
+\subsection{Name Services}\label{sec:ens}
 
-The final category in Table~\ref{tab:top25DApps} is name services, which are primarily aimed at displacing central parties involved in web domain registration (\eg ICAAN and registrars) and resolution (\eg DNS).
+The final category in Table~\ref{tab:top25DApps} is name services, which are primarily aimed at displacing central parties involved in web domain registration (\eg ICAAN) and resolution (\eg DNS).
 For simple name services (such as some academic work like Ghazal~\cite{moosavighazal}), domains purchases are transactions and network monitors can front-run other users attempting to register domains.
@@
 Users are allowed to bid for 48 hours before the 48-hour reveal phase begins, in which bidders must send a transaction to reveal their bids for a specific domain in the auction.
-It is possible for a user to front-run other bids with the same bid amount by revealing first.
+It is possible for a user to front-run other bids with the same bid amount by revealing first --displacement attack--.
 The auction model is similar to crypto-collectibles auctions in \ref{sec:cryptogames}.
@@
 
-During the time the ICO was open for participation, there were reports of Ethereum network being unusable and transactions were not confirming.
+During the time frame the ICO was open for participation, there were reports of Ethereum network being unusable and transactions were not confirming.
 Further study showed that some mining pools might have been manipulating the network for their own profit.
@@
 According to the analysis we carried out, we discovered that the F2Pool---an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure~\ref{fig:mining_pool_ratio})---sent 100 Ether to 30 new Ethereum addresses before the Status.im ICO started.
-When the ICO opened, F2Pool constructed 31 transactions to the ICO smart contract from these new address, without broadcasting the transactions to the network.
+When the ICO opened, F2Pool constructed 31 transactions to the ICO smart contract from their addresses, without broadcasting the transactions to the network.
 They used their entire mining power to mine their own transactions and some other potentially failing high gas price transactions.
@@
 As shown in Figure~\ref{fig:Transactions_miners_while_status_ico_cut}, most of the top miners in the mentioned time frame, have mined almost the same number of failed and successful transactions which were directed toward Status.im token sale, however F2Pool's transactions indicate their successful transactions were equivalent to 10\% of the failed transactions, hence maximizing the mining rewards on gas, while censoring other transactions to the token sale smart contract.
-The terminology used here is specific to smart contract transactions on Ethereum, by \textit{``failed transaction''} we mean the transactions in which the smart contract code flow rejected and threw an exception and by \textit{``successful transaction''} we mean the transactions that went through and received tokens from the smart contract.
+The terminology used here is specific to smart contract transactions on Ethereum, by \textit{``failed transaction''} we mean the transactions in which the smart contract code rejected and threw an exception and by \textit{``successful transaction''} we mean the transactions that went through and received tokens from the smart contract.
 
@@
 \floatbox[{\capbeside\thisfloatsetup{capbesideposition={left,top},capbesidewidth=0.3\linewidth}}]{figure}[\FBwidth]
-{\caption{This chart shows the miners behaviour on the time window that Status.im ICO was running.
+{\caption{This chart shows the miners behaviour on the time frame that Status.im ICO was running.
 It is clear that the number of successful transactions mined by F2Pool do not follow the random homogeneous pattern of the rest of the network.}\label{fig:Transactions_miners_while_status_ico_cut}}
@@
 {\caption{Prior to \textit{Status.im} ICO  \textit{F2Pool} deposited 100 Ether in multiple new Ethereum addresses.
-On the time of the ICO transactions were sent from these addresses to \textit{Status} ICO smart contract and were prioritized their mining pool and received \textit{ERC20} tokens.
+On the time of the ICO, transactions sent from these addresses to \textit{Status} ICO smart contract were prioritized in their mining pool, resulting in purchasing \textit{ERC20} tokens.
 This method was used to overcome the dynamic ceiling algorithm of the ICO smart contract.
@@
 
-By tracing the transactions from these 30 addresses, we found explicit interference by the F2Pool\footnote{F2Pool Ethereum address was identified by their mining reward deposit address \url{https://etherscan.io/address/0x61c808d82a3ac53231750dadc13c777b59310bd9}.} in this scenario.
-As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses were sent to Status.im ICO and mined by F2Pool themselves, where the dynamic ceiling algorithm refunded a portion of the deposited funds back to these addresses, these funds were sent back to F2Pool main address a few days after and the tokens were aggregated later on in one single address.
-Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their mining software to behave in a certain way to front-run other transactions and gain monetary profit.
+By tracing the transactions from these 30 addresses, we found explicit interference by F2Pool\footnote{F2Pool Ethereum address was identified by their mining reward deposit address \url{https://etherscan.io/address/0x61c808d82a3ac53231750dadc13c777b59310bd9}.} in this scenario.
+As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses were sent to Status.im ICO and mined by F2Pool themselves, where the dynamic ceiling algorithm refunded a portion of the deposited funds back to these addresses, these funds were sent back to F2Pool main address a few days after and the tokens were aggregated later in one single address.
+Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their mining software to behave in a certain way to front-run other transactions by \textit{bulk displacement} and gain monetary profit.
 

### 2018-12-20 frontrunning/Latex/sections/paper.tex
edits

--- 2018-12-13 frontrunning/Latex/sections/paper.tex
@@
 Function calls (or transactions) to the DApp are processed by a decentralized network.
-Transactions are finalized in stages: they (generally) first relay around the network, then selected by a miner and put into a valid block, and finally, the block is well-enough incorporated that is unlikely to be reorganized.
-Front-running is an attack where a malicious node observes a transaction after it is broadcast but before it is finalized, and attempts to have its own transaction confirmed before or instead of the observed transaction.
+Transactions are finalized in stages: they (generally) first relay around the network, then are selected by a miner and put into a valid block, and finally, the block is well-enough incorporated that is unlikely to be reorganized.
+Front-running is an attack where a malicious node observes a transaction after it is broadcast but before it is finalized, and adapts its own transactions to be confirmed before or instead of the observed transaction.
 
@@
 Therefore, DApps need to be studied individually or in categories.
-In this paper, we draw from a scattered body of knowledge regarding front-running attacks on blockchain applications and proposed solutions, with series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps).
+In this paper we draw from a scattered body of knowledge regarding front-running attacks on blockchain applications and proposed solutions, with series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps).
 We do case studies on decentralized exchanges (\eg Bancor), crypto-collectibles (\eg CryptoKitties), gambling services (\eg Fomo3D), and decentralized name services (\eg Ethereum Name Service).
 We also study initial coin offerings (ICOs).
-Finally, we provide a categorization of techniques to eliminate or mitigate front-running including transaction sequencing, cryptographic techniques like commit/reveal, and redesigning the functioning of the DApp to provide the same utility while removing time dependencies.
+Finally, we provide a categorization of  techniques to mitigate front-running including transaction sequencing, cryptographic techniques like commit/reveal, and redesigning the functioning of the DApp to provide the same utility while removing time dependencies.
 
@@
 \emph{Front-running} is a course of action where someone benefits from early access to market information about upcoming transactions and trades, typically because of a privileged position along the transmission of this information and is applicable to both financial and non-financial systems.
-In traditional stock exchanges, floor traders might overhear a broker's negotiation with her client over a large purchase, and literally race the broker to buy first, potentially profiting when the large sale temporarily reduces the supply of the stock.
-A malicious broker might also front-run their own client's orders by purchasing stock for themselves between receiving the instruction to purchase from the client and actually executing the purchase (similar techniques can be used for large sell orders).
-Front-running is unethical and illegal in jurisdictions with mature securities regulation.
+Historically, floor traders might have overhear a broker's negotiation with her client over a large purchase, and literally race the broker to buy first, potentially profiting when the large purchase temporarily reduces the supply of the stock.
+Alternatively, a malicious broker might front-run their own client's orders by purchasing stock for themselves between receiving the instruction to purchase from the client and actually executing the purchase (similar techniques can be used for large sell orders).
+Front-running is illegal in jurisdictions with established securities regulation.
 
@@
 In front-running, a person sees a concrete transaction that is set to execute and reacts to it before it actually gets executed.
-If the person instead has access to more general privileged information that might predict future transactions but is not reacting at the actual pending trades, we would classify this activity as insider trading.
+If the person instead has access to more general privileged information that might predict future transactions, but is not reacting at the actual pending trades, we would classify this activity as insider trading.
 If the person reacts after the trade is executed, or information is made public, and profits from being the fastest to react, this is considered arbitrage and is legal and encouraged because it helps markets integrate new information into prices quickly.
@@
 Front-running originates on the Chicago Board Options Exchange (\textit{CBoE}) \cite{markham1988front}.
-The Securities Exchange Commission \textit{(SEC)} in 1977 defines it as: ``The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{A block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily change the price.} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}'' Self-regulating exchanges (\eg \textit{CBoE}) and the \textit{SEC} spent the ensuing years planning how to detect and outlaw front-running practices~\cite{markham1988front}.
+The Securities Exchange Commission \textit{(SEC)} in 1977 defines it as: ``The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{A block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}'' Self-regulating exchanges (\eg \textit{CBoE}) and the \textit{SEC} spent the ensuing years planning how to detect and outlaw front-running practices~\cite{markham1988front}.
 The \textit{SEC} stated: ``It seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge.\footnote{Securities Exchange Act Release No.
@@
 
-% we can say other illegal activities in the traditional system, such as wash trading, ...
-(notes from AMF) could fall under our definition of front-running on blockchain apps, as the transparency and public nature of the transactions could result in any actor to be involved in such trades?
+% we can say other illegal activities in the tranditional system, such as wash trading, ...
+(notes from AMF) could fall under our definition of front running on blockchain apps, as the transparency and public nature of the transactions could result in any actor to be involved in such trades?
 does it make sense?
@@
 
+%Shayan -> Jeremy: Not sure if this figure adds value to the paper. I edited and looked at this for so long that it lost its meaning. I'll come back to it tomorrow.
+% Jeremy: Agree, let's remove it. 
+%
 \begin{figure}[t]
-\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,bottom},capbesidewidth=0.3\linewidth}}]{figure}[\FBwidth]
-{\caption{The adversarial miner monitors the Ethereum mempool for decentralized exchange transactions.
-Upon spotting a profitable cancellation transaction, he puts his buy order prior to the cancel transaction in the block he mines.
-Doing so, the miner can profit from the underlying trade and also get the gas included in the cancel transaction.}\label{fig:MinerFrontrunning}}
-{\includegraphics[width=\linewidth]{figures/Miner_reorder_frontrun.png}}
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={left,top},capbesidewidth=0.3\linewidth}}]{figure}[\FBwidth]
+{\caption{The front-runner upon spotting the profitable transaction \textit{Buy(1000)} sends his own transaction with higher gas price to bribe the miners to prioritize his transaction over initial transaction.}\label{fig:RegularFrontrunning}}
+{\includegraphics[width=1.0\linewidth]{figures/Regular_frontrunning.png}}
 \end{figure}
-%https://www.lucidchart.com/invitations/accept/c8768786-4a3f-4c78-b3c8-aa04a6b81d06
+%https://www.lucidchart.com/invitations/accept/f8ca2662-5269-425d-9deb-deb14af2aac7
 
-In one sense, blockchain technology (introduced via Bitcoin in 2008~\cite{nakamoto2008bitcoin}) strives to disintermediate certain central parties that participate in a transaction.
-However, blockchains also introduce new participants in the relaying and finalization (\ie mining) of transactions that can act as front-runners.
-Any user monitoring blockchain network transactions (\eg running a full node) can see an unconfirmed transaction and broadcast a reactionary transaction that might be confirmed ahead of the original transaction.
-For regular users to front-run others on the blockchain, they need to be well connected to other nodes on the network and listen to the network to monitor all transactions that are broadcast.
+Blockchain technology (introduced via Bitcoin in 2008~\cite{nakamoto2008bitcoin}) strives to disintermediate  central parties that participate in a transaction.
+However, blockchains also introduce new participants in the process of relaying and finalizing transactions.
+Miners are in the best position to conduct these attacks as they hold fine-grained control over the exact set of transactions that will execute and in what order and can mix in their own (late) transactions without broadcasting them.
+Miners do however have to commit to what their own transactions will be before beginning the proof of work required to solve a block.
+
+Any user monitoring network transactions (\eg running a full node) can see unconfirmed transactions.
 On the Ethereum blockchain, users have to pay for the computations in a small amount of Ether called \textsf{gas}~\cite{AccountT67:online}.
 The price that users pay for transactions, \textsf{gasPrice}, can increase or decrease how quickly miners will execute them and include them within the blocks they mine.
-Once seeing two identical transactions with different transaction fees, a rational miner, due to limited space in the blocks, will prioritize the transaction that pays a higher gas price, this is also known as gas auctions~\cite{frontrunme}.
-Therefore, any regular user who runs a full-node Ethereum client can front-run pending transactions by sending similar transaction with a higher gas price.
-Also, blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this in case of malicious reordering is known as \textsf{transaction reordering} attack.
+A profit-motivated miner who sees identical transactions with different transaction fees will prioritize the transaction that pays a higher gas price due to limited space in the blocks.
+This has been called a gas auction~\cite{frontrunme}.
+Therefore, any regular user who runs a full-node Ethereum client can front-run pending transactions by sending adaptive transactions with a higher gas price (see Figure~\ref{fig:RegularFrontrunning}).
 
-% Jeremy: Merge this
-%Finally, we note that in addition to the three things the front-runner wants to accomplish, there are three basic mechanisms to accomplishing them: (1) miners can choose transaction order, (2) non-miners can prioritize their later transactions over earlier transactions with higher gas fees, and (3) well-positioned network nodes can try to influence how transactions are propagated through the network.
+Finally, well-positioned relaying nodes on the network (or part of the broader internet backbone) can attempt to influence how transactions are propagated through the network, which can influence the order miners receive transactions, or if they receive them at all~\cite{HKZG15,MGH18}.
 
@@
 First, we are not aware of any other systematic study of this issue.
-Second, front-running is related to two concepts that are often not considered front-running per se: double-spending and rushing adversaries.
+Second, front-running is related to two well-studied concepts: double-spending and rushing adversaries.
 
@@
 
-In the cryptographic literature, front-running attacks are modeled by allowing a `rushing' adversary to interact with the protocol.
-In particular, ideal functionalities of blockchains (such as those used in simulation-based proofs) need to capture this adversarial capability, assuming the real blockchain does not address front-running.
+In the cryptographic literature, front-running attacks are modelled by allowing a `rushing' adversary to interact with the protocol.
+In particular, ideal functionalities of blockchains (such as those used in simulation-based proofs) need to capture this adversarial capability, assuming the realized blockchain does not address front-running.
 See \eg Bitcoin backbone~\cite{garay2015bitcoin} and Hawk~\cite{kosba2016hawk}.
@@
 
-As we will illustrate with examples throughout the paper, front-running attacks can often be reduced to one of a few basic templates.
-First, we consider what the adversary is trying to accomplish (without worrying about how) and we distinguish three cases: displacement, insertion, and suppression attacks.
-In all three cases, Alice is trying to invoke a function on a contract that is in a particular state, and Mallory will try to invoke her own function call on that contract in that particular state before Alice.
+As we will illustrate with examples through-out the paper, front-running attacks can often be reduced to one of a few basic templates.
+We emphasize what the adversary is trying to accomplish (without worrying about how) and we distinguish three cases: displacement, insertion, and suppression attacks.
+In all three cases, Alice is trying to invoke a function on a contract that is in a particular state, and Mallory will try to invoke her own function call on the same contract in the same state before Alice.
 
-In a \textit{displacement attack}, after Mallory runs her function, Alice's function is either orphaned or runs with no meaningful effect.
-Examples of displacement include: Alice trying to register a domain name and Mallory registering it first; Alice trying to submit a bug to receive a bounty and Mallory stealing it and submitting it first~\cite{}; and Alice trying to submit a bid in an auction and Mallory copying it.
+In the first type of attack, a \textit{displacement attack}, it is not important to the adversary for Alice's function call to run after Mallory runs her function.
+Alice's can be orphaned or run with no meaningful effect.
+Examples of displacement include: Alice trying to register a domain name and Mallory registering it first~\cite{kalodner2015empirical}; Alice trying to submit a bug to receive a bounty and Mallory stealing it and submitting it first~\cite{breidenbach2018enter}; and Alice trying to submit a bid in an auction and Mallory copying it.
 In some cases, Alice's function and Mallory's function are different: \eg Alice trying to cancel an offer and Mallory fulfilling the offer first.
 We call this \textit{asymmetric displacement}.
-Finally, in some cases, Mallory is trying to run a large set of functions: for example, Alice and others are trying to buy a limited set of shares offered by a firm on a blockchain.
+Finally, in some cases, Mallory is trying to run a large set of functions: for example Alice and others are trying to buy a limited set of shares offered by a firm on a blockchain.
 We call this \textit{bulk displacement}.
@@
 In a \textit{suppression attack}, after Mallory runs her function, she tries to delay Alice from running her function.
-After the delay, she is invariant to whether Alice functions runs or not.
+After the delay, she is invariant to whether Alice's function runs or not.
 We only observe this attack pattern in one DApp and the details are quite specific to it, so we defer discussion until Section~\ref{sec:gambling}.
@@
 \section{Cases of Front-running in DApps}
+
 \input{setup/table}
 
-To find example DApps to study, we use the top 25 DApps based on recent user activity from \texttt{DAppradar.com} and sample it in the first week of September 2018\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}.}.
-User activity is admittedly an imperfect metric for finding the `most significant' DApps: significant DApps might be lower volume overall or for extended periods of time (\eg ICOs, which we remedy by studying independently in Section~\ref{sec:ICOsfrontrunning}).
-However, user activity is arguably the best objective criteria for which data is readily available, the list captures our intuition about which DApps are significant, and it is at least better than an ad hoc approach.
+To find example DApps to study, we used the top 25 DApps based on recent user activity from \texttt{DAppradar.com} in September 2018.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} User activity is admittedly an imperfect metric for finding the `most significant' DApps: significant DApps might be lower volume overall or for extended periods of time (\eg ICOs, which we remedy by studying independently in Section~\ref{sec:ICOsfrontrunning}).
+However, user activity is an objective criteria, data on it is available, and the list captures our intuition about which DApps are significant.
+It suffices for a first study in this area, and is preferable over an ad hoc approach.
 Using the dataset, we categorized the top 25 applications into 4 principal use cases.
@@
 
+\begin{figure}[t]
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,bottom},capbesidewidth=0.3\linewidth}}]{figure}[\FBwidth]
+{\caption{The adversarial miner monitors the Ethereum mempool for decentralized exchange transactions.
+Upon spotting a profitable cancellation transaction, he puts his buy order prior to the cancel transaction in the block he mines.
+Doing so, the miner can profit from the underlying trade and also get the gas included in the cancel transaction.}\label{fig:MinerFrontrunning}}
+{\includegraphics[width=\linewidth]{figures/Miner_reorder_frontrun.png}}
+\end{figure}
+%https://www.lucidchart.com/invitations/accept/c8768786-4a3f-4c78-b3c8-aa04a6b81d06
+
 % talk about velocity ~\cite{eskandari2017feasibility} that seems to be not front-runnable but because of the liquidity pool limitation, there can be an order that consumes the last chunk of liquidity ``edge case'', to front run others and make their "option calls" fail
@@
 
-The first category of DApp in Table~\ref{tab:top25DApps} is exchanges.
-Exchanges such as EtherDelta\footnote{Also known as ForkDelta for the UI \url{https://forkdelta.app/}.}, purport to implement a decentralized exchange, however, their order books are stored on a central server they control and shown to their users with a website interface.
-Central exchanges can front-run orders in the traditional sense, as well as re-order or block orders on their servers.
-0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the order book holders and could front-run the orders they relay.
-As seen in traditional financial markets, one method to manipulation the spot price of an asset is to flood the market with orders and cancel them when there are filling orders --taker's griefing~\cite{consesnsys0xReview2017}.
-As mentioned putting an order in the current decentralized exchange is free, but to prevent taker's griefing attacks, the user needs to send a transaction to cancel each of his orders.
-The reason for canceling order could be the unprofitability of the order due to price change.
-In this case, when an adversarial actor sees a pending cancellation transaction, he sends a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled, this is known as \textit{\todo{cancellation grief}}.
-This is illustrated in Figure~\ref{fig:MinerFrontrunning}.
+The first category of DApp in Table~\ref{tab:top25DApps} are financial exchanges for trading ether and Ethereum-based tokens.
+Exchanges such as EtherDelta\footnote{Also known as ForkDelta for the user interface: \url{https://forkdelta.app/}}, purport to implement a decentralized exchange, however, their order books are stored on a central server they control and shown to their users with a website interface.
+Central exchanges can front-run orders in the traditional sense, as well as re-order or block orders on their servers 0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the order book holders and could front-run the orders they relay.
 
-%Shayan -> Jeremy: Not sure if this figure adds value to the paper. I edited and looked at this for so long that it lost its meaning. I'll come back to it tomorrow.
-\begin{figure}[t]
-\floatbox[{\capbeside\thisfloatsetup{capbesideposition={left,top},capbesidewidth=0.3\linewidth}}]{figure}[\FBwidth]
-{\caption{The front-runner upon spotting the profitable transaction \textit{Buy(1000)} sends his own transaction with higher gas price to bribe the miners to prioritize his transaction over initial transaction.}\label{fig:RegularFrontrunning}}
-{\includegraphics[width=1.1\linewidth]{figures/Regular_frontrunning.png}}
-\end{figure}
-%https://www.lucidchart.com/invitations/accept/f8ca2662-5269-425d-9deb-deb14af2aac7
+As seen in traditional financial markets, one method to manipulate the spot price of an asset, is to flood the market with orders and cancel them when there are filling orders (``taker's griefing''~\cite{consesnsys0xReview2017}).
+Placing an order in a partially centralized exchange is free, but to prevent taker's griefing attacks, the user needs to send an Ethereum transaction to cancel each of his orders.
+Cancelling orders is most important when prices change faster than order execution.
+In this case, when an adversarial actor sees a pending cancellation transaction, he sends a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled (this is known as \textit{cancellation grief}).
+This attack follows the (asymmetric) insertion template and is illustrated in Figure~\ref{fig:MinerFrontrunning}.
 
 Designing truly decentralized exchanges, where the order book is implemented directly on a public blockchain, is being pursued by a number of projects~\cite{inDEXgithub}.
-These designs generally face the following attack (illustrated in Figure~\ref{fig:RegularFrontrunning}).
-An adversary can monitor the network with a full node for pending \textit{buy} (or \textit{sell}) transactions which could increase (or \textit{decrease}) the future price of the asset.
-A front-runner can send a competing order with a higher gas price and hope to have her transactions mined ahead of the original pending transaction.
-The benefits of doing this vary.
-If the original bid is a large market order (\ie it will execute at any price), the adversary can front-run a pair of limit orders that will bid near the best offer price and offer at a higher price.
-If these execute ahead of the market order, the front-runner profits by scalping the price of the shares.
-If the adversary has pre-existing offers likely to be reached by the market order, she could front-run a cancelation and a new offer at a higher price.
-A simpler attack would be to gauge the demand for trades at a given price by the number of pending orders and to front-run at the same price in hopes that the market demand is the result of the accurate new market information.
-Miners are in the best position to conduct these attacks as they hold fine-grained control over the exact set of transactions that will execute and in what order and can mix in their own (late) transactions without broadcasting them.
-Miners do however have to commit to what their own transactions will be before beginning the proof of work required to solve a block.
+These designs are generally vulnerable to front-running attacks following a displacement or insertion template.
+For example, a front-running full node or miner might gauge the demand for trades at a given price by the number of pending orders, and try to displace them at the same price assuming the demand is the result of the accurate new information about the asset.
+Alternatively,  the front-runner might observe a large market order (\ie it will execute at any price).
+The adversary can try to insert a pair of limit orders that will bid near the best offer price and offer at a higher price.
+If the pair executes ahead of the market order, the front-runner profits by scalping the price of the shares.
+Finally, if adversary has pre-existing offers likely to be reached by the market order, she could insert cancelations and new offers at a higher price.
 
@@
 
-Bancor is another DApp that allows users to exchange their tokens without any counter-party risk.
+Bancor is an exchange DApp that allows users to exchange their tokens without any counter-party risk.
 The protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}.
@@
 Since Bancor handles all the trades and exchanges on the chain (unlike other existing decentralized exchanges), these transactions are all visible to the public for some time before being included within a block.
-This leaves Bancor vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions, in which they can gain favorable profits by buying before the order and fill the original order with slightly higher price~\cite{BancorIs7:online}.
+This leaves Bancor vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions, in which they can gain favourable profits by buying before the order and fill the original order with slightly higher price~\cite{BancorIs7:online}.
 Researchers have shown and implemented a proof of concept code to front-run Bancor as a non-miner user~\cite{NewTab13:online}.
@@
 The second category of DApp in Table~\ref{tab:top25DApps} is crypto-collectables.
-Consider Cryptokitties\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}.}, the most active DApp in this category and third most active overall.
+Consider Cryptokitties\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}}, the most active DApp in this category and third most active overall.
 Each kitty (see Appendix~\ref{app:cryptokitty}) is a cartoon kitten with a set of unique features to distinguish it from other cryptokitties, some features are rarer and harder to obtain.
@@
 It contains the kitty's ID which can be found either on their website or on the ERC721 token smart contract.
-This is similar to open auctions and markets on Section~\ref{sec:frontrunningExchanges}, bid value and the object bidding on is visible to the network and any user could easily front-run by sending the same transaction with higher gasPrice to replace the initial bidder.
-The front-runner can see there is an interest in a specific kitty and by buying it and auctioning it at a higher price can profit from the transaction.
+This is similar to open auctions and markets on section~\ref{sec:frontrunningExchanges}, bid value and the object bidding on is visible to the network and any user could  easily front-run by sending the same transaction with higher gasPrice to replace the initial bidder.
+The front-runner can see there is an interest in a specific kitty and insert a pair of transactions to buy it and re-auctioning it at a higher price, keeping any profit.
 %we call this auction-frontrunning.
@@
 
-\textsf{Fomo3D} is an example of a game style (known as \textsf{Exit Scam}\footnote{\url{https://exitscam.me/play}.}) not based on random outcomes, and it is the most active game on Ethereum in our sample.
+\textsf{Fomo3D} is an example of a game style (known as \textsf{Exit Scam}\footnote{\url{https://exitscam.me/play}}) not based on random outcomes, and it is the most active game on Ethereum in our sample.
 The aim of this game is to be the last person to have purchased a ticket when a timer goes to zero in a scenario where anyone can buy a ticket and each purchase increases the timer by 30 seconds.
-Many speculated such a game would never end but on August 22, 2018, the first round of the game ended with the winner collecting 10,469 Ether\footnote{The first winner of Fomo3D, won 10,469 Ether \url{ https://etherscan.io/tx/0xe08a519c03cb0aed0e04b33104112d65fa1d3a48cd3aeab65f047b2abce9d508}.} equivalent to \$2.1M USD at the time.
-Blockchain forensics indicate a sophisticated winning strategy to front-run new ticket purchases~\cite{fomo3dhacker,fomo3dmedium} that would reset the counter.
+Many speculated such a game would never end but on August 22, 2018, the first round of the game ended with the winner collecting 10,469 Ether\footnote{The first winner of Fomo3D, won 10,469 Ether \url{ https://etherscan.io/tx/0xe08a519c03cb0aed0e04b33104112d65fa1d3a48cd3aeab65f047b2abce9d508}} equivalent to \$2.1M USD at the time.
+Blockchain forensics indicate a sophisticated winning strategy to displace any new ticket purchases~\cite{fomo3dhacker,fomo3dmedium} that would reset the counter.
 The winner appears to have started by deploying many high gas consumption DApps unrelated to the game.
@@
 We classify this in the unique category of a suppression attack in our taxonomy (see Section~\ref{sec:taxonomy}).
-At first glance, it seemed like an asymmetric/bulk displacement attack on any new ticket purchase transactions.
-However, the key difference is that the front-runner does not care about the execution of her transactions---if miners mined empty blocks for three minutes, that would be fine as well.
-Thus, front-running, in this case, is not the end-goal of the adversary, the way it is in each other category but is rather a means to an end.
+At first glance, it seemed like an extreme version of an asymmetric/bulk displacement attack on any new ticket purchase transactions.
+However the key difference is that the front-runner does not care at all about the execution of her transactions---if miners mined empty blocks for three minutes, that would also be acceptable.
+Thus, bulk displacement is simply a means-to-an-end and not the actual end goal of the adversary.
 
@@
 
-The final category in Table~\ref{tab:top25DApps} is name services, which are primarily aimed at displacing central parties involved in web domain registration (\eg ICAAN and registrars) and resolution (\eg DNS).
-For simple name services (such as some academic work like Ghazal~\cite{moosavighazal}), domains purchases are transactions and network monitors can front-run other users attempting to register domains.
+The final category in Table~\ref{tab:top25DApps} is name services, which are primarily aimed at disintermediating central parties involved in web domain registration (\eg ICAAN and registrars) and resolution (\eg DNS).
+For simple name services (such as some academic work like Ghazal~\cite{moosavighazal}), domains purchases are transactions and network monitors can displace other users attempting to register domains.
 This parallels front-running attacks seen in regular (non-blockchain) domain registration~\cite{sac022en33:online}.
@@
 Initial coin offerings (ICOs) have changed how blockchain firms raise capital.
-More than 3000 ICOs have been held on Ethereum, and the market capitalization of these tokens appear to exceed \$75B USD in the first half of 2018~\cite{zetzsche2018ico}.
-At the DApp level, tokens are offered in short-term sales that see high transaction activity while the sale is on-going and then ICO activity tapers off to occasional owner transfers.
-When we collected the top 25 most active DApps on \texttt{DAppRadar.com}, no significant ICOs were in the initial sale stage.
-Despite the ICO category falls through our sampling method, we identify it as a major category of DApp and study it here.
+More than 3000 ICOs have been held on Ethereum, and the market capitalization of these tokens appears to exceed \$75B USD in the first half of 2018~\cite{zetzsche2018ico}.
+At the DApp level, tokens are offered in short-term sales that see high transaction activity while the sale is on-going and then the activity tapers off to occasional owner transfers.
+When we collected the top 25 most active DApps on \texttt{DAppRadar.com}, no significant ICOs were being sold.
+The ICO category slips through our sampling method, but we identify it as a major category of DApp and study it here.
 
@@
 \subsection{Data Collection and Analysis}
-According to the analysis we carried out, we discovered that the F2Pool---an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure~\ref{fig:mining_pool_ratio})---sent 100 Ether to 30 new Ethereum addresses before the Status.im ICO started.
+According to analysis we carried out, we discovered that the F2Pool---an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure~\ref{fig:mining_pool_ratio})---sent 100 Ether to 30 new Ethereum addresses before the Status.im ICO started.
 When the ICO opened, F2Pool constructed 31 transactions to the ICO smart contract from these new address, without broadcasting the transactions to the network.
@@
 While the default client and online blockchain explorers offer some limited query capabilities, in order to analyze this case, we built our own database.
-Specifically, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation\url{https://github.com/ethereum/go-ethereum}.} for the full node, a python script for extracting, transforming and loading Ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery.\footnote{\url{https://cloud.google.com/bigquery/}} Using this software stack, we were able to isolate transactions within the Status.im ICO.
+Specifically, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation\url{https://github.com/ethereum/go-ethereum}} for the full node, a python script for extracting, transforming and loading Ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery.\footnote{\url{https://cloud.google.com/bigquery/}} Using this software stack, we were able to isolate transactions within the Status.im ICO.
 We used data analysis tool \texttt{Tableau}.\footnote{\url{https://www.tableau.com/}} A copy of this dataset and the initial findings can be found in our Github repository.\footnote{\url{github.com/} Removed for anonymity.}
@@
 
-By tracing the transactions from these 30 addresses, we found explicit interference by the F2Pool\footnote{F2Pool Ethereum address was identified by their mining reward deposit address \url{https://etherscan.io/address/0x61c808d82a3ac53231750dadc13c777b59310bd9}.} in this scenario.
+By tracing the transactions from these 30 addresses, we found explicit interference by the F2Pool\footnote{F2Pool Ethereum address was identified by their mining reward deposit address \url{https://etherscan.io/address/0x61c808d82a3ac53231750dadc13c777b59310bd9}} in this scenario.
 As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses were sent to Status.im ICO and mined by F2Pool themselves, where the dynamic ceiling algorithm refunded a portion of the deposited funds back to these addresses, these funds were sent back to F2Pool main address a few days after and the tokens were aggregated later on in one single address.
@@
 
-As we studied front-running attacks on the blockchain, we also encountered a number of ways of preventing, detecting or mitigating front-running attacks.
+As we studied front-running attacks on blockchain, we also encountered a number of ways of preventing, detecting, or mitigating front-running attacks.
 Instead of providing the details of exact solutions which will change over time, we extract the main principles or primitives that address the attack.
@@
 In the second category, cryptographic techniques are used to limit the visibility of transactions, giving the potential front-running less information to base their strategy on.
-In the final category, DApps are designed from the bottom-up to remove the importance of transaction ordering or time in their operations.
-We also note that for DApps that are legally well-formed (\eg with identified parties and a clear jurisdiction), front-running attacks can violate laws, which is its own deterrent.
+In the final category, dapps are designed from the bottom-up to remove the importance of transaction ordering or time in their operations.
+We also note that for dapps that are legally well-formed (\eg with identified parties and a clear jurisdiction), front-running attacks can violate laws, which is its own deterrent.
 We do not discuss this further here; see Appendix ~\ref{app:traditionalprevention}.
@@
 
-One alternative is to sequence transactions pseudorandomly.
+One alternative is to sequence transactions psuedorandomly.
 This can be seen in proposals like Canonical Transaction Ordering Rule (CTOR) by Bitcoin Cash ABC~\cite{bitcoincashabcFork} which adds transactions in lexicographical order according to their hash~\cite{bitcoinABC2018CTOR}.
@@
 
-Finally, the transactions themselves could enforce an order.
+Finally, transactions themselves could enforce order.
 For example, they could specify the current state of the contract as the only state to execute on.
 This transaction chaining only prevents certain types of front-running; \ie it prevents insertion attacks but not displacement attacks (recall our taxonomy in Section~\ref{sec:taxonomy}).
-As transaction chaining only allows one state-changing transaction per state, at most one of a set of concurrent transactions can be confirmed.
+As transaction chaining only allows one state-changing transaction per state, at most one of a set of concurrent transactions can be confirmed; a drawback for active DApps.
 
@@
 
-All transaction details in Bitcoin are made public and participant identities are only lightly protected.
+All transaction details in Bitcoin are make public and participant identities are only lightly protected.
 A number of techniques increase confidentiality~\cite{bunzBulletproofs,maxwell2015confidential} and anonymity ~\cite{miers2013zerocoin,cryptoeprint2015,sasson2014zerocash} for cryptocurrencies.
@@
 It is tempting to think that a confidential DApp would not permit front-running, as the front-runner would not know the details of the transaction she is front-running.
-However, there are some nuances here to explore.
+However there are some nuances here to explore.
 
@@
 Confidentiality applied to a DApp could mean different levels of protection for each of these.
-For front-running, function calls (3,4) are the most important, however, function calls could be inferred from state changes (2).
+For front-running, function calls (3,4) are the most important, however function calls could be inferred from state changes (2).
 Hawk~\cite{kosba2016hawk} and Ekiden~\cite{cheng2018ekiden} are examples of (2,3,4)-confidentiality (with limitations we are glossing over).
@@
 The applicability of privacy-preserving blockchains needs to be evaluated on a case-by-case base.
-For example, one method used by traditional financial exchanges in dealing with front-running from high-frequency traders is a dark market: essentially a (2,3,4)-confidential order book maintained by a trusted party.
+For example, one method used by traditional financial exchanges in dealing with front-running from high frequency traders is a dark market: essentially a (2,3,4)-confidential order book maintained by a trusted party.
 A DApp could disintermediate this trusted party.
-Users whose balances are affected by changes in the contract's state would need to be able to learn this information.
-Further, if the contract addresses are known (no 5-confidentiality), front-runners can know about the traffic pattern of calls to contracts which could be sufficient grounds for attack; for example, if each asset on an exchange has its own market contract, this leaks trade volume information.
+Users whose balances are effected by changes in the contract's state would need to be able to learn this information.
+Further, if the contract addresses are known (\ie no 5-confidentiality), front-runners can know about the traffic pattern of calls to contracts which could be sufficient grounds for attack; for example, if each asset on an exchange has its own market contract, this leaks trade volume information.
 As a contrasting example, consider again decentralized domain registration: hiding state changes (2-confidentiality) defeats the entire purpose of the DApp, and protecting function calls is ineffective with a public state change since the state itself reveals the domain being registered.
@@
 %Shayan: maybe just a reference ^ suffices! 
-%A recent attempt to build confidential transactions for DApps is AZTEC protocol~\cite{aztec2018}.
+%A recent attempt to build confidential transactions for DApps, is AZTEC protocol~\cite{aztec2018}.
 Similar to ZCash ~\cite{hopwood2016zcash}, it uses the concept of encrypted ‘notes’ and join-split transactions.
-ZCash uses two distinct types of addresses, transparent and shielded addresses, wherein AZTEC, the user transfers her ERC20 tokens into encrypted notes.
+ZCash uses two distinct types of addresses, transparent and shielded addresses, where in AZTEC, user transfers her ERC20 tokens into encrypted notes.
 Users can transfer these notes by destroying the unspent notes and creating new notes for the new owners, where the sum of the old notes should be equal to the sum of the new notes.
 %Shayan: Talk about AZTEC confidential transactions and their approach for CT.
-it will be possible to do dark pool-style transactions within Ethereum DApps however they would still expose some information such as sender, receiver (exposes 5,6), hides (3,4?).
+it will be possible to do dark pool style transactions within Ethereum dapps however they would still expose some information such as sender, receiver (exposes 5,6), hides (3,4?).
 https://medium.com/aztec-protocol/confidential-transactions-have-arrived-a-dive-into-the-aztec-protocol-a1794c00c009
@@
 
-While confidentiality appears insufficient for solving domain name front-running alone, a hybrid approach of sequencing and confidentiality can be effective and is, in fact, an example of an older cryptographic trick known as commit/reveal.
-The essence of the approach is to protect the function call (\eg (3,4)- or (4)-confidentiality) until the function is enqueued in a sequence of functions to be executed.
-Once the sequence is established, the confidentiality is lifted and the function can only be executed in the place it was given (or, generally speaking, not at all).
+While confidentiality appears insufficient for solving domain name front-running alone, a hybrid approach of sequencing and confidentiality can be effective, and is in fact an example of an older cryptographic trick known as commit/reveal.
+The essence of the approach is to protect the function call (\eg (3,4)- or (4)-confidentiality) until the function is enqueued in sequence of functions to be executed.
+Once the sequence is established, the confidentiality is lifted and the function can only be executed in the place is was given (or, generally speaking, not at all).
 
@@
 After the delay, a second transaction reveals the details of the requested domain.
-This prevents front-running if the reveal transaction is confirmed faster than an adversarial node or miner can redo the entire process.
+This prevent front-running if the reveal transaction is confirmed faster than an adversarial node or miner can redo the entire process.
 
-Commit/reveal is a two-round protocol, and aborting after the first round (early aborts) could be an issue for this (along with most multi-round cryptographic protocols).
+Commit/reveal is a two round protocol, and aborting after the first round (early aborts) could be an issue for this (along with most multi-round cryptographic protocols).
 For example, in a financial exchange where the number of other orders might be in a predictable interval, an adversary can spray the sequence (\ie a price-time priority queue) with multiple committed transactions and no intention of executing them all.
-She then only reveal the ones that result in an advantageous trade.\footnote{This is analogous to behavior in traditional financial markets where high-frequency traders will make and cancel orders at many price points (flash orders or pinging).
+She then only reveal the ones that result in an advantageous trade.\footnote{This is analogous to behaviour in traditional financial markets where high frequency traders will make and cancel orders at many price points (flash orders or pinging).
 If they can cancel faster than someone can execute it---someone who has only seen the order and not the cancelation---then the victim reveals their price information.} There are other ways of aborting; if payments are required but not collateralized, the aborting party can ensure that payment is not available for transfer.
 One mitigation to early aborts that blockchain is uniquely positioned to make is having users post a fidelity bond of a certain amount of cryptocurrency that can be automatically dispensed if they fail to fully execute committed transactions (this is used in multi-round blockchain voting~\cite{mccorry2017smart}).
-Finally, we note that any multiple round protocol will have usability challenges: users must be aware that participating in the first round is not sufficient for completing their intention.
+Finally we note that any multiple round protocol will have usability challenges: users must be aware that participating in the first round is not sufficient for completing their intention.
 
@@
 They model indirect trading costs on search and trading at decentralized exchanges to make front-running costly and inefficient.
-They split big investments into smaller ones using intermediaries --liquidity demander-- and liquidity providers.
-To prevent front-running, the liquidity demander offers the liquidity-providing trader an incentive; establishing an equilibrium behavior, in which front-runner needs to pay more incentives to come in front of the original trade, making front-running not too profitable.
+They split big investments into smaller ones using intermediaries---liquidity demanders and providers.
+To prevent front-running, the liquidity demander offers the liquidity-providing trader an incentive; establishing an equilibrium behaviour, in which front-runner needs to pay more incentives to come in front of the original trade, minimizing front-running profits.
 

### 2018-12-20 frontrunning/Latex/sections/paper.tex

@@
 Function calls (or transactions) to the DApp are processed by a decentralized network.
-Transactions are finalized in stages: they (generally) first relay around the network, then are selected by a miner and put into a valid block, and finally, the block is well-enough incorporated that is unlikely to be reorganized.
-Front-running is an attack where a malicious node observes a transaction after it is broadcast but before it is finalized, and adapts its own transactions to be confirmed before or instead of the observed transaction.
+Transactions are finalized in stages: they (generally) first relay around the network, then selected by a miner and put into a valid block, and finally, the block is well-enough incorporated that is unlikely to be reorganized.
+Front-running is an attack where a malicious node observes a transaction after it is broadcast but before it is finalized, and attempts to have its own transaction confirmed before or instead of the observed transaction.
 
@@
 Therefore, DApps need to be studied individually or in categories.
-In this paper we draw from a scattered body of knowledge regarding front-running attacks on blockchain applications and proposed solutions, with series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps).
+In this paper, we draw from a scattered body of knowledge regarding front-running attacks on blockchain applications and the proposed solutions, with series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps).
 We do case studies on decentralized exchanges (\eg Bancor), crypto-collectibles (\eg CryptoKitties), gambling services (\eg Fomo3D), and decentralized name services (\eg Ethereum Name Service).
 We also study initial coin offerings (ICOs).
-Finally, we provide a categorization of  techniques to mitigate front-running including transaction sequencing, cryptographic techniques like commit/reveal, and redesigning the functioning of the DApp to provide the same utility while removing time dependencies.
+Finally, we provide a categorization of techniques to eliminate or mitigate front-running including transaction sequencing, cryptographic techniques like commit/reveal, and redesigning the functioning of the DApp to provide the same utility while removing time dependencies.
 
@@
 Front-running originates on the Chicago Board Options Exchange (\textit{CBoE}) \cite{markham1988front}.
-The Securities Exchange Commission \textit{(SEC)} in 1977 defines it as: ``The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{A block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}'' Self-regulating exchanges (\eg \textit{CBoE}) and the \textit{SEC} spent the ensuing years planning how to detect and outlaw front-running practices~\cite{markham1988front}.
+The Securities Exchange Commission \textit{(SEC)} in 1977 defined it as: ``The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{A block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily change the price.} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}'' Self-regulating exchanges (\eg \textit{CBoE}) and the \textit{SEC} spent the ensuing years planning how to detect and outlaw front-running practices~\cite{markham1988front}.
 The \textit{SEC} stated: ``It seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge.\footnote{Securities Exchange Act Release No.
@@
 The user can then broadcast a competing transaction that sends the same unspent coins to herself, perhaps using higher transaction fees, arrangements with miners or artifacts of the network topology to have the second transaction confirmed instead of the first.
-This can be considered a form of self-front-running.
+This can be considered a form of \textsf{self-front-running}.
 
-In the cryptographic literature, front-running attacks are modelled by allowing a `rushing' adversary to interact with the protocol.
-In particular, ideal functionalities of blockchains (such as those used in simulation-based proofs) need to capture this adversarial capability, assuming the realized blockchain does not address front-running.
+In the cryptographic literature, front-running attacks are modeled by allowing a `rushing' adversary to interact with the protocol.
+In particular, ideal functionalities of blockchains (such as those used in simulation-based proofs) need to capture this adversarial capability, assuming the real blockchain does not address front-running.
 See \eg Bitcoin backbone~\cite{garay2015bitcoin} and Hawk~\cite{kosba2016hawk}.
@@
 While a large category of gambling games are based on random outcomes, DApps do not have unique access to an unpredictable data stream to harvest for randomness~\cite{pierrot2018malleability}.
-Any candidate (such as block headers) source of randomness is accessible to all DApp functions and can also be manipulated to an extent by miners.
+Any candidate source of randomness (such as block headers) is accessible to all DApp functions and can also be manipulated to an extent by miners.
 
@@
 
-\subsection{Name Services.}\label{sec:ens}
+\subsection{Name Services}\label{sec:ens}
 
@@
 \subsection{Data Collection and Analysis}
-According to analysis we carried out, we discovered that the F2Pool---an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure~\ref{fig:mining_pool_ratio})---sent 100 Ether to 30 new Ethereum addresses before the Status.im ICO started.
-When the ICO opened, F2Pool constructed 31 transactions to the ICO smart contract from these new address, without broadcasting the transactions to the network.
+According to the analysis we carried out, we discovered that the F2Pool---an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure~\ref{fig:mining_pool_ratio})---sent 100 Ether to 30 new Ethereum addresses before the Status.im ICO started.
+When the ICO opened, F2Pool constructed 31 transactions to the ICO smart contract from their addresses, without broadcasting the transactions to the network.
 They used their entire mining power to mine their own transactions and some other potentially failing high gas price transactions.
@@
 
-By tracing the transactions from these 30 addresses, we found explicit interference by the F2Pool\footnote{F2Pool Ethereum address was identified by their mining reward deposit address \url{https://etherscan.io/address/0x61c808d82a3ac53231750dadc13c777b59310bd9}} in this scenario.
-As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses were sent to Status.im ICO and mined by F2Pool themselves, where the dynamic ceiling algorithm refunded a portion of the deposited funds back to these addresses, these funds were sent back to F2Pool main address a few days after and the tokens were aggregated later on in one single address.
-Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their mining software to behave in a certain way to front-run other transactions and gain monetary profit.
+By tracing the transactions from these 30 addresses, we found explicit interference by F2Pool\footnote{F2Pool Ethereum address was identified by their mining reward deposit address \url{https://etherscan.io/address/0x61c808d82a3ac53231750dadc13c777b59310bd9}.} in this scenario.
+As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses were sent to Status.im ICO and mined by F2Pool themselves, where the dynamic ceiling algorithm refunded a portion of the deposited funds back to these addresses, these funds were sent back to F2Pool main address a few days after and the tokens were aggregated later in one single address.
+Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their mining software to behave in a certain way to front-run other transactions by \textit{bulk displacement} and gain monetary profit.
 
@@
 %Shayan: maybe just a reference ^ suffices!
-%A recent attempt to build confidential transactions for DApps, is AZTEC protocol~\cite{aztec2018}.
+%A recent attempt to build confidential transactions for DApps is AZTEC protocol~\cite{aztec2018}.
 Similar to ZCash ~\cite{hopwood2016zcash}, it uses the concept of encrypted ‘notes’ and join-split transactions.
-ZCash uses two distinct types of addresses, transparent and shielded addresses, where in AZTEC, user transfers her ERC20 tokens into encrypted notes.
+ZCash uses two distinct types of addresses, transparent and shielded addresses, wherein AZTEC, the user transfers her ERC20 tokens into encrypted notes.
 Users can transfer these notes by destroying the unspent notes and creating new notes for the new owners, where the sum of the old notes should be equal to the sum of the new notes.
 %Shayan: Talk about AZTEC confidential transactions and their approach for CT.
-it will be possible to do dark pool style transactions within Ethereum dapps however they would still expose some information such as sender, receiver (exposes 5,6), hides (3,4?).
+it will be possible to do dark pool-style transactions within Ethereum DApps however they would still expose some information such as sender, receiver (exposes 5,6), hides (3,4?).
 https://medium.com/aztec-protocol/confidential-transactions-have-arrived-a-dive-into-the-aztec-protocol-a1794c00c009

### 2018-12-20 frontrunning/Latex/setup/table.tex

@@
 
+\definecolor{UnitedNationBlue}{rgb}{0.30,0.53,1}
+\definecolor{LightSteelBlue}{rgb}{0.69,0.77,0.87}
+\definecolor{LightGrey}{rgb}{0.83,0.83,0.83}
+
 \begin{table}[t]
@@
 {\caption{Top 25 DApps based on recent user activity from \texttt{DAppRadar.com} on September 4th, 2018. The DApps that are in bold are discussed in this paper.}\label{tab:top25DApps}}
-\begin{tabular}{|c|c|l|}
+\begin{tabular}{|c|c|c|l|}
 
 \hline
-\textbf{DApp Category}    										& \textbf{Names (Ranking)} \\  \hline
-\multirow{6}{*}{Exchanges} 										& IDEX (1) \\ 
-															& \textbf{ForkDelta, EtherDelta} (2) \\
-															& \textbf{Bancor} (7) \\
-															& The Token Store (13) \\
-															& LocalEthereum (14) \\
-															& Kyber (22) \\ 
-															& \textbf{0x Protocol} (23) \\ \hline
+\rowcolor{LightSteelBlue}
+ \textbf{DApp Category}    										& \textbf{Names} & Rank \\  \hline
+\multirow{6}{*}{Exchanges} 										& IDEX & 1 \\ 
+															& \cellcolor{LightGrey} \textbf{ForkDelta, EtherDelta} & 2 \\
+															& \cellcolor{LightGrey} \textbf{Bancor} & 7 \\
+															& The Token Store & 13 \\
+															& LocalEthereum & 14 \\
+															& Kyber & 22 \\ 
+															& \cellcolor{LightGrey} \textbf{0x Protocol} & 23 \\ \hline
 
-\multirow{9}{*}{\shortstack{Crypto-Collectible \\ Games \\ (ERC 721)}}		& \textbf{CryptoKitties} (3) \\  
-															& Ethermon (4)\\
-															& Cryptogirl (9)\\
-															& Gods Unchained TCG (12)\\
-															& Blockchain Cuties (15)\\
-															& ETH.TOWN! (16)\\
-															& 0xUniverse (18)\\
-															& MLBCrypto Baseball (19)\\
-															& HyperDragons (25)\\ \hline
+\multirow{9}{*}{\shortstack{Crypto-Collectible \\ Games \\ (ERC-721~\cite{erc721})}}
+															& \cellcolor{LightGrey} \textbf{CryptoKitties} & 3 \\  
+															& Ethermon & 4\\
+															& Cryptogirl & 9\\
+															& Gods Unchained TCG & 12\\
+															& Blockchain Cuties & 15\\
+															& ETH.TOWN! & 16\\
+															& 0xUniverse & 18\\
+															& MLBCrypto Baseball & 19\\
+															& HyperDragons & 25\\ \hline
 
-\multirow{8}{*}{Gambling}											& \textbf{Fomo3D} (5) \\  
-															& DailyDivs (6) \\																								& PoWH 3D (8)	 \\ 
-															& FomoWar (10) \\
-															& FairDapp (11)\\
-															& Zethr (17) \\
-															& dice2.win (20) \\ 
-															& Ether Shrimp Farm (21) \\  \hline
+\multirow{8}{*}{Gambling}										& \cellcolor{LightGrey} \textbf{Fomo3D} & 5 \\  
+															& DailyDivs & 6 \\													& PoWH 3D & 8	 \\ 
+															& FomoWar & 10 \\
+															& FairDapp & 11\\
+															& Zethr & 17 \\
+															& dice2.win & 20 \\ 
+															& Ether Shrimp Farm & 21 \\  \hline
 
-\multirow{1}{*}{Name Services}									& \textbf{Ethereum Name Service} (24)  \\  \hline
+\multirow{1}{*}{Name Services}									& \cellcolor{LightGrey} \textbf{Ethereum Name Service} & 24  \\  \hline
 

### 2018-12-20 frontrunning/Latex/sections/paper.tex
Still could not understand Malinova/Park summary, so fixed

@@
 
-Malinova and Park discuss similar design consideration for financial markets and trading platforms to mitigate front-running~\cite{malinova2017market}.
-They model indirect trading costs on search and trading at decentralized exchanges to make front-running costly and inefficient.
-They split big investments into smaller ones using intermediaries---liquidity demanders and providers.
-To prevent front-running, the liquidity demander offers the liquidity-providing trader an incentive; establishing an equilibrium behaviour, in which front-runner needs to pay more incentives to come in front of the original trade, minimizing front-running profits.
+In the finance literature, Malinova and Park discuss front-running mitigations for blockchain-based trading platforms~\cite{malinova2017market}.
+Instead of studying DApps, they develop an economic model where transactions, asset holdings, and traders' identities have greater transparency than in standard economic models---transparency they argue that could be accomplished by blockchain technology.
+However, in their model, they assume entities can interact directly over private channels to arrange trades.
+They define front-running in the context of private offers, where one party might adjust their position before accepted or countering a received offer.
+This model is quite different than the concrete DApp-based model we study here.
 

### 2019-01-13 frontrunning/Latex/sections/paper.tex
[frontrunning] add block stuffing attack ref
[frontrunning] batch auctions + authors + WIP watermark

@@
 However the key difference is that the front-runner does not care at all about the execution of her transactions---if miners mined empty blocks for three minutes, that would also be acceptable.
-Thus, bulk displacement is simply a means-to-an-end and not the actual end goal of the adversary.
+Thus, bulk displacement\footnote{Also known as Block Stuffing Attack~\cite{blockstuffing18}} is simply a means-to-an-end and not the actual end goal of the adversary.
 
@@
 For example, when designing a decentralized exchange, one can use a call market design instead of a time-sensitive order book~\cite{clark2014decentralizing} to side-step and disincentivize front-running.
-In a call market design, the arrival time of orders does not matter as they are executed in batches.
+In a call market design, the arrival time of orders does not matter as they are executed in batches\footnote{Also known as batch auctions~\cite{batchAuctions18}} .
 The call market solution pivots profitable gains that front-running miners stand to gain into fees that they collect~\cite{clark2014decentralizing}, removing the financial incentive to front-run.

### 2019-01-17 frontrunning/Latex/sections/paper.tex
[frontrunning] add a text/comment regarding ERC20 approve frontrunning

@@
 This attack follows the (asymmetric) insertion template and is illustrated in Figure~\ref{fig:MinerFrontrunning}.
+%Similarly, a front-running attack on ERC20 standard~\cite{erc20}, is on the allowance functionality, this allows a second entity to be able to spend N tokens from the owners balance.
+This attack is possible when the owner changes the allowance by calling a function \textit{approve()}, an attacker can front-run this transaction to allow herself to spend the allowance before the change replace the new allowance.
+There has been a few proposals to fix this issue, however some of them simply move the attack vector to another function.
+\\ citations: https://blog.smartdec.net/erc20-approve-issue-in-simple-words-a41aaf47bca6 , https://github.com/OpenZeppelin/openzeppelin-solidity/issues/437
 

### 2019-02-06 frontrunning/Latex/sections/paper.tex
[frontrunning] Fix affiliate + comments about cryptokitties
Add notes from meeting on Feb 5th
[frontrunning] add erc20 approve attack

--- 2019-01-13 frontrunning/Latex/sections/paper.tex
@@
 First, we are not aware of any other systematic study of this issue.
-Second, front-running is related to two well-studied concepts: double-spending and rushing adversaries.
+Second, front-running is related to two well-studied concepts: double-spending and rushing adversaries~\cite{kosba2016hawk}.
 
@@
 This can be considered a form of \textsf{self-front-running}.
-
-In the cryptographic literature, front-running attacks are modeled by allowing a `rushing' adversary to interact with the protocol.
+In the cryptographic literature, front-running attacks are modeled by allowing a so called `rushing' adversary to interact with the protocol~\cite{beaver1992cryptographic}.
 In particular, ideal functionalities of blockchains (such as those used in simulation-based proofs) need to capture this adversarial capability, assuming the real blockchain does not address front-running.
@@
 This attack follows the (asymmetric) insertion template and is illustrated in Figure~\ref{fig:MinerFrontrunning}.
+%0x has also added an option to cancel all orders through a batch cancellation mechanism to mitigate this issue.
 
@@
 % https://etherscan.io/tx/0x62a76b7e345e8abd463487d0348c118a9314b197024e090fee7b1fbce434da40
+
+% Shayan TODO:
+% remove most of the text above and replace it with references: https://hackernoon.com/how-we-made-100k-trading-cryptokitties-2d69aebe715b
+% disuss the application specific front-running, which is with giveBirth() function and front-running other calls
+% https://medium.com/block-science/exploring-cryptokitties-part-2-the-cryptomidwives-a0df37eb35a6
+% maybe: https://blog.kleros.io/generalized-ethereum-frontrunners-an-implementation-and-a-cheat/
 
@@
 
+%Shayan -> Jeremy: the following probably needs some rewrite to focus on the solution rather than the issue.
+Another example is in the design of ERC20 standard~\cite{erc20}, is on the allowance functionality.
+\textit{approve()} function in the specification allows a second entity to be able to spend N tokens from the sender's balance.
+In order to change the allowance, sender must set the new allowance value to\textit{approve()}.
+An attacker, using the insertion attack, could front-run the new allowance transaction and spend the old value before the new value is set~\cite{blockchainProjectAllowanceAttack,erc20GithubIssue}.
+Later on solutions such as \textit{decreaseApproval() / increaseApproval()} was added instead of replacing the value.
+
 % = = = = = = = = = = = = = = = = = = = = = = = = = = %

### 2019-02-06 frontrunning/Latex/sections/paper.tex
fix typos

@@
 \emph{Front-running} is a course of action where someone benefits from early access to market information about upcoming transactions and trades, typically because of a privileged position along the transmission of this information and is applicable to both financial and non-financial systems.
-Historically, floor traders might have overhear a broker's negotiation with her client over a large purchase, and literally race the broker to buy first, potentially profiting when the large purchase temporarily reduces the supply of the stock.
+Historically, floor traders might have overheard a broker's negotiation with her client over a large purchase, and literally race the broker to buy first, potentially profiting when the large purchase temporarily reduces the supply of the stock.
 Alternatively, a malicious broker might front-run their own client's orders by purchasing stock for themselves between receiving the instruction to purchase from the client and actually executing the purchase (similar techniques can be used for large sell orders).
@@
 Exchanges such as EtherDelta\footnote{Also known as ForkDelta for the user interface: \url{https://forkdelta.app/}}, purport to implement a decentralized exchange, however, their order books are stored on a central server they control and shown to their users with a website interface.
-Central exchanges can front-run orders in the traditional sense, as well as re-order or block orders on their servers 0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the order book holders and could front-run the orders they relay.
+Central exchanges can front-run orders in the traditional sense, as well as re-order or block orders on their servers.
+0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the order book holders and could front-run the orders they relay.
 
@@
 The final category in Table~\ref{tab:top25DApps} is name services, which are primarily aimed at disintermediating central parties involved in web domain registration (\eg ICAAN and registrars) and resolution (\eg DNS).
-For simple name services (such as some academic work like Ghazal~\cite{moosavighazal}), domains purchases are transactions and network monitors can displace other users attempting to register domains.
-This parallels front-running attacks seen in regular (non-blockchain) domain registration~\cite{sac022en33:online}.
+For simple name services (such as some academic work like Ghazal~\cite{moosavighazal}), domains purchases are transactions and front-runners can displace other users attempting to register domains.
+This parallels front-running attacks have been seen in regular (non-blockchain) domain registration~\cite{sac022en33:online}.
 \textsf{Ethereum Name Service (ENS)}\footnote{\url{https://ens.domains/}} is the most active naming service on Ethereum.
@@
 A DApp could disintermediate this trusted party.
-Users whose balances are effected by changes in the contract's state would need to be able to learn this information.
+Users whose balances are affected by changes in the contract's state would need to be able to learn this information.
 Further, if the contract addresses are known (\ie no 5-confidentiality), front-runners can know about the traffic pattern of calls to contracts which could be sufficient grounds for attack; for example, if each asset on an exchange has its own market contract, this leaks trade volume information.

### 2019-02-06 frontrunning/Latex/sections/paper.tex
fix ENS section

@@
 For simple name services (such as some academic work like Ghazal~\cite{moosavighazal}), domains purchases are transactions and front-runners can displace other users attempting to register domains.
-This parallels front-running attacks have been seen in regular (non-blockchain) domain registration~\cite{sac022en33:online}.
+This parallels front-running attacks seen in regular (non-blockchain) domain registration~\cite{sac022en33:online}.
 \textsf{Ethereum Name Service (ENS)}\footnote{\url{https://ens.domains/}} is the most active naming service on Ethereum.
 Instead of allowing new \texttt{.eth} domain names to be purchased directly, they are put up for a sealed bid auction which seals the domain name in the bids, but not the bid amounts.
-The most common way of getting a domain is to call \texttt{startAuctionsAndBid()} in ENS auction smart contract, which leaks the hash of the domain name and the initial bid amount in the auction.
+Most implementations use the more user friendly but less confidential method for starting and bidding on a domain name, \texttt{startAuctionsAndBid()}.
+This method leaks the hash of the domain and the initial bid amount in the auction.
 Users are allowed to bid for 48 hours before the 48-hour reveal phase begins, in which bidders must send a transaction to reveal their bids for a specific domain in the auction.
-It is possible for a user to front-run other bids with the same bid amount by revealing first.
+A front-runner using the leaked information can bid with the same amount and reveal prior to the original bidder to win the auction.
 The auction model is similar to crypto-collectibles auctions in \ref{sec:cryptogames}.

### 2019-02-06 frontrunning/Latex/sections/paper.tex
More citations and fixes

@@
 When the timer of the game reached about 3 minutes, the winner bought 1 ticket and then sent multiple high gasPrice transactions to her own DApps.
-These transactions congested the network and bribed miners to prioritize them ahead of any new ticket purchases in \textsf{Fomo3D}.
+These transactions congested the network and bribed miners~\cite{mccorry2018smart,bonneau2016buy} to prioritize them ahead of any new ticket purchases in \textsf{Fomo3D} .
 
@@
 Users are allowed to bid for 48 hours before the 48-hour reveal phase begins, in which bidders must send a transaction to reveal their bids for a specific domain in the auction.
-A front-runner using the leaked information can bid with the same amount and reveal prior to the original bidder to win the auction.
+A front-runner using the leaked information can bid with the same amount and reveal prior to the original bidder to win the auction~\cite{ENSHandlingFrontRunningDiscussion}.
 The auction model is similar to crypto-collectibles auctions in \ref{sec:cryptogames}.
@@
 According to the analysis we carried out, we discovered that the F2Pool---an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure~\ref{fig:mining_pool_ratio})---sent 100 Ether to 30 new Ethereum addresses before the Status.im ICO started.
-When the ICO opened, F2Pool constructed 31 transactions to the ICO smart contract from their addresses, without broadcasting the transactions to the network.
+When the ICO opened, F2Pool constructed 31 transactions to the ICO smart contract from their addresses, without broadcasting the transactions to the network\footnote{Note that we don’t have an authoritative copy of the mempool over time, however, the probability of these transactions being broadcasted to the network and exclusively get mined by the same pool as the sender is really low.}.
 They used their entire mining power to mine their own transactions and some other potentially failing high gas price transactions.

### 2019-02-06 frontrunning/Latex/sections/paper.tex
De-anonymize the github url + minor edits

@@
 Given the purpose of this entire paper is systemizing the existing literature, we do not re-enumerate the literature here.
-However, we note two things.
+However, we note two points.
 First, we are not aware of any other systematic study of this issue.
@@
 Further study showed that some mining pools might have been manipulating the network for their own profit.
-In addition, there were many transactions sent with a higher gas price to front-run other transactions, however, these transactions were failing due to the restriction in the ICO smart contract to reject any transactions with higher than 50 \textit{GWei} gas price (another mitigation against front-running).
+In addition, there were many transactions sent with a higher gas price to front-run other transactions, however, these transactions were failing due to the restriction in the ICO smart contract to reject transactions with higher than 50 \textit{GWei} gas price (as a mitigation against front-running).
 
@@
 Specifically, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation\url{https://github.com/ethereum/go-ethereum}.} for the full node, a python script for extracting, transforming and loading Ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery.\footnote{\url{https://cloud.google.com/bigquery/}} Using this software stack, we were able to isolate transactions within the Status.im ICO.
-We used data analysis tool \texttt{Tableau}.\footnote{\url{https://www.tableau.com/}} A copy of this dataset and the initial findings can be found in our Github repository.\footnote{\url{github.com/} Removed for anonymity.}
+We used data analysis tool \texttt{Tableau}.\footnote{\url{https://www.tableau.com/}} A copy of this dataset and the initial findings can be found in our Github repository\footnote{\url{http://bit.ly/madibaFrontrunning}}.
 
@@
 
-By tracing the transactions from these 30 addresses, we found explicit interference by F2Pool\footnote{F2Pool Ethereum address was identified by their mining reward deposit address \url{https://etherscan.io/address/0x61c808d82a3ac53231750dadc13c777b59310bd9}.} in this scenario.
+By tracing the transactions from these 30 addresses, we found explicit interference by F2Pool\footnote{F2Pool address was identified by their mining reward deposit address \url{https://etherscan.io/address/0x61c808d82a3ac53231750dadc13c777b59310bd9}.} in this scenario.
 As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses were sent to Status.im ICO and mined by F2Pool themselves, where the dynamic ceiling algorithm refunded a portion of the deposited funds back to these addresses, these funds were sent back to F2Pool main address a few days after and the tokens were aggregated later in one single address.
@@
 %Shayan -> Jeremy: the following probably needs some rewrite to focus on the solution rather than the issue.
-Another example is in the design of ERC20 standard~\cite{erc20}, is on the allowance functionality.
+Another example in the design of ERC20 standard~\cite{erc20}, is on the allowance functionality.
 \textit{approve()} function in the specification allows a second entity to be able to spend N tokens from the sender's balance.
-In order to change the allowance, sender must set the new allowance value to\textit{approve()}.
-An attacker, using the insertion attack, could front-run the new allowance transaction and spend the old value before the new value is set~\cite{blockchainProjectAllowanceAttack,erc20GithubIssue}.
-Later on solutions such as \textit{decreaseApproval() / increaseApproval()} was added instead of replacing the value.
+In order to change the allowance, sender must send a transaction to set the new allowance value.
+Using the insertion attack, attacker could front-run the new allowance transaction and spend the old value before the new value is set~\cite{blockchainProjectAllowanceAttack,erc20GithubIssue}.
+Solutions such as \textit{decreaseApproval()}/\textit{increaseApproval()} were added in updated implementations.
 

### 2019-02-06 frontrunning/Latex/sections/paper.tex
Some more edits, will continue later

@@
 At the Ethereum level, the kitty is a token implemented with \textit{ERC-721: Non-Fungible Token Standard}~\cite{erc721}.
-The market cap of cryptokitties peaked at more than 6 million dollars in the first few months of their launch, however, it has declined since.
+
+% SHAYAN: TODO: Continue here! 
+Specific to Cryptokitties protocol, they can breed and give birth.
+Anyone calling \textit{giveBirth()} quickly after the expected birthing time, will receive the birthing reward and give birth to the new cryptokitten which will be owned by the mother's owner.
+
 ERC-721 are similar enough to ERC-20 tokens that they can be listed on exchanges that are ERC-20 compatible.
 To buy a kitty from their main website, the user sends the following bid transaction: \texttt{bid(uint256 \_tokenId)}.
-It contains the kitty's ID which can be found either on their website or on the ERC721 token smart contract.
-This is similar to open auctions and markets on section~\ref{sec:frontrunningExchanges}, bid value and the object bidding on is visible to the network and any user could  easily front-run by sending the same transaction with higher gasPrice to replace the initial bidder.
+This is similar to open auctions and markets on section~\ref{sec:frontrunningExchanges}, bid value and the object (tokenId) bidding on is visible to the network and any user could easily front-run using insertion or displacement attack.
 The front-runner can see there is an interest in a specific kitty and insert a pair of transactions to buy it and re-auctioning it at a higher price, keeping any profit.
@@
 % https://etherscan.io/tx/0x62a76b7e345e8abd463487d0348c118a9314b197024e090fee7b1fbce434da40
+
+~\cite{zhou2018erays}
 

### 2019-02-08 frontrunning/Latex/sections/paper.tex
[frontrunning] modifications on cryptokitties specific front-running

@@
 
-% SHAYAN: TODO: Continue here! 
+%Shayan -> Jeremy: does this make sense? there are more details in the references that due to space limitations cannot be discussed here.
 Specific to Cryptokitties protocol, they can breed and give birth.
-Anyone calling \textit{giveBirth()} quickly after the expected birthing time, will receive the birthing reward and give birth to the new cryptokitten which will be owned by the mother's owner.
+When cryptokitties breed, a variable is set on the pregnant cat to indicate what block the pregnancy will be complete.
+Anyone calling \texttt{giveBirth()} quickly after the expected birthing time, will receive the birthing reward\footnote{As there are no automated function calls in Ethereum, this incentive model --known as \textit{Action Callback}~\cite{klerosGeneralizedFrontrunner2019}-- is used to encourage users to call these functions.}.
+Even though front-running these calls would not affect the protocol workflow, but it could result in financial profit for front-runners~\cite{zhou2018erays,cryptoMidwivesBot2018}.
 
@@
 % https://etherscan.io/tx/0x62a76b7e345e8abd463487d0348c118a9314b197024e090fee7b1fbce434da40
-
-~\cite{zhou2018erays}
-
-% Shayan TODO:
-% remove most of the text above and replace it with references: https://hackernoon.com/how-we-made-100k-trading-cryptokitties-2d69aebe715b
-% disuss the application specific front-running, which is with giveBirth() function and front-running other calls
-% https://medium.com/block-science/exploring-cryptokitties-part-2-the-cryptomidwives-a0df37eb35a6
-% maybe: https://blog.kleros.io/generalized-ethereum-frontrunners-an-implementation-and-a-cheat/
 

### 2019-02-08 frontrunning/Latex/sections/paper.tex
make it almost 15 pages again.

@@
 The second category of DApp in Table~\ref{tab:top25DApps} is crypto-collectables.
-Consider Cryptokitties\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}}, the most active DApp in this category and third most active overall.
+Consider Cryptokitties~\cite{cryptokitties}, the most active DApp in this category and third most active overall.
 Each kitty (see Appendix~\ref{app:cryptokitty}) is a cartoon kitten with a set of unique features to distinguish it from other cryptokitties, some features are rarer and harder to obtain.
@@
 This parallels front-running attacks seen in regular (non-blockchain) domain registration~\cite{sac022en33:online}.
-\textsf{Ethereum Name Service (ENS)}\footnote{\url{https://ens.domains/}} is the most active naming service on Ethereum.
+\textsf{Ethereum Name Service (ENS)}~\cite{ensEIP} is the most active naming service on Ethereum.
 Instead of allowing new \texttt{.eth} domain names to be purchased directly, they are put up for a sealed bid auction which seals the domain name in the bids, but not the bid amounts.
@@
 This method leaks the hash of the domain and the initial bid amount in the auction.
-Users are allowed to bid for 48 hours before the 48-hour reveal phase begins, in which bidders must send a transaction to reveal their bids for a specific domain in the auction.
+Users are allowed to bid for 48 hours before the 48-hour reveal phase begins, in which bidders must send a transaction to reveal their bids for a specific domain.
 A front-runner using the leaked information can bid with the same amount and reveal prior to the original bidder to win the auction~\cite{ENSHandlingFrontRunningDiscussion}.
@@
 By tracing the transactions from these 30 addresses, we found explicit interference by F2Pool\footnote{F2Pool address was identified by their mining reward deposit address \url{https://etherscan.io/address/0x61c808d82a3ac53231750dadc13c777b59310bd9}.} in this scenario.
-As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses were sent to Status.im ICO and mined by F2Pool themselves, where the dynamic ceiling algorithm refunded a portion of the deposited funds back to these addresses, these funds were sent back to F2Pool main address a few days after and the tokens were aggregated later in one single address.
-Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their mining software to behave in a certain way to front-run other transactions by \textit{bulk displacement} and gain monetary profit.
+As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses were sent to \textit{Status.im} ICO and mined by F2Pool themselves, where the dynamic ceiling algorithm refunded a portion of the deposited funds.
+A few days after these funds were sent back to F2Pool main address and the tokens were aggregated later in one single address.
+Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their mining software to behave in a certain way to front-run other transactions by \textit{bulk displacement} to gain monetary profit.
 
@@
 However, in their model, they assume entities can interact directly over private channels to arrange trades.
-They define front-running in the context of private offers, where one party might adjust their position before accepted or countering a received offer.
-This model is quite different than the concrete DApp-based model we study here.
+They define front-running in the context of private offers, where parties might adjust their position before accepting or countering a received offer.
+This model is quite different than the DApp-based model we study here.
 

### 2019-02-11 frontrunning/Latex/sections/paper.tex
Updates, ENS still needs more work!

@@
 At the Ethereum level, the kitty is a token implemented with \textit{ERC-721: Non-Fungible Token Standard}~\cite{erc721}.
+Kitties are generally bought and sold on-chain through auction smart contracts.
+See Sections ~\ref{sec:frontrunningExchanges} and ~\ref{sec:ens} for more details on auction-based front-running attacks.
 
-%Shayan -> Jeremy: does this make sense? there are more details in the references that due to space limitations cannot be discussed here.
-Specific to Cryptokitties protocol, they can breed and give birth.
-When cryptokitties breed, a variable is set on the pregnant cat to indicate what block the pregnancy will be complete.
-Anyone calling \texttt{giveBirth()} quickly after the expected birthing time, will receive the birthing reward\footnote{As there are no automated function calls in Ethereum, this incentive model --known as \textit{Action Callback}~\cite{klerosGeneralizedFrontrunner2019}-- is used to encourage users to call these functions.}.
-Even though front-running these calls would not affect the protocol workflow, but it could result in financial profit for front-runners~\cite{zhou2018erays,cryptoMidwivesBot2018}.
-
-ERC-721 are similar enough to ERC-20 tokens that they can be listed on exchanges that are ERC-20 compatible.
+%ERC-721 are similar enough to ERC-20 tokens that they can be listed on exchanges that are ERC-20 compatible.
 To buy a kitty from their main website, the user sends the following bid transaction: \texttt{bid(uint256 \_tokenId)}.
@@
 % https://etherscan.io/tx/0x62a76b7e345e8abd463487d0348c118a9314b197024e090fee7b1fbce434da40
+
+Specific to Cryptokitties protocol, they can breed and give birth.
+When cryptokitties breed, the smart contract sets from which future block the pregnancy of the cat can be completed.
+Anyone can complete the pregnancy by calling \texttt{giveBirth()} after the birthing block and they will receive a reward in ether\footnote{As there are no automated function calls in Ethereum, this incentive model --known as \textit{Action Callback}~\cite{klerosGeneralizedFrontrunner2019}-- is used to encourage users to call these functions.}.
+Even though front-running these calls would not affect the protocol workflow, but this displacement attack could result in financial profit for front-runners~\cite{zhou2018erays,cryptoMidwivesBot2018}.
 
@@
 When the timer of the game reached about 3 minutes, the winner bought 1 ticket and then sent multiple high gasPrice transactions to her own DApps.
-These transactions congested the network and bribed miners~\cite{mccorry2018smart,bonneau2016buy} to prioritize them ahead of any new ticket purchases in \textsf{Fomo3D} .
+These transactions congested the network and bribed miners to prioritize them ahead of any new ticket purchases in \textsf{Fomo3D}.
+Recall this basic form of bribery is called a \textit{Gas Auction}; See related work ~\cite{mccorry2018smart,bonneau2016buy} for more sophisticated bribery contracts.
 
@@
 \textsf{Ethereum Name Service (ENS)}~\cite{ensEIP} is the most active naming service on Ethereum.
-Instead of allowing new \texttt{.eth} domain names to be purchased directly, they are put up for a sealed bid auction which seals the domain name in the bids, but not the bid amounts.
-Most implementations use the more user friendly but less confidential method for starting and bidding on a domain name, \texttt{startAuctionsAndBid()}.
+Instead of allowing new \texttt{.eth} domain names to be purchased directly, they are put up for a sealed bid auction which seals the domain name in a bid, but not the bid amount.
+Most implementations use the more user friendly but less confidential method for starting and bidding on a domain name: \texttt{startAuctionsAndBid()}.
 This method leaks the hash of the domain and the initial bid amount in the auction.
-Users are allowed to bid for 48 hours before the 48-hour reveal phase begins, in which bidders must send a transaction to reveal their bids for a specific domain.
+Original names can be guessed from the hashes (\eg rainbow tables, used in ENS Twitter bot) or people can bid on domains even though they do not know what they are because of speculation on its value.
+
+Users are allowed to bid for 3 days before the 48-hour reveal phase begins (see ~\ref{sec:comm}), in which all bidders (winners and losers) must send a transaction to reveal their bids for a specific domain or sacrifice their bid amount .
+Also note that if two bidders bid the same price, the first to reveal wins it.
+
+Two strategies: (1) Attacker knows the domain name, then he makes sure he is first to reveal.
+(2) Attacker is speculating, so he waits to see other reveal, then insert myself with the information from the other reveal.
+(3) If my amount is bigger, I see other reveal and then reveal.
+
+Displacement attack <--
+
 A front-runner using the leaked information can bid with the same amount and reveal prior to the original bidder to win the auction~\cite{ENSHandlingFrontRunningDiscussion}.
-The auction model is similar to crypto-collectibles auctions in \ref{sec:cryptogames}.
+The auction model is similar to open auctions in \ref{sec:cryptogames}.
 
@@
 According to the analysis we carried out, we discovered that the F2Pool---an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure~\ref{fig:mining_pool_ratio})---sent 100 Ether to 30 new Ethereum addresses before the Status.im ICO started.
-When the ICO opened, F2Pool constructed 31 transactions to the ICO smart contract from their addresses, without broadcasting the transactions to the network\footnote{Note that we don’t have an authoritative copy of the mempool over time, however, the probability of these transactions being broadcasted to the network and exclusively get mined by the same pool as the sender is really low.}.
+When the ICO opened, F2Pool constructed 31 transactions to the ICO smart contract from their addresses, without broadcasting the transactions to the network\footnote{Note that we do not have an authoritative copy of the mempool over time, however, the probability of these transactions being broadcasted to the network and exclusively get mined by the same pool as the sender is low.}.
 They used their entire mining power to mine their own transactions and some other potentially failing high gas price transactions.

### 2019-02-11 frontrunning/Latex/sections/paper.tex
Blocked! will wrap up ENS tmr.

@@
 This method leaks the hash of the domain and the initial bid amount in the auction.
-Original names can be guessed from the hashes (\eg rainbow tables, used in ENS Twitter bot) or people can bid on domains even though they do not know what they are because of speculation on its value.
+Original names can be guessed from the hashes (\eg rainbow tables, used in ENS Twitter bot\footnote{\url{https://twitter.com/ensbot}}) or people can bid on domains even though they do not know what they are because of speculation on its value.
 
 Users are allowed to bid for 3 days before the 48-hour reveal phase begins (see ~\ref{sec:comm}), in which all bidders (winners and losers) must send a transaction to reveal their bids for a specific domain or sacrifice their bid amount .
-Also note that if two bidders bid the same price, the first to reveal wins it.
+Also note that if two bidders bid the same price, the first to reveal wins it~\cite{ENSHandlingFrontRunningDiscussion}.
+Combined with the leaked information, this introduces a race condition which could be mitigated if bidding time was taken into effect instead of solely reveal time.
 
 Two strategies: (1) Attacker knows the domain name, then he makes sure he is first to reveal.
-(2) Attacker is speculating, so he waits to see other reveal, then insert myself with the information from the other reveal.
+(2) Attacker is speculating, which he will bid with a slightly higher value %so he waits to see other reveal, then insert myself with the information from the other reveal.
 (3) If my amount is bigger, I see other reveal and then reveal.
+
+Sealed bids could easily be identified from the recent transactions --> depends on the anonymity set
 
@@
 
-A front-runner using the leaked information can bid with the same amount and reveal prior to the original bidder to win the auction~\cite{ENSHandlingFrontRunningDiscussion}.
-The auction model is similar to open auctions in \ref{sec:cryptogames}.
+%A front-runner using the leaked information can bid with the same amount and reveal prior to the original bidder to win the auction.
+
+Also using the leaked information, the front-running attack vector mimics the traditional domain front-running attacks. The auction model is similar to open auctions in \ref{sec:cryptogames}.
 

### 2019-02-12 frontrunning/Latex/sections/paper.tex
[frontrunning] ENS stuff

@@
 
-Users are allowed to bid for 3 days before the 48-hour reveal phase begins (see ~\ref{sec:comm}), in which all bidders (winners and losers) must send a transaction to reveal their bids for a specific domain or sacrifice their bid amount .
+Users are allowed to bid for 3 days before the 2-day reveal phase begins (see ~\ref{sec:comm}), in which all bidders (winners and losers) must send a transaction to reveal their bids for a specific domain or sacrifice their bid amount .
 Also note that if two bidders bid the same price, the first to reveal wins it~\cite{ENSHandlingFrontRunningDiscussion}.
-Combined with the leaked information, this introduces a race condition which could be mitigated if bidding time was taken into effect instead of solely reveal time.
-
-Two strategies: (1) Attacker knows the domain name, then he makes sure he is first to reveal.
-(2) Attacker is speculating, which he will bid with a slightly higher value %so he waits to see other reveal, then insert myself with the information from the other reveal.
-(3) If my amount is bigger, I see other reveal and then reveal.
-
-Sealed bids could easily be identified from the recent transactions --> depends on the anonymity set
-
-Displacement attack <--
-
-%A front-runner using the leaked information can bid with the same amount and reveal prior to the original bidder to win the auction.
-
-Also using the leaked information, the front-running attack vector mimics the traditional domain front-running attacks. The auction model is similar to open auctions in \ref{sec:cryptogames}.
+Using the leaked information, the domain squatter can win the auction with the same price of the original bidder by revealing it first.
+This is similar to front-running as it relies on inserting an action before the user, however we do not consider this specific action as front-running attack.
 
@@
 
-%Shayan -> Jeremy: the following probably needs some rewrite to focus on the solution rather than the issue.
+%Shayan -> TODO: Jeremy: the following probably needs some rewrite to focus on the solution rather than the issue.
 Another example in the design of ERC20 standard~\cite{erc20}, is on the allowance functionality.
@@
 
+%Jeremy TODO
 \section{Concluding Remarks}

### 2019-02-13 frontrunning/Latex/sections/paper.tex
[frontrunning] minor edit

@@
 In order to change the allowance, sender must send a transaction to set the new allowance value.
-Using the insertion attack, attacker could front-run the new allowance transaction and spend the old value before the new value is set~\cite{blockchainProjectAllowanceAttack,erc20GithubIssue}.
+Using the insertion attack, attacker could front-run the new allowance transaction and spend the old value before the new value is set~\cite{blockchainProjectAllowanceAttack,erc20GithubIssue}, and then additionally spend the new amount at a later time.
 Solutions such as \textit{decreaseApproval()}/\textit{increaseApproval()} were added in updated implementations.

### 2019-02-13 frontrunning/Latex/main.tex
some other edits
Still could not understand Malinova/Park summary, so fixed
[frontrunning] batch auctions + authors + WIP watermark
[frontrunning] Fix affiliate + comments about cryptokitties
Add notes from meeting on Feb 5th
[frontrunning] uncomment Acknowledgements

--- 2018-09-28 frontrunning/Latex/main.tex
@@
 
-\title{The paper on blockchain front-running}
-\author{Shayan Eskandari, Seyedehmahsa Moosavi, \and Jeremy Clark}
+\title{SoK: Transparent Dishonesty: front-running attacks on Blockchain.}
+\author{}
+
+\author{
+	Shayan Eskandari\inst{\dag\ddag},
+	Seyedehmahsa Moosavi\inst{\dag},
+	Jeremy Clark\inst{\dag}
+	}
 
 \institute{
-	Gina Cody School of Engineering and Computer Science\\ Concordia University
+	\textsuperscript{\dag} Gina Cody School of Engineering and Computer Science\\ Concordia University \\
+	\textsuperscript{\ddag} ConsenSys Diligence
 	}
@@
 
-\clearpage
 \bibliography{bib/Frontrunning_Ref}

### 2019-02-13 frontrunning/Latex/sections/appendix.tex
[Frontrunning] Remove extra stuff from Appendix

@@
 \appendix
-
-\textblue{\textbf{Note to Reviewers:}} If accepted, the camera-ready version will link to a full version of the paper on eprint that will include the information in this appendix.
-We include it here for reference.
 
@@
 
-\section{LocalEthereum} \label{app:localethereum}
-
+%\section{LocalEthereum} \label{app:localethereum}
+%
 %Possibly remove this code snippet due to page limit . don't forget to remove the refrence to it ^
-\begin{lstlisting}[basicstyle=\scriptsize\ttfamily,caption={Code snippet from LocalEthereum smart contract.
+%\begin{lstlisting}[basicstyle=\scriptsize\ttfamily,caption={Code snippet from LocalEthereum smart contract.
 Values V,R and S are set by LocalEtherem to have a valid signature, also the tradeHash uses buyer and seller addresses, mitigating the possibility of front-running by a third party.},label={code:localethereum}]
-    function createEscrow(bytes16 _tradeID, address _seller, address _buyer, uint256 _value, uint16 _fee,
-					uint32 _paymentWindowInSeconds, uint32 _expiry, uint8 _v, bytes32 _r, bytes32 _s) 
-        payable external {
-        bytes32 _tradeHash = keccak256(abi.encodePacked(_tradeID, _seller, _buyer, _value, _fee));
-	...
-        // A signature (v, r and s) must come from localethereum to open an escrow
-        bytes32 _invitationHash = keccak256(abi.encodePacked(
-            _tradeHash,
-            _paymentWindowInSeconds,
-            _expiry
-        )); 
-\end{lstlisting}
-
-Code~\ref{code:localethereum} shows a mitigation technique employed by LocalEthereum. \\
+%    function createEscrow(bytes16 _tradeID, address _seller, address _buyer, uint256 _value, uint16 _fee,
+%					uint32 _paymentWindowInSeconds, uint32 _expiry, uint8 _v, bytes32 _r, bytes32 _s) 
+%        payable external {
+%        bytes32 _tradeHash = keccak256(abi.encodePacked(_tradeID, _seller, _buyer, _value, _fee));
+%	...
+%        // A signature (v, r and s) must come from localethereum to open an escrow
+%        bytes32 _invitationHash = keccak256(abi.encodePacked(
+%            _tradeHash,
+%            _paymentWindowInSeconds,
+%            _expiry
+%        )); 
+%\end{lstlisting}
+%
+%Code~\ref{code:localethereum} shows a mitigation technique employed by LocalEthereum. \\
 

### 2019-02-16 frontrunning/Latex/sections/paper.tex
[frontrunning] variants and minor fixes

@@
 Examples of displacement include: Alice trying to register a domain name and Mallory registering it first~\cite{kalodner2015empirical}; Alice trying to submit a bug to receive a bounty and Mallory stealing it and submitting it first~\cite{breidenbach2018enter}; and Alice trying to submit a bid in an auction and Mallory copying it.
-In some cases, Alice's function and Mallory's function are different: \eg Alice trying to cancel an offer and Mallory fulfilling the offer first.
-We call this \textit{asymmetric displacement}.
-Finally, in some cases, Mallory is trying to run a large set of functions: for example Alice and others are trying to buy a limited set of shares offered by a firm on a blockchain.
-We call this \textit{bulk displacement}.
 
@@
 We only observe this attack pattern in one DApp and the details are quite specific to it, so we defer discussion until Section~\ref{sec:gambling}.
+
+Each of these attacks have two other variants, \textit{asymmetric} and \textit{bulk}.
+For example, Alice's function and Mallory's function are different: \eg Alice trying to cancel an offer and Mallory fulfilling the offer first.
+We call this \textit{asymmetric displacement}.
+Finally, in some cases, Mallory is trying to run a large set of functions: for example Alice and others are trying to buy a limited set of shares offered by a firm on a blockchain.
+We call this \textit{bulk displacement}.
 
@@
 In this case, when an adversarial actor sees a pending cancellation transaction, he sends a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled (this is known as \textit{cancellation grief}).
-This attack follows the (asymmetric) insertion template and is illustrated in Figure~\ref{fig:MinerFrontrunning}.
+This attack follows the asymmetric displacement template and is illustrated in Figure~\ref{fig:MinerFrontrunning}.
 %0x has also added an option to cancel all orders through a batch cancellation mechanism to mitigate this issue.
@@
 To deal with demand, ICOs cap sales in a variety of ways to mitigate front-running attacks.
-In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached the predefined cap within 3 hours, collecting close to 300,000 Ether.
+In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached the predefined cap within 16 hours, collecting close to 300,000 Ether.
 In order to prevent wealthy investors purchasing all the tokens and limit the amount of Ether deposited in each investment, they used a \textit{fair} token distribution method called \textit{Dynamic Ceiling} as an attempt to increase the opportunity for smaller investors.

### 2019-02-18 frontrunning/Latex/sections/paper.tex
[frontrunning] minor fix
[frontrunning] fix some wording

@@
 Function calls (or transactions) to the DApp are processed by a decentralized network.
-Transactions are finalized in stages: they (generally) first relay around the network, then selected by a miner and put into a valid block, and finally, the block is well-enough incorporated that is unlikely to be reorganized.
+Transactions are finalized in stages: they (generally) first relay around the network, then are selected by a miner and put into a valid block, and finally, the block is well-enough incorporated that is unlikely to be reorganized.
 Front-running is an attack where a malicious node observes a transaction after it is broadcast but before it is finalized, and attempts to have its own transaction confirmed before or instead of the observed transaction.
 
-The mechanics of front-running works on all DApps but front-running is not necessarily beneficial, depending on the DApp's internal logic and/or as any mitigations it might implement.
+The mechanics of front-running work on all DApps but front-running is not necessarily beneficial, depending on the DApp's internal logic and/or as any mitigations it might implement.
 Therefore, DApps need to be studied individually or in categories.
-In this paper, we draw from a scattered body of knowledge regarding front-running attacks on blockchain applications and the proposed solutions, with series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps).
+In this paper, we draw from a scattered body of knowledge regarding front-running attacks on blockchain applications and the proposed solutions, with a series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps).
 We do case studies on decentralized exchanges (\eg Bancor), crypto-collectibles (\eg CryptoKitties), gambling services (\eg Fomo3D), and decentralized name services (\eg Ethereum Name Service).
@@
 
-Each of these attacks have two other variants, \textit{asymmetric} and \textit{bulk}.
+Each of these attacks have two variants, \textit{asymmetric} and \textit{bulk}.
 For example, Alice's function and Mallory's function are different: \eg Alice trying to cancel an offer and Mallory fulfilling the offer first.
@@
 The applicability of privacy-preserving blockchains needs to be evaluated on a case-by-case base.
-For example, one method used by traditional financial exchanges in dealing with front-running from high frequency traders is a dark market: essentially a (2,3,4)-confidential order book maintained by a trusted party.
+For example, one method used by traditional financial exchanges in dealing with front-running from high frequency traders is a dark pool: essentially a (2,3,4)-confidential order book maintained by a trusted party.
 A DApp could disintermediate this trusted party.

### 2019-02-18 frontrunning/Latex/sections/paper.tex
[forontrunning] fix ghazal citation

@@
 The final category in Table~\ref{tab:top25DApps} is name services, which are primarily aimed at disintermediating central parties involved in web domain registration (\eg ICAAN and registrars) and resolution (\eg DNS).
-For simple name services (such as some academic work like Ghazal~\cite{moosavighazal}), domains purchases are transactions and front-runners can displace other users attempting to register domains.
+For simple name services (such as some academic work like Ghazal~\cite{moosavi2018ghazal}), domains purchases are transactions and front-runners can displace other users attempting to register domains.
 This parallels front-running attacks seen in regular (non-blockchain) domain registration~\cite{sac022en33:online}.

### 2019-02-19 frontrunning/Latex/sections/paper.tex
[frontrunning] Fix some typos and conclusion

--- 2019-02-18 frontrunning/Latex/sections/paper.tex
@@
 A trusted third party can be used to assign sequential numbers to transactions (and sign them), but this is contrary to blockchain's core innovation of distributed trust.
-None the less, some exchanges do centralize time-sensitive functionalities (\eg  \textit{EtherDelta} and \textit{0xProject}) in off-chain order books~\cite{warren20170x,0xfrontrunning:online}.
+Nonetheless, some exchanges do centralize time-sensitive functionalities (\eg  \textit{EtherDelta} and \textit{0xProject}) in off-chain order books~\cite{warren20170x,0xfrontrunning:online}.
 
@@
 
-A DApp includes the following components: (1) the code of the DApp, (2) the current state of the DApp, (3) the name of the function being invoked, (4) the parameters supplied to the function, (5) the address of the contract the function is being invoked on, and (6) the identity of the sender.
+A DApp interaction includes the following components: (1) the code of the DApp, (2) the current state of the DApp, (3) the name of the function being invoked, (4) the parameters supplied to the function, (5) the address of the contract the function is being invoked on, and (6) the identity of the sender.
 Confidentiality applied to a DApp could mean different levels of protection for each of these.
@@
 %Shayan -> TODO: Jeremy: the following probably needs some rewrite to focus on the solution rather than the issue.
-Another example in the design of ERC20 standard~\cite{erc20}, is on the allowance functionality.
+Another example in the design of ERC20 standard~\cite{erc20} is the allowance functionality.
 \textit{approve()} function in the specification allows a second entity to be able to spend N tokens from the sender's balance.
@@
 Front-running is a pervasive issue in Ethereum DApps.
+DApp developers don't necessarily have the mindset to design DApps with front-running in mind.
+This is an attempt to bring forward the subject and make more awareness of these type of attacks.
 While some DApp-level application logic could be built to mitigate these attacks, its ubiquity across different DApp categories suggests mitigations at the blockchain-level would perhaps be more effective.

### 2019-02-19 frontrunning/Latex/sections/paper.tex
[frontrunning] minor fixes

@@
 In a \textit{suppression attack}, after Mallory runs her function, she tries to delay Alice from running her function.
-After the delay, she is invariant to whether Alice's function runs or not.
+After the delay, she is indifferent to whether Alice's function runs or not.
 We only observe this attack pattern in one DApp and the details are quite specific to it, so we defer discussion until Section~\ref{sec:gambling}.
@@
 Each of these attacks have two variants, \textit{asymmetric} and \textit{bulk}.
-For example, Alice's function and Mallory's function are different: \eg Alice trying to cancel an offer and Mallory fulfilling the offer first.
+In some cases, Alice and Mallory are performing different operations.
+For example, Alice is trying to cancel an offer, and Mallory is trying to fulfill it first.
 We call this \textit{asymmetric displacement}.
-Finally, in some cases, Mallory is trying to run a large set of functions: for example Alice and others are trying to buy a limited set of shares offered by a firm on a blockchain.
+In other cases, Mallory is trying to run a large set of functions: for example Alice and others are trying to buy a limited set of shares offered by a firm on a blockchain.
 We call this \textit{bulk displacement}.
@@
 
-The applicability of privacy-preserving blockchains needs to be evaluated on a case-by-case base.
+The applicability of privacy-preserving blockchains needs to be evaluated on a case-by-case basis.
 For example, one method used by traditional financial exchanges in dealing with front-running from high frequency traders is a dark pool: essentially a (2,3,4)-confidential order book maintained by a trusted party.
@@
 The essence of the approach is to protect the function call (\eg (3,4)- or (4)-confidentiality) until the function is enqueued in a sequence of functions to be executed.
-Once the sequence is established, the confidentiality is lifted and the function can only be executed in the place it was given (or, generally speaking, not at all).
+Once the sequence is established, the confidentiality is lifted and the function can only be executed in the order it was enqueued (or, generally speaking, not at all).
 
@@
 DApp developers don't necessarily have the mindset to design DApps with front-running in mind.
-This is an attempt to bring forward the subject and make more awareness of these type of attacks.
+This is an attempt to bring forward the subject and increase awareness of these type of attacks.
 While some DApp-level application logic could be built to mitigate these attacks, its ubiquity across different DApp categories suggests mitigations at the blockchain-level would perhaps be more effective.

### 2019-04-09 frontrunning/Latex/sections/paper.tex
[front-running] remove appendix. full 16 pages.

@@
 Consider Cryptokitties~\cite{cryptokitties}, the most active DApp in this category and third most active overall.
-Each kitty (see Appendix~\ref{app:cryptokitty}) is a cartoon kitten with a set of unique features to distinguish it from other cryptokitties, some features are rarer and harder to obtain.
+Each kitty is a cartoon kitten with a set of unique features to distinguish it from other cryptokitties, some features are rarer and harder to obtain.
 They can be bought, sold, or bred with other cryptokitties.
@@
 We also note that for DApps that are legally well-formed (\eg with identified parties and a clear jurisdiction), front-running attacks can violate laws, which is its own deterrent.
-We do not discuss this further here; see Appendix ~\ref{app:traditionalprevention}.
+
+\paragraph{Traditional Front-running Prevention Methods.} There are debates in traditional markets regarding the fact that front-running is considered to be a form of insider trading which deemed to be illegal.
+Traditional methods to prevent front-running mainly involves after the fact investigation and legal action against the front-runners~\cite{FTFrontrunning18}.
+As mentioned in section~\ref{traditionalFrontrunning}, defining front-running and educating the employees were the first step taken to prevent such issues in traditional markets, however, front-running became less likely to happen mainly because of the high fine and lawsuits against firms who behaved in an unethical way.
+Other methods such as dark pools~\cite{zhu2014dark,buti2011diving} and sealed bids~\cite{radner1989sealed} were discussed and implemented in a variety of regulated trading systems.
+The traditional methods to prevent front-running does not apply to blockchain applications, as mainly they are based on central enforcement and limitations, also in case of blockchains the actors who are front-running could be anonymous and the fear of lawsuits would not apply.
 
@@
 Recall that a commitment scheme enables one to commit to a digital value (\eg a statement, transaction, data, \etc) while keeping it a secret (\textit{hiding}), and then open it (and only it: \textit{binding}) at a later time of the committer's choosing~\cite{brassard1988minimum}.
-A common approach (conjectured to be hiding) is to submit the cryptographic hash of the value with a random nonce (for low entropy data) to a smart contract, and later reveal the original value and nonce which can be verified by the contract to correctly hash to the commitment (see Figure~\ref{fig:commitReveal} in Appendix~\ref{app:cr}).
+A common approach (conjectured to be hiding) is to submit the cryptographic hash of the value with a random nonce (for low entropy data) to a smart contract, and later reveal the original value and nonce which can be verified by the contract to correctly hash to the commitment (see Figure~\ref{fig:commitReveal}).
+
+\begin{figure}[t]
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={left,bottom},capbesidewidth=0.5\linewidth}}]{figure}[\FBwidth]
+{\caption{Commit and Reveal.
+User sends a commitment transaction with the hash of the data, After the commitment period is over, user sends her reveal transaction to the DApp revealing the information that matches the commitment.}\label{fig:commitReveal}}
+{\includegraphics[width=\linewidth]{figures/commit-reveal.png}}
+\end{figure}
 
